### 2017-05-02 paper.tex
notes on sequential Monte Carlo with neural network

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2017
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2017}

\usepackage{nips_2017}
\usepackage{dsfont}
% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2017}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfig} 
\usepackage{fancyvrb}

\usepackage{caption}
\usepackage{subcaption}

\fvset{fontsize=\footnotesize}

\usepackage{multirow}
\usepackage{array}

\usepackage{amssymb}
\usepackage{listings}
\usepackage{wrapfig}
\usepackage{tabularx}

\usepackage{verbatim}
 \usepackage{booktabs}
 % For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
% As of 2011, we use the hyperref package to produce hyperlinks in the
% resulting PDF.  If this breaks your system, please commend out the
% following usepackage line and replace \usepackage{icml2016} with
% \usepackage[nohyperref]{icml2016} above.
\usepackage{amsmath}
\usepackage{hyperref}
\DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays
\DeclareMathOperator{\argmin}{argmin} % no space, limits underneath in displays

\newcommand{\expect}{\mathds{E}} %{{\rm I\kern-.3em E}}
\newcommand{\probability}{\mathds{P}} %{{\rm I\kern-.3em P}}

\title{Inferring Graphics Programs from Images}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
  David S.~Hippocampus\thanks{Use footnote for providing further
    information about author (webpage, alternative
    address)---\emph{not} for acknowledging funding agencies.} \\
  Department of Computer Science\\
  Cranberry-Lemon University\\
  Pittsburgh, PA 15213 \\
  \texttt{hippo@cs.cranberry-lemon.edu} \\
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
% \nipsfinalcopy is no longer used

\maketitle

\begin{abstract}
\end{abstract}

\section{Neural networks for guiding SMC}

Let $L(\cdot | \cdot):\text{image}^2\to \mathcal{R}$ be our likelihood
function: it takes two images, an observed target image and a
hypothesized program output, and gives the likelihood of the observed
image conditioned on the program output. We want to sample from:
\begin{equation}
\probability [p|x]  \propto L(x | \text{render}(p)) \probability [p]
\end{equation}
where $\probability [p]$ is the prior probability of program $p$, and $x$ is the observed image.

Let $p$ be a program with $L$ lines, which we will write as $p = (p_1,p_2,\cdots,p_L)$. Assume the prior factors into:
\begin{equation}
  \probability [p]\propto \prod_{l\leq L}\probability [p_l]
\end{equation}
Define the distribution $q_L(\cdot)$, which happens to be proportional to the above posterior:
\begin{equation}
  q_L(p_1,p_2,\cdots,p_{L - 1},p_L)\propto q_{L - 1}(p_1,p_2,\cdots,p_{L - 1})\times \frac{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1}))}\times\probability [p_L]
\end{equation}
Now suppose we have some samples from $q_{L - 1}(\cdot)$, and that we
then sample a $p_L$ from a distribution proportional to $\frac{L(x |
  \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x |
  \text{render}(p_1,p_2,\cdots,p_{L - 1}))}\times\probability [p_L]$.
The resulting programs $p$ are distributed according to $q_L$, and so
are also distributed according to $\probability [p|x]$.

How do we sample $p_L$ from a distribution proportional to $\frac{L(x
  | \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x |
  \text{render}(p_1,p_2,\cdots,p_{L - 1}))}\times\probability [p_L]$?
We have a neural network that takes as input the target image $x$ and
the program so far, and produces a distribution over next lines of
code ($p_L$).  We write $\text{NN}(p_L | p_1,\cdots,p_{L - 1};x)$ for
the distribution output by the neural network. So we can sample from NN and then weight the samples by:
\begin{equation}
  w(p_L) = \frac{\probability [p_L]}{\text{NN}(p_L | p_1,\cdots,p_{L - 1};x)}\times \frac{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1}))}
\end{equation}
Then we can resample from these now weighted samples to get a new
population of particles (here programs are particles), where each
program now has $L$ lines instead of $L - 1$.

This procedure can be seen as a particle filter, where each successive
latent variable is another line of code, and the emission
probabilities are successive ratios of likelihoods under $L(\cdot |
\cdot)$.

\textbf{Comments for Dan}. Right now I'm not actually sampling from
the neural network - instead, I enumerate the top few hundred lines of
code suggested by the network, and then weight them by their
likelihoods.
So actually the form of NN is:
\begin{equation}
  \text{NN}(p_L | p_1,\cdots,p_{L - 1};x)\propto \begin{cases}
    1,&\text{ if }p_L \in \text{top hundred neural network proposals}\\
0,&\text{otherwise}.    \end{cases}
\end{equation}
Do you think this is a problem? The neural network puts almost all of its mass on a few guesses.
In order to get the correct line of code I sometimes need to get something like the 50th  top guess,
so I don't want to literally just sample from the distribution suggested by the neural network.

\section{Submission of papers to NIPS 2017}

NIPS requires electronic submissions.  The electronic submission site
is
\begin{center}
  \url{https://cmt.research.microsoft.com/NIPS2017/}
\end{center}

Please read carefully the instructions below and follow them
faithfully.

\subsection{Style}

Papers to be submitted to NIPS 2017 must be prepared according to the
instructions presented here. Papers may only be up to eight pages
long, including figures. This does not include acknowledgments and 
cited references which are allowed on subsequent pages.
Papers that exceed these limits will not be reviewed, or in any
other way considered for presentation at the conference.

The margins in 2017 are the same as since 2007, which allow for
$\sim$$15\%$ more words in the paper compared to earlier years.

Authors are required to use the NIPS \LaTeX{} style files obtainable
at the NIPS website as indicated below. Please make sure you use the
current files and not previous versions. Tweaking the style files may
be grounds for rejection.

\subsection{Retrieval of style files}

The style files for NIPS and other conference information are
available on the World Wide Web at
\begin{center}
  \url{http://www.nips.cc/}
\end{center}
The file \verb+nips_2017.pdf+ contains these instructions and
illustrates the various formatting requirements your NIPS paper must
satisfy.

The only supported style file for NIPS 2017 is \verb+nips_2017.sty+,
rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{}
  2.09, Microsoft Word, and RTF are no longer supported!}

The new \LaTeX{} style file contains two optional arguments:
\verb+final+, which creates a camera-ready copy, and \verb+nonatbib+,
which will not load the \verb+natbib+ package for you in case of
package clash.

At submission time, please omit the \verb+final+ option. This will
anonymize your submission and add line numbers to aid review.  Please
do \emph{not} refer to these line numbers in your paper as they will
be removed during generation of camera-ready copies.

The file \verb+nips_2017.tex+ may be used as a ``shell'' for writing
your paper. All you have to do is replace the author, title, abstract,
and text of the paper with your own.

The formatting instructions contained in these style files are
summarized in Sections \ref{gen_inst}, \ref{headings}, and
\ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas)
wide and 9~inches (54~picas) long. The left margin is 1.5~inch
(9~picas).  Use 10~point type with a vertical spacing (leading) of
11~points.  Times New Roman is the preferred typeface throughout, and
will be selected for you by default.  Paragraphs are separated by
\nicefrac{1}{2}~line space (5.5 points), with no indentation.

The paper title should be 17~point, initial caps/lower case, bold,
centered between two horizontal rules. The top rule should be 4~points
thick and the bottom rule should be 1~point thick. Allow
\nicefrac{1}{4}~inch space above and below the title to rules. All
pages should start at 1~inch (6~picas) from the top of the page.

For the final version, authors' names are set in boldface, and each
name is centered above the corresponding address. The lead author's
name is to be listed first (left-most), and the co-authors' names (if
different address) are set to follow. If there is only one co-author,
list both author and co-author side by side.

Please pay special attention to the instructions in Section \ref{others}
regarding figures, tables, acknowledgments, and references.

\section{Headings: first level}
\label{headings}

All headings should be lower case (except for first word and proper
nouns), flush left, and bold.

First-level headings should be in 12-point type.

\subsection{Headings: second level}

Second-level headings should be in 10-point type.

\subsubsection{Headings: third level}

Third-level headings should be in 10-point type.

\paragraph{Paragraphs}

There is also a \verb+\paragraph+ command available, which sets the
heading in bold, flush left, and inline with the text, with the
heading followed by 1\,em of space.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone.

\subsection{Citations within the text}

The \verb+natbib+ package will be loaded for you by default.
Citations may be author/year or numeric, as long as you maintain
internal consistency.  As to the format of the references themselves,
any style is acceptable as long as it is used consistently.

The documentation for \verb+natbib+ may be found at
\begin{center}
  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
\end{center}
Of note is the command \verb+\citet+, which produces citations
appropriate for use in inline text.  For example,
\begin{verbatim}
   \citet{hasselmo} investigated\dots
\end{verbatim}
produces
\begin{quote}
  Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

If you wish to load the \verb+natbib+ package with options, you may
add the following before loading the \verb+nips_2017+ package:
\begin{verbatim}
   \PassOptionsToPackage{options}{natbib}
\end{verbatim}

If \verb+natbib+ clashes with another package you load, you can add
the optional argument \verb+nonatbib+ when loading the style file:
\begin{verbatim}
   \usepackage[nonatbib]{nips_2017}
\end{verbatim}

As submission is double blind, refer to your own published work in the
third person. That is, use ``In the previous work of Jones et
al.\ [4],'' not ``In our previous work [4].'' If you cite your other
papers that are not widely available (e.g., a journal paper under
review), use anonymous author names in the citation, e.g., an author
of the form ``A.\ Anonymous.''

\subsection{Footnotes}

Footnotes should be used sparingly.  If you do require a footnote,
indicate footnotes with a number\footnote{Sample of the first
  footnote.} in the text. Place the footnotes at the bottom of the
page on which they appear.  Precede the footnote with a horizontal
rule of 2~inches (12~picas).

Note that footnotes are properly typeset \emph{after} punctuation
marks.\footnote{As in this example.}

\subsection{Figures}

All artwork must be neat, clean, and legible. Lines should be dark
enough for purposes of reproduction. The figure number and caption
always appear after the figure. Place one line space before the figure
caption and one line space after the figure. The figure caption should
be lower case (except for first word and proper nouns); figures are
numbered consecutively.

You may use color figures.  However, it is best for the figure
captions and the paper body to be legible if the paper is printed in
either black/white or in color.
\begin{figure}[h]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  \caption{Sample figure caption.}
\end{figure}

\subsection{Tables}

All tables must be centered, neat, clean and legible.  The table
number and title always appear before the table.  See
Table~\ref{sample-table}.

Place one line space before the table title, one line space after the
table title, and one line space after the table. The table title must
be lower case (except for first word and proper nouns); tables are
numbered consecutively.

Note that publication-quality tables \emph{do not contain vertical
  rules.} We strongly suggest the use of the \verb+booktabs+ package,
which allows for typesetting high-quality, professional tables:
\begin{center}
  \url{https://www.ctan.org/pkg/booktabs}
\end{center}
This package was used to typeset Table~\ref{sample-table}.

\begin{table}[t]
  \caption{Sample table title}
  \label{sample-table}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{2}{c}{Part}                   \\
    \cmidrule{1-2}
    Name     & Description     & Size ($\mu$m) \\
    \midrule
    Dendrite & Input terminal  & $\sim$100     \\
    Axon     & Output terminal & $\sim$10      \\
    Soma     & Cell body       & up to $10^6$  \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Final instructions}

Do not change any aspects of the formatting parameters in the style
files.  In particular, do not modify the width or length of the
rectangle the text should fit into, and do not change font sizes
(except perhaps in the \textbf{References} section; see below). Please
note that pages should be numbered.

\section{Preparing PDF files}

Please prepare submission files with paper size ``US Letter,'' and
not, for example, ``A4.''

Fonts were the main cause of problems in the past years. Your PDF file
must only contain Type 1 or Embedded TrueType fonts. Here are a few
instructions to achieve this.

\begin{itemize}

\item You should directly generate PDF files using \verb+pdflatex+.

\item You can check which fonts a PDF files uses.  In Acrobat Reader,
  select the menu Files$>$Document Properties$>$Fonts and select Show
  All Fonts. You can also use the program \verb+pdffonts+ which comes
  with \verb+xpdf+ and is available out-of-the-box on most Linux
  machines.

\item The IEEE has recommendations for generating PDF files whose
  fonts are also acceptable for NIPS. Please see
  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}

\item \verb+xfig+ "patterned" shapes are implemented with bitmap
  fonts.  Use "solid" shapes instead.

\item The \verb+\bbold+ package almost always uses bitmap fonts.  You
  should use the equivalent AMS Fonts:
\begin{verbatim}
   \usepackage{amsfonts}
\end{verbatim}
followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or
\verb+\mathbb{C}+ for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You
can also use the following workaround for reals, natural and complex:
\begin{verbatim}
   \newcommand{\RR}{I\!\!R} %real numbers
   \newcommand{\Nat}{I\!\!N} %natural numbers
   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
\end{verbatim}
Note that \verb+amsfonts+ is automatically loaded by the
\verb+amssymb+ package.

\end{itemize}

If your file contains type 3 fonts or non embedded TrueType fonts, we
will ask you to fix it.

\subsection{Margins in \LaTeX{}}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+ from the \verb+graphicx+ package. Always
specify the figure width as a multiple of the line width as in the
example below:
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
See Section 4.4 in the graphics bundle documentation
(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})

A number of width problems arise when \LaTeX{} cannot properly
hyphenate a line. Please give LaTeX hyphenation hints using the
\verb+\-+ command when necessary.

\subsubsection*{Acknowledgments}

Use unnumbered third level headings for the acknowledgments. All
acknowledgments go at the end of the paper. Do not include
acknowledgments in the anonymized submission, only in the final paper.

\section*{References}

References follow the acknowledgments. Use unnumbered first-level
heading for the references. Any choice of citation style is acceptable
as long as you are consistent. It is permissible to reduce the font
size to \verb+small+ (9 point) when listing the references. {\bf
  Remember that you can go over 8 pages as long as the subsequent ones contain
  \emph{only} cited references.}
\medskip

\small

[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms
for connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and
T.K.\ Leen (eds.), {\it Advances in Neural Information Processing
  Systems 7}, pp.\ 609--616. Cambridge, MA: MIT Press.

[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS:
  Exploring Realistic Neural Models with the GEneral NEural SImulation
  System.}  New York: TELOS/Springer--Verlag.

[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of
learning and recall at excitatory recurrent synapses and cholinergic
modulation in rat hippocampal region CA3. {\it Journal of
  Neuroscience} {\bf 15}(7):5249-5262.

\end{document}

### 2017-05-02 handout.tex
handout for human subjects

\documentclass{article}
\usepackage{tikz}
\usepackage[margin=0.1in]{geometry}
\begin{document}
\centering\textbf{CoCoSci NIPS Data Blitz!}

Draw diagrams on a grid. You can draw rectangles, lines, arrows,
dashed lines, and circles of radius 1.  Your drawings don't have to be
perfect, but they should be good enough for a human to understand. On
the last grid you can draw whatever diagram you want.

\centering
\begin{tikzpicture}[scale = 0.5]
  \node[align = right] at (5,14) {Here is an example diagram:};
  \draw[step=1cm,gray,ultra thin] (0,0) grid (13,13);
  \draw[ultra thick] (3,3) circle (1cm);
  \draw[ultra thick] (3,8) circle (1cm);
  \draw[line width = 0.1cm,dashed] (3,4) -- (3,7);
  \draw[ultra thick] (8,3) rectangle (13,10);
  \draw[ultra thick] (9,4) rectangle (12,9);
  \draw[ultra thick,-{>[scale = 1.5]}]  (4,3) -- (8,4);
  \draw[ultra thick,-{>[scale = 1.5]}]  (4,3+5) -- (8,4+5);

    \node[align = right] at (5 + 19,14) {Can you copy the diagram on to this grid?};
    \draw[step=1cm,gray,ultra thin] (17,0) grid (13+17,13);

  \node[align = right] at (5,14 - 16) {Come up with a new diagram:};
  \draw[step=1cm,gray,ultra thin] (0,0-16) grid (13,13 - 16);

  \node[align = right] at (5 + 17,14 - 16) {Come up with a new diagram:};
  \draw[step=1cm,gray,ultra thin] (17,0-16) grid (13 + 17,13 - 16);

  \node[align = right] at (5,14 - 16 - 16) {Come up with a new diagram:};
  \draw[step=1cm,gray,ultra thin] (0,0-16 - 16) grid (13,13 - 16 - 16);

  \node[align = center] at (8 + 17,14 - 16 - 16) {Diagram anything you want\\(stars, text, ellipses, spirals, thought bubbles, fractals, flowcharts, ...)};
  \draw[step=1cm,gray,ultra thin] (17,0-16 - 16) grid (13 + 17,13 - 16 - 16);
\end{tikzpicture}

\end{document}

### 2017-05-03 paper.tex
pseudocode for SMC

@@
 
+\section{Introducing visual programs}
+
+In this work we consider programs that draw diagrams, similar to those found in papers.
+
 \section{Neural networks for guiding SMC}
@@
 so I don't want to literally just sample from the distribution suggested by the neural network.
+
+  \begin{algorithm}[tb]
+   \caption{Neurally guided SMC}
+   \label{guideAlgorithm}
+\begin{algorithmic}
+  \STATE {\bfseries Input:} Neural network NN, beam size $N$, maximum length $L$, target image $x$
+  \STATE {\bfseries Output:} Samples of the program trace
+  \STATE Set $B_0 = \{\text{empty program}\}$
+  \FOR{$1\leq l\leq L$}
+  \FOR{$1\leq n\leq N$}
+  \STATE{ $p_n\sim \text{Uniform}(B_{l - 1})$}
+  \STATE{ $p'_{n}\sim \text{NN}(\text{render}(p),x)$}
+  \STATE{ Define $r_n = p'_n\cdot p_n$}
+  \STATE{ Set $\tilde{w}(r_n) = \frac{L(x|r_n)}{L(x|p_n)}\times\frac{\probability [p'_n]}{\probability [p'_n = \text{NN}(\text{render}(p),x)]}$}
+  \ENDFOR
+  \STATE{ Define $w(p) = \frac{\tilde{w}(p)}{\sum_{p'}\tilde{w}(p')}$}
+  \STATE{ Set $B_l$ to be $N$ samples from $r_n$ distributed according to $w(\cdot)$}
+  \ENDFOR
+  \STATE {\bfseries return} $\{p : p\in B_{l\leq L}, p \text{ is finished}\}$
+\end{algorithmic}
+  \end{algorithm}
 

### 2017-05-03 handout.tex
handout improvements

@@
 \documentclass{article}
+\usepackage[most]{tcolorbox}
 \usepackage{tikz}
@@
 
-Draw diagrams on a grid. You can draw rectangles, lines, arrows,
-dashed lines, and circles of radius 1.  Your drawings don't have to be
+Draw diagrams, sometimes on a grid. You can draw rectangles, lines, arrows,
+dashed lines, and circles of radius 1 grid cell.  Your drawings don't have to be
 perfect, but they should be good enough for a human to understand. On
@@
 \begin{tikzpicture}[scale = 0.5]
-  \node[align = right] at (5,14) {Here is an example diagram:};
+  \node[align = right] at (5,14) {Copy (a) onto the grid below:};
   \draw[step=1cm,gray,ultra thin] (0,0) grid (13,13);
@@
 
-    \node[align = right] at (5 + 19,14) {Can you copy the diagram on to this grid?};
-    \draw[step=1cm,gray,ultra thin] (17,0) grid (13+17,13);
+  \node[align = right] at (5 + 19,14) {Copy (b) onto the region below:};
+    \draw[step=1cm,gray,ultra thin] (17,0) rectangle (13+17,13);
 
-  \node[align = right] at (5,14 - 16) {Come up with a new diagram:};
+  \node[align = right] at (5,14 - 16) {Come up with a new diagram on a grid:};
   \draw[step=1cm,gray,ultra thin] (0,0-16) grid (13,13 - 16);
 
-  \node[align = right] at (5 + 17,14 - 16) {Come up with a new diagram:};
-  \draw[step=1cm,gray,ultra thin] (17,0-16) grid (13 + 17,13 - 16);
+  \node[align = right] at (5 + 17,14 - 16) {Come up with a new diagram (no grid):};
+  \draw[step=1cm,gray,ultra thin] (17,0-16) rectangle (13 + 17,13 - 16);
 
-  \node[align = right] at (5,14 - 16 - 16) {Come up with a new diagram:};
+  \node[align = right] at (5,14 - 16 - 16) {Come up with a new diagram on a grid:};
   \draw[step=1cm,gray,ultra thin] (0,0-16 - 16) grid (13,13 - 16 - 16);
@@
   \node[align = center] at (8 + 17,14 - 16 - 16) {Diagram anything you want\\(stars, text, ellipses, spirals, thought bubbles, fractals, flowcharts, ...)};
-  \draw[step=1cm,gray,ultra thin] (17,0-16 - 16) grid (13 + 17,13 - 16 - 16);
+  \draw[step=1cm,gray,ultra thin] (17,0-16 - 16) rectangle (13 + 17,13 - 16 - 16);
 \end{tikzpicture}
 
+\pagebreak
+
+\begin{tabular}{cc}
+\textbf{(a)}  \tcbox{\includegraphics[width = 5cm]{figures/expert-58.png}}&  \textbf{(b)} \tcbox{\includegraphics[width = 5cm]{figures/expert-36.png}}\\
+\textbf{(c)}    \tcbox{\includegraphics[width = 5cm]{figures/expert-34.png}}&\textbf{(d)}  \tcbox{\includegraphics[width = 5cm]{figures/expert-38.png}}\\
+\textbf{(e)}  \tcbox{\includegraphics[width = 5cm]{figures/expert-1.png}}&  \textbf{(f)}\tcbox{\includegraphics[width = 5cm]{figures/randomScene-33-5.png}}\\
+\textbf{(g)}  \tcbox{\includegraphics[width = 5cm]{figures/randomScene-58-7.png}}&  \textbf{(h)}\tcbox{\includegraphics[width = 5cm]{figures/randomScene-58-noisy.png}}\\
+\end{tabular}
+
 \end{document}

### 2017-05-05 paper.tex
figure explaining neural network: needs work

@@
 \usepackage{tikz}
+\usetikzlibrary{fit}
 % As of 2011, we use the hyperref package to produce hyperlinks in the
@@
 In this work we consider programs that draw diagrams, similar to those found in papers.
+
+\section{Neural architecture for inferring image parses}
+
+\begin{tikzpicture}
+  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image](observation) at (0,0) {\includegraphics[width = 3cm]{figures/expert-18.png}};
+  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm,label=below:Canvas] (canvas) at (0,-5) {};
+
+  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm] (CNN) at (4.5,-2.5) {CNN};
+
+  \node[rotate = -90,draw,thick,inner sep=0pt,minimum width = 3cm,minimum height = 0.5cm] (features) at ([xshift = 1cm]CNN.east) {Image features};
+
+  \node[draw,thick,circle,minimum size = 1cm](c1) at ([xshift = 1.5cm]features.north);
+  \node(l1) at ([yshift = -2cm]c1.south) {\verb|CIRCLE(|};
+  \node[draw,thick,circle,minimum size = 1cm](c2) at ([xshift = 1cm]c1.east);
+  \draw[->,thick] (c1.south) -- (l1.north);
+  \node(l2) at ([yshift = -2cm]c2.south) {\verb|X=3,|};
+  \draw[->,thick] (c2.south) -- (l2.north);
+  \node[draw,thick,circle,minimum size = 1cm](c3) at ([xshift = 1cm]c2.east);
+  \node(l3) at ([yshift = -2cm]c3.south) {\verb|Y=14)|};
+  \draw[->,thick] (c3.south) -- (l3.north);
+
+  \draw[->,thick] (features.north) -- (c1.west);
+  \draw[->,thick] (c1.east) -- (c2.west);
+  \draw[->,thick] (c2.east) -- (c3.west);
+
+  \node(next)[draw,fit = (l1) (l2) (l3), dashed, label = below:{Next line of code}] {};
+
+  \draw[->,thick,dashed] (next.west) -- node[below] {Renderer} (canvas.east);
+
+  \draw[->,thick] (canvas.east) -- ([yshift = -0.5cm]CNN.west);
+  \draw[->,thick] (observation.east) -- ([yshift = 0.5cm]CNN.west);
+  \draw[->,thick] (CNN.east) -- (features.south);
+%  \draw[]
+
+%  \node at (canvas.x,canvas.y) {Canvas};
+
+  \end{tikzpicture}
 

### 2017-05-06 paper.tex
new figures and committed content you need to compile the paper

@@
 
+We develop a hybrid architecture for inferring graphics programs.  Our
+approach uses a deep network infer an execution trace from an image;
+this recovers primitive drawing operations like lines, circles, or
+arrows.  For added robustness we use the deep network as a proposal
+distribution for a stochastic search over execution traces.
+Finally we use techniques in the program synthesis community to
+recover the program from its trace.
+
+Each of these three components -- the deep network, the stochastic
+search, the program synthesizer -- confers its own advantages. From
+the deep network we get a very fast system that can recover plausible
+execution traces in about a minute. From the stochastic search we get
+added robustness; essentially the stochastic search can correct
+mistakes made by the deep network's proposals.  From the program
+synthesizer we get abstraction: our system recovers coordinate
+transformations, for loops, and subroutines, which are useful for
+downstream tasks.
+
 \section{Neural architecture for inferring image parses}
@@
   \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm,label=below:Canvas] (canvas) at (0,-5) {};
+  % draw partial image on canvas
+  \draw (0.5cm,-4cm) circle (0.1875cm);
+  \draw (1.2cm,-4.3) circle (0.1875cm);
+  \draw (0.85cm,-4.6) circle (0.1875cm);
 
@@
 \end{tikzpicture}
+
+\section{Generalizing to hand drawings}
+
+\begin{figure}
+  \begin{minipage}[b]{0.3\textwidth}
+    \centering\includegraphics[width = 3cm]{figures/expert-60.png}
+    \subcaption{(a)}
+  \end{minipage}%
+  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 3cm]{figures/60-groundTruth.png}
+    \subcaption{(b)}
+  \end{minipage}\\
+  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 3cm]{figures/60-1.png}
+    \subcaption{(c)}
+  \end{minipage}%
+  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 3cm]{figures/60-2.png}
+    \subcaption{(d)}
+  \end{minipage}
+  \caption{(a): a hand drawing.
+(b): Rendering of the parse our model infers for (a).
+We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) \& (d) for noisy renderings of (b).}
+  \end{figure}
 

### 2017-05-06 paper.tex
description of neural architecture

@@
 
+We developed a deep network architecture for efficiently inferring a
+execution trace, $T$, from an image, $I$.  Our model constructs the
+trace one drawing command at a time.  When predicting the next drawing
+command, the network takes as input the target image $I$ as well as
+the rendered output of previous drawing commands.  Intuitively, the
+network looks at the image it wants to explain, as well as what it has
+already drawn.  It then decides either to stop drawing or proposes
+another drawing command to add to the execution trace; if it decides
+to continue drawing, the predicted primitive is rendered to its
+``canvas'' and the process repeats.
+
+Figure~\ref{architecture} illustrates this architecture.  We first
+pass the target image and a rendering of the trace so far to a
+convolutional network. Given the features extracted by the
+convolutionional network, a multilayer perceptron then predicts a
+distribution over the next drawing command to add to the trace.  We
+predict the drawing command token-by-token, and condition each token
+both on the image features and on the previously generated tokens.
+For example, the network first decides to emit the \verb|CIRCLE| token
+conditioned on the image features, then it emits the $x$ coordinate of
+the circle conditioned on the image features and the \verb|CIRCLE|
+token, and finally it predicts the $y$ coordinate of the circle
+conditioned on the image features, the \verb|CIRCLE| token, and the
+$x$ coordinate.
+
+The distribution over the next drawing command factorizes:
+\begin{equation}
+  \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta [t_k | f_\theta(I,\text{render}(T)), \{t_j\}_{j = 1}^{k - 1}]
+\end{equation}
+where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
+the target image, $T$ is an execution trace, $\theta$ are the
+parameters of the neural network, and $f_\theta(\cdot,\cdot)$ is the
+image feature extractor (convolutional network). The distribution over
+execution traces factorizes as:
+\begin{equation}
+  \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
+\end{equation}
+where $|T|$ is the length of execution trace $T$, and the \verb|STOP|
+token is emitted by the network to signal that the execution trace
+explains the image.
+
+We train the network by sampling execution traces $T$ and target
+images $I$ for randomly generated scenes, and maximizing
+(\ref{objective}) wrt $\theta$ by gradient ascent. Despite the
+architecture being recurrent, training is fully supervised. In a
+sense, this model is like an autoregressive variant of AIR. When we
+have the generative model (the rendering function), we need not solve
+an unsupervised or reinforcement learning problem.
+
 \begin{tikzpicture}
-  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image](observation) at (0,0) {\includegraphics[width = 3cm]{figures/expert-18.png}};
-  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm,label=below:Canvas] (canvas) at (0,-5) {};
+  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image $I$](observation) at (0,0) {\includegraphics[width = 3cm]{figures/expert-18.png}};
+  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm,label=below:Canvas: render$(T)$] (canvas) at (0,-5) {};
   % draw partial image on canvas
@@
 %  \node at (canvas.x,canvas.y) {Canvas};
-
+\caption{Our neural architecture for inferring the execution trace of a graphics program from its output.}  \label{architecture}
 \end{tikzpicture}

### 2017-05-06 paper.tex
new introduction

@@
 
+\textbf{Comment for reader: this paragraph is a little grandiose and goes
+  beyond what we've actually done. But these are the kinds of things
+  that motivate the work, and I think that in some form these ideas
+  should be in the introduction or the conclusion.} How could an agent go from noisy,
+high-dimensional perceptual input to a symbolic, abstract object, like
+a computer program?  Here we consider this problem within the context
+of \emph{graphics program synthesis}.  We develop an approach for
+converting natural images, such as hand drawings, into executable
+source code for drawing the original image.
+The source code captures not just the objects in the image,
+but also describes their geometric relationships.
+
+High dimensional perceptual input is ill matched to the abstract
+semantics of a programming language. But programs with constructs like
+recursion or iteration produce a simpler \emph{execution trace} of
+primitive actions. Our hypothesis is that the execution trace of the
+program is better aligned with the perceptual input, and that the
+trace can act as a kind of bridge between perception and programs. We
+test this hypothesis by developing a model that learns to map from an
+image to the execution trace of the graphics program that drew it.
+With the execution trace in hand, we can bring to bear techniques from
+the program synthesis community to recover the latent graphics program.
+
 In this work we consider programs that draw diagrams, similar to those found in papers.
@@
 sense, this model is like an autoregressive variant of AIR. When we
-have the generative model (the rendering function), we need not solve
-an unsupervised or reinforcement learning problem.
+have the generative model (the rendering function) and treat the trace
+as fully observed, we need not solve an unsupervised or reinforcement
+learning problem.
 
+\begin{figure}
   \begin{tikzpicture}
-  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image $I$](observation) at (0,0) {\includegraphics[width = 3cm]{figures/expert-18.png}};
+  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image: $I$](observation) at (0,0) {\includegraphics[width = 3cm]{figures/expert-18.png}};
   \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm,label=below:Canvas: render$(T)$] (canvas) at (0,-5) {};
@@
 
-  \draw[->,thick,dashed] (next.west) -- node[below] {Renderer} (canvas.east);
+  \draw[->,thick,dashed] (next.west) -- node[below] {Renderer: \LaTeX} (canvas.east);
 
@@
 %  \node at (canvas.x,canvas.y) {Canvas};
+\end{tikzpicture}
 \caption{Our neural architecture for inferring the execution trace of a graphics program from its output.}  \label{architecture}
-\end{tikzpicture}
+  \end{figure}
+
+\begin{table}
+\begin{tabular}{ll}\toprule
+  \begin{tabular}{l}
+    \verb|CIRCLE|$(x,y)$
+    \end{tabular}& Circle at $(x,y)$\\
+  \begin{tabular}{l}
+    \verb|RECTANGLE|$(x_1,y_1,x_2,y_2)$
+    \end{tabular}&Rectangle with corners at $(x_1,y_1)$ \& $(x_2,y_2)$\\
+  \begin{tabular}{l}
+    \verb|LINE|$(x_1,y_1,x_2,y_2,$\\
+    \hspace{1cm}$\text{arrow}\in\{0,1\},\text{dashed}\in\{0,1\})$
+    \end{tabular}&Line from $(x_1,y_1)$ to  $(x_2,y_2)$, optionally with an arrow and/or dashed\\
+  \begin{tabular}{l}
+    \verb|STOP|
+  \end{tabular}&Finishes execution trace inference
+\\  \bottomrule
+\end{tabular}
+\caption{The deep network in (\ref{architecture}) predicts drawing commands, shown above.}
+\label{drawingCommandTable}
+\end{table}
 
@@
   \end{figure}
+
+\section{Synthesizing graphics programs from execution traces}
+
+\begin{table}
+  \begin{tabular}{rl}
+  Program$\to$&Command; $\cdots$; Command\\
+  Command$\to$&\texttt{CIRCLE}(Expression,Expression)\\
+  Command$\to$&\texttt{RECTANGLE}(Expression,Expression,Expression,Expression)\\
+  Command$\to$&\texttt{LINE}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
+  Command$\to$&\texttt{FOR}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ }Program\texttt{ \}}\\
+  Command$\to$&\texttt{REFLECT}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
+  Expression$\to$&\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}\\
+  Var$\to$&A free (unused) variable\\
+  \mathcal{Z}$\to$&an integer\\
+  Axis$\to$&\texttt{X = }\mathcal{Z}\\
+  Axis$\to$&\texttt{Y = }\mathcal{Z}
+  \end{tabular}
+  \caption{Grammar over graphics programs.
+We allow loops (\texttt{FOR}), vertical/horizontal reflections (\texttt{REFLECT}), and affine transformations (\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}).}
+  \end{table}
 

### 2017-05-08 paper.tex
removed the sentence
related work

@@
 
-\textbf{Comment for reader: this paragraph is a little grandiose and goes
-  beyond what we've actually done. But these are the kinds of things
-  that motivate the work, and I think that in some form these ideas
-  should be in the introduction or the conclusion.} How could an agent go from noisy,
+How could an agent go from noisy,
 high-dimensional perceptual input to a symbolic, abstract object, like
@@
 source code for drawing the original image.
-The source code captures not just the objects in the image,
-but also describes their geometric relationships.
 
@@
 downstream tasks.
+
+\section{Related work}
+attend infer repeat:~\cite{eslami1603attend}. Crucial distinction is
+that they focus on learning the generative model jointly with the
+inference network. Advantages of our system is that we learn symbolic
+programs, and that we do it from hand sketches rather than synthetic
+renderings.
+
+ngpm:~\cite{ritchie2016neurally}. We build on the idea of a guide program, extending it to scenes composed of objects, and then show how to learn programs from the objects we discover.
+
+Sketch-n-Sketch:~\cite{Hempel:2016:SSP:2984511.2984575}.
+Semiautomated synthesis presented in a nice user interface.
+Complementary to our work: you could pass a sketch to our system and then pass the program to sketch-n-sketch
+
+Converting hand drawings into procedural models using deep networks:~\cite{huang2017shape,Nishida:2016:ISU:2897824.2925951}.
 
@@
 architecture being recurrent, training is fully supervised. In a
-sense, this model is like an autoregressive variant of AIR. When we
-have the generative model (the rendering function) and treat the trace
-as fully observed, we need not solve an unsupervised or reinforcement
-learning problem.
+sense, this model is like an autoregressive variant of AIR.
+
+%% When we
+%% have the generative model (the rendering function) and treat the trace
+%% as fully observed, we need not solve an unsupervised or reinforcement
+%% learning problem.
 
@@
 
+\section{Contributions}
+
+We see this system as a first step towards more powerful graphics
+program synthesizers.  We look forward to, in the near future, being
+able to hand-draw our figures and automatically convert them into
+publication-quality \LaTeX code.
+
+\pagebreak
+
 \section{Neural networks for guiding SMC}
@@
 
-\section{Submission of papers to NIPS 2017}
-
-NIPS requires electronic submissions.  The electronic submission site
-is
-\begin{center}
-  \url{https://cmt.research.microsoft.com/NIPS2017/}
-\end{center}
-
-Please read carefully the instructions below and follow them
-faithfully.
-
-\subsection{Style}
-
-Papers to be submitted to NIPS 2017 must be prepared according to the
-instructions presented here. Papers may only be up to eight pages
-long, including figures. This does not include acknowledgments and 
-cited references which are allowed on subsequent pages.
-Papers that exceed these limits will not be reviewed, or in any
-other way considered for presentation at the conference.
-
-The margins in 2017 are the same as since 2007, which allow for
-$\sim$$15\%$ more words in the paper compared to earlier years.
-
-Authors are required to use the NIPS \LaTeX{} style files obtainable
-at the NIPS website as indicated below. Please make sure you use the
-current files and not previous versions. Tweaking the style files may
-be grounds for rejection.
-
-\subsection{Retrieval of style files}
-
-The style files for NIPS and other conference information are
-available on the World Wide Web at
-\begin{center}
-  \url{http://www.nips.cc/}
-\end{center}
-The file \verb+nips_2017.pdf+ contains these instructions and
-illustrates the various formatting requirements your NIPS paper must
-satisfy.
-
-The only supported style file for NIPS 2017 is \verb+nips_2017.sty+,
-rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{}
-  2.09, Microsoft Word, and RTF are no longer supported!}
-
-The new \LaTeX{} style file contains two optional arguments:
-\verb+final+, which creates a camera-ready copy, and \verb+nonatbib+,
-which will not load the \verb+natbib+ package for you in case of
-package clash.
-
-At submission time, please omit the \verb+final+ option. This will
-anonymize your submission and add line numbers to aid review.  Please
-do \emph{not} refer to these line numbers in your paper as they will
-be removed during generation of camera-ready copies.
-
-The file \verb+nips_2017.tex+ may be used as a ``shell'' for writing
-your paper. All you have to do is replace the author, title, abstract,
-and text of the paper with your own.
-
-The formatting instructions contained in these style files are
-summarized in Sections \ref{gen_inst}, \ref{headings}, and
-\ref{others} below.
-
-\section{General formatting instructions}
-\label{gen_inst}
-
-The text must be confined within a rectangle 5.5~inches (33~picas)
-wide and 9~inches (54~picas) long. The left margin is 1.5~inch
-(9~picas).  Use 10~point type with a vertical spacing (leading) of
-11~points.  Times New Roman is the preferred typeface throughout, and
-will be selected for you by default.  Paragraphs are separated by
-\nicefrac{1}{2}~line space (5.5 points), with no indentation.
-
-The paper title should be 17~point, initial caps/lower case, bold,
-centered between two horizontal rules. The top rule should be 4~points
-thick and the bottom rule should be 1~point thick. Allow
-\nicefrac{1}{4}~inch space above and below the title to rules. All
-pages should start at 1~inch (6~picas) from the top of the page.
-
-For the final version, authors' names are set in boldface, and each
-name is centered above the corresponding address. The lead author's
-name is to be listed first (left-most), and the co-authors' names (if
-different address) are set to follow. If there is only one co-author,
-list both author and co-author side by side.
-
-Please pay special attention to the instructions in Section \ref{others}
-regarding figures, tables, acknowledgments, and references.
-
-\section{Headings: first level}
-\label{headings}
-
-All headings should be lower case (except for first word and proper
-nouns), flush left, and bold.
-
-First-level headings should be in 12-point type.
-
-\subsection{Headings: second level}
-
-Second-level headings should be in 10-point type.
-
-\subsubsection{Headings: third level}
-
-Third-level headings should be in 10-point type.
-
-\paragraph{Paragraphs}
-
-There is also a \verb+\paragraph+ command available, which sets the
-heading in bold, flush left, and inline with the text, with the
-heading followed by 1\,em of space.
-
-\section{Citations, figures, tables, references}
-\label{others}
-
-These instructions apply to everyone.
-
-\subsection{Citations within the text}
-
-The \verb+natbib+ package will be loaded for you by default.
-Citations may be author/year or numeric, as long as you maintain
-internal consistency.  As to the format of the references themselves,
-any style is acceptable as long as it is used consistently.
-
-The documentation for \verb+natbib+ may be found at
-\begin{center}
-  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
-\end{center}
-Of note is the command \verb+\citet+, which produces citations
-appropriate for use in inline text.  For example,
-\begin{verbatim}
-   \citet{hasselmo} investigated\dots
-\end{verbatim}
-produces
-\begin{quote}
-  Hasselmo, et al.\ (1995) investigated\dots
-\end{quote}
-
-If you wish to load the \verb+natbib+ package with options, you may
-add the following before loading the \verb+nips_2017+ package:
-\begin{verbatim}
-   \PassOptionsToPackage{options}{natbib}
-\end{verbatim}
-
-If \verb+natbib+ clashes with another package you load, you can add
-the optional argument \verb+nonatbib+ when loading the style file:
-\begin{verbatim}
-   \usepackage[nonatbib]{nips_2017}
-\end{verbatim}
-
-As submission is double blind, refer to your own published work in the
-third person. That is, use ``In the previous work of Jones et
-al.\ [4],'' not ``In our previous work [4].'' If you cite your other
-papers that are not widely available (e.g., a journal paper under
-review), use anonymous author names in the citation, e.g., an author
-of the form ``A.\ Anonymous.''
-
-\subsection{Footnotes}
-
-Footnotes should be used sparingly.  If you do require a footnote,
-indicate footnotes with a number\footnote{Sample of the first
-  footnote.} in the text. Place the footnotes at the bottom of the
-page on which they appear.  Precede the footnote with a horizontal
-rule of 2~inches (12~picas).
-
-Note that footnotes are properly typeset \emph{after} punctuation
-marks.\footnote{As in this example.}
-
-\subsection{Figures}
-
-All artwork must be neat, clean, and legible. Lines should be dark
-enough for purposes of reproduction. The figure number and caption
-always appear after the figure. Place one line space before the figure
-caption and one line space after the figure. The figure caption should
-be lower case (except for first word and proper nouns); figures are
-numbered consecutively.
-
-You may use color figures.  However, it is best for the figure
-captions and the paper body to be legible if the paper is printed in
-either black/white or in color.
-\begin{figure}[h]
-  \centering
-  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
-  \caption{Sample figure caption.}
-\end{figure}
-
-\subsection{Tables}
-
-All tables must be centered, neat, clean and legible.  The table
-number and title always appear before the table.  See
-Table~\ref{sample-table}.
-
-Place one line space before the table title, one line space after the
-table title, and one line space after the table. The table title must
-be lower case (except for first word and proper nouns); tables are
-numbered consecutively.
-
-Note that publication-quality tables \emph{do not contain vertical
-  rules.} We strongly suggest the use of the \verb+booktabs+ package,
-which allows for typesetting high-quality, professional tables:
-\begin{center}
-  \url{https://www.ctan.org/pkg/booktabs}
-\end{center}
-This package was used to typeset Table~\ref{sample-table}.
-
-\begin{table}[t]
-  \caption{Sample table title}
-  \label{sample-table}
-  \centering
-  \begin{tabular}{lll}
-    \toprule
-    \multicolumn{2}{c}{Part}                   \\
-    \cmidrule{1-2}
-    Name     & Description     & Size ($\mu$m) \\
-    \midrule
-    Dendrite & Input terminal  & $\sim$100     \\
-    Axon     & Output terminal & $\sim$10      \\
-    Soma     & Cell body       & up to $10^6$  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\section{Final instructions}
-
-Do not change any aspects of the formatting parameters in the style
-files.  In particular, do not modify the width or length of the
-rectangle the text should fit into, and do not change font sizes
-(except perhaps in the \textbf{References} section; see below). Please
-note that pages should be numbered.
-
-\section{Preparing PDF files}
-
-Please prepare submission files with paper size ``US Letter,'' and
-not, for example, ``A4.''
-
-Fonts were the main cause of problems in the past years. Your PDF file
-must only contain Type 1 or Embedded TrueType fonts. Here are a few
-instructions to achieve this.
-
-\begin{itemize}
-
-\item You should directly generate PDF files using \verb+pdflatex+.
-
-\item You can check which fonts a PDF files uses.  In Acrobat Reader,
-  select the menu Files$>$Document Properties$>$Fonts and select Show
-  All Fonts. You can also use the program \verb+pdffonts+ which comes
-  with \verb+xpdf+ and is available out-of-the-box on most Linux
-  machines.
-
-\item The IEEE has recommendations for generating PDF files whose
-  fonts are also acceptable for NIPS. Please see
-  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}
-
-\item \verb+xfig+ "patterned" shapes are implemented with bitmap
-  fonts.  Use "solid" shapes instead.
-
-\item The \verb+\bbold+ package almost always uses bitmap fonts.  You
-  should use the equivalent AMS Fonts:
-\begin{verbatim}
-   \usepackage{amsfonts}
-\end{verbatim}
-followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or
-\verb+\mathbb{C}+ for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You
-can also use the following workaround for reals, natural and complex:
-\begin{verbatim}
-   \newcommand{\RR}{I\!\!R} %real numbers
-   \newcommand{\Nat}{I\!\!N} %natural numbers
-   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
-\end{verbatim}
-Note that \verb+amsfonts+ is automatically loaded by the
-\verb+amssymb+ package.
-
-\end{itemize}
-
-If your file contains type 3 fonts or non embedded TrueType fonts, we
-will ask you to fix it.
-
-\subsection{Margins in \LaTeX{}}
-
-Most of the margin problems come from figures positioned by hand using
-\verb+\special+ or other commands. We suggest using the command
-\verb+\includegraphics+ from the \verb+graphicx+ package. Always
-specify the figure width as a multiple of the line width as in the
-example below:
-\begin{verbatim}
-   \usepackage[pdftex]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]{myfile.pdf}
-\end{verbatim}
-See Section 4.4 in the graphics bundle documentation
-(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})
-
-A number of width problems arise when \LaTeX{} cannot properly
-hyphenate a line. Please give LaTeX hyphenation hints using the
-\verb+\-+ command when necessary.
-
-\subsubsection*{Acknowledgments}
-
-Use unnumbered third level headings for the acknowledgments. All
-acknowledgments go at the end of the paper. Do not include
-acknowledgments in the anonymized submission, only in the final paper.
-
-\section*{References}
-
-References follow the acknowledgments. Use unnumbered first-level
-heading for the references. Any choice of citation style is acceptable
-as long as you are consistent. It is permissible to reduce the font
-size to \verb+small+ (9 point) when listing the references. {\bf
-  Remember that you can go over 8 pages as long as the subsequent ones contain
-  \emph{only} cited references.}
-\medskip
-
-\small
-
-[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms
-for connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and
-T.K.\ Leen (eds.), {\it Advances in Neural Information Processing
-  Systems 7}, pp.\ 609--616. Cambridge, MA: MIT Press.
-
-[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS:
-  Exploring Realistic Neural Models with the GEneral NEural SImulation
-  System.}  New York: TELOS/Springer--Verlag.
-
-[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of
-learning and recall at excitatory recurrent synapses and cholinergic
-modulation in rat hippocampal region CA3. {\it Journal of
-  Neuroscience} {\bf 15}(7):5249-5262.
+\bibliographystyle{unsrt}
+{\small \bibliography{main}}
 

### 2017-05-09 paper.tex
added figures for parsing of latex quantitative results
added caption
figure on the first page which gives examples of what the system does

@@
 %\usepackage{epsfig} % less modern
-\usepackage{subfig} 
+%\usepackage{subfig} 
 \usepackage{fancyvrb}
@@
 source code for drawing the original image.
+
+\newcommand{\exampleImageSize}{2cm}
+\begin{figure}[h]
+  \begin{minipage}[t]{0.8\linewidth}  
+\begin{tabular}{llll}
+  \includegraphics[width = \exampleImageSize]{figures/expert-60.png}&
+  \includegraphics[width = \exampleImageSize]{figures/expert-5.png}&
+    \includegraphics[width = \exampleImageSize]{figures/expert-17.png}&
+    \includegraphics[width = \exampleImageSize]{figures/expert-58.png}\\
+  \includegraphics[width = \exampleImageSize]{figures/60.png}&
+  \includegraphics[width = \exampleImageSize]{figures/5.png}&
+    \includegraphics[width = \exampleImageSize]{figures/17.png}&
+    \includegraphics[width = \exampleImageSize]{figures/58.png}
+\end{tabular}
+\subcaption{}
+  \end{minipage}%
+  \begin{minipage}[t]{0.2\linewidth}
+    \begin{tikzpicture}
+      \node(picture) at (0,0) {\includegraphics[width = 2cm]{figures/expert-31.png}};
+      \draw[very thick,->] (picture.south)  -- (0,-2);
+    \end{tikzpicture}
+    \texttt{FOR} $0\leq i\leq 3$:\\
+    \texttt{RECTANGLE} $()$\\
+    \texttt{FOR} $0\leq j < i$:\\
+    \texttt{CIRCLE} $()$\\
+    \subcaption{}
+  \end{minipage}
+  \caption{(a): Model parses hand drawings (top) into \LaTeX~(bottom). (b) Synthesizes high-level \emph{graphics program} from hand drawing.}
+  \end{figure}
 
@@
 
+\begin{figure}
+  \begin{minipage}[t]{15cm}
+    \includegraphics[width = 15cm]{figures/editDistance.png}
+  \end{minipage}\\
+  \begin{minipage}[t]{15cm}
+    \includegraphics[width = 15cm]{figures/accuracy.png}
+  \end{minipage}\\
+  \begin{minipage}[t]{15cm}
+    \includegraphics[width = 15cm]{figures/time.png}
+  \end{minipage}
+  \caption{Using the model to parse latex output.
+The model is trained on diagrams with up to 8 objects.
+As shown above it generalizes to scenes with many more objects.
+Neither the stochastic search nor the neural network are sufficient on their own.}
+  \end{figure}
+
 \section{Generalizing to hand drawings}

### 2017-05-09 paper.tex
Comments.

--- 2017-05-06 paper.tex
@@
 \newcommand{\probability}{\mathds{P}} %{{\rm I\kern-.3em P}}
+
+\newcommand{\remark}[1]{\textcolor{red}{[#1]}}
 
@@
 source code for drawing the original image.
-The source code captures not just the objects in the image,
-but also describes their geometric relationships.
+\remark{The use of `graphics programs / visual programs' in the paper title, title of this section, and the body of this section feels too broad.
+`Graphics program' could conjur a lot of different ideas (esp.
+3D graphics); don't want to set the reader up to expect one thing and then be disappointed that what you've done isn't that.
+You bring up diagram-drawing later in the intro; I think it should be made clear sooner (and certainly mentioned explicitly in the abstract, when you get around to writing that).}
+
+\newcommand{\exampleImageSize}{2cm}
+\begin{figure}[h]
+  \begin{minipage}[t]{0.8\linewidth}  
+\begin{tabular}{llll}
+  \includegraphics[width = \exampleImageSize]{figures/expert-60.png}&
+  \includegraphics[width = \exampleImageSize]{figures/expert-5.png}&
+    \includegraphics[width = \exampleImageSize]{figures/expert-17.png}&
+    \includegraphics[width = \exampleImageSize]{figures/expert-58.png}\\
+  \includegraphics[width = \exampleImageSize]{figures/60.png}&
+  \includegraphics[width = \exampleImageSize]{figures/5.png}&
+    \includegraphics[width = \exampleImageSize]{figures/17.png}&
+    \includegraphics[width = \exampleImageSize]{figures/58.png}
+\end{tabular}
+\subcaption{}
+  \end{minipage}%
+  \begin{minipage}[t]{0.2\linewidth}
+    \begin{tikzpicture}
+      \node(picture) at (0,0) {\includegraphics[width = 2cm]{figures/expert-31.png}};
+      \draw[very thick,->] (picture.south)  -- (0,-2);
+    \end{tikzpicture}
+    \texttt{FOR} $0\leq i\leq 3$:\\
+    \texttt{RECTANGLE} $()$\\
+    \texttt{FOR} $0\leq j < i$:\\
+    \texttt{CIRCLE} $()$\\
+    \subcaption{}
+  \end{minipage}
+  \caption{(a): Model parses hand drawings (top) into \LaTeX~(bottom). (b) Synthesizes high-level \emph{graphics program} from hand drawing.}
+  \end{figure}
 
@@
 the program synthesis community to recover the latent graphics program.
+\remark{This is an \emph{excellent} explanation!
+I would add maybe one more sentence / citation to elaborate on what you mean by `techniques from the program synthesis community', as this will be an unfamiliar concept to some readers, I imagine.}
 
@@
 We develop a hybrid architecture for inferring graphics programs.  Our
-approach uses a deep network infer an execution trace from an image;
-this recovers primitive drawing operations like lines, circles, or
-arrows.  For added robustness we use the deep network as a proposal
+approach uses a deep neural network infer an execution trace from an image;
+this network recovers primitive drawing operations such as lines, circles, or
+arrows~\remark{and their parameters?}
+. For added robustness, we use the deep network as a proposal
 distribution for a stochastic search over execution traces.
-Finally we use techniques in the program synthesis community to
+Finally, we use techniques in the program synthesis community to
 recover the program from its trace.
+\remark{This paragraph is all about making things a bit more specific, so you really need more specifics about program synth here.}
 
@@
 search, the program synthesizer -- confers its own advantages. From
-the deep network we get a very fast system that can recover plausible
-execution traces in about a minute. From the stochastic search we get
-added robustness; essentially the stochastic search can correct
+the deep network, we get a very fast system that can recover plausible
+execution traces in about a minute~\remark{A minute seems slow to me, for deep net inference. Are you talking about training time, here, or...?}. From the stochastic search we get
+added robustness; essentially, the stochastic search can correct
 mistakes made by the deep network's proposals.  From the program
-synthesizer we get abstraction: our system recovers coordinate
+synthesizer, we get abstraction: our system recovers coordinate
 transformations, for loops, and subroutines, which are useful for
-downstream tasks.
+downstream tasks~\remark{and can help correct some mistakes of the earlier stages?}.
+\remark{I wonder if this would work even better as a bulleted list...}
 
@@
 $x$ coordinate.
+\remark{There are some more details that are important to provide about this architecture, though possibly in an Appendix: the functional form(s) of the probability distributions over tokens, the network layer sizes, which MLPs share parameters, etc.}
+
+\remark{Planning to move the description of SMC / beam search up here, too?}
 
@@
 architecture being recurrent, training is fully supervised. In a
-sense, this model is like an autoregressive variant of AIR. When we
-have the generative model (the rendering function) and treat the trace
-as fully observed, we need not solve an unsupervised or reinforcement
-learning problem.
+sense, this model is like an autoregressive variant of AIR.
+\remark{I like that you make this connection, but it could be made more precisely.
+Specifically, (1) the architecture isn't \emph{really} recurrent (it uses no hidden state cells), so it'd be good to use a different term or drop this part of the point: (2) training of recurrent nets is also typically fully-supervised (Most RNNs lack latent variables per timestep)---if you're thinking about AIR specifically, maybe just say that, and (3) it's like an autogressive AIR \emph{without attention}.}
+\remark{Something related to this that's also cool to point out: training this model doesn't require backpropagation across the entire sequence of drawing commands (drawing to the canvas `blocks' the gradients, effectively offloading memory to an external (visual) store, so in principle it might be scalable to much longer sequences.}
+
+%% When we
+%% have the generative model (the rendering function) and treat the trace
+%% as fully observed, we need not solve an unsupervised or reinforcement
+%% learning problem.
 
@@
 \end{tikzpicture}
-\caption{Our neural architecture for inferring the execution trace of a graphics program from its output.}  \label{architecture}
+\caption{Our neural architecture for inferring the execution trace of a graphics program from its output.~\remark{Thoughts on improving this figure: (1) Convnet diagrams typically show the sequence of layers, if possible (space might not permit it here, but those thin arrows just aren't doing it for me).
+(2) Are the target image / canvas convolved down independently, or jointly (i.e.
+starting as a 2-channel image)?
+That's an important detail that's not clear with the current figure/explanation.
+(3) The three circles downstream from `Image Features' are supposed to be MLPs, I assume(?), but it took me a little while to parse that.
+Having some visual way of clearly separating network operations from data (color, perhaps) would go a long way.}}  \label{architecture}
   \end{figure}

### 2017-05-09 paper.tex
added figures back in

--- 2017-05-09 paper.tex
@@
 
+\newcommand{\remark}[1]{\textcolor{red}{[#1]}}
+
 \title{Inferring Graphics Programs from Images}
@@
 
-How could an agent go from noisy,
+\textbf{Comment for reader: this paragraph is a little grandiose and goes
+  beyond what we've actually done. But these are the kinds of things
+  that motivate the work, and I think that in some form these ideas
+  should be in the introduction or the conclusion.} How could an agent go from noisy,
 high-dimensional perceptual input to a symbolic, abstract object, like
@@
 source code for drawing the original image.
+\remark{The use of `graphics programs / visual programs' in the paper title, title of this section, and the body of this section feels too broad.
+`Graphics program' could conjur a lot of different ideas (esp.
+3D graphics); don't want to set the reader up to expect one thing and then be disappointed that what you've done isn't that.
+You bring up diagram-drawing later in the intro; I think it should be made clear sooner (and certainly mentioned explicitly in the abstract, when you get around to writing that).}
 
@@
 sense, this model is like an autoregressive variant of AIR.
+\remark{I like that you make this connection, but it could be made more precisely.
+Specifically, (1) the architecture isn't \emph{really} recurrent (it uses no hidden state cells), so it'd be good to use a different term or drop this part of the point: (2) training of recurrent nets is also typically fully-supervised (Most RNNs lack latent variables per timestep)---if you're thinking about AIR specifically, maybe just say that, and (3) it's like an autogressive AIR \emph{without attention}.}
+\remark{Something related to this that's also cool to point out: training this model doesn't require backpropagation across the entire sequence of drawing commands (drawing to the canvas `blocks' the gradients, effectively offloading memory to an external (visual) store, so in principle it might be scalable to much longer sequences.}
 
@@
   \end{table}
-
-\section{Contributions}
-
-We see this system as a first step towards more powerful graphics
-program synthesizers.  We look forward to, in the near future, being
-able to hand-draw our figures and automatically convert them into
-publication-quality \LaTeX code.
-
-\pagebreak
 

### 2017-05-09 paper.tex
some revision based on Dan's comment

@@
 
-\section{Introducing visual programs}
+\section{Introduction}
 
-\textbf{Comment for reader: this paragraph is a little grandiose and goes
-  beyond what we've actually done. But these are the kinds of things
-  that motivate the work, and I think that in some form these ideas
-  should be in the introduction or the conclusion.} How could an agent go from noisy,
-high-dimensional perceptual input to a symbolic, abstract object, like
-a computer program?  Here we consider this problem within the context
-of \emph{graphics program synthesis}.  We develop an approach for
-converting natural images, such as hand drawings, into executable
-source code for drawing the original image.
-\remark{The use of `graphics programs / visual programs' in the paper title, title of this section, and the body of this section feels too broad.
-`Graphics program' could conjur a lot of different ideas (esp.
-3D graphics); don't want to set the reader up to expect one thing and then be disappointed that what you've done isn't that.
-You bring up diagram-drawing later in the intro; I think it should be made clear sooner (and certainly mentioned explicitly in the abstract, when you get around to writing that).}
+ How could an agent go from noisy, high-dimensional perceptual input
+ to a symbolic, abstract object, like a computer program?  Here we
+ consider this problem within a graphics program synthesis domain.  We
+ develop an approach for converting natural images, such as hand
+ drawings, into executable source code for drawing the original image.
+ The graphics programs in our domain draw simple figures like those found in
+ machine learning papers (see Fig.\ref{firstPageExamples}).
+ \remark{The use of `graphics programs / visual programs' in the paper
+   title, title of this section, and the body of this section feels
+   too broad. `Graphics program' could conjur a lot of different ideas
+   (esp. 3D graphics); don't want to set the reader up to expect one
+   thing and then be disappointed that what you've done isn't
+   that. You bring up diagram-drawing later in the intro; I think it
+   should be made clear sooner (and certainly mentioned explicitly in
+   the abstract, when you get around to writing that).}
 
@@
 \begin{figure}[h]
-  \begin{minipage}[t]{0.8\linewidth}  
+  \begin{minipage}[t]{0.7\linewidth}  
 \begin{tabular}{llll}
@@
   \end{minipage}%
-  \begin{minipage}[t]{0.2\linewidth}
+  \begin{minipage}[t]{0.3\linewidth}
     \begin{tikzpicture}
@@
       \draw[very thick,->] (picture.south)  -- (0,-2);
-    \end{tikzpicture}
-    \texttt{FOR} $0\leq i\leq 3$:\\
-    \texttt{RECTANGLE} $()$\\
-    \texttt{FOR} $0\leq j < i$:\\
-    \texttt{CIRCLE} $()$\\
+    \end{tikzpicture}\\
+    \texttt{for} $0\leq i < 4$:\\
+    \texttt{rectangle} $(-3i + 9,2i - 2, -3i + 11,6)$\\
+    \texttt{for} $0\leq j < i$:\\
+    \texttt{circle} $(3i-2,-2j+5)$\\
     \subcaption{}
   \end{minipage}
-  \caption{(a): Model parses hand drawings (top) into \LaTeX~(bottom). (b) Synthesizes high-level \emph{graphics program} from hand drawing.}
+  \caption{(a): Model learns to convert hand drawings (top) into \LaTeX~(bottom). (b) Synthesizes high-level \emph{graphics program} from hand drawing.}\label{firstPageExamples}
   \end{figure}
 
-High dimensional perceptual input is ill matched to the abstract
+High dimensional perceptual input may seem ill matched to the abstract
 semantics of a programming language. But programs with constructs like
 recursion or iteration produce a simpler \emph{execution trace} of
-primitive actions. Our hypothesis is that the execution trace of the
-program is better aligned with the perceptual input, and that the
-trace can act as a kind of bridge between perception and programs. We
-test this hypothesis by developing a model that learns to map from an
-image to the execution trace of the graphics program that drew it.
-With the execution trace in hand, we can bring to bear techniques from
-the program synthesis community to recover the latent graphics program.
-\remark{This is an \emph{excellent} explanation!
-I would add maybe one more sentence / citation to elaborate on what you mean by `techniques from the program synthesis community', as this will be an unfamiliar concept to some readers, I imagine.}
-
-In this work we consider programs that draw diagrams, similar to those found in papers.
+primitive actions; for our domain the primitive actions are drawing
+commands. Our hypothesis is that the execution trace of the program is
+better aligned with the perceptual input, and that the trace can act
+as a kind of bridge between perception and programs. We test this
+hypothesis by developing a model that learns to map from an image to
+the execution trace of the graphics program that drew it.  With the
+execution trace in hand, we can bring to bear techniques from the
+program synthesis community to recover the latent graphics program.
+\remark{This is an \emph{excellent} explanation! I would add maybe one
+  more sentence / citation to elaborate on what you mean by
+  `techniques from the program synthesis community', as this will be
+  an unfamiliar concept to some readers, I imagine.}
 
@@
 both on the image features and on the previously generated tokens.
-For example, the network first decides to emit the \verb|CIRCLE| token
+For example, the network first decides to emit the \verb|circle| token
 conditioned on the image features, then it emits the $x$ coordinate of
-the circle conditioned on the image features and the \verb|CIRCLE|
+the circle conditioned on the image features and the \verb|circle|
 token, and finally it predicts the $y$ coordinate of the circle
-conditioned on the image features, the \verb|CIRCLE| token, and the
+conditioned on the image features, the \verb|circle| token, and the
 $x$ coordinate.
@@
 images $I$ for randomly generated scenes, and maximizing
-(\ref{objective}) wrt $\theta$ by gradient ascent. Despite the
-architecture being recurrent, training is fully supervised. In a
-sense, this model is like an autoregressive variant of AIR.
+(\ref{objective}) wrt $\theta$ by gradient ascent.
+Training does not require backpropagation across the entire sequence of drawing commands:
+drawing to the canvas `blocks' the gradients,
+effectively offloading memory to an external visual store.
+In a sense, this model is like an autoregressive variant of AIR~\cite{eslami1603attend} without attention.
+
 \remark{I like that you make this connection, but it could be made more precisely.
@@
   \node[draw,thick,circle,minimum size = 1cm](c1) at ([xshift = 1.5cm]features.north);
-  \node(l1) at ([yshift = -2cm]c1.south) {\verb|CIRCLE(|};
+  \node(l1) at ([yshift = -2cm]c1.south) {\verb|circle(|};
   \node[draw,thick,circle,minimum size = 1cm](c2) at ([xshift = 1cm]c1.east);
@@
   \begin{tabular}{l}
-    \verb|CIRCLE|$(x,y)$
+    \verb|circle|$(x,y)$
     \end{tabular}& Circle at $(x,y)$\\
   \begin{tabular}{l}
-    \verb|RECTANGLE|$(x_1,y_1,x_2,y_2)$
+    \verb|rectangle|$(x_1,y_1,x_2,y_2)$
     \end{tabular}&Rectangle with corners at $(x_1,y_1)$ \& $(x_2,y_2)$\\
@@
   Program$\to$&Command; $\cdots$; Command\\
-  Command$\to$&\texttt{CIRCLE}(Expression,Expression)\\
-  Command$\to$&\texttt{RECTANGLE}(Expression,Expression,Expression,Expression)\\
+  Command$\to$&\texttt{circle}(Expression,Expression)\\
+  Command$\to$&\texttt{rectangle}(Expression,Expression,Expression,Expression)\\
   Command$\to$&\texttt{LINE}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
-  Command$\to$&\texttt{FOR}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ }Program\texttt{ \}}\\
+  Command$\to$&\texttt{for}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ }Program\texttt{ \}}\\
   Command$\to$&\texttt{REFLECT}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
@@
   \caption{Grammar over graphics programs.
-We allow loops (\texttt{FOR}), vertical/horizontal reflections (\texttt{REFLECT}), and affine transformations (\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}).}
+We allow loops (\texttt{for}), vertical/horizontal reflections (\texttt{REFLECT}), and affine transformations (\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}).}
   \end{table}

### 2017-05-09 synthesizerOutputs.tex
example synthesizer outputs

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-41.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(2,0,3,6)
  Rectangle(4,0,5,6)
  Rectangle(0,0,1,6)
  Rectangle(0 * None + None,0,5,6)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-17.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  for (4)
      Line(-2 * i + 9,3 * i + None,-2 * i + 10,3 * i + -2,arrow = True,solid = True)
      Line(-2 * i + 9,3 * i + None,-2 * i + 8,3 * i + -2,arrow = True,solid = True)
      Rectangle(2 * i + -2,-3 * i + 9,2 * i + None,-3 * i + 11)
      Rectangle(2 * i + 2,-3 * i + 9,2 * i + 4,-3 * i + 11)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-43.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(4,0,4,5,arrow = False,solid = True)
  Line(0,0,0,5,arrow = False,solid = True)
  Line(0 * None + None,0,4,5,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-63.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(2,2,3,3)
  Rectangle(1,1,4,4)
  Rectangle(0,0,5,5)
  Rectangle(1 * None + None,2,3,3)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-11.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(1,1)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-45.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(4,6,6,6,arrow = True,solid = True)
        reflect(y = 12)
        Circle(7,6)
        Line(2,2,2,4,arrow = True,solid = True)
        Rectangle(1,10,3,12)
        Rectangle(0,4,4,8)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-51.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(0,0,3,1)
  Rectangle(2,2,5,3)
  Rectangle(4,4,7,5)
  Rectangle(4 * None + None,0,3,1)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-21.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(1,5)
  Rectangle(4,4,6,6)
  Rectangle(8,4,10,6)
    for (4)
        Line(4 * i + -4,1,4 * i + -6,1,arrow = True,solid = True)
        Line(4 * i + -3,2,4 * i + -3,4,arrow = True,solid = True)
        Rectangle(4 * i + -4,0,4 * i + -2,2)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-2.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(4,2,6,5)
        reflect(y = 7)
        Line(2,6,4,4,arrow = True,solid = True)
        Rectangle(0,0,2,2)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-24.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(0,3,6,6)
  Rectangle(2,0,4,2)
  Rectangle(0,7,6,9)
        Line(1,7,1,6,arrow = True,solid = True)
        Line(3,3,3,2,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-7.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  for (3)
      Circle(3 * i + 1,6)
      Circle(-3 * i + 7,1)
      Line(3 * i + 1,None * i + 2,3 * i + 1,5,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-44.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
      reflect(x = 12)
      Circle(8,1)
      Line(9,1,10,1,arrow = False,solid = True)
      Rectangle(10,0,12,2)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-64.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
      reflect(x = 6)
      Line(1,2,1,4,arrow = False,solid = True)
            reflect(y = 6)
            Line(2,5,4,5,arrow = False,solid = True)
            Rectangle(0,0,2,2)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-36.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  for (2)
      Rectangle(5 * i + None,5 * i + None,5 * i + 4,5 * i + 4)
      Rectangle(7 * i + None,-3 * i + 5,7 * i + 2,-3 * i + 7)
      Rectangle(8 * i + None,-8 * i + 8,8 * i + 1,-8 * i + 9)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-58.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  for (3)
      Line(8,0,8 * i + -8,7 * i + -7,arrow = True,solid = True)
      Rectangle(2 * i + 2,0,2 * i + 3,None * i + 3)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-3.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
      reflect(y = 10)
      Circle(10,5)
        for (2)
            Line(-4 * i + 7,-3 * i + 5,-4 * i + 9,-1 * i + 5,arrow = True,solid = True)
            Rectangle(24 * i + 5,3,-18 * i + 7,7)
            Rectangle(-1 * i + 1,-1 * i + 1,9 * i + 3,7 * i + 3)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-28.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(0,2,2,2,arrow = False,solid = True)
  Line(0,0,0,2,arrow = False,solid = True)
  Line(0 * None + None,0,0,2,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-22.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  for (3)
      Line(4 * i + 1,4,4 * i + 1,2,arrow = True,solid = True)
      Line(4 * i + None,5,4 * i + -2,5,arrow = True,solid = True)
      Rectangle(-4 * i + 8,4,-4 * i + 10,6)
      Rectangle(-4 * i + 8,0,-4 * i + 10,2)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-69.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(0,4,5,6)
        reflect(x = 5)
        Circle(4,1)
        Line(1,4,1,2,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-14.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  for (4)
      Rectangle(-2 * i + 6,2 * i + -2,-2 * i + 7,2 * i + -1)
      Rectangle(2 * i + None,-2 * i + 6,2 * i + 1,-2 * i + 7)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-68.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  for (4)
      Circle(-4 * i + 9,1)
      Rectangle(4 * i + -4,0,4 * i + -2,2)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-65.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
      reflect(x = 6)
      Line(1,2,1,4,arrow = False,solid = True)
            reflect(y = 6)
            Circle(5,5)
            Line(2,5,4,5,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-67.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(1,5,5,1,arrow = False,solid = True)
  Line(1,4,5,0,arrow = False,solid = True)
  Rectangle(0,4,1,5)
  Rectangle(5,0,6,1)
  Line(1 * None + None,4,5,0,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-12.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(2,1,5,1,arrow = False,solid = True)
        reflect(x = 7)
        Circle(1,1)
        Line(1,2,1,5,arrow = False,solid = True)
        Line(2,6,5,6,arrow = False,solid = True)
        Rectangle(5,5,7,7)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-42.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(0,0,0,5,arrow = False,solid = False)
  Line(4,1,4,5,arrow = False,solid = False)
  Line(4,0,4,1,arrow = False,solid = False)
  Line(0 * None + None,0,4,1,arrow = False,solid = False)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-10.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(0,0,3,4)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-35.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(6,1)
    for (2)
        Circle(1,5 * i + 1)
        Line(None * i + 1,None * i + 5,5 * i + 1,2,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-31.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(4,5)
    for (4)
        Circle(-3 * i + 10,2 * i + -1)
        Circle(7,2 * i + -1)
        Rectangle(-3 * i + 9,2 * i + -2,-3 * i + 11,6)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-37.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(1,8)
    for (4)
        Line(4 * i + 1,-5 * i + 7,2 * i + 3,5,arrow = False,solid = True)
        Rectangle(4 * i + -8,-5 * i + 15,6,-7 * i + 23)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-40.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(1,1)
        reflect(x = 11)
        Circle(4,1)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-29.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  for (3)
      Line(None * i + None,-1 * i + 6,4 * i + -2,-1 * i + 6,arrow = False,solid = True)
      Line(None * i + None,-2 * i + 4,None * i + None,-1 * i + 6,arrow = False,solid = True)
      Line(-2 * i + 2,None * i + 5,-2 * i + 4,None * i + 5,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-62.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(5,0,8,3)
  Rectangle(2,1,4,3)
  Rectangle(0,2,1,3)
  Rectangle(2 * None + None,0,8,3)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-57.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  for (3)
      Circle(-4 * i + 9,4)
      Circle(-4 * i + 9,1)
      Circle(4 * i + 1,7)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-55.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Circle(1,5)
  Line(1,4,1,2,arrow = True,solid = True)
  Rectangle(0,0,2,2)
  Circle(1,None * None + None)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-66.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(1,1,6,1,arrow = False,solid = True)
  Line(0,2,7,2,arrow = False,solid = True)
  Line(2,0,5,0,arrow = False,solid = True)
  Line(2 * None + None,1,6,1,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-26.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(1,3,1,4,arrow = False,solid = True)
    for (3)
        Circle(1,-4 * i + 9)
        Line(1,-5 * i + 8,1,-4 * i + 6,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-15.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(1,2,3,2,arrow = False,solid = True)
  Line(0,3,2,3,arrow = False,solid = False)
  Line(3,0,5,0,arrow = False,solid = True)
  Line(2,1,4,1,arrow = False,solid = False)
  Line(1 * None + None,1,4,1,arrow = False,solid = False)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-19.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(4,4,2,2,arrow = True,solid = True)
  Rectangle(3,4,5,6)
  Rectangle(0,0,2,2)
  Line(4,4,2,2,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-8.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(0,0,0,4,arrow = False,solid = True)
  Line(0,0,0,4,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-23.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(4,1,2,1,arrow = False,solid = True)
    for (3)
        Circle(-4 * i + 9,5)
        Circle(-4 * i + 9,1)
        Line(-1 * i + 9,-1 * i + 2,-3 * i + 9,-3 * i + 4,arrow = True,solid = False)
        Line(-4 * i + 5,2,-4 * i + 5,4,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-60.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Rectangle(0,3,2,5)
    for (2)
        Circle(3 * i + 4,1)
        Circle(2 * i + 5,3 * i + 4)
        Line(-1 * i + 6,-4 * i + 7,-1 * i + 5,-3 * i + 5,arrow = True,solid = True)
        Line(-3 * i + 5,None * i + 3,-3 * i + 7,2 * i + 2,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-16.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  for (4)
      Circle(2 * i + 3,-3 * i + 10)
      Circle(2 * i + 1,-3 * i + 7)
      Line(2 * i + 3,-3 * i + 9,2 * i + 4,-3 * i + 7,arrow = False,solid = True)
      Line(-2 * i + 8,3 * i + -2,-2 * i + 9,3 * i + None,arrow = False,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-13.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(5,0,3,0,arrow = True,solid = True)
  Line(2,1,4,1,arrow = True,solid = True)
  Line(0,3,2,3,arrow = True,solid = True)
  Line(3,2,1,2,arrow = True,solid = True)
  Line(2 * None + None,2,1,2,arrow = True,solid = True)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-47.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
      reflect(x = 11)
      Rectangle(9,4,10,7)
            reflect(y = 11)
            Rectangle(0,0,3,3)
            Rectangle(4,9,7,10)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-5.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(12,9,12,0,arrow = True,solid = True)
    for (2)
        Rectangle(-3 * i + 9,2 * i + 3,-3 * i + 11,9)
        Rectangle(3 * i + None,None * i + 7,3 * i + 2,9)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-59.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(4,0,0,0,arrow = False,solid = False)
  Line(4,0,0,0,arrow = False,solid = False)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-50.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(8,3,9,3,arrow = False,solid = True)
    for (2)
        Line(-6 * i + 8,3 * i + 3,-3 * i + 7,None * i + 3,arrow = True,solid = True)
        Line(5 * i + 2,3 * i + 1,5 * i + 4,None * i + 3,arrow = True,solid = True)
        Rectangle(9 * i + None,2 * i + None,10 * i + 2,3 * i + 2)
        Rectangle(4 * i + None,-3 * i + 5,5 * i + 2,-2 * i + 7)
        \end{verbatim}
\end{minipage}
\end{tabular}        
        \\

        \begin{tabular}{ll}
\includegraphics[width = 5cm]{../TikZ/drawings/expert-6.png}&
        \begin{minipage}{10cm}
        \begin{verbatim}
  Line(0,4,3,4,arrow = False,solid = True)
    for (2)
        Line(3 * i + None,3 * i + 1,3 * i + 2,3 * i + None,arrow = False,solid = True)
        Line(0,3 * i + 1,2 * i + None,-1 * i + 4,arrow = False,solid = True)
        Rectangle(2,-8 * i + 8,29 * i + -24,12 * i + -9)
        \end{verbatim}
\end{minipage}
\end{tabular}

### 2017-05-09 synthesizerOutputs.tex
updated synthesis results

@@
         \begin{verbatim}
+  Rectangle(0,0,1,6)
   Rectangle(2,0,3,6)
   Rectangle(4,0,5,6)
-  Rectangle(0,0,1,6)
-  Rectangle(0 * None + None,0,5,6)
         \end{verbatim}
@@
         \begin{verbatim}
-  for (4)
-      Line(-2 * i + 9,3 * i + None,-2 * i + 10,3 * i + -2,arrow = True,solid = True)
-      Line(-2 * i + 9,3 * i + None,-2 * i + 8,3 * i + -2,arrow = True,solid = True)
-      Rectangle(2 * i + -2,-3 * i + 9,2 * i + None,-3 * i + 11)
-      Rectangle(2 * i + 2,-3 * i + 9,2 * i + 4,-3 * i + 11)
+  Rectangle(2,9,4,11)
+    for (3)
+        Line(-2*i + 7,3*i + 3,-2*i + 6,3*i + 1,arrow = True,solid = True)
+        Line(2*i + 3,-3*i + 9,2*i + 4,-3*i + 7,arrow = True,solid = True)
+        Rectangle(2*i,-3*i + 6,2*i + 2,-3*i + 8)
+        Rectangle(-2*i + 8,3*i,-2*i + 10,3*i + 2)
         \end{verbatim}
@@
         \begin{verbatim}
-  Line(4,0,4,5,arrow = False,solid = True)
       Line(0,0,0,5,arrow = False,solid = True)
-  Line(0 * None + None,0,4,5,arrow = False,solid = True)
         \end{verbatim}
@@
         \begin{verbatim}
+  Rectangle(0,0,5,5)
+  Rectangle(1,1,4,4)
   Rectangle(2,2,3,3)
-  Rectangle(1,1,4,4)
-  Rectangle(0,0,5,5)
-  Rectangle(1 * None + None,2,3,3)
         \end{verbatim}
@@
         \begin{verbatim}
-  Line(4,6,6,6,arrow = True,solid = True)
+  Rectangle(0,4,4,8)
         reflect(y = 12)
@@
         Line(2,2,2,4,arrow = True,solid = True)
-        Rectangle(1,10,3,12)
-        Rectangle(0,4,4,8)
+        Line(4,6,6,6,arrow = True,solid = True)
+        Rectangle(1,0,3,2)
         \end{verbatim}
@@
         \begin{verbatim}
+  Rectangle(2,2,5,3)
   Rectangle(0,0,3,1)
-  Rectangle(2,2,5,3)
   Rectangle(4,4,7,5)
-  Rectangle(4 * None + None,0,3,1)
         \end{verbatim}
@@
   Circle(1,5)
-  Rectangle(4,4,6,6)
-  Rectangle(8,4,10,6)
-    for (4)
-        Line(4 * i + -4,1,4 * i + -6,1,arrow = True,solid = True)
-        Line(4 * i + -3,2,4 * i + -3,4,arrow = True,solid = True)
-        Rectangle(4 * i + -4,0,4 * i + -2,2)
+    for (2)
+        Line(-5*i + 9,-1*i + 2,-7*i + 9,-3*i + 4,arrow = True,solid = True)
+        Rectangle(-4*i + 8,4*i,-4*i + 10,4*i + 2)
+              reflect(x = 6)
+              Line(7*i + 1,-1*i + 2,5*i + 1,-3*i + 4,arrow = True,solid = True)
+              Rectangle(8*i,4*i,8*i + 2,4*i + 2)
         \end{verbatim}
@@
         Line(2,6,4,4,arrow = True,solid = True)
-        Rectangle(0,0,2,2)
+        Rectangle(0,5,2,7)
         \end{verbatim}
@@
         \begin{verbatim}
+  Line(3,3,3,2,arrow = True,solid = True)
+  Rectangle(0,7,6,9)
+  Rectangle(2,0,4,2)
   Rectangle(0,3,6,6)
-  Rectangle(2,0,4,2)
-  Rectangle(0,7,6,9)
         Line(1,7,1,6,arrow = True,solid = True)
-        Line(3,3,3,2,arrow = True,solid = True)
         \end{verbatim}
@@
   for (3)
-      Circle(3 * i + 1,6)
-      Circle(-3 * i + 7,1)
-      Line(3 * i + 1,None * i + 2,3 * i + 1,5,arrow = False,solid = True)
+      Circle(-3*i + 7,1)
+      Circle(3*i + 1,6)
+      Line(3*i + 1,2,3*i + 1,5,arrow = False,solid = True)
         \end{verbatim}
@@
       reflect(x = 12)
-      Circle(8,1)
+      Circle(4,1)
       Line(9,1,10,1,arrow = False,solid = True)
@@
       reflect(x = 6)
-      Line(1,2,1,4,arrow = False,solid = True)
+      Line(5,2,5,4,arrow = False,solid = True)
             reflect(y = 6)
             Line(2,5,4,5,arrow = False,solid = True)
-            Rectangle(0,0,2,2)
+            Rectangle(0,4,2,6)
         \end{verbatim}
@@
   for (2)
-      Rectangle(5 * i + None,5 * i + None,5 * i + 4,5 * i + 4)
-      Rectangle(7 * i + None,-3 * i + 5,7 * i + 2,-3 * i + 7)
-      Rectangle(8 * i + None,-8 * i + 8,8 * i + 1,-8 * i + 9)
+      Rectangle(0,-3*i + 8,1,-2*i + 9)
+      Rectangle(-3*i + 8,5*i,9,8*i + 1)
+      Rectangle(-7*i + 7,-2*i + 2,-5*i + 9,4)
         \end{verbatim}
@@
         \begin{verbatim}
-  for (3)
-      Line(8,0,8 * i + -8,7 * i + -7,arrow = True,solid = True)
-      Rectangle(2 * i + 2,0,2 * i + 3,None * i + 3)
+  Rectangle(4,0,5,4)
+    for (2)
+        Line(8,0,-8*i + 8,-7*i + 7,arrow = True,solid = True)
+        Rectangle(-4*i + 6,0,-4*i + 7,-2*i + 5)
         \end{verbatim}
@@
         \begin{verbatim}
+  Circle(10,5)
+  Line(7,5,9,5,arrow = True,solid = True)
+  Rectangle(5,3,7,7)
+  Rectangle(0,0,12,10)
         reflect(y = 10)
-      Circle(10,5)
-        for (2)
-            Line(-4 * i + 7,-3 * i + 5,-4 * i + 9,-1 * i + 5,arrow = True,solid = True)
-            Rectangle(24 * i + 5,3,-18 * i + 7,7)
-            Rectangle(-1 * i + 1,-1 * i + 1,9 * i + 3,7 * i + 3)
+        Line(3,2,5,4,arrow = True,solid = True)
+        Rectangle(1,1,3,3)
         \end{verbatim}
@@
         \begin{verbatim}
+  Line(0,0,0,2,arrow = False,solid = True)
   Line(0,2,2,2,arrow = False,solid = True)
-  Line(0,0,0,2,arrow = False,solid = True)
-  Line(0 * None + None,0,0,2,arrow = False,solid = True)
         \end{verbatim}
@@
         \begin{verbatim}
+  Line(8,5,6,5,arrow = True,solid = True)
+  Line(4,5,2,5,arrow = True,solid = True)
     for (3)
-      Line(4 * i + 1,4,4 * i + 1,2,arrow = True,solid = True)
-      Line(4 * i + None,5,4 * i + -2,5,arrow = True,solid = True)
-      Rectangle(-4 * i + 8,4,-4 * i + 10,6)
-      Rectangle(-4 * i + 8,0,-4 * i + 10,2)
+        Line(-4*i + 9,4,-4*i + 9,2,arrow = True,solid = True)
+        Rectangle(4*i,0,4*i + 2,2)
+        Rectangle(-4*i + 8,4,-4*i + 10,6)
         \end{verbatim}
@@
         \begin{verbatim}
-  for (4)
-      Rectangle(-2 * i + 6,2 * i + -2,-2 * i + 7,2 * i + -1)
-      Rectangle(2 * i + None,-2 * i + 6,2 * i + 1,-2 * i + 7)
+  Rectangle(0,6,1,7)
+    for (3)
+        Rectangle(-2*i + 6,2*i,-2*i + 7,2*i + 1)
+        Rectangle(-2*i + 4,2*i,-2*i + 5,2*i + 1)
         \end{verbatim}
@@
         \begin{verbatim}
-  for (4)
-      Circle(-4 * i + 9,1)
-      Rectangle(4 * i + -4,0,4 * i + -2,2)
+  for (3)
+      Circle(4*i + 1,1)
+      Rectangle(4*i,0,4*i + 2,2)
         \end{verbatim}
@@
         \begin{verbatim}
+      reflect(y = 6)
+      Line(2,1,4,1,arrow = False,solid = True)
             reflect(x = 6)
+            Circle(1,1)
             Line(1,2,1,4,arrow = False,solid = True)
-            reflect(y = 6)
-            Circle(5,5)
-            Line(2,5,4,5,arrow = False,solid = True)
         \end{verbatim}
@@
   Line(1,4,5,0,arrow = False,solid = True)
+  Rectangle(5,0,6,1)
   Rectangle(0,4,1,5)
-  Rectangle(5,0,6,1)
-  Line(1 * None + None,4,5,0,arrow = False,solid = True)
         \end{verbatim}
@@
         \begin{verbatim}
-  Line(2,1,5,1,arrow = False,solid = True)
-        reflect(x = 7)
-        Circle(1,1)
-        Line(1,2,1,5,arrow = False,solid = True)
-        Line(2,6,5,6,arrow = False,solid = True)
-        Rectangle(5,5,7,7)
+  for (2)
+      Circle(-5*i + 6,1)
+      Line(-4*i + 6,-1*i + 2,-1*i + 6,-4*i + 5,arrow = False,solid = True)
+      Line(-1*i + 2,-4*i + 6,-4*i + 5,-1*i + 6,arrow = False,solid = True)
+      Rectangle(5*i,5,5*i + 2,7)
         \end{verbatim}
@@
   Line(4,0,4,1,arrow = False,solid = False)
-  Line(0 * None + None,0,4,1,arrow = False,solid = False)
         \end{verbatim}
@@
         \begin{verbatim}
-  Circle(6,1)
+  Circle(1,1)
     for (2)
-        Circle(1,5 * i + 1)
-        Line(None * i + 1,None * i + 5,5 * i + 1,2,arrow = True,solid = True)
+        Circle(-5*i + 6,5*i + 1)
+        Line(1,5,5*i + 1,2,arrow = True,solid = True)
         \end{verbatim}
@@
         \begin{verbatim}
-  Circle(4,5)
-    for (4)
-        Circle(-3 * i + 10,2 * i + -1)
-        Circle(7,2 * i + -1)
-        Rectangle(-3 * i + 9,2 * i + -2,-3 * i + 11,6)
+  Circle(7,3)
+    for (3)
+        Circle(-3*i + 7,5)
+        Circle(-3*i + 7,2*i + 1)
+        Rectangle(-3*i + 6,2*i,-3*i + 8,6)
         \end{verbatim}
@@
   Circle(1,8)
-    for (4)
-        Line(4 * i + 1,-5 * i + 7,2 * i + 3,5,arrow = False,solid = True)
-        Rectangle(4 * i + -8,-5 * i + 15,6,-7 * i + 23)
+    for (2)
+        Line(4*i + 1,-5*i + 7,2*i + 3,5,arrow = False,solid = True)
+        Rectangle(-4*i + 4,5*i,6,7*i + 2)
         \end{verbatim}
@@
         \begin{verbatim}
+  Circle(7,1)
+  Circle(4,1)
   Circle(1,1)
-        reflect(x = 11)
-        Circle(4,1)
         \end{verbatim}
@@
         \begin{verbatim}
-  for (3)
-      Line(None * i + None,-1 * i + 6,4 * i + -2,-1 * i + 6,arrow = False,solid = True)
-      Line(None * i + None,-2 * i + 4,None * i + None,-1 * i + 6,arrow = False,solid = True)
-      Line(-2 * i + 2,None * i + 5,-2 * i + 4,None * i + 5,arrow = False,solid = True)
+  Line(1,2,1,5,arrow = False,solid = True)
+    for (2)
+        Line(2,-4*i + 4,-4*i + 6,4,arrow = False,solid = True)
+        Line(0,-2*i + 6,-2*i + 2,6,arrow = False,solid = True)
+        Line(1,5,2*i + 2,5,arrow = False,solid = True)
         \end{verbatim}
@@
   Rectangle(0,2,1,3)
-  Rectangle(2 * None + None,0,8,3)
         \end{verbatim}
@@
   for (3)
-      Circle(-4 * i + 9,4)
-      Circle(-4 * i + 9,1)
-      Circle(4 * i + 1,7)
+      Circle(-4*i + 9,4)
+      Circle(-4*i + 9,1)
+      Circle(4*i + 1,7)
         \end{verbatim}
@@
   Rectangle(0,0,2,2)
-  Circle(1,None * None + None)
         \end{verbatim}
@@
         \begin{verbatim}
+  Line(0,2,7,2,arrow = False,solid = True)
   Line(1,1,6,1,arrow = False,solid = True)
-  Line(0,2,7,2,arrow = False,solid = True)
   Line(2,0,5,0,arrow = False,solid = True)
-  Line(2 * None + None,1,6,1,arrow = False,solid = True)
         \end{verbatim}
@@
         \begin{verbatim}
+  Circle(1,9)
+  Line(1,8,1,6,arrow = True,solid = True)
+  Line(1,3,1,2,arrow = True,solid = True)
   Line(1,3,1,4,arrow = False,solid = True)
-    for (3)
-        Circle(1,-4 * i + 9)
-        Line(1,-5 * i + 8,1,-4 * i + 6,arrow = True,solid = True)
+        reflect(y = 6)
+        Circle(1,1)
         \end{verbatim}
@@
   Line(1,2,3,2,arrow = False,solid = True)
+  Line(2,1,4,1,arrow = False,solid = False)
+  Line(3,0,5,0,arrow = False,solid = True)
   Line(0,3,2,3,arrow = False,solid = False)
-  Line(3,0,5,0,arrow = False,solid = True)
-  Line(2,1,4,1,arrow = False,solid = False)
-  Line(1 * None + None,1,4,1,arrow = False,solid = False)
         \end{verbatim}
@@
   Rectangle(0,0,2,2)
-  Line(4,4,2,2,arrow = True,solid = True)
         \end{verbatim}
@@
         \begin{verbatim}
-  Line(0,0,0,4,arrow = False,solid = True)
   Line(0,0,0,4,arrow = False,solid = True)
@@
   Line(4,1,2,1,arrow = False,solid = True)
+    for (2)
+        Line(-4*i + 5,2,-4*i + 5,4,arrow = True,solid = True)
           for (3)
-        Circle(-4 * i + 9,5)
-        Circle(-4 * i + 9,1)
-        Line(-1 * i + 9,-1 * i + 2,-3 * i + 9,-3 * i + 4,arrow = True,solid = False)
-        Line(-4 * i + 5,2,-4 * i + 5,4,arrow = True,solid = True)
+              Circle(-4*j + 9,4*i + 1)
+              Line(8,1,3*i + 6,3*i + 1,arrow = True,solid = False)
         \end{verbatim}
@@
     for (2)
-        Circle(3 * i + 4,1)
-        Circle(2 * i + 5,3 * i + 4)
-        Line(-1 * i + 6,-4 * i + 7,-1 * i + 5,-3 * i + 5,arrow = True,solid = True)
-        Line(-3 * i + 5,None * i + 3,-3 * i + 7,2 * i + 2,arrow = True,solid = True)
+        Circle(3*i + 4,1)
+        Circle(-2*i + 7,-3*i + 7)
+        Line(5,3,-3*i + 7,2,arrow = True,solid = True)
+        Line(4*i + 2,3*i + 4,4,4,arrow = True,solid = True)
         \end{verbatim}
@@
         \begin{verbatim}
-  for (4)
-      Circle(2 * i + 3,-3 * i + 10)
-      Circle(2 * i + 1,-3 * i + 7)
-      Line(2 * i + 3,-3 * i + 9,2 * i + 4,-3 * i + 7,arrow = False,solid = True)
-      Line(-2 * i + 8,3 * i + -2,-2 * i + 9,3 * i + None,arrow = False,solid = True)
+  Circle(9,1)
+    for (3)
+        Circle(2*i + 3,-3*i + 10)
+        Circle(-2*i + 5,3*i + 1)
+        Line(2*i + 2,-3*i + 7,2*i + 3,-3*i + 9,arrow = False,solid = True)
+        Line(-2*i + 7,3*i + 3,-2*i + 8,3*i + 1,arrow = False,solid = True)
         \end{verbatim}
@@
   Line(5,0,3,0,arrow = True,solid = True)
-  Line(2,1,4,1,arrow = True,solid = True)
   Line(0,3,2,3,arrow = True,solid = True)
   Line(3,2,1,2,arrow = True,solid = True)
-  Line(2 * None + None,2,1,2,arrow = True,solid = True)
+  Line(2,1,4,1,arrow = True,solid = True)
         \end{verbatim}
@@
         \begin{verbatim}
+      reflect(y = 11)
+      Rectangle(4,9,7,10)
             reflect(x = 11)
-      Rectangle(9,4,10,7)
-            reflect(y = 11)
-            Rectangle(0,0,3,3)
-            Rectangle(4,9,7,10)
+            Rectangle(8,0,11,3)
+            Rectangle(1,4,2,7)
         \end{verbatim}
@@
     for (2)
-        Rectangle(-3 * i + 9,2 * i + 3,-3 * i + 11,9)
-        Rectangle(3 * i + None,None * i + 7,3 * i + 2,9)
+        Rectangle(-3*i + 6,3*i + 5,-3*i + 8,9)
+        Rectangle(9*i,-4*i + 7,9*i + 2,9)
         \end{verbatim}
@@
         \begin{verbatim}
-  Line(4,0,0,0,arrow = False,solid = False)
   Line(4,0,0,0,arrow = False,solid = False)
@@
     for (2)
-        Line(-6 * i + 8,3 * i + 3,-3 * i + 7,None * i + 3,arrow = True,solid = True)
-        Line(5 * i + 2,3 * i + 1,5 * i + 4,None * i + 3,arrow = True,solid = True)
-        Rectangle(9 * i + None,2 * i + None,10 * i + 2,3 * i + 2)
-        Rectangle(4 * i + None,-3 * i + 5,5 * i + 2,-2 * i + 7)
+        Line(-6*i + 8,3*i + 3,-3*i + 7,3,arrow = True,solid = True)
+        Line(5*i + 2,3*i + 1,5*i + 4,3,arrow = True,solid = True)
+        Rectangle(9*i,2*i,10*i + 2,3*i + 2)
+        Rectangle(-4*i + 4,3*i + 2,-5*i + 7,2*i + 5)
         \end{verbatim}
@@
         \begin{verbatim}
-  Line(0,4,3,4,arrow = False,solid = True)
+  Line(0,1,0,4,arrow = False,solid = True)
+  Rectangle(2,0,5,3)
     for (2)
-        Line(3 * i + None,3 * i + 1,3 * i + 2,3 * i + None,arrow = False,solid = True)
-        Line(0,3 * i + 1,2 * i + None,-1 * i + 4,arrow = False,solid = True)
-        Rectangle(2,-8 * i + 8,29 * i + -24,12 * i + -9)
+        Line(0,3*i + 1,2,3*i,arrow = False,solid = True)
+        Line(-3*i + 3,4,-2*i + 5,3,arrow = False,solid = True)
         \end{verbatim}

### 2017-05-12 paper.tex
example synthesizer outputs
updated synthesis results
improvements to figure in order to take into account Dan's feedback

@@
 \usetikzlibrary{fit}
+
+\usetikzlibrary{positioning}
+\usetikzlibrary{decorations.text}
+\usetikzlibrary{decorations.pathmorphing}
+
 % As of 2011, we use the hyperref package to produce hyperlinks in the
@@
 program synthesis community to recover the latent graphics program.
-\remark{This is an \emph{excellent} explanation! I would add maybe one
-  more sentence / citation to elaborate on what you mean by
-  `techniques from the program synthesis community', as this will be
-  an unfamiliar concept to some readers, I imagine.}
+This family of techniques, called \emph{constraint-based program synthesis}~\cite{solar2008program},
+work by modeling a set of possible programs inside of a constraint solver,
+like a SAT or SMT solver~\cite{de2008z3}.
+
+%% \remark{This is an \emph{excellent} explanation! I would add maybe one
+%%   more sentence / citation to elaborate on what you mean by
+%%   `techniques from the program synthesis community', as this will be
+%%   an unfamiliar concept to some readers, I imagine.}
 
 We develop a hybrid architecture for inferring graphics programs.  Our
-approach uses a deep neural network infer an execution trace from an image;
-this network recovers primitive drawing operations such as lines, circles, or
-arrows~\remark{and their parameters?}
-. For added robustness, we use the deep network as a proposal
-distribution for a stochastic search over execution traces.
-Finally, we use techniques in the program synthesis community to
-recover the program from its trace.
-\remark{This paragraph is all about making things a bit more specific, so you really need more specifics about program synth here.}
+approach uses a deep neural network infer an execution trace from an
+image; this network recovers primitive drawing operations such as
+lines, circles, or arrows, along with their parameters. For added
+robustness, we use the deep network as a proposal distribution for a
+stochastic search over execution traces.  Finally, we use techniques
+in the program synthesis community to recover the program from its
+trace.  The program synthesizer discovers constructs like loops and
+geometric operations like reflections and affine transformations.
+\remark{This paragraph is all about making things a bit more specific,
+  so you really need more specifics about program synth here.}
 
@@
 search, the program synthesizer -- confers its own advantages. From
-the deep network, we get a very fast system that can recover plausible
+the deep network, we get a fast system that can recover plausible
 execution traces in about a minute~\remark{A minute seems slow to me, for deep net inference. Are you talking about training time, here, or...?}. From the stochastic search we get
@@
 transformations, for loops, and subroutines, which are useful for
-downstream tasks~\remark{and can help correct some mistakes of the earlier stages?}.
+downstream tasks and can help correct some mistakes of the earlier stages.
 \remark{I wonder if this would work even better as a bulleted list...}
@@
 Figure~\ref{architecture} illustrates this architecture.  We first
-pass the target image and a rendering of the trace so far to a
-convolutional network. Given the features extracted by the
-convolutionional network, a multilayer perceptron then predicts a
-distribution over the next drawing command to add to the trace.  We
-predict the drawing command token-by-token, and condition each token
-both on the image features and on the previously generated tokens.
-For example, the network first decides to emit the \verb|circle| token
-conditioned on the image features, then it emits the $x$ coordinate of
-the circle conditioned on the image features and the \verb|circle|
-token, and finally it predicts the $y$ coordinate of the circle
-conditioned on the image features, the \verb|circle| token, and the
-$x$ coordinate.
-\remark{There are some more details that are important to provide about this architecture, though possibly in an Appendix: the functional form(s) of the probability distributions over tokens, the network layer sizes, which MLPs share parameters, etc.}
+pass a $256\times 256$ target image and a rendering of the trace so
+far to a convolutional network -- these two inputs are represented as
+separate channels for the convnet. Given the features extracted by the
+convnet, a multilayer perceptron then predicts a distribution over the
+next drawing command to add to the trace.  We predict the drawing
+command token-by-token, and condition each token both on the image
+features and on the previously generated tokens.  For example, the
+network first decides to emit the \verb|circle| token conditioned on
+the image features, then it emits the $x$ coordinate of the circle
+conditioned on the image features and the \verb|circle| token, and
+finally it predicts the $y$ coordinate of the circle conditioned on
+the image features, the \verb|circle| token, and the $x$ coordinate.
+\remark{There are some more details that are important to provide
+  about this architecture, though possibly in an Appendix: the
+  functional form(s) of the probability distributions over tokens, the
+  network layer sizes, which MLPs share parameters, etc.}
 
@@
   \begin{tikzpicture}
-  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image: $I$](observation) at (0,0) {\includegraphics[width = 3cm]{figures/expert-18.png}};
-  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm,label=below:Canvas: render$(T)$] (canvas) at (0,-5) {};
+  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image: $I$](observation) at (0,-1) {\includegraphics[width = 2cm]{figures/expert-18.png}};
+  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(T)$] (canvas) at (0,-4) {};
   % draw partial image on canvas
@@
 
-  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 3cm,minimum height = 3cm] (CNN) at (4.5,-2.5) {CNN};
+  \node[draw,ultra thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 3cm] (CNN) at (4.5,-2.5) {CNN};
+  \node[inner sep = 0pt](tensorProduct) at ([xshift = -1.5cm]CNN.west) {$\bigotimes$};
 
-  \node[rotate = -90,draw,thick,inner sep=0pt,minimum width = 3cm,minimum height = 0.5cm] (features) at ([xshift = 1cm]CNN.east) {Image features};
+  \node[rotate = -90,draw,ultra thick,inner sep=0pt,minimum width = 3cm,minimum height = 0.5cm] (features) at ([xshift = 1cm]CNN.east) {Image features};
 
-  \node[draw,thick,circle,minimum size = 1cm](c1) at ([xshift = 1.5cm]features.north);
+  \node[draw,ultra thick,minimum size = 1cm](c1) at ([xshift = 1.5cm]features.north) {MLP};
   \node(l1) at ([yshift = -2cm]c1.south) {\verb|circle(|};
-  \node[draw,thick,circle,minimum size = 1cm](c2) at ([xshift = 1cm]c1.east);
-  \draw[->,thick] (c1.south) -- (l1.north);
+  \node[draw,ultra thick,minimum size = 1cm](c2) at ([xshift = 1cm]c1.east) {MLP};
+  \draw[->,ultra thick] (c1.south) -- (l1.north);
   \node(l2) at ([yshift = -2cm]c2.south) {\verb|X=3,|};
-  \draw[->,thick] (c2.south) -- (l2.north);
-  \node[draw,thick,circle,minimum size = 1cm](c3) at ([xshift = 1cm]c2.east);
+  \draw[->,ultra thick] (c2.south) -- (l2.north);
+  \node[draw,ultra thick,minimum size = 1cm](c3) at ([xshift = 1cm]c2.east) {MLP};
   \node(l3) at ([yshift = -2cm]c3.south) {\verb|Y=14)|};
-  \draw[->,thick] (c3.south) -- (l3.north);
+  \draw[->,ultra thick] (c3.south) -- (l3.north);
 
-  \draw[->,thick] (features.north) -- (c1.west);
-  \draw[->,thick] (c1.east) -- (c2.west);
-  \draw[->,thick] (c2.east) -- (c3.west);
+  \draw[->,ultra thick] (features.north) -- (c1.west);
+  \draw[->,ultra thick] (features.north) to[out = 45,in = 90] (c2.north);
+  \draw[->,ultra thick] (features.north) to[out = 70,in = 90] (c3.north);
+  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c2.west);
+  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c3.west);
+  \draw[->,ultra thick] ([xshift = 0.25cm]l2.north) -- (c3.west);
 
@@
 
-  \draw[->,thick,dashed] (next.west) -- node[below] {Renderer: \LaTeX} (canvas.east);
+  \draw[->,thick,dashed] (next.west) -- (canvas.east) node [midway, below, sloped] (TextNode) {Renderer: \LaTeX};
 
-  \draw[->,thick] (canvas.east) -- ([yshift = -0.5cm]CNN.west);
-  \draw[->,thick] (observation.east) -- ([yshift = 0.5cm]CNN.west);
-  \draw[->,thick] (CNN.east) -- (features.south);
+  \draw[->,ultra thick] (canvas.east) -- (tensorProduct.south);%[yshift = -0.5cm]CNN.west);
+  \draw[->,ultra thick] (observation.east) -- (tensorProduct.north);%([yshift = 0.5cm]CNN.west);
+  \draw[->,ultra thick] (tensorProduct.east)  -- node[center,fill = white,rotate = 90] {{\tiny $256\times 256\times 2$}}  (CNN.west);
+  \draw[->,ultra thick] (CNN.east) -- node[center,fill = white,rotate = 90] {{\tiny $16\times 16\times 10$}} (features.south);
 %  \draw[]
@@
 
+  \pagebreak
+  \section{Preliminary Synthesis results} 
+\input{synthesizerOutputs.tex}
+
 \bibliographystyle{unsrt}

### 2017-05-12 paper.tex
added colors to diagram

@@
   \begin{tikzpicture}
-  \node[draw,ultra thick,anchor = west,inner sep=0pt,label=below:Target image: $I$](observation) at (0,-1) {\includegraphics[width = 2cm]{figures/expert-18.png}};
-  \node[draw,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(T)$] (canvas) at (0,-4) {};
+  \node[draw,blue,ultra thick,anchor = west,inner sep=0pt,label=below:Target image: $I$](observation) at (0,-1) {\includegraphics[width = 2cm]{figures/expert-18.png}};
+  \node[draw,blue,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(T)$] (canvas) at (0,-4) {};
   % draw partial image on canvas
@@
   \node[draw,ultra thick,minimum size = 1cm](c2) at ([xshift = 1cm]c1.east) {MLP};
-  \draw[->,ultra thick] (c1.south) -- (l1.north);
+  \draw[->,ultra thick,red] (c1.south) -- (l1.north);
   \node(l2) at ([yshift = -2cm]c2.south) {\verb|X=3,|};
-  \draw[->,ultra thick] (c2.south) -- (l2.north);
+  \draw[->,ultra thick,red] (c2.south) -- (l2.north);
   \node[draw,ultra thick,minimum size = 1cm](c3) at ([xshift = 1cm]c2.east) {MLP};
   \node(l3) at ([yshift = -2cm]c3.south) {\verb|Y=14)|};
-  \draw[->,ultra thick] (c3.south) -- (l3.north);
+  \draw[->,ultra thick,red] (c3.south) -- (l3.north);
 
@@
 \end{tikzpicture}
-\caption{Our neural architecture for inferring the execution trace of a graphics program from its output.~\remark{Thoughts on improving this figure: (1) Convnet diagrams typically show the sequence of layers, if possible (space might not permit it here, but those thin arrows just aren't doing it for me).
+\caption{Our neural architecture for inferring the execution trace of a graphics program from its output.
+\textcolor{blue}{Blue}: network inputs.
+Black: network operations.
+\textcolor{red}{Red}: samples from a multinomial.~\remark{Thoughts on improving this figure: (1) Convnet diagrams typically show the sequence of layers, if possible (space might not permit it here, but those thin arrows just aren't doing it for me).
 (2) Are the target image / canvas convolved down independently, or jointly (i.e.

### 2017-05-12 paper.tex
more figure improvements

@@
   \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c3.west);
-  \draw[->,ultra thick] ([xshift = 0.25cm]l2.north) -- (c3.west);
+  \draw[->,ultra thick] ([xshift = 0.25cm]l2.north) -- ([yshift = -0.2cm]c3.west);
 
@@
 Black: network operations.
-\textcolor{red}{Red}: samples from a multinomial.~\remark{Thoughts on improving this figure: (1) Convnet diagrams typically show the sequence of layers, if possible (space might not permit it here, but those thin arrows just aren't doing it for me).
+\textcolor{red}{Red}: samples from a multinomial.
+\texttt{Typewriter font}: network outputs.~\remark{Thoughts on improving this figure: (1) Convnet diagrams typically show the sequence of layers, if possible (space might not permit it here, but those thin arrows just aren't doing it for me).
 (2) Are the target image / canvas convolved down independently, or jointly (i.e.

### 2017-05-12 paper.tex
grid illustration update

@@
 \usetikzlibrary{fit}
-
+\usetikzlibrary{arrows.meta}
 \usetikzlibrary{positioning}
@@
   \node[draw,blue,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(T)$] (canvas) at (0,-4) {};
+  \draw[lightgray,ultra thin,step = 0.125] ([xshift = 0.5,yshift = 0.5]canvas.south west) grid ([xshift = -0.5,yshift = -0.5]canvas.north east);
   % draw partial image on canvas
@@
 
-  \node[rotate = -90,draw,ultra thick,inner sep=0pt,minimum width = 3cm,minimum height = 0.5cm] (features) at ([xshift = 1cm]CNN.east) {Image features};
+  \node[rotate = -90,draw,ultra thick,inner sep=0pt,minimum width = 3cm,minimum height = 0.5cm] (features) at ([xshift = 1.5cm]CNN.east) {Image features};
 
@@
 
-  \node(next)[draw,fit = (l1) (l2) (l3), dashed, label = below:{Next line of code}] {};
+  \node(next)[draw,very thick,fit = (l1) (l2) (l3), dashed, label = below:{Next line of code}] {};
 
-  \draw[->,thick,dashed] (next.west) -- (canvas.east) node [midway, below, sloped] (TextNode) {Renderer: \LaTeX};
+  \draw[-{>[scale = 1.5]},very thick,dashed] (next.west) -- ([yshift = -0.2cm]canvas.east) node [midway, below, sloped] (TextNode) {Renderer: \LaTeX};
 
@@
 \textcolor{red}{Red}: samples from a multinomial.
-\texttt{Typewriter font}: network outputs.~\remark{Thoughts on improving this figure: (1) Convnet diagrams typically show the sequence of layers, if possible (space might not permit it here, but those thin arrows just aren't doing it for me).
+\texttt{Typewriter font}: network outputs.
+Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}.~\remark{Thoughts on improving this figure: (1) Convnet diagrams typically show the sequence of layers, if possible (space might not permit it here, but those thin arrows just aren't doing it for me).
 (2) Are the target image / canvas convolved down independently, or jointly (i.e.

### 2017-05-12 paper.tex
changed arrow style
improved section on handwritten drawings

@@
 %% learning problem.
-
+\tikzset{>=latex}
 \begin{figure}
@@
 \end{figure}
-
 \begin{table}
@@
 
+This network suffices to ``derender'' images like those shown in
+Figure~\ref{trainingData}.  We can perform a beam search decoding to
+recover what the network thinks is the most likely execution trace for
+images like these. But, if the network makes a mistake (predicts an
+incorrect line of code), it has no way of recovering from the error.
+In order to derender an image with $n$ objects, it must correctly
+predict $n$ drawing commands -- so is probability of success will
+decrease exponentially in $n$.  For added robustness as $n$ becomes
+large, we treat the neural network outputs as proposals for a SMC
+sampling scheme.  For the SMC sampler, we use pixel wise distance as a
+surrogate for a likelihood function; see
+supplement. Figure~\ref{syntheticResults} compares the neural network
+with SMC against the neural network by itself or SMC by itself.  Only
+the combination of the two passes a critical test of generalization:
+when trained on images with $\leq 8$ objects, it successfully parses
+scenes with many more objects than the training data.
+
 \begin{figure}
@@
 As shown above it generalizes to scenes with many more objects.
-Neither the stochastic search nor the neural network are sufficient on their own.}
+Neither the stochastic search nor the neural network are sufficient on their own.}\label{syntheticResults}
 \end{figure}
 
-\section{Generalizing to hand drawings}
-
-\begin{figure}
-  \begin{minipage}[b]{0.3\textwidth}
-    \centering\includegraphics[width = 3cm]{figures/expert-60.png}
-    \subcaption{(a)}
+\subsection{Generalizing to hand drawings}
+We believe that converting synthetic, noiseless images into a restricted subset of
+\LaTeX has limited usefulness.  A more practical
+application is one that extends to hand drawings.  We train the model
+to generalize to hand drawings by introducing noise into the
+renderings of the training target images.
+We designed this noise process to introduce the kinds of variations found in hand drawings (figure~\ref{handDrawingExamples}).
+We drew 100 figures by hand; see figure~\ref{lotsOfHandDrawings}.
+These were drawn reasonably carefully but not perfectly.
+Because our model assumes that objects are snapped to a $16\times 16$ grid,
+we used graph paper.
+\begin{figure}[H]%
+  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
+    \subcaption{}
   \end{minipage}%
-  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 3cm]{figures/60-groundTruth.png}
-    \subcaption{(b)}
-  \end{minipage}\\
-  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 3cm]{figures/60-1.png}
-    \subcaption{(c)}
+   \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
+    \subcaption{}
   \end{minipage}%
-  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 3cm]{figures/60-2.png}
-    \subcaption{(d)}
+  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
+    \subcaption{}
+  \end{minipage}%
+  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-2-reduced.png} 
+    \subcaption{}
   \end{minipage}
@@
 (b): Rendering of the parse our model infers for (a).
-We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) \& (d) for noisy renderings of (b).}
+We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) \& (d) for noisy renderings of (b).}\label{handDrawingExamples}
 \end{figure}

### 2017-05-12 paper.tex
small changes

@@
 In order to derender an image with $n$ objects, it must correctly
-predict $n$ drawing commands -- so is probability of success will
-decrease exponentially in $n$.  For added robustness as $n$ becomes
-large, we treat the neural network outputs as proposals for a SMC
-sampling scheme.  For the SMC sampler, we use pixel wise distance as a
-surrogate for a likelihood function; see
-supplement. Figure~\ref{syntheticResults} compares the neural network
-with SMC against the neural network by itself or SMC by itself.  Only
-the combination of the two passes a critical test of generalization:
-when trained on images with $\leq 8$ objects, it successfully parses
-scenes with many more objects than the training data.
+predict $n$ drawing commands -- so its probability of success will
+decrease exponentially in $n$, assuming it has any nonzero chance of
+making a mistake.  For added robustness as $n$ becomes large, we treat
+the neural network outputs as proposals for a SMC sampling scheme.
+For the SMC sampler, we use pixel wise distance as a surrogate for a
+likelihood function; see supplement. Figure~\ref{syntheticResults}
+compares the neural network with SMC against the neural network by
+itself or SMC by itself.  Only the combination of the two passes a
+critical test of generalization: when trained on images with $\leq 8$
+objects, it successfully parses scenes with many more objects than the
+training data.
 
@@
 Because our model assumes that objects are snapped to a $16\times 16$ grid,
-we used graph paper.
+we made the drawings on graph paper.
 \begin{figure}[H]%
@@
 
-\begin{table}
+\begin{table}[h]
   \begin{tabular}{rl}

### 2017-05-12 paper.tex
better formatting for one of the tables

@@
     \verb|circle|$(x,y)$
-    \end{tabular}& Circle at $(x,y)$\\
+  \end{tabular}& \begin{tabular}{l}
+    Circle at $(x,y)$
+    \end{tabular}\\
   \begin{tabular}{l}
     \verb|rectangle|$(x_1,y_1,x_2,y_2)$
-    \end{tabular}&Rectangle with corners at $(x_1,y_1)$ \& $(x_2,y_2)$\\
+  \end{tabular}&\begin{tabular}{l}
+    Rectangle with corners at $(x_1,y_1)$ \& $(x_2,y_2)$
+    \end{tabular}\\
   \begin{tabular}{l}
@@
     \hspace{1cm}$\text{arrow}\in\{0,1\},\text{dashed}\in\{0,1\})$
-    \end{tabular}&Line from $(x_1,y_1)$ to  $(x_2,y_2)$, optionally with an arrow and/or dashed\\
+  \end{tabular}&\begin{tabular}{l}
+    Line from $(x_1,y_1)$ to  $(x_2,y_2)$,\\\hspace{1cm}optionally with an arrow and/or dashed
+    \end{tabular}\\
   \begin{tabular}{l}
     \verb|STOP|
-  \end{tabular}&Finishes execution trace inference
+  \end{tabular}&\begin{tabular}{l}
+    Finishes execution trace inference
+    \end{tabular}
 \\  \bottomrule

### 2017-05-13 extrapolations.tex
preliminary extrapolation results

--- 2017-05-09 synthesizerOutputs.tex
@@
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-41.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(0,0,1,6)
-  Rectangle(2,0,3,6)
-  Rectangle(4,0,5,6)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
             \begin{tabular}{ll}
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-17.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(2,9,4,11)
-    for (3)
-        Line(-2*i + 7,3*i + 3,-2*i + 6,3*i + 1,arrow = True,solid = True)
-        Line(2*i + 3,-3*i + 9,2*i + 4,-3*i + 7,arrow = True,solid = True)
-        Rectangle(2*i,-3*i + 6,2*i + 2,-3*i + 8)
-        Rectangle(-2*i + 8,3*i,-2*i + 10,3*i + 2)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-43.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-      Line(0,0,0,5,arrow = False,solid = True)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-63.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(0,0,5,5)
-  Rectangle(1,1,4,4)
-  Rectangle(2,2,3,3)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-11.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Circle(1,1)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-45.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(0,4,4,8)
-        reflect(y = 12)
-        Circle(7,6)
-        Line(2,2,2,4,arrow = True,solid = True)
-        Line(4,6,6,6,arrow = True,solid = True)
-        Rectangle(1,0,3,2)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-51.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(2,2,5,3)
-  Rectangle(0,0,3,1)
-  Rectangle(4,4,7,5)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-17-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-21.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Circle(1,5)
-    for (2)
-        Line(-5*i + 9,-1*i + 2,-7*i + 9,-3*i + 4,arrow = True,solid = True)
-        Rectangle(-4*i + 8,4*i,-4*i + 10,4*i + 2)
-              reflect(x = 6)
-              Line(7*i + 1,-1*i + 2,5*i + 1,-3*i + 4,arrow = True,solid = True)
-              Rectangle(8*i,4*i,8*i + 2,4*i + 2)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-2.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(4,2,6,5)
-        reflect(y = 7)
-        Line(2,6,4,4,arrow = True,solid = True)
-        Rectangle(0,5,2,7)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-24.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(3,3,3,2,arrow = True,solid = True)
-  Rectangle(0,7,6,9)
-  Rectangle(2,0,4,2)
-  Rectangle(0,3,6,6)
-        Line(1,7,1,6,arrow = True,solid = True)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-21-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-7.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  for (3)
-      Circle(-3*i + 7,1)
-      Circle(3*i + 1,6)
-      Line(3*i + 1,2,3*i + 1,5,arrow = False,solid = True)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-44.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-      reflect(x = 12)
-      Circle(4,1)
-      Line(9,1,10,1,arrow = False,solid = True)
-      Rectangle(10,0,12,2)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-64.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-      reflect(x = 6)
-      Line(5,2,5,4,arrow = False,solid = True)
-            reflect(y = 6)
-            Line(2,5,4,5,arrow = False,solid = True)
-            Rectangle(0,4,2,6)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-7-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-36.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  for (2)
-      Rectangle(0,-3*i + 8,1,-2*i + 9)
-      Rectangle(-3*i + 8,5*i,9,8*i + 1)
-      Rectangle(-7*i + 7,-2*i + 2,-5*i + 9,4)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-36-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-58.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(4,0,5,4)
-    for (2)
-        Line(8,0,-8*i + 8,-7*i + 7,arrow = True,solid = True)
-        Rectangle(-4*i + 6,0,-4*i + 7,-2*i + 5)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-3.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Circle(10,5)
-  Line(7,5,9,5,arrow = True,solid = True)
-  Rectangle(5,3,7,7)
-  Rectangle(0,0,12,10)
-        reflect(y = 10)
-        Line(3,2,5,4,arrow = True,solid = True)
-        Rectangle(1,1,3,3)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-28.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(0,0,0,2,arrow = False,solid = True)
-  Line(0,2,2,2,arrow = False,solid = True)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-58-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-22.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(8,5,6,5,arrow = True,solid = True)
-  Line(4,5,2,5,arrow = True,solid = True)
-    for (3)
-        Line(-4*i + 9,4,-4*i + 9,2,arrow = True,solid = True)
-        Rectangle(4*i,0,4*i + 2,2)
-        Rectangle(-4*i + 8,4,-4*i + 10,6)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-69.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(0,4,5,6)
-        reflect(x = 5)
-        Circle(4,1)
-        Line(1,4,1,2,arrow = True,solid = True)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-22-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-14.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(0,6,1,7)
-    for (3)
-        Rectangle(-2*i + 6,2*i,-2*i + 7,2*i + 1)
-        Rectangle(-2*i + 4,2*i,-2*i + 5,2*i + 1)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-14-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-68.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  for (3)
-      Circle(4*i + 1,1)
-      Rectangle(4*i,0,4*i + 2,2)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-65.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-      reflect(y = 6)
-      Line(2,1,4,1,arrow = False,solid = True)
-            reflect(x = 6)
-            Circle(1,1)
-            Line(1,2,1,4,arrow = False,solid = True)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-67.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(1,5,5,1,arrow = False,solid = True)
-  Line(1,4,5,0,arrow = False,solid = True)
-  Rectangle(5,0,6,1)
-  Rectangle(0,4,1,5)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-68-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-12.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  for (2)
-      Circle(-5*i + 6,1)
-      Line(-4*i + 6,-1*i + 2,-1*i + 6,-4*i + 5,arrow = False,solid = True)
-      Line(-1*i + 2,-4*i + 6,-4*i + 5,-1*i + 6,arrow = False,solid = True)
-      Rectangle(5*i,5,5*i + 2,7)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-42.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(0,0,0,5,arrow = False,solid = False)
-  Line(4,1,4,5,arrow = False,solid = False)
-  Line(4,0,4,1,arrow = False,solid = False)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-10.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(0,0,3,4)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-12-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-35.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Circle(1,1)
-    for (2)
-        Circle(-5*i + 6,5*i + 1)
-        Line(1,5,5*i + 1,2,arrow = True,solid = True)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-35-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-31.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Circle(7,3)
-    for (3)
-        Circle(-3*i + 7,5)
-        Circle(-3*i + 7,2*i + 1)
-        Rectangle(-3*i + 6,2*i,-3*i + 8,6)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-31-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-37.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Circle(1,8)
-    for (2)
-        Line(4*i + 1,-5*i + 7,2*i + 3,5,arrow = False,solid = True)
-        Rectangle(-4*i + 4,5*i,6,7*i + 2)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-40.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Circle(7,1)
-  Circle(4,1)
-  Circle(1,1)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-37-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-29.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(1,2,1,5,arrow = False,solid = True)
-    for (2)
-        Line(2,-4*i + 4,-4*i + 6,4,arrow = False,solid = True)
-        Line(0,-2*i + 6,-2*i + 2,6,arrow = False,solid = True)
-        Line(1,5,2*i + 2,5,arrow = False,solid = True)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-62.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(5,0,8,3)
-  Rectangle(2,1,4,3)
-  Rectangle(0,2,1,3)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-29-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-57.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  for (3)
-      Circle(-4*i + 9,4)
-      Circle(-4*i + 9,1)
-      Circle(4*i + 1,7)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-55.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Circle(1,5)
-  Line(1,4,1,2,arrow = True,solid = True)
-  Rectangle(0,0,2,2)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-66.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(0,2,7,2,arrow = False,solid = True)
-  Line(1,1,6,1,arrow = False,solid = True)
-  Line(2,0,5,0,arrow = False,solid = True)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-26.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Circle(1,9)
-  Line(1,8,1,6,arrow = True,solid = True)
-  Line(1,3,1,2,arrow = True,solid = True)
-  Line(1,3,1,4,arrow = False,solid = True)
-        reflect(y = 6)
-        Circle(1,1)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-15.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(1,2,3,2,arrow = False,solid = True)
-  Line(2,1,4,1,arrow = False,solid = False)
-  Line(3,0,5,0,arrow = False,solid = True)
-  Line(0,3,2,3,arrow = False,solid = False)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-19.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(4,4,2,2,arrow = True,solid = True)
-  Rectangle(3,4,5,6)
-  Rectangle(0,0,2,2)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-8.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(0,0,0,4,arrow = False,solid = True)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-57-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-23.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(4,1,2,1,arrow = False,solid = True)
-    for (2)
-        Line(-4*i + 5,2,-4*i + 5,4,arrow = True,solid = True)
-          for (3)
-              Circle(-4*j + 9,4*i + 1)
-              Line(8,1,3*i + 6,3*i + 1,arrow = True,solid = False)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-23-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-60.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(0,3,2,5)
-    for (2)
-        Circle(3*i + 4,1)
-        Circle(-2*i + 7,-3*i + 7)
-        Line(5,3,-3*i + 7,2,arrow = True,solid = True)
-        Line(4*i + 2,3*i + 4,4,4,arrow = True,solid = True)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-60-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-16.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Circle(9,1)
-    for (3)
-        Circle(2*i + 3,-3*i + 10)
-        Circle(-2*i + 5,3*i + 1)
-        Line(2*i + 2,-3*i + 7,2*i + 3,-3*i + 9,arrow = False,solid = True)
-        Line(-2*i + 7,3*i + 3,-2*i + 8,3*i + 1,arrow = False,solid = True)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-13.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(5,0,3,0,arrow = True,solid = True)
-  Line(0,3,2,3,arrow = True,solid = True)
-  Line(3,2,1,2,arrow = True,solid = True)
-  Line(2,1,4,1,arrow = True,solid = True)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-47.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-      reflect(y = 11)
-      Rectangle(4,9,7,10)
-            reflect(x = 11)
-            Rectangle(8,0,11,3)
-            Rectangle(1,4,2,7)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-16-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-5.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(12,9,12,0,arrow = True,solid = True)
-    for (2)
-        Rectangle(-3*i + 6,3*i + 5,-3*i + 8,9)
-        Rectangle(9*i,-4*i + 7,9*i + 2,9)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-59.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(4,0,0,0,arrow = False,solid = False)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-5-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-50.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(8,3,9,3,arrow = False,solid = True)
-    for (2)
-        Line(-6*i + 8,3*i + 3,-3*i + 7,3,arrow = True,solid = True)
-        Line(5*i + 2,3*i + 1,5*i + 4,3,arrow = True,solid = True)
-        Rectangle(9*i,2*i,10*i + 2,3*i + 2)
-        Rectangle(-4*i + 4,3*i + 2,-5*i + 7,2*i + 5)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-50-extrapolation.png}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-6.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(0,1,0,4,arrow = False,solid = True)
-  Rectangle(2,0,5,3)
-    for (2)
-        Line(0,3*i + 1,2,3*i,arrow = False,solid = True)
-        Line(-3*i + 3,4,-2*i + 5,3,arrow = False,solid = True)
-        \end{verbatim}
-\end{minipage}
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-6-extrapolation.png}
     \end{tabular}

### 2017-05-13 paper.tex
I think this is a better section title, given the language used in the text.
preliminary extrapolation results

@@
 \section{Synthesizing graphics programs from execution traces}
+Although the execution trace of a graphics program describes the parts
+of a scene,
+it fails to encode higher-level features of the image,
+such as repeated motifs,
+symmetries or reflections.
 
@@
   \pagebreak
+  \section{Preliminary extrapolation results} 
+\input{extrapolations.tex}
+
+\pagebreak
   \section{Preliminary Synthesis results} 

### 2017-05-13 paper.tex
section describing how program synthesis works

@@
 \DeclareMathOperator{\argmin}{argmin} % no space, limits underneath in displays
+\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays
+\DeclareMathOperator{\argmax}{argmax} % no space, limits underneath in displays
 
@@
 like a SAT or SMT solver~\cite{de2008z3}.
-
-%% \remark{This is an \emph{excellent} explanation! I would add maybe one
-%%   more sentence / citation to elaborate on what you mean by
-%%   `techniques from the program synthesis community', as this will be
-%%   an unfamiliar concept to some readers, I imagine.}
+These techniques excel at uncovering high-level symbolic structure,
+but are not well equipped to deal with real-valued perceptual inputs.
 
@@
 
-\section{Neural architecture for inferring image parses}
+\section{Neural architecture for inferring drawing execution traces}
 
@@
 training data.
+\begin{wrapfigure}{R}{0.5\textwidth}
+  \begin{center}
+    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-58-7.png}}\end{minipage}
+    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-33-5.png}}\end{minipage}
+    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-25-4.png}}\end{minipage}
+%    \begin{minipage}[t]{2cm}\includegraphics[width=2cm]{figures/randomScene-26-7.png}\end{minipage}
+%    \begin{minipage}[t]{2cm}\includegraphics[width=2cm]{figures/randomScene-19-3.png}\end{minipage}
+  \end{center}
+  \caption{Network is trained to infer execution traces for figures like the three shown above.}\label{trainingData}
+\end{wrapfigure}
 
@@
 Although the execution trace of a graphics program describes the parts
-of a scene,
-it fails to encode higher-level features of the image,
-such as repeated motifs,
-symmetries or reflections.
+of a scene, it fails to encode higher-level features of the image,
+such as repeated motifs, symmetries or reflections.  A \emph{graphics
+  program} better describe structures like these,
+and we now take as our goal to synthesize simple graphics programs from
+their execution traces.
 
-\begin{table}[h]
+We constrain the space of allowed programs by writing down a context
+free grammar over a space of programs. Although it might be desirable
+to synthesize programs in a Turing-complete language like Lisp or
+Python, a more tractable approach is to specify what in the program
+languages community is called a Domain Specific Language (DSL). Our DSL (Table~\ref{DSL})
+encodes prior knowledge of what graphics programs tend to look like.
+
+\begin{table}[H]
   \begin{tabular}{rl}
@@
   \caption{Grammar over graphics programs.
-We allow loops (\texttt{for}), vertical/horizontal reflections (\texttt{REFLECT}), and affine transformations (\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}).}
+We allow loops (\texttt{for}), vertical/horizontal reflections (\texttt{REFLECT}), and affine transformations (\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}).}\label{DSL}
 \end{table}
 
-\section{Neural networks for guiding SMC}
+Given the DSL and a trace $T$, we want a program that evaluates to $T$
+and also minimizes some measure of program cost:
+\begin{equation}
+  \text{program}(T) = \argmin_{\substack{p\in \text{DSL}\\p \text{ evaluates to } T}} \text{cost}(p)\label{programObjective}
+\end{equation}
+An intuitive measure of program cost is its length.  We define the
+cost of a program to be the number of statements it contains, where a
+statement is a ``Command'' in Table~\ref{DSL}.
+
+The constrained optimization problem in
+equation~\ref{programObjective} is intractable in general, but there
+exist efficient-in-practice tools for finding exact solutions to
+program synthesis problems like these. We use the state-of-the-art Sketch
+tool~\cite{solar2008program}. Describing Sketch's program synthesis
+algorithm is beyond the scope of this paper; see supplement.  At a
+high level, Sketch takes as input a space of programs, along with a
+specification of the program 's behavior and optionally a cost
+function.  It translates the synthesis problem into a constraint
+satisfaction problem, and then uses a quasiboolean solver to find a
+minimum cost program satisfying the specification.  In exchange for
+not having any guarantees on how long it will take to find a minimum
+cost solution, it comes with the guarantee that it will always find a
+globally optimal program.
+
+Why synthesize a graphics program,
+if the execution trace already suffices to recover the objects in an image?
+Within our domain of hand-drawn figures, graphics program synthesis has several important uses:
+\subsection{Extrapolating figures}
+Given the source code of a graphics program,
+we can automatically tweak the program
+to make natural-feeling changes to the figure.
+For example,
+we can change all of the circles to squares,
+were make all of the lines be dashed.
+We can also \textbf{extrapolate} figures
+by increasing the number of times that loops are executed.
+\input{extrapolations.tex}
+
+\subsection{Modeling similarity between figures}
+
+\subsection{Correcting errors made by the neural network}
 
@@
 hypothesized program output, and gives the likelihood of the observed
-image conditioned on the program output. We want to sample from:
+image conditioned on the program output.
+Write $\hat{T}(I)$ for the trace the model predicts for image $I$.
+
+We can extract a few basic features of a program, like its size or how many
+loops it has,
+and use these features to help predict
+whether a trace is the correct explanation for an image.
 \begin{equation}
-\probability [p|x]  \propto L(x | \text{render}(p)) \probability [p]
+\hat{T}(I) = \argmax_{T} L(I | \text{render}(T)) + \theta\cdot  \phi \left( \text{program}(T) \right)
 \end{equation}
-where $\probability [p]$ is the prior probability of program $p$, and $x$ is the observed image.
-
-Let $p$ be a program with $L$ lines, which we will write as $p = (p_1,p_2,\cdots,p_L)$. Assume the prior factors into:
-\begin{equation}
-  \probability [p]\propto \prod_{l\leq L}\probability [p_l]
-\end{equation}
-Define the distribution $q_L(\cdot)$, which happens to be proportional to the above posterior:
-\begin{equation}
-  q_L(p_1,p_2,\cdots,p_{L - 1},p_L)\propto q_{L - 1}(p_1,p_2,\cdots,p_{L - 1})\times \frac{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1}))}\times\probability [p_L]
-\end{equation}
-Now suppose we have some samples from $q_{L - 1}(\cdot)$, and that we
-then sample a $p_L$ from a distribution proportional to $\frac{L(x |
-  \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x |
-  \text{render}(p_1,p_2,\cdots,p_{L - 1}))}\times\probability [p_L]$.
-The resulting programs $p$ are distributed according to $q_L$, and so
-are also distributed according to $\probability [p|x]$.
-
-How do we sample $p_L$ from a distribution proportional to $\frac{L(x
-  | \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x |
-  \text{render}(p_1,p_2,\cdots,p_{L - 1}))}\times\probability [p_L]$?
-We have a neural network that takes as input the target image $x$ and
-the program so far, and produces a distribution over next lines of
-code ($p_L$).  We write $\text{NN}(p_L | p_1,\cdots,p_{L - 1};x)$ for
-the distribution output by the neural network. So we can sample from NN and then weight the samples by:
-\begin{equation}
-  w(p_L) = \frac{\probability [p_L]}{\text{NN}(p_L | p_1,\cdots,p_{L - 1};x)}\times \frac{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1}))}
-\end{equation}
-Then we can resample from these now weighted samples to get a new
-population of particles (here programs are particles), where each
-program now has $L$ lines instead of $L - 1$.
-
-This procedure can be seen as a particle filter, where each successive
-latent variable is another line of code, and the emission
-probabilities are successive ratios of likelihoods under $L(\cdot |
-\cdot)$.
-
-\textbf{Comments for Dan}. Right now I'm not actually sampling from
-the neural network - instead, I enumerate the top few hundred lines of
-code suggested by the network, and then weight them by their
-likelihoods.
-So actually the form of NN is:
-\begin{equation}
-  \text{NN}(p_L | p_1,\cdots,p_{L - 1};x)\propto \begin{cases}
-    1,&\text{ if }p_L \in \text{top hundred neural network proposals}\\
-0,&\text{otherwise}.    \end{cases}
-\end{equation}
-Do you think this is a problem? The neural network puts almost all of its mass on a few guesses.
-In order to get the correct line of code I sometimes need to get something like the 50th  top guess,
-so I don't want to literally just sample from the distribution suggested by the neural network.
-
-  \begin{algorithm}[tb]
-   \caption{Neurally guided SMC}
-   \label{guideAlgorithm}
-\begin{algorithmic}
-  \STATE {\bfseries Input:} Neural network NN, beam size $N$, maximum length $L$, target image $x$
-  \STATE {\bfseries Output:} Samples of the program trace
-  \STATE Set $B_0 = \{\text{empty program}\}$
-  \FOR{$1\leq l\leq L$}
-  \FOR{$1\leq n\leq N$}
-  \STATE{ $p_n\sim \text{Uniform}(B_{l - 1})$}
-  \STATE{ $p'_{n}\sim \text{NN}(\text{render}(p),x)$}
-  \STATE{ Define $r_n = p'_n\cdot p_n$}
-  \STATE{ Set $\tilde{w}(r_n) = \frac{L(x|r_n)}{L(x|p_n)}\times\frac{\probability [p'_n]}{\probability [p'_n = \text{NN}(\text{render}(p),x)]}$}
-  \ENDFOR
-  \STATE{ Define $w(p) = \frac{\tilde{w}(p)}{\sum_{p'}\tilde{w}(p')}$}
-  \STATE{ Set $B_l$ to be $N$ samples from $r_n$ distributed according to $w(\cdot)$}
-  \ENDFOR
-  \STATE {\bfseries return} $\{p : p\in B_{l\leq L}, p \text{ is finished}\}$
-\end{algorithmic}
-  \end{algorithm}
+where $\phi (\cdot)$ is a feature extractor for programs.
+This is equivalent to doing MAP inference in a generative model where the program
+is first drawn from a log linear distribution $\propto \exp (\theta\cdot \phi (\text{program}))$,
+than the program is executed deterministically,
+and then we observe a noisy version of the program's output,
+where $L$ is the noise model.
 
@@
   \section{Preliminary extrapolation results}
-\input{extrapolations.tex}
 

### 2017-05-13 supplement.tex
supplement

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2016
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2016}

\usepackage{dsfont}

% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage{nips_2016}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\usepackage{listings}
\usepackage{amsthm}
% use Times
\usepackage{times}
% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfig} 
\usepackage{fancyvrb}

\usepackage{caption}
\usepackage{subcaption}

\fvset{fontsize=\footnotesize}

\usepackage{amssymb}
\usepackage{listings}
\usepackage{wrapfig}
\usepackage{tabularx}

\usepackage{verbatim}
 \usepackage{booktabs}
 % For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{tikz}
% As of 2011, we use the hyperref package to produce hyperlinks in the
% resulting PDF.  If this breaks your system, please commend out the
% following usepackage line and replace \usepackage{icml2016} with
% \usepackage[nohyperref]{icml2016} above.
\usepackage{amsmath}
\usepackage{hyperref}
\DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays
\DeclareMathOperator{\argmin}{argmin} % no space, limits underneath in displays

% Packages hyperref and algorithmic misbehave sometimes.  We can fix
% this with the following command.

\newcommand{\Expect}{\mathds{E}} %{{\rm I\kern-.3em E}}
\newcommand{\Probability}{\mathds{P}} %{{\rm I\kern-.3em P}}

\newtheorem{proposition}{Proposition}

\newcommand\modt{\stackrel{\mathclap{\normalfont 2}}{\equiv}}

\title{Supplement to: Inferring Graphics Programs from Images}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
Kevin Ellis \\
Brain and Cognitive Sciences\\
MIT\\
%Pittsburgh, PA 15213 \\
\texttt{ellisk@mit.edu} \\
Daniel Ritchie\\
Department of Computer Science\\
Brown
\And
Armando Solar-Lezama \\
  CSAIL\\
MIT \\
\texttt{asolar@csail.mit.edu} \\
\And
Joshua B. Tenenbaum \\
Brain and Cognitive Sciences\\
MIT\\
\texttt{jbt@mit.edu} \\
}

\begin{document}
% \nipsfinalcopy is no longer used

\maketitle

\section{Neural networks for guiding SMC}

Let $L(\cdot | \cdot):\text{image}^2\to \mathcal{R}$ be our likelihood
function: it takes two images, an observed target image and a
hypothesized program output, and gives the likelihood of the observed
image conditioned on the program output. We want to sample from:
\begin{equation}
\probability [p|x]  \propto L(x | \text{render}(p)) \probability [p]
\end{equation}
where $\probability [p]$ is the prior probability of program $p$, and $x$ is the observed image.

Let $p$ be a program with $L$ lines, which we will write as $p = (p_1,p_2,\cdots,p_L)$. Assume the prior factors into:
\begin{equation}
  \probability [p]\propto \prod_{l\leq L}\probability [p_l]
\end{equation}
Define the distribution $q_L(\cdot)$, which happens to be proportional to the above posterior:
\begin{equation}
  q_L(p_1,p_2,\cdots,p_{L - 1},p_L)\propto q_{L - 1}(p_1,p_2,\cdots,p_{L - 1})\times \frac{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1}))}\times\probability [p_L]
\end{equation}
Now suppose we have some samples from $q_{L - 1}(\cdot)$, and that we
then sample a $p_L$ from a distribution proportional to $\frac{L(x |
  \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x |
  \text{render}(p_1,p_2,\cdots,p_{L - 1}))}\times\probability [p_L]$.
The resulting programs $p$ are distributed according to $q_L$, and so
are also distributed according to $\probability [p|x]$.

How do we sample $p_L$ from a distribution proportional to $\frac{L(x
  | \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x |
  \text{render}(p_1,p_2,\cdots,p_{L - 1}))}\times\probability [p_L]$?
We have a neural network that takes as input the target image $x$ and
the program so far, and produces a distribution over next lines of
code ($p_L$).  We write $\text{NN}(p_L | p_1,\cdots,p_{L - 1};x)$ for
the distribution output by the neural network. So we can sample from NN and then weight the samples by:
\begin{equation}
  w(p_L) = \frac{\probability [p_L]}{\text{NN}(p_L | p_1,\cdots,p_{L - 1};x)}\times \frac{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1}))}
\end{equation}
Then we can resample from these now weighted samples to get a new
population of particles (here programs are particles), where each
program now has $L$ lines instead of $L - 1$.

This procedure can be seen as a particle filter, where each successive
latent variable is another line of code, and the emission
probabilities are successive ratios of likelihoods under $L(\cdot |
\cdot)$.

\textbf{Comments for Dan}. Right now I'm not actually sampling from
the neural network - instead, I enumerate the top few hundred lines of
code suggested by the network, and then weight them by their
likelihoods.
So actually the form of NN is:
\begin{equation}
  \text{NN}(p_L | p_1,\cdots,p_{L - 1};x)\propto \begin{cases}
    1,&\text{ if }p_L \in \text{top hundred neural network proposals}\\
0,&\text{otherwise}.    \end{cases}
\end{equation}
Do you think this is a problem? The neural network puts almost all of its mass on a few guesses.
In order to get the correct line of code I sometimes need to get something like the 50th  top guess,
so I don't want to literally just sample from the distribution suggested by the neural network.

  \begin{algorithm}[tb]
   \caption{Neurally guided SMC}
   \label{guideAlgorithm}
\begin{algorithmic}
  \STATE {\bfseries Input:} Neural network NN, beam size $N$, maximum length $L$, target image $x$
  \STATE {\bfseries Output:} Samples of the program trace
  \STATE Set $B_0 = \{\text{empty program}\}$
  \FOR{$1\leq l\leq L$}
  \FOR{$1\leq n\leq N$}
  \STATE{ $p_n\sim \text{Uniform}(B_{l - 1})$}
  \STATE{ $p'_{n}\sim \text{NN}(\text{render}(p),x)$}
  \STATE{ Define $r_n = p'_n\cdot p_n$}
  \STATE{ Set $\tilde{w}(r_n) = \frac{L(x|r_n)}{L(x|p_n)}\times\frac{\probability [p'_n]}{\probability [p'_n = \text{NN}(\text{render}(p),x)]}$}
  \ENDFOR
  \STATE{ Define $w(p) = \frac{\tilde{w}(p)}{\sum_{p'}\tilde{w}(p')}$}
  \STATE{ Set $B_l$ to be $N$ samples from $r_n$ distributed according to $w(\cdot)$}
  \ENDFOR
  \STATE {\bfseries return} $\{p : p\in B_{l\leq L}, p \text{ is finished}\}$
\end{algorithmic}
  \end{algorithm}

\end{document}

### 2017-05-14 paper.tex
figure with example drawings and what the model produces

@@
 (b): Rendering of the parse our model infers for (a).
-We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) \& (d) for noisy renderings of (b).}\label{handDrawingExamples}
+We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) \& (d) for noisy renderings of (b).}\ref{handDrawingExamples}
+\end{figure}
+
+\begin{figure}[H]
+  \begin{minipage}[t]{2.25cm}
+    \includegraphics[width = 2cm]{figures/expert-10.png}
+    \includegraphics[width = 2cm]{figures/10-parse.png}    
+    \subcaption{Noisy input}
+  \end{minipage}
+  \begin{minipage}[t]{2.25cm}
+    \includegraphics[width = 2cm]{figures/expert-21.png}
+    \includegraphics[width = 2cm]{figures/21-parse.png}    
+    \subcaption{A graphical model}
+  \end{minipage}
+  \begin{minipage}[t]{2.25cm}
+    \includegraphics[width = 2cm]{figures/expert-77.png}
+    \includegraphics[width = 2cm]{figures/77-parse.png}    
+    \subcaption{A figure from a deep learning textbook}
+    \end{minipage}
+  \begin{minipage}[t]{2.25cm}
+    \includegraphics[width = 2cm]{figures/expert-0.png}
+    \includegraphics[width = 2cm]{figures/0-parse.png}    
+    \subcaption{Near miss}
+  \end{minipage}
+  \begin{minipage}[t]{2.25cm}
+    \includegraphics[width = 2cm]{figures/expert-38.png}
+    \includegraphics[width = 2cm]{figures/38-parse.png}    
+    \subcaption{Failing on a Ising model}
+  \end{minipage}
+  \begin{minipage}[t]{2.25cm}
+    \includegraphics[width = 2cm]{figures/expert-34.png}
+    \includegraphics[width = 2cm]{figures/34-parse.png}     
+    \subcaption{Illusory contours}
+    \end{minipage}
+  \caption{Example drawings above model outputs. See also Fig.~\ref{firstPageExamples}}\label{handDrawingExamples}
   \end{figure}

### 2017-05-14 extrapolations.tex
updated extrapolation results

@@
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-3.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-3-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-5.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-5-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-6.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-6-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-7.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-7-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-12.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-12-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-14.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-14-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-16.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-16-extrapolation.png}
+    \end{tabular}        
+            \\
+
             \begin{tabular}{ll}
@@
     \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-17-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-18.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-18-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-20.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-20-extrapolation.png}
     \end{tabular}        
@@
             \begin{tabular}{ll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-7.png}&
-    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-7-extrapolation.png}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-22.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-22-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-23.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-23-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-24.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-24-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-26.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-26-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-29.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-29-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-30.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-30-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-31.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-31-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-34.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-34-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-35.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-35-extrapolation.png}
     \end{tabular}        
@@
             \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-37.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-37-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-45.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-45-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-48.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-48-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-49.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-49-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-50.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-50-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-52.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-52-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-56.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-56-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-57.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-57-extrapolation.png}
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-58.png}&
@@
             \begin{tabular}{ll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-22.png}&
-    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-22-extrapolation.png}
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{ll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-14.png}&
-    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-14-extrapolation.png}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-60.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-60-extrapolation.png}
     \end{tabular}        
@@
             \begin{tabular}{ll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-12.png}&
-    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-12-extrapolation.png}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-70.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-70-extrapolation.png}
     \end{tabular}        
@@
             \begin{tabular}{ll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-35.png}&
-    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-35-extrapolation.png}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-74.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-74-extrapolation.png}
     \end{tabular}        
@@
             \begin{tabular}{ll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-31.png}&
-    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-31-extrapolation.png}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-75.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-75-extrapolation.png}
     \end{tabular}        
@@
             \begin{tabular}{ll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-37.png}&
-    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-37-extrapolation.png}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-77.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-77-extrapolation.png}
     \end{tabular}        
@@
             \begin{tabular}{ll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-29.png}&
-    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-29-extrapolation.png}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-83.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-83-extrapolation.png}
     \end{tabular}        
@@
             \begin{tabular}{ll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-57.png}&
-    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-57-extrapolation.png}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-85.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-85-extrapolation.png}
     \end{tabular}        
@@
             \begin{tabular}{ll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-23.png}&
-    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-23-extrapolation.png}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-86.png}&
+    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-86-extrapolation.png}
     \end{tabular}
-            \\
-
-            \begin{tabular}{ll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-60.png}&
-    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-60-extrapolation.png}
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{ll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-16.png}&
-    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-16-extrapolation.png}
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{ll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-5.png}&
-    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-5-extrapolation.png}
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{ll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-50.png}&
-    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-50-extrapolation.png}
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{ll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-6.png}&
-    \includegraphics[width = 5cm]{../TikZ/extrapolations/expert-6-extrapolation.png}
-    \end{tabular}

### 2017-05-14 synthesizerOutputs.tex
updated extrapolation results

@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-41.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(0,0,1,6)
-  Rectangle(2,0,3,6)
-  Rectangle(4,0,5,6)
+  line(6,2,6,3,arrow = False,solid = True)
+  line(6,2,3,2,arrow = True,solid = True)
+  rectangle(0,0,8,9)
+  rectangle(5,3,7,6)
+        reflect(y = 9)
+        line(3,7,5,5,arrow = True,solid = True)
+        rectangle(1,6,3,8)
         \end{verbatim}
 \end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-2.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  rectangle(4,2,6,5)
+        reflect(y = 7)
+        line(2,6,4,4,arrow = True,solid = True)
+        rectangle(0,5,2,7)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-3.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  circle(10,5)
+  line(3,2,5,4,arrow = True,solid = True)
+    for (2)
+        line(-4*i + 7,3*i + 5,-4*i + 9,5,arrow = True,solid = True)
+        rectangle(-5*i + 5,-3*i + 3,5*i + 7,3*i + 7)
+        rectangle(1,6*i + 1,3,6*i + 3)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-4.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  circle(10,4)
+  line(10,1,10,3,arrow = False,solid = False)
+  line(10,1,2,1,arrow = True,solid = False)
+  rectangle(4,2,7,6)
+        reflect(y = 8)
+        line(2,1,4,3,arrow = True,solid = True)
+        line(7,4,9,4,arrow = True,solid = True)
+        rectangle(0,0,2,2)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-5.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(12,9,12,0,arrow = True,solid = True)
+    for (2)
+        rectangle(3*i + 6,-2*i + 5,3*i + 8,9)
+        rectangle(3*i,7,3*i + 2,9)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-6.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(0,4,3,4,arrow = False,solid = True)
+  rectangle(2,0,5,3)
+    for (2)
+        line(3*i,3*i + 1,3*i + 2,3*i,arrow = False,solid = True)
+        line(0,-3*i + 4,-2*i + 2,3,arrow = False,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-7.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  for (3)
+      circle(3*i + 1,6)
+      circle(-3*i + 7,1)
+      line(-3*i + 7,-1*i + 4,-3*i + 7,5,arrow = False,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-8.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(0,0,0,4,arrow = False,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-9.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(6,0,0,0,arrow = True,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-10.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  rectangle(0,0,3,4)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-11.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  circle(1,1)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-12.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  for (2)
+      circle(-5*i + 6,1)
+      line(2,5*i + 1,5,5*i + 1,arrow = False,solid = True)
+      line(5*i + 1,2,5*i + 1,5,arrow = False,solid = True)
+      rectangle(-5*i + 5,5,-5*i + 7,7)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-13.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(2,1,4,1,arrow = True,solid = True)
+  line(5,0,3,0,arrow = True,solid = True)
+  line(0,3,2,3,arrow = True,solid = True)
+  line(3,2,1,2,arrow = True,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-14.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  rectangle(6,0,7,1)
+    for (3)
+        rectangle(-2*i + 4,2*i + 2,-2*i + 5,2*i + 3)
+        rectangle(-2*i + 4,2*i,-2*i + 5,2*i + 1)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-15.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(3,0,5,0,arrow = False,solid = True)
+  line(2,1,4,1,arrow = False,solid = False)
+  line(0,3,2,3,arrow = False,solid = False)
+  line(1,2,3,2,arrow = False,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-16.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  circle(9,1)
+    for (3)
+        circle(2*i + 3,-3*i + 10)
+        circle(2*i + 1,-3*i + 7)
+        line(-2*i + 6,3*i + 1,-2*i + 7,3*i + 3,arrow = False,solid = True)
+        line(-2*i + 7,3*i + 3,-2*i + 8,3*i + 1,arrow = False,solid = True)
+        \end{verbatim}
+\end{minipage}
+
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-17.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(2,9,4,11)
+  rectangle(8,0,10,2)
     for (3)
-        Line(-2*i + 7,3*i + 3,-2*i + 6,3*i + 1,arrow = True,solid = True)
-        Line(2*i + 3,-3*i + 9,2*i + 4,-3*i + 7,arrow = True,solid = True)
-        Rectangle(2*i,-3*i + 6,2*i + 2,-3*i + 8)
-        Rectangle(-2*i + 8,3*i,-2*i + 10,3*i + 2)
+        line(-2*i + 7,3*i + 3,-2*i + 8,3*i + 1,arrow = True,solid = True)
+        line(2*i + 3,-3*i + 9,2*i + 2,-3*i + 7,arrow = True,solid = True)
+        rectangle(-2*i + 6,3*i + 3,-2*i + 8,3*i + 5)
+        rectangle(-2*i + 4,3*i,-2*i + 6,3*i + 2)
         \end{verbatim}
 \end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-18.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  for (2)
+      circle(-1*i + 4,-2*i + 5)
+      circle(-6*i + 7,3*i + 3)
+      circle(-2*i + 7,1)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-19.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(4,4,2,2,arrow = True,solid = True)
+  rectangle(3,4,5,6)
+  rectangle(0,0,2,2)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-20.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  rectangle(0,4,2,6)
+    for (2)
+        circle(4*i + 5,4*i + 1)
+        line(4*i + 4,5,4*i + 2,5,arrow = True,solid = True)
+              reflect(x = 10)
+              circle(4*i + 5,-4*i + 5)
+              line(4*i + 5,4,4*i + 5,2,arrow = True,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-21.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  circle(1,5)
+    for (2)
+        line(-4*i + 8,1,-4*i + 6,1,arrow = True,solid = True)
+        rectangle(4*i + 4,4*i,4*i + 6,4*i + 2)
+              reflect(x = 10)
+              line(-4*i + 5,2,-4*i + 5,4,arrow = True,solid = True)
+              rectangle(4*i,4*i,4*i + 2,4*i + 2)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-22.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(4,5,2,5,arrow = True,solid = True)
+  line(8,5,6,5,arrow = True,solid = True)
+    for (3)
+        line(4*i + 1,4,4*i + 1,2,arrow = True,solid = True)
+        rectangle(4*i,0,4*i + 2,2)
+        rectangle(-4*i + 8,4,-4*i + 10,6)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-23.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  for (2)
+      line(-4*i + 8,1,-4*i + 6,1,arrow = True,solid = True)
+            reflect(x = 10)
+            circle(5,-4*i + 5)
+            circle(-8*i + 9,4*i + 1)
+            line(-4*i + 9,2,-4*i + 9,4,arrow = True,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-24.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(5,7,5,6,arrow = True,solid = True)
+  rectangle(2,0,4,2)
+    for (2)
+        line(2*i + 1,-4*i + 7,2*i + 1,-4*i + 6,arrow = True,solid = True)
+        rectangle(0,4*i + 3,6,3*i + 6)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-25.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(3,1,2,1,arrow = True,solid = True)
+  rectangle(6,0,8,2)
+        reflect(x = 5)
+        line(6,1,5,1,arrow = True,solid = True)
+        rectangle(3,0,5,2)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-26.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(1,3,1,4,arrow = False,solid = True)
+  line(1,3,1,2,arrow = True,solid = True)
+  line(1,8,1,6,arrow = True,solid = True)
+    for (3)
+        circle(1,4*i + 1)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-27.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+      line(0,1,1,0,arrow = False,solid = True)
+      line(1,2,2,1,arrow = False,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-28.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(0,2,2,2,arrow = False,solid = True)
+  line(0,0,0,2,arrow = False,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-29.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  for (3)
+      line(0,-1*i + 6,2*i + 2,-1*i + 6,arrow = False,solid = True)
+      line(-1*i + 2,2*i,-1*i + 2,4,arrow = False,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-30.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  rectangle(0,0,2,2)
+    for (2)
+        circle(1,-3*i + 4)
+        circle(5,-2*i + 4)
+        rectangle(-4*i + 4,2*i + 1,-4*i + 6,5)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-31.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  circle(4,3)
+    for (3)
+        circle(-3*i + 7,5)
+        circle(7,-2*i + 5)
+        rectangle(-3*i + 6,2*i,-3*i + 8,6)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-32.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  circle(5,5)
+  line(2,5,4,5,arrow = False,solid = True)
+  rectangle(0,4,2,6)
+  rectangle(0,0,5,3)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-33.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(0,3,6,3,arrow = False,solid = False)
+  line(0,0,0,3,arrow = False,solid = True)
+  line(0,0,6,0,arrow = False,solid = False)
+  line(6,0,6,3,arrow = False,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-34.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  for (2)
+      line(-1*i + 2,-1*i + 3,-1*i + 2,-1*i + 5,arrow = False,solid = True)
+      line(3,-3*i + 3,5,-3*i + 3,arrow = False,solid = True)
+      line(4*i,-5*i + 5,2*i + 2,-3*i + 5,arrow = False,solid = True)
+      line(-4*i + 5,1,-2*i + 5,-1*i + 3,arrow = False,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-35.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  circle(1,6)
+    for (2)
+        circle(-5*i + 6,1)
+        line(-1*i + 2,-1*i + 6,-5*i + 6,2,arrow = True,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-36.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  for (2)
+      rectangle(-8*i + 8,5*i,-7*i + 9,6*i + 1)
+      rectangle(0,-8*i + 8,3*i + 1,-5*i + 9)
+      rectangle(-2*i + 7,3*i + 2,9,5*i + 4)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-37.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  circle(1,8)
+    for (2)
+        line(-4*i + 5,5*i + 2,-2*i + 5,5,arrow = False,solid = True)
+        rectangle(4*i,-5*i + 5,6,-7*i + 9)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-40.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  circle(4,1)
+        reflect(x = 8)
+        circle(1,1)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-41.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  rectangle(0,0,1,6)
+  rectangle(4,0,5,6)
+  rectangle(2,0,3,6)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-42.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(4,1,4,5,arrow = False,solid = False)
+  line(4,0,4,1,arrow = False,solid = False)
+  line(0,0,0,5,arrow = False,solid = False)
+        \end{verbatim}
+\end{minipage}
+
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-43.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-      Line(0,0,0,5,arrow = False,solid = True)
+  line(0,0,0,5,arrow = False,solid = True)
+  line(4,0,4,5,arrow = False,solid = True)
         \end{verbatim}
 \end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-44.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+      reflect(x = 12)
+      circle(4,1)
+      line(9,1,10,1,arrow = False,solid = True)
+      rectangle(0,0,2,2)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-45.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  circle(7,6)
+    for (2)
+            reflect(y = 12)
+            line(2*i + 2,4*i + 2,4*i + 2,2*i + 4,arrow = True,solid = True)
+            rectangle(-1*i + 1,-6*i + 10,3,-4*i + 12)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-46.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+      reflect(x = 9)
+      line(8,3,8,6,arrow = False,solid = True)
+            reflect(y = 9)
+            circle(1,1)
+            line(3,1,6,1,arrow = False,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-47.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+      reflect(y = 11)
+      rectangle(4,9,7,10)
+            reflect(x = 11)
+            rectangle(8,0,11,3)
+            rectangle(9,4,10,7)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-48.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  for (3)
+      line(3,-1*i + 2,5,-1*i + 2,arrow = False,solid = True)
+      line(-1*i + 2,3,-1*i + 4,3,arrow = False,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-49.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  rectangle(0,0,3,3)
+    for (2)
+        rectangle(0,-3*i + 7,-1*i + 3,-4*i + 10)
+        rectangle(-3*i + 7,0,-3*i + 9,2)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-50.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(8,3,9,3,arrow = False,solid = True)
+    for (2)
+        line(2,-5*i + 6,4,-1*i + 4,arrow = True,solid = True)
+        line(7,-1*i + 4,-2*i + 9,-1*i + 4,arrow = True,solid = True)
+        rectangle(0,-5*i + 5,2,-5*i + 7)
+        rectangle(-5*i + 9,2,-5*i + 12,5)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-51.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  rectangle(4,4,7,5)
+  rectangle(0,0,3,1)
+  rectangle(2,2,5,3)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-52.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  circle(4,10)
+    for (3)
+        circle(-3*i + 7,5)
+        circle(3*i + 1,1)
+        line(3*i + 1,4,3*i + 1,2,arrow = True,solid = True)
+        line(4,9,-3*i + 7,6,arrow = True,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-53.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(0,8,8,8,arrow = False,solid = True)
+  line(6,8,6,4,arrow = True,solid = True)
+  line(2,8,2,6,arrow = True,solid = True)
+  line(4,8,4,0,arrow = True,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-54.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(2,3,2,5,arrow = False,solid = True)
+  rectangle(1,5,3,7)
+  rectangle(0,0,4,7)
+  rectangle(1,1,3,3)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-55.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  circle(1,5)
+  line(1,4,1,2,arrow = True,solid = True)
+  rectangle(0,0,2,2)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-56.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  circle(3,1)
+    for (2)
+            reflect(x = 6)
+            circle(4*i + 1,-4*i + 8)
+            circle(-4*i + 5,5*i + 1)
+            rectangle(-4*i + 4,-3*i + 3,6,-7*i + 9)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-57.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  for (3)
+      circle(-4*i + 9,4)
+      circle(4*i + 1,7)
+      circle(-4*i + 9,1)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-58.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(8,0,8,7,arrow = True,solid = True)
+  line(8,0,0,0,arrow = True,solid = True)
+    for (3)
+        rectangle(-2*i + 6,0,-2*i + 7,-1*i + 5)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-59.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  line(4,0,0,0,arrow = False,solid = False)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-60.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  rectangle(0,3,2,5)
+    for (2)
+        circle(3*i + 4,1)
+        circle(-2*i + 7,-3*i + 7)
+        line(-1*i + 6,-4*i + 7,2*i + 5,-3*i + 5,arrow = True,solid = True)
+        line(3*i + 2,-1*i + 4,4,-2*i + 4,arrow = True,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-61.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  circle(2,1)
+  circle(6,1)
+  line(5,1,3,1,arrow = True,solid = True)
+  rectangle(0,0,7,2)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{ll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-62.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+  rectangle(2,1,4,3)
+  rectangle(5,0,8,3)
+  rectangle(0,2,1,3)
+        \end{verbatim}
+\end{minipage}
+
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-63.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(0,0,5,5)
-  Rectangle(1,1,4,4)
-  Rectangle(2,2,3,3)
+  rectangle(2,2,3,3)
+  rectangle(0,0,5,5)
+  rectangle(1,1,4,4)
         \end{verbatim}
 \end{minipage}
-\end{tabular}        
-        \\
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-11.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Circle(1,1)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-45.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(0,4,4,8)
-        reflect(y = 12)
-        Circle(7,6)
-        Line(2,2,2,4,arrow = True,solid = True)
-        Line(4,6,6,6,arrow = True,solid = True)
-        Rectangle(1,0,3,2)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-51.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(2,2,5,3)
-  Rectangle(0,0,3,1)
-  Rectangle(4,4,7,5)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-21.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Circle(1,5)
-    for (2)
-        Line(-5*i + 9,-1*i + 2,-7*i + 9,-3*i + 4,arrow = True,solid = True)
-        Rectangle(-4*i + 8,4*i,-4*i + 10,4*i + 2)
-              reflect(x = 6)
-              Line(7*i + 1,-1*i + 2,5*i + 1,-3*i + 4,arrow = True,solid = True)
-              Rectangle(8*i,4*i,8*i + 2,4*i + 2)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-2.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(4,2,6,5)
-        reflect(y = 7)
-        Line(2,6,4,4,arrow = True,solid = True)
-        Rectangle(0,5,2,7)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-24.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(3,3,3,2,arrow = True,solid = True)
-  Rectangle(0,7,6,9)
-  Rectangle(2,0,4,2)
-  Rectangle(0,3,6,6)
-        Line(1,7,1,6,arrow = True,solid = True)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-7.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  for (3)
-      Circle(-3*i + 7,1)
-      Circle(3*i + 1,6)
-      Line(3*i + 1,2,3*i + 1,5,arrow = False,solid = True)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-44.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-      reflect(x = 12)
-      Circle(4,1)
-      Line(9,1,10,1,arrow = False,solid = True)
-      Rectangle(10,0,12,2)
-        \end{verbatim}
-\end{minipage}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-64.png}&
+
         \begin{minipage}{10cm}
@@
       reflect(x = 6)
-      Line(5,2,5,4,arrow = False,solid = True)
+      line(5,2,5,4,arrow = False,solid = True)
             reflect(y = 6)
-            Line(2,5,4,5,arrow = False,solid = True)
-            Rectangle(0,4,2,6)
+            line(2,1,4,1,arrow = False,solid = True)
+            rectangle(0,0,2,2)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-36.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-65.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  for (2)
-      Rectangle(0,-3*i + 8,1,-2*i + 9)
-      Rectangle(-3*i + 8,5*i,9,8*i + 1)
-      Rectangle(-7*i + 7,-2*i + 2,-5*i + 9,4)
+      reflect(x = 6)
+      line(5,2,5,4,arrow = False,solid = True)
+            reflect(y = 6)
+            circle(1,1)
+            line(2,1,4,1,arrow = False,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-58.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-66.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(4,0,5,4)
-    for (2)
-        Line(8,0,-8*i + 8,-7*i + 7,arrow = True,solid = True)
-        Rectangle(-4*i + 6,0,-4*i + 7,-2*i + 5)
+  line(0,2,7,2,arrow = False,solid = True)
+  line(1,1,6,1,arrow = False,solid = True)
+  line(2,0,5,0,arrow = False,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-3.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-67.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Circle(10,5)
-  Line(7,5,9,5,arrow = True,solid = True)
-  Rectangle(5,3,7,7)
-  Rectangle(0,0,12,10)
-        reflect(y = 10)
-        Line(3,2,5,4,arrow = True,solid = True)
-        Rectangle(1,1,3,3)
+  line(1,5,5,1,arrow = False,solid = True)
+  line(1,4,5,0,arrow = False,solid = True)
+  rectangle(0,4,1,5)
+  rectangle(5,0,6,1)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-28.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-68.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(0,0,0,2,arrow = False,solid = True)
-  Line(0,2,2,2,arrow = False,solid = True)
+  for (3)
+      circle(4*i + 1,1)
+      rectangle(-4*i + 8,0,-4*i + 10,2)
         \end{verbatim}
 \end{minipage}
-\end{tabular}        
-        \\
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-22.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(8,5,6,5,arrow = True,solid = True)
-  Line(4,5,2,5,arrow = True,solid = True)
-    for (3)
-        Line(-4*i + 9,4,-4*i + 9,2,arrow = True,solid = True)
-        Rectangle(4*i,0,4*i + 2,2)
-        Rectangle(-4*i + 8,4,-4*i + 10,6)
-        \end{verbatim}
-\end{minipage}
     \end{tabular}        
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-69.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(0,4,5,6)
       reflect(x = 5)
-        Circle(4,1)
-        Line(1,4,1,2,arrow = True,solid = True)
+      circle(1,1)
+      line(4,4,4,2,arrow = True,solid = True)
+      rectangle(0,4,5,6)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-14.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-70.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(0,6,1,7)
-    for (3)
-        Rectangle(-2*i + 6,2*i,-2*i + 7,2*i + 1)
-        Rectangle(-2*i + 4,2*i,-2*i + 5,2*i + 1)
+  circle(3,1)
+    for (2)
+        line(-4*i + 5,8,-4*i + 5,6,arrow = True,solid = True)
+              reflect(x = 6)
+              circle(4*i + 1,-4*i + 9)
+              line(5,-4*i + 8,2,-3*i + 5,arrow = True,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-68.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-72.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  for (3)
-      Circle(4*i + 1,1)
-      Rectangle(4*i,0,4*i + 2,2)
+      reflect(x = 8)
+      circle(4,4)
+            reflect(y = 8)
+            circle(7,7)
+            rectangle(2,2,3,3)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-65.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-74.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-      reflect(y = 6)
-      Line(2,1,4,1,arrow = False,solid = True)
+  rectangle(0,0,6,6)
         reflect(x = 6)
-            Circle(1,1)
-            Line(1,2,1,4,arrow = False,solid = True)
+        rectangle(2,2,4,4)
+          for (3)
+              circle(3,2*i + 1)
+              circle(5,-2*i + 5)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-67.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-75.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(1,5,5,1,arrow = False,solid = True)
-  Line(1,4,5,0,arrow = False,solid = True)
-  Rectangle(5,0,6,1)
-  Rectangle(0,4,1,5)
+  for (3)
+      line(4*i + 2,5,4*i + 4,5,arrow = True,solid = True)
+            reflect(x = 10)
+            circle(-4*i + 13,1)
+            circle(4*i + 5,5)
+            line(4*i + 5,4,4*i + 5,2,arrow = True,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-12.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-76.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  for (2)
-      Circle(-5*i + 6,1)
-      Line(-4*i + 6,-1*i + 2,-1*i + 6,-4*i + 5,arrow = False,solid = True)
-      Line(-1*i + 2,-4*i + 6,-4*i + 5,-1*i + 6,arrow = False,solid = True)
-      Rectangle(5*i,5,5*i + 2,7)
+  line(4,5,4,10,arrow = False,solid = True)
+        reflect(x = 8)
+        circle(4,1)
+        circle(1,8)
+        line(4,5,8,2,arrow = False,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-42.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-77.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(0,0,0,5,arrow = False,solid = False)
-  Line(4,1,4,5,arrow = False,solid = False)
-  Line(4,0,4,1,arrow = False,solid = False)
+      reflect(x = 10)
+      line(6,8,8,8,arrow = False,solid = True)
+        for (2)
+            circle(-4*i + 5,7*i + 1)
+            line(3*i + 6,4*i + 1,9,4*i + 3,arrow = False,solid = True)
+            rectangle(4*i + 4,-4*i + 7,4*i + 6,-4*i + 9)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-10.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-78.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(0,0,3,4)
+  line(0,6,12,6,arrow = False,solid = True)
+  line(6,6,6,5,arrow = True,solid = True)
+  line(8,3,7,4,arrow = True,solid = True)
+  line(3,2,5,4,arrow = True,solid = True)
+        line(0,8,8,0,arrow = False,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-35.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-81.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Circle(1,1)
-    for (2)
-        Circle(-5*i + 6,5*i + 1)
-        Line(1,5,5*i + 1,2,arrow = True,solid = True)
+  rectangle(9,0,11,2)
+  rectangle(6,0,8,2)
+        reflect(x = 5)
+        circle(4,1)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-31.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-83.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Circle(7,3)
-    for (3)
-        Circle(-3*i + 7,5)
-        Circle(-3*i + 7,2*i + 1)
-        Rectangle(-3*i + 6,2*i,-3*i + 8,6)
+  for (2)
+      line(-4*i + 7,6,-6*i + 8,5,arrow = True,solid = True)
+            reflect(x = 10)
+            circle(2*i + 7,7)
+            circle(3*i + 2,-3*i + 4)
+            line(7*i + 1,-3*i + 6,3*i + 2,-3*i + 5,arrow = True,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-37.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-85.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Circle(1,8)
-    for (2)
-        Line(4*i + 1,-5*i + 7,2*i + 3,5,arrow = False,solid = True)
-        Rectangle(-4*i + 4,5*i,6,7*i + 2)
+  circle(1,1)
+    for (3)
+        circle(1,-3*i + 10)
+        line(1,-3*i + 9,1,-3*i + 8,arrow = True,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-40.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-86.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Circle(7,1)
-  Circle(4,1)
-  Circle(1,1)
+  for (2)
+      rectangle(-7*i + 7,-7*i + 7,-7*i + 8,-7*i + 8)
+      rectangle(-6*i + 6,-2*i + 4,-6*i + 8,-2*i + 6)
+      rectangle(-5*i + 5,5*i,-5*i + 8,5*i + 3)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
             \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-29.png}&
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-87.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(1,2,1,5,arrow = False,solid = True)
-    for (2)
-        Line(2,-4*i + 4,-4*i + 6,4,arrow = False,solid = True)
-        Line(0,-2*i + 6,-2*i + 2,6,arrow = False,solid = True)
-        Line(1,5,2*i + 2,5,arrow = False,solid = True)
+      reflect(x = 8)
+      rectangle(0,0,1,1)
+      rectangle(0,2,2,4)
+      rectangle(0,5,3,8)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-62.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(5,0,8,3)
-  Rectangle(2,1,4,3)
-  Rectangle(0,2,1,3)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-57.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  for (3)
-      Circle(-4*i + 9,4)
-      Circle(-4*i + 9,1)
-      Circle(4*i + 1,7)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-55.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Circle(1,5)
-  Line(1,4,1,2,arrow = True,solid = True)
-  Rectangle(0,0,2,2)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-66.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(0,2,7,2,arrow = False,solid = True)
-  Line(1,1,6,1,arrow = False,solid = True)
-  Line(2,0,5,0,arrow = False,solid = True)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-26.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Circle(1,9)
-  Line(1,8,1,6,arrow = True,solid = True)
-  Line(1,3,1,2,arrow = True,solid = True)
-  Line(1,3,1,4,arrow = False,solid = True)
-        reflect(y = 6)
-        Circle(1,1)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-15.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(1,2,3,2,arrow = False,solid = True)
-  Line(2,1,4,1,arrow = False,solid = False)
-  Line(3,0,5,0,arrow = False,solid = True)
-  Line(0,3,2,3,arrow = False,solid = False)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-19.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(4,4,2,2,arrow = True,solid = True)
-  Rectangle(3,4,5,6)
-  Rectangle(0,0,2,2)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-8.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(0,0,0,4,arrow = False,solid = True)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-23.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(4,1,2,1,arrow = False,solid = True)
-    for (2)
-        Line(-4*i + 5,2,-4*i + 5,4,arrow = True,solid = True)
-          for (3)
-              Circle(-4*j + 9,4*i + 1)
-              Line(8,1,3*i + 6,3*i + 1,arrow = True,solid = False)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-60.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Rectangle(0,3,2,5)
-    for (2)
-        Circle(3*i + 4,1)
-        Circle(-2*i + 7,-3*i + 7)
-        Line(5,3,-3*i + 7,2,arrow = True,solid = True)
-        Line(4*i + 2,3*i + 4,4,4,arrow = True,solid = True)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-16.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Circle(9,1)
-    for (3)
-        Circle(2*i + 3,-3*i + 10)
-        Circle(-2*i + 5,3*i + 1)
-        Line(2*i + 2,-3*i + 7,2*i + 3,-3*i + 9,arrow = False,solid = True)
-        Line(-2*i + 7,3*i + 3,-2*i + 8,3*i + 1,arrow = False,solid = True)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-13.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(5,0,3,0,arrow = True,solid = True)
-  Line(0,3,2,3,arrow = True,solid = True)
-  Line(3,2,1,2,arrow = True,solid = True)
-  Line(2,1,4,1,arrow = True,solid = True)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-47.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-      reflect(y = 11)
-      Rectangle(4,9,7,10)
-            reflect(x = 11)
-            Rectangle(8,0,11,3)
-            Rectangle(1,4,2,7)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-5.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(12,9,12,0,arrow = True,solid = True)
-    for (2)
-        Rectangle(-3*i + 6,3*i + 5,-3*i + 8,9)
-        Rectangle(9*i,-4*i + 7,9*i + 2,9)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-59.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(4,0,0,0,arrow = False,solid = False)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-50.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(8,3,9,3,arrow = False,solid = True)
-    for (2)
-        Line(-6*i + 8,3*i + 3,-3*i + 7,3,arrow = True,solid = True)
-        Line(5*i + 2,3*i + 1,5*i + 4,3,arrow = True,solid = True)
-        Rectangle(9*i,2*i,10*i + 2,3*i + 2)
-        Rectangle(-4*i + 4,3*i + 2,-5*i + 7,2*i + 5)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}        
-        \\
-
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-6.png}&
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-  Line(0,1,0,4,arrow = False,solid = True)
-  Rectangle(2,0,5,3)
-    for (2)
-        Line(0,3*i + 1,2,3*i,arrow = False,solid = True)
-        Line(-3*i + 3,4,-2*i + 5,3,arrow = False,solid = True)
-        \end{verbatim}
-\end{minipage}
-\end{tabular}

### 2017-05-15 paper.tex
Section 4 comments/edits.

@@
 statement is a ``Command'' in Table~\ref{DSL}.
+\remark{The flow here is a bit off/backwards.
+``We want a program that evaluates to $T$ and also minimizes some measure of program cost''---why do we care about cost?
+It'd be better to start by making a ``Bayesian Occam's razor'' appeal (e.g.
+the most compact/general program is the more likely explanation) and then saying that one way to do this is to minimize a cost function which is proportional to program length.}
 
@@
 \subsection{Extrapolating figures}
-Given the source code of a graphics program,
-we can automatically tweak the program
-to make natural-feeling changes to the figure.
+Having access to the source code of a graphics program facilitates coherent, high-level edits to the figure generated by that program. 
 For example,
@@
 \subsection{Correcting errors made by the neural network}
+
+\remark{Seems like you're still fleshing this part out, but I'll give my feedback anyway: (1) This subsection could really use a motivational introduction, e.g.
+``The program synthesizer can help correct errors/bad proposals from the neural network by favoring execution traces which lead to more concise/general programs.'' (2) The image likelihood function should probably be introduced sooner, when you talk about SMC/beam search.
+(3) Where does $\theta$ come from?
+Is it set by hand?
+Learned?
+(4) How does Equation 4 get used?
+Is this a modification to the beam search objective / SMC posterior?
+If so, it'd be great to have set up the version without it in an earlier section, and then be able to refer to this as a small modification of the previous equation.}
 

### 2017-05-15 paper.tex
Related work.

@@
 \section{Related work}
-attend infer repeat:~\cite{eslami1603attend}. Crucial distinction is
-that they focus on learning the generative model jointly with the
-inference network. Advantages of our system is that we learn symbolic
-programs, and that we do it from hand sketches rather than synthetic
-renderings.
 
-ngpm:~\cite{ritchie2016neurally}. We build on the idea of a guide program, extending it to scenes composed of objects, and then show how to learn programs from the objects we discover.
+Our work bears resemblance to the Attend-Infer-Repeat (AIR) system, which learns to decompose an image into its constituent objects~\cite{eslami1603attend}.
+AIR learns an iterative inference scheme which infers objects one by one and also decides when to stop inference; this is similar to our approach's first stage, which parses images into program execution traces.
+Our approach further produces interpretable, symbolic programs which generate those execution traces.
+The two approaches also differ in their architectures and training regimes: AIR learns a recurrent auto-encoding model via variational inference, whereas our parsing stage learns an autoregressive-style model from randomly-generated (execution trace, image) pairs.
+Finally, while AIR was evaluated on multi-MNIST images and synthetic 3D scenes, we focus on parsing and interpreting hand-drawn sketches.
+% attend infer repeat:~\cite{eslami1603attend}. Crucial distinction is
+% that they focus on learning the generative model jointly with the
+% inference network. Advantages of our system is that we learn symbolic
+% programs, and that we do it from hand sketches rather than synthetic
+% renderings.
 
-Sketch-n-Sketch:~\cite{Hempel:2016:SSP:2984511.2984575}.
-Semiautomated synthesis presented in a nice user interface.
-Complementary to our work: you could pass a sketch to our system and then pass the program to sketch-n-sketch
+Our image-to-execution-trace parsing architecture builds on prior work on controlling procedural graphics programs~\cite{ritchie2016neurally}.
+Given a program which generates random 2D recursive structures such as vines, that system learns a structurally-identical ``guide program'' whose output can be directed, via neural networks, to resemble a given target image.
+We adapt this method to a different visual domain (figures composed of multiple objects), using a broad prior over possible scenes as the initial program and viewing the execution trace through the guide program as a symbolic parse of the target image.
+We then show how to synthesize higher-level programs from these execution traces.
 
-Converting hand drawings into procedural models using deep networks:~\cite{huang2017shape,Nishida:2016:ISU:2897824.2925951}.
+In the computer graphics literature, there have been other systems which convert sketches into procedural representations.
+One uses a convolutional network to match a sketch to the output of a parametric 3D modeling system~\cite{huang2017shape}.
+Another uses convolutional networks to support sketch-based instantiation of procedural primitives within an interactive architectural modeling system~\cite{Nishida:2016:ISU:2897824.2925951}.
+Both systems focus on inferring fixed-dimensional parameter vectors.
+In contrast, we seek to automatically learn a structured, programmatic representation of a sketch which captures higher-level visual patterns.
+
+Prior work has also applied sketch-based program synthesis to authoring graphics programs.
+In particular, Sketch-n-Sketch presents a bi-directional editing system in which direct manipulations to a program's output automatically propagate to the program source code~\cite{Hempel:2016:SSP:2984511.2984575}.
+We see this work as complementary to our own: programs produced by our method could be provided to a Sketch-n-Sketch-like system as a starting point for further editing.
+
+\remark{Do you also want to cite your own work on ``Unsupverised Learning by Program Synthesis'' here?}
 

### 2017-05-15 paper.tex
similarity in program space figure
responses to comments

@@
 
-\section{Neural architecture for inferring drawing execution traces}
+\section{Neural architecture for inferring drawing execution traces}\label{neuralNetworkSection}
 
@@
   network layer sizes, which MLPs share parameters, etc.}
-
-\remark{Planning to move the description of SMC / beam search up here, too?}
 
@@
 recover what the network thinks is the most likely execution trace for
-images like these. But, if the network makes a mistake (predicts an
-incorrect line of code), it has no way of recovering from the error.
-In order to derender an image with $n$ objects, it must correctly
-predict $n$ drawing commands -- so its probability of success will
-decrease exponentially in $n$, assuming it has any nonzero chance of
-making a mistake.  For added robustness as $n$ becomes large, we treat
-the neural network outputs as proposals for a SMC sampling scheme.
-For the SMC sampler, we use pixel wise distance as a surrogate for a
-likelihood function; see supplement. Figure~\ref{syntheticResults}
+images like these, recovering traces maximizing $\probability_\theta
+[T|I]$. But, if the network makes a mistake (predicts an incorrect
+line of code), it has no way of recovering from the error.  In order
+to derender an image with $n$ objects, it must correctly predict $n$
+drawing commands -- so its probability of success will decrease
+exponentially in $n$, assuming it has any nonzero chance of making a
+mistake.  For added robustness as $n$ becomes large, we treat the
+neural network outputs as proposals for a SMC sampling scheme.  For
+the SMC sampler, we use pixel wise distance as a surrogate for a
+likelihood function. The SMC sampler is designed to produce samples
+from the distribution $\propto L(I|\text{render}(T))
+\probability_\theta[T|I]$, where $L(\cdot | \cdot):\text{image}^2\to
+\mathcal{R}$ uses the distance between two images as a proxy for a
+likelihood.
+
+Figure~\ref{syntheticResults}
 compares the neural network with SMC against the neural network by
@@
 
-Given the DSL and a trace $T$, we want a program that evaluates to $T$
-and also minimizes some measure of program cost:
+Given the DSL and a trace $T$, we want to recover a program that both evaluates to $T$
+and, at the same time, is the ``best'' explanation of $T$.
+For example, we might prefer more general programs or, in the spirit of Occam's razor,
+prefer shorter programs.
+We wrap these intuitions up into a cost function over programs,
+and seek the minimum cost program consistent with $T$:
 \begin{equation}
@@
 \end{equation}
-An intuitive measure of program cost is its length.  We define the
+We define the
 cost of a program to be the number of statements it contains, where a
 statement is a ``Command'' in Table~\ref{DSL}.
-\remark{The flow here is a bit off/backwards.
+%\remark{The flow here is a bit off/backwards.
 ``We want a program that evaluates to $T$ and also minimizes some measure of program cost''---why do we care about cost?
@@
 function.  It translates the synthesis problem into a constraint
-satisfaction problem, and then uses a quasiboolean solver to find a
+satisfaction problem, and then uses a SAT solver to find a
 minimum cost program satisfying the specification.  In exchange for
@@
 if the execution trace already suffices to recover the objects in an image?
-Within our domain of hand-drawn figures, graphics program synthesis has several important uses:
+Within our domain of hand-drawn figures, graphics program synthesis has several uses:
 \subsection{Extrapolating figures}
@@
 by increasing the number of times that loops are executed.
-\input{extrapolations.tex}
+%\input{extrapolations.tex}
 
@@
 
+\includegraphics[width = 8in]{figures/similarity.png}
+
 \subsection{Correcting errors made by the neural network}
+The program synthesizer can help correct errors from  the neural network by favoring execution traces which lead to more concise or general programs.
+For example, one generally prefers figures with neatly aligned objects over figures whose parts are slightly misaligned -- and nice alignment lends itself to short programs.
+Similarly, figures often have repeated parts,
+which the program synthesizer might model as a reflection.
+So, if one is considering several candidate traces proposed by the neural network,
+we might prefer traces whose best programs have desirable features like being short or having iterated structures.
+
+Concretely we implemented the following scheme: the neurally guided sampling scheme of section~\ref{neuralNetworkSection} for image $I$ produces (samples) candidate traces, $\mathcal{F}(I)$.
+Instead of predicting the most likely trace in $\mathcal{F}(I)$ according to the neural network,
+we can take into account the programs that best explain the traces. 
+Writing $\hat{T}(I)$ for the trace the model predicts for image $I$,
+\begin{equation}
+\hat{T}(I) = \argmax_{T\in \mathcal{F}(I)} L(I | \text{render}(T)) \times\probability_{\theta_p} [ \text{program}(T)] 
+\end{equation}
+where $\probability_{\theta_p} [\cdot]$ is a prior probability
+distribution over programs parameterized by $\theta_p$.
+This is equivalent to doing
+MAP inference in a generative model where the program is first drawn
+from $\probability_{\theta_p} [\cdot]$, then the program is executed deterministically,
+and then we observe a noisy version of the program's output, where $L$
+is the noise model.
+
+Given a corpus of graphics program synthesis problems with annotated ground truth traces (so pairs of $(I,T)$),
+we find a maximum likelihood estimate of $\theta_p$:
+\begin{equation}
+  \theta_p^* = \argmax_{\theta_p} \expect \left[ \log \frac{\probability_{\theta_p} [\text{program}(T)]\times L(I|\text{render}(T))}{\sum_{T'\in \mathcal{F}(I)} \probability_{\theta_p} [\text{program}(T')]\times L(I|\text{render}(T'))} \right]
+\end{equation}
+where the expectation is taken both over the model predictions and the
+$(I,T)$ pairs in the training corpus.  We define $\probability_{\theta_p}
+[\cdot]$ to be a log linear distribution $\propto \exp
+(\theta\cdot \phi(\text{program}))$, where $\phi(\cdot)$ is a feature
+extractor for programs.  We can extract a few basic features of a
+program, like its size or how many loops it has, and use these
+features to help predict whether a trace is the correct explanation
+for an image.
 
@@
 
-Let $L(\cdot | \cdot):\text{image}^2\to \mathcal{R}$ be our likelihood
-function: it takes two images, an observed target image and a
-hypothesized program output, and gives the likelihood of the observed
-image conditioned on the program output.
-Write $\hat{T}(I)$ for the trace the model predicts for image $I$.
-
-We can extract a few basic features of a program, like its size or how many
-loops it has,
-and use these features to help predict
-whether a trace is the correct explanation for an image.
-\begin{equation}
-\hat{T}(I) = \argmax_{T} L(I | \text{render}(T)) + \theta\cdot  \phi \left( \text{program}(T) \right)
-\end{equation}
-where $\phi (\cdot)$ is a feature extractor for programs.
-This is equivalent to doing MAP inference in a generative model where the program
-is first drawn from a log linear distribution $\propto \exp (\theta\cdot \phi (\text{program}))$,
-than the program is executed deterministically,
-and then we observe a noisy version of the program's output,
-where $L$ is the noise model.
-
   \pagebreak
@@
   \section{Preliminary Synthesis results} 
-\input{synthesizerOutputs.tex}
+%\input{synthesizerOutputs.tex}
 

### 2017-05-17 paper.tex
description of learned distance metric

@@
  machine learning papers (see Fig.\ref{firstPageExamples}).
- \remark{The use of `graphics programs / visual programs' in the paper
-   title, title of this section, and the body of this section feels
-   too broad. `Graphics program' could conjur a lot of different ideas
-   (esp. 3D graphics); don't want to set the reader up to expect one
-   thing and then be disappointed that what you've done isn't
-   that. You bring up diagram-drawing later in the intro; I think it
-   should be made clear sooner (and certainly mentioned explicitly in
-   the abstract, when you get around to writing that).}
+ %% \remark{The use of `graphics programs / visual programs' in the paper
+ %%   title, title of this section, and the body of this section feels
+ %%   too broad. `Graphics program' could conjur a lot of different ideas
+ %%   (esp. 3D graphics); don't want to set the reader up to expect one
+ %%   thing and then be disappointed that what you've done isn't
+ %%   that. You bring up diagram-drawing later in the intro; I think it
+ %%   should be made clear sooner (and certainly mentioned explicitly in
+ %%   the abstract, when you get around to writing that).}
 
@@
 
-\remark{I like that you make this connection, but it could be made more precisely.
+%% \remark{I like that you make this connection, but it could be made more precisely.
 Specifically, (1) the architecture isn't \emph{really} recurrent (it uses no hidden state cells), so it'd be good to use a different term or drop this part of the point: (2) training of recurrent nets is also typically fully-supervised (Most RNNs lack latent variables per timestep)---if you're thinking about AIR specifically, maybe just say that, and (3) it's like an autogressive AIR \emph{without attention}.}
-\remark{Something related to this that's also cool to point out: training this model doesn't require backpropagation across the entire sequence of drawing commands (drawing to the canvas `blocks' the gradients, effectively offloading memory to an external (visual) store, so in principle it might be scalable to much longer sequences.}
+%% \remark{Something related to this that's also cool to point out: training this model doesn't require backpropagation across the entire sequence of drawing commands (drawing to the canvas `blocks' the gradients, effectively offloading memory to an external (visual) store, so in principle it might be scalable to much longer sequences.}
 
@@
 \texttt{Typewriter font}: network outputs.
-Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}.~\remark{Thoughts on improving this figure: (1) Convnet diagrams typically show the sequence of layers, if possible (space might not permit it here, but those thin arrows just aren't doing it for me).
-(2) Are the target image / canvas convolved down independently, or jointly (i.e.
-starting as a 2-channel image)?
-That's an important detail that's not clear with the current figure/explanation.
-(3) The three circles downstream from `Image Features' are supposed to be MLPs, I assume(?), but it took me a little while to parse that.
-Having some visual way of clearly separating network operations from data (color, perhaps) would go a long way.}}  \label{architecture}
+Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}.~\remark{Thoughts on improving this figure: (1) Convnet diagrams typically show the sequence of layers, if possible (space might not permit it here, but those thin arrows just aren't doing it for me).}}  \label{architecture}
 \end{figure}
@@
 \subsection{Generalizing to hand drawings}
-We believe that converting synthetic, noiseless images into a restricted subset of
-\LaTeX has limited usefulness.  A more practical
-application is one that extends to hand drawings.  We train the model
+A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
+ We train the model
 to generalize to hand drawings by introducing noise into the
@@
 We designed this noise process to introduce the kinds of variations found in hand drawings (figure~\ref{handDrawingExamples}).
+Our neurally-guided SMC procedure
+used pixel-wise distance as a surrogate for a likelihood function ($L(\cdot|\cdot)$ in section~\ref{neuralNetworkSection}).
+But pixel-wise distance fares poorly on hand drawings, which never exactly match
+the model's renders.
+So, for hand drawings,
+we \emph{learned} a surrogate likelihood function.
+Our learned $L(\cdot|\cdot)$
+is a convolutional network that we train to predict
+the distance between two traces conditioned upon their renderings.
+Formally we train our likelihood surrogate to approximate:
+\begin{equation}
+  L(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|
+  \end{equation}
+
 We drew 100 figures by hand; see figure~\ref{lotsOfHandDrawings}.
@@
 
+Similarity metric in program space:\\
 \includegraphics[width = 8in]{figures/similarity.png}
+
+Similarity metric in image space:\\
+\includegraphics[width = 8in]{figures/imageSimilarity.png}
 
@@
 \begin{equation}
-\hat{T}(I) = \argmax_{T\in \mathcal{F}(I)} L(I | \text{render}(T)) \times\probability_{\theta_p} [ \text{program}(T)] 
+\hat{T}(I) = \argmax_{T\in \mathcal{F}(I)} L(I | \text{render}(T)) \times\probability_{\beta} [ \text{program}(T)] 
 \end{equation}
-where $\probability_{\theta_p} [\cdot]$ is a prior probability
-distribution over programs parameterized by $\theta_p$.
+where $\probability_{\beta} [\cdot]$ is a prior probability
+distribution over programs parameterized by $\beta$.
 This is equivalent to doing
 MAP inference in a generative model where the program is first drawn
-from $\probability_{\theta_p} [\cdot]$, then the program is executed deterministically,
+from $\probability_{\beta} [\cdot]$, then the program is executed deterministically,
 and then we observe a noisy version of the program's output, where $L$
@@
 Given a corpus of graphics program synthesis problems with annotated ground truth traces (so pairs of $(I,T)$),
-we find a maximum likelihood estimate of $\theta_p$:
+we find a maximum likelihood estimate of $\beta$:
 \begin{equation}
-  \theta_p^* = \argmax_{\theta_p} \expect \left[ \log \frac{\probability_{\theta_p} [\text{program}(T)]\times L(I|\text{render}(T))}{\sum_{T'\in \mathcal{F}(I)} \probability_{\theta_p} [\text{program}(T')]\times L(I|\text{render}(T'))} \right]
+  \beta^* = \argmax_{\beta} \expect \left[ \log \frac{\probability_{\beta} [\text{program}(T)]\times L(I|\text{render}(T))}{\sum_{T'\in \mathcal{F}(I)} \probability_{\beta} [\text{program}(T')]\times L(I|\text{render}(T'))} \right]
 \end{equation}
 where the expectation is taken both over the model predictions and the
-$(I,T)$ pairs in the training corpus.  We define $\probability_{\theta_p}
+$(I,T)$ pairs in the training corpus.  We define $\probability_{\beta}
 [\cdot]$ to be a log linear distribution $\propto \exp
-(\theta\cdot \phi(\text{program}))$, where $\phi(\cdot)$ is a feature
+(\beta\cdot \phi(\text{program}))$, where $\phi(\cdot)$ is a feature
 extractor for programs.  We can extract a few basic features of a

### 2017-05-17 paper.tex
added figures
better figures for synthetic results

@@
 training data.
-\begin{wrapfigure}{R}{0.5\textwidth}
-  \begin{center}
+
+\begin{figure}\centering
+  \begin{minipage}{0.35\textwidth}
     \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-58-7.png}}\end{minipage}
     \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-33-5.png}}\end{minipage}
-    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-25-4.png}}\end{minipage}
-%    \begin{minipage}[t]{2cm}\includegraphics[width=2cm]{figures/randomScene-26-7.png}\end{minipage}
-%    \begin{minipage}[t]{2cm}\includegraphics[width=2cm]{figures/randomScene-19-3.png}\end{minipage}
-  \end{center}
-  \caption{Network is trained to infer execution traces for figures like the three shown above.}\label{trainingData}
-\end{wrapfigure}
-
-\begin{figure}
-  \begin{minipage}[t]{15cm}
-    \includegraphics[width = 15cm]{figures/editDistance.png}
-  \end{minipage}\\
-  \begin{minipage}[t]{15cm}
-    \includegraphics[width = 15cm]{figures/accuracy.png}
-  \end{minipage}\\
-  \begin{minipage}[t]{15cm}
-    \includegraphics[width = 15cm]{figures/time.png}
-  \end{minipage}
+    \caption{Network is trained to infer execution traces for randomly generated figures like the two shown above.}\label{trainingData}
+  \end{minipage}\hfill
+  \begin{minipage}{0.6\textwidth}
+    \includegraphics[width = 4cm]{figures/editDistance.png}
+    \includegraphics[width = 4cm]{figures/accuracy.png}
       \caption{Using the model to parse latex output.
@@
 Neither the stochastic search nor the neural network are sufficient on their own.}\label{syntheticResults}
+    \end{minipage}
+
   \end{figure}
@@
 \begin{equation}
-  L(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|
+-\log L(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|
   \end{equation}
@@
 by increasing the number of times that loops are executed.
+
+\includegraphics[width = 8in]{figures/extrapolationMatrix.png}
 %\input{extrapolations.tex}

### 2017-05-17 paper.tex
abstract

@@
 \begin{abstract}
+  We introduce a model that learns to convert simple hand drawings
+  into graphics programs written in a subset of \LaTeX.~The model
+  combines techniques from deep learning and program synthesis.  We
+  learn a neural network that proposes plausible drawing primitives
+  that explain an image.  From these deep net proposals we can use
+  program synthesis techniques to recover a graphics
+  program with constructs like variable bindings, iterative loops, or
+  simple kinds of conditionals. With a graphics program in hand,
+  we can extrapolate figures, form visual analogies, \remark{what else should go here?}, and correct errors made by the deep network.
+  Taken together these results are a step towards
+  agents that induce programs from perceptual input.  
 \end{abstract}
@@
 
-  \draw[-{>[scale = 1.5]},very thick,dashed] (next.west) -- ([yshift = -0.2cm]canvas.east) node [midway, below, sloped] (TextNode) {Renderer: \LaTeX};
+  \draw[-{>[scale = 1.5]},very thick,dashed] (next.west) -- ([yshift = -0.2cm]canvas.east) node [midway, below, sloped] (TextNode) {Renderer: \LaTeX~Ti\emph{k}Z};
 
@@
   \begin{tabular}{l}
-    \verb|LINE|$(x_1,y_1,x_2,y_2,$\\
+    \verb|line|$(x_1,y_1,x_2,y_2,$\\
     \hspace{1cm}$\text{arrow}\in\{0,1\},\text{dashed}\in\{0,1\})$
@@
 As shown above it generalizes to scenes with many more objects.
-Neither the stochastic search nor the neural network are sufficient on their own.}\label{syntheticResults}
+Neither the stochastic search nor the neural network are sufficient on their own.
+\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}
     \end{minipage}
@@
 \begin{table}[H]
-  \begin{tabular}{rl}
+  \begin{tabular}{rl}\toprule
   Program$\to$&Command; $\cdots$; Command\\
@@
   Command$\to$&\texttt{rectangle}(Expression,Expression,Expression,Expression)\\
-  Command$\to$&\texttt{LINE}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
-  Command$\to$&\texttt{for}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ }Program\texttt{ \}}\\
-  Command$\to$&\texttt{REFLECT}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
+  Command$\to$&\texttt{line}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
+  Command$\to$&\texttt{for}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ if }$(\text{Var} > 0)$\texttt{ \{ }Program\texttt{ \}; }Program\texttt{ \}}\\
+  Command$\to$&\texttt{reflect}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
   Expression$\to$&\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}\\
@@
   Axis$\to$&\texttt{X = }\mathcal{Z}\\
-  Axis$\to$&\texttt{Y = }\mathcal{Z}
+  Axis$\to$&\texttt{Y = }\mathcal{Z}\\\bottomrule
   \end{tabular}
   \caption{Grammar over graphics programs.
-We allow loops (\texttt{for}), vertical/horizontal reflections (\texttt{REFLECT}), and affine transformations (\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}).}\label{DSL}
+We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertical/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations (\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}).}\label{DSL}
 \end{table}
@@
 statement is a ``Command'' in Table~\ref{DSL}.
+We also penalize using more distant constants,
+which encourages reuse of coefficients.
 %\remark{The flow here is a bit off/backwards.
@@
 
-  \pagebreak
-  \section{Preliminary extrapolation results}
-
-\pagebreak
-  \section{Preliminary Synthesis results} 
 %\input{synthesizerOutputs.tex}

### 2017-05-17 paper.tex
description of the performance of the parser

@@
 \end{figure}
+For each drawing we annotated a ground truth trace, and evaluated the
+model by asking it to sample many candidate traces for each drawing.
+For 55\% of the drawings the Top-1 most likely sample matches the
+ground truth; as we consider more samples the model encounters traces
+that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
+\begin{figure}
+  \includegraphics[width = 5cm]{figures/drawingAccuracy.png}
+  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1, 5, 10, 100 samples)?
+  Distance to the ground truth trace is measured by the intersection over union of predicted vs. ground truth traces (sets of drawing commands).}\label{drawingIntersectionOverUnion}
+\end{figure}
+Because our current model sometimes makes mistakes on hand drawings,
+we envision the current system working as follows:
+a user sketches a diagram,
+and the system responds by proposing a few candidate interpretations.
+The user could then select the one closest to their intention and edit it if necessary.
 

### 2017-05-17 paper.tex
more writing and rearrangement of figures

@@
 we made the drawings on graph paper.
-\begin{figure}[H]%
-  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
+\begin{figure}\centering
+  \begin{minipage}{0.45\textwidth}
+  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/expert-60-reduced.png}
     \subcaption{}
   \end{minipage}%
-   \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
+   \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/60-groundTruth-reduced.png}
     \subcaption{}
   \end{minipage}%
-  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
+  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/60-1-reduced.png}
     \subcaption{}
   \end{minipage}%
-  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-2-reduced.png} 
-    \subcaption{}
+    \caption{(a): a hand drawing.
+(b): Rendering of the trace our model infers for (a).
+We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) for a noisy rendering of (b).}\ref{handDrawingExamples}
+  \end{minipage}\hfill
+  \begin{minipage}{0.45\textwidth}
+  \includegraphics[width = 6cm]{figures/drawingAccuracy.png}
+  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1, 5, 10, 100 samples)?
+  Distance to the ground truth trace is measured by the intersection over union of predicted vs. ground truth traces (sets of drawing commands).}\label{drawingIntersectionOverUnion}
     \end{minipage}
-  \caption{(a): a hand drawing.
-(b): Rendering of the parse our model infers for (a).
-We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) \& (d) for noisy renderings of (b).}\ref{handDrawingExamples}
 \end{figure}
@@
 model by asking it to sample many candidate traces for each drawing.
-For 55\% of the drawings the Top-1 most likely sample matches the
+For 55\% of the drawings the Top-1 most likely sample exactly matches the
 ground truth; as we consider more samples the model encounters traces
 that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
-\begin{figure}
-  \includegraphics[width = 5cm]{figures/drawingAccuracy.png}
-  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1, 5, 10, 100 samples)?
-  Distance to the ground truth trace is measured by the intersection over union of predicted vs. ground truth traces (sets of drawing commands).}\label{drawingIntersectionOverUnion}
-\end{figure}
 Because our current model sometimes makes mistakes on hand drawings,
@@
 by increasing the number of times that loops are executed.
+Extrapolating repetitive visuals patterns comes naturally to humans,
+and building this ability into an application is practical:
+imagine hand drawing a repetitive graphical model structure
+and having the model automatically induce and extend the pattern.
+Fig.~\ref{extrapolationFigure} shows extrapolations of programs synthesized from ground truth traces;
+see supplement for our full set of extrapolations.
 
+\begin{figure}
   \includegraphics[width = 8in]{figures/extrapolationMatrix.png}
+  \caption{Left: hand drawings. Right: extrapolations produced by
+    running different parts of different loops either forward or
+    backward an extra iteration.}\label{extrapolationFigure}
+  \end{figure}
 %\input{extrapolations.tex}

### 2017-05-17 paper.tex
Title change, comments, edits.

--- 2017-05-17 paper.tex
@@
 
-\title{Inferring Graphics Programs from Images}
+% \title{Inferring Graphics Programs from Images}
+\title{Learning to Infer Graphics Programs from Hand-Drawn Images}
 
@@
   combines techniques from deep learning and program synthesis.  We
-  learn a neural network that proposes plausible drawing primitives
+  learn a convolutional neural network that proposes plausible drawing primitives
   that explain an image.  From these deep net proposals we can use
@@
   program with constructs like variable bindings, iterative loops, or
-  simple kinds of conditionals. With a graphics program in hand,
-  we can extrapolate figures, form visual analogies, \remark{what else should go here?}, and correct errors made by the deep network.
+  simple kinds of conditionals.~\remark{Can you (concisely) communicate the idea of treating the deep net proposal as an `execution trace?' It's a really neat intellectual framing that deserves to be foregrounded.} With a graphics program in hand,
+  we can correct errors made by the deep network, extrapolate drawings, and~\remark{what else: `visual analogies' is vague. `Cluster drawings by use of similar high-level program structures?'}
   Taken together these results are a step towards
-  agents that induce programs from perceptual input.  
+  agents that induce useful, human-readable programs from perceptual input.  
 \end{abstract}
@@
 
- How could an agent go from noisy, high-dimensional perceptual input
- to a symbolic, abstract object, like a computer program?  Here we
+ How can an agent convert noisy, high-dimensional perceptual input
+ to a symbolic, abstract object, such as a computer program?  Here we
  consider this problem within a graphics program synthesis domain.  We
@@
  The graphics programs in our domain draw simple figures like those found in
- machine learning papers (see Fig.\ref{firstPageExamples}).
+ machine learning papers (see Figure~\ref{firstPageExamples}).
  %% \remark{The use of `graphics programs / visual programs' in the paper
@@
   \end{minipage}
-  \caption{(a): Model learns to convert hand drawings (top) into \LaTeX~(bottom). (b) Synthesizes high-level \emph{graphics program} from hand drawing.}\label{firstPageExamples}
+  \caption{(a): Model learns to convert hand drawings (top) into \LaTeX~(bottom).
+(b) Synthesizes high-level \emph{graphics program} from hand drawing.~\remark{Any objection to putting this on page bottom?}}\label{firstPageExamples}
   \end{figure}
@@
 High dimensional perceptual input may seem ill matched to the abstract
-semantics of a programming language. But programs with constructs like
+semantics of a programming language. But programs with constructs such as
 recursion or iteration produce a simpler \emph{execution trace} of
-primitive actions; for our domain the primitive actions are drawing
+primitive actions; for our domain, the primitive actions are drawing
 commands. Our hypothesis is that the execution trace of the program is
@@
 work by modeling a set of possible programs inside of a constraint solver,
-like a SAT or SMT solver~\cite{de2008z3}.
+such as a SAT or SMT solver~\cite{de2008z3}.
 These techniques excel at uncovering high-level symbolic structure,
@@
 robustness, we use the deep network as a proposal distribution for a
-stochastic search over execution traces.  Finally, we use techniques
-in the program synthesis community to recover the program from its
-trace.  The program synthesizer discovers constructs like loops and
-geometric operations like reflections and affine transformations.
-\remark{This paragraph is all about making things a bit more specific,
-  so you really need more specifics about program synth here.}
+stochastic search over execution traces.  Finally, we use program synthesis to recover the program from its
+trace.  The program synthesizer discovers constructs such as loops and
+geometric operations such as reflections and affine transformations.
+% \remark{This paragraph is all about making things a bit more specific,
+%   so you really need more specifics about program synth here.}
 
@@
 the deep network, we get a fast system that can recover plausible
-execution traces in about a minute~\remark{A minute seems slow to me, for deep net inference. Are you talking about training time, here, or...?}. From the stochastic search we get
-added robustness; essentially, the stochastic search can correct
+execution traces in about a minute~\remark{A minute seems slow to me, for deep net inference...}. From the stochastic search, we get
+added robustness: essentially, the stochastic search can correct
 mistakes made by the deep network's proposals.  From the program
@@
 downstream tasks and can help correct some mistakes of the earlier stages.
-\remark{I wonder if this would work even better as a bulleted list...}
+% \remark{I wonder if this would work even better as a bulleted list...}
+\remark{Tie these claims into the paper results: state what the `downstream' tasks are that you actually do, and refer to the sections where they occur}
 
@@
 Both systems focus on inferring fixed-dimensional parameter vectors.
-In contrast, we seek to automatically learn a structured, programmatic representation of a sketch which captures higher-level visual patterns.
+In contrast, we seek to automatically infer a structured, programmatic representation of a sketch which captures higher-level visual patterns.
 
@@
 pass a $256\times 256$ target image and a rendering of the trace so
-far to a convolutional network -- these two inputs are represented as
-separate channels for the convnet. Given the features extracted by the
+far (encoded as a two-channel image) to a convolutional network. Given the features extracted by the
 convnet, a multilayer perceptron then predicts a distribution over the
 next drawing command to add to the trace.  We predict the drawing
-command token-by-token, and condition each token both on the image
+command token-by-token, conditioning each token both on the image
 features and on the previously generated tokens.  For example, the
@@
 \remark{There are some more details that are important to provide
-  about this architecture, though possibly in an Appendix: the
+  about this architecture in the supplement: the
   functional form(s) of the probability distributions over tokens, the
@@
 
-The distribution over the next drawing command factorizes:
+The distribution over the next drawing command factorizes as:
 \begin{equation}
@@
 token is emitted by the network to signal that the execution trace
-explains the image.
+explains the image.~\remark{Make explicit that a $T_n$ in Equation 2 is a concise way of referring to a sequence of tokens from Equation 1?}
 
 We train the network by sampling execution traces $T$ and target
-images $I$ for randomly generated scenes, and maximizing
-(\ref{objective}) wrt $\theta$ by gradient ascent.
+images $I$ for randomly generated scenes~\remark{this process ought to be explained, perhaps in supplement if it is at all detailed}, and maximizing
+(\ref{objective}) with respect to $\theta$ by gradient ascent.
 Training does not require backpropagation across the entire sequence of drawing commands:
@@
 In a sense, this model is like an autoregressive variant of AIR~\cite{eslami1603attend} without attention.
+~\remark{Somewhere (not necessarily here) you should probably cite the deep learning toolkit you used.}
 
@@
 
-This network suffices to ``derender'' images like those shown in
+This network suffices to ``derender'' synthetic images like those shown in
 Figure~\ref{trainingData}.  We can perform a beam search decoding to
@@
 mistake.  For added robustness as $n$ becomes large, we treat the
-neural network outputs as proposals for a SMC sampling scheme.  For
-the SMC sampler, we use pixel wise distance as a surrogate for a
+neural network outputs as proposals for a Sequential Monte Carlo (SMC) sampling scheme~\cite{SMCBook}.  For
+the SMC sampler, we use pixel-wise distance as a surrogate for a
 likelihood function. The SMC sampler is designed to produce samples
@@
 renderings of the training target images.
-We designed this noise process to introduce the kinds of variations found in hand drawings (figure~\ref{handDrawingExamples}).
+We designed this noise process to introduce the kinds of variations found in hand drawings (Figure~\ref{handDrawingExamples}).~\remark{Process should be described (in supplement)}
 Our neurally-guided SMC procedure
@@
 So, for hand drawings,
-we \emph{learned} a surrogate likelihood function.
+we \emph{learn} a surrogate likelihood function.
 Our learned $L(\cdot|\cdot)$
 is a convolutional network that we train to predict
-the distance between two traces conditioned upon their renderings.
+the distance between two traces conditioned upon their renderings~\remark{The two $L$'s should have some kind of identifier e.g. a subscript to distinguish them}.
 Formally we train our likelihood surrogate to approximate:
@@
 
+\remark{What distance metric is this? Some kind of edit distance?}
 We drew 100 figures by hand; see figure~\ref{lotsOfHandDrawings}.
@@
 (b): Rendering of the parse our model infers for (a).
-We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) \& (d) for noisy renderings of (b).}\ref{handDrawingExamples}
+We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) \& (d) for noisy renderings of (b).}\ref{handDrawingExamples}~\remark{This figure is never referenced?
+Is the ref here supposed to be a label?}
 \end{figure}
@@
     \end{minipage}
-  \caption{Example drawings above model outputs. See also Fig.~\ref{firstPageExamples}}\label{handDrawingExamples}
+  \caption{Example drawings above model outputs.
+See also Figure~\ref{firstPageExamples}}\label{handDrawingExamples}\remark{Showing `failure cases' (the last three above) out-of-context seems not great.
+Perhaps remind people in the caption that stochastic search can help correct some of these issues?}
   \end{figure}
@@
 of a scene, it fails to encode higher-level features of the image,
-such as repeated motifs, symmetries or reflections.  A \emph{graphics
+such as repeated motifs or symmetries.  A \emph{graphics
   program} better describe structures like these,
@@
 free grammar over a space of programs. Although it might be desirable
-to synthesize programs in a Turing-complete language like Lisp or
+to synthesize programs in a Turing-complete language such as Lisp or
 Python, a more tractable approach is to specify what in the program
-languages community is called a Domain Specific Language (DSL). Our DSL (Table~\ref{DSL})
+languages community is called a Domain Specific Language (DSL)~\remark{citation?}. Our DSL (Table~\ref{DSL})
 encodes prior knowledge of what graphics programs tend to look like.
@@
 statement is a ``Command'' in Table~\ref{DSL}.
-We also penalize using more distant constants,
-which encourages reuse of coefficients.
+We also penalize using more distant constants~\remark{awkward},
+which encourages reuse of coefficients.~\remark{More detail on this in supplement}
 %\remark{The flow here is a bit off/backwards.
@@
 Within our domain of hand-drawn figures, graphics program synthesis has several uses:
+\remark{I'm of two minds about how these subsections should be ordered.
+The current ordering leads with the coolest results, which is nice.
+But it's a bit...deflating?...to start with such cool results and then end on the somewhat technical point of how the synthesizer can help correct parse errors.
+An alternative would be to flip the ordering, starting with the technical point and building toward progressively cooler results.
+This requires a bit more patience on the part of the reader, but the overall narrative flow/payoff feels better.
+In any case, whatever ordering you pick should be the same order as these applications are mentioned in the abstract.}
+
 \subsection{Extrapolating figures}
@@
 For example,
-we can change all of the circles to squares,
-were make all of the lines be dashed.
+we can change all of the circles to squares or make all of the lines be dashed.
 We can also \textbf{extrapolate} figures
-by increasing the number of times that loops are executed.
+by increasing the number of times that loops are executed.~\remark{Pick a few of these to show off and put the rest in supplement}
 
@@
 
-\subsection{Correcting errors made by the neural network}
-The program synthesizer can help correct errors from  the neural network by favoring execution traces which lead to more concise or general programs.
-For example, one generally prefers figures with neatly aligned objects over figures whose parts are slightly misaligned -- and nice alignment lends itself to short programs.
+\subsection{Correcting errors made by the parsing network}
+The program synthesizer can help correct errors from the parse proposal network by favoring execution traces which lead to more concise or general programs.
+For example, one generally prefers figures with perfectly aligned objects over figures whose parts are slightly misaligned -- and precise alignment lends itself to short programs.
 Similarly, figures often have repeated parts,
-which the program synthesizer might model as a reflection.
-So, if one is considering several candidate traces proposed by the neural network,
-we might prefer traces whose best programs have desirable features like being short or having iterated structures.
+which the program synthesizer might be able to model as a loop or reflectional symmetry.
+So, in considering several candidate traces proposed by the neural network,
+we might prefer traces whose best programs have desirable features such being short or having iterated structures.
 
-Concretely we implemented the following scheme: the neurally guided sampling scheme of section~\ref{neuralNetworkSection} for image $I$ produces (samples) candidate traces, $\mathcal{F}(I)$.
+Concretely, we implemented the following scheme: the neurally guided sampling scheme of section~\ref{neuralNetworkSection} for image $I$ samples candidate traces $\mathcal{F}(I)$.
 Instead of predicting the most likely trace in $\mathcal{F}(I)$ according to the neural network,
@@
 
-Given a corpus of graphics program synthesis problems with annotated ground truth traces (so pairs of $(I,T)$),
+Given a corpus of graphics program synthesis problems with annotated ground truth traces (i.e. $(I,T)$ pairs),
 we find a maximum likelihood estimate of $\beta$:
@@
 (\beta\cdot \phi(\text{program}))$, where $\phi(\cdot)$ is a feature
-extractor for programs.  We can extract a few basic features of a
-program, like its size or how many loops it has, and use these
+extractor for programs.  We extract a few basic features of a
+program, such as its size and how many loops it has, and use these
 features to help predict whether a trace is the correct explanation
@@
 
-\remark{Seems like you're still fleshing this part out, but I'll give my feedback anyway: (1) This subsection could really use a motivational introduction, e.g.
+% \remark{Seems like you're still fleshing this part out, but I'll give my feedback anyway: (1) This subsection could really use a motivational introduction, e.g.
 ``The program synthesizer can help correct errors/bad proposals from the neural network by favoring execution traces which lead to more concise/general programs.'' (2) The image likelihood function should probably be introduced sooner, when you talk about SMC/beam search.

### 2017-05-17 paper.tex

@@
 we made the drawings on graph paper.
-\begin{figure}[H]%
-  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
+\begin{figure}\centering
+  \begin{minipage}{0.45\textwidth}
+  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/expert-60-reduced.png}
     \subcaption{}
   \end{minipage}%
-   \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
+   \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/60-groundTruth-reduced.png}
     \subcaption{}
   \end{minipage}%
-  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
+  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/60-1-reduced.png}
     \subcaption{}
   \end{minipage}%
-  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-2-reduced.png} 
-    \subcaption{}
+    \caption{(a): a hand drawing.
+(b): Rendering of the trace our model infers for (a).
+We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) for a noisy rendering of (b).}\ref{handDrawingExamples}
+  \end{minipage}\hfill
+  \begin{minipage}{0.45\textwidth}
+  \includegraphics[width = 6cm]{figures/drawingAccuracy.png}
+  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1, 5, 10, 100 samples)?
+  Distance to the ground truth trace is measured by the intersection over union of predicted vs. ground truth traces (sets of drawing commands).}\label{drawingIntersectionOverUnion}
     \end{minipage}
-  \caption{(a): a hand drawing.
-(b): Rendering of the parse our model infers for (a).
-We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) \& (d) for noisy renderings of (b).}\ref{handDrawingExamples}~\remark{This figure is never referenced?
-Is the ref here supposed to be a label?}
 \end{figure}
@@
   \caption{Example drawings above model outputs.
-See also Figure~\ref{firstPageExamples}}\label{handDrawingExamples}\remark{Showing `failure cases' (the last three above) out-of-context seems not great.
+See also Fig.~\ref{firstPageExamples}}\label{handDrawingExamples}~\remark{Showing `failure cases' (the last three above) out-of-context seems not great.
 Perhaps remind people in the caption that stochastic search can help correct some of these issues?}
 \end{figure}
+For each drawing we annotated a ground truth trace, and evaluated the
+model by asking it to sample many candidate traces for each drawing.
+For 55\% of the drawings the Top-1 most likely sample exactly matches the
+ground truth; as we consider more samples the model encounters traces
+that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
+Because our current model sometimes makes mistakes on hand drawings,
+we envision the current system working as follows:
+a user sketches a diagram,
+and the system responds by proposing a few candidate interpretations.
+The user could then select the one closest to their intention and edit it if necessary.
 
@@
 We can also \textbf{extrapolate} figures
-by increasing the number of times that loops are executed.~\remark{Pick a few of these to show off and put the rest in supplement}
+by increasing the number of times that loops are executed.~\remark{Pick a few of these to show off and put the rest in supplement?}
+Extrapolating repetitive visuals patterns comes naturally to humans,
+and building this ability into an application is practical:
+imagine hand drawing a repetitive graphical model structure
+and having the model automatically induce and extend the pattern.
+Fig.~\ref{extrapolationFigure} shows extrapolations of programs synthesized from ground truth traces;
+see supplement for our full set of extrapolations.
 
+\begin{figure}
   \includegraphics[width = 8in]{figures/extrapolationMatrix.png}
+  \caption{Left: hand drawings. Right: extrapolations produced by
+    running different parts of different loops either forward or
+    backward an extra iteration.}\label{extrapolationFigure}
+  \end{figure}
 %\input{extrapolations.tex}

### 2017-05-17 paper.tex
related work
fixes based on Dan's comments

@@
   learn a convolutional neural network that proposes plausible drawing primitives
-  that explain an image.  From these deep net proposals we can use
+  that explain an image. This set of drawing primitives is like an execution trace for a graphics program. From this trace we use
   program synthesis techniques to recover a graphics
   program with constructs like variable bindings, iterative loops, or
-  simple kinds of conditionals.~\remark{Can you (concisely) communicate the idea of treating the deep net proposal as an `execution trace?' It's a really neat intellectual framing that deserves to be foregrounded.} With a graphics program in hand,
-  we can correct errors made by the deep network, extrapolate drawings, and~\remark{what else: `visual analogies' is vague. `Cluster drawings by use of similar high-level program structures?'}
+  simple kinds of conditionals. With a graphics program in hand,
+  we can correct errors made by the deep network, extrapolate drawings, and cluster drawings by use of similar high-level geometric structures.
   Taken together these results are a step towards
@@
   \caption{(a): Model learns to convert hand drawings (top) into \LaTeX~(bottom).
-(b) Synthesizes high-level \emph{graphics program} from hand drawing.~\remark{Any objection to putting this on page bottom?}}\label{firstPageExamples}
+(b) Synthesizes high-level \emph{graphics program} from hand drawing.~\remark{Kevin to Dan: how about this placement?}}\label{firstPageExamples}
   \end{figure}
@@
 \section{Related work}
+
+The CogSketch~\cite{forbus2011cogsketch} system also aims to have a high-level understanding of hand-drawn figures.
+Their primary goal is cognitive modeling, whereas we are interested in building an automated AI application.
+
+%% open domain sketch understanding.
+structure mapping style model.
+also taps into cyc?
+the user segments the ink and labels them with concepts from knowledge base.
+like us they focus on compositional understanding.
+``cognitive simulation", solves things like Raven matrices in IQ tests.
+not really trying right now to be automated like our system.
 
@@
 So, for hand drawings,
-we \emph{learn} a surrogate likelihood function.
-Our learned $L(\cdot|\cdot)$
-is a convolutional network that we train to predict
-the distance between two traces conditioned upon their renderings~\remark{The two $L$'s should have some kind of identifier e.g. a subscript to distinguish them}.
-Formally we train our likelihood surrogate to approximate:
+we \emph{learn} a surrogate likelihood function,
+$L_{\text{learned}}(\cdot|\cdot)$.
+The density $L_{\text{learned}}(\cdot|\cdot)$ is predicted by a convolutional network that we train to predict
+the distance between two traces conditioned upon their renderings.
+Completely we train our likelihood surrogate to approximate the symmetric difference:
 \begin{equation}
--\log L(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|
+-\log L_{\text{learned}}(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|
   \end{equation}
 
-\remark{What distance metric is this? Some kind of edit distance?}
 We drew 100 figures by hand; see figure~\ref{lotsOfHandDrawings}.
@@
 statement is a ``Command'' in Table~\ref{DSL}.
-We also penalize using more distant constants~\remark{awkward},
-which encourages reuse of coefficients.~\remark{More detail on this in supplement}
+We also penalize using more constants; see supplement.
 %\remark{The flow here is a bit off/backwards.
@@
 imagine hand drawing a repetitive graphical model structure
-and having the model automatically induce and extend the pattern.
+and having our system automatically induce and extend the pattern.
 Fig.~\ref{extrapolationFigure} shows extrapolations of programs synthesized from ground truth traces;
@@
 \begin{equation}
-\hat{T}(I) = \argmax_{T\in \mathcal{F}(I)} L(I | \text{render}(T)) \times\probability_{\beta} [ \text{program}(T)] 
+\hat{T}(I) = \argmax_{T\in \mathcal{F}(I)} L_{\text{learned}}(I | \text{render}(T)) \times\probability_{\beta} [ \text{program}(T)] 
 \end{equation}
@@
 \begin{equation}
-  \beta^* = \argmax_{\beta} \expect \left[ \log \frac{\probability_{\beta} [\text{program}(T)]\times L(I|\text{render}(T))}{\sum_{T'\in \mathcal{F}(I)} \probability_{\beta} [\text{program}(T')]\times L(I|\text{render}(T'))} \right]
+  \beta^* = \argmax_{\beta} \expect \left[ \log \frac{\probability_{\beta} [\text{program}(T)]\times L_{\text{learned}}(I|\text{render}(T))}{\sum_{T'\in \mathcal{F}(I)} \probability_{\beta} [\text{program}(T')]\times L_{\text{learned}}(I|\text{render}(T'))} \right]
 \end{equation}

### 2017-05-17 paper.tex
fixed canvas figure
Removing a couple of comments that have been sufficiently addressed; a couple minor tweaks.

@@
   \end{minipage}
-  \caption{(a): Model learns to convert hand drawings (top) into \LaTeX~(bottom).
-(b) Synthesizes high-level \emph{graphics program} from hand drawing.~\remark{Kevin to Dan: how about this placement?}}\label{firstPageExamples}
+  \caption{(a): Model learns to convert hand drawings (top) into \LaTeX~(bottom). (b) Synthesizes high-level \emph{graphics program} from hand drawing.}\label{firstPageExamples}
   \end{figure}
@@
 \texttt{Typewriter font}: network outputs.
-Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}.~\remark{Thoughts on improving this figure: (1) Convnet diagrams typically show the sequence of layers, if possible (space might not permit it here, but those thin arrows just aren't doing it for me).}}  \label{architecture}
+Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}.}  \label{architecture}
 \end{figure}
@@
 the distance between two traces conditioned upon their renderings.
-Completely we train our likelihood surrogate to approximate the symmetric difference:
+We train our likelihood surrogate to approximate the symmetric difference:
 \begin{equation}
@@
 statement is a ``Command'' in Table~\ref{DSL}.
-We also penalize using more constants; see supplement.
+We also penalize using many different numerical constants; see supplement.
 %\remark{The flow here is a bit off/backwards.

### 2017-05-17 paper.tex
more responses to comments

--- 2017-05-17 paper.tex
@@
 robustness, we use the deep network as a proposal distribution for a
-stochastic search over execution traces.  Finally, we use program synthesis to recover the program from its
+stochastic search over execution traces.
+Section~\ref{neuralNetworkSection} describes this first stage of the architecture where we infer drawing commands from images, and explains how we handle noisy hand drawings.
+Finally, we use program synthesis techniques to recover the program from its
 trace.  The program synthesizer discovers constructs such as loops and
 geometric operations such as reflections and affine transformations.
-% \remark{This paragraph is all about making things a bit more specific,
+% \remark{This paragraph is all about making things a bit more
+Section~\ref{programSynthesisSection} describes how the architecture
+synthesizes programs from execution traces,
+and how those programs are used for measuring similarity between hand drawings,
+extrapolating figures, and correcting errors made by the deep network.
+
 %   so you really need more specifics about program synth here.}
 
-Each of these three components -- the deep network, the stochastic
-search, the program synthesizer -- confers its own advantages. From
-the deep network, we get a fast system that can recover plausible
-execution traces in about a minute~\remark{A minute seems slow to me, for deep net inference...}. From the stochastic search, we get
-added robustness: essentially, the stochastic search can correct
-mistakes made by the deep network's proposals.  From the program
-synthesizer, we get abstraction: our system recovers coordinate
-transformations, for loops, and subroutines, which are useful for
-downstream tasks and can help correct some mistakes of the earlier stages.
-% \remark{I wonder if this would work even better as a bulleted list...}
-\remark{Tie these claims into the paper results: state what the `downstream' tasks are that you actually do, and refer to the sections where they occur}
+%% Each of these three components -- the deep network, the stochastic
+%% search, the program synthesizer -- confers its own advantages. From
+%% the deep network, we get a fast system that can recover plausible
+%% execution traces in about a minute~\remark{A minute seems slow to me, for deep net inference...}. From the stochastic search, we get
+%% added robustness: essentially, the stochastic search can correct
+%% mistakes made by the deep network's proposals.  From the program
+%% synthesizer, we get abstraction: our system recovers coordinate
+%% transformations, for loops, and subroutines, which are useful for
+%% downstream tasks and can help correct some mistakes of the earlier stages.
+%% % \remark{I wonder if this would work even better as a bulleted list...}
+%% \remark{Tie these claims into the paper results: state what the `downstream' tasks are that you actually do, and refer to the sections where they occur}
 
@@
   % draw partial image on canvas
-  \draw (0.5cm,-4cm) circle (0.1875cm);
-  \draw (1.2cm,-4.3) circle (0.1875cm);
-  \draw (0.85cm,-4.6) circle (0.1875cm);
+  \draw (0.375cm,-3.25cm) circle (0.125cm);
+  \draw (0.625cm,-3.625) circle (0.125cm);
+  \draw (0.75cm,-3.375) circle (0.125cm);
 
@@
 
-\section{Synthesizing graphics programs from execution traces}
+\section{Synthesizing graphics programs from execution traces}\label{programSynthesisSection}
 Although the execution trace of a graphics program describes the parts

### 2017-05-17 paper.tex
better explanation of distance metric

@@
 the distance between two traces conditioned upon their renderings.
-We train our likelihood surrogate to approximate the symmetric difference:
+We train our likelihood surrogate to approximate the symmetric difference,
+which is  the number of drawing commands by which to traces differ:
 \begin{equation}
--\log L_{\text{learned}}(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|
+-\log L_{\text{learned}}(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|\label{symmetricDistance}
 \end{equation}
+Intuitively, Eq.~\ref{symmetricDistance} says that
+$L_{\text{learned}}(\cdot|\cdot)$ approximates the distance between
+the trace we want and the trace we have so far.  Pixel-wise distance
+metrics are sensitive to the fine details of how and exactly where
+arrows, dashes, and corners are drawn -- but we wish to be invariant
+to these details. So, we learn a distance metric over images that
+approximates the distance metric in the search space over traces.
 
@@
 (b): Rendering of the trace our model infers for (a).
-We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) for a noisy rendering of (b).}\ref{handDrawingExamples}
+We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) for a noisy rendering of (b).}\label{handDrawingExamples}
   \end{minipage}\hfill
@@
   \caption{Example drawings above model outputs.
-See also Fig.~\ref{firstPageExamples}}\label{handDrawingExamples}~\remark{Showing `failure cases' (the last three above) out-of-context seems not great.
+See also Fig.~\ref{firstPageExamples}}\label{lotsOfHandDrawings}~\remark{Showing `failure cases' (the last three above) out-of-context seems not great.
 Perhaps remind people in the caption that stochastic search can help correct some of these issues?}

### 2017-05-18 paper.tex
Typo fix.
added bibliography for real

@@
 renderings of the training target images.
-We designed this noise process to introduce the kinds of variations found in hand drawings (Figure~\ref{handDrawingExamples}).~\remark{Process should be described (in supplement)}
+We designed this noise process to introduce the kinds of variations found in hand drawings (Figure~\ref{handDrawingExamples}; see supplement for details).
 Our neurally-guided SMC procedure
@@
 model by asking it to sample many candidate traces for each drawing.
-For 55\% of the drawings the Top-1 most likely sample exactly matches the
+For 57\% of the drawings the Top-1 most likely sample exactly matches the
 ground truth; as we consider more samples the model encounters traces
@@
 
-Similarity metric in program space:\\
-\includegraphics[width = 8in]{figures/similarity.png}
-
-Similarity metric in image space:\\
-\includegraphics[width = 8in]{figures/imageSimilarity.png}
+\begin{figure}
+  \begin{minipage}{0.4\textwidth}
+  \includegraphics[width = 3in]{figures/NMF.png}
+  \caption{NMF on features of the programs that were synthesized for each image.
+Horizontal component roughly corresponds to ``symmetry'' while vertical component roughly corresponds to ``loopyness'', with images on the diagonal having both of these.}
+    \end{minipage}\hfill
+\begin{minipage}{0.4\textwidth}
+  \includegraphics[width = 3in]{figures/imageSimilarity.png} 
+  \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
+    \end{minipage}
+  \end{figure}
 

### 2017-05-18 supplement.tex
supplement
added bibliography for real

@@
 % to compile a camera-ready version, add the [final] option, e.g.:
-\usepackage{nips_2016}
+\usepackage{nips_2017}
 
@@
 
+\section{Simulating hand drawings}
+
+We introduce noise into the rendering process by:
+
+\begin{itemize}
+\item Rescaling the image intensity by a factor chosen uniformly at random from $[0.5,1.5]$
+\item Translating the image by $\pm 3$ pixels chosen uniformly random
+\item Rendering the \LaTeX~using the \verb|pencildraw| style,
+  which adds random perturbations to the paths drawn by \LaTeX in a way designed to resemble a pencil.
+\item Randomly perturbing the positions and sizes of primitive  \LaTeX drawing commands
+  \end{itemize}
+
 \section{Neural networks for guiding SMC}

### 2017-05-18 paper.tex
Conclusion.

@@
 We train our likelihood surrogate to approximate the symmetric difference,
-which is  the number of drawing commands by which to traces differ:
+which is  the number of drawing commands by which two traces differ:
 \begin{equation}
@@
 
+\section{Conclusion}
+
+We have presented a system for inferring graphics programs which generate \LaTeX-style figures from hand-drawn images.
+The system uses a combination of deep neural networks and stochastic search to parse drawings into symbolic execution traces; it then feeds these traces to a general-purpose program synthesis engine to infer a structured graphics program.
+We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings and to organize them according to high-level geometric features.
+
+There are many directions for future work.
+In the parsing phase, the proposal network currently samples positional variables on a discrete grid.
+More general types of drawings could be supported by instead sampling from continuous distributions, e.g.
+using Mixture Density Networks~\cite{MDN}.
+The proposal network also currently handles only a very small subset of \LaTeX drawing commands, though there is no reason that it could not be extended to handle more with a higher-capacity network.
+Exploring more sophisticated network architectures, including ones that utilize attention, could also help correct some of the errors the network makes.
+In the synthesis phase, a more expressive DSL---including subroutines, recursion, and symmetry groups beyond reflections---would allow the system to effectively model a wider variety of graphical phenomena.
+The synthesizer itself could also be the subject of future work: the system currently uses the general-purpose Sketch synthesizer, which can take minutes to hours to run, whereas program synthesizers which are custom-built for special problem domains can run much faster or even interactively~\cite{le2014flashextract}.
+
+In the not-too-distant future, we believe it should be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the corresponding code.
+More generally, we believe that the two-phase system we have proposed---parsing into execution traces, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for other domains in which agents must programmatically reason about noisy perceptual input.
+
 %\input{synthesizerOutputs.tex}

### 2017-05-18 paper.tex
edits motivated by Dan's comments

@@
   simple kinds of conditionals. With a graphics program in hand,
-  we can correct errors made by the deep network, extrapolate drawings, and cluster drawings by use of similar high-level geometric structures.
+  we can correct errors made by the deep network, cluster drawings by use of similar high-level geometric structures, and extrapolate drawings.
   Taken together these results are a step towards
@@
 
-The CogSketch~\cite{forbus2011cogsketch} system also aims to have a high-level understanding of hand-drawn figures.
-Their primary goal is cognitive modeling, whereas we are interested in building an automated AI application.
-
-%% open domain sketch understanding.
-structure mapping style model.
-also taps into cyc?
-the user segments the ink and labels them with concepts from knowledge base.
-like us they focus on compositional understanding.
-``cognitive simulation", solves things like Raven matrices in IQ tests.
-not really trying right now to be automated like our system.
-
 Our work bears resemblance to the Attend-Infer-Repeat (AIR) system, which learns to decompose an image into its constituent objects~\cite{eslami1603attend}.
@@
 
-\remark{Do you also want to cite your own work on ``Unsupverised Learning by Program Synthesis'' here?}
+The CogSketch~\cite{forbus2011cogsketch} system also aims to have a
+high-level understanding of hand-drawn figures. Their primary goal is
+cognitive modeling (eg, they apply their system to solving IQ-test
+style visual reasoning problems), whereas we are interested in
+building an automated AI application (eg, in our system the user need
+not annotate which strokes correspond to which shapes; our neural
+network produces something equivalent to the annotations).  A key
+similarity however is that both CogSketch and our system have as a
+goal to make it easier to produce nice-looking figures.
+Unsupervised Program Synthesis~\cite{ellis2015unsupervised} is a related framework which was also applied to geometric reasoning problems.
+The goals of~\cite{ellis2015unsupervised} were cognitive modeling,
+and they applied their technique to synthetic scenes used in human behavioral studies.
+%% open domain sketch understanding.
+structure mapping style model.
+also taps into cyc?
+the user segments the ink and labels them with concepts from knowledge base.
+like us they focus on compositional understanding.
+``cognitive simulation", solves things like Raven matrices in IQ tests.
+not really trying right now to be automated like our system.
 
@@
   \draw[->,ultra thick,red] (c1.south) -- (l1.north);
-  \node(l2) at ([yshift = -2cm]c2.south) {\verb|X=3,|};
+  \node(l2) at ([yshift = -2cm]c2.south) {\verb|X=7,|};
   \draw[->,ultra thick,red] (c2.south) -- (l2.north);
   \node[draw,ultra thick,minimum size = 1cm](c3) at ([xshift = 1cm]c2.east) {MLP};
-  \node(l3) at ([yshift = -2cm]c3.south) {\verb|Y=14)|};
+  \node(l3) at ([yshift = -2cm]c3.south) {\verb|Y=12)|};
   \draw[->,ultra thick,red] (c3.south) -- (l3.north);
@@
   \caption{Example drawings above model outputs.
-See also Fig.~\ref{firstPageExamples}}\label{lotsOfHandDrawings}~\remark{Showing `failure cases' (the last three above) out-of-context seems not great.
+See also Fig.~\ref{firstPageExamples}.
+Stochastic search (SMC) can help correct for these errors, as can the program synthesizer (Section~\ref{synthesizerHelpsParsing})}\label{lotsOfHandDrawings}%~\remark{Showing `failure cases' (the last three above) out-of-context seems not great.
 Perhaps remind people in the caption that stochastic search can help correct some of these issues?}
@@
 Python, a more tractable approach is to specify what in the program
-languages community is called a Domain Specific Language (DSL)~\remark{citation?}. Our DSL (Table~\ref{DSL})
+languages community is called a Domain Specific Language (DSL)~\cite{polozov2015flashmeta}. Our DSL (Table~\ref{DSL})
 encodes prior knowledge of what graphics programs tend to look like.
@@
 high level, Sketch takes as input a space of programs, along with a
-specification of the program 's behavior and optionally a cost
+specification of the program's behavior and optionally a cost
 function.  It translates the synthesis problem into a constraint
@@
 Within our domain of hand-drawn figures, graphics program synthesis has several uses:
-\remark{I'm of two minds about how these subsections should be ordered.
+%\remark{I'm of two minds about how these subsections should be ordered.
 The current ordering leads with the coolest results, which is nice.
@@
 
-\subsection{Extrapolating figures}
-Having access to the source code of a graphics program facilitates coherent, high-level edits to the figure generated by that program. 
-For example,
-we can change all of the circles to squares or make all of the lines be dashed.
-We can also \textbf{extrapolate} figures
-by increasing the number of times that loops are executed.~\remark{Pick a few of these to show off and put the rest in supplement?}
-Extrapolating repetitive visuals patterns comes naturally to humans,
-and building this ability into an application is practical:
-imagine hand drawing a repetitive graphical model structure
-and having our system automatically induce and extend the pattern.
-Fig.~\ref{extrapolationFigure} shows extrapolations of programs synthesized from ground truth traces;
-see supplement for our full set of extrapolations.
-
-\begin{figure}
-  \includegraphics[width = 8in]{figures/extrapolationMatrix.png}
-  \caption{Left: hand drawings. Right: extrapolations produced by
-    running different parts of different loops either forward or
-    backward an extra iteration.}\label{extrapolationFigure}
-  \end{figure}
-%\input{extrapolations.tex}
-
-\subsection{Modeling similarity between figures}
-
-\begin{figure}
-  \begin{minipage}{0.4\textwidth}
-  \includegraphics[width = 3in]{figures/NMF.png}
-  \caption{NMF on features of the programs that were synthesized for each image.
-Horizontal component roughly corresponds to ``symmetry'' while vertical component roughly corresponds to ``loopyness'', with images on the diagonal having both of these.}
-    \end{minipage}\hfill
-\begin{minipage}{0.4\textwidth}
-  \includegraphics[width = 3in]{figures/imageSimilarity.png} 
-  \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
-    \end{minipage}
-  \end{figure}
-
-\subsection{Correcting errors made by the parsing network}
-The program synthesizer can help correct errors from the parse proposal network by favoring execution traces which lead to more concise or general programs.
+\subsection{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
+The program synthesizer can help correct errors from the execution trace proposal network by favoring execution traces which lead to more concise or general programs.
 For example, one generally prefers figures with perfectly aligned objects over figures whose parts are slightly misaligned -- and precise alignment lends itself to short programs.
@@
 
+\subsection{Modeling similarity between figures}
+
+\begin{figure}
+  \begin{minipage}{0.4\textwidth}
+  \includegraphics[width = 3in]{figures/NMF.png}
+  \caption{NMF on features of the programs that were synthesized for each image.
+Horizontal component roughly corresponds to ``symmetry'' while vertical component roughly corresponds to ``loopyness'', with images on the diagonal having both of these.}
+    \end{minipage}\hfill
+\begin{minipage}{0.4\textwidth}
+  \includegraphics[width = 3in]{figures/imageSimilarity.png} 
+  \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
+    \end{minipage}
+  \end{figure}
+
+\subsection{Extrapolating figures}
+Having access to the source code of a graphics program facilitates coherent, high-level edits to the figure generated by that program. 
+For example,
+we can change all of the circles to squares or make all of the lines be dashed.
+We can also \textbf{extrapolate} figures
+by increasing the number of times that loops are executed.~\remark{Pick a few of these to show off and put the rest in supplement?}
+Extrapolating repetitive visuals patterns comes naturally to humans,
+and building this ability into an application is practical:
+imagine hand drawing a repetitive graphical model structure
+and having our system automatically induce and extend the pattern.
+Fig.~\ref{extrapolationFigure} shows extrapolations of programs synthesized from ground truth traces;
+see supplement for our full set of extrapolations.
+
+\begin{figure}
+  \includegraphics[width = 8in]{figures/extrapolationMatrix.png}
+  \caption{Left: hand drawings. Right: extrapolations produced by
+    running different parts of different loops either forward or
+    backward an extra iteration.}\label{extrapolationFigure}
+  \end{figure}
+%\input{extrapolations.tex}
+
 % \remark{Seems like you're still fleshing this part out, but I'll give my feedback anyway: (1) This subsection could really use a motivational introduction, e.g.

### 2017-05-18 paper.tex
writing for the similarity section

@@
 
-\subsection{Modeling similarity between figures}
+\subsection{Modeling similarity between drawings}
+Modeling an image using a program opens up new ways of measuring similarity between drawings.
+For example, we might say that two drawings are similar if they both contain repetitions of length 4,
+or if they share the same reflectional symmetry,
+or if they are both organized according to a grid-like structure.
 
+We measure the similarity between two drawings by extracting features
+of the best programs that describe them.  Here the features we use are
+just counts of the number of times that different components in the
+DSL were used (Table~\ref{DSL}).  We project these features down to a
+2-dimensional subspace using nonnegative matrix factorization
+(NMF:~\cite{lee1999learning}); see Fig.\ref{NMF}.  One could use many
+alternative similarity metrics between drawings which would capture pixel-level or object-level similarities while missing high-level geometric similarities.
+For example, we can use our learned distance metric between execution traces, $L_{\text{learned}}(\cdot|\cdot)$.
+Projecting these distances to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}) reveals similarities between the objects in the drawings,
+while missing similarities at the level of the program.
 \begin{figure}
@@
     \caption{NMF on features of the programs that were synthesized for each image.
-Horizontal component roughly corresponds to ``symmetry'' while vertical component roughly corresponds to ``loopyness'', with images on the diagonal having both of these.}
+Horizontal component roughly corresponds to ``symmetry'' while vertical component roughly corresponds to ``loopyness'', with images on the diagonal having both of these.}    \label{NMF}
   \end{minipage}\hfill

### 2017-05-18 paper.tex
Fixing some math mode build errors.

@@
 \DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays
-\DeclareMathOperator{\argmin}{argmin} % no space, limits underneath in displays
+% \DeclareMathOperator{\argmin}{argmin} % no space, limits underneath in displays
 \DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays
-\DeclareMathOperator{\argmax}{argmax} % no space, limits underneath in displays
+% \DeclareMathOperator{\argmax}{argmax} % no space, limits underneath in displays
 
@@
   Command$\to$&\texttt{reflect}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
-  Expression$\to$&\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}\\
+  Expression$\to$&$\mathcal{Z}$\texttt{ * }Var\texttt{ + }$\mathcal{Z}$\\
   Var$\to$&A free (unused) variable\\
-  \mathcal{Z}$\to$&an integer\\
-  Axis$\to$&\texttt{X = }\mathcal{Z}\\
-  Axis$\to$&\texttt{Y = }\mathcal{Z}\\\bottomrule
+  $\mathcal{Z}$$\to$&an integer\\
+  Axis$\to$&\texttt{X = }$\mathcal{Z}$\\
+  Axis$\to$&\texttt{Y = }$\mathcal{Z}$\\\bottomrule
   \end{tabular}
   \caption{Grammar over graphics programs.
-We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertical/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations (\mathcal{Z}\texttt{ * }Var\texttt{ + }\mathcal{Z}).}\label{DSL}
+We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertical/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations ($\mathcal{Z}$\texttt{ * }Var\texttt{ + }$\mathcal{Z}$).}\label{DSL}
 \end{table}

### 2017-05-18 supplement.tex
more stuff in the supplement

@@
 \newcommand{\Expect}{\mathds{E}} %{{\rm I\kern-.3em E}}
-\newcommand{\Probability}{\mathds{P}} %{{\rm I\kern-.3em P}}
+\newcommand{\probability}{\mathds{P}} %{{\rm I\kern-.3em P}}
 
@@
 
+\section{Neural network architecture}
+
+\subsection{Convolutional network}
+The convolutional network takes as input 2 $256\times 256$ images
+represented as a $2\times 256\times 256\times$ volume. These are
+passed through two layers of convolutions separated by ReLU
+nonlinearities and max pooling:
+\begin{itemize}
+\item Layer 1: 20 $8\times 8$ convolutions, 2 $16\times 4$ convolutions, 2 $4\times 16$ convolutions. Followed by $8\times 8$ pooling with a stride size of 4.
+\item Layer 2: 10 $8\times 8$ convolutions. Followed by $4\times 4$ pooling with a stride size of 4.
+\end{itemize}
+Training takes a little bit less than a day on a Nvidia TitanX GPU.
+The network was trained on $10^5$ synthetic examples.
+
+\subsection{Autoregressive decoding of drawing commands}
+
+Given the image features $f$, we predict the first token using logistic regression:
+\begin{equation}
+  \probability [T_1]\propto W_{T_1}f
+\end{equation}
+where $W_{T_1}$ is a learned weight matrix.
+
+Subsequent tokens are predicted as:
+\begin{equation}
+  \probability [T_n|T_{1:(n - 1)}]\propto \text{MLP}_{T_1,n}(I \otimes \bigotimes_{j < n} \text{oneHot}(T_j))
+\end{equation}
+Thus each token of each drawing primitive has its own learned MLP.
+For predicting the coordinates of lines we found that using 32 hidden nodes with sigmoid activations worked well;
+for other tokens the MLP's are just logistic regression (no hidden nodes).
+
+\subsection{A learned likelihood surrogate}
+
+Our architecture for
+$L_{\text{learned}}(\text{render}(T_1)|\text{render}(T_2))$ has the
+same series of convolutions as the network that predicts the next
+drawing command. We train it to predict two scalars: $|T_1 - T_2|$ and
+$|T_2 - T_1|$.  These predictions are made using linear regression
+from the image features followed by a ReLU nonlinearity; this
+nonlinearity makes sense because the predictions can never be negative
+but could be arbitrarily large positive numbers.
+
+We train this network by sampling random synthetic scenes for $T_1$,
+and then perturbing them in small ways to produce $T_2$.
+We minimize the squared loss between the network's prediction and the ground truth symmetric differences.
+$T_1$ is rendered in a ``simulated hand drawing'' style which we describe next.
+
 \section{Simulating hand drawings}
@@
 
-\section{Neural networks for guiding SMC}
+%% \section{Neural networks for guiding SMC}
 
-Let $L(\cdot | \cdot):\text{image}^2\to \mathcal{R}$ be our likelihood
-function: it takes two images, an observed target image and a
-hypothesized program output, and gives the likelihood of the observed
-image conditioned on the program output. We want to sample from:
-\begin{equation}
-\probability [p|x]  \propto L(x | \text{render}(p)) \probability [p]
-\end{equation}
-where $\probability [p]$ is the prior probability of program $p$, and $x$ is the observed image.
+%% Let $L(\cdot | \cdot):\text{image}^2\to \mathcal{R}$ be our likelihood
+%% function: it takes two images, an observed target image and a
+%% hypothesized program output, and gives the likelihood of the observed
+%% image conditioned on the program output. We want to sample from:
+%% \begin{equation}
+%% \probability [p|x]  \propto L(x | \text{render}(p)) \probability [p]
+%% \end{equation}
+%% where $\probability [p]$ is the prior probability of program $p$, and $x$ is the observed image.
 
-Let $p$ be a program with $L$ lines, which we will write as $p = (p_1,p_2,\cdots,p_L)$. Assume the prior factors into:
-\begin{equation}
-  \probability [p]\propto \prod_{l\leq L}\probability [p_l]
-\end{equation}
-Define the distribution $q_L(\cdot)$, which happens to be proportional to the above posterior:
-\begin{equation}
-  q_L(p_1,p_2,\cdots,p_{L - 1},p_L)\propto q_{L - 1}(p_1,p_2,\cdots,p_{L - 1})\times \frac{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1}))}\times\probability [p_L]
-\end{equation}
-Now suppose we have some samples from $q_{L - 1}(\cdot)$, and that we
-then sample a $p_L$ from a distribution proportional to $\frac{L(x |
-  \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x |
-  \text{render}(p_1,p_2,\cdots,p_{L - 1}))}\times\probability [p_L]$.
-The resulting programs $p$ are distributed according to $q_L$, and so
-are also distributed according to $\probability [p|x]$.
+%% Let $p$ be a program with $L$ lines, which we will write as $p = (p_1,p_2,\cdots,p_L)$. Assume the prior factors into:
+%% \begin{equation}
+%%   \probability [p]\propto \prod_{l\leq L}\probability [p_l]
+%% \end{equation}
+%% Define the distribution $q_L(\cdot)$, which happens to be proportional to the above posterior:
+%% \begin{equation}
+%%   q_L(p_1,p_2,\cdots,p_{L - 1},p_L)\propto q_{L - 1}(p_1,p_2,\cdots,p_{L - 1})\times \frac{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1}))}\times\probability [p_L]
+%% \end{equation}
+%% Now suppose we have some samples from $q_{L - 1}(\cdot)$, and that we
+%% then sample a $p_L$ from a distribution proportional to $\frac{L(x |
+%%   \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x |
+%%   \text{render}(p_1,p_2,\cdots,p_{L - 1}))}\times\probability [p_L]$.
+%% The resulting programs $p$ are distributed according to $q_L$, and so
+%% are also distributed according to $\probability [p|x]$.
 
-How do we sample $p_L$ from a distribution proportional to $\frac{L(x
-  | \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x |
-  \text{render}(p_1,p_2,\cdots,p_{L - 1}))}\times\probability [p_L]$?
-We have a neural network that takes as input the target image $x$ and
-the program so far, and produces a distribution over next lines of
-code ($p_L$).  We write $\text{NN}(p_L | p_1,\cdots,p_{L - 1};x)$ for
-the distribution output by the neural network. So we can sample from NN and then weight the samples by:
-\begin{equation}
-  w(p_L) = \frac{\probability [p_L]}{\text{NN}(p_L | p_1,\cdots,p_{L - 1};x)}\times \frac{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1}))}
-\end{equation}
-Then we can resample from these now weighted samples to get a new
-population of particles (here programs are particles), where each
-program now has $L$ lines instead of $L - 1$.
+%% How do we sample $p_L$ from a distribution proportional to $\frac{L(x
+%%   | \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x |
+%%   \text{render}(p_1,p_2,\cdots,p_{L - 1}))}\times\probability [p_L]$?
+%% We have a neural network that takes as input the target image $x$ and
+%% the program so far, and produces a distribution over next lines of
+%% code ($p_L$).  We write $\text{NN}(p_L | p_1,\cdots,p_{L - 1};x)$ for
+%% the distribution output by the neural network. So we can sample from NN and then weight the samples by:
+%% \begin{equation}
+%%   w(p_L) = \frac{\probability [p_L]}{\text{NN}(p_L | p_1,\cdots,p_{L - 1};x)}\times \frac{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1},p_L))}{L(x | \text{render}(p_1,p_2,\cdots,p_{L - 1}))}
+%% \end{equation}
+%% Then we can resample from these now weighted samples to get a new
+%% population of particles (here programs are particles), where each
+%% program now has $L$ lines instead of $L - 1$.
 
-This procedure can be seen as a particle filter, where each successive
-latent variable is another line of code, and the emission
-probabilities are successive ratios of likelihoods under $L(\cdot |
-\cdot)$.
+%% This procedure can be seen as a particle filter, where each successive
+%% latent variable is another line of code, and the emission
+%% probabilities are successive ratios of likelihoods under $L(\cdot |
+%% \cdot)$.
 
-\textbf{Comments for Dan}. Right now I'm not actually sampling from
-the neural network - instead, I enumerate the top few hundred lines of
-code suggested by the network, and then weight them by their
-likelihoods.
-So actually the form of NN is:
-\begin{equation}
-  \text{NN}(p_L | p_1,\cdots,p_{L - 1};x)\propto \begin{cases}
-    1,&\text{ if }p_L \in \text{top hundred neural network proposals}\\
-0,&\text{otherwise}.    \end{cases}
-\end{equation}
-Do you think this is a problem? The neural network puts almost all of its mass on a few guesses.
-In order to get the correct line of code I sometimes need to get something like the 50th  top guess,
-so I don't want to literally just sample from the distribution suggested by the neural network.
-
-  \begin{algorithm}[tb]
-   \caption{Neurally guided SMC}
-   \label{guideAlgorithm}
-\begin{algorithmic}
-  \STATE {\bfseries Input:} Neural network NN, beam size $N$, maximum length $L$, target image $x$
-  \STATE {\bfseries Output:} Samples of the program trace
-  \STATE Set $B_0 = \{\text{empty program}\}$
-  \FOR{$1\leq l\leq L$}
-  \FOR{$1\leq n\leq N$}
-  \STATE{ $p_n\sim \text{Uniform}(B_{l - 1})$}
-  \STATE{ $p'_{n}\sim \text{NN}(\text{render}(p),x)$}
-  \STATE{ Define $r_n = p'_n\cdot p_n$}
-  \STATE{ Set $\tilde{w}(r_n) = \frac{L(x|r_n)}{L(x|p_n)}\times\frac{\probability [p'_n]}{\probability [p'_n = \text{NN}(\text{render}(p),x)]}$}
-  \ENDFOR
-  \STATE{ Define $w(p) = \frac{\tilde{w}(p)}{\sum_{p'}\tilde{w}(p')}$}
-  \STATE{ Set $B_l$ to be $N$ samples from $r_n$ distributed according to $w(\cdot)$}
-  \ENDFOR
-  \STATE {\bfseries return} $\{p : p\in B_{l\leq L}, p \text{ is finished}\}$
-\end{algorithmic}
-  \end{algorithm}
+%%   \begin{algorithm}[tb]
+%%    \caption{Neurally guided SMC}
+%%    \label{guideAlgorithm}
+%% \begin{algorithmic}
+%%   \STATE {\bfseries Input:} Neural network NN, beam size $N$, maximum length $L$, target image $x$
+%%   \STATE {\bfseries Output:} Samples of the program trace
+%%   \STATE Set $B_0 = \{\text{empty program}\}$
+%%   \FOR{$1\leq l\leq L$}
+%%   \FOR{$1\leq n\leq N$}
+%%   \STATE{ $p_n\sim \text{Uniform}(B_{l - 1})$}
+%%   \STATE{ $p'_{n}\sim \text{NN}(\text{render}(p),x)$}
+%%   \STATE{ Define $r_n = p'_n\cdot p_n$}
+%%   \STATE{ Set $\tilde{w}(r_n) = \frac{L(x|r_n)}{L(x|p_n)}\times\frac{\probability [p'_n]}{\probability [p'_n = \text{NN}(\text{render}(p),x)]}$}
+%%   \ENDFOR
+%%   \STATE{ Define $w(p) = \frac{\tilde{w}(p)}{\sum_{p'}\tilde{w}(p')}$}
+%%   \STATE{ Set $B_l$ to be $N$ samples from $r_n$ distributed according to $w(\cdot)$}
+%%   \ENDFOR
+%%   \STATE {\bfseries return} $\{p : p\in B_{l\leq L}, p \text{ is finished}\}$
+%% \end{algorithmic}
+%%   \end{algorithm}
 

### 2017-05-18 paper.tex
small latex cleanup motivated by comments from Dan

@@
   \draw[->,ultra thick] (observation.east) -- (tensorProduct.north);%([yshift = 0.5cm]CNN.west);
-  \draw[->,ultra thick] (tensorProduct.east)  -- node[center,fill = white,rotate = 90] {{\tiny $256\times 256\times 2$}}  (CNN.west);
-  \draw[->,ultra thick] (CNN.east) -- node[center,fill = white,rotate = 90] {{\tiny $16\times 16\times 10$}} (features.south);
+  \draw[->,ultra thick] (tensorProduct.east)  -- node[fill = white,rotate = 90] {{\tiny $256\times 256\times 2$}}  (CNN.west);
+  \draw[->,ultra thick] (CNN.east) -- node[fill = white,rotate = 90] {{\tiny $16\times 16\times 10$}} (features.south);
 %  \draw[]

### 2017-05-18 paper.tex
smaller extrapolation figure. still need to make things more legible by changing colors hands rescaling the pictures

@@
 We can also \textbf{extrapolate} figures
-by increasing the number of times that loops are executed.~\remark{Pick a few of these to show off and put the rest in supplement?}
+by increasing the number of times that loops are executed.
 Extrapolating repetitive visuals patterns comes naturally to humans,
@@
 \begin{figure}
-  \includegraphics[width = 8in]{figures/extrapolationMatrix.png}
-  \caption{Left: hand drawings. Right: extrapolations produced by
-    running different parts of different loops either forward or
-    backward an extra iteration.}\label{extrapolationFigure}
+  \includegraphics[width = \textwidth]{figures/extrapolationMatrix.png}
+  \caption{Top: hand drawings. Bottom: extrapolations produced by
+running loops for extra iterations.}\label{extrapolationFigure}
   \end{figure}

### 2017-05-18 synthesizerOutputs.tex
better figure for multidimensional scaling result

--- 2017-05-09 synthesizerOutputs.tex
@@
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-41.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-0.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-0-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(0,0,1,6)
-  Rectangle(2,0,3,6)
-  Rectangle(4,0,5,6)
+line(6,2,3,2,arrow = True,solid = True);
+line(6,2,6,3,arrow = False,solid = True);
+rectangle(0,0,8,9);
+rectangle(5,3,7,6);
+reflect(reflect(y = 9)){
+line(3,2,5,4,arrow = True,solid = True);
+rectangle(1,6,3,8)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-17.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-2.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-2-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(2,9,4,11)
-    for (3)
-        Line(-2*i + 7,3*i + 3,-2*i + 6,3*i + 1,arrow = True,solid = True)
-        Line(2*i + 3,-3*i + 9,2*i + 4,-3*i + 7,arrow = True,solid = True)
-        Rectangle(2*i,-3*i + 6,2*i + 2,-3*i + 8)
-        Rectangle(-2*i + 8,3*i,-2*i + 10,3*i + 2)
+rectangle(4,2,6,5);
+reflect(reflect(y = 7)){
+line(2,6,4,4,arrow = True,solid = True);
+rectangle(0,5,2,7)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-43.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-3.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-3-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-      Line(0,0,0,5,arrow = False,solid = True)
+circle(10,5);
+line(7,5,9,5,arrow = True,solid = True);
+rectangle(0,0,12,10);
+reflect(reflect(y = 10)){
+line(3,8,5,6,arrow = True,solid = True);
+rectangle(1,1,3,3);
+rectangle(5,3,7,7)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-63.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-4.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-4-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(0,0,5,5)
-  Rectangle(1,1,4,4)
-  Rectangle(2,2,3,3)
+circle(10,4);
+line(10,1,10,3,arrow = False,solid = False);
+line(10,1,2,1,arrow = True,solid = False);
+line(7,4,9,4,arrow = True,solid = True);
+reflect(reflect(y = 8)){
+line(2,1,4,3,arrow = True,solid = True);
+rectangle(0,6,2,8);
+rectangle(4,2,7,6)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-11.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-6.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-6-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Circle(1,1)
+rectangle(2,0,5,3);
+for (i < 3){
+if (i > 0){
+line(0,3*i + -2,3*i + -3,4,arrow = False,solid = True);
+line(3*i + -3,4,3*i + -1,3,arrow = False,solid = True)
+}line(0,1,2,0,arrow = False,solid = True)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-45.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-7.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-7-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(0,4,4,8)
-        reflect(y = 12)
-        Circle(7,6)
-        Line(2,2,2,4,arrow = True,solid = True)
-        Line(4,6,6,6,arrow = True,solid = True)
-        Rectangle(1,0,3,2)
+for (i < 3){
+circle(-3*i + 7,6);
+circle(-3*i + 7,1);
+line(-3*i + 7,-1*i + 4,-3*i + 7,5,arrow = False,solid = True)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-51.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-8.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-8-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(2,2,5,3)
-  Rectangle(0,0,3,1)
-  Rectangle(4,4,7,5)
+line(0,0,0,4,arrow = False,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-21.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-9.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-9-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Circle(1,5)
-    for (2)
-        Line(-5*i + 9,-1*i + 2,-7*i + 9,-3*i + 4,arrow = True,solid = True)
-        Rectangle(-4*i + 8,4*i,-4*i + 10,4*i + 2)
-              reflect(x = 6)
-              Line(7*i + 1,-1*i + 2,5*i + 1,-3*i + 4,arrow = True,solid = True)
-              Rectangle(8*i,4*i,8*i + 2,4*i + 2)
+line(6,0,0,0,arrow = True,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-2.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-10.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-10-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(4,2,6,5)
-        reflect(y = 7)
-        Line(2,6,4,4,arrow = True,solid = True)
-        Rectangle(0,5,2,7)
+rectangle(0,0,3,4)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-24.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-11.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-11-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(3,3,3,2,arrow = True,solid = True)
-  Rectangle(0,7,6,9)
-  Rectangle(2,0,4,2)
-  Rectangle(0,3,6,6)
-        Line(1,7,1,6,arrow = True,solid = True)
+circle(1,1)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-7.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-12.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-12-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  for (3)
-      Circle(-3*i + 7,1)
-      Circle(3*i + 1,6)
-      Line(3*i + 1,2,3*i + 1,5,arrow = False,solid = True)
+line(2,1,5,1,arrow = False,solid = True);
+reflect(reflect(x = 7)){
+circle(1,1);
+line(2,6,5,6,arrow = False,solid = True);
+line(1,2,1,5,arrow = False,solid = True);
+rectangle(0,5,2,7)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-44.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-13.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-13-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-      reflect(x = 12)
-      Circle(4,1)
-      Line(9,1,10,1,arrow = False,solid = True)
-      Rectangle(10,0,12,2)
+line(3,2,1,2,arrow = True,solid = True);
+line(5,0,3,0,arrow = True,solid = True);
+line(2,1,4,1,arrow = True,solid = True);
+line(0,3,2,3,arrow = True,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-64.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-14.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-14-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-      reflect(x = 6)
-      Line(5,2,5,4,arrow = False,solid = True)
-            reflect(y = 6)
-            Line(2,5,4,5,arrow = False,solid = True)
-            Rectangle(0,4,2,6)
+for (i < 4){
+if (i > 0){
+rectangle(2*i + -2,-2*i + 6,2*i + -1,-2*i + 7)
+}rectangle(2*i,-2*i + 6,2*i + 1,-2*i + 7)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-36.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-15.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-15-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  for (2)
-      Rectangle(0,-3*i + 8,1,-2*i + 9)
-      Rectangle(-3*i + 8,5*i,9,8*i + 1)
-      Rectangle(-7*i + 7,-2*i + 2,-5*i + 9,4)
+line(0,3,2,3,arrow = False,solid = False);
+line(2,1,4,1,arrow = False,solid = False);
+line(1,2,3,2,arrow = False,solid = True);
+line(3,0,5,0,arrow = False,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-58.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-17.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-17-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(4,0,5,4)
-    for (2)
-        Line(8,0,-8*i + 8,-7*i + 7,arrow = True,solid = True)
-        Rectangle(-4*i + 6,0,-4*i + 7,-2*i + 5)
+for (i < 4){
+if (i > 0){
+line(-2*i + 9,3*i,-2*i + 10,3*i + -2,arrow = True,solid = True);
+line(-2*i + 9,3*i,-2*i + 8,3*i + -2,arrow = True,solid = True);
+rectangle(-2*i + 6,3*i + -3,-2*i + 8,3*i + -1)
+}rectangle(-2*i + 8,3*i,-2*i + 10,3*i + 2)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-3.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-19.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-19-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Circle(10,5)
-  Line(7,5,9,5,arrow = True,solid = True)
-  Rectangle(5,3,7,7)
-  Rectangle(0,0,12,10)
-        reflect(y = 10)
-        Line(3,2,5,4,arrow = True,solid = True)
-        Rectangle(1,1,3,3)
+line(4,4,2,2,arrow = True,solid = True);
+rectangle(0,0,2,2);
+rectangle(3,4,5,6)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-28.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-21.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-21-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(0,0,0,2,arrow = False,solid = True)
-  Line(0,2,2,2,arrow = False,solid = True)
+circle(1,5);
+for (i < 3){
+if (i > 0){
+line(-4*i + 12,1,-4*i + 10,1,arrow = True,solid = True);
+rectangle(-4*i + 12,4,-4*i + 14,6)
+}line(-4*i + 9,2,-4*i + 9,4,arrow = True,solid = True);
+rectangle(-4*i + 8,0,-4*i + 10,2)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
+            \begin{tabular}{lll}
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-22.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-22-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(8,5,6,5,arrow = True,solid = True)
-  Line(4,5,2,5,arrow = True,solid = True)
-    for (3)
-        Line(-4*i + 9,4,-4*i + 9,2,arrow = True,solid = True)
-        Rectangle(4*i,0,4*i + 2,2)
-        Rectangle(-4*i + 8,4,-4*i + 10,6)
+for (i < 3){
+if (i > 0){
+line(4*i,5,4*i + -2,5,arrow = True,solid = True)
+}line(4*i + 1,4,4*i + 1,2,arrow = True,solid = True);
+rectangle(4*i,0,4*i + 2,2);
+rectangle(4*i,4,4*i + 2,6)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-69.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-23.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-23-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(0,4,5,6)
-        reflect(x = 5)
-        Circle(4,1)
-        Line(1,4,1,2,arrow = True,solid = True)
+for (i < 3){
+line(-4*i + 9,2,-4*i + 9,4,arrow = True,solid = True);
+for (j < 2){
+circle(-4*i + 9,4*j + 1);
+line(-4*j + 8,1,-4*j + 6,1,arrow = True,solid = True)
+}
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-14.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-24.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-24-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(0,6,1,7)
-    for (3)
-        Rectangle(-2*i + 6,2*i,-2*i + 7,2*i + 1)
-        Rectangle(-2*i + 4,2*i,-2*i + 5,2*i + 1)
+reflect(reflect(x = 6)){
+for (i < 3){
+if (i > 0){
+line(-2*i + 7,-4*i + 11,-2*i + 7,-4*i + 10,arrow = True,solid = True);
+rectangle(0,-4*i + 11,6,-3*i + 12)
+}rectangle(2,0,4,2)
+}
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-68.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-25.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-25-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  for (3)
-      Circle(4*i + 1,1)
-      Rectangle(4*i,0,4*i + 2,2)
+for (i < 3){
+if (i > 0){
+line(-3*i + 9,1,-3*i + 8,1,arrow = True,solid = True)
+}rectangle(-3*i + 6,0,-3*i + 8,2)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-65.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-26.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-26-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-      reflect(y = 6)
-      Line(2,1,4,1,arrow = False,solid = True)
-            reflect(x = 6)
-            Circle(1,1)
-            Line(1,2,1,4,arrow = False,solid = True)
+line(1,3,1,4,arrow = False,solid = True);
+for (i < 3){
+if (i > 0){
+line(1,-5*i + 13,1,-4*i + 10,arrow = True,solid = True)
+}circle(1,-4*i + 9)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-67.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-27.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-27-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(1,5,5,1,arrow = False,solid = True)
-  Line(1,4,5,0,arrow = False,solid = True)
-  Rectangle(5,0,6,1)
-  Rectangle(0,4,1,5)
+reflect(reflect(x = 2)){
+line(0,1,1,2,arrow = False,solid = True);
+line(1,0,2,1,arrow = False,solid = True)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-12.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-28.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-28-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  for (2)
-      Circle(-5*i + 6,1)
-      Line(-4*i + 6,-1*i + 2,-1*i + 6,-4*i + 5,arrow = False,solid = True)
-      Line(-1*i + 2,-4*i + 6,-4*i + 5,-1*i + 6,arrow = False,solid = True)
-      Rectangle(5*i,5,5*i + 2,7)
+line(0,2,2,2,arrow = False,solid = True);
+line(0,0,0,2,arrow = False,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-42.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-29.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-29-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(0,0,0,5,arrow = False,solid = False)
-  Line(4,1,4,5,arrow = False,solid = False)
-  Line(4,0,4,1,arrow = False,solid = False)
+for (i < 3){
+line(-1*i + 2,i + 4,-2*i + 6,i + 4,arrow = False,solid = True);
+line(-1*i + 2,2*i,-1*i + 2,i + 4,arrow = False,solid = True)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-10.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-30.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-30-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(0,0,3,4)
+for (i < 3){
+if (i > 0){
+circle(5,2*i);
+circle(1,-3*i + 7);
+rectangle(0,-3*i + 6,2,-3*i + 8)
+}rectangle(4,1,6,5)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-35.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-31.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-31-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Circle(1,1)
-    for (2)
-        Circle(-5*i + 6,5*i + 1)
-        Line(1,5,5*i + 1,2,arrow = True,solid = True)
+for (i < 3){
+rectangle(3*i,-2*i + 4,3*i + 2,6);
+for (j < i + 1){
+circle(3*i + 1,-2*j + 5)
+}
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-31.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-32.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-32-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Circle(7,3)
-    for (3)
-        Circle(-3*i + 7,5)
-        Circle(-3*i + 7,2*i + 1)
-        Rectangle(-3*i + 6,2*i,-3*i + 8,6)
+circle(5,5);
+line(2,5,4,5,arrow = False,solid = True);
+rectangle(0,0,5,3);
+rectangle(0,4,2,6)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-37.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-33.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-33-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Circle(1,8)
-    for (2)
-        Line(4*i + 1,-5*i + 7,2*i + 3,5,arrow = False,solid = True)
-        Rectangle(-4*i + 4,5*i,6,7*i + 2)
+line(0,0,6,0,arrow = False,solid = False);
+line(0,3,6,3,arrow = False,solid = False);
+line(6,0,6,3,arrow = False,solid = True);
+line(0,0,0,3,arrow = False,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-40.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-35.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-35-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Circle(7,1)
-  Circle(4,1)
-  Circle(1,1)
+for (i < 3){
+if (i > 0){
+circle(5*i + -4,1);
+line(i,i + 4,5*i + -4,2,arrow = True,solid = True)
+}circle(1,6)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-29.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-37.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-37-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(1,2,1,5,arrow = False,solid = True)
-    for (2)
-        Line(2,-4*i + 4,-4*i + 6,4,arrow = False,solid = True)
-        Line(0,-2*i + 6,-2*i + 2,6,arrow = False,solid = True)
-        Line(1,5,2*i + 2,5,arrow = False,solid = True)
+for (i < 3){
+if (i > 0){
+line(-4*i + 9,5*i + -3,-2*i + 7,5,arrow = False,solid = True);
+rectangle(-4*i + 8,5*i + -5,6,7*i + -5)
+}circle(1,8)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-62.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-40.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-40-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(5,0,8,3)
-  Rectangle(2,1,4,3)
-  Rectangle(0,2,1,3)
+for (i < 3){
+circle(3*i + 1,1)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-57.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-41.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-41-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  for (3)
-      Circle(-4*i + 9,4)
-      Circle(-4*i + 9,1)
-      Circle(4*i + 1,7)
+for (i < 3){
+rectangle(2*i,0,2*i + 1,6)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-55.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-42.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-42-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Circle(1,5)
-  Line(1,4,1,2,arrow = True,solid = True)
-  Rectangle(0,0,2,2)
+line(0,0,0,5,arrow = False,solid = False);
+line(4,1,4,5,arrow = False,solid = False);
+line(4,0,4,1,arrow = False,solid = False)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-66.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-43.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-43-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(0,2,7,2,arrow = False,solid = True)
-  Line(1,1,6,1,arrow = False,solid = True)
-  Line(2,0,5,0,arrow = False,solid = True)
+line(0,0,0,5,arrow = False,solid = True);
+line(4,0,4,5,arrow = False,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-26.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-44.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-44-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Circle(1,9)
-  Line(1,8,1,6,arrow = True,solid = True)
-  Line(1,3,1,2,arrow = True,solid = True)
-  Line(1,3,1,4,arrow = False,solid = True)
-        reflect(y = 6)
-        Circle(1,1)
+reflect(reflect(x = 12)){
+circle(4,1);
+line(9,1,10,1,arrow = False,solid = True);
+rectangle(10,0,12,2)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-15.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-45.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-45-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(1,2,3,2,arrow = False,solid = True)
-  Line(2,1,4,1,arrow = False,solid = False)
-  Line(3,0,5,0,arrow = False,solid = True)
-  Line(0,3,2,3,arrow = False,solid = False)
+line(4,6,6,6,arrow = True,solid = True);
+rectangle(0,4,4,8);
+reflect(reflect(y = 12)){
+circle(7,6);
+line(2,10,2,8,arrow = True,solid = True);
+rectangle(1,0,3,2)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-19.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-46.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-46-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(4,4,2,2,arrow = True,solid = True)
-  Rectangle(3,4,5,6)
-  Rectangle(0,0,2,2)
+reflect(reflect(x = 9)){
+line(1,3,1,6,arrow = False,solid = True);
+reflect(reflect(y = 9)){
+circle(1,8);
+line(3,1,6,1,arrow = False,solid = True)
+}
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-8.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-47.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-47-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(0,0,0,4,arrow = False,solid = True)
+reflect(reflect(y = 11)){
+rectangle(4,1,7,2);
+reflect(reflect(x = 11)){
+rectangle(1,4,2,7);
+rectangle(0,8,3,11)
+}
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-23.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-48.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-48-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(4,1,2,1,arrow = False,solid = True)
-    for (2)
-        Line(-4*i + 5,2,-4*i + 5,4,arrow = True,solid = True)
-          for (3)
-              Circle(-4*j + 9,4*i + 1)
-              Line(8,1,3*i + 6,3*i + 1,arrow = True,solid = False)
+for (i < 3){
+line(-2*i + 5,2*i,-2*i + 7,2*i,arrow = False,solid = True);
+line(-2*i + 4,2*i + 1,-2*i + 6,2*i + 1,arrow = False,solid = True)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-60.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-49.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-49-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Rectangle(0,3,2,5)
-    for (2)
-        Circle(3*i + 4,1)
-        Circle(-2*i + 7,-3*i + 7)
-        Line(5,3,-3*i + 7,2,arrow = True,solid = True)
-        Line(4*i + 2,3*i + 4,4,4,arrow = True,solid = True)
+for (i < 3){
+if (i > 0){
+rectangle(-3*i + 10,i + -1,-3*i + 12,2);
+rectangle(0,-7*i + 14,3,-7*i + 17)
+}rectangle(1,4,2,6)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-16.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-51.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-51-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Circle(9,1)
-    for (3)
-        Circle(2*i + 3,-3*i + 10)
-        Circle(-2*i + 5,3*i + 1)
-        Line(2*i + 2,-3*i + 7,2*i + 3,-3*i + 9,arrow = False,solid = True)
-        Line(-2*i + 7,3*i + 3,-2*i + 8,3*i + 1,arrow = False,solid = True)
+for (i < 3){
+rectangle(2*i,2*i,2*i + 3,2*i + 1)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-13.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-52.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-52-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(5,0,3,0,arrow = True,solid = True)
-  Line(0,3,2,3,arrow = True,solid = True)
-  Line(3,2,1,2,arrow = True,solid = True)
-  Line(2,1,4,1,arrow = True,solid = True)
+circle(4,10);
+for (i < 3){
+circle(3*i + 1,5);
+circle(3*i + 1,1);
+line(4,9,3*i + 1,6,arrow = True,solid = True);
+line(3*i + 1,4,3*i + 1,2,arrow = True,solid = True)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-47.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-53.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-53-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-      reflect(y = 11)
-      Rectangle(4,9,7,10)
-            reflect(x = 11)
-            Rectangle(8,0,11,3)
-            Rectangle(1,4,2,7)
+line(6,8,6,4,arrow = True,solid = True);
+line(0,8,8,8,arrow = False,solid = True);
+line(4,8,4,0,arrow = True,solid = True);
+line(2,8,2,6,arrow = True,solid = True)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-5.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-54.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-54-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(12,9,12,0,arrow = True,solid = True)
-    for (2)
-        Rectangle(-3*i + 6,3*i + 5,-3*i + 8,9)
-        Rectangle(9*i,-4*i + 7,9*i + 2,9)
+line(2,3,2,5,arrow = False,solid = True);
+rectangle(0,0,4,8);
+reflect(reflect(y = 8)){
+rectangle(1,5,3,7)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-59.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-55.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-55-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(4,0,0,0,arrow = False,solid = False)
+circle(1,5);
+line(1,4,1,2,arrow = True,solid = True);
+rectangle(0,0,2,2)
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-50.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-57.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-57-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(8,3,9,3,arrow = False,solid = True)
-    for (2)
-        Line(-6*i + 8,3*i + 3,-3*i + 7,3,arrow = True,solid = True)
-        Line(5*i + 2,3*i + 1,5*i + 4,3,arrow = True,solid = True)
-        Rectangle(9*i,2*i,10*i + 2,3*i + 2)
-        Rectangle(-4*i + 4,3*i + 2,-5*i + 7,2*i + 5)
+for (i < 3){
+for (j < 3){
+circle(-4*i + 9,-3*j + 7)
+}
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
@@
 
-        \begin{tabular}{ll}
-\includegraphics[width = 5cm]{../TikZ/drawings/expert-6.png}&
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-58.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-58-parses/0.png}&
+
         \begin{minipage}{10cm}
         \begin{verbatim}
-  Line(0,1,0,4,arrow = False,solid = True)
-  Rectangle(2,0,5,3)
-    for (2)
-        Line(0,3*i + 1,2,3*i,arrow = False,solid = True)
-        Line(-3*i + 3,4,-2*i + 5,3,arrow = False,solid = True)
+for (i < 3){
+if (i > 0){
+line(8,0,8*i + -8,7*i + -7,arrow = True,solid = True)
+}rectangle(-2*i + 6,0,-2*i + 7,-1*i + 5)
+}
         \end{verbatim}
 \end{minipage}
+
     \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-59.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-59-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+line(4,0,0,0,arrow = False,solid = False)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-61.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-61-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+circle(2,1);
+circle(6,1);
+line(5,1,3,1,arrow = True,solid = True);
+rectangle(0,0,7,2)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-62.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-62-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+rectangle(5,0,8,3);
+rectangle(0,2,1,3);
+rectangle(2,1,4,3)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-63.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-63-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+for (i < 3){
+rectangle(i,i,-1*i + 5,-1*i + 5)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-64.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-64-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(reflect(x = 6)){
+line(5,2,5,4,arrow = False,solid = True);
+reflect(reflect(y = 6)){
+line(2,1,4,1,arrow = False,solid = True);
+rectangle(4,4,6,6)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-65.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-65-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(reflect(x = 6)){
+line(1,2,1,4,arrow = False,solid = True);
+reflect(reflect(y = 6)){
+circle(5,1);
+line(2,1,4,1,arrow = False,solid = True)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-66.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-66-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+for (i < 3){
+line(i,-1*i + 2,-1*i + 7,-1*i + 2,arrow = False,solid = True)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-67.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-67-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+line(1,4,5,0,arrow = False,solid = True);
+line(1,5,5,1,arrow = False,solid = True);
+rectangle(0,4,1,5);
+rectangle(5,0,6,1)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-68.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-68-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+for (i < 3){
+circle(4*i + 1,1);
+rectangle(4*i,0,4*i + 2,2)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-69.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-69-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+rectangle(0,4,5,6);
+reflect(reflect(x = 5)){
+circle(1,1);
+line(1,4,1,2,arrow = True,solid = True)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-70.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-70-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(reflect(x = 6)){
+circle(1,9);
+for (i < 3){
+if (i > 0){
+circle(-2*i + 7,-4*i + 9);
+line(5,-4*i + 12,-2*i + 7,-4*i + 10,arrow = True,solid = True)
+}line(1,8,4,5,arrow = True,solid = True)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-72.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-72-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(reflect(y = 8)){
+for (i < 3){
+if (i > 0){
+rectangle(3*i + -1,-3*i + 8,3*i,-3*i + 9)
+}circle(3*i + 1,-3*i + 7)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-74.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-74-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+for (i < 3){
+if (i > 0){
+rectangle(2*i + -2,2*i + -2,-2*i + 8,-2*i + 8)
+}for (j < 3){
+circle(2*j + 1,2*i + 1)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-75.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-75-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+for (i < 4){
+line(-4*i + 13,4,-4*i + 13,2,arrow = True,solid = True);
+for (j < 3){
+if (j > 0){
+circle(-4*i + 13,-4*j + 9)
+}line(-4*j + 10,5,-4*j + 12,5,arrow = True,solid = True)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-76.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-76-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+line(4,5,4,10,arrow = False,solid = True);
+reflect(reflect(x = 8)){
+circle(4,1);
+circle(1,8);
+line(4,5,8,2,arrow = False,solid = True)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-78.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-78-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+line(0,6,12,6,arrow = False,solid = True);
+line(8,3,7,4,arrow = True,solid = True);
+line(3,2,5,4,arrow = True,solid = True);
+line(6,6,6,5,arrow = True,solid = True);
+reflect(reflect(x = 12)){
+line(4,0,12,8,arrow = False,solid = True)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-81.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-81-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+circle(1,1);
+circle(4,1);
+rectangle(9,0,11,2);
+rectangle(6,0,8,2)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-85.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-85-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+for (i < 4){
+if (i > 0){
+line(1,-3*i + 12,1,-3*i + 11,arrow = True,solid = True)
+}circle(1,-3*i + 10)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-87.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-87-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(reflect(x = 8)){
+rectangle(0,0,1,1);
+rectangle(0,5,3,8);
+rectangle(0,2,2,4)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-88.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-88-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+for (i < 3){
+rectangle(2*i,i,-1*i + 8,-2*i + 7)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-90.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-90-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+circle(6,2);
+line(6,6,6,3,arrow = True,solid = True);
+rectangle(4,0,8,9);
+for (i < 3){
+if (i > 0){
+line(-5*i + 15,7,-5*i + 12,7,arrow = True,solid = True)
+}circle(-5*i + 11,7)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-91.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-91-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(reflect(y = 5)){
+reflect(reflect(x = 5)){
+line(0,0,2,0,arrow = False,solid = True);
+line(0,0,0,2,arrow = False,solid = True)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-92.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-92-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(reflect(x = 14)){
+for (i < 3){
+circle(5,-4*i + 9);
+line(10,-4*i + 9,12,-4*i + 9,arrow = False,solid = True);
+rectangle(12,-4*i + 8,14,-4*i + 10)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-93.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-93-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(reflect(x = 10)){
+for (i < 3){
+if (i > 0){
+line(-4*i + 13,4*i + -2,-4*i + 9,4*i,arrow = True,solid = True)
+}circle(-4*i + 9,4*i + 1)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-94.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-94-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+line(0,2,12,2,arrow = False,solid = True);
+line(6,2,6,3,arrow = True,solid = True);
+reflect(reflect(x = 12)){
+line(0,0,9,9,arrow = False,solid = True);
+line(10,7,7,4,arrow = True,solid = True)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-95.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-95-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+circle(4,1);
+reflect(reflect(x = 8)){
+for (i < 3){
+if (i > 0){
+circle(1,-5*i + 16);
+line(1,10,6*i + -5,7,arrow = True,solid = True)
+}line(7,5,4,2,arrow = True,solid = True)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-96.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-96-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(reflect(x = 10)){
+circle(9,1);
+for (i < 4){
+circle(-2*i + 7,2*i + 3)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-97.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-97-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(reflect(x = 6)){
+for (i < 3){
+if (i > 0){
+line(1,-4*i + 10,1,-4*i + 12,arrow = False,solid = True)
+}circle(1,-4*i + 9);
+line(2,-4*i + 9,4,-4*i + 9,arrow = False,solid = True)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-98.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-98-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+rectangle(0,0,4,9);
+for (i < 3){
+if (i > 0){
+circle(2,-4*i + 10);
+line(2,-5*i + 15,2,-4*i + 11,arrow = True,solid = True)
+}circle(2,11)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-99.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-99-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+for (i < 2){
+circle(4,6*i + 1);
+circle(1,6*i + 4);
+rectangle(3,6*i + 3,5,6*i + 5);
+rectangle(0,6*i,2,6*i + 2)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}

### 2017-05-18 supplement.tex
better figure for multidimensional scaling result
including programs and parses in the supplement. it looks like I made some changes that made the synthesizer worse because it seems to be missing some programs I expected it to learn

@@
 
+\section{Full results on drawings data set}
+
+Below we show our full data set of drawings.
+The leftmost column is a hand drawing.
+The middle column is a rendering of the most likely trace discovered by the neurally guided SMC sampling scheme.
+The rightmost column is the program we synthesized from a ground truth execution trace of the drawing.
+\input{synthesizerOutputs.tex}
+
 \end{document}

### 2017-05-18 synthesizerOutputs.tex
including programs and parses in the supplement. it looks like I made some changes that made the synthesizer worse because it seems to be missing some programs I expected it to learn

@@
 }
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-1.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-1-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
         \end{verbatim}
@@
             \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-5.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-5-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-6.png}&
@@
             \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-16.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-16-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-17.png}&
@@
             \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-18.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-18-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-19.png}&
@@
 rectangle(3,4,5,6)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-20.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-20-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
         \end{verbatim}
@@
             \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-34.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-34-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-35.png}&
@@
             \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-36.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-36-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-37.png}&
@@
 }
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-38.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-38-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-39.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-39-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
         \end{verbatim}
@@
             \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-50.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-50-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-51.png}&
@@
             \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-56.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-56-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-57.png}&
@@
 line(4,0,0,0,arrow = False,solid = False)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-60.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-60-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
         \end{verbatim}
@@
             \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-71.png}&
+            Sampled no finished traces.&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-72.png}&
@@
 }
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-73.png}&
+            Sampled no finished traces.&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
         \end{verbatim}
@@
             \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-77.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-77-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-78.png}&
@@
             \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-79.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-79-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-80.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-80-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-81.png}&
@@
             \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-82.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-82-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-83.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-83-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-84.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-84-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-85.png}&
@@
 }
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-86.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-86-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
         \end{verbatim}
@@
             \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-89.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-89-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-90.png}&
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-94.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-94-parses/0.png}&
+            Sampled no finished traces.&
 

### 2017-05-18 paper.tex
better extrapolation figure
shrunk figures to make them fit within the margins - they still look bad

@@
     \end{tikzpicture}\\
-    \texttt{for} $0\leq i < 4$:\\
-    \texttt{rectangle} $(-3i + 9,2i - 2, -3i + 11,6)$\\
-    \texttt{for} $0\leq j < i$:\\
-    \texttt{circle} $(3i-2,-2j+5)$\\
+    \begin{minipage}[t]{0.3\linewidth}
+\begin{verbatim}
+for (i < 3)
+ rectangle(3*i,-2*i + 4,
+           3*i + 2,6)
+ for (j < i + 1)
+  circle(3*i + 1,-2*j + 5)
+\end{verbatim}      
+      \end{minipage}
     \subcaption{}
@@
 synthesizes programs from execution traces,
-and how those programs are used for measuring similarity between hand drawings,
-extrapolating figures, and correcting errors made by the deep network.
+and how those programs are used for  correcting errors made by the deep network, measuring similarity between hand drawings,
+and extrapolating figures.
 
@@
 the image features, the \verb|circle| token, and the $x$ coordinate.
-\remark{There are some more details that are important to provide
-  about this architecture in the supplement: the
-  functional form(s) of the probability distributions over tokens, the
-  network layer sizes, which MLPs share parameters, etc.}
+See supplement for the full details of the architecture,
+which we implemented in Tensorflow.
+%% \remark{There are some more details that are important to provide
+%%   about this architecture in the supplement: the
+%%   functional form(s) of the probability distributions over tokens, the
+%%   network layer sizes, which MLPs share parameters, etc.}
 
@@
 We train the network by sampling execution traces $T$ and target
-images $I$ for randomly generated scenes~\remark{this process ought to be explained, perhaps in supplement if it is at all detailed}, and maximizing
+images $I$ for randomly generated scenes
+%~\remark{this process ought to be explained, perhaps in supplement if it is at all detailed},
+and maximizing
 (\ref{objective}) with respect to $\theta$ by gradient ascent.
@@
 In a sense, this model is like an autoregressive variant of AIR~\cite{eslami1603attend} without attention.
-~\remark{Somewhere (not necessarily here) you should probably cite the deep learning toolkit you used.}
 
@@
     \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-33-5.png}}\end{minipage}
-    \caption{Network is trained to infer execution traces for randomly generated figures like the two shown above.}\label{trainingData}
+    \caption{Network is trained to infer execution traces for randomly generated figures like the two shown above. See supplement for details of the training data generation.}\label{trainingData}
   \end{minipage}\hfill
@@
 for an image.
+Learning this prior over programs modestly improves our Top-1 accuracy from 57\% to \textbf{experiment is still running},
+but recall from Fig.~\ref{drawingIntersectionOverUnion}
+that the best improvement in accuracy we could possibly get is 65\%.
 
@@
 \begin{figure}
-  \begin{minipage}{0.4\textwidth}
-    \includegraphics[width = 3in]{figures/NMF.png}
+  \begin{minipage}{0.45\textwidth}
+    \includegraphics[width = 2in]{figures/NMF.png}
     \caption{NMF on features of the programs that were synthesized for each image.
@@
   \end{minipage}\hfill
-  \begin{minipage}{0.4\textwidth}
-    \includegraphics[width = 3in]{figures/imageSimilarity.png} 
+  \begin{minipage}{0.45\textwidth}
+    \includegraphics[width = 2in]{figures/imageSimilarity.png} 
     \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
@@
   \caption{Top: hand drawings. Bottom: extrapolations produced by
-running loops for extra iterations.}\label{extrapolationFigure}
+running loops for extra iterations. Rightmost pair is an illustrative failure case.}\label{extrapolationFigure}
   \end{figure}

### 2017-05-18 supplement.tex
shrunk figures to make them fit within the margins - they still look bad

@@
 
-We introduce noise into the rendering process by:
+We introduce noise into the \LaTeX~rendering process by:
 
@@
   \end{itemize}
+
+\section{Generating synthetic training data}
+
+I need to describe the procedure that I used to sample the scenes. it's pretty involved
+
+\section{The cost function for programs}
+
+We seek the minimum cost program which evaluates to (produces the drawing primitives in) an execution trace $T$:
+\begin{equation}
+  \text{program}(T) = \argmin_{\substack{p\in \text{DSL}\\p \text{ evaluates to } T}} \text{cost}(p)\label{programObjective}
+\end{equation}
+
+Programs incur a cost of 1 for each command (primitive drawing action,
+loop, or reflection).  They incur a cost of $\frac{1}{3}$ for each
+unique coefficient they use in a linear transformation beyond the
+first coefficient. This encourages reuse of coefficients, which leads
+to code that has translational symmetry; rather than provide a
+translational symmetry operator as we did with reflection, we modify
+what is effectively a prior over the space of program so that it tends
+to produce programs that have this symmetry.
+
+Programs also incur a cost of 1 for having loops of constant length 2;
+otherwise there is often no pressure from the cost function to explain
+a repetition of length to as being a reflection rather a loop.
 

### 2017-05-19 paper.tex
very early results on using the program synthesis to improve the parsing

@@
 model by asking it to sample many candidate traces for each drawing.
-For 57\% of the drawings the Top-1 most likely sample exactly matches the
+For 58\% of the drawings the Top-1 most likely sample exactly matches the
 ground truth; as we consider more samples the model encounters traces
@@
 for an image.
-Learning this prior over programs modestly improves our Top-1 accuracy from 57\% to \textbf{experiment is still running},
-but recall from Fig.~\ref{drawingIntersectionOverUnion}
-that the best improvement in accuracy we could possibly get is 65\%.
+
+We synthesized programs for the top five traces
+output by the deep network.  Learning this prior over programs can
+help correct mistakes made by the neural network, and also
+occasionally introduces mistakes of its own; see
+Fig.~\ref{exampleOfProgramCorrectingMistake} for a representative
+example of the kinds of corrections that it makes. On the whole
+modestly improves our Top-1 accuracy from 58\% to 60\%.  Recall that
+from Fig.~\ref{drawingIntersectionOverUnion} that the best improvement
+in accuracy we could possibly get is 63\% by looking at the top 5 traces.
+\begin{wrapfigure}{R}{5.5cm}
+  \includegraphics[width = 5cm]{figures/programSuccess7.png}
+  \caption{Left: hand drawing. Center: interpretation favored by the deep network. Right: interpretation favored after learning a prior over programs.}\label{exampleOfProgramCorrectingMistake}
+  \end{wrapfigure}
 

### 2017-05-19 paper.tex
attention citation; improvements to supplement

@@
 See supplement for the full details of the architecture,
-which we implemented in Tensorflow.
+which we implemented in Tensorflow~\cite{tensorflow2015-whitepaper}.
 %% \remark{There are some more details that are important to provide
@@
 images $I$ for randomly generated scenes
-%~\remark{this process ought to be explained, perhaps in supplement if it is at all detailed},
 and maximizing
@@
 
+We trained the network on $10^5$ scenes, which takes a little less than a day on a Nvidia TitanX GPU.
+
 This network suffices to ``derender'' synthetic images like those shown in
@@
     \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-33-5.png}}\end{minipage}
-    \caption{Network is trained to infer execution traces for randomly generated figures like the two shown above. See supplement for details of the training data generation.}\label{trainingData}
+    \caption{Network is trained to infer execution traces for randomly generated scenes like the two shown above. See supplement for details of the training data generation.}\label{trainingData}
   \end{minipage}\hfill
@@
 tool~\cite{solar2008program}. Describing Sketch's program synthesis
-algorithm is beyond the scope of this paper; see supplement.  At a
+algorithm is beyond the scope of this paper; see~\cite{solar2008program}.  At a
 high level, Sketch takes as input a space of programs, along with a
@@
 example of the kinds of corrections that it makes. On the whole
-modestly improves our Top-1 accuracy from 58\% to 60\%.  Recall that
+it modestly improves our Top-1 accuracy from 58\% to 60\%.  Recall that
 from Fig.~\ref{drawingIntersectionOverUnion} that the best improvement
@@
 \begin{figure}
-  \begin{minipage}{0.45\textwidth}
-    \includegraphics[width = 2in]{figures/NMF.png}
+  \begin{minipage}{0.48\textwidth}
+    \includegraphics[width = \textwidth]{figures/NMF.png}
     \caption{NMF on features of the programs that were synthesized for each image.
@@
   \end{minipage}\hfill
-  \begin{minipage}{0.45\textwidth}
-    \includegraphics[width = 2in]{figures/imageSimilarity.png} 
+  \begin{minipage}{0.48\textwidth}
+    \includegraphics[width = \textwidth]{figures/imageSimilarity.png} 
     \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
@@
 The proposal network also currently handles only a very small subset of \LaTeX drawing commands, though there is no reason that it could not be extended to handle more with a higher-capacity network.
-Exploring more sophisticated network architectures, including ones that utilize attention, could also help correct some of the errors the network makes.
+Exploring more sophisticated network architectures, including ones that utilize attention~\cite{mnih2014recurrent}, could also help correct some of the errors the network makes.
 In the synthesis phase, a more expressive DSL---including subroutines, recursion, and symmetry groups beyond reflections---would allow the system to effectively model a wider variety of graphical phenomena.

### 2017-05-19 supplement.tex
attention citation; improvements to supplement

@@
 
+\section{Likelihood surrogate for synthetic data}
+For synthetic data (e.g., \LaTeX~output)
+it is relatively straightforward to engineer an adequate distance measure between images,
+because it is possible for the system to discover
+drawing commands that exactly match the pixels in the target image.
+We use:
+\begin{equation}
+  -\log L(I_1|I_2) = \sum_{1\leq x\leq 256} \sum_{1\leq y\leq 256} |I_1[x,y] - I_2[x,y]|\begin{cases}
+    \alpha\text{, if }$I_1[x,y] > I_2[x,y]$\\
+    \beta\text{, if }$I_1[x,y] <  I_2[x,y]$\\
+        0\text{, if }$I_1[x,y] = I_2[x,y]$\\
+    \end{cases}
+  \end{equation}
+where $\alpha$, $\beta$ are constants that control the trade-off
+between preferring to explain the pixels in the image (at the expense
+of having extraneous pixels) and not predicting pixels where they
+don't exist (at the expense of leaving some pixels unexplained). Because our sampling procedure incrementally constructs the scene part-by-part,
+we want $\alpha > \beta$.
+That is, it is preferable to leave some pixels unexplained;
+for once a particle in SMC adds a drawing primitive to its trace that is not actually in the latent scene,
+it can never recover from this error.
+In our experiments on synthetic data we used $\alpha = 0.8$ and $\beta = 0.04$. 
 \section{Generating synthetic training data}
 
-I need to describe the procedure that I used to sample the scenes. it's pretty involved
+We generated synthetic training data for the neural network by
+sampling \LaTeX~code according to the following generative process:
+First,
+the number of objects in the scene are sampled uniformly from 1 to 8.
+For each object we uniformly sample its identity (circle, rectangle, or line).
+Then we sample the parameters of the circles,
+than the parameters of the rectangles,
+and finally the parameters of the lines;
+this has the effect of teaching the network to first draw the circles in the scene,
+then the rectangles,
+and finally the lines.
+We furthermore put the circle (respectively, rectangle and line) drawing commands in order by
+left-to-right, bottom-to-top;
+thus the training data enforces a canonical order in which to draw any scene.
+
+To make the training data look more like naturally occurring figures,
+we put a Chinese restaurant process prior~\cite{gershman2012tutorial} over
+the values of the X and Y coordinates that occur in the execution trace.
+This encourages reuse of coordinate values,
+and so produces training data that tends to have parts that are nicely aligned.
+
+In the synthetic training data we excluded any sampled scenes that had
+overlapping drawing commands.  As shown in the main paper, the network
+is then able to generalize to scenes with, for example, intersecting
+lines or lines that penetrate a rectangle.
+
+When sampling the endpoints of a line,
+we biased the sampling process so that it would
+be more likely to start an endpoint
+along one of the sides of a rectangle or at the boundary of a circle.
+If $n$ is the number of points either along the side of a rectangle or at the boundary of a circle,
+we would sample an arbitrary endpoint with probability $\frac{2}{2 + n}$
+and sample one of the ``attaching'' endpoints with probability $\frac{1}{2 + n}$.
+
+See figure~\ref{exampleTrainingData} for examples of the kinds of scenes that the network is trained on.
+\begin{figure}
+  \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-58-7.png}}\end{minipage}
+  \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-33-5.png}}\end{minipage}
+  \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-4-4.png}}\end{minipage}
+  \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-26-7.png}}\end{minipage}
+      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-25-4.png}}\end{minipage}\\
+      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-22-3.png}}\end{minipage}
+      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-20-7.png}}\end{minipage}
+      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-19-3.png}}\end{minipage}
+      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-17-7.png}}\end{minipage}
+      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-1-4.png}}\end{minipage}
+      \caption{Example synthetic training data}\label{exampleTrainingData}
+\end{figure}
+
+For readers wishing to generate their own synthetic training sets,
+we refer them to our source code at:~\url{http://www.redactedForAnonymousReview.com}.
 
@@
 otherwise there is often no pressure from the cost function to explain
-a repetition of length to as being a reflection rather a loop.
+a repetition of length 2 as being a reflection rather a loop.
 

### 2017-05-19 synthesizerOutputs.tex
attention citation; improvements to supplement

@@
         \begin{verbatim}
-line(6,2,3,2,arrow = True,solid = True);
-line(6,2,6,3,arrow = False,solid = True);
+line(6,2,6,3,
+arrow = False,solid = True);
+line(6,2,3,2,
+arrow = True,solid = True);
+reflect(reflect(y = 9)){
+line(3,2,5,4,
+arrow = True,solid = True);
 rectangle(0,0,8,9);
 rectangle(5,3,7,6);
-reflect(reflect(y = 9)){
-line(3,2,5,4,arrow = True,solid = True);
-rectangle(1,6,3,8)
+rectangle(1,1,3,3)
 }
@@
 reflect(reflect(y = 7)){
-line(2,6,4,4,arrow = True,solid = True);
-rectangle(0,5,2,7)
+line(2,6,4,4,
+arrow = True,solid = True);
+rectangle(0,0,2,2)
 }
@@
 circle(10,5);
-line(7,5,9,5,arrow = True,solid = True);
+line(7,5,9,5,
+arrow = True,solid = True);
+rectangle(5,3,7,7);
 rectangle(0,0,12,10);
 reflect(reflect(y = 10)){
-line(3,8,5,6,arrow = True,solid = True);
-rectangle(1,1,3,3);
-rectangle(5,3,7,7)
+line(3,8,5,6,
+arrow = True,solid = True);
+rectangle(1,7,3,9)
 }
@@
 circle(10,4);
-line(10,1,10,3,arrow = False,solid = False);
-line(10,1,2,1,arrow = True,solid = False);
-line(7,4,9,4,arrow = True,solid = True);
+line(10,1,2,1,
+arrow = True,solid = False);
+line(10,1,10,3,
+arrow = False,solid = False);
+line(7,4,9,4,
+arrow = True,solid = True);
 reflect(reflect(y = 8)){
-line(2,1,4,3,arrow = True,solid = True);
-rectangle(0,6,2,8);
-rectangle(4,2,7,6)
+line(2,7,4,5,
+arrow = True,solid = True);
+rectangle(4,2,7,6);
+rectangle(0,6,2,8)
 }
@@
         \begin{verbatim}
-rectangle(2,0,5,3);
-for (i < 3){
-if (i > 0){
-line(0,3*i + -2,3*i + -3,4,arrow = False,solid = True);
-line(3*i + -3,4,3*i + -1,3,arrow = False,solid = True)
-}line(0,1,2,0,arrow = False,solid = True)
+line(0,1,2,0,
+arrow = False,solid = True);
+for (i < 3){
+if (i > 0){
+line(3*i + -3,4,3*i + -1,3,
+arrow = False,solid = True);
+line(0,3*i + -2,3*i + -3,4,
+arrow = False,solid = True)
+}
+rectangle(2,0,5,3)
 }
@@
 for (i < 3){
+circle(-3*i + 7,1);
 circle(-3*i + 7,6);
-circle(-3*i + 7,1);
-line(-3*i + 7,-1*i + 4,-3*i + 7,5,arrow = False,solid = True)
+line(-3*i + 7,-1*i + 4,-3*i + 7,5,
+arrow = False,solid = True)
 }
@@
         \begin{verbatim}
-line(0,0,0,4,arrow = False,solid = True)
+line(0,0,0,4,
+arrow = False,solid = True)
         \end{verbatim}
@@
         \begin{verbatim}
-line(6,0,0,0,arrow = True,solid = True)
+line(6,0,0,0,
+arrow = True,solid = True)
         \end{verbatim}
@@
         \begin{verbatim}
-line(2,1,5,1,arrow = False,solid = True);
+line(2,6,5,6,
+arrow = False,solid = True);
 reflect(reflect(x = 7)){
-circle(1,1);
-line(2,6,5,6,arrow = False,solid = True);
-line(1,2,1,5,arrow = False,solid = True);
-rectangle(0,5,2,7)
+circle(6,1);
+line(2,1,5,1,
+arrow = False,solid = True);
+line(1,2,1,5,
+arrow = False,solid = True);
+rectangle(5,5,7,7)
 }
@@
         \begin{verbatim}
-line(3,2,1,2,arrow = True,solid = True);
-line(5,0,3,0,arrow = True,solid = True);
-line(2,1,4,1,arrow = True,solid = True);
-line(0,3,2,3,arrow = True,solid = True)
+line(2,1,4,1,
+arrow = True,solid = True);
+line(3,2,1,2,
+arrow = True,solid = True);
+line(5,0,3,0,
+arrow = True,solid = True);
+line(0,3,2,3,
+arrow = True,solid = True)
         \end{verbatim}
@@
 if (i > 0){
-rectangle(2*i + -2,-2*i + 6,2*i + -1,-2*i + 7)
-}rectangle(2*i,-2*i + 6,2*i + 1,-2*i + 7)
+rectangle(-2*i + 6,2*i + -2,-2*i + 7,2*i + -1)
+}
+rectangle(-2*i + 6,2*i,-2*i + 7,2*i + 1)
 }
@@
         \begin{verbatim}
-line(0,3,2,3,arrow = False,solid = False);
-line(2,1,4,1,arrow = False,solid = False);
-line(1,2,3,2,arrow = False,solid = True);
-line(3,0,5,0,arrow = False,solid = True)
+line(0,3,2,3,
+arrow = False,solid = False);
+line(2,1,4,1,
+arrow = False,solid = False);
+line(1,2,3,2,
+arrow = False,solid = True);
+line(3,0,5,0,
+arrow = False,solid = True)
         \end{verbatim}
@@
         \begin{verbatim}
-Solver timeout
+for (i < 4){
+if (i > 0){
+circle(-2*i + 7,3*i + -2);
+line(-2*i + 9,3*i,-2*i + 10,3*i + -2,
+arrow = False,solid = True);
+line(-2*i + 8,3*i + -2,-2*i + 9,3*i,
+arrow = False,solid = True)
+}
+circle(-2*i + 9,3*i + 1)
+}
         \end{verbatim}
@@
 if (i > 0){
-line(-2*i + 9,3*i,-2*i + 10,3*i + -2,arrow = True,solid = True);
-line(-2*i + 9,3*i,-2*i + 8,3*i + -2,arrow = True,solid = True);
-rectangle(-2*i + 6,3*i + -3,-2*i + 8,3*i + -1)
-}rectangle(-2*i + 8,3*i,-2*i + 10,3*i + 2)
+line(2*i + 1,-3*i + 12,2*i,-3*i + 10,
+arrow = True,solid = True);
+line(2*i + 1,-3*i + 12,2*i + 2,-3*i + 10,
+arrow = True,solid = True);
+rectangle(2*i + -2,-3*i + 9,2*i,-3*i + 11)
+}
+rectangle(2*i + 2,-3*i + 9,2*i + 4,-3*i + 11)
 }
@@
         \begin{verbatim}
-Solver timeout
+circle(5,1);
+for (i < 3){
+if (i > 0){
+circle(7,2*i + -1);
+circle(i + 2,2*i + 1)
+}
+circle(1,6)
+}
         \end{verbatim}
@@
         \begin{verbatim}
-line(4,4,2,2,arrow = True,solid = True);
-rectangle(0,0,2,2);
-rectangle(3,4,5,6)
+line(4,4,2,2,
+arrow = True,solid = True);
+rectangle(3,4,5,6);
+rectangle(0,0,2,2)
         \end{verbatim}
@@
         \begin{verbatim}
-Solver timeout
+rectangle(0,4,2,6);
+for (i < 3){
+if (i > 0){
+line(-4*i + 12,5,-4*i + 10,5,
+arrow = True,solid = True);
+for (j < i + 1){
+circle(-4*j + 9,-4*i + 9)
+}
+}
+line(-4*i + 9,4,-4*i + 9,2,
+arrow = True,solid = True)
+}
         \end{verbatim}
@@
         \begin{verbatim}
-circle(1,5);
-for (i < 3){
-if (i > 0){
-line(-4*i + 12,1,-4*i + 10,1,arrow = True,solid = True);
-rectangle(-4*i + 12,4,-4*i + 14,6)
-}line(-4*i + 9,2,-4*i + 9,4,arrow = True,solid = True);
-rectangle(-4*i + 8,0,-4*i + 10,2)
-}
+Solver timeout
         \end{verbatim}
@@
 for (i < 3){
-if (i > 0){
-line(4*i,5,4*i + -2,5,arrow = True,solid = True)
-}line(4*i + 1,4,4*i + 1,2,arrow = True,solid = True);
-rectangle(4*i,0,4*i + 2,2);
-rectangle(4*i,4,4*i + 2,6)
+line(-4*i + 9,4,-4*i + 9,2,
+arrow = True,solid = True);
+for (j < 2){
+line(-4*j + 8,5,-4*j + 6,5,
+arrow = True,solid = True);
+rectangle(-4*i + 8,4*j,-4*i + 10,4*j + 2)
+}
 }
@@
 for (i < 3){
-line(-4*i + 9,2,-4*i + 9,4,arrow = True,solid = True);
-for (j < 2){
-circle(-4*i + 9,4*j + 1);
-line(-4*j + 8,1,-4*j + 6,1,arrow = True,solid = True)
-}
+if (i > 0){
+line(-4*i + 12,1,-4*i + 10,1,
+arrow = True,solid = True)
+}
+circle(-4*i + 9,1);
+circle(-4*i + 9,5);
+line(-4*i + 9,2,-4*i + 9,4,
+arrow = True,solid = True)
 }
@@
 if (i > 0){
-line(-2*i + 7,-4*i + 11,-2*i + 7,-4*i + 10,arrow = True,solid = True);
+line(-2*i + 7,-4*i + 11,-2*i + 7,-4*i + 10,
+arrow = True,solid = True);
 rectangle(0,-4*i + 11,6,-3*i + 12)
-}rectangle(2,0,4,2)
+}
+rectangle(2,0,4,2)
 }
@@
 if (i > 0){
-line(-3*i + 9,1,-3*i + 8,1,arrow = True,solid = True)
-}rectangle(-3*i + 6,0,-3*i + 8,2)
+line(3*i,1,3*i + -1,1,
+arrow = True,solid = True)
+}
+rectangle(3*i,0,3*i + 2,2)
 }
@@
         \begin{verbatim}
-line(1,3,1,4,arrow = False,solid = True);
-for (i < 3){
-if (i > 0){
-line(1,-5*i + 13,1,-4*i + 10,arrow = True,solid = True)
-}circle(1,-4*i + 9)
+line(1,3,1,4,
+arrow = False,solid = True);
+for (i < 3){
+if (i > 0){
+line(1,-5*i + 13,1,-4*i + 10,
+arrow = True,solid = True)
+}
+circle(1,-4*i + 9)
 }
@@
 reflect(reflect(x = 2)){
-line(0,1,1,2,arrow = False,solid = True);
-line(1,0,2,1,arrow = False,solid = True)
+line(0,1,1,2,
+arrow = False,solid = True);
+line(1,0,2,1,
+arrow = False,solid = True)
 }
@@
         \begin{verbatim}
-line(0,2,2,2,arrow = False,solid = True);
-line(0,0,0,2,arrow = False,solid = True)
+line(0,0,0,2,
+arrow = False,solid = True);
+line(0,2,2,2,
+arrow = False,solid = True)
         \end{verbatim}
@@
 for (i < 3){
-line(-1*i + 2,i + 4,-2*i + 6,i + 4,arrow = False,solid = True);
-line(-1*i + 2,2*i,-1*i + 2,i + 4,arrow = False,solid = True)
+line(i,-1*i + 6,2*i + 2,-1*i + 6,
+arrow = False,solid = True);
+line(i,-2*i + 4,i,-1*i + 6,
+arrow = False,solid = True)
 }
@@
 if (i > 0){
-circle(5,2*i);
 circle(1,-3*i + 7);
+circle(5,-2*i + 6);
 rectangle(0,-3*i + 6,2,-3*i + 8)
-}rectangle(4,1,6,5)
+}
+rectangle(4,1,6,5)
 }
@@
 circle(5,5);
-line(2,5,4,5,arrow = False,solid = True);
+line(2,5,4,5,
+arrow = False,solid = True);
 rectangle(0,0,5,3);
@@
         \begin{verbatim}
-line(0,0,6,0,arrow = False,solid = False);
-line(0,3,6,3,arrow = False,solid = False);
-line(6,0,6,3,arrow = False,solid = True);
-line(0,0,0,3,arrow = False,solid = True)
+line(0,0,6,0,
+arrow = False,solid = False);
+reflect(reflect(x = 6)){
+line(6,0,6,3,
+arrow = False,solid = True);
+line(0,3,6,3,
+arrow = False,solid = False)
+}
         \end{verbatim}
@@
 if (i > 0){
-circle(5*i + -4,1);
-line(i,i + 4,5*i + -4,2,arrow = True,solid = True)
-}circle(1,6)
+circle(-5*i + 11,1);
+line(-1*i + 3,-1*i + 7,-5*i + 11,2,
+arrow = True,solid = True)
+}
+circle(1,6)
 }
@@
 if (i > 0){
-line(-4*i + 9,5*i + -3,-2*i + 7,5,arrow = False,solid = True);
-rectangle(-4*i + 8,5*i + -5,6,7*i + -5)
-}circle(1,8)
+line(4*i + -3,-5*i + 12,2*i + 1,5,
+arrow = False,solid = True);
+rectangle(4*i + -4,-5*i + 10,6,-7*i + 16)
+}
+circle(1,8)
 }
@@
 for (i < 3){
-circle(3*i + 1,1)
+circle(-3*i + 7,1)
 }
@@
 for (i < 3){
-rectangle(2*i,0,2*i + 1,6)
+rectangle(-2*i + 4,0,-2*i + 5,6)
 }
@@
         \begin{verbatim}
-line(0,0,0,5,arrow = False,solid = False);
-line(4,1,4,5,arrow = False,solid = False);
-line(4,0,4,1,arrow = False,solid = False)
+line(4,0,4,1,
+arrow = False,solid = False);
+line(0,0,0,5,
+arrow = False,solid = False);
+line(4,1,4,5,
+arrow = False,solid = False)
         \end{verbatim}
@@
         \begin{verbatim}
-line(0,0,0,5,arrow = False,solid = True);
-line(4,0,4,5,arrow = False,solid = True)
+line(4,0,4,5,
+arrow = False,solid = True);
+line(0,0,0,5,
+arrow = False,solid = True)
         \end{verbatim}
@@
 circle(4,1);
-line(9,1,10,1,arrow = False,solid = True);
-rectangle(10,0,12,2)
+line(9,1,10,1,
+arrow = False,solid = True);
+rectangle(0,0,2,2)
 }
@@
         \begin{verbatim}
-line(4,6,6,6,arrow = True,solid = True);
 rectangle(0,4,4,8);
@@
 circle(7,6);
-line(2,10,2,8,arrow = True,solid = True);
-rectangle(1,0,3,2)
+line(2,2,2,4,
+arrow = True,solid = True);
+line(4,6,6,6,
+arrow = True,solid = True);
+rectangle(1,10,3,12)
 }
@@
         \begin{verbatim}
+reflect(reflect(y = 9)){
+line(3,8,6,8,
+arrow = False,solid = True);
 reflect(reflect(x = 9)){
-line(1,3,1,6,arrow = False,solid = True);
-reflect(reflect(y = 9)){
 circle(1,8);
-line(3,1,6,1,arrow = False,solid = True)
+line(1,3,1,6,
+arrow = False,solid = True)
 }
@@
 reflect(reflect(y = 11)){
-rectangle(4,1,7,2);
+rectangle(4,9,7,10);
 reflect(reflect(x = 11)){
 rectangle(1,4,2,7);
-rectangle(0,8,3,11)
+rectangle(8,8,11,11)
 }
@@
         \begin{verbatim}
-for (i < 3){
-line(-2*i + 5,2*i,-2*i + 7,2*i,arrow = False,solid = True);
-line(-2*i + 4,2*i + 1,-2*i + 6,2*i + 1,arrow = False,solid = True)
+for (i < 4){
+line(i,-1*i + 5,i + 2,-1*i + 5,
+arrow = False,solid = True);
+line(i + 2,-1*i + 3,i + 4,-1*i + 3,
+arrow = False,solid = True)
 }
@@
 if (i > 0){
-rectangle(-3*i + 10,i + -1,-3*i + 12,2);
-rectangle(0,-7*i + 14,3,-7*i + 17)
-}rectangle(1,4,2,6)
+rectangle(3*i + 1,-1*i + 2,3*i + 3,2);
+rectangle(0,7*i + -7,3,7*i + -4)
+}
+rectangle(1,4,2,6)
 }
@@
 for (i < 3){
-rectangle(2*i,2*i,2*i + 3,2*i + 1)
+rectangle(-2*i + 4,-2*i + 4,-2*i + 7,-2*i + 5)
 }
@@
 for (i < 3){
-circle(3*i + 1,5);
-circle(3*i + 1,1);
-line(4,9,3*i + 1,6,arrow = True,solid = True);
-line(3*i + 1,4,3*i + 1,2,arrow = True,solid = True)
+circle(-3*i + 7,5);
+circle(-3*i + 7,1);
+line(-3*i + 7,4,-3*i + 7,2,
+arrow = True,solid = True);
+line(4,9,-3*i + 7,6,
+arrow = True,solid = True)
 }
@@
         \begin{verbatim}
-line(6,8,6,4,arrow = True,solid = True);
-line(0,8,8,8,arrow = False,solid = True);
-line(4,8,4,0,arrow = True,solid = True);
-line(2,8,2,6,arrow = True,solid = True)
+line(2,8,2,6,
+arrow = True,solid = True);
+line(6,8,6,4,
+arrow = True,solid = True);
+line(4,8,4,0,
+arrow = True,solid = True);
+line(0,8,8,8,
+arrow = False,solid = True)
         \end{verbatim}
@@
         \begin{verbatim}
-line(2,3,2,5,arrow = False,solid = True);
-rectangle(0,0,4,8);
-reflect(reflect(y = 8)){
-rectangle(1,5,3,7)
-}
+line(2,3,2,5,
+arrow = False,solid = True);
+rectangle(1,1,3,3);
+rectangle(1,5,3,7);
+rectangle(0,0,4,8)
         \end{verbatim}
@@
 circle(1,5);
-line(1,4,1,2,arrow = True,solid = True);
+line(1,4,1,2,
+arrow = True,solid = True);
 rectangle(0,0,2,2)
@@
 for (j < 3){
-circle(-4*i + 9,-3*j + 7)
+circle(-4*j + 9,-3*i + 7)
 }
@@
 if (i > 0){
-line(8,0,8*i + -8,7*i + -7,arrow = True,solid = True)
-}rectangle(-2*i + 6,0,-2*i + 7,-1*i + 5)
+line(8,0,8*i + -8,7*i + -7,
+arrow = True,solid = True)
+}
+rectangle(2*i + 2,0,2*i + 3,i + 3)
 }
@@
         \begin{verbatim}
-line(4,0,0,0,arrow = False,solid = False)
+line(4,0,0,0,
+arrow = False,solid = False)
         \end{verbatim}
@@
 circle(6,1);
-line(5,1,3,1,arrow = True,solid = True);
+line(5,1,3,1,
+arrow = True,solid = True);
 rectangle(0,0,7,2)
@@
 rectangle(5,0,8,3);
-rectangle(0,2,1,3);
-rectangle(2,1,4,3)
+rectangle(2,1,4,3);
+rectangle(0,2,1,3)
         \end{verbatim}
@@
 for (i < 3){
-rectangle(i,i,-1*i + 5,-1*i + 5)
+rectangle(-1*i + 2,-1*i + 2,i + 3,i + 3)
 }
@@
 reflect(reflect(x = 6)){
-line(5,2,5,4,arrow = False,solid = True);
+line(5,2,5,4,
+arrow = False,solid = True);
 reflect(reflect(y = 6)){
-line(2,1,4,1,arrow = False,solid = True);
+line(2,1,4,1,
+arrow = False,solid = True);
 rectangle(4,4,6,6)
@@
         \begin{verbatim}
+reflect(reflect(y = 6)){
+line(2,5,4,5,
+arrow = False,solid = True);
 reflect(reflect(x = 6)){
-line(1,2,1,4,arrow = False,solid = True);
-reflect(reflect(y = 6)){
-circle(5,1);
-line(2,1,4,1,arrow = False,solid = True)
+circle(5,5);
+line(1,2,1,4,
+arrow = False,solid = True)
 }
@@
 for (i < 3){
-line(i,-1*i + 2,-1*i + 7,-1*i + 2,arrow = False,solid = True)
+line(i,-1*i + 2,-1*i + 7,-1*i + 2,
+arrow = False,solid = True)
 }
@@
         \begin{verbatim}
-line(1,4,5,0,arrow = False,solid = True);
-line(1,5,5,1,arrow = False,solid = True);
-rectangle(0,4,1,5);
-rectangle(5,0,6,1)
+line(1,4,5,0,
+arrow = False,solid = True);
+line(1,5,5,1,
+arrow = False,solid = True);
+rectangle(5,0,6,1);
+rectangle(0,4,1,5)
         \end{verbatim}
@@
         \begin{verbatim}
-rectangle(0,4,5,6);
 reflect(reflect(x = 5)){
 circle(1,1);
-line(1,4,1,2,arrow = True,solid = True)
+line(4,4,4,2,
+arrow = True,solid = True);
+rectangle(0,4,5,6)
 }
@@
         \begin{verbatim}
-reflect(reflect(x = 6)){
-circle(1,9);
-for (i < 3){
-if (i > 0){
-circle(-2*i + 7,-4*i + 9);
-line(5,-4*i + 12,-2*i + 7,-4*i + 10,arrow = True,solid = True)
-}line(1,8,4,5,arrow = True,solid = True)
-}
-}
+Solver timeout
         \end{verbatim}
@@
 if (i > 0){
-rectangle(3*i + -1,-3*i + 8,3*i,-3*i + 9)
-}circle(3*i + 1,-3*i + 7)
+rectangle(3*i + -1,2,3*i,3)
+}
+circle(3*i + 1,3*i + 1)
 }
@@
 if (i > 0){
-rectangle(2*i + -2,2*i + -2,-2*i + 8,-2*i + 8)
-}for (j < 3){
-circle(2*j + 1,2*i + 1)
+rectangle(-2*i + 4,-2*i + 4,2*i + 2,2*i + 2)
+}
+for (j < 3){
+circle(-2*i + 5,2*j + 1)
 }
@@
 for (i < 4){
-line(-4*i + 13,4,-4*i + 13,2,arrow = True,solid = True);
+line(-4*i + 13,4,-4*i + 13,2,
+arrow = True,solid = True);
 for (j < 3){
 if (j > 0){
-circle(-4*i + 13,-4*j + 9)
-}line(-4*j + 10,5,-4*j + 12,5,arrow = True,solid = True)
+circle(-4*i + 13,4*j + -3)
+}
+line(-4*j + 10,5,-4*j + 12,5,
+arrow = True,solid = True)
 }
@@
         \begin{verbatim}
-line(4,5,4,10,arrow = False,solid = True);
+circle(4,1);
 reflect(reflect(x = 8)){
-circle(4,1);
 circle(1,8);
-line(4,5,8,2,arrow = False,solid = True)
+line(4,5,8,2,
+arrow = False,solid = True);
+line(4,5,4,10,
+arrow = False,solid = True)
 }
@@
         \begin{verbatim}
-line(0,6,12,6,arrow = False,solid = True);
-line(8,3,7,4,arrow = True,solid = True);
-line(3,2,5,4,arrow = True,solid = True);
-line(6,6,6,5,arrow = True,solid = True);
+line(0,6,12,6,
+arrow = False,solid = True);
+line(6,6,6,5,
+arrow = True,solid = True);
+line(8,3,7,4,
+arrow = True,solid = True);
+line(3,2,5,4,
+arrow = True,solid = True);
 reflect(reflect(x = 12)){
-line(4,0,12,8,arrow = False,solid = True)
+line(4,0,12,8,
+arrow = False,solid = True)
 }
@@
 if (i > 0){
-line(1,-3*i + 12,1,-3*i + 11,arrow = True,solid = True)
-}circle(1,-3*i + 10)
+line(1,-3*i + 12,1,-3*i + 11,
+arrow = True,solid = True)
+}
+circle(1,-3*i + 10)
 }
@@
 reflect(reflect(x = 8)){
-rectangle(0,0,1,1);
 rectangle(0,5,3,8);
-rectangle(0,2,2,4)
+rectangle(0,2,2,4);
+rectangle(0,0,1,1)
 }
@@
 for (i < 3){
-rectangle(2*i,i,-1*i + 8,-2*i + 7)
+rectangle(-2*i + 4,-1*i + 2,i + 6,2*i + 3)
 }
@@
         \begin{verbatim}
-circle(6,2);
-line(6,6,6,3,arrow = True,solid = True);
-rectangle(4,0,8,9);
-for (i < 3){
-if (i > 0){
-line(-5*i + 15,7,-5*i + 12,7,arrow = True,solid = True)
-}circle(-5*i + 11,7)
+line(6,6,6,3,
+arrow = True,solid = True);
+for (i < 3){
+if (i > 0){
+circle(-5*i + 16,7);
+circle(-5*i + 11,5*i + -3);
+line(-5*i + 15,7,-5*i + 12,7,
+arrow = True,solid = True)
+}
+rectangle(4,0,8,9)
 }
@@
         \begin{verbatim}
+reflect(reflect(x = 5)){
 reflect(reflect(y = 5)){
-reflect(reflect(x = 5)){
-line(0,0,2,0,arrow = False,solid = True);
-line(0,0,0,2,arrow = False,solid = True)
+line(5,3,5,5,
+arrow = False,solid = True);
+line(3,5,5,5,
+arrow = False,solid = True)
 }
@@
 for (i < 3){
-circle(5,-4*i + 9);
-line(10,-4*i + 9,12,-4*i + 9,arrow = False,solid = True);
-rectangle(12,-4*i + 8,14,-4*i + 10)
+circle(9,-4*i + 9);
+line(10,-4*i + 9,12,-4*i + 9,
+arrow = False,solid = True);
+rectangle(0,-4*i + 8,2,-4*i + 10)
 }
@@
 if (i > 0){
-line(-4*i + 13,4*i + -2,-4*i + 9,4*i,arrow = True,solid = True)
-}circle(-4*i + 9,4*i + 1)
+line(4*i + -3,4*i + -2,4*i + 1,4*i,
+arrow = True,solid = True)
+}
+circle(4*i + 1,4*i + 1)
 }
@@
         \begin{verbatim}
-line(0,2,12,2,arrow = False,solid = True);
-line(6,2,6,3,arrow = True,solid = True);
+line(0,2,12,2,
+arrow = False,solid = True);
+line(6,2,6,3,
+arrow = True,solid = True);
 reflect(reflect(x = 12)){
-line(0,0,9,9,arrow = False,solid = True);
-line(10,7,7,4,arrow = True,solid = True)
+line(0,0,9,9,
+arrow = False,solid = True);
+line(10,7,7,4,
+arrow = True,solid = True)
 }
@@
         \begin{verbatim}
+reflect(reflect(x = 8)){
 circle(4,1);
-reflect(reflect(x = 8)){
-for (i < 3){
-if (i > 0){
-circle(1,-5*i + 16);
-line(1,10,6*i + -5,7,arrow = True,solid = True)
-}line(7,5,4,2,arrow = True,solid = True)
+for (i < 3){
+if (i > 0){
+circle(7,-5*i + 16);
+line(-6*i + 13,10,7,7,
+arrow = True,solid = True)
+}
+line(1,5,4,2,
+arrow = True,solid = True)
 }
@@
 reflect(reflect(x = 10)){
-circle(9,1);
+circle(1,1);
 for (i < 4){
@@
 if (i > 0){
-line(1,-4*i + 10,1,-4*i + 12,arrow = False,solid = True)
-}circle(1,-4*i + 9);
-line(2,-4*i + 9,4,-4*i + 9,arrow = False,solid = True)
+line(1,-4*i + 10,1,-4*i + 12,
+arrow = False,solid = True)
+}
+circle(5,-4*i + 9);
+line(2,-4*i + 9,4,-4*i + 9,
+arrow = False,solid = True)
 }
@@
 circle(2,-4*i + 10);
-line(2,-5*i + 15,2,-4*i + 11,arrow = True,solid = True)
-}circle(2,11)
+line(2,-5*i + 15,2,-4*i + 11,
+arrow = True,solid = True)
+}
+circle(2,11)
 }
@@
 for (i < 2){
-circle(4,6*i + 1);
-circle(1,6*i + 4);
-rectangle(3,6*i + 3,5,6*i + 5);
-rectangle(0,6*i,2,6*i + 2)
-}
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}
+circle(4,-6*i + 7);
+circle(1,-6*i + 10);
+rectangle(0,-6*i + 6,2,-6*i + 8);
+rectangle(3,-6*i + 9,5,-6*i + 11)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}

### 2017-05-19 paper.tex
added caption

@@
 \end{equation}
-where $|T|$ is the length of execution trace $T$, and the \verb|STOP|
+where $|T|$ is the length of execution trace $T$, and the subscripts
+on $T$ index drawing commands within the trace, and the \verb|STOP|
 token is emitted by the network to signal that the execution trace
-explains the image.~\remark{Make explicit that a $T_n$ in Equation 2 is a concise way of referring to a sequence of tokens from Equation 1?}
+explains the image.
+%% ~\remark{Make explicit that a $T_n$ in Equation 2
+%%   is a concise way of referring to a sequence of tokens from Equation
+%%   1?}
 
@@
 
-Concretely, we implemented the following scheme: the neurally guided sampling scheme of section~\ref{neuralNetworkSection} for image $I$ samples candidate traces $\mathcal{F}(I)$.
+Concretely, we implemented the following scheme: for an image $I$, the neurally guided sampling scheme of section~\ref{neuralNetworkSection} samples a set of candidate traces, written $\mathcal{F}(I)$.
 Instead of predicting the most likely trace in $\mathcal{F}(I)$ according to the neural network,
@@
 \begin{equation}
-\hat{T}(I) = \argmax_{T\in \mathcal{F}(I)} L_{\text{learned}}(I | \text{render}(T)) \times\probability_{\beta} [ \text{program}(T)] 
+\hat{T}(I) = \argmax_{T\in \mathcal{F}(I)} L_{\text{learned}}(I | \text{render}(T))\times \probability_\theta[T|I] \times\probability_{\beta} [ \text{program}(T)] 
 \end{equation}
@@
 from $\probability_{\beta} [\cdot]$, then the program is executed deterministically,
-and then we observe a noisy version of the program's output, where $L$
-is the noise model.
+and then we observe a noisy version of the program's output, where $L_\text{learned}(I|\text{render}(\cdot))\times\probability_\theta[\cdot|I]$
+is our observation model.
 
@@
 \begin{equation}
-  \beta^* = \argmax_{\beta} \expect \left[ \log \frac{\probability_{\beta} [\text{program}(T)]\times L_{\text{learned}}(I|\text{render}(T))}{\sum_{T'\in \mathcal{F}(I)} \probability_{\beta} [\text{program}(T')]\times L_{\text{learned}}(I|\text{render}(T'))} \right]
+  \beta^* = \argmax_{\beta} \expect \left[ \log \frac{\probability_{\beta} [\text{program}(T)]\times L_{\text{learned}}(I|\text{render}(T))\times \probability_\theta[T|I]}{\sum_{T'\in \mathcal{F}(I)} \probability_{\beta} [\text{program}(T')]\times L_{\text{learned}}(I|\text{render}(T'))\times \probability_\theta[T'|I]} \right]
 \end{equation}
@@
   \includegraphics[width = 5cm]{figures/programSuccess7.png}
-  \caption{Left: hand drawing. Center: interpretation favored by the deep network. Right: interpretation favored after learning a prior over programs.}\label{exampleOfProgramCorrectingMistake}
+  \caption{Left: hand drawing.
+Center: interpretation favored by the deep network.
+Right: interpretation favored after learning a prior over programs.
+Our learned prior favors shorter, simpler programs, thus continuing the pattern of not having an arrow is preferred.}\label{exampleOfProgramCorrectingMistake}
   \end{wrapfigure}

### 2017-05-19 paper.tex
lots of changes and now it needs to be smaller

@@
  The graphics programs in our domain draw simple figures like those found in
- machine learning papers (see Figure~\ref{firstPageExamples}).
+ machine learning papers (see Figure~\ref{firstPageExamples}a).
  %% \remark{The use of `graphics programs / visual programs' in the paper
@@
     \begin{minipage}[t]{0.3\linewidth}
-\begin{verbatim}
+\begin{Verbatim}
 for (i < 3)
- rectangle(3*i,-2*i + 4,
-           3*i + 2,6)
+ rectangle(3*i,-2*i+4,
+           3*i+2,6)
  for (j < i + 1)
-  circle(3*i + 1,-2*j + 5)
-\end{verbatim}      
+  circle(3*i+1,-2*j+5)
+\end{Verbatim}      
       \end{minipage}
@@
 
-High dimensional perceptual input may seem ill matched to the abstract
-semantics of a programming language. But programs with constructs such as
-recursion or iteration produce a simpler \emph{execution trace} of
-primitive actions; for our domain, the primitive actions are drawing
-commands. Our hypothesis is that the execution trace of the program is
-better aligned with the perceptual input, and that the trace can act
-as a kind of bridge between perception and programs. We test this
-hypothesis by developing a model that learns to map from an image to
-the execution trace of the graphics program that drew it.  With the
-execution trace in hand, we can bring to bear techniques from the
-program synthesis community to recover the latent graphics program.
-This family of techniques, called \emph{constraint-based program synthesis}~\cite{solar2008program},
-work by modeling a set of possible programs inside of a constraint solver,
-such as a SAT or SMT solver~\cite{de2008z3}.
-These techniques excel at uncovering high-level symbolic structure,
-but are not well equipped to deal with real-valued perceptual inputs.
+The key observation behind our work is that generating a programmatic representation from an image of a diagram actually involves two distinct steps that require different technical approaches.
+The first step involves identifying the components such as boxes, lines and arrows that make up the image.
+The second step involves identifying the high-level structure in how the components were drawn; for example, in Figure 1(b), it means identifying that there is a pattern in how the circles and rectangles are being drawn that is best described with two nested loops, and which can easily be extrapolated to a bigger diagram.
 
-We develop a hybrid architecture for inferring graphics programs.  Our
-approach uses a deep neural network infer an execution trace from an
-image; this network recovers primitive drawing operations such as
-lines, circles, or arrows, along with their parameters. For added
-robustness, we use the deep network as a proposal distribution for a
-stochastic search over execution traces.
+We present a hybrid architecture for inferring graphics programs that is structured around these two steps.
+For the first step, our approach uses a deep neural network to infer a sequence of primitive shape-drawing commands that can generate an image similar to the observed image.
+We refer to this sequence as a \emph{program trace}, since it corresponds to the sequence of primitive commands that the desired program would have issued, but it lacks the high-level structure that determines how the program decided to issue those commands.
+For added robustness, we train the network to produce a proposal distribution of the most likely traces, and use stochastic search to find the trace that best matches the input.
+The network is trained from an automatically generated corpus of synthetic image generating programs.
+
+The second step involves generating a high-level program capable of producing the program trace identified by the first phase.
+In principle, we could also train a neural network to learn this mapping.
+In practice, though, this would be challenging because it would no longer be sufficient to train the network with a synthetic corpus of randomly generated programs, since our goal is to generate programs that satisfy certain semantic constraints that ensure that we get the program that the user most likely intended.
+This paper argues that this stage is best achieved by \emph{constraint-based program synthesis} \cite{}.
+Without the need for training, the program synthesizer can search the space of possible programs for one capable of producing the desired trace under a quantitative objective that maximizes the likelihood according to a prior distribution that aims to capture the user’s preference.
+
+%% The key observation behind our work is that generating a programmatic representation from an image of a diagram actually involves two distinct steps that require different technical approaches.
+The first step involves identifying the components such as boxes, lines and arrows that make up the image.
+The second step involves identifying the high-level structure in how the components were drawn; for example, in Figure 1(b), it means identifying that there is a pattern in how the circles and rectangles are being drawn that is best described with two nested loops, and which can easily be extrapolated to a bigger diagram.
+
+%% We present a hybrid architecture for inferring graphics programs that is structured around these two steps.
+For the first step, our approach uses a deep neural network to infer a sequence of primitive shape-drawing commands that can generate an image similar to the observed image.
+We refer to this sequence as an \emph{execution trace}, since it corresponds to the sequence of primitive commands that the desired program would have issued, but it lacks the high-level structure that determines how the program decided to issue those commands.
+For added robustness, we train the network to produce a proposal distribution of the most likely traces, and use stochastic search to find the trace that best matches the input.
+The network is trained from an automatically generated corpus of synthetic image generating programs.
+
+%% High dimensional perceptual input may seem ill matched to the abstract
+%% semantics of a programming language. But programs with constructs such as
+%% recursion or iteration produce a simpler \emph{execution trace} of
+%% primitive actions; for our domain, the primitive actions are drawing
+%% commands. Our hypothesis is that the execution trace of the program is
+%% better aligned with the perceptual input, and that the trace can act
+%% as a kind of bridge between perception and programs. We test this
+%% hypothesis by developing a model that learns to map from an image to
+%% the execution trace of the graphics program that drew it.  With the
+%% execution trace in hand, we can bring to bear techniques from the
+%% program synthesis community to recover the latent graphics program.
+%% This family of techniques, called \emph{constraint-based program synthesis}~\cite{solar2008program},
+%% work by modeling a set of possible programs inside of a constraint solver,
+%% such as a SAT or SMT solver~\cite{de2008z3}.
+%% These techniques excel at uncovering high-level symbolic structure,
+%% but are not well equipped to deal with real-valued perceptual inputs.
+
+%% We develop a hybrid architecture for inferring graphics programs.  Our
+%% approach uses a deep neural network infer an execution trace from an
+%% image; this network recovers primitive drawing operations such as
+%% lines, circles, or arrows, along with their parameters. For added
+%% robustness, we use the deep network as a proposal distribution for a
+%% stochastic search over execution traces.
 Section~\ref{neuralNetworkSection} describes this first stage of the architecture where we infer drawing commands from images, and explains how we handle noisy hand drawings.
-Finally, we use program synthesis techniques to recover the program from its
-trace.  The program synthesizer discovers constructs such as loops and
-geometric operations such as reflections and affine transformations.
-% \remark{This paragraph is all about making things a bit more
-Section~\ref{programSynthesisSection} describes how the architecture
-synthesizes programs from execution traces,
-and how those programs are used for  correcting errors made by the deep network, measuring similarity between hand drawings,
-and extrapolating figures.
+%% Finally, we use program synthesis techniques to recover the program from its
+%% trace.  The program synthesizer discovers constructs such as loops and
+%% geometric operations such as reflections and affine transformations.
+%% % \remark{This paragraph is all about making things a bit more
+%% Section~\ref{programSynthesisSection} describes how the architecture
+%% synthesizes programs from execution traces,
+%% and how those programs are used for  correcting errors made by the deep network, measuring similarity between hand drawings,
+%% and extrapolating figures.
 
@@
 convnet, a multilayer perceptron then predicts a distribution over the
-next drawing command to add to the trace.  We predict the drawing
+next drawing command to add to the trace; see Table~\ref{drawingCommandTable}.  We predict the drawing
 command token-by-token, conditioning each token both on the image
@@
 \end{equation}
-where $|T|$ is the length of execution trace $T$, and the subscripts
+where $|T|$ is the length of execution trace $T$, the subscripts
 on $T$ index drawing commands within the trace, and the \verb|STOP|
@@
 \end{figure}
-\begin{table}
+\begin{table}[h]
 \begin{tabular}{ll}\toprule
@@
 
-We trained the network on $10^5$ scenes, which takes a little less than a day on a Nvidia TitanX GPU.
+We trained the network on $10^5$ scenes, which takes a little less than a day on an Nvidia TitanX GPU.
 
@@
 likelihood.
-
+%
 Figure~\ref{syntheticResults}
@@
   \includegraphics[width = 6cm]{figures/drawingAccuracy.png}
-  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1, 5, 10, 100 samples)?
-  Distance to the ground truth trace is measured by the intersection over union of predicted vs. ground truth traces (sets of drawing commands).}\label{drawingIntersectionOverUnion}
+  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1,5,10,100)?
+  Distance to ground truth trace measured by the intersection over union of predicted vs. ground truth traces (sets of drawing commands).}\label{drawingIntersectionOverUnion}
     \end{minipage}
@@
 
+\newcommand{\exampleProgramSize}{2.3cm} 
+\begin{figure}
+  \begin{tabular}{lllll}
+  \includegraphics[width = \exampleProgramSize]{figures/expert-29.png}&
+  \includegraphics[width = \exampleProgramSize]{figures/expert-52.png}&
+  \includegraphics[width = \exampleProgramSize]{figures/expert-38.png}&
+  \includegraphics[width = \exampleProgramSize]{figures/expert-72.png}&
+  \includegraphics[width = \exampleProgramSize]{figures/expert-75.png}\\
+    \begin{minipage}[t]{\exampleProgramSize}
+\begin{Verbatim}[fontsize = \small]
+for(i<3){
+line(i,-1*i+6,
+2*i+2,-1*i+6)
+line(i,-2*i+4,
+i,-1*i+6)
+\end{Verbatim}
+    \end{minipage}&
+    \begin{minipage}[t]{\exampleProgramSize}
+\begin{Verbatim}[fontsize = \small]
+circle(4,10)
+for(i<3){
+circle(-3*i+7,5)
+circle(-3*i+7,1)
+line(-3*i+7,4,
+-3*i+7,2,
+arrow=True)
+line(4,9,
+-3*i+7,6,
+arrow=True)
+\end{Verbatim}
+\end{minipage}&
+\begin{minipage}[t]{\exampleProgramSize}
+\begin{Verbatim}[fontsize=\small]
+for(i<3)
+for(j<3)
+if(j>0)
+line(-3*j+8,
+-3*i+7,-3*j+9,
+-3*i+7)
+line(-3*i+7,-3*j+8,
+-3*i+7,
+-3*j+9)
+circle(-3*j+7,-3*i+7)
+\end{Verbatim}
+\end{minipage}&
+\begin{minipage}[t]{\exampleProgramSize}
+\begin{Verbatim}[fontsize=\small]
+reflect(y=8){
+for(i<3){
+if(i>0){
+rectangle(3*i-1,
+2,3*i,3)}
+circle(3*i+1,
+       3*i+1)
+\end{Verbatim}
+\end{minipage}&
+ \begin{minipage}[t]{\exampleProgramSize}
+    \begin{Verbatim}[fontsize = \small]
+for(i<4){
+line(-4*i+13,4,
+-4*i+13,2,
+arrow=True)
+for(j<3){
+if(j>0){
+circle(-4*i+13,
+4*j+-3)}
+line(-4*j+10,5,
+-4*j+12,5,
+arrow=True)
+\end{Verbatim}
+  \end{minipage}
+  \end{tabular}
+  \caption{Example drawings (top row) and the programs we synthesize from their ground truth traces (bottom row).
+Notice the nested loops in the Ising model (middle), special case conditionals for the HMM (rightmost), combination of symmetry and iteration in middle left, and affine transformation in the leftmost figure.}
+  \end{figure}
+
 Why synthesize a graphics program,
@@
 \subsection{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
-The program synthesizer can help correct errors from the execution trace proposal network by favoring execution traces which lead to more concise or general programs.
-For example, one generally prefers figures with perfectly aligned objects over figures whose parts are slightly misaligned -- and precise alignment lends itself to short programs.
-Similarly, figures often have repeated parts,
-which the program synthesizer might be able to model as a loop or reflectional symmetry.
-So, in considering several candidate traces proposed by the neural network,
-we might prefer traces whose best programs have desirable features such being short or having iterated structures.
-
-Concretely, we implemented the following scheme: for an image $I$, the neurally guided sampling scheme of section~\ref{neuralNetworkSection} samples a set of candidate traces, written $\mathcal{F}(I)$.
-Instead of predicting the most likely trace in $\mathcal{F}(I)$ according to the neural network,
-we can take into account the programs that best explain the traces. 
-Writing $\hat{T}(I)$ for the trace the model predicts for image $I$,
-\begin{equation}
-\hat{T}(I) = \argmax_{T\in \mathcal{F}(I)} L_{\text{learned}}(I | \text{render}(T))\times \probability_\theta[T|I] \times\probability_{\beta} [ \text{program}(T)] 
-\end{equation}
-where $\probability_{\beta} [\cdot]$ is a prior probability
-distribution over programs parameterized by $\beta$.
-This is equivalent to doing
-MAP inference in a generative model where the program is first drawn
-from $\probability_{\beta} [\cdot]$, then the program is executed deterministically,
-and then we observe a noisy version of the program's output, where $L_\text{learned}(I|\text{render}(\cdot))\times\probability_\theta[\cdot|I]$
-is our observation model.
-
-Given a corpus of graphics program synthesis problems with annotated ground truth traces (i.e. $(I,T)$ pairs),
-we find a maximum likelihood estimate of $\beta$:
-\begin{equation}
-  \beta^* = \argmax_{\beta} \expect \left[ \log \frac{\probability_{\beta} [\text{program}(T)]\times L_{\text{learned}}(I|\text{render}(T))\times \probability_\theta[T|I]}{\sum_{T'\in \mathcal{F}(I)} \probability_{\beta} [\text{program}(T')]\times L_{\text{learned}}(I|\text{render}(T'))\times \probability_\theta[T'|I]} \right]
-\end{equation}
-where the expectation is taken both over the model predictions and the
-$(I,T)$ pairs in the training corpus.  We define $\probability_{\beta}
-[\cdot]$ to be a log linear distribution $\propto \exp
-(\beta\cdot \phi(\text{program}))$, where $\phi(\cdot)$ is a feature
-extractor for programs.  We extract a few basic features of a
-program, such as its size and how many loops it has, and use these
-features to help predict whether a trace is the correct explanation
-for an image.
-
-We synthesized programs for the top five traces
-output by the deep network.  Learning this prior over programs can
+The program synthesizer can help correct errors from the execution
+trace proposal network by favoring execution traces which lead to more
+concise or general programs.  For example, one generally prefers
+figures with perfectly aligned objects over figures whose parts are
+slightly misaligned -- and precise alignment lends itself to short
+programs.  Concretely, we estimated a prior over programs. Then,
+given the few most likely traces output by the neurally guided sampler,
+we reranked them according to the prior probability of their programs.
+Our neurally guided sampler could only do better on
+7 drawings by looking at the Top-100 sampled traces
+(see Fig.~\ref{drawingIntersectionOverUnion}),
+precluding a statistically significant analysis of how much
+learning a prior over programs could help correct errors.
+But,
+learning this prior does sometimes
 help correct mistakes made by the neural network, and also
@@
 Fig.~\ref{exampleOfProgramCorrectingMistake} for a representative
-example of the kinds of corrections that it makes. On the whole
-it modestly improves our Top-1 accuracy from 58\% to 60\%.  Recall that
-from Fig.~\ref{drawingIntersectionOverUnion} that the best improvement
-in accuracy we could possibly get is 63\% by looking at the top 5 traces.
+example of the kinds of corrections that it makes.
+See supplement for details.
 \begin{wrapfigure}{R}{5.5cm}
@@
 
+%% This is equivalent to doing
+%% MAP inference in a generative model where the program is first drawn
+%% from $\probability_{\beta} [\cdot]$, then the program is executed deterministically,
+%% and then we observe a noisy version of the program's output, where $L_\text{learned}(I|\text{render}(\cdot))\times\probability_\theta[\cdot|I]$
+%% is our observation model.
+
+%% Learning this prior over programs can
+%%  On the whole
+%% it modestly improves our Top-1 accuracy from 58\% to 61\%.  Recall that
+%% from Fig.~\ref{drawingIntersectionOverUnion} that the best improvement
+%% in accuracy we could possibly get is 65\% by looking at the top 10 traces.
+
 \subsection{Modeling similarity between drawings}
@@
 We measure the similarity between two drawings by extracting features
-of the best programs that describe them.  Here the features we use are
-just counts of the number of times that different components in the
+of the best programs that describe them. Our features are counts of the number of times that different components in the
 DSL were used (Table~\ref{DSL}).  We project these features down to a
@@
 (NMF:~\cite{lee1999learning}); see Fig.\ref{NMF}.  One could use many
-alternative similarity metrics between drawings which would capture pixel-level or object-level similarities while missing high-level geometric similarities.
-For example, we can use our learned distance metric between execution traces, $L_{\text{learned}}(\cdot|\cdot)$.
-Projecting these distances to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}) reveals similarities between the objects in the drawings,
+alternative similarity metrics between drawings which would capture pixel-level while missing high-level geometric similarities.
+We used our learned distance metric between execution traces, $L_{\text{learned}}(\cdot|\cdot)$, and projected to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}).
+This reveals similarities between the objects in the drawings,
 while missing similarities at the level of the program.
@@
 \begin{figure}
-  \includegraphics[width = \textwidth]{figures/extrapolationMatrix.png} 
+  \includegraphics[width = \textwidth]{figures/extrapolationMatrix1.png}  
   \caption{Top: hand drawings. Bottom: extrapolations produced by

### 2017-05-19 supplement.tex
lots of changes and now it needs to be smaller

@@
 
-\title{Supplement to: Inferring Graphics Programs from Images}
+\title{Supplement to: Learning to Infer Graphics Programs from Hand-Drawn Images}
 
@@
 \maketitle
+
+\section{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
+The program synthesizer can help correct errors from the execution trace proposal network by favoring execution traces which lead to more concise or general programs.
+For example, one generally prefers figures with perfectly aligned objects over figures whose parts are slightly misaligned -- and precise alignment lends itself to short programs.
+Similarly, figures often have repeated parts,
+which the program synthesizer might be able to model as a loop or reflectional symmetry.
+So, in considering several candidate traces proposed by the neural network,
+we might prefer traces whose best programs have desirable features such being short or having iterated structures.
+
+Concretely, we implemented the following scheme: for an image $I$, the neurally guided sampling scheme of section~\ref{neuralNetworkSection} samples a set of candidate traces, written $\mathcal{F}(I)$.
+Instead of predicting the most likely trace in $\mathcal{F}(I)$ according to the neural network,
+we can take into account the programs that best explain the traces. 
+Writing $\hat{T}(I)$ for the trace the model predicts for image $I$,
+\begin{equation}
+\hat{T}(I) = \argmax_{T\in \mathcal{F}(I)} L_{\text{learned}}(I | \text{render}(T))\times \probability_\theta[T|I] \times\probability_{\beta} [ \text{program}(T)] 
+\end{equation}
+where $\probability_{\beta} [\cdot]$ is a prior probability
+distribution over programs parameterized by $\beta$.
+This is equivalent to doing
+MAP inference in a generative model where the program is first drawn
+from $\probability_{\beta} [\cdot]$, then the program is executed deterministically,
+and then we observe a noisy version of the program's output, where $L_\text{learned}(I|\text{render}(\cdot))\times\probability_\theta[\cdot|I]$
+is our observation model.
+
+Given a corpus of graphics program synthesis problems with annotated ground truth traces (i.e. $(I,T)$ pairs),
+we find a maximum likelihood estimate of $\beta$:
+\begin{equation}
+  \beta^* = \argmax_{\beta} \expect \left[ \log \frac{\probability_{\beta} [\text{program}(T)]\times L_{\text{learned}}(I|\text{render}(T))\times \probability_\theta[T|I]}{\sum_{T'\in \mathcal{F}(I)} \probability_{\beta} [\text{program}(T')]\times L_{\text{learned}}(I|\text{render}(T'))\times \probability_\theta[T'|I]} \right]
+\end{equation}
+where the expectation is taken both over the model predictions and the
+$(I,T)$ pairs in the training corpus.  We define $\probability_{\beta}
+[\cdot]$ to be a log linear distribution $\propto \exp
+(\beta\cdot \phi(\text{program}))$, where $\phi(\cdot)$ is a feature
+extractor for programs.  We extract a few basic features of a
+program, such as its size and how many loops it has, and use these
+features to help predict whether a trace is the correct explanation
+for an image.
+
+We synthesized programs for the top 10 traces
+output by the deep network.  Learning this prior over programs can
+help correct mistakes made by the neural network, and also
+occasionally introduces mistakes of its own; see
+Fig.~\ref{exampleOfProgramCorrectingMistake} for a representative
+example of the kinds of corrections that it makes. On the whole
+it modestly improves our Top-1 accuracy from 58\% to 61\%.  Recall that
+from Fig. 6 of the main paper that the best improvement
+in accuracy we could possibly get is 65\% by looking at the top 10 traces. 
+\begin{wrapfigure}{R}{5.5cm}
+  \includegraphics[width = 5cm]{figures/programSuccess7.png}
+  \caption{Left: hand drawing.
+Center: interpretation favored by the deep network.
+Right: interpretation favored after learning a prior over programs.
+Our learned prior favors shorter, simpler programs, thus continuing the pattern of not having an arrow is preferred.}\label{exampleOfProgramCorrectingMistake}
+\end{wrapfigure}
 

### 2017-05-19 paper.tex
paper is done now I just need to make it shorter

@@
 The key observation behind our work is that generating a programmatic representation from an image of a diagram actually involves two distinct steps that require different technical approaches.
-The first step involves identifying the components such as boxes, lines and arrows that make up the image.
-The second step involves identifying the high-level structure in how the components were drawn; for example, in Figure 1(b), it means identifying that there is a pattern in how the circles and rectangles are being drawn that is best described with two nested loops, and which can easily be extrapolated to a bigger diagram.
+The first step involves identifying the components such as rectangles, lines and arrows that make up the image.
+The second step involves identifying the high-level structure in how the components were drawn.
+In Figure 1(b), it means identifying a pattern in how the circles and rectangles are being drawn that is best described with two nested loops, and which can easily be extrapolated to a bigger diagram.
 
 We present a hybrid architecture for inferring graphics programs that is structured around these two steps.
-For the first step, our approach uses a deep neural network to infer a sequence of primitive shape-drawing commands that can generate an image similar to the observed image.
-We refer to this sequence as a \emph{program trace}, since it corresponds to the sequence of primitive commands that the desired program would have issued, but it lacks the high-level structure that determines how the program decided to issue those commands.
+For the first step, our approach uses a deep network to infer a sequence of primitive shape-drawing commands that can generate an image similar to the observed image.
+We refer to this sequence as a \emph{execution trace}, since it corresponds to the sequence of primitive commands that a program would have issued, but it lacks the high-level structure that determines how the program decided to issue those commands.
 For added robustness, we train the network to produce a proposal distribution of the most likely traces, and use stochastic search to find the trace that best matches the input.
@@
   \includegraphics[width = \textwidth]{figures/extrapolationMatrix1.png}
-  \caption{Top: hand drawings. Bottom: extrapolations produced by
-running loops for extra iterations. Rightmost pair is an illustrative failure case.}\label{extrapolationFigure}
+    \includegraphics[width = \textwidth]{figures/extrapolationMatrix2.png}  
+  \caption{Top, white: hand drawings. Bottom, black: extrapolations produced by
+running loops for extra iterations..}\label{extrapolationFigure}
   \end{figure}

### 2017-05-19 paper.tex
removed some lines

@@
 The two approaches also differ in their architectures and training regimes: AIR learns a recurrent auto-encoding model via variational inference, whereas our parsing stage learns an autoregressive-style model from randomly-generated (execution trace, image) pairs.
-Finally, while AIR was evaluated on multi-MNIST images and synthetic 3D scenes, we focus on parsing and interpreting hand-drawn sketches.
+Finally, while AIR was evaluated on multi-MNIST images and synthetic 3D scenes, we focus on hand-drawn sketches.
 % attend infer repeat:~\cite{eslami1603attend}. Crucial distinction is
@@
 Prior work has also applied sketch-based program synthesis to authoring graphics programs.
-In particular, Sketch-n-Sketch presents a bi-directional editing system in which direct manipulations to a program's output automatically propagate to the program source code~\cite{Hempel:2016:SSP:2984511.2984575}.
+Sketch-n-Sketch is a bi-directional editing system in which direct manipulations to a program's output automatically propagate to the program source code~\cite{Hempel:2016:SSP:2984511.2984575}.
 We see this work as complementary to our own: programs produced by our method could be provided to a Sketch-n-Sketch-like system as a starting point for further editing.
@@
 %%   network layer sizes, which MLPs share parameters, etc.}
-
 The distribution over the next drawing command factorizes as:
@@
 on $T$ index drawing commands within the trace, and the \verb|STOP|
-token is emitted by the network to signal that the execution trace
+token is emitted by the network to signal that the trace
 explains the image.
@@
 In a sense, this model is like an autoregressive variant of AIR~\cite{eslami1603attend} without attention.
+We trained the network on $10^5$ scenes, which takes a little less than a day on an Nvidia TitanX GPU.
 
@@
 
-We trained the network on $10^5$ scenes, which takes a little less than a day on an Nvidia TitanX GPU.
-
 This network suffices to ``derender'' synthetic images like those shown in
@@
 the trace we want and the trace we have so far.  Pixel-wise distance
-metrics are sensitive to the fine details of how and exactly where
+metrics are sensitive to the details of how
 arrows, dashes, and corners are drawn -- but we wish to be invariant
@@
 We drew 100 figures by hand; see figure~\ref{lotsOfHandDrawings}.
-These were drawn reasonably carefully but not perfectly.
-Because our model assumes that objects are snapped to a $16\times 16$ grid,
+These were drawn carefully but not perfectly.
+Our model assumes that objects are snapped to a $16\times 16$ grid, so
 we made the drawings on graph paper.
@@
 that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
-Because our current model sometimes makes mistakes on hand drawings,
-we envision the current system working as follows:
+Because our current model sometimes makes mistakes, % on hand drawings,
+we envision it working as follows:
 a user sketches a diagram,
 and the system responds by proposing a few candidate interpretations.
-The user could then select the one closest to their intention and edit it if necessary.
+The user could then select one and edit it if necessary.
 
@@
   $\mathcal{Z}$$\to$&an integer\\
-  Axis$\to$&\texttt{X = }$\mathcal{Z}$\\
-  Axis$\to$&\texttt{Y = }$\mathcal{Z}$\\\bottomrule
+  Axis$\to$&\texttt{X = }$\mathcal{Z}$ | \texttt{Y = }$\mathcal{Z}$\\\bottomrule
   \end{tabular}
@@
 \begin{equation}
-  \text{program}(T) = \argmin_{\substack{p\in \text{DSL}\\p \text{ evaluates to } T}} \text{cost}(p)\label{programObjective}
+  \text{program}(T) = \argmin_{p\in \text{DSL, s.t. }p \text{ evaluates to } T} \text{cost}(p)\label{programObjective}
 \end{equation}
@@
   \caption{Top, white: hand drawings. Bottom, black: extrapolations produced by
-running loops for extra iterations..}\label{extrapolationFigure}
+running loops for extra iterations.}\label{extrapolationFigure}
   \end{figure}

### 2017-05-19 paper.tex
very close page limit

@@
 The second step involves generating a high-level program capable of producing the program trace identified by the first phase.
-In principle, we could also train a neural network to learn this mapping.
+%In principle, we could also train a neural network to learn this mapping.
 In practice, though, this would be challenging because it would no longer be sufficient to train the network with a synthetic corpus of randomly generated programs, since our goal is to generate programs that satisfy certain semantic constraints that ensure that we get the program that the user most likely intended.
-This paper argues that this stage is best achieved by \emph{constraint-based program synthesis} \cite{}.
-Without the need for training, the program synthesizer can search the space of possible programs for one capable of producing the desired trace under a quantitative objective that maximizes the likelihood according to a prior distribution that aims to capture the user’s preference.
+This paper argues that this stage is best achieved by \emph{constraint-based program synthesis} \cite{solar2008program}.
+Without the need for training, the program synthesizer can search the space of possible programs for one capable of producing the desired trace.
+%under a quantitative objective that maximizes the likelihood according to a prior distribution that aims to capture the user’s preference.
 
@@
 The proposal network also currently handles only a very small subset of \LaTeX drawing commands, though there is no reason that it could not be extended to handle more with a higher-capacity network.
-Exploring more sophisticated network architectures, including ones that utilize attention~\cite{mnih2014recurrent}, could also help correct some of the errors the network makes.
+Exploring more sophisticated network architectures, including ones that utilize attention~\cite{mnih2014recurrent}, could help correct some of the errors the network makes.
 In the synthesis phase, a more expressive DSL---including subroutines, recursion, and symmetry groups beyond reflections---would allow the system to effectively model a wider variety of graphical phenomena.
@@
 
-In the not-too-distant future, we believe it should be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the corresponding code.
-More generally, we believe that the two-phase system we have proposed---parsing into execution traces, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for other domains in which agents must programmatically reason about noisy perceptual input.
+In the not-too-distant future, we believe it should be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the code.
+More generally, we believe that the two-phase system we have proposed---parsing into execution traces, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for domains in which agents must programmatically reason about noisy perceptual input.
 

### 2017-05-19 paper.tex
Edit down some lines.

--- 2017-05-19 paper.tex
@@
 We present a hybrid architecture for inferring graphics programs that is structured around these two steps.
-For the first step, our approach uses a deep network to infer a sequence of primitive shape-drawing commands that can generate an image similar to the observed image.
-We refer to this sequence as a \emph{execution trace}, since it corresponds to the sequence of primitive commands that a program would have issued, but it lacks the high-level structure that determines how the program decided to issue those commands.
-For added robustness, we train the network to produce a proposal distribution of the most likely traces, and use stochastic search to find the trace that best matches the input.
-The network is trained from an automatically generated corpus of synthetic image generating programs.
+For the first step, our approach uses a deep network to infer a sequence of primitive shape-drawing commands that generates an image similar to the observed image.
+We refer to this sequence as a \emph{execution trace}, since it corresponds to the sequence of primitive commands that a program would have issued but lacks the high-level structure that determines how the program decided to issue them.
+For added robustness, we train the network to produce a proposal distribution of the most likely traces and use stochastic search to find the trace that best matches the input.
+The network is trained from an automatically-generated corpus of synthetic image-generating programs.
 
@@
 \end{equation}
-Intuitively, Eq.~\ref{symmetricDistance} says that
+Intuitively,
 $L_{\text{learned}}(\cdot|\cdot)$ approximates the distance between
@@
 These were drawn reasonably carefully but not perfectly.
-Because our model assumes that objects are snapped to a $16\times 16$ grid,
+Because our model assumes that objects lie on a $16\times 16$ grid,
 we made the drawings on graph paper.
@@
 \end{figure}
-For each drawing we annotated a ground truth trace, and evaluated the
-model by asking it to sample many candidate traces for each drawing.
-For 58\% of the drawings the Top-1 most likely sample exactly matches the
-ground truth; as we consider more samples the model encounters traces
+For each drawing we annotated a ground truth trace and asked the model
+to sample many candidate traces for each drawing.
+For 58\% of the drawings, the Top-1 most likely sample exactly matches the
+ground truth; with more samples, the model finds traces
 that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
-Because our current model sometimes makes mistakes on hand drawings,
+As the model sometimes makes mistakes on hand drawings,
 we envision the current system working as follows:
@@
 \section{Synthesizing graphics programs from execution traces}\label{programSynthesisSection}
-Although the execution trace of a graphics program describes the parts
-of a scene, it fails to encode higher-level features of the image,
+While the execution trace of a graphics program describes the contents
+of a scene, it does not encode higher-level features of the image,
 such as repeated motifs or symmetries.  A \emph{graphics
-  program} better describe structures like these,
-and we now take as our goal to synthesize simple graphics programs from
-their execution traces.
+  program} better describe such structures;
+we seek to synthesize simple graphics graphics from their execution traces.
 
@@
 The constrained optimization problem in
-equation~\ref{programObjective} is intractable in general, but there
-exist efficient-in-practice tools for finding exact solutions to
-program synthesis problems like these. We use the state-of-the-art Sketch
+Equation~\ref{programObjective} is intractable in general, but there
+exist efficient-in-practice tools for finding exact solutions to such
+program synthesis problems. We use the state-of-the-art Sketch
 tool~\cite{solar2008program}. Describing Sketch's program synthesis
@@
 function.  It translates the synthesis problem into a constraint
-satisfaction problem, and then uses a SAT solver to find a
-minimum cost program satisfying the specification.  In exchange for
-not having any guarantees on how long it will take to find a minimum
+satisfaction problem and then uses a SAT solver to find a
+minimum-cost program satisfying the specification.  In exchange for
+having no guarantee on the time required to find a minimum
 cost solution, it comes with the guarantee that it will always find a
@@
   \end{tabular}
-  \caption{Example drawings (top row) and the programs we synthesize from their ground truth traces (bottom row).
-Notice the nested loops in the Ising model (middle), special case conditionals for the HMM (rightmost), combination of symmetry and iteration in middle left, and affine transformation in the leftmost figure.}
+  \caption{Example drawings (top) and programs synthesized from their ground truth traces (bottom).
+Note the nested loops in the Ising model (middle), special case conditionals for the HMM (rightmost), combination of symmetry and iteration in middle left, and affine transformation in the leftmost figure.}
   \end{figure}
@@
 \subsection{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
-The program synthesizer can help correct errors from the execution
-trace proposal network by favoring execution traces which lead to more
-concise or general programs.  For example, one generally prefers
-figures with perfectly aligned objects over figures whose parts are
-slightly misaligned -- and precise alignment lends itself to short
+The program synthesizer can correct errors from the execution
+trace proposal network by favoring traces which lead to more
+concise or general programs.  For example, figures with perfectly aligned objects are preferrale to figures whose parts are slightly misaligned, and precise alignment lends itself to short
 programs.  Concretely, we estimated a prior over programs. Then,
@@
 we reranked them according to the prior probability of their programs.
-Our neurally guided sampler could only do better on
+Our sampler could only do better on
 7 drawings by looking at the Top-100 sampled traces
@@
 \subsection{Modeling similarity between drawings}
-Modeling an image using a program opens up new ways of measuring similarity between drawings.
-For example, we might say that two drawings are similar if they both contain repetitions of length 4,
-or if they share the same reflectional symmetry,
+Modeling drawings using programs opens up new ways to measure similarity them.
+For example, we might say that two drawings are similar if they both contain loops of length 4,
+or if they share a reflectional symmetry,
 or if they are both organized according to a grid-like structure.
@@
 
-In the not-too-distant future, we believe it should be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the corresponding code.
+In the near future, we believe it will be possible to produce professional-looking figures by drawing them and then letting an artificially-intelligent agent write the corresponding code.
 More generally, we believe that the two-phase system we have proposed---parsing into execution traces, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for other domains in which agents must programmatically reason about noisy perceptual input.

### 2017-05-19 paper.tex

@@
 We drew 100 figures by hand; see figure~\ref{lotsOfHandDrawings}.
-These were drawn reasonably carefully but not perfectly.
-Because our model assumes that objects lie on a $16\times 16$ grid,
+These were drawn carefully but not perfectly.
+Our model assumes that objects are snapped to a $16\times 16$ grid, so
 we made the drawings on graph paper.
@@
 that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
-As the model sometimes makes mistakes on hand drawings,
-we envision the current system working as follows:
+Because our current model sometimes makes mistakes, % on hand drawings,
+we envision it working as follows:
 a user sketches a diagram,
 and the system responds by proposing a few candidate interpretations.
-The user could then select the one closest to their intention and edit it if necessary.
+The user could then select one and edit it if necessary.
 
@@
 
-In the near future, we believe it will be possible to produce professional-looking figures by drawing them and then letting an artificially-intelligent agent write the corresponding code.
-More generally, we believe that the two-phase system we have proposed---parsing into execution traces, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for other domains in which agents must programmatically reason about noisy perceptual input.
+In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the code.
+More generally, we believe that the two-phase system we have proposed---parsing into execution traces, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for domains in which agents must programmatically reason about noisy perceptual input.
 

### 2017-05-19 paper.tex
more improvements to dimensionality reduction section

@@
 DSL were used (Table~\ref{DSL}).  We project these features down to a
-2-dimensional subspace using nonnegative matrix factorization
-(NMF:~\cite{lee1999learning}); see Fig.\ref{NMF}.  One could use many
+2-dimensional subspace using primary component analysis
+(PCA); see Fig.\ref{NMF}.  One could use many
 alternative similarity metrics between drawings which would capture pixel-level while missing high-level geometric similarities.
@@
   \begin{minipage}{0.48\textwidth}
-    \includegraphics[width = \textwidth]{figures/NMF.png}
-    \caption{NMF on features of the programs that were synthesized for each image.
-Horizontal component roughly corresponds to ``symmetry'' while vertical component roughly corresponds to ``loopyness'', with images on the diagonal having both of these.}    \label{NMF}
+    \includegraphics[width = \textwidth]{figures/PCA.png}
+    \caption{PCA on features of the programs that were synthesized for each drawing. Symmetric figures cluster to the right; ``loopy'' figures cluster to the left.}    \label{NMF}
   \end{minipage}\hfill

### 2017-05-19 synthesizerOutputs.tex
latest synthesis results in the supplement

@@
         \begin{verbatim}
-Solver timeout
+for (i < 3){
+if (i > 0){
+rectangle(-6*i + 12,2*i + 3,-6*i + 14,9);
+rectangle(-6*i + 15,5*i + -2,-6*i + 17,9)
+}
+line(12,9,12,0,
+arrow = True,solid = True)
+}
         \end{verbatim}
@@
         \begin{verbatim}
-Solver timeout
+circle(1,5);
+for (i < 3){
+if (i > 0){
+line(-4*i + 12,1,-4*i + 10,1,
+arrow = True,solid = True);
+rectangle(-4*i + 12,4,-4*i + 14,6)
+}
+line(-4*i + 9,2,-4*i + 9,4,
+arrow = True,solid = True);
+rectangle(-4*i + 8,0,-4*i + 10,2)
+}
         \end{verbatim}
@@
         \begin{verbatim}
-Solver timeout
+for (i < 3){
+for (j < 3){
+if (j > 0){
+line(-3*j + 8,-3*i + 7,-3*j + 9,-3*i + 7,
+arrow = False,solid = True);
+line(-3*i + 7,-3*j + 8,-3*i + 7,-3*j + 9,
+arrow = False,solid = True)
+}
+circle(-3*j + 7,-3*i + 7)
+}
+}
         \end{verbatim}
@@
         \begin{verbatim}
-Solver timeout
+rectangle(0,0,6,2);
+reflect(reflect(x = 6)){
+rectangle(0,3,2,9);
+for (i < 3){
+circle(5,2*i + 4);
+circle(2*i + 1,1)
+}
+}
         \end{verbatim}
@@
         \begin{verbatim}
-Solver timeout
+circle(3,1);
+reflect(reflect(x = 6)){
+for (i < 3){
+if (i > 0){
+circle(1,-4*i + 13);
+line(5,-4*i + 12,-2*i + 7,-4*i + 10,
+arrow = True,solid = True)
+}
+line(1,8,4,5,
+arrow = True,solid = True)
+}
+}
         \end{verbatim}

### 2017-05-19 paper.tex
A few typo fixes / wording changes.

--- 2017-05-19 paper.tex
@@
   program synthesis techniques to recover a graphics
-  program with constructs like variable bindings, iterative loops, or
+  program with constructs such as variable bindings, iterative loops, or
   simple kinds of conditionals. With a graphics program in hand,
@@
 For the first step, our approach uses a deep network to infer a sequence of primitive shape-drawing commands that generates an image similar to the observed image.
-We refer to this sequence as a \emph{execution trace}, since it corresponds to the sequence of primitive commands that a program would have issued but lacks the high-level structure that determines how the program decided to issue them.
+We refer to this sequence as an \emph{execution trace}, since it corresponds to the sequence of primitive commands that a program would have issued but lacks the high-level structure that determines how the program decided to issue them.
 For added robustness, we train the network to produce a proposal distribution of the most likely traces and use stochastic search to find the trace that best matches the input.
@@
 high-level understanding of hand-drawn figures. Their primary goal is
-cognitive modeling (eg, they apply their system to solving IQ-test
+cognitive modeling (they apply their system to solving IQ-test
 style visual reasoning problems), whereas we are interested in
-building an automated AI application (eg, in our system the user need
+building an automated AI application (e.g. in our system the user need
 not annotate which strokes correspond to which shapes; our neural
@@
 \subsection{Modeling similarity between drawings}
-Modeling drawings using programs opens up new ways to measure similarity them.
+Modeling drawings using programs opens up new ways to measure similarity between them.
 For example, we might say that two drawings are similar if they both contain loops of length 4,
@@
 using Mixture Density Networks~\cite{MDN}.
-The proposal network also currently handles only a very small subset of \LaTeX drawing commands, though there is no reason that it could not be extended to handle more with a higher-capacity network.
+The proposal network also currently handles only a very small subset of \LaTeX~drawing commands, though there is no reason that it could not be extended to handle more with a higher-capacity network.
 Exploring more sophisticated network architectures, including ones that utilize attention~\cite{mnih2014recurrent}, could help correct some of the errors the network makes.

### 2017-05-19 paper.tex
improvements to images

--- 2017-05-19 paper.tex
@@
   \begin{minipage}[t]{2.25cm}
-    \includegraphics[width = 2cm]{figures/expert-0.png}
-    \includegraphics[width = 2cm]{figures/0-parse.png}    
+    \includegraphics[width = 2cm]{figures/expert-1.png}
+    \includegraphics[width = 2cm]{figures/expert-1-parse.png}    
     \subcaption{Near miss}
@@
 \end{figure}
-For each drawing we annotated a ground truth trace and asked the model
-to sample many candidate traces for each drawing.
+For each drawing we annotated a ground truth trace and asked the neurally guided SMC sampler
+to produce many candidate traces for each drawing.
 For 58\% of the drawings, the Top-1 most likely sample exactly matches the
@@
 and the system responds by proposing a few candidate interpretations.
-The user could then select one and edit it if necessary.
+The user could then select the one closest to their intention and edit it if necessary.
 

### 2017-05-19 supplement.tex
latest synthesis results in the supplement
improvements to images

@@
 \DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays
+\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays
 \DeclareMathOperator{\argmin}{argmin} % no space, limits underneath in displays
@@
 
-Concretely, we implemented the following scheme: for an image $I$, the neurally guided sampling scheme of section~\ref{neuralNetworkSection} samples a set of candidate traces, written $\mathcal{F}(I)$.
+Concretely, we implemented the following scheme: for an image $I$, the neurally guided sampling scheme of section 3 of the main paper samples a set of candidate traces, written $\mathcal{F}(I)$.
 Instead of predicting the most likely trace in $\mathcal{F}(I)$ according to the neural network,
@@
 
+\bibliographystyle{unsrt}
+{\small \bibliography{main}}
+
 \end{document}

### 2017-05-19 paper.tex
added a single word

@@
 In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the code.
-More generally, we believe that the two-phase system we have proposed---parsing into execution traces, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for domains in which agents must programmatically reason about noisy perceptual input.
+More generally, we believe that the two-phase system we have proposed---parsing into execution traces, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for other domains in which agents must programmatically reason about noisy perceptual input.
 

### 2017-05-19 paper.tex

--- 2017-05-19 paper.tex
@@
 This paper argues that this stage is best achieved by \emph{constraint-based program synthesis} \cite{solar2008program}.
-Without the need for training, the program synthesizer can search the space of possible programs for one capable of producing the desired trace.
+Without the need for training, the program synthesizer can search the space of possible programs for one capable of producing the desired trace -- inducing structures like
+symmetries, repetition, or conditional branches.
 %under a quantitative objective that maximizes the likelihood according to a prior distribution that aims to capture the user’s preference.

### 2017-05-27 paper.tex
ready for archive

@@
 
-\usepackage{nips_2017}
+%\usepackage{nips_2017}
 \usepackage{dsfont}
 % to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[final]{nips_2017}
+\usepackage[final]{nips_2017}
 
@@
 \newcommand{\remark}[1]{\textcolor{red}{[#1]}}
+\newcommand{\exampleImageSize}{2cm}
 
@@
 \author{
-  David S.~Hippocampus\thanks{Use footnote for providing further
-    information about author (webpage, alternative
-    address)---\emph{not} for acknowledging funding agencies.} \\
-  Department of Computer Science\\
-  Cranberry-Lemon University\\
-  Pittsburgh, PA 15213 \\
-  \texttt{hippo@cs.cranberry-lemon.edu} \\
-  %% examples of more authors
-  %% \And
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
-  %% \AND
-  %% Coauthor \\
+Kevin Ellis\\
+  MIT\\
+  \texttt{ellisk@mit.edu} \\
+  \And
+  Daniel Ritchie\\
+Stanford University\\
+ \texttt{dritchie@stanford.edu} \\
+ \And
+ Armando Solar-Lezama\\
+ MIT\\
+\texttt{asolar@csail.mit.edu} \\
+\And
+Joshua B. Tenenbaum \\
+MIT\\
+\texttt{jbt@mit.edu}
   %% Affiliation \\
@@
  machine learning papers (see Figure~\ref{firstPageExamples}a).
- %% \remark{The use of `graphics programs / visual programs' in the paper
- %%   title, title of this section, and the body of this section feels
- %%   too broad. `Graphics program' could conjur a lot of different ideas
- %%   (esp. 3D graphics); don't want to set the reader up to expect one
- %%   thing and then be disappointed that what you've done isn't
- %%   that. You bring up diagram-drawing later in the intro; I think it
- %%   should be made clear sooner (and certainly mentioned explicitly in
- %%   the abstract, when you get around to writing that).}
-
-\newcommand{\exampleImageSize}{2cm}
-\begin{figure}[h]
+\begin{figure}[H]
   \begin{minipage}[t]{0.7\linewidth}  
@@
   \caption{(a): Model learns to convert hand drawings (top) into \LaTeX~(bottom). (b) Synthesizes high-level \emph{graphics program} from hand drawing.}\label{firstPageExamples}
+  \vspace{-1cm}
 \end{figure}
@@
 globally optimal program.
+See Figure~\ref{exampleSynthesisResults} for examples of the kinds of programs our system recovers.
 
@@
   \caption{Example drawings (top) and programs synthesized from their ground truth traces (bottom).
-Note the nested loops in the Ising model (middle), special case conditionals for the HMM (rightmost), combination of symmetry and iteration in middle left, and affine transformation in the leftmost figure.}
+Note the nested loops in the Ising model (middle), special case conditionals for the HMM (rightmost), combination of symmetry and iteration in middle right, and affine transformation in the leftmost figure.}\label{exampleSynthesisResults}
   \end{figure}
@@
 
+\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl on the design of the neural architecture.
+
+\subsubsection*{Supplemental information.} The supplement may be found at:~\url{http://web.mit.edu/ellisk/www/graphicsProgramSupplement.pdf}
+
 %\input{synthesizerOutputs.tex}
 
-\bibliographystyle{unsrt}
-{\small \bibliography{main}}
+\bibliographystyle{unsrt} {\small \bibliography{main}}
 

### 2017-07-21 paper.tex
small changes to spacing
better figures

@@
  machine learning papers (see Figure~\ref{firstPageExamples}a).
-\begin{figure}[H]
+ \begin{figure}[H]\vspace{-0.7cm}
   \begin{minipage}[t]{0.7\linewidth}  
@@
   \caption{(a): Model learns to convert hand drawings (top) into \LaTeX~(bottom). (b) Synthesizes high-level \emph{graphics program} from hand drawing.}\label{firstPageExamples}
-  \vspace{-1cm}
 \end{figure}
@@
 pass a $256\times 256$ target image and a rendering of the trace so
-far (encoded as a two-channel image) to a convolutional network. Given the features extracted by the
-convnet, a multilayer perceptron then predicts a distribution over the
-next drawing command to add to the trace; see Table~\ref{drawingCommandTable}.  We predict the drawing
+far (encoded as a two-channel image) to a convolutional network. Given
+the features extracted by the convnet, a multilayer perceptron then
+predicts a distribution over the next drawing command to add to the
+trace; see Table~\ref{drawingCommandTable}.  We predict the drawing
 command token-by-token, conditioning each token both on the image
-features and on the previously generated tokens.  For example, the
-network first decides to emit the \verb|circle| token conditioned on
-the image features, then it emits the $x$ coordinate of the circle
-conditioned on the image features and the \verb|circle| token, and
-finally it predicts the $y$ coordinate of the circle conditioned on
-the image features, the \verb|circle| token, and the $x$ coordinate.
-See supplement for the full details of the architecture,
-which we implemented in Tensorflow~\cite{tensorflow2015-whitepaper}.
+features and on the previously generated tokens. We also use a
+differentiable attention mechanism (Spatial Transformer
+Networks:~\cite{jaderberg2015spatial}) to let the model attend to
+different regions of the image while predicting each token. For
+example, the network first decides to emit the \verb|circle| token
+conditioned on the image features, then it emits the $x$ coordinate of
+the circle conditioned on the image features and the \verb|circle|
+token, and finally it predicts the $y$ coordinate of the circle
+conditioned on the image features, the \verb|circle| token, and the
+$x$ coordinate.  See supplement for the full details of the
+architecture, which we implemented in
+Tensorflow~\cite{tensorflow2015-whitepaper}.
 %% \remark{There are some more details that are important to provide
@@
 \begin{equation}
-  \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta [t_k | f_\theta(I,\text{render}(T)), \{t_j\}_{j = 1}^{k - 1}]
+  \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(T)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
 \end{equation}
@@
 the target image, $T$ is an execution trace, $\theta$ are the
-parameters of the neural network, and $f_\theta(\cdot,\cdot)$ is the
-image feature extractor (convolutional network). The distribution over
+parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
+image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
 execution traces factorizes as:
@@
   \node(l1) at ([yshift = -2cm]c1.south) {\verb|circle(|};
+  \node[draw,ultra thick,minimum size = 1cm](a2) at ([xshift = 1cm,yshift = 1.5cm]c1.east) {STN};
   \node[draw,ultra thick,minimum size = 1cm](c2) at ([xshift = 1cm]c1.east) {MLP};
+  \draw[->,ultra thick] (a2.south) -- (c2.north);
   \draw[->,ultra thick,red] (c1.south) -- (l1.north);
@@
   \draw[->,ultra thick,red] (c2.south) -- (l2.north);
+  \node[draw,ultra thick,minimum size = 1cm](a3) at ([xshift = 1cm,yshift = 1.5cm]c2.east) {STN};
   \node[draw,ultra thick,minimum size = 1cm](c3) at ([xshift = 1cm]c2.east) {MLP};
+
+  \draw[->,ultra thick] (a3.south) -- (c3.north);
   \node(l3) at ([yshift = -2cm]c3.south) {\verb|Y=12)|};
@@
   \draw[->,ultra thick] (features.north) -- (c1.west);
-  \draw[->,ultra thick] (features.north) to[out = 45,in = 90] (c2.north);
-  \draw[->,ultra thick] (features.north) to[out = 70,in = 90] (c3.north);
+  \draw[->,ultra thick] (features.north) to[out = 45,in = 160] (a2.north);
+  \draw[->,ultra thick] (features.north) to[out = 70,in = 140] (a3.north);
   \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c2.west);
@@
 \texttt{Typewriter font}: network outputs.
-Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}.}  \label{architecture}
+Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}.
+STN (spatial transformer network) is a differentiable attention mechanism~\cite{jaderberg2015spatial}.}  \label{architecture}
 \end{figure}
@@
 itself or SMC by itself.  Only the combination of the two passes a
-critical test of generalization: when trained on images with $\leq 8$
+critical test of generalization: when trained on images with $\leq 12$
 objects, it successfully parses scenes with many more objects than the
@@
 \begin{figure}\centering
-  \begin{minipage}{0.35\textwidth}
-    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-58-7.png}}\end{minipage}
-    \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-33-5.png}}\end{minipage}
+  \begin{minipage}{6cm}
+    \begin{minipage}[t]{2.9cm}\fbox{\includegraphics[width=2.75cm]{figures/randomScene-58-7.png}}\end{minipage}
+    \begin{minipage}[t]{2.9cm}\fbox{\includegraphics[width=2.75cm]{figures/randomScene-33-5.png}}\end{minipage}
     \caption{Network is trained to infer execution traces for randomly generated scenes like the two shown above. See supplement for details of the training data generation.}\label{trainingData}
-  \end{minipage}\hfill
-  \begin{minipage}{0.6\textwidth}
-    \includegraphics[width = 4cm]{figures/editDistance.png}
-    \includegraphics[width = 4cm]{figures/accuracy.png}
+  \end{minipage}\hfill%
+  \begin{minipage}{7.5cm}\centering
+    \includegraphics[width = 7cm]{figures/editDistanceRecurrent.png} 
+%    \includegraphics[width = 4cm]{figures/accuracy.png}
       \caption{Using the model to parse latex output.
-The model is trained on diagrams with up to 8 objects.
+The model is trained on diagrams with up to 12 objects.
 As shown above it generalizes to scenes with many more objects.
@@
 \begin{figure}\centering
-  \begin{minipage}{0.45\textwidth}
-  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/expert-60-reduced.png}
+  \begin{minipage}{0.35\textwidth}
+  \begin{minipage}[t]{\textwidth}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
+    \subcaption{}
+  \end{minipage}\\
+   \begin{minipage}[t]{0.5\textwidth}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
     \subcaption{}
   \end{minipage}%
-   \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/60-groundTruth-reduced.png}
-    \subcaption{}
-  \end{minipage}%
-  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/60-1-reduced.png}
+  \begin{minipage}[t]{0.5\textwidth}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
     \subcaption{}
@@
   \end{minipage}\hfill
-  \begin{minipage}{0.45\textwidth}
-  \includegraphics[width = 6cm]{figures/drawingAccuracy.png}
-  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1,5,10,100)?
-  Distance to ground truth trace measured by the intersection over union of predicted vs. ground truth traces (sets of drawing commands).}\label{drawingIntersectionOverUnion}
+  \begin{minipage}{0.6\textwidth} 
+  \includegraphics[width = 7.5cm]{figures/drawingAccuracy.png}
+  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1,10,100)?
+    Distance to ground truth trace measured by the intersection over union of predicted vs.
+ground truth traces.
+(a) for 62\% of drawings the model's top prediction is exactly correct; (b) for 69\% of drawings the ground truth is in the top 10 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth trace.}\label{drawingIntersectionOverUnion}
     \end{minipage}
@@
 
-\newcommand{\exampleProgramSize}{2.3cm} 
+\newcommand{\exampleProgramSize}{4.5cm} 
+\newcommand{\exampleDrawingSize}{2cm}
+
 \begin{figure}
-  \begin{tabular}{lllll}
-  \includegraphics[width = \exampleProgramSize]{figures/expert-29.png}&
-  \includegraphics[width = \exampleProgramSize]{figures/expert-52.png}&
-  \includegraphics[width = \exampleProgramSize]{figures/expert-38.png}&
-  \includegraphics[width = \exampleProgramSize]{figures/expert-72.png}&
-  \includegraphics[width = \exampleProgramSize]{figures/expert-75.png}\\
-    \begin{minipage}[t]{\exampleProgramSize}
-\begin{Verbatim}[fontsize = \small]
-for(i<3){
-line(i,-1*i+6,
-2*i+2,-1*i+6)
-line(i,-2*i+4,
-i,-1*i+6)
-\end{Verbatim}
+  \begin{tabular}{m{4cm}ll}
+    \toprule
+    Drawing&Trace&Program\\
+    \midrule
+    \includegraphics[width = \exampleDrawingSize]{figures/expert-29-trim.png}&
+\begin{minipage}{\exampleProgramSize}\begin{verbatim}
+Line(2,15, 4,15)
+Line(4,9, 4,13)
+Line(3,11, 3,14)
+Line(2,13, 2,15)
+Line(3,14, 6,14)
+Line(4,13, 8,13)
+\end{verbatim}
+\end{minipage}&     \begin{minipage}{\exampleProgramSize} \begin{verbatim}
+for(i<3)
+ line(i,-1*i+6, 2*i+2,-1*i+6)
+ line(i,-2*i+4,i,-1*i+6)
+       \end{verbatim}
+     \end{minipage}&\\\midrule
+     \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
+\begin{minipage}{\exampleProgramSize}\begin{verbatim}
+Line(5,13, 2,10),
+  arrow = True)
+Circle(center = (5,9)
+Circle(center = (8,5)
+Line(2,8, 2,6), 
+  arrow = True)
+Circle(center = (2,5)
+Circle(center = (5,14)
+Circle(center = (2,9)
+Line(5,13, 8,10), 
+  arrow = True)
+\end{verbatim}
+\emph{... etc. ...}\\
 \end{minipage}&
-    \begin{minipage}[t]{\exampleProgramSize}
-\begin{Verbatim}[fontsize = \small]
+             \begin{minipage}{\exampleProgramSize}\begin{verbatim}
 circle(4,10)
-for(i<3){
+for(i<3)
  circle(-3*i+7,5)
  circle(-3*i+7,1)
-line(-3*i+7,4,
--3*i+7,2,
-arrow=True)
-line(4,9,
--3*i+7,6,
-arrow=True)
-\end{Verbatim}
-\end{minipage}&
-\begin{minipage}[t]{\exampleProgramSize}
-\begin{Verbatim}[fontsize=\small]
+ line(-3*i+7,4,-3*i+7,2,arrow=True)
+ line(4,9,-3*i+7,6,arrow=True)
+\end{verbatim}
+\end{minipage}\\\midrule
+    \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
+\begin{minipage}{\exampleProgramSize}\begin{verbatim}
+Circle(center = (5,8)
+Circle(center = (2,8)
+Circle(center = (8,11)
+Line(2,9, 2,10)
+Circle(center = (8,8)
+Line(3,8, 4,8)
+Line(3,11, 4,11)
+Line(8,9, 8,10)
+Circle(center = (5,14)
+Line(5,9, 5,10)
+Circle(center = (2,14)
+\end{verbatim}
+  \emph{... etc. ...}\\
+\end{minipage}&\begin{minipage}[t]{\exampleProgramSize}
+\begin{verbatim}
 for(i<3)
@@
   if(j>0)
-line(-3*j+8,
--3*i+7,-3*j+9,
--3*i+7)
-line(-3*i+7,-3*j+8,
--3*i+7,
--3*j+9)
+   line(-3*j+8,-3*i+7,-3*j+9,-3*i+7)
+  line(-3*i+7,-3*j+8,-3*i+7,-3*j+9)
   circle(-3*j+7,-3*i+7)
-\end{Verbatim}
+\end{verbatim}
+\end{minipage}\\\midrule
+\includegraphics[width = \exampleDrawingSize]{figures/expert-75-trim.png}&
+\begin{minipage}{\exampleProgramSize}\begin{verbatim}
+Line(11,14, 13,14), 
+  arrow = True)
+Circle(center = (10,10)
+Line(10,13, 10,11), 
+  arrow = True)
+Line(7,14, 9,14), 
+  arrow = True)
+Circle(center = (6,10)
+Circle(center = (2,10)
+Line(3,14, 5,14), 
+  arrow = True)
+\end{verbatim}
+    \emph{... etc. ...}\\
 \end{minipage}&
 \begin{minipage}[t]{\exampleProgramSize}
-\begin{Verbatim}[fontsize=\small]
-reflect(y=8){
-for(i<3){
-if(i>0){
-rectangle(3*i-1,
-2,3*i,3)}
-circle(3*i+1,
-       3*i+1)
-\end{Verbatim}
-\end{minipage}&
- \begin{minipage}[t]{\exampleProgramSize}
-    \begin{Verbatim}[fontsize = \small]
-for(i<4){
-line(-4*i+13,4,
--4*i+13,2,
-arrow=True)
-for(j<3){
-if(j>0){
-circle(-4*i+13,
-4*j+-3)}
-line(-4*j+10,5,
--4*j+12,5,
-arrow=True)
-\end{Verbatim}
-  \end{minipage}
+    \begin{verbatim}
+for(i<4)
+ line(-4*i+13,4,-4*i+13,2,arrow=True)
+ for(j<3)
+  if(j>0)
+   circle(-4*i+13,4*j+-3)
+  line(-4*j+10,5,-4*j+12,5,arrow=True)
+\end{verbatim}
+  \end{minipage}\\\midrule
+
+  \includegraphics[width = \exampleDrawingSize]{figures/expert-72-trim.png}&
+
+\begin{minipage}{\exampleProgramSize}\begin{verbatim}
+Circle(center = (2,8)
+Rectangle(6,9, 7,10)
+Circle(center = (8,8)
+Rectangle(6,12, 7,13)
+Rectangle(3,9, 4,10)
+Circle(center = (2,14)
+Circle(center = (8,14)
+Circle(center = (5,11)
+Rectangle(3,12, 4,13)
+\end{verbatim}
+  \end{minipage}&\begin{minipage}[t]{\exampleProgramSize}
+\begin{verbatim}
+reflect(y=8)
+ for(i<3)
+  if(i>0)
+   rectangle(3*i-1,2,3*i,3)
+  circle(3*i+1,3*i+1)
+\end{verbatim}
+\end{minipage}\\\bottomrule
   \end{tabular}
-  \caption{Example drawings (top) and programs synthesized from their ground truth traces (bottom).
-Note the nested loops in the Ising model (middle), special case conditionals for the HMM (rightmost), combination of symmetry and iteration in middle right, and affine transformation in the leftmost figure.}\label{exampleSynthesisResults}
+  \caption{Example drawings (left), their ground truth traces (middle), and programs synthesized from these traces (right).
+Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformation in the top figure.}\label{exampleSynthesisResults}
   \end{figure}

### 2017-07-21 paper.tex
improved example programs figure

@@
 
-\newcommand{\exampleProgramSize}{4.5cm} 
+\newcommand{\exampleProgramSize}{6cm}
+\newcommand{\exampleTraceSize}{4.5cm}
 \newcommand{\exampleDrawingSize}{2cm}
@@
 \begin{figure}
-  \begin{tabular}{m{4cm}ll}
+  \begin{tabular}{m{2.5cm}ll}
     \toprule
@@
     \includegraphics[width = \exampleDrawingSize]{figures/expert-29-trim.png}&
-\begin{minipage}{\exampleProgramSize}\begin{verbatim}
+\begin{minipage}{\exampleTraceSize}\begin{verbatim}
 Line(2,15, 4,15)
@@
      \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
-\begin{minipage}{\exampleProgramSize}\begin{verbatim}
+\begin{minipage}{\exampleTraceSize}\begin{verbatim}
 Line(5,13, 2,10),
@@
 Circle(center = (2,9)
-Line(5,13, 8,10), 
-  arrow = True)
 \end{verbatim}
@@
  circle(-3*i+7,1)
- line(-3*i+7,4,-3*i+7,2,arrow=True)
- line(4,9,-3*i+7,6,arrow=True)
+ line(-3*i+7,4,-3*i+7,2,
+      arrow=True)
+ line(4,9,-3*i+7,6,
+      arrow=True)
 \end{verbatim}
@@
     \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
-\begin{minipage}{\exampleProgramSize}\begin{verbatim}
+\begin{minipage}{\exampleTraceSize}\begin{verbatim}
 Circle(center = (5,8)
@@
 Circle(center = (5,14)
-Line(5,9, 5,10)
-Circle(center = (2,14)
 \end{verbatim}
   \emph{... etc. ...}\\
-\end{minipage}&\begin{minipage}[t]{\exampleProgramSize}
+\end{minipage}&\begin{minipage}{\exampleProgramSize}
 \begin{verbatim}
@@
 \includegraphics[width = \exampleDrawingSize]{figures/expert-75-trim.png}&
-\begin{minipage}{\exampleProgramSize}\begin{verbatim}
+\begin{minipage}{\exampleTraceSize}\begin{verbatim}
 Line(11,14, 13,14), 
@@
 Circle(center = (2,10)
-Line(3,14, 5,14), 
-  arrow = True)
 \end{verbatim}
@@
 \end{minipage}&
-\begin{minipage}[t]{\exampleProgramSize}
+\begin{minipage}{\exampleProgramSize}
     \begin{verbatim}
 for(i<4)
- line(-4*i+13,4,-4*i+13,2,arrow=True)
+ line(-4*i+13,4,-4*i+13,2,
+      arrow=True)
  for(j<3)
@@
    circle(-4*i+13,4*j+-3)
-  line(-4*j+10,5,-4*j+12,5,arrow=True)
+  line(-4*j+10,5,-4*j+12,5,
+       arrow=True)
 \end{verbatim}
@@
 
-\begin{minipage}{\exampleProgramSize}\begin{verbatim}
+\begin{minipage}{\exampleTraceSize}\begin{verbatim}
 Circle(center = (2,8)
@@
 \end{verbatim}
-  \end{minipage}&\begin{minipage}[t]{\exampleProgramSize}
+  \end{minipage}&\begin{minipage}{\exampleProgramSize}
 \begin{verbatim}
@@
   \caption{Example drawings (left), their ground truth traces (middle), and programs synthesized from these traces (right).
-Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformation in the top figure.}\label{exampleSynthesisResults}
+Compared to the trace the programs are more compressive and automatically group together related drawing commands.
+are Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformation in the top figure.}\label{exampleSynthesisResults}
   \end{figure}

### 2017-07-24 paper.tex
minor changes to figure
included latest data on using the synthesizer to better rank programs

@@
 training data.
+We also compare with a natural baseline that models the problem as a kind of image captioning (``LSTM'' in Figure~\ref{syntheticResults}).
+Given the target image, this baseline produces the program trace in one shot by
+using a CNN to extract features of the input which are passed to an LSTM which finally predicts
+the trace token-by-token.
+This architecture is used in several successful neural models of image captioning (e.g.,~\cite{vinyals2015show}),
+but, for this domain, does not suffice to parse cluttered scenes with many objects.
 
@@
 ground truth traces.
-(a) for 62\% of drawings the model's top prediction is exactly correct; (b) for 69\% of drawings the ground truth is in the top 10 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth trace.}\label{drawingIntersectionOverUnion}
+(a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 10 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth trace.}\label{drawingIntersectionOverUnion}
     \end{minipage}
@@
 to produce many candidate traces for each drawing.
-For 58\% of the drawings, the Top-1 most likely sample exactly matches the
+For 63\% of the drawings, the Top-1 most likely sample exactly matches the
 ground truth; with more samples, the model finds traces
@@
     \toprule
-    Drawing&Trace&Program\\
+    \textbf{Drawing}&\textbf{Trace}&\textbf{Program}\\
     \midrule
@@
 Our sampler could only do better on
-7 drawings by looking at the Top-100 sampled traces
+7/100 drawings by looking at the Top-100 sampled traces
 (see Fig.~\ref{drawingIntersectionOverUnion}),

### 2017-07-24 supplement.tex
ready for archive
better figures
included latest data on using the synthesizer to better rank programs

@@
 % to compile a camera-ready version, add the [final] option, e.g.:
-\usepackage{nips_2017}
+\usepackage[final]{nips_2017}
 
@@
 \author{
-Kevin Ellis \\
-Brain and Cognitive Sciences\\
+Kevin Ellis\\
   MIT\\
-%Pittsburgh, PA 15213 \\
   \texttt{ellisk@mit.edu} \\
+  \And
   Daniel Ritchie\\
-Department of Computer Science\\
-Brown
+Stanford University\\
+ \texttt{dritchie@stanford.edu} \\
  \And
-Armando Solar-Lezama \\
-  CSAIL\\
-MIT \\
+ Armando Solar-Lezama\\
+ MIT\\
 \texttt{asolar@csail.mit.edu} \\
@@
 Joshua B. Tenenbaum \\
-Brain and Cognitive Sciences\\
 MIT\\
-\texttt{jbt@mit.edu} \\
+\texttt{jbt@mit.edu}
+  %% Affiliation \\
+  %% Address \\
+  %% \texttt{email} \\
+  %% \And
+  %% Coauthor \\
+  %% Affiliation \\
+  %% Address \\
+  %% \texttt{email} \\
+  %% \And
+  %% Coauthor \\
+  %% Affiliation \\
+  %% Address \\
+  %% \texttt{email} \\
 }
@@
 example of the kinds of corrections that it makes. On the whole
-it modestly improves our Top-1 accuracy from 58\% to 61\%.  Recall that
+it modestly improves our Top-1 accuracy from 63\% to 67\%.  Recall that
 from Fig. 6 of the main paper that the best improvement
-in accuracy we could possibly get is 65\% by looking at the top 10 traces. 
+in accuracy we could possibly get is 70\% by looking at the top 10 traces. 
 \begin{wrapfigure}{R}{5.5cm}
@@
 The convolutional network takes as input 2 $256\times 256$ images
-represented as a $2\times 256\times 256\times$ volume. These are
+represented as a $2\times 256\times 256$ volume. These are
 passed through two layers of convolutions separated by ReLU
@@
 \end{itemize}
-Training takes a little bit less than a day on a Nvidia TitanX GPU.
-The network was trained on $10^5$ synthetic examples.
 
@@
 
-Given the image features $f$, we predict the first token using logistic regression:
+Given the image features $f$, we predict the first token (i.e., the name of the drawing command: \verb|circle|, \verb|rectangle|, \verb|line|, or \verb|STOP|) using logistic regression:
 \begin{equation}
-  \probability [T_1]\propto W_{T_1}f
+  \probability [T_1]\propto \exp\left( W_{T_1}f + b_{T_1}\right)
 \end{equation}
-where $W_{T_1}$ is a learned weight matrix.
+where $W_{T_1}$ is a learned weight matrix and  $b_{T_1}$ is a learned bias vector.
 
-Subsequent tokens are predicted as:
+Given an attention mechanism $a(\cdot | \cdot)$, subsequent tokens are predicted as:
 \begin{equation}
-  \probability [T_n|T_{1:(n - 1)}]\propto \text{MLP}_{T_1,n}(I \otimes \bigotimes_{j < n} \text{oneHot}(T_j))
+  \probability [T_n|T_{1:(n - 1)}]\propto \text{MLP}_{T_1,n}(a(f|T_{1:(n - 1)}) \otimes \bigotimes_{j < n} \text{oneHot}(T_j))
 \end{equation}
@@
 for other tokens the MLP's are just logistic regression (no hidden nodes).
+
+We use Spatial Transformer Networks~\cite{jaderberg2015spatial}
+as our attention mechanism.
+The parameters of the spatial transform are predicted on the basis of previously predicted tokens.
+For example, in order to decide where to focus our attention when predicting the $y$ coordinate of a circle,
+we condition upon both the identity of the drawing command (\verb|circle|) and upon the value of the previously predicted $x$ coordinate:
+\begin{equation}
+  a(f|T_{1:(n - 1)}) = \text{AffineTransform}(f, \text{MLP}_{T_1,n}(\bigotimes_{j < n}\text{oneHot}(T_j)))
+  \label{spatialTransformEquation}
+\end{equation}
+So, we learn a different network for predicting special transforms
+\emph{for each drawing command} (value of $T_1$) and also \emph{for each token of the drawing command}.
+These networks ($\text{MLP}_{T_1,n}$ in equation~\ref{spatialTransformEquation}) have no hidden layers and
+output the 6 entries of an affine transformation matrix; see~\cite{jaderberg2015spatial}
+for more details.
+
+Training takes a little bit less than a day on a Nvidia TitanX GPU.
+The network was trained on $10^5$ synthetic examples.
 
@@
 For readers wishing to generate their own synthetic training sets,
-we refer them to our source code at:~\url{http://www.redactedForAnonymousReview.com}.
+we refer them to our source code at:~\url{https://github.com/ellisk42/TikZ}.
 

### 2017-07-26 synthesizerOutputs.tex
updated the supplement to have the latest parsing results

@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-71.png}&
-            Sampled no finished traces.&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-71-parses/0.png}&
 
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-73.png}&
-            Sampled no finished traces.&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-73-parses/0.png}&
 
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-94.png}&
-            Sampled no finished traces.&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-94-parses/0.png}&
 

### 2017-07-28 paper.tex
updated the supplement to have the latest parsing results
marginally improved the drawing accuracy plot

@@
 conditioned on the image features, the \verb|circle| token, and the
-$x$ coordinate.  See supplement for the full details of the
-architecture, which we implemented in
+$x$ coordinate. For our main experiments we constrain
+coordinates to lie on a discrete $16\times 16$ grid, and later explain
+how to remove this restriction.  See supplement for the full details
+of the architecture, which we implemented in
 Tensorflow~\cite{tensorflow2015-whitepaper}.
@@
 %%   network layer sizes, which MLPs share parameters, etc.}
-The distribution over the next drawing command factorizes as:
-\begin{equation}
-  \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(T)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
-\end{equation}
-where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
-the target image, $T$ is an execution trace, $\theta$ are the
-parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
-image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
-execution traces factorizes as:
-\begin{equation}
-  \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
-\end{equation}
-where $|T|$ is the length of execution trace $T$, the subscripts
-on $T$ index drawing commands within the trace, and the \verb|STOP|
-token is emitted by the network to signal that the trace
-explains the image.
-%% ~\remark{Make explicit that a $T_n$ in Equation 2
-%%   is a concise way of referring to a sequence of tokens from Equation
-%%   1?}
 
-We train the network by sampling execution traces $T$ and target
-images $I$ for randomly generated scenes
-and maximizing
-(\ref{objective}) with respect to $\theta$ by gradient ascent.
-Training does not require backpropagation across the entire sequence of drawing commands:
-drawing to the canvas `blocks' the gradients,
-effectively offloading memory to an external visual store.
-In a sense, this model is like an autoregressive variant of AIR~\cite{eslami1603attend} without attention.
-We trained the network on $10^5$ scenes, which takes a little less than a day on an Nvidia TitanX GPU.
-
-%% \remark{I like that you make this connection, but it could be made more precisely.
-Specifically, (1) the architecture isn't \emph{really} recurrent (it uses no hidden state cells), so it'd be good to use a different term or drop this part of the point: (2) training of recurrent nets is also typically fully-supervised (Most RNNs lack latent variables per timestep)---if you're thinking about AIR specifically, maybe just say that, and (3) it's like an autogressive AIR \emph{without attention}.}
-%% \remark{Something related to this that's also cool to point out: training this model doesn't require backpropagation across the entire sequence of drawing commands (drawing to the canvas `blocks' the gradients, effectively offloading memory to an external (visual) store, so in principle it might be scalable to much longer sequences.}
-
-%% When we
-%% have the generative model (the rendering function) and treat the trace
-%% as fully observed, we need not solve an unsupervised or reinforcement
-%% learning problem.
 \tikzset{>=latex}
-\begin{figure}
+\begin{figure}[h]
   \begin{tikzpicture}
@@
   \node[draw,ultra thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 3cm] (CNN) at (4.5,-2.5) {CNN};
-  \node[inner sep = 0pt](tensorProduct) at ([xshift = -1.5cm]CNN.west) {$\bigotimes$};
+  \node[inner sep = 0pt](tensorProduct) at ([xshift = -1.5cm]CNN.west) {$\bigoplus$};
 
@@
 \end{tabular}
-\caption{The deep network in (\ref{architecture}) predicts drawing commands, shown above.}
+\caption{The deep network in Fig.~\ref{architecture} predicts drawing commands, shown above.}
 \label{drawingCommandTable}
@@
 
-This network suffices to ``derender'' synthetic images like those shown in
+For the model in Fig.~\ref{architecture}, the distribution over the next drawing command factorizes as:
+\begin{equation}
+  \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(T)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
+\end{equation}
+where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
+the target image, $T$ is an execution trace, $\theta$ are the
+parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
+image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
+execution traces factorizes as:
+\begin{equation}
+  \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
+\end{equation}
+where $|T|$ is the length of execution trace $T$, the subscripts
+on $T$ index drawing commands within the trace, and the \verb|STOP|
+token is emitted by the network to signal that the trace
+explains the image.
+
+We train the network by sampling execution traces $T$ and target
+images $I$ for randomly generated scenes
+and maximizing
+Eq.~\ref{objective} with respect to $\theta$ by gradient ascent.
+We trained the network on $10^5$ scenes, which takes a little less than a day on an Nvidia TitanX GPU.
+
+Training does not require backpropagation across the entire sequence
+of drawing commands: drawing to the canvas `blocks' the gradients,
+effectively offloading memory to an external visual store.  In a
+sense, this model is like an autoregressive variant of
+AIR~\cite{eslami1603attend}, but critically, \emph{without a learned
+  recurrent memory state}, e.g. an RNN.  We can do without an RNN
+because we have access to ground truth (image, trace) pairs.  This
+allows handling scenes with a very large number of objects without
+having to worry about the conditioning of gradients as they propagate
+over long sequences, and also makes training more straightforward (it
+is just maximum likelihood estimation of the model parameters).
+
+Our network suffices to ``derender'' synthetic images like those shown in
 Figure~\ref{trainingData}.  We can perform a beam search decoding to
@@
 \probability_\theta[T|I]$, where $L(\cdot | \cdot):\text{image}^2\to
-\mathcal{R}$ uses the distance between two images as a proxy for a
-likelihood.
-%
+\mathbb{R}$ uses the distance between two images as a proxy for a
+likelihood. Unconventionally, the target distribution of the SMC sampler
+includes the likelihood under the proposal distribution.
+Intuitively, both the proposal
+distribution and the distance function offer complementary signals for
+whether a drawing command is correct. Empirically, accuracy is much
+better when we combine these signals.
+
 Figure~\ref{syntheticResults}
@@
 
-\begin{figure}\centering
+\begin{figure}[H]\centering
   \begin{minipage}{6cm}
-    \begin{minipage}[t]{2.9cm}\fbox{\includegraphics[width=2.75cm]{figures/randomScene-58-7.png}}\end{minipage}
-    \begin{minipage}[t]{2.9cm}\fbox{\includegraphics[width=2.75cm]{figures/randomScene-33-5.png}}\end{minipage}
+    \begin{minipage}[t]{3cm}\fbox{\includegraphics[width=2.75cm]{figures/randomScene-58-7.png}}\end{minipage}%
+    \begin{minipage}[t]{3cm}\fbox{\includegraphics[width=2.75cm]{figures/randomScene-33-5.png}}\end{minipage}
     \caption{Network is trained to infer execution traces for randomly generated scenes like the two shown above. See supplement for details of the training data generation.}\label{trainingData}
@@
 %    \includegraphics[width = 4cm]{figures/accuracy.png}
-      \caption{Using the model to parse latex output.
-The model is trained on diagrams with up to 12 objects.
-As shown above it generalizes to scenes with many more objects.
+      \caption{Parsing latex output after training on diagrams with $\leq 12$ objects.
+It generalizes to scenes with many more objects.
 Neither the stochastic search nor the neural network are sufficient on their own.
@@
 We designed this noise process to introduce the kinds of variations found in hand drawings (Figure~\ref{handDrawingExamples}; see supplement for details).
+
+\begin{wrapfigure}{R}{6cm}
+\centering  \begin{minipage}[t]{2.5cm}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
+    \subcaption{}
+  \end{minipage}\\
+   \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
+    \subcaption{}
+  \end{minipage}%
+  \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
+    \subcaption{}
+  \end{minipage}%
+    \caption{(a): a hand drawing.
+(b): Rendering of the trace our model infers for (a).
+We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) for a noisy rendering of (b).}\label{handDrawingExamples}
+\end{wrapfigure}
+
 Our neurally-guided SMC procedure
@@
 which is  the number of drawing commands by which two traces differ:
-\begin{equation}
--\log L_{\text{learned}}(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|\label{symmetricDistance}
-\end{equation}
+\begin{multline}
+-\log L_{\text{learned}}(\text{render}(T_1)|\text{render}(T_2))\approx\\ |T_1 - T_2| + |T_2 - T_1|\label{symmetricDistance}
+\end{multline}
 Intuitively,
@@
 These were drawn carefully but not perfectly.
-Our model assumes that objects are snapped to a $16\times 16$ grid, so
+Because our model assumes that objects are snapped to a $16\times 16$ grid, 
 we made the drawings on graph paper.
-\begin{figure}\centering
-  \begin{minipage}{0.35\textwidth}
-  \begin{minipage}[t]{\textwidth}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
-    \subcaption{}
-  \end{minipage}\\
-   \begin{minipage}[t]{0.5\textwidth}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
-    \subcaption{}
-  \end{minipage}%
-  \begin{minipage}[t]{0.5\textwidth}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
-    \subcaption{}
-  \end{minipage}%
-    \caption{(a): a hand drawing.
-(b): Rendering of the trace our model infers for (a).
-We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) for a noisy rendering of (b).}\label{handDrawingExamples}
-  \end{minipage}\hfill
-  \begin{minipage}{0.6\textwidth} 
-  \includegraphics[width = 7.5cm]{figures/drawingAccuracy.png}
-  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1,10,100)?
-    Distance to ground truth trace measured by the intersection over union of predicted vs.
-ground truth traces.
-(a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 10 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth trace.}\label{drawingIntersectionOverUnion}
-    \end{minipage}
-\end{figure}
+
+For each drawing we annotated a ground truth trace and asked the neurally guided SMC sampler
+to produce many candidate traces for each drawing.
+For 63\% of the drawings, the Top-1 most likely sample exactly matches the
+ground truth; with more samples, the model finds traces
+that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
+Because our current model sometimes makes mistakes on hand drawings,
+we envision it working as follows:
+a user sketches a diagram,
+and the system responds by proposing a few candidate interpretations.
+The user could then select the one closest to their intention and edit it if necessary.
 
@@
   \begin{minipage}[t]{2.25cm}
-    \includegraphics[width = 2cm]{figures/expert-10.png}
-    \includegraphics[width = 2cm]{figures/10-parse.png}    
-    \subcaption{Noisy input}
+    \includegraphics[width = 2cm]{figures/expert-73.png}
+    \includegraphics[width = 2cm]{figures/73-parse.png}     
+    \subcaption{A recurrent network architecture}
   \end{minipage}
@@
     \includegraphics[width = 2cm]{figures/38-parse.png}     
-    \subcaption{Failing on a Ising model}
+    \subcaption{Ising model}
   \end{minipage}
@@
     \includegraphics[width = 2cm]{figures/34-parse.png}     
-    \subcaption{Illusory contours}
+    \subcaption{Illusory contours (note: no SMC)}
     \end{minipage}
@@
 See also Fig.~\ref{firstPageExamples}.
-Stochastic search (SMC) can help correct for these errors, as can the program synthesizer (Section~\ref{synthesizerHelpsParsing})}\label{lotsOfHandDrawings}%~\remark{Showing `failure cases' (the last three above) out-of-context seems not great.
-Perhaps remind people in the caption that stochastic search can help correct some of these issues?}
+Stochastic search (SMC) can help correct for these errors, as can the program synthesizer (Section~\ref{synthesizerHelpsParsing})}\label{lotsOfHandDrawings}
 \end{figure}
-For each drawing we annotated a ground truth trace and asked the neurally guided SMC sampler
-to produce many candidate traces for each drawing.
-For 63\% of the drawings, the Top-1 most likely sample exactly matches the
-ground truth; with more samples, the model finds traces
-that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
-Because our current model sometimes makes mistakes, % on hand drawings,
-we envision it working as follows:
-a user sketches a diagram,
-and the system responds by proposing a few candidate interpretations.
-The user could then select the one closest to their intention and edit it if necessary.
+
+\begin{figure}[h]\centering
+  \begin{minipage}{0.8\textwidth} 
+\centering  \includegraphics[width = 8cm]{figures/drawingAccuracy.png} 
+  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1,10,100)?
+    Distance to ground truth trace measured by the intersection over union of predicted vs.
+ground truth traces.
+(a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 10 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth trace.}\label{drawingIntersectionOverUnion}
+    \end{minipage}
+\end{figure}
 
@@
 globally optimal program.
+In practice, synthesis times vary from a few minutes to a few hours,
+with 16\% of the diagrams timing out the synthesizer after 3 hours.
 See Figure~\ref{exampleSynthesisResults} for examples of the kinds of programs our system recovers.
@@
 Compared to the trace the programs are more compressive and automatically group together related drawing commands.
-are Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformation in the top figure.}\label{exampleSynthesisResults}
+Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformation in the top figure.}\label{exampleSynthesisResults}
   \end{figure}
@@
 \subsection{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
+\begin{wrapfigure}{r}{5.5cm}\vspace{-1cm}
+  \includegraphics[width = 5cm]{figures/programSuccess7.png}
+  \includegraphics[width = 5cm]{figures/programSuccess16.png}
+  \caption{Left: hand drawings.
+Center: interpretations favored by the deep network.
+Right: interpretations favored after learning a prior over programs.
+Our learned prior favors shorter, simpler programs, thus (top example) continuing the pattern of not having an arrow is preferred, or (bottom example) continuing the ``binary search tree'' is preferred.}\label{exampleOfProgramCorrectingMistake}
+%  \vspace{1cm}
+  \end{wrapfigure}
 The program synthesizer can correct errors from the execution
 trace proposal network by favoring traces which lead to more
-concise or general programs.  For example, figures with perfectly aligned objects are preferrale to figures whose parts are slightly misaligned, and precise alignment lends itself to short
+concise or general programs.  For example, figures with perfectly aligned objects are preferable to figures whose parts are slightly misaligned, and precise alignment lends itself to short
 programs.  Concretely, we estimated a prior over programs. Then,
@@
 See supplement for details.
-\begin{wrapfigure}{R}{5.5cm}
-  \includegraphics[width = 5cm]{figures/programSuccess7.png}
-  \caption{Left: hand drawing.
-Center: interpretation favored by the deep network.
-Right: interpretation favored after learning a prior over programs.
-Our learned prior favors shorter, simpler programs, thus continuing the pattern of not having an arrow is preferred.}\label{exampleOfProgramCorrectingMistake}
-  \end{wrapfigure}
 
@@
 (PCA); see Fig.\ref{NMF}.  One could use many
-alternative similarity metrics between drawings which would capture pixel-level while missing high-level geometric similarities.
+alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
 We used our learned distance metric between execution traces, $L_{\text{learned}}(\cdot|\cdot)$, and projected to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}).
@@
 while missing similarities at the level of the program.
-\begin{figure}
-  \begin{minipage}{0.48\textwidth}
-    \includegraphics[width = \textwidth]{figures/PCA.png}
+\begin{figure}[h]
+\centering  \begin{minipage}{\textwidth}\centering
+    \includegraphics[width = 0.69\textwidth]{figures/PCA.png}
     \caption{PCA on features of the programs that were synthesized for each drawing. Symmetric figures cluster to the right; ``loopy'' figures cluster to the left.}    \label{NMF}
-  \end{minipage}\hfill
-  \begin{minipage}{0.48\textwidth}
-    \includegraphics[width = \textwidth]{figures/imageSimilarity.png} 
+  \end{minipage} %\hfill
+  \begin{minipage}{\textwidth}\centering
+    \includegraphics[width = 0.69\textwidth]{figures/imageSimilarity.png} 
     \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
@@
 
+\pagebreak
 \subsection{Extrapolating figures}
@@
 
-\begin{figure}
+\begin{figure}[h]
   \includegraphics[width = \textwidth]{figures/extrapolationMatrix1.png}
@@
 
-\section{Conclusion}
+\section{Discussion}
+
+\subsection{Future work}
+There are many directions for future work.
+The proposal network  currently handles only a very small subset of \LaTeX~drawing commands, though there is no reason that it could not be extended to handle more with a higher-capacity network.
+In the synthesis phase, a more expressive DSL---including subroutines, recursion, and symmetry groups beyond reflections---would allow the system to effectively model a wider variety of graphical phenomena.
+The synthesizer itself could also be the subject of future work: the system currently uses the general-purpose Sketch synthesizer, which can take minutes to hours to run, whereas program synthesizers which are custom-built for special problem domains can run much faster or even interactively~\cite{le2014flashextract}.
+
+In the parsing phase, the proposal network currently samples positional variables on a discrete $16\times 16$ grid.
+More general types of drawings could be supported by instead sampling from continuous distributions, e.g.
+using Mixture Density Networks~\cite{MDN}.
+Implementing a variant of our model that predicts continuous coordinates
+using Mixture Density Networks is straightforward;
+we have prototyped such a system and
+show examples of it working in the supplement.
+But, for our collection of hand drawings, discrete positional variables suffice.
+
+\subsection{Contributions}
 
@@
 We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings and to organize them according to high-level geometric features.
-
-There are many directions for future work.
-In the parsing phase, the proposal network currently samples positional variables on a discrete grid.
-More general types of drawings could be supported by instead sampling from continuous distributions, e.g.
-using Mixture Density Networks~\cite{MDN}.
-The proposal network also currently handles only a very small subset of \LaTeX~drawing commands, though there is no reason that it could not be extended to handle more with a higher-capacity network.
-Exploring more sophisticated network architectures, including ones that utilize attention~\cite{mnih2014recurrent}, could help correct some of the errors the network makes.
-In the synthesis phase, a more expressive DSL---including subroutines, recursion, and symmetry groups beyond reflections---would allow the system to effectively model a wider variety of graphical phenomena.
-The synthesizer itself could also be the subject of future work: the system currently uses the general-purpose Sketch synthesizer, which can take minutes to hours to run, whereas program synthesizers which are custom-built for special problem domains can run much faster or even interactively~\cite{le2014flashextract}.
 

### 2017-07-28 supplement.tex
updated the supplement to have the latest parsing results
marginally improved the drawing accuracy plot

@@
   \includegraphics[width = 5cm]{figures/programSuccess7.png}
+  \includegraphics[width = 5cm]{figures/programSuccess16.png}
   \caption{Left: hand drawing.
@@
 Right: interpretation favored after learning a prior over programs.
-Our learned prior favors shorter, simpler programs, thus continuing the pattern of not having an arrow is preferred.}\label{exampleOfProgramCorrectingMistake}
+Our learned prior favors shorter, simpler programs, thus (top example) continuing the pattern of not having an arrow is preferred, or (bottom example) continuing the binary search tree is preferred.}\label{exampleOfProgramCorrectingMistake}
 \end{wrapfigure}
@@
 \begin{equation}
-  \probability [T_1]\propto \exp\left( W_{T_1}f + b_{T_1}\right)
+  \probability [t_1]\propto \exp\left( W_{t_1}f + b_{t_1}\right)
 \end{equation}
-where $W_{T_1}$ is a learned weight matrix and  $b_{T_1}$ is a learned bias vector.
+where $W_{t_1}$ is a learned weight matrix and  $b_{t_1}$ is a learned bias vector.
 
@@
 \begin{equation}
-  \probability [T_n|T_{1:(n - 1)}]\propto \text{MLP}_{T_1,n}(a(f|T_{1:(n - 1)}) \otimes \bigotimes_{j < n} \text{oneHot}(T_j))
+  \probability [t_n|t_{1:(n - 1)}]\propto \text{MLP}_{t_1,n}(a(f|t_{1:(n - 1)}) \oplus \bigoplus_{j < n} \text{oneHot}(t_j))\label{discreteTokenPrediction}
 \end{equation}
@@
 \begin{equation}
-  a(f|T_{1:(n - 1)}) = \text{AffineTransform}(f, \text{MLP}_{T_1,n}(\bigotimes_{j < n}\text{oneHot}(T_j)))
+  a(f|t_{1:(n - 1)}) = \text{AffineTransform}(f, \text{MLP}_{t_1,n}(\bigoplus_{j < n}\text{oneHot}(t_j)))
   \label{spatialTransformEquation}
@@
 So, we learn a different network for predicting special transforms
-\emph{for each drawing command} (value of $T_1$) and also \emph{for each token of the drawing command}.
-These networks ($\text{MLP}_{T_1,n}$ in equation~\ref{spatialTransformEquation}) have no hidden layers and
+\emph{for each drawing command} (value of $t_1$) and also \emph{for each token of the drawing command}.
+These networks ($\text{MLP}_{t_1,n}$ in equation~\ref{spatialTransformEquation}) have no hidden layers and
 output the 6 entries of an affine transformation matrix; see~\cite{jaderberg2015spatial}
@@
 The network was trained on $10^5$ synthetic examples.
+
+\section{Predicting continuous coordinates using Mixture Density Networks}
+
+Our main paper describes a neural model for parsing hand drawings
+into~\LaTeX, but comes with the restriction that all of the
+coordinates of all the drawing commands are snapped to a $16\times 16$
+grid. Now we describe a variant of our model that
+can predict continuous real valued coordinates.
+
+The key obstacle to overcome is \emph{multimodality}: if the network
+is unsure whether it should predict a coordinate value of $a$ or $b$,
+we wish to predict a distribution that splits its mass between $a$ and
+$b$, rather than predicting the single value $\frac{a + b}{2}$.  In
+the model where everything is snapped to a discrete grid, supporting
+this multimodality falls out naturally from our parameterization of
+the network predictions (i.e., the network predicts the parameters of
+a multinomial distribution). To predict continuous real valued
+coordinates we turn to Mixture Density Networks (MDN:~\cite{MDN}).  In
+an MDN, a distribution over a real-valued random variable is
+parameterized using a mixture of Gaussians, and the deep network
+predicts the parameters of the Gaussian mixture.
+
+Concretely,
+we modify our autoregressive drawing command decoder to
+predict distributions over real-valued coordinates
+as:
+\begin{equation}
+  p(t_n|t_{1:(n - 1)}) = \text{MDN}_{t_1,n} (a(f|t_{1:(n - 1)}) \oplus \bigoplus_{j < n} t_j)\text{, if }n^{\text{th}}\text{ token is continuous}
+\end{equation}
+Compare this equation with Equation~\ref{discreteTokenPrediction} to see that we have only
+replaced a draw from a multinomial (whose parameters are predicted by an MLP)
+with a draw from a mixture of Gaussians (whose parameters are predicted by an MDN).
+Otherwise the two models are identical.
+
+For an MDN $i$ with $K$ mixture components that takes as input $x$, we parameterize it's output distribution as:
+\begin{eqnarray}
+  \text{MDN}_i(x) &=& \sum_{1\leq k\leq K} \pi_{i,k}(x)\times \mathcal{N}(\mu_{i,k}(x),\sigma^2_{i,k}(x))\\
+  \mu_{i,k}(x)& = &\text{sigmoid} (W^{\mu_{i,k}}x + b^{\mu_{i,k}}x)\label{mixtureMean}
+  \\\sigma^2_{i,k}(x)& = &\log \left(1 + \exp\left(W^{\sigma^2_{i,k}}x + b^{\sigma^2_{i,k}}x\right) \right)
+  \\\pi_{i,k}(x)& = &\frac{\exp\left(W^{\pi_{i,k}}x + b^{\pi_{i,k}}x \right)}{\sum_{k'} \exp\left(W^{\pi_{i,k'}}x + b^{\pi_{i,k'}}x \right)}
+  \end{eqnarray}
+where $W$ with a superscript is a learned weight matrix and $b$ is a
+learned bias vector. Notice that Equation~\ref{mixtureMean} normalizes
+the predicted means to be within $[0,1]$: this is because we wish to
+constrain the predicted coordinates to lie within the plane
+$[0,1]^2$. We used $K = 16$ mixture components.
+
+\subsection{LSTM Baseline}
+
+We  compared our deep network with a baseline that models the problem as a kind of image captioning.
+Given the target image, this baseline produces the program trace in one shot by
+using a CNN to extract features of the input which are passed to an LSTM which finally predicts
+the trace token-by-token.
+This general architecture is used in several successful neural models of image captioning (e.g.,~\cite{vinyals2015show}).
+
+Concretely, we kept the image feature extractor architecture (a CNN) as in our model,
+but only passed it one image as input (the target image to explain).
+Then, instead of using an autoregressive decoder to predict a single drawing command,
+we used an LSTM to predict a sequence of drawing commands token-by-token.
+This LSTM had 128 memory cells,
+and at each time step produced as output the next token in the sequence of drawing commands.
+It took as input both the image representation and its previously predicted token.
 

### 2017-07-29 paper.tex
mixture density network description for supplement

@@
 
-  \draw[-{>[scale = 1.5]},very thick,dashed] (next.west) -- ([yshift = -0.2cm]canvas.east) node [midway, below, sloped] (TextNode) {Renderer: \LaTeX~Ti\emph{k}Z};
+  \draw[-{>[scale = 1.5]},very thick,dashed] (next.west) -- ([yshift = -0.2cm]canvas.east) node [midway, below, sloped] (TextNode) {Renderer}; %: \LaTeX~Ti\emph{k}Z};
 
@@
 More general types of drawings could be supported by instead sampling from continuous distributions, e.g.
-using Mixture Density Networks~\cite{MDN}.
+using Mixture Density Networks (MDN)~\cite{MDN}.
 Implementing a variant of our model that predicts continuous coordinates
@@
 we have prototyped such a system and
-show examples of it working in the supplement.
-But, for our collection of hand drawings, discrete positional variables suffice.
+show examples of it both working and failing in the supplement.
+But, for our collection of hand drawings, discrete positional variables suffice,
+and currently work much better in practice.
+Engineering better handling of the MDN variant of our model is a prime target for future research.
 

### 2017-07-29 supplement.tex
mixture density network description for supplement

@@
 
-\section{Predicting continuous coordinates using Mixture Density Networks}
+\subsection{Predicting continuous coordinates using Mixture Density Networks}
 
@@
 \begin{equation}
-  p(t_n|t_{1:(n - 1)}) = \text{MDN}_{t_1,n} (a(f|t_{1:(n - 1)}) \oplus \bigoplus_{j < n} t_j)\text{, if }n^{\text{th}}\text{ token is continuous}
+  p(t_n|t_{1:(n - 1)}) = \text{MDN}_{t_1,n} (a(f|t_{1:(n - 1)}) \oplus \bigoplus_{j < n} t_j)\text{, if }n^{\text{th}}\text{ token is continuous}\label{continuousDensityEquation}
 \end{equation}
@@
 
+Figure~\ref{syntheticContinuous}  shows the behavior of the MDN variant of our model on noisy synthetic drawings.
+Contrast these mediocre results with Figure~4 of the main paper to see that although
+our main model is essentially at ceiling for parsing scenes like these,
+the MDN variant fares poorly in comparison.
+\begin{figure}
+  \includegraphics[width = \textwidth]{figures/syntheticContinuous.png}
+  \caption{Left column: \LaTeX~output corrupted by noise process designed to resemble the variability is introduced by hand drawings.
+Right columns: samples from the MDN variant of the model.}\label{syntheticContinuous}
+\end{figure}
+
+We evaluated the MDN version of our model on hand drawings by (1)
+performing a beam search in order to find the trace maximizing
+$\probability [T|I]$, and (2) constraining the predicted coordinates
+to lie on the $16\times 16$ grid. We constrain the predicted coordinates
+to lie on the grid by integrating the predicted densities about each grid location.
+So, using the probability density $p(t_n|t_{1:(n - 1)})$ in Eq.~\ref{continuousDensityEquation},
+we compute a probability mass function $\probability [t_n|t_{1:(n - 1)}]$ as:
+\begin{equation}
+  \probability [t_n = t|t_{1:(n - 1)}] = \int_{t - \frac{1}{2}}^{t + \frac{1}{2}} \mathrm{d}t_n \; p(t_n|t_{1:(n - 1)})\label{constrainingEquation}
+\end{equation}
+Even after using Eq.~\ref{constrainingEquation} to constrain the predicted coordinates to lie on the $16\times 16$ grid, the MDN variant of the model only produces finished traces for 48/100 of the drawings.
+See Figure~\ref{continuousParses} to see the traces recovered by the beam search.
+
+\begin{figure}
+  \includegraphics[width = \textwidth]{figures/continuousParses.png}
+  \caption{Parsing hand drawings using the MDN variant of our
+    model. Black-on-white: hand drawings. White-on-black, below each
+    hand drawing: the parse inferred by the model.}\label{continuousParses} 
+  \end{figure}
 \subsection{LSTM Baseline}

### 2017-07-30 makeArchive.sh
arxiv posting

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+rm -r archive archive.tar
+mkdir archive
+mkdir archive/figures
+
+cp paper.tex main.bib paper.bbl nips_2017.sty /usr/share/texlive/texmf-dist/tex/latex/natbib/natbib.sty archive
+
+cp `grep png paper.tex|sed 's/.*figures/figures/'|sed 's/}.*//'` archive/figures
+tar cvf archive.tar archive/

### 2017-08-29 paper.tex
arxiv posting
compression factor illustration for synthesized program examples

@@
 % if you need to pass options to natbib, use, e.g.:
-% \PassOptionsToPackage{numbers, compress}{natbib}
+\PassOptionsToPackage{numbers, compress}{natbib}
 % before loading nips_2017
@@
   Daniel Ritchie\\
-Stanford University\\
- \texttt{dritchie@stanford.edu} \\
+Brown University\\
+ \texttt{daniel\_ritchie@brown.edu} \\
  \And
@@
 \begin{figure}[h]\centering
-  \begin{minipage}{0.8\textwidth} 
+\vspace{-0.25cm}  \begin{minipage}{0.8\textwidth} 
 \centering  \includegraphics[width = 8cm]{figures/drawingAccuracy.png} 
@@
   program} better describe such structures;
-we seek to synthesize simple graphics graphics from their execution traces.
+we seek to synthesize simple graphics from their execution traces.
 
@@
 
-\newcommand{\exampleProgramSize}{6cm}
-\newcommand{\exampleTraceSize}{4.5cm}
+\newcommand{\exampleProgramSize}{4.5cm}
+\newcommand{\exampleTraceSize}{4cm}
 \newcommand{\exampleDrawingSize}{2cm}
@@
 \begin{figure}
-  \begin{tabular}{m{2.5cm}ll}
+\hspace{-0.7cm}  \begin{tabular}{m{2.5cm}llc}
     \toprule
-    \textbf{Drawing}&\textbf{Trace}&\textbf{Program}\\
+    \textbf{Drawing}&\textbf{Trace}&\textbf{Program}&\begin{tabular}{c}
+      \textbf{Compression}\\\textbf{factor}
+      \end{tabular}\\
     \midrule
@@
        \end{verbatim}
-     \end{minipage}&\\\midrule
+     \end{minipage}&$\frac{6}{3} = 2\text{x}$\\\midrule
      \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
@@
   arrow = True)
-Circle(center = (5,9)
-Circle(center = (8,5)
+Circle(5,9)
+Circle(8,5)
 Line(2,8, 2,6), 
   arrow = True)
-Circle(center = (2,5)
-Circle(center = (5,14)
-Circle(center = (2,9)
+Circle(2,5)
+Circle(5,14)
+Circle(2,9)
 \end{verbatim}
-\emph{... etc. ...}\\
+\emph{... etc. ...; 13 lines}\\
 \end{minipage}&
@@
 \end{verbatim}
-\end{minipage}\\\midrule
+\end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
     \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
 \begin{minipage}{\exampleTraceSize}\begin{verbatim}
-Circle(center = (5,8)
-Circle(center = (2,8)
-Circle(center = (8,11)
+Circle(5,8)
+Circle(2,8)
+Circle(8,11)
 Line(2,9, 2,10)
-Circle(center = (8,8)
+Circle(8,8)
 Line(3,8, 4,8)
@@
 Line(8,9, 8,10)
-Circle(center = (5,14)
+Circle(5,14)
 \end{verbatim}
-  \emph{... etc. ...}\\
+  \emph{... etc. ...; 21 lines}\\
 \end{minipage}&\begin{minipage}{\exampleProgramSize}
@@
   if(j>0)
-   line(-3*j+8,-3*i+7,-3*j+9,-3*i+7)
-  line(-3*i+7,-3*j+8,-3*i+7,-3*j+9)
+   line(-3*j+8,-3*i+7,
+        -3*j+9,-3*i+7)
+  line(-3*i+7,-3*j+8,
+       -3*i+7,-3*j+9)
   circle(-3*j+7,-3*i+7)
 \end{verbatim}
-\end{minipage}\\\midrule
+\end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
 \includegraphics[width = \exampleDrawingSize]{figures/expert-75-trim.png}&
@@
   arrow = True)
-Circle(center = (10,10)
+Circle(10,10)
 Line(10,13, 10,11), 
@@
   arrow = True)
-Circle(center = (6,10)
-Circle(center = (2,10)
+Circle(6,10)
+Circle(2,10)
 \end{verbatim}
-    \emph{... etc. ...}\\
+    \emph{... etc. ...; 15 lines}\\
 \end{minipage}&
@@
 \end{verbatim}
-  \end{minipage}\\\midrule
+  \end{minipage}&$\frac{15}{6} = 2.5\text{x}$\\\midrule
 
@@
 \begin{minipage}{\exampleTraceSize}\begin{verbatim}
-Circle(center = (2,8)
+Circle(2,8)
 Rectangle(6,9, 7,10)
-Circle(center = (8,8)
+Circle(8,8)
 Rectangle(6,12, 7,13)
 Rectangle(3,9, 4,10)
-Circle(center = (2,14)
-Circle(center = (8,14)
-Circle(center = (5,11)
+Circle(2,14)
+Circle(8,14)
+Circle(5,11)
 Rectangle(3,12, 4,13)
@@
 \end{verbatim}
-\end{minipage}\\\bottomrule
+\end{minipage}&$\frac{9}{5} = 1.8\text{x}$\\\bottomrule
   \end{tabular}
-  \caption{Example drawings (left), their ground truth traces (middle), and programs synthesized from these traces (right).
-Compared to the trace the programs are more compressive and automatically group together related drawing commands.
+  \caption{Example drawings (left), their ground truth traces (middle left), and programs synthesized from these traces (middle right).
+Compared to the trace the programs are more compressive (right: programs have fewer lines than traces) and automatically group together related drawing commands.
 Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformation in the top figure.}\label{exampleSynthesisResults}
@@
 and currently work much better in practice.
-Engineering better handling of the MDN variant of our model is a prime target for future research.
 

### 2017-10-03 paper.tex
fix another typo
switch to iclr template

@@
 % to compile a camera-ready version, add the [final] option, e.g.:
-\usepackage[final]{nips_2017}
+%\usepackage[final]{nips_2017}
+%ICLR packages:
+\usepackage{iclr2018_conference,times}
 
@@
 not annotate which strokes correspond to which shapes; our neural
-network produces something equivalent to the annotations).  A key
-similarity however is that both CogSketch and our system have as a
-goal to make it easier to produce nice-looking figures.
+network produces something equivalent to the annotations).
+%A key similarity however is that both CogSketch and our system have as a goal to make it easier to produce nice-looking figures.
 Unsupervised Program Synthesis~\cite{ellis2015unsupervised} is a related framework which was also applied to geometric reasoning problems.
@@
 not really trying right now to be automated like our system.
+
+Synthesizing programs from their execution traces is an old
+idea~\cite{Summers:1977:MLP:321992.322002}.  This previous work
+departs from our approach in the nature of the problem (synthesizing
+recursive algorithms in Lisp vs. graphics programs in~\LaTeX) and the
+specifics of the solution (hand-coded source-to-source transformations vs. neural networks
+combined with general-purpose program synthesis techniques).
+What they share is the use of an execution trace as a
+stepping stone toward a full program.
 
@@
   program} better describe such structures;
-we seek to synthesize simple graphics from their execution traces.
+we seek to synthesize simple graphics programs from their execution traces.
 

### 2017-10-20 paper.tex
new writing on learning to synthesize and a new program features PCA result

@@
 symmetries, repetition, or conditional branches.
+Although these program synthesizers do not \emph{need} any training data,
+we show how to combine conventional machine learning with bias optimal search~\cite{schmidhuber2004optimal},
+learning to improve the wall clock speed of these synthesis algorithms by two orders of magnitude.
+
 %under a quantitative objective that maximizes the likelihood according to a prior distribution that aims to capture the user’s preference.
@@
 globally optimal program.
-In practice, synthesis times vary from a few minutes to a few hours,
+In practice, synthesis times vary from a few minutes to a a few hours,
 with 16\% of the diagrams timing out the synthesizer after 3 hours.
 See Figure~\ref{exampleSynthesisResults} for examples of the kinds of programs our system recovers.
+A main impediment here to our use of these general techniques is
+the prohibitively high cost of searching for programs.
+
+\subsection{Learning a search policy for synthesizing programs}
+
+We want to leverage powerful, domain-general techniques from the program synthesis community,
+but make them much faster by
+learning a domain-specific \emph{search policy}.
+A search policy proposes search problems
+like those in Equation~\ref{programObjective},
+but can also offer additional constraints on the structure of the program (Table~\ref{policyOutput}).
+For example, a policy might decide to first try searching over small programs before searching over large programs,
+or decide to prioritize searching over programs that have loops.
+
+A search policy $\pi_\theta(\sigma  | T )$ takes as input a trace $T$ and predicts a distribution over synthesis problems, each of which is written $\sigma $ and corresponds to a set of possible programs to search over (so $\sigma \subset \text{DSL}$).
+Good policies will prefer tractable program spaces,
+so that the search procedure will terminate early.
+Good policies will also prefer program spaces that are likely to contain
+programs that can explain the data.
+In general these two desiderata are in tension:
+tractable synthesis problems involve searching over smaller spaces,
+but smaller spaces are less likely to contain a minimum cost program
+for explaining the trace.
+Our goal now is to find the parameters of the policy, written $\theta$, which best navigate this trade-off.
+
+\begin{table}[h]\centering
+  \begin{tabular}{lll}\toprule
+  Parameter&Description&Range\\\midrule
+  Loops?&Is the program allowed to loop?&$\{\text{True},\text{False}\}$\\
+  Reflects?&Is the program allowed to have reflections?&$\{\text{True},\text{False}\}$\\
+  Incremental?&Solve the problem piece-by-piece or all at once?&$\{\text{True},\text{False}\}$\\
+  Maximum depth& Bound on the depth of the program syntax tree&$\{1,2,3\}$
+  \\\bottomrule
+  \end{tabular}
+  \caption{Parameterization of different ways of posing the program synthesis problem.
+The policy learns to choose parameters likely to quickly yield a minimal cost program.
+In our notation, we write $\sigma $ to mean an assignment to each of these parameters.}\label{policyOutput}
+  \end{table}
+
+Given a search policy, what is the best way of using it to quickly find minimum cost programs?
+We use a \emph{bias-optimal search algorithm} (see Schmidhuber 2004:~\cite{schmidhuber2004optimal}):
+
+\textbf{Definition: Bias optimality.} A search algorithm is $n$-\emph{bias optimal}
+with respect to a distribution $\probability_{\text{bias}}[\cdot ]$ if it is
+guaranteed to find a solution $\sigma $ after searching for at least time
+$n\times\frac{t(\sigma )}{\probability_{\text{bias}}[\sigma ]}$, where $t(\sigma )$ is the time it
+takes to verify that $\sigma $ is a solution to the
+search problem.
+
+An example of a $1$-bias optimal search algorithm is a time-sharing system
+that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to testing $\sigma $.
+We construct a $1$-bias optimal search algorithm for our domain by
+identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |T)$
+and $t(\sigma )  $ with how long the program synthesizer takes to search through the programs in $\sigma $.
+
+In theory any $\pi_\theta(\cdot |\cdot ) $ is a bias-optimal searcher.
+But the real world runtime of the algorithm depends strongly upon
+the bias $\probability_{\text{bias}}[\cdot ]$.
+Our approach is to learn $\probability_{\text{bias}}[\cdot ]$
+by picking the policy that minimizes the
+expected bias-optimal time to solve a training corpus of graphics program synthesis problems,
+which is:
+\begin{align}
+\textsc{Loss}(\theta ; \text{training corpus})& =  \expect_{T\in \text{training corpus}}\left[ \min_{\sigma\in \text{\textsc{Best}}(T)}\frac{t(\sigma | T)}{\pi_\theta (\sigma | T)}\right]\label{policyLoss}\\
+\text{where }  \sigma \in\text{\textsc{Best}}(T) &\text{ iff:  } \text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t. }p\text{ evaluates to }T} \text{cost}(p) \nonumber
+\end{align}
+This loss is differentiable but nonconvex even if $\pi_{\theta}(\cdot |\cdot )^{-1}$ is convex.
+We locally minimize it using gradient descent while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}. See supplement for details.
+
+Because we want to learn a policy from only $100$ hand-drawn sketches,
+we chose a simple low-capacity, bilinear model for a policy:
+\begin{equation}
+  \pi_{\theta}(\sigma |T)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{trace}}(T)\right)
+\end{equation}
+where $\phi_{\text{params}}(\sigma  )$ is a one-hot encoding of
+the parameter settings of $\sigma $ (see Table~\ref{policyOutput})
+and $\phi_{\text{trace}}(T)$ extracts a few simple features of the trace $T$;
+see supplement for details.
+
+We contrast our learned search policy
+with two alternatives (see Figure~\ref{policyEvaluation}):
+(1) \emph{Sketch}, which poses the
+entire problem wholesale to the Sketch program synthesizer;
+and (2) an \emph{Oracle},
+a policy which always picks the quickest to search $\sigma $
+ also containing a minimum cost program.
+Our approach improves upon Sketch by itself,
+and comes close to the Oracle's performance.
+Of course one could never construct such an Oracle,
+because the agent does not know ahead of time which
+$\sigma $'s contain minimum cost programs nor does it know how long each
+$\sigma $ will take to search.
+
+This generalizes and strengthens previous work: Levin
+search~\cite{levin1973universal,solomonoff1984optimum} \&
+OOPS~\cite{schmidhuber2004optimal}: theoretically appealing but
+impractical; fails to leverage either techniques from machine learning
+or from program synthesis. More of a mathematical framing and less of
+an algorithm.  DeepCoder~\cite{BalGauBroetal16}: in addition to
+picking what sort of primitives can go into a program, we are picking
+the details of the search algorithm as well as how deep the algorithms
+should search.  Main difference is that we identify this interesting
+trade-off between tractability and probability of getting a solution.
+TerpreT~\cite{gaunt2016terpret}: suggests that constraint solvers outperform gradient-based search techniques like those used in differentiable neural computers.
+
+Two intuitions: want a model that prefers sketches that are likely to
+contain a valid solution, but at the same time prefers sketches that
+are easy to search.  In general these two preferences are at odds with
+one another.  For example, a sketch which allows very long programs
+and allows lots of primitives is extremely likely to contain a
+shortest program -- but might also take hours for the synthesizer to
+search through.
 
@@
 
-Why synthesize a graphics program,
+With this policy in hand we can now synthesize most programs in under a minute. But why synthesize a graphics program,
 if the execution trace already suffices to recover the objects in an image?
@@
   \includegraphics[width = 0.69\textwidth]{figures/PCA.png}
-    \caption{PCA on features of the programs that were synthesized for each drawing. Symmetric figures cluster to the right; ``loopy'' figures cluster to the left.}    \label{NMF}
+  \includegraphics[width = 0.69\textwidth]{figures/PCA_improved.png}
+    \caption{PCA on features of the programs that were synthesized for each drawing.
+Symmetric figures cluster to the right; ``loopy'' figures cluster to the left; complicated programs are at the top and simple programs are at the bottom.}    \label{NMF}
   \end{minipage} %\hfill

### 2017-10-20 supplement.tex
arxiv posting
compression factor illustration for synthesized program examples
new writing on learning to synthesize and a new program features PCA result

@@
 First,
-the number of objects in the scene are sampled uniformly from 1 to 8.
+the number of objects in the scene are sampled uniformly from 1 to 12.
 For each object we uniformly sample its identity (circle, rectangle, or line).

### 2017-10-20 synthesizerOutputs.tex
new writing on learning to synthesize and a new program features PCA result

--- 2017-05-19 synthesizerOutputs.tex
@@
 arrow = True,solid = True);
-reflect(reflect(y = 9)){
-line(3,2,5,4,
-arrow = True,solid = True);
-rectangle(0,0,8,9);
+reflect(y = 9){
+line(3,7,5,5,
+arrow = True,solid = True);
+rectangle(1,1,3,3);
 rectangle(5,3,7,6);
-rectangle(1,1,3,3)
+rectangle(0,0,8,9)
 }
@@
         \begin{verbatim}
-Solver timeout
+for (i < 2){
+line(8,8,3,8,
+arrow = True,solid = False);
+line(-2 * i + 12,5,-2 * i + 13,5,
+arrow = True,solid = True);
+line(6,5,7,5,
+arrow = True,solid = True);
+line(3,-6 * i + 8,5,-2 * i + 6,
+arrow = True,solid = True);
+rectangle(-2 * i + 13,4,-2 * i + 14,6);
+rectangle(1,-6 * i + 7,3,-6 * i + 9)
+};
+circle(8,5);
+rectangle(5,3,6,7);
+rectangle(0,0,10,10);
+line(8,6,8,8,
+arrow = False,solid = False)
         \end{verbatim}
@@
         \begin{verbatim}
-rectangle(4,2,6,5);
-reflect(reflect(y = 7)){
+reflect(y = 7){
 line(2,6,4,4,
@@
 rectangle(0,0,2,2)
-}
+};
+rectangle(4,2,6,5)
         \end{verbatim}
@@
         \begin{verbatim}
-circle(10,5);
 line(7,5,9,5,
@@
 rectangle(0,0,12,10);
-reflect(reflect(y = 10)){
-line(3,8,5,6,
-arrow = True,solid = True);
-rectangle(1,7,3,9)
+reflect(y = 10){
+circle(10,5);
+line(3,2,5,4,
+arrow = True,solid = True);
+rectangle(1,1,3,3)
 }
@@
         \begin{verbatim}
-circle(10,4);
 line(10,1,2,1,
@@
 arrow = True,solid = True);
-reflect(reflect(y = 8)){
-line(2,7,4,5,
+reflect(y = 8){
+circle(10,4);
+line(2,1,4,3,
 arrow = True,solid = True);
@@
         \begin{verbatim}
-Solver timeout
+line(12,9,12,0,
+arrow = True,solid = True);
+rectangle(9,3,11,9);
+rectangle(6,5,8,9);
+rectangle(0,7,2,9);
+rectangle(3,8,5,9)
         \end{verbatim}
@@
         \begin{verbatim}
-line(0,1,2,0,
-arrow = False,solid = True);
-for (i < 3){
-if (i > 0){
-line(3*i + -3,4,3*i + -1,3,
-arrow = False,solid = True);
-line(0,3*i + -2,3*i + -3,4,
+for (i < 3){
+for (j < (1*i + 1)){
+if (j > 0){
+line(3 * j + -3,3 * i + -2,3 * j + -1,3 * i + -3,
+arrow = False,solid = True);
+line(0,3 * j + -2,3 * j + -3,4,
 arrow = False,solid = True)
@@
 rectangle(2,0,5,3)
+}
 }
@@
 for (i < 3){
-circle(-3*i + 7,1);
-circle(-3*i + 7,6);
-line(-3*i + 7,-1*i + 4,-3*i + 7,5,
+circle(-3 * i + 7,1);
+circle(-3 * i + 7,6);
+line(-3 * i + 7,-1 * i + 4,-3 * i + 7,5,
 arrow = False,solid = True)
@@
         \begin{verbatim}
+reflect(x = 7){
+circle(6,1);
+line(6,2,6,5,
+arrow = False,solid = True);
+rectangle(5,5,7,7)
+};
 line(2,6,5,6,
 arrow = False,solid = True);
-reflect(reflect(x = 7)){
-circle(6,1);
 line(2,1,5,1,
-arrow = False,solid = True);
-line(1,2,1,5,
-arrow = False,solid = True);
-rectangle(5,5,7,7)
-}
+arrow = False,solid = True)
         \end{verbatim}
@@
         \begin{verbatim}
+line(3,2,1,2,
+arrow = True,solid = True);
+line(0,3,2,3,
+arrow = True,solid = True);
+line(5,0,3,0,
+arrow = True,solid = True);
 line(2,1,4,1,
-arrow = True,solid = True);
-line(3,2,1,2,
-arrow = True,solid = True);
-line(5,0,3,0,
-arrow = True,solid = True);
-line(0,3,2,3,
 arrow = True,solid = True)
@@
         \begin{verbatim}
-for (i < 4){
-if (i > 0){
-rectangle(-2*i + 6,2*i + -2,-2*i + 7,2*i + -1)
-}
-rectangle(-2*i + 6,2*i,-2*i + 7,2*i + 1)
+rectangle(6,0,7,1);
+for (i < 3){
+rectangle(-2 * i + 4,2 * i + 2,-2 * i + 5,2 * i + 3);
+rectangle(-2 * i + 4,2 * i,-2 * i + 5,2 * i + 1)
 }
@@
         \begin{verbatim}
+line(3,0,5,0,
+arrow = False,solid = True);
+line(1,2,3,2,
+arrow = False,solid = True);
 line(0,3,2,3,
@@
 line(2,1,4,1,
-arrow = False,solid = False);
-line(1,2,3,2,
-arrow = False,solid = True);
-line(3,0,5,0,
-arrow = False,solid = True)
+arrow = False,solid = False)
         \end{verbatim}
@@
         \begin{verbatim}
-for (i < 4){
-if (i > 0){
-circle(-2*i + 7,3*i + -2);
-line(-2*i + 9,3*i,-2*i + 10,3*i + -2,
-arrow = False,solid = True);
-line(-2*i + 8,3*i + -2,-2*i + 9,3*i,
-arrow = False,solid = True)
-}
-circle(-2*i + 9,3*i + 1)
+circle(9,1);
+for (i < 3){
+circle(-2 * i + 7,3 * i + 4);
+circle(-2 * i + 5,3 * i + 1);
+line(-2 * i + 6,3 * i + 1,-2 * i + 7,3 * i + 3,
+arrow = False,solid = True);
+line(-2 * i + 7,3 * i + 3,-2 * i + 8,3 * i + 1,
+arrow = False,solid = True)
 }
@@
         \begin{verbatim}
-for (i < 4){
-if (i > 0){
-line(2*i + 1,-3*i + 12,2*i,-3*i + 10,
-arrow = True,solid = True);
-line(2*i + 1,-3*i + 12,2*i + 2,-3*i + 10,
-arrow = True,solid = True);
-rectangle(2*i + -2,-3*i + 9,2*i,-3*i + 11)
-}
-rectangle(2*i + 2,-3*i + 9,2*i + 4,-3*i + 11)
-}
+for (i < 3){
+line(2 * i + 3,-3 * i + 9,2 * i + 2,-3 * i + 7,
+arrow = True,solid = True);
+line(2 * i + 3,-3 * i + 9,2 * i + 4,-3 * i + 7,
+arrow = True,solid = True);
+rectangle(2 * i + 2,-3 * i + 9,2 * i + 4,-3 * i + 11);
+rectangle(2 * i,-3 * i + 6,2 * i + 2,-3 * i + 8)
+};
+rectangle(8,0,10,2)
         \end{verbatim}
@@
         \begin{verbatim}
-circle(5,1);
-for (i < 3){
-if (i > 0){
-circle(7,2*i + -1);
-circle(i + 2,2*i + 1)
-}
-circle(1,6)
+for (i < 2){
+circle(2 * i + 1,-3 * i + 6);
+circle(-3 * i + 7,2 * i + 3);
+circle(2 * i + 5,1)
 }
@@
 arrow = True,solid = True);
-rectangle(3,4,5,6);
-rectangle(0,0,2,2)
+rectangle(0,0,2,2);
+rectangle(3,4,5,6)
         \end{verbatim}
@@
         \begin{verbatim}
-rectangle(0,4,2,6);
-for (i < 3){
-if (i > 0){
-line(-4*i + 12,5,-4*i + 10,5,
-arrow = True,solid = True);
-for (j < i + 1){
-circle(-4*j + 9,-4*i + 9)
-}
-}
-line(-4*i + 9,4,-4*i + 9,2,
+for (i < 3){
+line(-4 * i + 9,4,-4 * i + 9,2,
+arrow = True,solid = True);
+for (j < (1*i + 2)){
+if (j > 0){
+circle(-4 * j + 13,-4 * i + 9);
+line(-4 * i + 12,5,-4 * i + 10,5,
 arrow = True,solid = True)
+}
+rectangle(0,4,2,6)
+}
 }
@@
         \begin{verbatim}
-Solver timeout
+circle(1,5);
+line(4,1,2,1,
+arrow = True,solid = True);
+line(8,1,6,1,
+arrow = True,solid = True);
+for (i < 3){
+line(4 * i + 1,2,4 * i + 1,4,
+arrow = True,solid = True);
+rectangle(4,4,6,6);
+rectangle(4 * i,0,4 * i + 2,2)
+};
+rectangle(8,4,10,6)
         \end{verbatim}
@@
 for (i < 3){
-line(-4*i + 9,4,-4*i + 9,2,
+line(4 * i + 1,4,4 * i + 1,2,
 arrow = True,solid = True);
 for (j < 2){
-line(-4*j + 8,5,-4*j + 6,5,
-arrow = True,solid = True);
-rectangle(-4*i + 8,4*j,-4*i + 10,4*j + 2)
+line(4 * j + 4,5,4 * j + 2,5,
+arrow = True,solid = True);
+rectangle(4 * i,-4 * j + 4,4 * i + 2,-4 * j + 6)
 }
@@
 for (i < 3){
-if (i > 0){
-line(-4*i + 12,1,-4*i + 10,1,
+line(4 * i + 1,2,4 * i + 1,4,
+arrow = True,solid = True);
+for (j < 2){
+circle(4 * i + 1,4 * j + 1);
+line(4 * j + 4,1,4 * j + 2,1,
 arrow = True,solid = True)
 }
-circle(-4*i + 9,1);
-circle(-4*i + 9,5);
-line(-4*i + 9,2,-4*i + 9,4,
-arrow = True,solid = True)
 }
@@
         \begin{verbatim}
-reflect(reflect(x = 6)){
-for (i < 3){
-if (i > 0){
-line(-2*i + 7,-4*i + 11,-2*i + 7,-4*i + 10,
-arrow = True,solid = True);
-rectangle(0,-4*i + 11,6,-3*i + 12)
-}
-rectangle(2,0,4,2)
-}
-}
+line(5,7,5,6,
+arrow = True,solid = True);
+line(3,3,3,2,
+arrow = True,solid = True);
+line(1,7,1,6,
+arrow = True,solid = True);
+rectangle(0,3,6,6);
+rectangle(2,0,4,2);
+rectangle(0,7,6,9)
         \end{verbatim}
@@
         \begin{verbatim}
-for (i < 3){
-if (i > 0){
-line(3*i,1,3*i + -1,1,
-arrow = True,solid = True)
-}
-rectangle(3*i,0,3*i + 2,2)
+line(6,1,5,1,
+arrow = True,solid = True);
+for (i < 3){
+line(3,1,2,1,
+arrow = True,solid = True);
+rectangle(3 * i,0,3 * i + 2,2)
 }
@@
         \begin{verbatim}
-line(1,3,1,4,
-arrow = False,solid = True);
-for (i < 3){
-if (i > 0){
-line(1,-5*i + 13,1,-4*i + 10,
+for (i < 3){
+circle(1,-4 * i + 9)
+};
+line(1,4,1,2,
+arrow = True,solid = True);
+line(1,8,1,6,
 arrow = True,solid = True)
-}
-circle(1,-4*i + 9)
-}
         \end{verbatim}
@@
         \begin{verbatim}
-reflect(reflect(x = 2)){
+reflect(y = 2){
 line(0,1,1,2,
@@
 for (i < 3){
-line(i,-1*i + 6,2*i + 2,-1*i + 6,
-arrow = False,solid = True);
-line(i,-2*i + 4,i,-1*i + 6,
+line(1 * i,-2 * i + 4,1 * i,-1 * i + 6,
+arrow = False,solid = True);
+line(1 * i,-1 * i + 6,2 * i + 2,-1 * i + 6,
 arrow = False,solid = True)
@@
         \begin{verbatim}
-for (i < 3){
-if (i > 0){
-circle(1,-3*i + 7);
-circle(5,-2*i + 6);
-rectangle(0,-3*i + 6,2,-3*i + 8)
-}
-rectangle(4,1,6,5)
+circle(5,2);
+circle(5,4);
+rectangle(4,1,6,5);
+reflect(y = 5){
+circle(1,4);
+rectangle(0,3,2,5)
 }
@@
 for (i < 3){
-rectangle(3*i,-2*i + 4,3*i + 2,6);
-for (j < i + 1){
-circle(3*i + 1,-2*j + 5)
-}
+for (j < (1*i + 1)){
+circle(3 * i + 1,-2 * j + 5)
+};
+rectangle(3 * i,-2 * i + 4,3 * i + 2,6)
 }
@@
         \begin{verbatim}
+line(0,0,0,3,
+arrow = False,solid = True);
+line(6,0,6,3,
+arrow = False,solid = True);
+line(0,3,6,3,
+arrow = False,solid = False);
 line(0,0,6,0,
-arrow = False,solid = False);
-reflect(reflect(x = 6)){
-line(6,0,6,3,
-arrow = False,solid = True);
-line(0,3,6,3,
 arrow = False,solid = False)
-}
         \end{verbatim}
@@
         \begin{verbatim}
-Solver timeout
+for (i < 2){
+line(2 * i,-2 * i + 5,2,5,
+arrow = False,solid = True);
+line(1,2,2 * i + 1,-2 * i + 4,
+arrow = False,solid = True);
+line(2 * i + 3,-2 * i + 3,5,3,
+arrow = False,solid = True);
+line(4,0,2 * i + 4,-2 * i + 2,
+arrow = False,solid = True)
+}
         \end{verbatim}
@@
         \begin{verbatim}
-for (i < 3){
-if (i > 0){
-circle(-5*i + 11,1);
-line(-1*i + 3,-1*i + 7,-5*i + 11,2,
+circle(6,1);
+circle(1,1);
+circle(1,6);
+line(2,6,6,2,
+arrow = True,solid = True);
+line(1,5,1,2,
 arrow = True,solid = True)
-}
-circle(1,6)
-}
         \end{verbatim}
@@
         \begin{verbatim}
-Solver timeout
+rectangle(5,5,9,9);
+rectangle(0,0,4,4);
+for (i < 2){
+rectangle(1 * i + 7,-2 * i + 2,9,-3 * i + 4);
+rectangle(0,-3 * i + 8,1 * i + 1,-2 * i + 9)
+}
         \end{verbatim}
@@
         \begin{verbatim}
-for (i < 3){
-if (i > 0){
-line(4*i + -3,-5*i + 12,2*i + 1,5,
-arrow = False,solid = True);
-rectangle(4*i + -4,-5*i + 10,6,-7*i + 16)
-}
-circle(1,8)
-}
+circle(1,8);
+line(5,2,5,5,
+arrow = False,solid = True);
+line(1,7,3,5,
+arrow = False,solid = True);
+rectangle(4,0,6,2);
+rectangle(0,5,6,9)
         \end{verbatim}
@@
         \begin{verbatim}
-Solver timeout
+for (i < 3){
+for (j < 3){
+if (j > 0){
+line(3 * j + -1,3 * i + 1,3 * j,3 * i + 1,
+arrow = False,solid = True);
+line(3 * i + 1,3 * j + -1,3 * i + 1,3 * j,
+arrow = False,solid = True)
+}
+circle(3 * i + 1,3 * j + 1)
+}
+}
         \end{verbatim}
@@
         \begin{verbatim}
-Solver timeout
+for (i < 3){
+for (j < 3){
+if (j > 0){
+line(3 * i + 1,3 * j + -1,3 * i + 1,3 * j,
+arrow = False,solid = True);
+line(3 * j + -1,3 * i + 1,3 * j,3 * i + 1,
+arrow = False,solid = True)
+}
+rectangle(3 * i,3 * j,3 * i + 2,3 * j + 2)
+}
+}
         \end{verbatim}
@@
 for (i < 3){
-circle(-3*i + 7,1)
+circle(-3 * i + 7,1)
 }
@@
 for (i < 3){
-rectangle(-2*i + 4,0,-2*i + 5,6)
+rectangle(-2 * i + 4,0,-2 * i + 5,6)
 }
@@
         \begin{verbatim}
+line(0,0,0,5,
+arrow = False,solid = True);
 line(4,0,4,5,
-arrow = False,solid = True);
-line(0,0,0,5,
 arrow = False,solid = True)
@@
         \begin{verbatim}
-reflect(reflect(x = 12)){
+reflect(x = 12){
 circle(4,1);
-line(9,1,10,1,
+line(2,1,3,1,
 arrow = False,solid = True);
@@
         \begin{verbatim}
-rectangle(0,4,4,8);
-reflect(reflect(y = 12)){
 circle(7,6);
-line(2,2,2,4,
-arrow = True,solid = True);
+reflect(y = 12){
 line(4,6,6,6,
 arrow = True,solid = True);
-rectangle(1,10,3,12)
-}
+line(2,10,2,8,
+arrow = True,solid = True);
+rectangle(1,0,3,2)
+};
+rectangle(0,4,4,8)
         \end{verbatim}
@@
         \begin{verbatim}
-reflect(reflect(y = 9)){
+reflect(y = 9){
+reflect(x = 9){
+circle(8,8);
 line(3,8,6,8,
 arrow = False,solid = True);
-reflect(reflect(x = 9)){
-circle(1,8);
 line(1,3,1,6,
@@
         \begin{verbatim}
-reflect(reflect(y = 11)){
-rectangle(4,9,7,10);
-reflect(reflect(x = 11)){
-rectangle(1,4,2,7);
-rectangle(8,8,11,11)
+reflect(x = 11){
+rectangle(9,4,10,7);
+reflect(y = 11){
+rectangle(8,0,11,3);
+rectangle(4,9,7,10)
 }
@@
         \begin{verbatim}
-for (i < 4){
-line(i,-1*i + 5,i + 2,-1*i + 5,
-arrow = False,solid = True);
-line(i + 2,-1*i + 3,i + 4,-1*i + 3,
+for (i < 3){
+line(2 * i,-2 * i + 5,2 * i + 2,-2 * i + 5,
+arrow = False,solid = True);
+line(2 * i + 1,-2 * i + 4,2 * i + 3,-2 * i + 4,
 arrow = False,solid = True)
@@
         \begin{verbatim}
-for (i < 3){
-if (i > 0){
-rectangle(3*i + 1,-1*i + 2,3*i + 3,2);
-rectangle(0,7*i + -7,3,7*i + -4)
-}
+rectangle(4,1,6,2);
+rectangle(7,0,9,2);
+reflect(y = 10){
+rectangle(0,0,3,3);
 rectangle(1,4,2,6)
@@
         \begin{verbatim}
-Solver timeout
+line(7,4,9,4,
+arrow = True,solid = True);
+line(8,3,7,3,
+arrow = True,solid = True);
+reflect(y = 7){
+line(2,1,4,3,
+arrow = True,solid = True);
+rectangle(0,0,2,2)
+};
+line(8,3,9,3,
+arrow = False,solid = True);
+rectangle(9,2,12,5);
+rectangle(4,2,7,5)
         \end{verbatim}
@@
 for (i < 3){
-rectangle(-2*i + 4,-2*i + 4,-2*i + 7,-2*i + 5)
+rectangle(2 * i,2 * i,2 * i + 3,2 * i + 1)
 }
@@
 for (i < 3){
-circle(-3*i + 7,5);
-circle(-3*i + 7,1);
-line(-3*i + 7,4,-3*i + 7,2,
-arrow = True,solid = True);
-line(4,9,-3*i + 7,6,
+circle(3 * i + 1,1);
+circle(3 * i + 1,5);
+line(4,9,3 * i + 1,6,
+arrow = True,solid = True);
+line(3 * i + 1,4,3 * i + 1,2,
 arrow = True,solid = True)
@@
 arrow = True,solid = True);
+line(4,8,4,0,
+arrow = True,solid = True);
 line(6,8,6,4,
-arrow = True,solid = True);
-line(4,8,4,0,
 arrow = True,solid = True);
@@
 arrow = False,solid = True);
+rectangle(0,0,4,8);
 rectangle(1,1,3,3);
-rectangle(1,5,3,7);
-rectangle(0,0,4,8)
+rectangle(1,5,3,7)
         \end{verbatim}
@@
         \begin{verbatim}
-Solver timeout
+rectangle(0,0,6,2);
+reflect(x = 6){
+for (i < 3){
+circle(5,2 * i + 4);
+circle(2 * i + 1,1);
+rectangle(4,3,6,9)
+}
+}
         \end{verbatim}
@@
 for (j < 3){
-circle(-4*j + 9,-3*i + 7)
+circle(4 * i + 1,-3 * j + 7)
 }
@@
         \begin{verbatim}
-for (i < 3){
-if (i > 0){
-line(8,0,8*i + -8,7*i + -7,
-arrow = True,solid = True)
-}
-rectangle(2*i + 2,0,2*i + 3,i + 3)
+line(8,0,0,0,
+arrow = True,solid = True);
+line(8,0,8,7,
+arrow = True,solid = True);
+for (i < 3){
+rectangle(-2 * i + 6,0,-2 * i + 7,-1 * i + 5)
 }
@@
         \begin{verbatim}
-Solver timeout
+line(2,4,4,4,
+arrow = True,solid = True);
+line(6,7,5,5,
+arrow = True,solid = True);
+for (i < 2){
+circle(-2 * i + 7,-3 * i + 7);
+circle(3 * i + 4,1);
+line(5,3,3 * i + 4,2,
+arrow = True,solid = True);
+rectangle(0,3,2,5)
+}
         \end{verbatim}
@@
 rectangle(5,0,8,3);
-rectangle(2,1,4,3);
-rectangle(0,2,1,3)
+rectangle(0,2,1,3);
+rectangle(2,1,4,3)
         \end{verbatim}
@@
 for (i < 3){
-rectangle(-1*i + 2,-1*i + 2,i + 3,i + 3)
+rectangle(-1 * i + 2,-1 * i + 2,1 * i + 3,1 * i + 3)
 }
@@
         \begin{verbatim}
-reflect(reflect(x = 6)){
+reflect(y = 6){
+line(2,5,4,5,
+arrow = False,solid = True);
+reflect(x = 6){
 line(5,2,5,4,
 arrow = False,solid = True);
-reflect(reflect(y = 6)){
-line(2,1,4,1,
-arrow = False,solid = True);
-rectangle(4,4,6,6)
+rectangle(0,4,2,6)
 }
@@
         \begin{verbatim}
-reflect(reflect(y = 6)){
-line(2,5,4,5,
-arrow = False,solid = True);
-reflect(reflect(x = 6)){
-circle(5,5);
-line(1,2,1,4,
-arrow = False,solid = True)
-}
+reflect(y = 6){
+reflect(x = 6){
+circle(1,1);
+line(5,2,5,4,
+arrow = False,solid = True)
+};
+line(2,1,4,1,
+arrow = False,solid = True)
 }
@@
 for (i < 3){
-line(i,-1*i + 2,-1*i + 7,-1*i + 2,
+line(1 * i,-1 * i + 2,-1 * i + 7,-1 * i + 2,
 arrow = False,solid = True)
@@
         \begin{verbatim}
+line(1,5,5,1,
+arrow = False,solid = True);
 line(1,4,5,0,
 arrow = False,solid = True);
-line(1,5,5,1,
-arrow = False,solid = True);
-rectangle(5,0,6,1);
-rectangle(0,4,1,5)
+rectangle(0,4,1,5);
+rectangle(5,0,6,1)
         \end{verbatim}
@@
 for (i < 3){
-circle(4*i + 1,1);
-rectangle(4*i,0,4*i + 2,2)
+circle(-4 * i + 9,1);
+rectangle(-4 * i + 8,0,-4 * i + 10,2)
 }
@@
         \begin{verbatim}
-reflect(reflect(x = 5)){
-circle(1,1);
+reflect(x = 5){
+circle(4,1);
 line(4,4,4,2,
-arrow = True,solid = True);
+arrow = True,solid = True)
+};
 rectangle(0,4,5,6)
-}
         \end{verbatim}
@@
         \begin{verbatim}
-Solver timeout
+circle(3,1);
+reflect(x = 6){
+circle(5,5);
+circle(1,9);
+line(5,4,3,2,
+arrow = True,solid = True);
+line(5,8,2,5,
+arrow = True,solid = True);
+line(1,8,1,6,
+arrow = True,solid = True)
+}
         \end{verbatim}
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-71.png}&
-            Sampled no finished traces.&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-Solver timeout
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-71-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+for (i < 3){
+line(7,1,5 * i + 2,3,
+arrow = True,solid = True);
+for (j < (1*i + 1)){
+if (j > 0){
+line(5 * j + -1,9,5 * i,5,
+arrow = True,solid = True)
+}
+line(5 * j + 2,5,5 * j + 2,9,
+arrow = True,solid = True)
+};
+rectangle(5 * i,3,5 * i + 4,5);
+rectangle(5 * i,9,5 * i + 4,10)
+};
+rectangle(2,0,12,1)
         \end{verbatim}
@@
         \begin{verbatim}
-reflect(reflect(y = 8)){
-for (i < 3){
-if (i > 0){
-rectangle(3*i + -1,2,3*i,3)
-}
-circle(3*i + 1,3*i + 1)
-}
+reflect(y = 8){
+for (i < 3){
+circle(-3 * i + 7,-3 * i + 7)
+};
+rectangle(2,2,3,3);
+rectangle(5,5,6,6)
 }
@@
     \includegraphics[width = 5cm]{../TikZ/drawings/expert-73.png}&
-            Sampled no finished traces.&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-Solver timeout
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-73-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+line(10,8,12,4,
+arrow = True,solid = True);
+line(6,8,8,4,
+arrow = True,solid = True);
+for (i < 3){
+line(4 * i + 5,5,4 * i + 5,7,
+arrow = True,solid = True);
+line(4 * i + 5,1,4 * i + 5,3,
+arrow = True,solid = True);
+rectangle(4 * i + 4,3,4 * i + 6,5);
+rectangle(4 * i + 4,7,4 * i + 6,9);
+line(2,1,13,1,
+arrow = False,solid = True)
+};
+rectangle(0,0,2,8)
         \end{verbatim}
@@
 for (i < 3){
-if (i > 0){
-rectangle(-2*i + 4,-2*i + 4,2*i + 2,2*i + 2)
-}
 for (j < 3){
-circle(-2*i + 5,2*j + 1)
-}
-}
+circle(2 * j + 1,2 * i + 1)
+}
+};
+rectangle(2,2,4,4);
+rectangle(0,0,6,6)
         \end{verbatim}
@@
 for (i < 4){
-line(-4*i + 13,4,-4*i + 13,2,
-arrow = True,solid = True);
+circle(4 * i + 1,1);
+circle(4 * i + 1,5);
+for (j < 3){
+line(4 * i + 1,4,4 * i + 1,2,
+arrow = True,solid = True);
+line(4 * j + 2,5,4 * j + 4,5,
+arrow = True,solid = True)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-76.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-76-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(x = 8){
+circle(4,1);
+circle(1,8);
+line(0,2,4,5,
+arrow = False,solid = True);
+line(4,5,4,10,
+arrow = False,solid = True)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-77.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-77-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+circle(9,8);
+circle(5,1);
+circle(1,8);
+reflect(x = 10){
+line(6,1,9,3,
+arrow = False,solid = True);
+line(2,8,4,8,
+arrow = False,solid = True);
+line(9,5,9,7,
+arrow = False,solid = True);
+rectangle(0,3,2,5)
+};
+rectangle(4,7,6,9)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-78.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-78-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+line(3,2,5,4,
+arrow = True,solid = True);
+line(6,6,6,5,
+arrow = True,solid = True);
+line(8,3,7,4,
+arrow = True,solid = True);
+line(4,0,12,8,
+arrow = False,solid = True);
+line(0,6,12,6,
+arrow = False,solid = True);
+line(0,8,8,0,
+arrow = False,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-79.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-79-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+for (i < 3){
+circle(4 * i + 1,13);
+circle(5,-4 * i + 9);
+circle(4 * i + 1,9);
+line(4 * i + 1,12,4 * i + 1,10,
+arrow = True,solid = True);
+line(5,-4 * i + 12,5,-4 * i + 10,
+arrow = True,solid = True)
+};
+line(9,8,6,5,
+arrow = True,solid = True);
+line(1,8,4,5,
+arrow = True,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-80.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-80-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(x = 14){
+circle(11,10);
+circle(3,4);
+circle(7,1);
+reflect(y = 20){
+circle(13,7);
+circle(9,7)
+};
+line(3,3,7,2,
+arrow = True,solid = True);
+line(10,10,5,8,
+arrow = True,solid = True);
+reflect(x = 6){
+line(5,12,3,11,
+arrow = True,solid = True);
+line(1,6,3,5,
+arrow = True,solid = True);
+line(3,9,5,8,
+arrow = True,solid = True)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-81.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-81-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+circle(1,1);
+circle(4,1);
+rectangle(6,0,8,2);
+rectangle(9,0,11,2)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-82.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-82-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-83.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-83-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(x = 10){
+circle(5,1);
+circle(2,4);
+line(2,3,5,2,
+arrow = True,solid = True);
+reflect(x = 16){
+circle(9,7);
+line(9,6,8,5,
+arrow = True,solid = True)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-84.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-84-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+Solver timeout
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-85.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-85-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+for (i < 4){
+if (i > 0){
+line(1,3 * i,1,3 * i + -1,
+arrow = True,solid = True)
+}
+circle(1,3 * i + 1)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-86.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-86-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+rectangle(5,0,8,3);
+rectangle(0,5,3,8);
+for (i < 2){
+rectangle(1 * i + 6,3 * i + 4,8,2 * i + 6);
+rectangle(0,2 * i,1 * i + 1,3 * i + 1)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-87.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-87-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(x = 8){
+rectangle(0,0,1,1);
+rectangle(5,5,8,8);
+rectangle(0,2,2,4)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-88.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-88-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+for (i < 3){
+rectangle(-2 * i + 4,-1 * i + 2,1 * i + 6,2 * i + 3)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-89.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-89-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+circle(9,5);
+line(3,1,8,1,
+arrow = True,solid = True);
+line(8,5,7,5,
+arrow = True,solid = True);
+line(9,8,0,8,
+arrow = True,solid = True);
+line(9,2,9,4,
+arrow = True,solid = True);
+line(12,1,10,1,
+arrow = True,solid = True);
+line(9,2,10,1,
+arrow = False,solid = True);
+line(12,1,12,5,
+arrow = False,solid = True);
+reflect(x = 6){
+line(6,5,4,5,
+arrow = True,solid = True)
+};
+rectangle(2,4,4,6);
+rectangle(1,0,13,9);
+line(9,6,9,8,
+arrow = False,solid = True);
+line(6,4,7,5,
+arrow = False,solid = True);
+line(10,5,12,5,
+arrow = False,solid = True);
+line(3,1,3,4,
+arrow = False,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-90.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-90-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+circle(6,2);
+for (i < 3){
+circle(5 * i + 1,7)
+};
+line(5,7,2,7,
+arrow = True,solid = True);
+line(6,6,6,3,
+arrow = True,solid = True);
+line(10,7,7,7,
+arrow = True,solid = True);
+rectangle(4,0,8,9)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-91.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-91-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(x = 5){
+reflect(y = 5){
+line(0,5,2,5,
+arrow = False,solid = True);
+line(0,3,0,5,
+arrow = False,solid = True)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-92.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-92-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+for (i < 3){
+reflect(x = 14){
+circle(9,4 * i + 1);
+line(10,4 * i + 1,12,4 * i + 1,
+arrow = False,solid = True);
+rectangle(0,4 * i,2,4 * i + 2)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-93.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-93-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(x = 10){
+line(5,6,1,8,
+arrow = True,solid = True);
+line(9,2,5,4,
+arrow = True,solid = True);
+for (i < 3){
+circle(4 * i + 1,4 * i + 1)
+}
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-94.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-94-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+reflect(x = 12){
+line(6,2,6,3,
+arrow = True,solid = True);
+line(2,7,5,4,
+arrow = True,solid = True);
+line(0,0,9,9,
+arrow = False,solid = True)
+};
+line(0,2,12,2,
+arrow = False,solid = True)
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}        
+            \\
+
+            \begin{tabular}{lll}
+    \includegraphics[width = 5cm]{../TikZ/drawings/expert-95.png}&
+            \includegraphics[width = 5cm]{../TikZ/drawings/expert-95-parses/0.png}&
+
+        \begin{minipage}{10cm}
+        \begin{verbatim}
+for (i < 3){
 for (j < 3){
 if (j > 0){
-circle(-4*i + 13,4*j + -3)
-}
-line(-4*j + 10,5,-4*j + 12,5,
+circle(6 * i + -5,-5 * j + 16);
+line(6 * i + -5,5,4,2,
+arrow = True,solid = True);
+line(6 * j + -5,10,6 * i + -5,7,
 arrow = True,solid = True)
 }
-}
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-76.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-76-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-circle(4,1);
-reflect(reflect(x = 8)){
-circle(1,8);
-line(4,5,8,2,
-arrow = False,solid = True);
-line(4,5,4,10,
-arrow = False,solid = True)
-}
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-77.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-77-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-Solver timeout
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-78.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-78-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-line(0,6,12,6,
-arrow = False,solid = True);
-line(6,6,6,5,
-arrow = True,solid = True);
-line(8,3,7,4,
-arrow = True,solid = True);
-line(3,2,5,4,
-arrow = True,solid = True);
-reflect(reflect(x = 12)){
-line(4,0,12,8,
-arrow = False,solid = True)
-}
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-79.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-79-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-Solver timeout
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-80.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-80-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-Solver timeout
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-81.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-81-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-circle(1,1);
-circle(4,1);
-rectangle(9,0,11,2);
-rectangle(6,0,8,2)
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-82.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-82-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-Solver timeout
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-83.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-83-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-Solver timeout
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-84.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-84-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-Solver timeout
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-85.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-85-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-for (i < 4){
-if (i > 0){
-line(1,-3*i + 12,1,-3*i + 11,
-arrow = True,solid = True)
-}
-circle(1,-3*i + 10)
-}
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-86.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-86-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-Solver timeout
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-87.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-87-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-reflect(reflect(x = 8)){
-rectangle(0,5,3,8);
-rectangle(0,2,2,4);
-rectangle(0,0,1,1)
-}
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-88.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-88-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-for (i < 3){
-rectangle(-2*i + 4,-1*i + 2,i + 6,2*i + 3)
-}
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-89.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-89-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-Solver timeout
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-90.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-90-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-line(6,6,6,3,
-arrow = True,solid = True);
-for (i < 3){
-if (i > 0){
-circle(-5*i + 16,7);
-circle(-5*i + 11,5*i + -3);
-line(-5*i + 15,7,-5*i + 12,7,
-arrow = True,solid = True)
-}
-rectangle(4,0,8,9)
-}
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-91.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-91-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-reflect(reflect(x = 5)){
-reflect(reflect(y = 5)){
-line(5,3,5,5,
-arrow = False,solid = True);
-line(3,5,5,5,
-arrow = False,solid = True)
-}
-}
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-92.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-92-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-reflect(reflect(x = 14)){
-for (i < 3){
-circle(9,-4*i + 9);
-line(10,-4*i + 9,12,-4*i + 9,
-arrow = False,solid = True);
-rectangle(0,-4*i + 8,2,-4*i + 10)
-}
-}
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-93.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-93-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-reflect(reflect(x = 10)){
-for (i < 3){
-if (i > 0){
-line(4*i + -3,4*i + -2,4*i + 1,4*i,
-arrow = True,solid = True)
-}
-circle(4*i + 1,4*i + 1)
-}
-}
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-94.png}&
-            Sampled no finished traces.&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-line(0,2,12,2,
-arrow = False,solid = True);
-line(6,2,6,3,
-arrow = True,solid = True);
-reflect(reflect(x = 12)){
-line(0,0,9,9,
-arrow = False,solid = True);
-line(10,7,7,4,
-arrow = True,solid = True)
-}
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}        
-            \\
-
-            \begin{tabular}{lll}
-    \includegraphics[width = 5cm]{../TikZ/drawings/expert-95.png}&
-            \includegraphics[width = 5cm]{../TikZ/drawings/expert-95-parses/0.png}&
-
-        \begin{minipage}{10cm}
-        \begin{verbatim}
-reflect(reflect(x = 8)){
-circle(4,1);
-for (i < 3){
-if (i > 0){
-circle(7,-5*i + 16);
-line(-6*i + 13,10,7,7,
-arrow = True,solid = True)
-}
-line(1,5,4,2,
-arrow = True,solid = True)
+circle(4,1)
 }
@@
         \begin{verbatim}
-reflect(reflect(x = 10)){
-circle(1,1);
+reflect(y = 10){
+circle(1,9);
 for (i < 4){
-circle(-2*i + 7,2*i + 3)
+circle(-2 * i + 9,-2 * i + 9)
 }
@@
         \begin{verbatim}
-reflect(reflect(x = 6)){
-for (i < 3){
-if (i > 0){
-line(1,-4*i + 10,1,-4*i + 12,
-arrow = False,solid = True)
-}
-circle(5,-4*i + 9);
-line(2,-4*i + 9,4,-4*i + 9,
+for (i < 3){
+circle(1,-4 * i + 9);
+circle(5,-4 * i + 9);
+for (j < 3){
+if (j > 0){
+line(4 * i + -3,-4 * j + 10,4 * i + -3,-4 * j + 12,
+arrow = False,solid = True)
+}
+line(2,-4 * j + 9,4,-4 * j + 9,
 arrow = False,solid = True)
@@
         \begin{verbatim}
-rectangle(0,0,4,9);
-for (i < 3){
-if (i > 0){
-circle(2,-4*i + 10);
-line(2,-5*i + 15,2,-4*i + 11,
-arrow = True,solid = True)
-}
-circle(2,11)
-}
+circle(2,2);
+circle(2,6);
+circle(2,11);
+line(2,5,2,3,
+arrow = True,solid = True);
+line(2,10,2,7,
+arrow = True,solid = True);
+rectangle(0,0,4,9)
         \end{verbatim}
@@
 for (i < 2){
-circle(4,-6*i + 7);
-circle(1,-6*i + 10);
-rectangle(0,-6*i + 6,2,-6*i + 8);
-rectangle(3,-6*i + 9,5,-6*i + 11)
-}
-        \end{verbatim}
-\end{minipage}
-
-    \end{tabular}
+circle(4,6 * i + 1);
+circle(1,6 * i + 4);
+rectangle(0,6 * i,2,6 * i + 2);
+rectangle(3,6 * i + 3,5,6 * i + 5)
+}
+        \end{verbatim}
+\end{minipage}
+
+    \end{tabular}

### 2017-10-20 paper.tex
paper roadmap figure

@@
 \usepackage{microtype}      % microtypography
-
+\usepackage{listings}
+\lstset{basicstyle = \small\ttfamily}
 \usepackage{graphicx} % more modern
@@
 \usetikzlibrary{positioning}
-\usetikzlibrary{decorations.text}
+\usetikzlibrary{decorations.text,decorations.pathreplacing}
 \usetikzlibrary{decorations.pathmorphing}
@@
  consider this problem within a graphics program synthesis domain.  We
- develop an approach for converting natural images, such as hand
- drawings, into executable source code for drawing the original image.
+ develop an approach for converting  hand
+ drawings into executable source code for drawing the original image.
  The graphics programs in our domain draw simple figures like those found in
@@
 We present a hybrid architecture for inferring graphics programs that is structured around these two steps.
-For the first step, our approach uses a deep network to infer a sequence of primitive shape-drawing commands that generates an image similar to the observed image.
-We refer to this sequence as an \emph{execution trace}, since it corresponds to the sequence of primitive commands that a program would have issued but lacks the high-level structure that determines how the program decided to issue them.
+For the first step, our approach uses a deep network to infer a sequence of primitive shape-drawing commands.
+We refer to this sequence as an \emph{execution trace}, since it corresponds to the: commands that a program would have issued but lacks the high-level structure that determines how the program decided to issue them.
 For added robustness, we train the network to produce a proposal distribution of the most likely traces and use stochastic search to find the trace that best matches the input.
@@
 Although these program synthesizers do not \emph{need} any training data,
-we show how to combine conventional machine learning with bias optimal search~\cite{schmidhuber2004optimal},
-learning to improve the wall clock speed of these synthesis algorithms by two orders of magnitude.
+we show how to combine conventional machine learning with bias optimal search~\cite{schmidhuber2004optimal}
+in order to synthesize complicated programs in only a few minutes.
+
+Images are high-dimensional and unstructured while programs are high-level
+and symbolic. We resolve this mismatch by advancing a new model of
+collaboration between these two representations, which we call The Trace Hypothesis:
+
+\noindent \textbf{The Trace Hypothesis.} The execution trace of a program
+is the correct liaison between high-level structured symbolic representations
+and high-dimensional unstructured perceptual input.
+
+The roadmap of our paper is structured around the trace hypothesis, as outlined in Figure~\ref{roadmap}.
+\begin{figure}
+  \begin{tikzpicture}
+    \node[ thick,anchor = west,inner sep=0pt,label=below:{\small Perceptual input}](observation) at (0,0) {\includegraphics[width = 1.5cm]{figures/expert-39-trimmed.png}};
+    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Trace}](trace) at (3,0) {\includegraphics[width = 1.5cm]{../TikZ/drawings/expert-39-parses/0.png}};
+
+    \node[draw, thick,anchor = west,inner sep=0pt,label=below:{\small Program}](program) at (6,0) {
+      \begin{lstlisting}
+for (j < 3)
+for (i < 3)
+if (...)
+ line(...)
+ line(...)
+rectangle(...)
+    \end{lstlisting}};
+    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Extrapolation}](extrapolate) at (9.5,-0.4) {\includegraphics[width = 1.3cm]{figures/39-extrapolated.png}};
+    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Similarity}](similarity) at (11.3,0) {\includegraphics[width = 1cm]{figures/expert-38-trim.png}};
+    \node[ultra thick,anchor = west,text width = 1.3cm,inner sep=0pt](errors) at (10,1) {\small Error correction};
+
+    \draw[->, thick] (observation.east) -- node[draw,fill = white,rotate = -90] {{\small Neural network}} (trace.west);
+    \draw[->, thick] (trace.east) -- node[draw,fill = white,rotate = -90] {{\small Program synthesis}} (program.west);
+    \draw[->, thick] (program.east) to[out = 80,in = 180] (errors.west);
+    \draw[->, thick] (program.east) to[out = 40,in = -230] (similarity.west);
+        \draw[->, thick] (program.east) to[out = -90,in = 180] (extrapolate.west);
+
+    \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
+    ([yshift = -15,xshift = -30]observation.south) -- node[below = 6pt] {Section~\ref{neuralNetworkSection}: Perception$\to$Trace} ([yshift = -15,xshift = -5]trace.south);
+    \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
+    ([xshift = 5,yshift = -15]trace.south) -- node[below = 6pt] {Section~\ref{programSynthesisSection}: Trace$\to$Program} ([xshift = 140,yshift = -15]trace.south);
+    \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
+([xshift = 150,yshift = -15]trace.south) -- node[below = 6pt] {Section~\ref{applicationsSection}: Applications} ([xshift = 250,yshift = -15]trace.south);
+  \end{tikzpicture}
+  \caption{Paper roadmap: Structured around the \emph{trace hypothesis}}\label{roadmap}
+\end{figure}
 
@@
 for explaining the trace.
-Our goal now is to find the parameters of the policy, written $\theta$, which best navigate this trade-off.
+Our goal now is to find the parameters of the policy, written $\theta$, which best navigates this trade-off.
 
@@
 The policy learns to choose parameters likely to quickly yield a minimal cost program.
-In our notation, we write $\sigma $ to mean an assignment to each of these parameters.}\label{policyOutput}
+In our notation, we write $\sigma $ to mean an assignment to each of these parameters, so $\sigma $ can assume one of 24 different values.}\label{policyOutput}
   \end{table}
@@
 \textsc{Loss}(\theta ; \text{training corpus})& =  \expect_{T\in \text{training corpus}}\left[ \min_{\sigma\in \text{\textsc{Best}}(T)}\frac{t(\sigma | T)}{\pi_\theta (\sigma | T)}\right]\label{policyLoss}\\
-\text{where }  \sigma \in\text{\textsc{Best}}(T) &\text{ iff:  } \text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t. }p\text{ evaluates to }T} \text{cost}(p) \nonumber
+\text{where }  \sigma \in\text{\textsc{Best}}(T) &\text{ if  a minimum cost program for }T \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t.
+}p\text{ evaluates to }T} \text{cost}(p) \nonumber
 \end{align}
-This loss is differentiable but nonconvex even if $\pi_{\theta}(\cdot |\cdot )^{-1}$ is convex.
-We locally minimize it using gradient descent while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}. See supplement for details.
+To generate a training corpus for learning a policy which minimizes this loss,
+we synthesized minimum cost programs for each trace of our hand drawings
+and for each $\sigma $.
+Solving these 2400\footnote{There are 100 the drawings and $2\times 2\times 2\times 3 = 24$ different values of $\sigma $} synthesis problems takes a little over a day on a 20-CPU machine.
+With the training set in hand we  %This loss is differentiable but nonconvex even if $\pi_{\theta}(\cdot |\cdot )^{-1}$ is convex.
+ locally minimize this loss using gradient descent.% while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}.
+See supplement for details.
 
@@
 $\sigma $ will take to search.
+
+\begin{figure}
+  \includegraphics[width = 12cm]{figures/policyComparison.png}
+  \caption{$\infty = $ timeout}\label{policyEvaluation}
+  \end{figure}
 
@@
 
-With this policy in hand we can now synthesize most programs in under a minute. But why synthesize a graphics program,
+With this policy in hand we can now synthesize most programs in under a minute.
+
+\section{Applications of graphics program synthesis}\label{applicationsSection}
+Why synthesize a graphics program,
 if the execution trace already suffices to recover the objects in an image?

### 2017-10-21 paper.tex
related work and improved search policy section

@@
 This paper argues that this stage is best achieved by \emph{constraint-based program synthesis} \cite{solar2008program}.
-Without the need for training, the program synthesizer can search the space of possible programs for one capable of producing the desired trace -- inducing structures like
+The program synthesizer can search the space of possible programs for one capable of producing the desired trace -- inducing structures like
 symmetries, repetition, or conditional branches.
@@
 we show how to combine conventional machine learning with bias optimal search~\cite{schmidhuber2004optimal}
-in order to synthesize complicated programs in only a few minutes.
+in order to synthesize programs over an order of magnitude faster than constraint-based synthesis techniques alone.
 
@@
 \noindent \textbf{The Trace Hypothesis.} The execution trace of a program
-is the correct liaison between high-level structured symbolic representations
-and high-dimensional unstructured perceptual input.
+is the correct liaison between high-dimensional unstructured perceptual input and high-level structured symbolic representations.
 
 The roadmap of our paper is structured around the trace hypothesis, as outlined in Figure~\ref{roadmap}.
-\begin{figure}
+\begin{figure}[h]
   \begin{tikzpicture}
@@
   \end{tikzpicture}
-  \caption{Paper roadmap: Structured around the \emph{trace hypothesis}}\label{roadmap}
+  \caption{Paper roadmap. Both the paper and the system pipeline are structured around the \emph{trace hypothesis}}\label{roadmap}
 \end{figure}
 
+Prior work addresses converting hand drawings to vectors~\cite{huang2017shape,Nishida:2016:ISU:2897824.2925951} and converting synthetic images to symbolic parses~\cite{nsd,DBLP:journals/corr/Beltramelli17}.
+Our new contribution is an approach for
+converting perceptual input to high-level programs.
 %under a quantitative objective that maximizes the likelihood according to a prior distribution that aims to capture the user’s preference.
@@
 
-\section{Related work}
-
-Our work bears resemblance to the Attend-Infer-Repeat (AIR) system, which learns to decompose an image into its constituent objects~\cite{eslami1603attend}.
-AIR learns an iterative inference scheme which infers objects one by one and also decides when to stop inference; this is similar to our approach's first stage, which parses images into program execution traces.
-Our approach further produces interpretable, symbolic programs which generate those execution traces.
-The two approaches also differ in their architectures and training regimes: AIR learns a recurrent auto-encoding model via variational inference, whereas our parsing stage learns an autoregressive-style model from randomly-generated (execution trace, image) pairs.
-Finally, while AIR was evaluated on multi-MNIST images and synthetic 3D scenes, we focus on hand-drawn sketches.
-% attend infer repeat:~\cite{eslami1603attend}. Crucial distinction is
-% that they focus on learning the generative model jointly with the
-% inference network. Advantages of our system is that we learn symbolic
-% programs, and that we do it from hand sketches rather than synthetic
-% renderings.
-
-Our image-to-execution-trace parsing architecture builds on prior work on controlling procedural graphics programs~\cite{ritchie2016neurally}.
-Given a program which generates random 2D recursive structures such as vines, that system learns a structurally-identical ``guide program'' whose output can be directed, via neural networks, to resemble a given target image.
-We adapt this method to a different visual domain (figures composed of multiple objects), using a broad prior over possible scenes as the initial program and viewing the execution trace through the guide program as a symbolic parse of the target image.
-We then show how to synthesize higher-level programs from these execution traces.
-
-In the computer graphics literature, there have been other systems which convert sketches into procedural representations.
-One uses a convolutional network to match a sketch to the output of a parametric 3D modeling system~\cite{huang2017shape}.
-Another uses convolutional networks to support sketch-based instantiation of procedural primitives within an interactive architectural modeling system~\cite{Nishida:2016:ISU:2897824.2925951}.
-Both systems focus on inferring fixed-dimensional parameter vectors.
-In contrast, we seek to automatically infer a structured, programmatic representation of a sketch which captures higher-level visual patterns.
-
-Prior work has also applied sketch-based program synthesis to authoring graphics programs.
-Sketch-n-Sketch is a bi-directional editing system in which direct manipulations to a program's output automatically propagate to the program source code~\cite{Hempel:2016:SSP:2984511.2984575}.
-We see this work as complementary to our own: programs produced by our method could be provided to a Sketch-n-Sketch-like system as a starting point for further editing.
-
-The CogSketch~\cite{forbus2011cogsketch} system also aims to have a
-high-level understanding of hand-drawn figures. Their primary goal is
-cognitive modeling (they apply their system to solving IQ-test
-style visual reasoning problems), whereas we are interested in
-building an automated AI application (e.g. in our system the user need
-not annotate which strokes correspond to which shapes; our neural
-network produces something equivalent to the annotations).
-%A key similarity however is that both CogSketch and our system have as a goal to make it easier to produce nice-looking figures.
-Unsupervised Program Synthesis~\cite{ellis2015unsupervised} is a related framework which was also applied to geometric reasoning problems.
-The goals of~\cite{ellis2015unsupervised} were cognitive modeling,
-and they applied their technique to synthetic scenes used in human behavioral studies.
-%% open domain sketch understanding.
-structure mapping style model.
-also taps into cyc?
-the user segments the ink and labels them with concepts from knowledge base.
-like us they focus on compositional understanding.
-``cognitive simulation", solves things like Raven matrices in IQ tests.
-not really trying right now to be automated like our system.
-
-Synthesizing programs from their execution traces is an old
-idea~\cite{Summers:1977:MLP:321992.322002}.  This previous work
-departs from our approach in the nature of the problem (synthesizing
-recursive algorithms in Lisp vs. graphics programs in~\LaTeX) and the
-specifics of the solution (hand-coded source-to-source transformations vs. neural networks
-combined with general-purpose program synthesis techniques).
-What they share is the use of an execution trace as a
-stepping stone toward a full program.
-
 \section{Neural architecture for inferring drawing execution traces}\label{neuralNetworkSection}
@@
 predicts a distribution over the next drawing command to add to the
-trace; see Table~\ref{drawingCommandTable}.  We predict the drawing
-command token-by-token, conditioning each token both on the image
+trace; see Table~\ref{drawingCommandTable} for the drawing commands we currently model.  We predict the drawing
+command token-by-token,\footnote{A token is an atomic symbol  -- so the model is \emph{not} predicting lines of code character-by-character, but instead knows about the syntactic structure of primitive commands} conditioning each token both on the image
 features and on the previously generated tokens. We also use a
@@
 \end{tabular}
-\caption{The deep network in Fig.~\ref{architecture} predicts drawing commands, shown above.}
+\caption{Primitive drawing commands currently supported by our model.}
 \label{drawingCommandTable}
@@
 where $|T|$ is the length of execution trace $T$, the subscripts
-on $T$ index drawing commands within the trace, and the \verb|STOP|
+on $T$ index drawing commands within the trace (so $T_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
 token is emitted by the network to signal that the trace
@@
 globally optimal program.
-In practice, synthesis times vary from a few minutes to a a few hours,
+In practice, synthesis times vary from minutes to hours,
 with 16\% of the diagrams timing out the synthesizer after 3 hours.
 See Figure~\ref{exampleSynthesisResults} for examples of the kinds of programs our system recovers.
-A main impediment here to our use of these general techniques is
+A main impediment to our use of these general techniques is
 the prohibitively high cost of searching for programs.
-
-\subsection{Learning a search policy for synthesizing programs}
+We next describe how to learn to synthesize programs much faster (Section~\ref{learningASearchPolicy}).
+
+\subsection{Learning a search policy for synthesizing programs}\label{learningASearchPolicy}
 
@@
 An example of a $1$-bias optimal search algorithm is a time-sharing system
-that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to testing $\sigma $.
+that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
 We construct a $1$-bias optimal search algorithm for our domain by
@@
 and comes close to the Oracle's performance.
-Of course one could never construct such an Oracle,
+Of course one could never construct this Oracle,
 because the agent does not know ahead of time which
@@
 \begin{figure}
-  \includegraphics[width = 12cm]{figures/policyComparison.png}
-  \caption{$\infty = $ timeout}\label{policyEvaluation}
+\centering  \includegraphics[width = 14cm]{figures/policyComparison.png}
+  \caption{How long does it typically take to synthesize a minimum cost program?
+Sketch: out-of-the-box performance of the Sketch~\cite{solar2008program} program synthesizer.
+Oracle: baseline that always picks the easiest synthesis problem containing a minimum cost program.
+Learned policy: a bias-optimal learned search policy.
+Oracle is impossible to implement and is an upper bound on the performance of any search policy.
+$\infty = $ timeout.
+Red dashed line is median time.}\label{policyEvaluation}
   \end{figure}
 
-This generalizes and strengthens previous work: Levin
-search~\cite{levin1973universal,solomonoff1984optimum} \&
-OOPS~\cite{schmidhuber2004optimal}: theoretically appealing but
-impractical; fails to leverage either techniques from machine learning
-or from program synthesis. More of a mathematical framing and less of
-an algorithm.  DeepCoder~\cite{BalGauBroetal16}: in addition to
-picking what sort of primitives can go into a program, we are picking
-the details of the search algorithm as well as how deep the algorithms
-should search.  Main difference is that we identify this interesting
-trade-off between tractability and probability of getting a solution.
-TerpreT~\cite{gaunt2016terpret}: suggests that constraint solvers outperform gradient-based search techniques like those used in differentiable neural computers.
-
-Two intuitions: want a model that prefers sketches that are likely to
-contain a valid solution, but at the same time prefers sketches that
-are easy to search.  In general these two preferences are at odds with
-one another.  For example, a sketch which allows very long programs
-and allows lots of primitives is extremely likely to contain a
-shortest program -- but might also take hours for the synthesizer to
-search through.
+With this policy in hand we can now synthesize most programs in under a minute.
 
@@
 
-With this policy in hand we can now synthesize most programs in under a minute.
-
 \section{Applications of graphics program synthesis}\label{applicationsSection}
@@
 \centering  \begin{minipage}{\textwidth}\centering
-  \includegraphics[width = 0.69\textwidth]{figures/PCA.png}
+  %\includegraphics[width = 0.69\textwidth]{figures/PCA.png}
   \includegraphics[width = 0.69\textwidth]{figures/PCA_improved.png}
@@
 
+\section{Related work}
+
+Our approach to learning to search for programs draws theoretical
+underpinnings from Levin
+search~\cite{levin1973universal,solomonoff1984optimum} and
+Schmidhuber's OOPS model~\cite{schmidhuber2004optimal}.
+DeepCoder~\cite{BalGauBroetal16} and~\cite{menon2013machine} are
+recent models which, like ours, learn to predict which program
+components are likely to be useful given a program synthesis problem.
+Our work is different from their approaches because we treat the
+problem as a variety of \emph{metareasoning}, identifying and modeling
+the trade-off between tractable search and probability of successful
+search.  TerpreT~\cite{gaunt2016terpret} was the first work to
+systematically compare constraint-based program synthesis techniques
+against gradient-based search techniques (e.g., a
+DNC~\cite{graves2016hybrid}).  The TerpreT experiments help motivate
+our use of constraint-based techniques.
+
+Our work bears resemblance to the Attend-Infer-Repeat (AIR) system, which learns to decompose an image into its constituent objects~\cite{eslami1603attend}.
+AIR learns an iterative inference scheme which infers objects one by one and also decides when to stop inference; this is similar to our approach's first stage, which parses images into program execution traces.
+Our approach further produces interpretable, symbolic programs which generate those execution traces.
+The two approaches also differ in their architectures and training regimes: AIR learns a recurrent auto-encoding model via variational inference, whereas our parsing stage learns an autoregressive-style model from randomly-generated (execution trace, image) pairs.
+Finally, while AIR was evaluated on multi-MNIST images and synthetic 3D scenes, we focus on hand-drawn sketches.
+% attend infer repeat:~\cite{eslami1603attend}. Crucial distinction is
+% that they focus on learning the generative model jointly with the
+% inference network. Advantages of our system is that we learn symbolic
+% programs, and that we do it from hand sketches rather than synthetic
+% renderings.
+
+Our image-to-execution-trace parsing architecture builds on prior work on controlling procedural graphics programs~\cite{ritchie2016neurally}.
+Given a program which generates random 2D recursive structures such as vines, that system learns a structurally-identical ``guide program'' whose output can be directed, via neural networks, to resemble a given target image.
+We adapt this method to a different visual domain (figures composed of multiple objects), using a broad prior over possible scenes as the initial program and viewing the execution trace through the guide program as a symbolic parse of the target image.
+We then show how to synthesize higher-level programs from these execution traces.
+
+In the computer graphics literature, there have been other systems which convert sketches into procedural representations.
+One uses a convolutional network to match a sketch to the output of a parametric 3D modeling system~\cite{huang2017shape}.
+Another uses convolutional networks to support sketch-based instantiation of procedural primitives within an interactive architectural modeling system~\cite{Nishida:2016:ISU:2897824.2925951}.
+Both systems focus on inferring fixed-dimensional parameter vectors.
+In contrast, we seek to automatically infer a structured, programmatic representation of a sketch which captures higher-level visual patterns.
+
+Prior work has also applied sketch-based program synthesis to authoring graphics programs.
+Sketch-n-Sketch is a bi-directional editing system in which direct manipulations to a program's output automatically propagate to the program source code~\cite{Hempel:2016:SSP:2984511.2984575}.
+We see this work as complementary to our own: programs produced by our method could be provided to a Sketch-n-Sketch-like system as a starting point for further editing.
+
+The CogSketch~\cite{forbus2011cogsketch} system also aims to have a
+high-level understanding of hand-drawn figures. Their primary goal is
+cognitive modeling (they apply their system to solving IQ-test
+style visual reasoning problems), whereas we are interested in
+building an automated AI application (e.g. in our system the user need
+not annotate which strokes correspond to which shapes; our neural
+network produces something equivalent to the annotations).
+%A key similarity however is that both CogSketch and our system have as a goal to make it easier to produce nice-looking figures.
+Unsupervised Program Synthesis~\cite{ellis2015unsupervised} is a related framework which was also applied to geometric reasoning problems.
+The goals of~\cite{ellis2015unsupervised} were cognitive modeling,
+and they applied their technique to synthetic scenes used in human behavioral studies.
+%% open domain sketch understanding.
+structure mapping style model.
+also taps into cyc?
+the user segments the ink and labels them with concepts from knowledge base.
+like us they focus on compositional understanding.
+``cognitive simulation", solves things like Raven matrices in IQ tests.
+not really trying right now to be automated like our system.
+
+The idea that an execution trace could assist in program learning goes back to the 1970's~\cite{Summers:1977:MLP:321992.322002} and has also been applied in neural models of program induction, like Neural Program Interpreters~\cite{DBLP:journals/corr/ReedF15}.
+Our contribution to this idea is the trace hypothesis:
+that execution traces can be inferred from perceptual data,
+and that the trace is the correct bridge between perception and symbolic representation.
+Our work is the first to articulate and explore this hypothesis
+by demonstrating how a trace could be inferred and how it can be used to synthesize a high-level program.
+
 \subsection{Future work}

### 2017-10-24 paper.tex
new experimental data and re- factored some figures

@@
 We present a hybrid architecture for inferring graphics programs that is structured around these two steps.
-For the first step, our approach uses a deep network to infer a sequence of primitive shape-drawing commands.
-We refer to this sequence as an \emph{execution trace}, since it corresponds to the: commands that a program would have issued but lacks the high-level structure that determines how the program decided to issue them.
+For the first step, our approach uses a deep network to infer a set of primitive shape-drawing commands.
+We refer to this set as an \emph{execution trace}, since it corresponds to the commands that a program would have issued but lacks the high-level structure that determines how the program decided to issue them.
 For added robustness, we train the network to produce a proposal distribution of the most likely traces and use stochastic search to find the trace that best matches the input.
@@
 symmetries, repetition, or conditional branches.
-Although these program synthesizers do not \emph{need} any training data,
-we show how to combine conventional machine learning with bias optimal search~\cite{schmidhuber2004optimal}
-in order to synthesize programs over an order of magnitude faster than constraint-based synthesis techniques alone.
+Although these program synthesizers do not need any training data,
+we show how to learn a \emph{search policy} 
+in order to synthesize programs an order of magnitude faster than constraint-based synthesis techniques alone.
 
@@
 
-\noindent \textbf{The Trace Hypothesis.} The execution trace of a program
+\noindent \textbf{The Trace Hypothesis.} The set of commands issued by a program
 is the correct liaison between high-dimensional unstructured perceptual input and high-level structured symbolic representations.
@@
 Prior work addresses converting hand drawings to vectors~\cite{huang2017shape,Nishida:2016:ISU:2897824.2925951} and converting synthetic images to symbolic parses~\cite{nsd,DBLP:journals/corr/Beltramelli17}.
-Our new contribution is an approach for
-converting perceptual input to high-level programs.
+Our new contributions are:
+\begin{itemize}
+\item [-] A model that converts sketches to high-level programs
+\item [-] An algorithm for learning a policy for efficiently searching for programs
+\item [-] The trace hypothesis: a framework for going from perception to programs
+  \end{itemize}
+
 %under a quantitative objective that maximizes the likelihood according to a prior distribution that aims to capture the user’s preference.
@@
 
-\section{Neural architecture for inferring drawing execution traces}\label{neuralNetworkSection}
+\section{Neural architecture for inferring drawing drawing commands}\label{neuralNetworkSection}
 
@@
   \begin{minipage}{7.5cm}\centering
-    \includegraphics[width = 7cm]{figures/editDistanceRecurrent.png}
+    \includegraphics[width = 7cm]{figures/editDistance36.png}
 %    \includegraphics[width = 4cm]{figures/accuracy.png}
-      \caption{Parsing latex output after training on diagrams with $\leq 12$ objects.
+      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
 It generalizes to scenes with many more objects.
@@
 
+\setlength\tabcolsep{3.5pt}
 \begin{figure}[H]
-  \begin{minipage}[t]{2.25cm}
-    \includegraphics[width = 2cm]{figures/expert-73.png}
-    \includegraphics[width = 2cm]{figures/73-parse.png}     
-    \subcaption{A recurrent network architecture}
+  \begin{minipage}[t]{8.25cm}
+    \begin{tabular}{llll}
+      \includegraphics[width = 2cm]{figures/expert-38.png}&
+      \includegraphics[width = 2cm]{figures/expert-73.png}&
+      \includegraphics[width = 2cm]{figures/expert-77.png}&
+      \includegraphics[width = 2cm]{figures/expert-21.png}
+      \\
+      \includegraphics[width = 2cm]{figures/38-parse.png}     &
+      \includegraphics[width = 2cm]{figures/73-parse.png}     &
+      \includegraphics[width = 2cm]{figures/77-parse.png}    &
+      \includegraphics[width = 2cm]{figures/21-parse.png}    
+      \end{tabular}
+    \subcaption{Left to right: Ising model, recurrent network architecture, a figure from a deep learning textbook, graphical model}
   \end{minipage}
-  \begin{minipage}[t]{2.25cm}
-    \includegraphics[width = 2cm]{figures/expert-21.png}
-    \includegraphics[width = 2cm]{figures/21-parse.png}    
-    \subcaption{A graphical model}
+\hfill  \begin{minipage}[t]{4.25cm}
+    \begin{tabular}{ll}
+          \includegraphics[width = 2cm]{figures/expert-34.png}&
+          \includegraphics[width = 2cm]{figures/expert-1.png}\\
+              \includegraphics[width = 2cm]{figures/34-parse.png}     &
+      \includegraphics[width = 2cm]{figures/expert-1-parse.png}    
+    \end{tabular}
+
+    \subcaption{Near misses. Rightmost: illusory contours (note: no SMC)}
   \end{minipage}
-  \begin{minipage}[t]{2.25cm}
-    \includegraphics[width = 2cm]{figures/expert-77.png}
-    \includegraphics[width = 2cm]{figures/77-parse.png}    
-    \subcaption{A figure from a deep learning textbook}
-    \end{minipage}
-  \begin{minipage}[t]{2.25cm}
-    \includegraphics[width = 2cm]{figures/expert-1.png}
-    \includegraphics[width = 2cm]{figures/expert-1-parse.png}    
-    \subcaption{Near miss}
-  \end{minipage}
-  \begin{minipage}[t]{2.25cm}
-    \includegraphics[width = 2cm]{figures/expert-38.png}
-    \includegraphics[width = 2cm]{figures/38-parse.png}     
-    \subcaption{Ising model}
-  \end{minipage}
-  \begin{minipage}[t]{2.25cm}
-    \includegraphics[width = 2cm]{figures/expert-34.png}
-    \includegraphics[width = 2cm]{figures/34-parse.png}     
-    \subcaption{Illusory contours (note: no SMC)}
-    \end{minipage}
+
   \caption{Example drawings above model outputs.
@@
 \end{figure}
+\setlength\tabcolsep{6pt}
 
@@
 
+\pagebreak
+
 \section{Synthesizing graphics programs from execution traces}\label{programSynthesisSection}
@@
   \begin{tabular}{rl}\toprule
-  Program$\to$&Command; $\cdots$; Command\\
-  Command$\to$&\texttt{circle}(Expression,Expression)\\
-  Command$\to$&\texttt{rectangle}(Expression,Expression,Expression,Expression)\\
-  Command$\to$&\texttt{line}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
-  Command$\to$&\texttt{for}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ if }$(\text{Var} > 0)$\texttt{ \{ }Program\texttt{ \}; }Program\texttt{ \}}\\
-  Command$\to$&\texttt{reflect}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
-  Expression$\to$&$\mathcal{Z}$\texttt{ * }Var\texttt{ + }$\mathcal{Z}$\\
+  Program$\to$&Statement; $\cdots$; Statement\\
+  Statement$\to$&\texttt{circle}(Expression,Expression)\\
+  Statement$\to$&\texttt{rectangle}(Expression,Expression,Expression,Expression)\\
+  Statement$\to$&\texttt{line}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
+  Statement$\to$&\texttt{for}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ if }$(\text{Var} > 0)$\texttt{ \{ }Program\texttt{ \}; }Program\texttt{ \}}\\
+  Statement$\to$&\texttt{reflect}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
+  Expression$\to$&$\mathbb{Z}$\texttt{ * }Var\texttt{ + }$\mathbb{Z}$\\
   Var$\to$&A free (unused) variable\\
-  $\mathcal{Z}$$\to$&an integer\\
-  Axis$\to$&\texttt{X = }$\mathcal{Z}$ | \texttt{Y = }$\mathcal{Z}$\\\bottomrule
+  $\mathbb{Z}$\to$&an integer\\
+  Axis$\to$&\texttt{X = }$\mathbb{Z}$ | \texttt{Y = }$\mathbb{Z}$\\\bottomrule
   \end{tabular}
   \caption{Grammar over graphics programs.
-We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertical/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations ($\mathcal{Z}$\texttt{ * }Var\texttt{ + }$\mathcal{Z}$).}\label{DSL}
+We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertibb/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations ($\mathbb{Z}$\texttt{ * }Var\texttt{ + }$\mathbb{Z}$).}\label{DSL}
 \end{table}
@@
 We define the
-cost of a program to be the number of statements it contains, where a
-statement is a ``Command'' in Table~\ref{DSL}.
+cost of a program to be the number of Statement's it contains (Table~\ref{DSL}).
 We also penalize using many different numerical constants; see supplement.
@@
 the prohibitively high cost of searching for programs.
-We next describe how to learn to synthesize programs much faster (Section~\ref{learningASearchPolicy}).
+We next describe how to learn to synthesize programs much faster (Section~\ref{learningASearchPolicy}),
+timing out on 2\% of the drawings and solving most problems in under a minute.
 
@@
 and comes close to the Oracle's performance.
-Of course one could never construct this Oracle,
+One could never construct this Oracle,
 because the agent does not know ahead of time which
@@
 $\sigma $ will take to search.
-
-\begin{figure}
+The Oracle is an upper bound on the performance of any search policy.
+With this learned policy in hand we can now synthesize most programs in under a minute.
+\begin{figure}[h]
   \centering  \includegraphics[width = 14cm]{figures/policyComparison.png}
@@
 Oracle: baseline that always picks the easiest synthesis problem containing a minimum cost program.
-Learned policy: a bias-optimal learned search policy.
+Learned policy: a bias-optimal learned search policy running on an ideal timesharing machine.
 Oracle is impossible to implement and is an upper bound on the performance of any search policy.
@@
 
-With this policy in hand we can now synthesize most programs in under a minute.
-
 \newcommand{\exampleProgramSize}{4.5cm}
-\newcommand{\exampleTraceSize}{4cm}
-\newcommand{\exampleDrawingSize}{2cm}
+\newcommand{\exampleTraceSize}{3.5cm}
+\newcommand{\exampleDrawingSize}{1.25cm}
+\lstset{basicstyle = \scriptsize\ttfamily}
 
 \begin{figure}
-\hspace{-0.7cm}  \begin{tabular}{m{2.5cm}llc}
+\centering  \begin{tabular}{m{1.5cm}llc}
     \toprule
@@
     \includegraphics[width = \exampleDrawingSize]{figures/expert-29-trim.png}&
-\begin{minipage}{\exampleTraceSize}\begin{verbatim}
+\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
 Line(2,15, 4,15)
@@
 Line(4,13, 8,13)
-\end{verbatim}
-\end{minipage}&     \begin{minipage}{\exampleProgramSize} \begin{verbatim}
+\end{lstlisting}
+\end{minipage}&     \begin{minipage}{\exampleProgramSize} \begin{lstlisting}
 for(i<3)
- line(i,-1*i+6, 2*i+2,-1*i+6)
+ line(i,-1*i+6,
+      2*i+2,-1*i+6)
  line(i,-2*i+4,i,-1*i+6)
-       \end{verbatim}
+       \end{lstlisting}
      \end{minipage}&$\frac{6}{3} = 2\text{x}$\\\midrule
      \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
-\begin{minipage}{\exampleTraceSize}\begin{verbatim}
+\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
 Line(5,13, 2,10),
@@
 Circle(2,9)
-\end{verbatim}
-\emph{... etc. ...; 13 lines}\\
+\end{lstlisting}
+\emph{... etc. ...; 13 lines}
 \end{minipage}&
-             \begin{minipage}{\exampleProgramSize}\begin{verbatim}
+             \begin{minipage}{\exampleProgramSize}\begin{lstlisting}
 circle(4,10)
@@
       arrow=True)
-\end{verbatim}
+\end{lstlisting}
 \end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
     \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
-\begin{minipage}{\exampleTraceSize}\begin{verbatim}
+\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
 Circle(5,8)
@@
 Circle(5,14)
-\end{verbatim}
-  \emph{... etc. ...; 21 lines}\\
+\end{lstlisting}
+  \emph{... etc. ...; 21 lines}
 \end{minipage}&\begin{minipage}{\exampleProgramSize}
-\begin{verbatim}
+\begin{lstlisting}
 for(i<3)
@@
   circle(-3*j+7,-3*i+7)
-\end{verbatim}
+\end{lstlisting}
 \end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
 \includegraphics[width = \exampleDrawingSize]{figures/expert-75-trim.png}&
-\begin{minipage}{\exampleTraceSize}\begin{verbatim}
+\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
 Line(11,14, 13,14), 
@@
 Circle(2,10)
-\end{verbatim}
-    \emph{... etc. ...; 15 lines}\\
+\end{lstlisting}
+    \emph{... etc. ...; 15 lines}
 \end{minipage}&
 \begin{minipage}{\exampleProgramSize}
-    \begin{verbatim}
+    \begin{lstlisting}
 for(i<4)
@@
        arrow=True)
-\end{verbatim}
+\end{lstlisting}
   \end{minipage}&$\frac{15}{6} = 2.5\text{x}$\\\midrule
 
+  \includegraphics[width = \exampleDrawingSize]{figures/expert-7-trim.png}&
+\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
+Line(5,11,5,13)
+Circle(5,9)
+Circle(5,14)
+Circle(2,9)
+Circle(2,14)
+Circle(8,14)
+Circle(8,9)
+Line(2,10,2,13)
+Line(8,12,8,13)
+\end{lstlisting}
+  \end{minipage}&\begin{minipage}{\exampleProgramSize}
+\begin{lstlisting}
+for (i<3)
+ circle(-3*i+7,1)
+ circle(-3*i+7,6)
+ line(-3*i+7,-1*i+4,-3*i+7,5)
+\end{lstlisting}
+\end{minipage}&$\frac{9}{4} = 2.25\text{x}$\\\midrule
+
   \includegraphics[width = \exampleDrawingSize]{figures/expert-72-trim.png}&
 
-\begin{minipage}{\exampleTraceSize}\begin{verbatim}
+\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
 Circle(2,8)
@@
 Rectangle(3,12, 4,13)
-\end{verbatim}
+\end{lstlisting}
   \end{minipage}&\begin{minipage}{\exampleProgramSize}
-\begin{verbatim}
+\begin{lstlisting}
 reflect(y=8)
@@
   circle(3*i+1,3*i+1)
-\end{verbatim}
+\end{lstlisting}
 \end{minipage}&$\frac{9}{5} = 1.8\text{x}$\\\bottomrule
@@
 Compared to the trace the programs are more compressive (right: programs have fewer lines than traces) and automatically group together related drawing commands.
-Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformation in the top figure.}\label{exampleSynthesisResults}
+Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformations in the top figure and second figure to bottom.}\label{exampleSynthesisResults}
   \end{figure}
 
+\pagebreak
 \section{Applications of graphics program synthesis}\label{applicationsSection}
@@
 see supplement for our full set of extrapolations.
-
-\begin{figure}[h]
+\begin{figure}[H]
   \includegraphics[width = \textwidth]{figures/extrapolationMatrix1.png}
@@
 
+%\pagebreak
 \section{Discussion}

### 2017-10-24 paper.tex
improvements to diagrams; terminology change: no longer call it an execution trace

@@
   combines techniques from deep learning and program synthesis.  We
-  learn a convolutional neural network that proposes plausible drawing primitives
-  that explain an image. This set of drawing primitives is like an execution trace for a graphics program. From this trace we use
-  program synthesis techniques to recover a graphics
-  program with constructs such as variable bindings, iterative loops, or
-  simple kinds of conditionals. With a graphics program in hand,
-  we can correct errors made by the deep network, cluster drawings by use of similar high-level geometric structures, and extrapolate drawings.
-  Taken together these results are a step towards
-  agents that induce useful, human-readable programs from perceptual input.  
+  learn a convolutional neural network that proposes plausible drawing
+  primitives that explain an image. This set of drawing primitives is
+  like a trace of the primitive commands issued by a graphics
+  program. From this trace we use program synthesis techniques to
+  recover a graphics program with constructs such as variable
+  bindings, iterative loops, or simple kinds of conditionals. With a
+  graphics program in hand, we can correct errors made by the deep
+  network, cluster drawings by use of similar high-level geometric
+  structures, and extrapolate drawings.  Taken together these results
+  are a step towards agents that induce useful, human-readable
+  programs from perceptual input.
 \end{abstract}
@@
   \end{minipage}
-  \caption{(a): Model learns to convert hand drawings (top) into \LaTeX~(bottom). (b) Synthesizes high-level \emph{graphics program} from hand drawing.}\label{firstPageExamples}
+  \caption{(a): Model learns to convert hand drawings (top) into \LaTeX~(rendered below). (b) Synthesizes high-level \emph{graphics program} from hand drawing.}\label{firstPageExamples}
 \end{figure}
@@
 For the first step, our approach uses a deep network to infer a set of primitive shape-drawing commands.
-We refer to this set as an \emph{execution trace}, since it corresponds to the commands that a program would have issued but lacks the high-level structure that determines how the program decided to issue them.
+We refer to this set as a \emph{trace},\footnote{For our domain we do not require the trace to be ordered -- so it is similar to, but not exactly the same as, the execution trace of the program.} since it corresponds to the commands that a program would have issued but lacks the high-level structure that determines how the program decided to issue them.
 For added robustness, we train the network to produce a proposal distribution of the most likely traces and use stochastic search to find the trace that best matches the input.
@@
 
-The second step involves generating a high-level program capable of producing the program trace identified by the first phase.
+The second step involves generating a high-level program capable of producing the trace identified by the first phase.
 %In principle, we could also train a neural network to learn this mapping.
@@
 
-\noindent \textbf{The Trace Hypothesis.} The set of commands issued by a program
+\noindent \textbf{The Trace Hypothesis.} The set of commands issued by a program,
+which we call a \emph{trace},
 is the correct liaison between high-dimensional unstructured perceptual input and high-level structured symbolic representations.
@@
     \node[ thick,anchor = west,inner sep=0pt,label=below:{\small Perceptual input}](observation) at (0,0) {\includegraphics[width = 1.5cm]{figures/expert-39-trimmed.png}};
-    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Trace}](trace) at (3,0) {\includegraphics[width = 1.5cm]{../TikZ/drawings/expert-39-parses/0.png}};
-
-    \node[draw, thick,anchor = west,inner sep=0pt,label=below:{\small Program}](program) at (6,0) {
+    \node[ultra thick,anchor = west,inner sep=0pt](traceSource) at (3,0.5){    \begin{lstlisting}[basicstyle = \scriptsize\ttfamily]
+line, line,
+rectangle,
+line, ...
+\end{lstlisting}};
+    \node[ultra thick,anchor = west,inner sep=0pt](traceImage) at (3.22,-0.5) {
+      \includegraphics[width = 0.9cm]{figures/39-parse.png}}; 
+    \node(trace)[draw,thin,fit = (traceImage) (traceSource), label = below:{{\small Trace}}] {};
+
+    \node[draw, thick,anchor = west,inner sep=2pt,label=below:{\small Program}](program) at (6.3,0) {
       \begin{lstlisting}
@@
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-    ([yshift = -15,xshift = -30]observation.south) -- node[below = 6pt] {Section~\ref{neuralNetworkSection}: Perception$\to$Trace} ([yshift = -15,xshift = -5]trace.south);
+    ([yshift = -15,xshift = -115]trace.south) -- node[below = 6pt] {Section~\ref{neuralNetworkSection}: Perception$\to$Trace} ([yshift = -15,xshift = -5]trace.south);
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
@@
 
-\section{Neural architecture for inferring drawing drawing commands}\label{neuralNetworkSection}
+\section{Neural architecture for inferring drawing commands}\label{neuralNetworkSection}
 
 We developed a deep network architecture for efficiently inferring a
-execution trace, $T$, from an image, $I$.  Our model constructs the
+trace, $T$, from an image, $I$.  Our model constructs the
 trace one drawing command at a time.  When predicting the next drawing
@@
 already drawn.  It then decides either to stop drawing or proposes
-another drawing command to add to the execution trace; if it decides
+another drawing command to add to the trace; if it decides
 to continue drawing, the predicted primitive is rendered to its
@@
   \node[draw,ultra thick,minimum size = 1cm](c1) at ([xshift = 1.5cm]features.north) {MLP};
-  \node(l1) at ([yshift = -2cm]c1.south) {\verb|circle(|};
+  \node(l1) at ([yshift = -1.5cm]c1.south) {\verb|circle(|};
   \node[draw,ultra thick,minimum size = 1cm](a2) at ([xshift = 1cm,yshift = 1.5cm]c1.east) {STN};
@@
   \draw[->,ultra thick,red] (c1.south) -- (l1.north);
-  \node(l2) at ([yshift = -2cm]c2.south) {\verb|X=7,|};
+  \node(l2) at ([yshift = -1.5cm]c2.south) {\verb|X=7,|};
   \draw[->,ultra thick,red] (c2.south) -- (l2.north);
@@
   \draw[->,ultra thick] (a3.south) -- (c3.north);
-  \node(l3) at ([yshift = -2cm]c3.south) {\verb|Y=12)|};
+  \node(l3) at ([yshift = -1.5cm]c3.south) {\verb|Y=12)|};
   \draw[->,ultra thick,red] (c3.south) -- (l3.north);
@@
   \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c2.west);
-  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c3.west);
-  \draw[->,ultra thick] ([xshift = 0.25cm]l2.north) -- ([yshift = -0.2cm]c3.west);
+  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- ([yshift = -0.2cm]c3.west);
+  \draw[->,ultra thick] ([xshift = 0.25cm]l2.north) -- ([yshift = -0.25cm]c3.west);
 
@@
 \end{tikzpicture}
-\caption{Our neural architecture for inferring the execution trace of a graphics program from its output.
+\caption{Our neural architecture for inferring the trace of a graphics program from its output.
 \textcolor{blue}{Blue}: network inputs.
@@
   \end{tabular}&\begin{tabular}{l}
-    Finishes execution trace inference
+    Finishes drawing command inference
     \end{tabular}
@@
 where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
-the target image, $T$ is an execution trace, $\theta$ are the
+the target image, $T$ is a trace, $\theta$ are the
 parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
 image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
-execution traces factorizes as:
+traces factorizes as:
 \begin{equation}
@@
 \end{equation}
-where $|T|$ is the length of execution trace $T$, the subscripts
+where $|T|$ is the length of trace $T$, the subscripts
 on $T$ index drawing commands within the trace (so $T_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
@@
 
-We train the network by sampling execution traces $T$ and target
+We train the network by sampling traces $T$ and target
 images $I$ for randomly generated scenes
@@
 Figure~\ref{trainingData}.  We can perform a beam search decoding to
-recover what the network thinks is the most likely execution trace for
+recover what the network thinks is the most likely trace for
 images like these, recovering traces maximizing $\probability_\theta
@@
     \begin{minipage}[t]{3cm}\fbox{\includegraphics[width=2.75cm]{figures/randomScene-33-5.png}}\end{minipage}
-    \caption{Network is trained to infer execution traces for randomly generated scenes like the two shown above. See supplement for details of the training data generation.}\label{trainingData}
+    \caption{Network is trained to infer traces for randomly generated scenes like the two shown above. See supplement for details of the training data generation.}\label{trainingData}
   \end{minipage}\hfill%
@@
       \end{tabular}
-    \subcaption{Left to right: Ising model, recurrent network architecture, a figure from a deep learning textbook, graphical model}
+    \subcaption{Left to right: Ising model, recurrent network architecture, figure from a deep learning textbook (Goodfellow et al:~\cite{Goodfellow-et-al-2016}), graphical model}
   \end{minipage}
@@
 \begin{figure}[h]\centering
-\vspace{-0.25cm}  \begin{minipage}{0.8\textwidth} 
+  \begin{minipage}[c]{0.57\textwidth} 
     \centering  \includegraphics[width = 8cm]{figures/drawingAccuracy.png}
-  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1,10,100)?
+  \end{minipage}\hfill%
+      \begin{minipage}[c]{0.4\textwidth} 
+  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1,5,100)?
     Distance to ground truth trace measured by the intersection over union of predicted vs.
 ground truth traces.
-(a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 10 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth trace.}\label{drawingIntersectionOverUnion}
+(a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 5 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth trace.}\label{drawingIntersectionOverUnion}
     \end{minipage}
@@
 
-\pagebreak
-
-\section{Synthesizing graphics programs from execution traces}\label{programSynthesisSection}
-While the execution trace of a graphics program describes the contents
+%\pagebreak
+
+\section{Synthesizing graphics programs from drawing commands}\label{programSynthesisSection}
+While the trace of a graphics program describes the contents
 of a scene, it does not encode higher-level features of the image,
@@
   program} better describe such structures;
-we seek to synthesize simple graphics programs from their execution traces.
+we seek to synthesize simple graphics programs from their traces.
 
@@
 \end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
-\includegraphics[width = \exampleDrawingSize]{figures/expert-75-trim.png}&
+\includegraphics[width = \exampleDrawingSize]{figures/expert-75-extra-trim.png}&
 \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
@@
 Why synthesize a graphics program,
-if the execution trace already suffices to recover the objects in an image?
+if the trace already suffices to recover the objects in an image?
 Within our domain of hand-drawn figures, graphics program synthesis has several uses:
@@
   \end{wrapfigure}
-The program synthesizer can correct errors from the execution
-trace proposal network by favoring traces which lead to more
+The program synthesizer can correct errors from the trace proposal network by favoring traces which lead to more
 concise or general programs.  For example, figures with perfectly aligned objects are preferable to figures whose parts are slightly misaligned, and precise alignment lends itself to short
@@
 alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
-We used our learned distance metric between execution traces, $L_{\text{learned}}(\cdot|\cdot)$, and projected to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}).
+We used our learned distance metric between traces, $L_{\text{learned}}(\cdot|\cdot)$, and projected to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}).
 This reveals similarities between the objects in the drawings,
@@
 problem as a variety of \emph{metareasoning}, identifying and modeling
-the trade-off between tractable search and probability of successful
+the trade-off between tractable search and the probability of successful
 search.  TerpreT~\cite{gaunt2016terpret} was the first work to
 systematically compare constraint-based program synthesis techniques
-against gradient-based search techniques (e.g., a
-DNC~\cite{graves2016hybrid}).  The TerpreT experiments help motivate
-our use of constraint-based techniques.
+against gradient-based search techniques, like those used to train
+Differentiable Neural Computers~\cite{graves2016hybrid}).  The TerpreT
+experiments help motivate our use of constraint-based techniques.
 
 Our work bears resemblance to the Attend-Infer-Repeat (AIR) system, which learns to decompose an image into its constituent objects~\cite{eslami1603attend}.
-AIR learns an iterative inference scheme which infers objects one by one and also decides when to stop inference; this is similar to our approach's first stage, which parses images into program execution traces.
-Our approach further produces interpretable, symbolic programs which generate those execution traces.
-The two approaches also differ in their architectures and training regimes: AIR learns a recurrent auto-encoding model via variational inference, whereas our parsing stage learns an autoregressive-style model from randomly-generated (execution trace, image) pairs.
+AIR learns an iterative inference scheme which infers objects one by one and also decides when to stop inference; this is similar to our approach's first stage, which parses images into traces.
+Our approach further produces interpretable, symbolic programs which generate those traces.
+The two approaches also differ in their architectures and training regimes: AIR learns a recurrent auto-encoding model via variational inference, whereas our parsing stage learns an autoregressive-style model from randomly-generated (trace, image) pairs.
 Finally, while AIR was evaluated on multi-MNIST images and synthetic 3D scenes, we focus on hand-drawn sketches.
@@
 
-Our image-to-execution-trace parsing architecture builds on prior work on controlling procedural graphics programs~\cite{ritchie2016neurally}.
+Our image-to-trace parsing architecture builds on prior work on controlling procedural graphics programs~\cite{ritchie2016neurally}.
 Given a program which generates random 2D recursive structures such as vines, that system learns a structurally-identical ``guide program'' whose output can be directed, via neural networks, to resemble a given target image.
-We adapt this method to a different visual domain (figures composed of multiple objects), using a broad prior over possible scenes as the initial program and viewing the execution trace through the guide program as a symbolic parse of the target image.
-We then show how to synthesize higher-level programs from these execution traces.
+We adapt this method to a different visual domain (figures composed of multiple objects), using a broad prior over possible scenes as the initial program and viewing the trace through the guide program as a symbolic parse of the target image.
+We then show how to synthesize higher-level programs from these traces.
 
@@
 Our contribution to this idea is the trace hypothesis:
-that execution traces can be inferred from perceptual data,
+that traces can be inferred from perceptual data,
 and that the trace is the correct bridge between perception and symbolic representation.

### 2017-10-24 paper.tex
fixed bibliography style
small fixes

@@
 We refer to this set as a \emph{trace},\footnote{For our domain we do not require the trace to be ordered -- so it is similar to, but not exactly the same as, the execution trace of the program.} since it corresponds to the commands that a program would have issued but lacks the high-level structure that determines how the program decided to issue them.
-For added robustness, we train the network to produce a proposal distribution of the most likely traces and use stochastic search to find the trace that best matches the input.
-The network is trained from an automatically-generated corpus of synthetic image-generating programs.
+For added robustness, we train the network to produce a proposal distribution of the most likely traces and use stochastic search to find the trace that best matches the image.
+%The network is trained from an automatically-generated corpus of synthetic image-generating programs.
 
@@
 In practice, though, this would be challenging because it would no longer be sufficient to train the network with a synthetic corpus of randomly generated programs, since our goal is to generate programs that satisfy certain semantic constraints that ensure that we get the program that the user most likely intended.
-This paper argues that this stage is best achieved by \emph{constraint-based program synthesis} \cite{solar2008program}.
+%This paper argues that this stage is best
+We achieve this by \emph{constraint-based program synthesis} \cite{solar2008program}.
 The program synthesizer can search the space of possible programs for one capable of producing the desired trace -- inducing structures like
 symmetries, repetition, or conditional branches.
-Although these program synthesizers do not need any training data,
+Although these program do not need any training data,
 we show how to learn a \emph{search policy} 
@@
 \begin{table}[h]
+  \caption{Primitive drawing commands currently supported by our model.}
+\label{drawingCommandTable}
 \begin{tabular}{ll}\toprule
@@
 \end{tabular}
-\caption{Primitive drawing commands currently supported by our model.}
-\label{drawingCommandTable}
 \end{table}
@@
       \end{tabular}
-    \subcaption{Left to right: Ising model, recurrent network architecture, figure from a deep learning textbook (Goodfellow et al:~\cite{Goodfellow-et-al-2016}), graphical model}
+    \subcaption{Left to right: Ising model, recurrent network architecture, figure from a deep learning textbook \cite{Goodfellow-et-al-2016}, graphical model}
   \end{minipage}
@@
     \begin{tabular}{ll}
-          \includegraphics[width = 2cm]{figures/expert-34.png}&
-          \includegraphics[width = 2cm]{figures/expert-1.png}\\
-              \includegraphics[width = 2cm]{figures/34-parse.png}     &
-      \includegraphics[width = 2cm]{figures/expert-1-parse.png}    
+          \includegraphics[width = 2cm]{figures/expert-1.png}&
+          \includegraphics[width = 2cm]{figures/expert-34.png}\\
+      \includegraphics[width = 2cm]{figures/expert-1-parse.png}     &
+              \includegraphics[width = 2cm]{figures/34-parse.png}    
     \end{tabular}
@@
 \begin{table}[H]
+  \caption{Grammar over graphics programs.
+We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertibb/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations ($\mathbb{Z}$\texttt{ * }Var\texttt{ + }$\mathbb{Z}$).}\label{DSL}
   \begin{tabular}{rl}\toprule
@@
   Var$\to$&A free (unused) variable\\
-  $\mathbb{Z}$\to$&an integer\\
+  $\mathbb{Z}\to$&an integer\\
   Axis$\to$&\texttt{X = }$\mathbb{Z}$ | \texttt{Y = }$\mathbb{Z}$\\\bottomrule
   \end{tabular}
-  \caption{Grammar over graphics programs.
-We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertibb/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations ($\mathbb{Z}$\texttt{ * }Var\texttt{ + }$\mathbb{Z}$).}\label{DSL}
 \end{table}
@@
 program synthesis problems. We use the state-of-the-art Sketch
-tool~\cite{solar2008program}. Describing Sketch's program synthesis
-algorithm is beyond the scope of this paper; see~\cite{solar2008program}.  At a
+tool~\cite{solar2008program}.
+%Describing Sketch's program synthesis
+%algorithm is beyond the scope of this paper; see~\cite{solar2008program}.
+At a
 high level, Sketch takes as input a space of programs, along with a
@@
 \begin{table}[h]\centering
+  \caption{Parameterization of different ways of posing the program synthesis problem.
+The policy learns to choose parameters likely to quickly yield a minimal cost program.
+In our notation, we write $\sigma $ to mean an assignment to each of these parameters, so $\sigma $ can assume one of 24 different values.}\label{policyOutput}
   \begin{tabular}{lll}\toprule
@@
   \end{tabular}
-  \caption{Parameterization of different ways of posing the program synthesis problem.
-The policy learns to choose parameters likely to quickly yield a minimal cost program.
-In our notation, we write $\sigma $ to mean an assignment to each of these parameters, so $\sigma $ can assume one of 24 different values.}\label{policyOutput}
   \end{table}
@@
 Given a search policy, what is the best way of using it to quickly find minimum cost programs?
-We use a \emph{bias-optimal search algorithm} (see Schmidhuber 2004:~\cite{schmidhuber2004optimal}):
+We use a \emph{bias-optimal search algorithm} (see~\cite{schmidhuber2004optimal}):
 
@@
 
-\bibliographystyle{unsrt} {\small \bibliography{main}}
+\bibliographystyle{iclr2018_conference}
+                  {\small \bibliography{main}}
 

### 2017-10-25 short.tex
started work on shorter version of the paper: see short.tex

--- 2017-10-24 paper.tex
@@
  The graphics programs in our domain draw simple figures like those found in
- machine learning papers (see Figure~\ref{firstPageExamples}a).
+ machine learning papers (see Fig.~\ref{firstPageExamples}a).
  \begin{figure}[H]\vspace{-0.7cm}
@@
 The second step involves identifying the high-level structure in how the components were drawn.
-In Figure 1(b), it means identifying a pattern in how the circles and rectangles are being drawn that is best described with two nested loops, and which can easily be extrapolated to a bigger diagram.
+In Fig.
+1(b), it means identifying a pattern in how the circles and rectangles are being drawn that is best described with two nested loops, and which can easily be extrapolated to a bigger diagram.
 
@@
 For the first step, our approach uses a deep network to infer a set of primitive shape-drawing commands.
-We refer to this set as a \emph{trace},\footnote{For our domain we do not require the trace to be ordered -- so it is similar to, but not exactly the same as, the execution trace of the program.} since it corresponds to the commands that a program would have issued but lacks the high-level structure that determines how the program decided to issue them.
-For added robustness, we train the network to produce a proposal distribution of the most likely traces and use stochastic search to find the trace that best matches the image.
+We refer to this set as an unordered \emph{trace},\footnote{For our domain we do not require the trace to be ordered -- so it is similar to, but not exactly the same as, the execution trace of the program.} since it corresponds to the commands that a program would have issued but lacks the high-level structure that determines how the program decided to issue them.
+%For added robustness, we train the network to produce a proposal distribution of the most likely traces and use stochastic search to find the trace that best matches the image.
 %The network is trained from an automatically-generated corpus of synthetic image-generating programs.
-
-The second step involves generating a high-level program capable of producing the trace identified by the first phase.
+The second step involves synthesizing a high-level program capable of producing the trace identified by the first phase.
 %In principle, we could also train a neural network to learn this mapping.
@@
 The program synthesizer can search the space of possible programs for one capable of producing the desired trace -- inducing structures like
-symmetries, repetition, or conditional branches.
+symmetries, loops, or conditional branches.
 Although these program do not need any training data,
@@
 
-The roadmap of our paper is structured around the trace hypothesis, as outlined in Figure~\ref{roadmap}.
+The roadmap of our paper is structured around the trace hypothesis, as outlined in Fig.~\ref{roadmap}.
 \begin{figure}[h]
@@
   \end{tikzpicture}
-  \caption{Paper roadmap. Both the paper and the system pipeline are structured around the \emph{trace hypothesis}}\label{roadmap}
+  \caption{Both the paper and the system pipeline are structured around the \emph{trace hypothesis}}\label{roadmap}
 \end{figure}
@@
 Prior work addresses converting hand drawings to vectors~\cite{huang2017shape,Nishida:2016:ISU:2897824.2925951} and converting synthetic images to symbolic parses~\cite{nsd,DBLP:journals/corr/Beltramelli17}.
-Our new contributions are:
-\begin{itemize}
-\item [-] A model that converts sketches to high-level programs
-\item [-] An algorithm for learning a policy for efficiently searching for programs
-\item [-] The trace hypothesis: a framework for going from perception to programs
+Our new contributions are: (1) A model that converts sketches to high-level programs.
+(2) An algorithm for learning a policy for efficiently searching for programs.
+(3) The trace hypothesis: a framework for going from perception to programs.
   \end{itemize}
@@
 The first step involves identifying the components such as boxes, lines and arrows that make up the image.
-The second step involves identifying the high-level structure in how the components were drawn; for example, in Figure 1(b), it means identifying that there is a pattern in how the circles and rectangles are being drawn that is best described with two nested loops, and which can easily be extrapolated to a bigger diagram.
+The second step involves identifying the high-level structure in how the components were drawn; for example, in Fig.
+1(b), it means identifying that there is a pattern in how the circles and rectangles are being drawn that is best described with two nested loops, and which can easily be extrapolated to a bigger diagram.
 
@@
 
-Figure~\ref{architecture} illustrates this architecture.  We first
+Fig.~\ref{architecture} illustrates this architecture.  We first
 pass a $256\times 256$ target image and a rendering of the trace so
@@
 predicts a distribution over the next drawing command to add to the
-trace; see Table~\ref{drawingCommandTable} for the drawing commands we currently model.  We predict the drawing
+trace; see Tbl.~\ref{drawingCommandTable} for the drawing commands we currently model.  We predict the drawing
 command token-by-token,\footnote{A token is an atomic symbol  -- so the model is \emph{not} predicting lines of code character-by-character, but instead knows about the syntactic structure of primitive commands} conditioning each token both on the image
@@
 conditioned on the image features, the \verb|circle| token, and the
-$x$ coordinate. For our main experiments we constrain
+$x$ coordinate. We constrain
 coordinates to lie on a discrete $16\times 16$ grid, and later explain
@@
 sense, this model is like an autoregressive variant of
-AIR~\cite{eslami1603attend}, but critically, \emph{without a learned
+Attend-Infer-Repeat~\cite{eslami1603attend}, but critically, \emph{without a learned
   recurrent memory state}, e.g. an RNN.  We can do without an RNN
 because we have access to ground truth (image, trace) pairs.  This
-allows handling scenes with a very large number of objects without
-having to worry about the conditioning of gradients as they propagate
+allows us to handle scenes with many objects without
+worrying about the conditioning of gradients as they propagate
 over long sequences, and also makes training more straightforward (it
@@
 Our network suffices to ``derender'' synthetic images like those shown in
-Figure~\ref{trainingData}.  We can perform a beam search decoding to
+Fig.~\ref{trainingData}.  We can perform a beam search decoding to
 recover what the network thinks is the most likely trace for
@@
 distribution and the distance function offer complementary signals for
-whether a drawing command is correct. Empirically, accuracy is much
-better when we combine these signals.
-
-Figure~\ref{syntheticResults}
+whether a drawing command is correct.
+%Empirically, accuracy is much better when we combine these signals.
+
+Fig.~\ref{syntheticResults}
 compares the neural network with SMC against the neural network by
@@
 training data.
-We also compare with a natural baseline that models the problem as a kind of image captioning (``LSTM'' in Figure~\ref{syntheticResults}).
-Given the target image, this baseline produces the program trace in one shot by
+We compare with a natural baseline that models the problem as a kind of image captioning (LSTM in Fig.~\ref{syntheticResults}).
+Given the target image, this baseline produces the trace in one shot by
 using a CNN to extract features of the input which are passed to an LSTM which finally predicts
@@
 renderings of the training target images.
-We designed this noise process to introduce the kinds of variations found in hand drawings (Figure~\ref{handDrawingExamples}; see supplement for details).
+We designed this noise process to introduce the kinds of variations found in hand drawings (Fig.~\ref{handDrawingExamples}; see supplement for details).
 
@@
 \end{multline}
-Intuitively,
-$L_{\text{learned}}(\cdot|\cdot)$ approximates the distance between
-the trace we want and the trace we have so far.  Pixel-wise distance
+%Intuitively,
+%$L_{\text{learned}}(\cdot|\cdot)$ approximates the distance between
+%the trace we want and the trace we have so far.
+Pixel-wise distance
 metrics are sensitive to the details of how
 arrows, dashes, and corners are drawn -- but we wish to be invariant
-to these details. So, we learn a distance metric over images that
+to these details.
+So, we learn a distance metric over images that
 approximates the distance metric in the search space over traces.
 
-We drew 100 figures by hand; see figure~\ref{lotsOfHandDrawings}.
+We drew 100 figures by hand; see Fig.~\ref{lotsOfHandDrawings}.
 These were drawn carefully but not perfectly.
@@
 that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
-Because our current model sometimes makes mistakes on hand drawings,
+Because the model sometimes makes mistakes % on hand drawings,
 we envision it working as follows:
@@
 Python, a more tractable approach is to specify what in the program
-languages community is called a Domain Specific Language (DSL)~\cite{polozov2015flashmeta}. Our DSL (Table~\ref{DSL})
+languages community is called a Domain Specific Language (DSL)~\cite{polozov2015flashmeta}. Our DSL (Tbl.~\ref{DSL})
 encodes prior knowledge of what graphics programs tend to look like.
@@
 We define the
-cost of a program to be the number of Statement's it contains (Table~\ref{DSL}).
+cost of a program to be the number of Statement's it contains (Tbl.~\ref{DSL}).
 We also penalize using many different numerical constants; see supplement.
@@
 The constrained optimization problem in
-Equation~\ref{programObjective} is intractable in general, but there
+Eq.~\ref{programObjective} is intractable in general, but there
 exist efficient-in-practice tools for finding exact solutions to such
@@
 globally optimal program.
-In practice, synthesis times vary from minutes to hours,
-with 16\% of the diagrams timing out the synthesizer after 3 hours.
-See Figure~\ref{exampleSynthesisResults} for examples of the kinds of programs our system recovers.
+Synthesis times vary from minutes to hours,
+with 27\% of the drawings timing out the synthesizer after 1 hour.
+See Fig.~\ref{exampleSynthesisResults} for examples of the kinds of programs our system recovers.
 A main impediment to our use of these general techniques is
@@
 
-\subsection{Learning a search policy for synthesizing programs}\label{learningASearchPolicy}
-
-We want to leverage powerful, domain-general techniques from the program synthesis community,
-but make them much faster by
-learning a domain-specific \emph{search policy}.
-A search policy proposes search problems
-like those in Equation~\ref{programObjective},
-but can also offer additional constraints on the structure of the program (Table~\ref{policyOutput}).
-For example, a policy might decide to first try searching over small programs before searching over large programs,
-or decide to prioritize searching over programs that have loops.
-
-A search policy $\pi_\theta(\sigma  | T )$ takes as input a trace $T$ and predicts a distribution over synthesis problems, each of which is written $\sigma $ and corresponds to a set of possible programs to search over (so $\sigma \subset \text{DSL}$).
-Good policies will prefer tractable program spaces,
-so that the search procedure will terminate early.
-Good policies will also prefer program spaces that are likely to contain
-programs that can explain the data.
-In general these two desiderata are in tension:
-tractable synthesis problems involve searching over smaller spaces,
-but smaller spaces are less likely to contain a minimum cost program
-for explaining the trace.
-Our goal now is to find the parameters of the policy, written $\theta$, which best navigates this trade-off.
-
-\begin{table}[h]\centering
-  \caption{Parameterization of different ways of posing the program synthesis problem.
-The policy learns to choose parameters likely to quickly yield a minimal cost program.
-In our notation, we write $\sigma $ to mean an assignment to each of these parameters, so $\sigma $ can assume one of 24 different values.}\label{policyOutput}
-  \begin{tabular}{lll}\toprule
-  Parameter&Description&Range\\\midrule
-  Loops?&Is the program allowed to loop?&$\{\text{True},\text{False}\}$\\
-  Reflects?&Is the program allowed to have reflections?&$\{\text{True},\text{False}\}$\\
-  Incremental?&Solve the problem piece-by-piece or all at once?&$\{\text{True},\text{False}\}$\\
-  Maximum depth& Bound on the depth of the program syntax tree&$\{1,2,3\}$
-  \\\bottomrule
-  \end{tabular}
-  \end{table}
-
-Given a search policy, what is the best way of using it to quickly find minimum cost programs?
-We use a \emph{bias-optimal search algorithm} (see~\cite{schmidhuber2004optimal}):
-
-\textbf{Definition: Bias optimality.} A search algorithm is $n$-\emph{bias optimal}
-with respect to a distribution $\probability_{\text{bias}}[\cdot ]$ if it is
-guaranteed to find a solution $\sigma $ after searching for at least time
-$n\times\frac{t(\sigma )}{\probability_{\text{bias}}[\sigma ]}$, where $t(\sigma )$ is the time it
-takes to verify that $\sigma $ is a solution to the
-search problem.
-
-An example of a $1$-bias optimal search algorithm is a time-sharing system
-that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
-We construct a $1$-bias optimal search algorithm for our domain by
-identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |T)$
-and $t(\sigma )  $ with how long the program synthesizer takes to search through the programs in $\sigma $.
-
-In theory any $\pi_\theta(\cdot |\cdot ) $ is a bias-optimal searcher.
-But the real world runtime of the algorithm depends strongly upon
-the bias $\probability_{\text{bias}}[\cdot ]$.
-Our approach is to learn $\probability_{\text{bias}}[\cdot ]$
-by picking the policy that minimizes the
-expected bias-optimal time to solve a training corpus of graphics program synthesis problems,
-which is:
-\begin{align}
-\textsc{Loss}(\theta ; \text{training corpus})& =  \expect_{T\in \text{training corpus}}\left[ \min_{\sigma\in \text{\textsc{Best}}(T)}\frac{t(\sigma | T)}{\pi_\theta (\sigma | T)}\right]\label{policyLoss}\\
-\text{where }  \sigma \in\text{\textsc{Best}}(T) &\text{ if  a minimum cost program for }T \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t.
-}p\text{ evaluates to }T} \text{cost}(p) \nonumber
-\end{align}
-To generate a training corpus for learning a policy which minimizes this loss,
-we synthesized minimum cost programs for each trace of our hand drawings
-and for each $\sigma $.
-Solving these 2400\footnote{There are 100 the drawings and $2\times 2\times 2\times 3 = 24$ different values of $\sigma $} synthesis problems takes a little over a day on a 20-CPU machine.
-With the training set in hand we  %This loss is differentiable but nonconvex even if $\pi_{\theta}(\cdot |\cdot )^{-1}$ is convex.
- locally minimize this loss using gradient descent.% while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}.
-See supplement for details.
-
-Because we want to learn a policy from only $100$ hand-drawn sketches,
-we chose a simple low-capacity, bilinear model for a policy:
-\begin{equation}
-  \pi_{\theta}(\sigma |T)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{trace}}(T)\right)
-\end{equation}
-where $\phi_{\text{params}}(\sigma  )$ is a one-hot encoding of
-the parameter settings of $\sigma $ (see Table~\ref{policyOutput})
-and $\phi_{\text{trace}}(T)$ extracts a few simple features of the trace $T$;
-see supplement for details.
-
-We contrast our learned search policy
-with two alternatives (see Figure~\ref{policyEvaluation}):
-(1) \emph{Sketch}, which poses the
-entire problem wholesale to the Sketch program synthesizer;
-and (2) an \emph{Oracle},
-a policy which always picks the quickest to search $\sigma $
- also containing a minimum cost program.
-Our approach improves upon Sketch by itself,
-and comes close to the Oracle's performance.
-One could never construct this Oracle,
-because the agent does not know ahead of time which
-$\sigma $'s contain minimum cost programs nor does it know how long each
-$\sigma $ will take to search.
-The Oracle is an upper bound on the performance of any search policy.
-With this learned policy in hand we can now synthesize most programs in under a minute.
-\begin{figure}[h]
-  \centering  \includegraphics[width = 14cm]{figures/policyComparison.png}
-  \caption{How long does it typically take to synthesize a minimum cost program?
-Sketch: out-of-the-box performance of the Sketch~\cite{solar2008program} program synthesizer.
-Oracle: baseline that always picks the easiest synthesis problem containing a minimum cost program.
-Learned policy: a bias-optimal learned search policy running on an ideal timesharing machine.
-Oracle is impossible to implement and is an upper bound on the performance of any search policy.
-$\infty = $ timeout.
-Red dashed line is median time.}\label{policyEvaluation}
-\end{figure}
-
 \newcommand{\exampleProgramSize}{4.5cm}
@@
 \begin{figure}
+  \vspace{-0.6cm}
 \centering  \begin{tabular}{m{1.5cm}llc}
-    \toprule
-    \textbf{Drawing}&\textbf{Trace}&\textbf{Program}&\begin{tabular}{c}
-      \textbf{Compression}\\\textbf{factor}
-      \end{tabular}\\
+%    \toprule
+    \textbf{Drawing}&\textbf{Trace}&\textbf{Program}&%\begin{tabular}{c}
+      \textbf{Compression factor}%\\\textbf{factor}
+      %      \end{tabular}\\
+      \\
     \midrule
@@
 \end{lstlisting}
-\end{minipage}&$\frac{9}{5} = 1.8\text{x}$\\\bottomrule
+\end{minipage}&$\frac{9}{5} = 1.8\text{x}$ %\\\bottomrule
   \end{tabular}
@@
 Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformations in the top figure and second figure to bottom.}\label{exampleSynthesisResults}
+  \vspace{-0.7cm}
   \end{figure}
 
-\pagebreak
+\subsection{Learning a search policy for synthesizing programs}\label{learningASearchPolicy}
+
+We want to leverage powerful, domain-general techniques from the program synthesis community,
+but make them much faster by
+learning a domain-specific \emph{search policy}.
+A search policy proposes search problems
+like those in Eq.~\ref{programObjective},
+but can also offer additional constraints on the structure of the program (Tbl.~\ref{policyOutput}).
+For example, a policy might decide to first try searching over small programs before searching over large programs,
+or decide to prioritize searching over programs that have loops.
+
+A search policy $\pi_\theta(\sigma  | T )$ takes as input a trace $T$ and predicts a distribution over synthesis problems, each of which is written $\sigma $ and corresponds to a set of possible programs to search over (so $\sigma \subset \text{DSL}$).
+Good policies will prefer tractable program spaces,
+so that the search procedure will terminate early, 
+but should also prefer program spaces likely to contain
+programs that can explain the data.
+In general these two desiderata are in tension:
+tractable synthesis problems involve searching over smaller spaces,
+but smaller spaces are less likely to contain a minimum cost program
+for explaining the trace.
+Our goal now is to find the parameters of the policy, written $\theta$, which best navigate this trade-off.
+
+\begin{table}[h]\centering
+  \caption{Parameterization of different ways of posing the program synthesis problem.
+The policy learns to choose parameters likely to quickly yield a minimal cost program.
+In our notation, we write $\sigma $ to mean an assignment to each of these parameters, so $\sigma $ can assume one of 24 different values.}\label{policyOutput}
+  \begin{tabular}{lll}\toprule
+  Parameter&Description&Range\\\midrule
+  Loops?&Is the program allowed to loop?&$\{\text{True},\text{False}\}$\\
+  Reflects?&Is the program allowed to have reflections?&$\{\text{True},\text{False}\}$\\
+  Incremental?&Solve the problem piece-by-piece or all at once?&$\{\text{True},\text{False}\}$\\
+  Maximum depth& Bound on the depth of the program syntax tree&$\{1,2,3\}$
+  \\\bottomrule
+  \end{tabular}
+  \end{table}
+
+Given a search policy, what is the best way of using it to quickly find minimum cost programs?
+We use a \emph{bias-optimal search algorithm} (see~\cite{schmidhuber2004optimal}):
+
+\textbf{Definition: Bias optimality.} A search algorithm is $n$-\emph{bias optimal}
+with respect to a distribution $\probability_{\text{bias}}[\cdot ]$ if it is
+guaranteed to find a solution $\sigma $ after searching for at least time
+$n\times\frac{t(\sigma )}{\probability_{\text{bias}}[\sigma ]}$, where $t(\sigma )$ is the time it
+takes to verify that $\sigma $ is a solution to the
+search problem.
+
+An example of a $1$-bias optimal search algorithm is a time-sharing system
+that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
+We construct a $1$-bias optimal search algorithm for our domain by
+identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |T)$
+and $t(\sigma )  $ with how long the synthesizer takes to search  the programs in $\sigma $.
+
+In theory any $\pi_\theta(\cdot |\cdot ) $ is a bias-optimal searcher.
+But the actual runtime of the algorithm depends strongly upon
+the bias $\probability_{\text{bias}}[\cdot ]$.
+Our new approach is to learn $\probability_{\text{bias}}[\cdot ]$
+by picking the policy minimizing the
+expected bias-optimal time to solve a training corpus of graphics program synthesis problems:
+\begin{align}
+\textsc{Loss}(\theta ; \text{training corpus})& =  \expect_{T\in \text{training corpus}}\left[ \min_{\sigma\in \text{\textsc{Best}}(T)}\frac{t(\sigma | T)}{\pi_\theta (\sigma | T)}\right]\label{policyLoss}\\
+\text{where }  \sigma \in\text{\textsc{Best}}(T) &\text{ if  a minimum cost program for }T \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t.
+}p\text{ evaluates to }T} \text{cost}(p) \nonumber
+\end{align}
+To generate a training corpus for learning a policy which minimizes this loss,
+we synthesized minimum cost programs for each trace of our hand drawings
+and for each $\sigma $.
+Solving these
+%\footnote{There are 100 the drawings and $2\times 2\times 2\times 3 = 24$ different values of $\sigma $}
+synthesis problems takes a little over a day on 40 CPUs.
+With the training set in hand we  %This loss is differentiable but nonconvex even if $\pi_{\theta}(\cdot |\cdot )^{-1}$ is convex.
+ locally minimize this loss using gradient descent. % while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}.
+See supplement for details.
+Because we want to learn a policy from only $100$ hand-drawn sketches,
+we chose a simple low-capacity, bilinear model for a policy:
+\begin{equation}
+  \pi_{\theta}(\sigma |T)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{trace}}(T)\right)
+\end{equation}
+where $\phi_{\text{params}}(\sigma  )$ is a one-hot encoding of
+the parameter settings of $\sigma $ (see Tbl.~\ref{policyOutput})
+and $\phi_{\text{trace}}(T)$ extracts a few simple features of the trace $T$;
+see supplement for details.
+
+We contrast our learned search policy
+with two alternatives (see Fig.~\ref{policyEvaluation}):
+(1) \emph{Sketch}, which poses the
+entire problem wholesale to the Sketch program synthesizer;
+and (2) an \emph{Oracle},
+a policy which always picks the quickest to search $\sigma $
+ also containing a minimum cost program.
+Our approach improves upon Sketch by itself,
+and comes close to the Oracle's performance.
+One could never construct this Oracle,
+because the agent does not know ahead of time which
+$\sigma $'s contain minimum cost programs nor does it know how long each
+$\sigma $ will take to search.
+The Oracle is an upper bound on the performance of any search policy.
+With this learned policy in hand we can synthesize most programs in under a minute.
+\begin{figure}[h]
+  \centering  \includegraphics[width = 14cm]{figures/policyComparison.png}
+  \caption{How long does it typically take to synthesize a minimum cost program?
+Sketch: out-of-the-box performance of the Sketch~\cite{solar2008program} program synthesizer.
+Oracle: baseline that picks the easiest synthesis problem containing a minimum cost program.
+Learned policy: a bias-optimal learned search policy running on an ideal timesharing machine.
+Oracle  upper bounds  the performance of any search policy.
+$\infty = $ timeout.
+Red dashed line is median time.}\label{policyEvaluation}
+\end{figure}
+
 \section{Applications of graphics program synthesis}\label{applicationsSection}
@@
 \subsection{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
-\begin{wrapfigure}{r}{5.5cm}\vspace{-1cm}
+\begin{wrapfigure}{r}{5.5cm}\vspace{-0.5cm}
   \includegraphics[width = 5cm]{figures/programSuccess7.png}
@@
 Our learned prior favors shorter, simpler programs, thus (top example) continuing the pattern of not having an arrow is preferred, or (bottom example) continuing the ``binary search tree'' is preferred.}\label{exampleOfProgramCorrectingMistake}
-%  \vspace{1cm}
+  \vspace{-1cm}
   \end{wrapfigure}
@@
 of the best programs that describe them. Our features are counts of the number of times that different components in the
-DSL were used (Table~\ref{DSL}).  We project these features down to a
+DSL were used (Tbl.~\ref{DSL}).  We project these features down to a
 2-dimensional subspace using primary component analysis
@@
 Learned?
-(4) How does Equation 4 get used?
+(4) How does Eq.
+4 get used?
 Is this a modification to the beam search objective / SMC posterior?
@@
 
-\section{Related work}
+\subsection{Related work}
 

### 2017-10-25 short.tex
added another example of a program being learned

@@
 
-\newcommand{\exampleProgramSize}{4.5cm}
+\newcommand{\exampleProgramSize}{4cm}
 \newcommand{\exampleTraceSize}{3.5cm}
@@
 \begin{figure}
-  \vspace{-0.6cm}
+%  \vspace{-0.6cm}
 \centering  \begin{tabular}{m{1.5cm}llc}
-%    \toprule
+    \toprule
     \textbf{Drawing}&\textbf{Trace}&\textbf{Program}&%\begin{tabular}{c}
@@
 Circle(2,5)
-Circle(5,14)
-Circle(2,9)
 \end{lstlisting}
-\emph{... etc. ...; 13 lines}
+\small\emph{... etc. ...; 13 lines}
 \end{minipage}&
@@
 Line(3,11, 4,11)
-Line(8,9, 8,10)
-Circle(5,14)
 \end{lstlisting}
-  \emph{... etc. ...; 21 lines}
+  \small\emph{... etc. ...; 21 lines}
 \end{minipage}&\begin{minipage}{\exampleProgramSize}
@@
 \end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
+\includegraphics[width = \exampleDrawingSize]{figures/expert-101-trim.png}&
+\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
+Rectangle((1,10), (3,11))
+Rectangle((1,12), (3,13))
+Rectangle((4,8), (6,9))
+Rectangle((4,10), (6,11))
+\end{lstlisting}
+  \small\emph{... etc. ...; 16 lines}
+\end{minipage}&\begin{minipage}{\exampleProgramSize}
+\begin{lstlisting}
+for(i<4)
+ for(j<4)
+  rectangle(-3*i+9,-2*j+6,
+            -3*i+11,-2*j+7)
+\end{lstlisting}
+\end{minipage}&$\frac{16}{3} = 5.3\text{x}$\\\midrule
 \includegraphics[width = \exampleDrawingSize]{figures/expert-75-extra-trim.png}&
@@
   arrow = True)
-Line(7,14, 9,14), 
-  arrow = True)
 Circle(6,10)
-Circle(2,10)
 \end{lstlisting}
-    \emph{... etc. ...; 15 lines}
+    \small\emph{... etc. ...; 15 lines}
 \end{minipage}&
@@
 Circle(5,14)
-Circle(2,9)
-Circle(2,14)
-Circle(8,14)
-Circle(8,9)
-Line(2,10,2,13)
 Line(8,12,8,13)
-\end{lstlisting}
+\end{lstlisting}\small\emph{... etc. ...; 9 lines}%
   \end{minipage}&\begin{minipage}{\exampleProgramSize}
@@
 Rectangle(3,9, 4,10)
-Circle(2,14)
-Circle(8,14)
-Circle(5,11)
-Rectangle(3,12, 4,13)
-\end{lstlisting}
+\end{lstlisting}\small\emph{... etc. ...; 9 lines}
   \end{minipage}&\begin{minipage}{\exampleProgramSize}
@@
 \begin{align}
-\textsc{Loss}(\theta ; \text{training corpus})& =  \expect_{T\in \text{training corpus}}\left[ \min_{\sigma\in \text{\textsc{Best}}(T)}\frac{t(\sigma | T)}{\pi_\theta (\sigma | T)}\right]\label{policyLoss}\\
+\textsc{Loss}(\theta ; \text{training corpus})& =  \expect_{T\in \text{training corpus}}\left[ \min_{\sigma\in \text{\textsc{Best}}(T)}\frac{t(\sigma | T)}{\pi_\theta (\sigma | T)}\right] + \lambda |\theta|_2^2\label{policyLoss}\\
 \text{where }  \sigma \in\text{\textsc{Best}}(T) &\text{ if  a minimum cost program for }T \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t.
@@
 $\infty = $ timeout.
-Red dashed line is median time.}\label{policyEvaluation}
+Red dashed line is median time.
+Performance measured using cross validation.}\label{policyEvaluation}
 \end{figure}
@@
 Schmidhuber's OOPS model~\cite{schmidhuber2004optimal}.
-DeepCoder~\cite{BalGauBroetal16} and~\cite{menon2013machine} are
-recent models which, like ours, learn to predict which program
-components are likely to be useful given a program synthesis problem.
-Our work is different from their approaches because we treat the
-problem as a variety of \emph{metareasoning}, identifying and modeling
-the trade-off between tractable search and the probability of successful
-search.  TerpreT~\cite{gaunt2016terpret} was the first work to
-systematically compare constraint-based program synthesis techniques
+DeepCoder~\cite{BalGauBroetal16}is a recent model which, like ours, learns to predict likely program components.
+Our work differs because we treat
+problem as \emph{metareasoning}, identifying and modeling
+the trade-off between tractability and probability of success.
+TerpreT~\cite{gaunt2016terpret} 
+systematically compares constraint-based program synthesis techniques
 against gradient-based search techniques, like those used to train
 Differentiable Neural Computers~\cite{graves2016hybrid}).  The TerpreT
-experiments help motivate our use of constraint-based techniques.
+experiments motivate our use of constraint-based techniques.
 
@@
 The two approaches also differ in their architectures and training regimes: AIR learns a recurrent auto-encoding model via variational inference, whereas our parsing stage learns an autoregressive-style model from randomly-generated (trace, image) pairs.
-Finally, while AIR was evaluated on multi-MNIST images and synthetic 3D scenes, we focus on hand-drawn sketches.
+%Finally, while AIR was evaluated on multi-MNIST images and synthetic 3D scenes, we focus on hand-drawn sketches.
 % attend infer repeat:~\cite{eslami1603attend}. Crucial distinction is
@@
 Our image-to-trace parsing architecture builds on prior work on controlling procedural graphics programs~\cite{ritchie2016neurally}.
-Given a program which generates random 2D recursive structures such as vines, that system learns a structurally-identical ``guide program'' whose output can be directed, via neural networks, to resemble a given target image.
+%Given a program which generates random 2D recursive structures such as vines, that system learns a structurally-identical ``guide program'' whose output can be directed, via neural networks, to resemble a given target image.
 We adapt this method to a different visual domain (figures composed of multiple objects), using a broad prior over possible scenes as the initial program and viewing the trace through the guide program as a symbolic parse of the target image.
-We then show how to synthesize higher-level programs from these traces.
+We then show how to efficiently synthesize higher-level programs from these traces.
 
@@
 %A key similarity however is that both CogSketch and our system have as a goal to make it easier to produce nice-looking figures.
-Unsupervised Program Synthesis~\cite{ellis2015unsupervised} is a related framework which was also applied to geometric reasoning problems.
+%Unsupervised Program Synthesis~\cite{ellis2015unsupervised} is a related framework which was also applied to geometric reasoning problems.
 The goals of~\cite{ellis2015unsupervised} were cognitive modeling,
-and they applied their technique to synthetic scenes used in human behavioral studies.
+%and they applied their technique to synthetic scenes used in human behavioral studies.
 %% open domain sketch understanding.
@@
 
-The idea that an execution trace could assist in program learning goes back to the 1970's~\cite{Summers:1977:MLP:321992.322002} and has also been applied in neural models of program induction, like Neural Program Interpreters~\cite{DBLP:journals/corr/ReedF15}.
+The idea that an execution trace could assist in program learning goes back to the 1970's~\cite{Summers:1977:MLP:321992.322002} and has  been applied in neural models of program induction, like Neural Program Interpreters~\cite{DBLP:journals/corr/ReedF15}.
 Our contribution to this idea is the trace hypothesis:
-that traces can be inferred from perceptual data,
+that (unordered) traces can be inferred from perceptual data,
 and that the trace is the correct bridge between perception and symbolic representation.
@@
 In the synthesis phase, a more expressive DSL---including subroutines, recursion, and symmetry groups beyond reflections---would allow the system to effectively model a wider variety of graphical phenomena.
-The synthesizer itself could also be the subject of future work: the system currently uses the general-purpose Sketch synthesizer, which can take minutes to hours to run, whereas program synthesizers which are custom-built for special problem domains can run much faster or even interactively~\cite{le2014flashextract}.
+The synthesizer itself could also be the subject of future work: the system currently uses the general-purpose Sketch synthesizer, which can take minutes to hours to run, whereas custom-built domain-specific synthesizers can run much faster or even interactively~\cite{le2014flashextract}.
 
@@
 using Mixture Density Networks (MDN)~\cite{MDN}.
-Implementing a variant of our model that predicts continuous coordinates
-using Mixture Density Networks is straightforward;
-we have prototyped such a system and
-show examples of it both working and failing in the supplement.
-But, for our collection of hand drawings, discrete positional variables suffice,
-and currently work much better in practice.
+We prototyped a variant of our model that predicts continuous coordinates. See supplement.
 
@@
 We have presented a system for inferring graphics programs which generate \LaTeX-style figures from hand-drawn images.
-The system uses a combination of deep neural networks and stochastic search to parse drawings into symbolic execution traces; it then feeds these traces to a general-purpose program synthesis engine to infer a structured graphics program.
+The system uses a combination of deep neural networks and stochastic search to parse drawings into symbolic traces; it then feeds these traces to a general-purpose program synthesis engine to infer a structured graphics program.
 We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings and to organize them according to high-level geometric features.
@@
 In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the code.
-More generally, we believe that the two-phase system we have proposed---parsing into execution traces, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for other domains in which agents must programmatically reason about noisy perceptual input.
-
-\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl on the design of the neural architecture.
+More generally, we believe that the two-phase system we have proposed---parsing into traces, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for other domains in which agents must programmatically reason about noisy perceptual input.
+
+\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on the design of the neural architecture.
 

### 2017-10-27 short.tex
bunches of changes

@@
 For the first step, our approach uses a deep network to infer a set of primitive shape-drawing commands.
-We refer to this set as an unordered \emph{trace},\footnote{For our domain we do not require the trace to be ordered -- so it is similar to, but not exactly the same as, the execution trace of the program.} since it corresponds to the commands that a program would have issued but lacks the high-level structure that determines how the program decided to issue them.
+We refer to this set as a \emph{trace set} since it corresponds to the set of commands in a program's execution trace but lacks the high-level structure that determines how the program decided to issue them.
 %For added robustness, we train the network to produce a proposal distribution of the most likely traces and use stochastic search to find the trace that best matches the image.
 %The network is trained from an automatically-generated corpus of synthetic image-generating programs.
-The second step involves synthesizing a high-level program capable of producing the trace identified by the first phase.
+The second step involves synthesizing a high-level program capable of producing the trace set identified by the first phase.
 %In principle, we could also train a neural network to learn this mapping.
@@
 %This paper argues that this stage is best
-We achieve this by \emph{constraint-based program synthesis} \cite{solar2008program}.
-The program synthesizer can search the space of possible programs for one capable of producing the desired trace -- inducing structures like
+We achieve this by \emph{constraint-based program synthesis} \citep{solar2008program}.
+The program synthesizer searches the space of possible programs for one capable of producing the desired trace -- inducing structures like
 symmetries, loops, or conditional branches.
-Although these program do not need any training data,
+Although these program synthesizers do not need any training data,
 we show how to learn a \emph{search policy} 
@@
 \noindent \textbf{The Trace Hypothesis.} The set of commands issued by a program,
-which we call a \emph{trace},
+which we call a \emph{trace set},
 is the correct liaison between high-dimensional unstructured perceptual input and high-level structured symbolic representations.
@@
 \end{lstlisting}};
-    \node[ultra thick,anchor = west,inner sep=0pt](traceImage) at (3.22,-0.5) {
+    \node[ultra thick,anchor = west,inner sep=0pt](traceImage) at (3.3,-0.5) {
       \includegraphics[width = 0.9cm]{figures/39-parse.png}}; 
-    \node(trace)[draw,thin,fit = (traceImage) (traceSource), label = below:{{\small Trace}}] {};
+    \node(trace)[draw,thin,fit = (traceImage) (traceSource), label = below:{{\small Trace set}}] {};
 
@@
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-    ([yshift = -15,xshift = -115]trace.south) -- node[below = 6pt] {Section~\ref{neuralNetworkSection}: Perception$\to$Trace} ([yshift = -15,xshift = -5]trace.south);
+    ([yshift = -15,xshift = -115]trace.south) -- node[below = 6pt] {{\small Section~\ref{neuralNetworkSection}: Perception$\to$Trace set}} ([yshift = -15,xshift = -5]trace.south);
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-    ([xshift = 5,yshift = -15]trace.south) -- node[below = 6pt] {Section~\ref{programSynthesisSection}: Trace$\to$Program} ([xshift = 140,yshift = -15]trace.south);
+    ([xshift = 5,yshift = -15]trace.south) -- node[below = 6pt] {{\small Section~\ref{programSynthesisSection}: Trace Set$\to$Program}} ([xshift = 140,yshift = -15]trace.south);
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-([xshift = 150,yshift = -15]trace.south) -- node[below = 6pt] {Section~\ref{applicationsSection}: Applications} ([xshift = 250,yshift = -15]trace.south);
+([xshift = 150,yshift = -15]trace.south) -- node[below = 6pt] {{\small Section~\ref{applicationsSection}: Applications}} ([xshift = 250,yshift = -15]trace.south);
   \end{tikzpicture}
@@
 
-Prior work addresses converting hand drawings to vectors~\cite{huang2017shape,Nishida:2016:ISU:2897824.2925951} and converting synthetic images to symbolic parses~\cite{nsd,DBLP:journals/corr/Beltramelli17}.
-Our new contributions are: (1) A model that converts sketches to high-level programs.
-(2) An algorithm for learning a policy for efficiently searching for programs.
-(3) The trace hypothesis: a framework for going from perception to programs.
-  \end{itemize}
+The new contributions of this work are:
+(1) A model that converts sketches to high-level programs:
+in contrast to converting images to vectors or low-level parses~\citep{huang2017shape,Nishida:2016:ISU:2897824.2925951,nsd,DBLP:journals/corr/Beltramelli17,im2latex}.
+(2) An algorithm for learning a policy for efficiently searching for programs,
+building on Levin search~\citep{levin1973universal}
+and generalizing recent work like DeepCoder~\citep{BalGauBroetal16}.
+(3) The trace hypothesis: a framework for going from perception to programs,
+which connects this work to other models of program induction that use traces,
+like the  Neural Program Interpreter~\citep{DBLP:journals/corr/ReedF15}.
 
@@
 
-\section{Neural architecture for inferring drawing commands}\label{neuralNetworkSection}
+\section{Neural architecture for inferring trace sets}\label{neuralNetworkSection}
 
 We developed a deep network architecture for efficiently inferring a
-trace, $T$, from an image, $I$.  Our model constructs the
+trace set, $T$, from an image, $I$.
+Our model is a combination of  ideas from 
+Neurally-Guided Procedural Models~\citep{ritchie2016neurally}
+and Attend-Infer-Repeat~\citep{eslami1603attend}.
+Our model constructs the
 trace one drawing command at a time.  When predicting the next drawing
@@
 Networks:~\cite{jaderberg2015spatial}) to let the model attend to
-different regions of the image while predicting each token. For
-example, the network first decides to emit the \verb|circle| token
-conditioned on the image features, then it emits the $x$ coordinate of
+different regions of the image while predicting each token. In Fig.~\ref{architecture} the network first decided to emit the \verb|circle| token
+conditioned on the image features, then it emitted the $x$ coordinate of
 the circle conditioned on the image features and the \verb|circle|
-token, and finally it predicts the $y$ coordinate of the circle
+token, and finally it predicted the $y$ coordinate of the circle
 conditioned on the image features, the \verb|circle| token, and the
-$x$ coordinate. We constrain
-coordinates to lie on a discrete $16\times 16$ grid, and later explain
-how to remove this restriction.  See supplement for the full details
+$x$ coordinate. We currently constrain
+coordinates to lie on a discrete $16\times 16$ grid,
+but the grid could be made arbitrarily fine.  See supplement for the full details
 of the architecture, which we implemented in
-Tensorflow~\cite{tensorflow2015-whitepaper}.
+Tensorflow~\citep{tensorflow2015-whitepaper}.
 %% \remark{There are some more details that are important to provide
@@
 \tikzset{>=latex}
-\begin{figure}[h]
+\begin{figure}[t]
   \begin{tikzpicture}
@@
 
-  \node(next)[draw,very thick,fit = (l1) (l2) (l3), dashed, label = below:{Next line of code}] {};
+  \node(next)[draw,very thick,fit = (l1) (l2) (l3), dashed, label = below:{Next drawing command}] {};
 
@@
 \end{tikzpicture}
-\caption{Our neural architecture for inferring the trace of a graphics program from its output.
+\caption{Our neural architecture for inferring the trace set of a graphics program from its output.
 \textcolor{blue}{Blue}: network inputs.
@@
 Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}.
-STN (spatial transformer network) is a differentiable attention mechanism~\cite{jaderberg2015spatial}.}  \label{architecture}
+STN (spatial transformer network) is a differentiable attention mechanism~\citep{jaderberg2015spatial}.}  \label{architecture}
 \end{figure}
-\begin{table}[h]
+\begin{table}[t]
   \caption{Primitive drawing commands currently supported by our model.}
@@
 
-For the model in Fig.~\ref{architecture}, the distribution over the next drawing command factorizes as:
-\begin{equation}
-  \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(T)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
-\end{equation}
-where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
-the target image, $T$ is a trace, $\theta$ are the
-parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
-image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
-traces factorizes as:
-\begin{equation}
-  \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
-\end{equation}
-where $|T|$ is the length of trace $T$, the subscripts
-on $T$ index drawing commands within the trace (so $T_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
-token is emitted by the network to signal that the trace
-explains the image.
-
-We train the network by sampling traces $T$ and target
+%% For the model in Fig.~\ref{architecture}, the distribution over the next drawing command factorizes as:
+%% \begin{equation}
+%%   \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(T)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
+%% \end{equation}
+%% where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
+%% the target image, $T$ is a trace set, $\theta$ are the
+%% parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
+%% image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
+%% traces factorizes as:
+%% \begin{equation}
+%%   \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
+%% \end{equation}
+%% where $|T|$ is the length of trace $T$, the subscripts
+%% on $T$ index drawing commands within the trace (so $T_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
+%% token is emitted by the network to signal that the trace
+%% explains the image.
+
+We train the network by sampling trace sets $T$ and target
 images $I$ for randomly generated scenes
 and maximizing
-Eq.~\ref{objective} with respect to $\theta$ by gradient ascent.
+%Eq.~\ref{objective}
+the likelihood of $T$ given $I$ with respect to
+the model parameters, $\theta$,
+  by gradient ascent.
 We trained the network on $10^5$ scenes, which takes a little less than a day on an Nvidia TitanX GPU.
 
-Training does not require backpropagation across the entire sequence
+Training does not require backpropagation across the sequence
 of drawing commands: drawing to the canvas `blocks' the gradients,
-effectively offloading memory to an external visual store.  In a
-sense, this model is like an autoregressive variant of
-Attend-Infer-Repeat~\cite{eslami1603attend}, but critically, \emph{without a learned
-  recurrent memory state}, e.g. an RNN.  We can do without an RNN
-because we have access to ground truth (image, trace) pairs.  This
+effectively offloading memory to an external visual store.  
+This approach is like an autoregressive version of
+Attend-Infer-Repeat~\citep{eslami1603attend}, but critically, without a learned
+  recurrent memory state, e.g. an RNN.  We can do without an RNN
+because we learn from ground truth (image, trace) pairs.  This
 allows us to handle scenes with many objects without
 worrying about the conditioning of gradients as they propagate
-over long sequences, and also makes training more straightforward (it
-is just maximum likelihood estimation of the model parameters).
-
-Our network suffices to ``derender'' synthetic images like those shown in
-Fig.~\ref{trainingData}.  We can perform a beam search decoding to
-recover what the network thinks is the most likely trace for
-images like these, recovering traces maximizing $\probability_\theta
+over long sequences, and makes training more straightforward: it
+is just maximum likelihood estimation of the model parameters.
+
+Our network can ``derender'' random synthetic images
+%those shown in Fig.~\ref{trainingData}.
+by doing a beam search decoding to
+recover  trace sets traces maximizing $\probability_\theta
 [T|I]$. But, if the network makes a mistake (predicts an incorrect
-line of code), it has no way of recovering from the error.  In order
-to derender an image with $n$ objects, it must correctly predict $n$
-drawing commands -- so its probability of success will decrease
-exponentially in $n$, assuming it has any nonzero chance of making a
+drawing command), it has no way of recovering from the error.  
+To derender an image with $n$ objects, it must correctly predict $n$
+commands -- so its probability of success will decrease
+exponentially in $n$, assuming it has a nonzero chance of making a
 mistake.  For added robustness as $n$ becomes large, we treat the
-neural network outputs as proposals for a Sequential Monte Carlo (SMC) sampling scheme~\cite{SMCBook}.  For
-the SMC sampler, we use pixel-wise distance as a surrogate for a
+neural network outputs as proposals for a Sequential Monte Carlo (SMC) sampling scheme~\citep{SMCBook}.  For
+the SMC sampler, we use pixel-wise distance as a surrogate
+\clearpage\begin{wrapfigure}{R}{8cm}
+  \centering
+      \includegraphics[width = 7cm]{figures/editDistance36.png}
+%    \includegraphics[width = 4cm]{figures/accuracy.png}
+      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
+It generalizes to scenes with many more objects.
+Neither the stochastic search nor the neural network are sufficient on their own.
+\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}
+\end{wrapfigure}
+\noindent
+for a
 likelihood function. The SMC sampler is designed to produce samples
@@
 whether a drawing command is correct.
-%Empirically, accuracy is much better when we combine these signals.
 
@@
 training data.
-We compare with a natural baseline that models the problem as a kind of image captioning (LSTM in Fig.~\ref{syntheticResults}).
+We compare with a baseline that models the problem as image captioning (LSTM in Fig.~\ref{syntheticResults}).
 Given the target image, this baseline produces the trace in one shot by
@@
 
-\begin{figure}[H]\centering
-  \begin{minipage}{6cm}
-    \begin{minipage}[t]{3cm}\fbox{\includegraphics[width=2.75cm]{figures/randomScene-58-7.png}}\end{minipage}%
-    \begin{minipage}[t]{3cm}\fbox{\includegraphics[width=2.75cm]{figures/randomScene-33-5.png}}\end{minipage}
-    \caption{Network is trained to infer traces for randomly generated scenes like the two shown above. See supplement for details of the training data generation.}\label{trainingData}
-  \end{minipage}\hfill%
-  \begin{minipage}{7.5cm}\centering
-    \includegraphics[width = 7cm]{figures/editDistance36.png}
-%    \includegraphics[width = 4cm]{figures/accuracy.png}
-      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
+%% \begin{figure}[H]\centering
+%%   \begin{minipage}{6cm}
+%%     \begin{minipage}[t]{3cm}\fbox{\includegraphics[width=2.75cm]{figures/randomScene-58-7.png}}\end{minipage}%
+%%     \begin{minipage}[t]{3cm}\fbox{\includegraphics[width=2.75cm]{figures/randomScene-33-5.png}}\end{minipage}
+%%     \caption{Network is trained to infer traces for randomly generated scenes like the two shown above. See supplement for details of the training data generation.}\label{trainingData}
+%%   \end{minipage}\hfill%
+%%   \begin{minipage}{7.5cm}\centering
+%%     \includegraphics[width = 7cm]{figures/editDistance36.png}
+%% %    \includegraphics[width = 4cm]{figures/accuracy.png}
+%%       \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
 It generalizes to scenes with many more objects.
@@
 \# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}
-    \end{minipage}
-
-  \end{figure}
-
-\subsection{Generalizing to hand drawings}
-A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
- We train the model
-to generalize to hand drawings by introducing noise into the
-renderings of the training target images.
-We designed this noise process to introduce the kinds of variations found in hand drawings (Fig.~\ref{handDrawingExamples}; see supplement for details).
-
+%%     \end{minipage}
+
+%%   \end{figure}
+
+\subsection{Generalizing to hand drawings}\label{generalizingTheHandDrawings}
 \begin{wrapfigure}{R}{6cm}
@@
   \end{minipage}%
-    \caption{(a): a hand drawing.
-(b): Rendering of the trace our model infers for (a).
-We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) for a noisy rendering of (b).}\label{handDrawingExamples}
+    \caption{(a): hand drawing. (b): Rendering of the trace our model infers for (a). (c): noisy rendering of (b).}\label{handDrawingExamples}
 \end{wrapfigure}
+
+A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
+ We train the model
+to generalize to hand drawings by introducing noise into the
+renderings of the training target images.
+We designed this noise process to introduce the kinds of variations found in hand drawings (Fig.~\ref{handDrawingExamples}; see supplement for details).
 
@@
 which is  the number of drawing commands by which two traces differ:
-\begin{multline}
--\log L_{\text{learned}}(\text{render}(T_1)|\text{render}(T_2))\approx\\ |T_1 - T_2| + |T_2 - T_1|\label{symmetricDistance}
-\end{multline}
-%Intuitively,
-%$L_{\text{learned}}(\cdot|\cdot)$ approximates the distance between
-%the trace we want and the trace we have so far.
-Pixel-wise distance
+  \begin{equation}
+    -\log L_{\text{learned}}(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|\label{symmetricDistance}
+    \end{equation}
+
+Pixel-wise
+distance
 metrics are sensitive to the details of how
@@
 
-We drew 100 figures by hand; see Fig.~\ref{lotsOfHandDrawings}.
+We evaluate our system on 100 hand-drawn figures; see Fig.~\ref{drawingSuccesses}--\ref{drawingFailures}.
 These were drawn carefully but not perfectly.
@@
 we made the drawings on graph paper.
-
-For each drawing we annotated a ground truth trace and asked the neurally guided SMC sampler
-to produce many candidate traces for each drawing.
+For each drawing we annotated a ground truth trace and have the neurally guided SMC sampler
+produce many candidate traces for each drawing.
 For 63\% of the drawings, the Top-1 most likely sample exactly matches the
@@
 that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
-Because the model sometimes makes mistakes % on hand drawings,
-we envision it working as follows:
-a user sketches a diagram,
-and the system responds by proposing a few candidate interpretations.
-The user could then select the one closest to their intention and edit it if necessary.
+We will show that the program synthesizer
+corrects some of these small errors (Sec.~\ref{synthesizerHelpsParsing}).
+
+%% Because the model sometimes makes mistakes % on hand drawings,
+%% we envision it working as follows:
+%% a user sketches a diagram,
+%% and the system responds by proposing a few candidate interpretations.
+%% The user could then select the one closest to their intention and edit it if necessary.
 
@@
       \end{tabular}
-    \subcaption{Left to right: Ising model, recurrent network architecture, figure from a deep learning textbook \cite{Goodfellow-et-al-2016}, graphical model}
+    \caption{Left to right: Ising model, recurrent network architecture, figure from a deep learning textbook \cite{Goodfellow-et-al-2016}, graphical model}\label{drawingSuccesses}
   \end{minipage}
@@
 
-    \subcaption{Near misses. Rightmost: illusory contours (note: no SMC)}
+    \caption{Near misses. Rightmost: illusory contours (note: no SMC)}\label{drawingFailures}
   \end{minipage}
 
-  \caption{Example drawings above model outputs.
+%  \caption{Example drawings above model outputs.
 See also Fig.~\ref{firstPageExamples}.
@@
       \end{minipage}
+            \vspace{-1cm}
 \end{figure}
@@
 
-\section{Synthesizing graphics programs from drawing commands}\label{programSynthesisSection}
-While the trace of a graphics program describes the contents
+\section{Synthesizing graphics programs from trace sets}\label{programSynthesisSection}
+Although the trace set of a graphics program describes the contents
 of a scene, it does not encode higher-level features of the image,
 such as repeated motifs or symmetries.  A \emph{graphics
-  program} better describe such structures;
-we seek to synthesize simple graphics programs from their traces.
+  program} better describes such structures.
+We seek to synthesize graphics programs from their traces.
 
@@
   \caption{Grammar over graphics programs.
-We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertibb/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations ($\mathbb{Z}$\texttt{ * }Var\texttt{ + }$\mathbb{Z}$).}\label{DSL}
+We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertical/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations ($\mathbb{Z}$\texttt{ * }Var\texttt{ + }$\mathbb{Z}$).}\label{DSL}
   \begin{tabular}{rl}\toprule
@@
 %algorithm is beyond the scope of this paper; see~\cite{solar2008program}.
-At a
-high level, Sketch takes as input a space of programs, along with a
-specification of the program's behavior and optionally a cost
+At a high level, Sketch takes as input a space of programs, along with
+a specification of the program's behavior and optionally a cost
 function.  It translates the synthesis problem into a constraint
-satisfaction problem and then uses a SAT solver to find a
-minimum-cost program satisfying the specification.  In exchange for
-having no guarantee on the time required to find a minimum
-cost solution, it comes with the guarantee that it will always find a
-globally optimal program.
-Synthesis times vary from minutes to hours,
+satisfaction problem and then uses a SAT solver to find a minimum-cost
+program satisfying the specification.  Sketch requires that the
+program space be \emph{finite}, which here means that the depth of the
+program syntax tree is bounded (we set the bound to 3),
+but comes with the guarantee that it will
+always eventually find the globally optimal (depth-bounded) solution.
+In exchange for this optimality guarantee
+it comes with no guarantees
+on runtime.
+For our domain synthesis times vary from minutes to hours,
 with 27\% of the drawings timing out the synthesizer after 1 hour.
@@
 We next describe how to learn to synthesize programs much faster (Section~\ref{learningASearchPolicy}),
-timing out on 2\% of the drawings and solving most problems in under a minute.
+timing out on 2\% of the drawings and solving 58\% of problems within a minute.
 
@@
 
-\begin{figure}
+\begin{figure}[t]
 %  \vspace{-0.6cm}
@@
   \end{tabular}
-\caption{Example drawings (left), their ground truth traces (middle left), and programs synthesized from these traces (middle right).
+\caption{Example drawings (left), their ground truth trace sets (middle left), and programs synthesized from these traces (middle right).
 Compared to the trace the programs are more compressive (right: programs have fewer lines than traces) and automatically group together related drawing commands.
 Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformations in the top figure and second figure to bottom.}\label{exampleSynthesisResults}
-  \vspace{-0.7cm}
+%  \vspace{-0.7cm}
   \end{figure}
@@
 like those in Eq.~\ref{programObjective},
-but can also offer additional constraints on the structure of the program (Tbl.~\ref{policyOutput}).
+but also offers additional constraints on the structure of the program (Tbl.~\ref{policyOutput}).
 For example, a policy might decide to first try searching over small programs before searching over large programs,
@@
 but should also prefer program spaces likely to contain
-programs that can explain the data.
+programs that concisely explain the data.
 In general these two desiderata are in tension:
@@
 The policy learns to choose parameters likely to quickly yield a minimal cost program.
-In our notation, we write $\sigma $ to mean an assignment to each of these parameters, so $\sigma $ can assume one of 24 different values.}\label{policyOutput}
+We slightly abuse notation by writing $\sigma $ to mean an assignment to each of these parameters (so $\sigma $ assumes one of 24 different values) and to mean the set of programs selected by that parameterization (so $\sigma \subseteq \text{DSL}$)}\label{policyOutput}
   \begin{tabular}{lll}\toprule
@@
 with respect to a distribution $\probability_{\text{bias}}[\cdot ]$ if it is
-guaranteed to find a solution $\sigma $ after searching for at least time
+guaranteed to find a solution in $\sigma $ after searching for at least time
 $n\times\frac{t(\sigma )}{\probability_{\text{bias}}[\sigma ]}$, where $t(\sigma )$ is the time it
-takes to verify that $\sigma $ is a solution to the
+takes to verify that $\sigma $ contains a solution to the
 search problem.
 
+Intuitively, an $n$-bias optimal search algorithm
+spends at least $\probability_{\text{bias}}[\sigma ]/n$ of its time
+exploring solution space $\sigma $.
 An example of a $1$-bias optimal search algorithm is a time-sharing system
@@
 and $t(\sigma )  $ with how long the synthesizer takes to search  the programs in $\sigma $.
-
-In theory any $\pi_\theta(\cdot |\cdot ) $ is a bias-optimal searcher.
+Now in theory any $\pi_\theta(\cdot |\cdot ) $ is a bias-optimal searcher.
 But the actual runtime of the algorithm depends strongly upon
@@
 by picking the policy minimizing the
-expected bias-optimal time to solve a training corpus of graphics program synthesis problems:
+expected bias-optimal time to solve a training corpus, $\mathcal{D}$, of graphics program synthesis problems:
 \begin{align}
-\textsc{Loss}(\theta ; \text{training corpus})& =  \expect_{T\in \text{training corpus}}\left[ \min_{\sigma\in \text{\textsc{Best}}(T)}\frac{t(\sigma | T)}{\pi_\theta (\sigma | T)}\right] + \lambda |\theta|_2^2\label{policyLoss}\\
+\textsc{Loss}(\theta ; \mathcal{D})& =  \expect_{T\sim\mathcal{D}}\left[ \min_{\sigma\in \text{\textsc{Best}}(T)}\frac{t(\sigma | T)}{\pi_\theta (\sigma | T)}\right] + \lambda \Vert\theta\Vert_2^2\label{policyLoss}\\
 \text{where }  \sigma \in\text{\textsc{Best}}(T) &\text{ if  a minimum cost program for }T \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t.
@@
 and for each $\sigma $.
-Solving these
+%Solving these
 %\footnote{There are 100 the drawings and $2\times 2\times 2\times 3 = 24$ different values of $\sigma $}
-synthesis problems takes a little over a day on 40 CPUs.
-With the training set in hand we  %This loss is differentiable but nonconvex even if $\pi_{\theta}(\cdot |\cdot )^{-1}$ is convex.
- locally minimize this loss using gradient descent. % while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}.
+%synthesis problems takes a little over a day on 40 CPUs.
+%With the training set in hand we  %This loss is differentiable but nonconvex even if $\pi_{\theta}(\cdot |\cdot )^{-1}$ is convex.
+We locally minimize this loss using gradient descent. % while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}.
 See supplement for details.
@@
 The Oracle is an upper bound on the performance of any search policy.
-With this learned policy in hand we can synthesize most programs in under a minute.
+With this learned policy in hand we can synthesize 58\% of programs within a minute.
 \begin{figure}[h]
@@
   \caption{How long does it typically take to synthesize a minimum cost program?
-Sketch: out-of-the-box performance of the Sketch~\cite{solar2008program} program synthesizer.
+Sketch: out-of-the-box performance of the Sketch~\citep{solar2008program} program synthesizer.
 Oracle: baseline that picks the easiest synthesis problem containing a minimum cost program.
@@
 Our learned prior favors shorter, simpler programs, thus (top example) continuing the pattern of not having an arrow is preferred, or (bottom example) continuing the ``binary search tree'' is preferred.}\label{exampleOfProgramCorrectingMistake}
-  \vspace{-1cm}
-  \end{wrapfigure}
-The program synthesizer can correct errors from the trace proposal network by favoring traces which lead to more
+\vspace{0.5cm}  \end{wrapfigure}
+The program synthesizer corrects errors made by the neural network by favoring trace sets which lead to more
 concise or general programs.  For example, figures with perfectly aligned objects are preferable to figures whose parts are slightly misaligned, and precise alignment lends itself to short
-programs.  Concretely, we estimated a prior over programs. Then,
-given the few most likely traces output by the neurally guided sampler,
-we reranked them according to the prior probability of their programs.
+programs.
+Concretely,
+we run the program synthesizer on the
+Top-$k$  most likely traces output by the neurally guided sampler.
+Then, the system
+reranks the Top-$k$  by  the prior probability of their programs.
+The prior probability of a program is learned by picking the prior maximizing
+the likelihood of the ground truth trace sets;
+see supplement for details.
+
+This procedure can only fix
+mistakes made by the neural network when
+a correct trace is in the Top-$k$.
 Our sampler could only do better on
-7/100 drawings by looking at the Top-100 sampled traces
+7/100 drawings by looking at the Top-5 or Top-100 sampled traces
 (see Fig.~\ref{drawingIntersectionOverUnion}),
@@
 We measure the similarity between two drawings by extracting features
-of the best programs that describe them. Our features are counts of the number of times that different components in the
-DSL were used (Tbl.~\ref{DSL}).  We project these features down to a
-2-dimensional subspace using primary component analysis
-(PCA); see Fig.\ref{NMF}.  One could use many
+of the lowest-cost programs that describe them. Our features are counts of the number of times that different components in the
+DSL were used (Tbl.~\ref{DSL}).
+We  then find drawings which are either close together or far apart in program feature space.
+One could use many
 alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
-We used our learned distance metric between traces, $L_{\text{learned}}(\cdot|\cdot)$, and projected to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}).
+We used our learned distance metric between trace sets, $L_{\text{learned}}(\cdot|\cdot)$,
+to find drawings that are either close together or far apart according to the learned
+distance metric over images.
+Tbl.~\ref{similarityMatrix} illustrates the kinds of drawings that these different metrics put closely together.
+
+\newcommand{\similaritySize}{1cm}
+\newcommand{\similarityArrowSize}{0.35cm}
+\begin{table}[t]
+\centering  \caption{Pairs of images either close together or far apart in different features spaces.
+The symbol $\leftrightarrow$ points to the compared images.
+Program features base captures abstract notions like symmetry and repetition.
+Distance metric over images is $L_{\text{learned}}(\cdot|\cdot)$ (see Section~\ref{generalizingTheHandDrawings}).}\label{similarityMatrix}
+  \begin{tabular}{lll}
+    &\textbf{Close in program space}&\textbf{Far apart in program space}\\\\
+    \textbf{Close in image space}&\begin{tabular}{l}
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-20-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-21-trim.png}\end{minipage}\\\\
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-50-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-2-trim.png}\end{minipage}
+      \end{tabular} &
+    \begin{tabular}{l}
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-22-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-77-trim.png}\end{minipage}\\\\
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-64-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-97-trim.png}\end{minipage}
+      \end{tabular}&\\
+    \textbf{Far apart in image space}&
+    \begin{tabular}{l}
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-16-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-17-trim.png}\end{minipage}
+    \end{tabular}&
+    \begin{tabular}{l}
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-75-extra-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-89-trim.png}\end{minipage}\\\\
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-3-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-39-trim.png}\end{minipage}
+      \end{tabular}
+  \end{tabular}
+  \end{table}
+
+%% We project these features down to a
+%% 2-dimensional subspace using primary component analysis
+%% (PCA); see Fig.\ref{NMF}.  One could use many
+%% alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
+%% We used our learned distance metric between traces, $L_{\text{learned}}(\cdot|\cdot)$, and projected to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}).
 This reveals similarities between the objects in the drawings,
-while missing similarities at the level of the program.
-\begin{figure}[h]
-\centering  \begin{minipage}{\textwidth}\centering
-  %\includegraphics[width = 0.69\textwidth]{figures/PCA.png}
-  \includegraphics[width = 0.69\textwidth]{figures/PCA_improved.png}
-    \caption{PCA on features of the programs that were synthesized for each drawing.
+%% while missing similarities at the level of the program.
+%% \begin{figure}[h]
+%% \centering  \begin{minipage}{\textwidth}\centering
+%%   %\includegraphics[width = 0.69\textwidth]{figures/PCA.png}
+%%   \includegraphics[width = 0.69\textwidth]{figures/PCA_improved.png}
+%%     \caption{PCA on features of the programs that were synthesized for each drawing.
 Symmetric figures cluster to the right; ``loopy'' figures cluster to the left; complicated programs are at the top and simple programs are at the bottom.}    \label{NMF}
-  \end{minipage} %\hfill
-  \begin{minipage}{\textwidth}\centering
-    \includegraphics[width = 0.69\textwidth]{figures/imageSimilarity.png} 
-    \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
-  \end{minipage}
-\end{figure}
-
-\pagebreak
+%%   \end{minipage} %\hfill
+%%   \begin{minipage}{\textwidth}\centering
+%%     \includegraphics[width = 0.69\textwidth]{figures/imageSimilarity.png} 
+%%     \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
+%%   \end{minipage}
+%% \end{figure}
+
 \subsection{Extrapolating figures}
@@
 For example,
-we can change all of the circles to squares or make all of the lines be dashed.
-We can also \textbf{extrapolate} figures
+we could change all of the circles to squares or make all of the lines be dashed.
+We \textbf{extrapolate} figures
 by increasing the number of times that loops are executed.
@@
 and having our system automatically induce and extend the pattern.
-Fig.~\ref{extrapolationFigure} shows extrapolations of programs synthesized from ground truth traces;
+Fig.~\ref{extrapolationFigure} shows extrapolations produced by our system;
 see supplement for our full set of extrapolations.
@@
   \includegraphics[width = \textwidth]{figures/extrapolationMatrix2.png}
+  \includegraphics[width = \textwidth]{figures/extrapolationMatrix3.png}  
   \caption{Top, white: hand drawings. Bottom, black: extrapolations produced by
@@
 %\pagebreak
-\section{Discussion}
-
-\subsection{Related work}
-
+%\section{Discussion}
+
+\section{Related work}
+
+\textbf{Program Induction:}
 Our approach to learning to search for programs draws theoretical
 underpinnings from Levin
-search~\cite{levin1973universal,solomonoff1984optimum} and
-Schmidhuber's OOPS model~\cite{schmidhuber2004optimal}.
-DeepCoder~\cite{BalGauBroetal16}is a recent model which, like ours, learns to predict likely program components.
+search~\citep{levin1973universal,solomonoff1984optimum} and
+Schmidhuber's OOPS model~\citep{schmidhuber2004optimal}.
+DeepCoder~\citep{BalGauBroetal16} is a recent model which, like ours, learns to predict likely program components.
 Our work differs because we treat
-problem as \emph{metareasoning}, identifying and modeling
+the problem as \emph{metareasoning}, identifying and modeling
 the trade-off between tractability and probability of success.
-TerpreT~\cite{gaunt2016terpret} 
+TerpreT~\citep{gaunt2016terpret} 
 systematically compares constraint-based program synthesis techniques
 against gradient-based search techniques, like those used to train
-Differentiable Neural Computers~\cite{graves2016hybrid}).  The TerpreT
+Differentiable Neural Computers~\citep{graves2016hybrid}.  The TerpreT
 experiments motivate our use of constraint-based techniques.
 
-Our work bears resemblance to the Attend-Infer-Repeat (AIR) system, which learns to decompose an image into its constituent objects~\cite{eslami1603attend}.
-AIR learns an iterative inference scheme which infers objects one by one and also decides when to stop inference; this is similar to our approach's first stage, which parses images into traces.
-Our approach further produces interpretable, symbolic programs which generate those traces.
-The two approaches also differ in their architectures and training regimes: AIR learns a recurrent auto-encoding model via variational inference, whereas our parsing stage learns an autoregressive-style model from randomly-generated (trace, image) pairs.
+\textbf{Deep Learning:} Our neural network bears resemblance to the Attend-Infer-Repeat (AIR) system, which learns to decompose an image into its constituent objects~\citep{eslami1603attend}.
+AIR learns an iterative inference scheme which infers objects one by one and also decides when to stop inference.
+%; this is similar to our approach's first stage, which parses images into traces. Our approach further produces interpretable, symbolic programs which generate those traces.
+Our network  differs in its architecture and training regime: AIR learns a recurrent auto-encoding model via variational inference, whereas our parsing stage learns an autoregressive-style model from randomly-generated (trace, image) pairs.
 %Finally, while AIR was evaluated on multi-MNIST images and synthetic 3D scenes, we focus on hand-drawn sketches.
-% attend infer repeat:~\cite{eslami1603attend}. Crucial distinction is
-% that they focus on learning the generative model jointly with the
-% inference network. Advantages of our system is that we learn symbolic
-% programs, and that we do it from hand sketches rather than synthetic
-% renderings.
-
-Our image-to-trace parsing architecture builds on prior work on controlling procedural graphics programs~\cite{ritchie2016neurally}.
+
+IM2LATEX~\citep{im2latex} is a recent work that also converts images to
+~\LaTeX.
+Their goal is to derender  \LaTeX~ equations,
+which recovers a markup language representation.
+Our goal is to go from
+noisy input to a high-level program,
+which goes beyond markup languages by supporting
+programming constructs like loops and conditionals.
+Recovering a high-level program is more challenging than recovering markup
+because it is a highly under constrained symbolic reasoning problem.
+
+Our image-to-trace parsing architecture builds on prior work on controlling procedural graphics programs~\citep{ritchie2016neurally}.
 %Given a program which generates random 2D recursive structures such as vines, that system learns a structurally-identical ``guide program'' whose output can be directed, via neural networks, to resemble a given target image.
@@
 In the computer graphics literature, there have been other systems which convert sketches into procedural representations.
-One uses a convolutional network to match a sketch to the output of a parametric 3D modeling system~\cite{huang2017shape}.
-Another uses convolutional networks to support sketch-based instantiation of procedural primitives within an interactive architectural modeling system~\cite{Nishida:2016:ISU:2897824.2925951}.
+One uses a convolutional network to match a sketch to the output of a parametric 3D modeling system~\citep{huang2017shape}.
+Another uses convolutional networks to support sketch-based instantiation of procedural primitives within an interactive architectural modeling system~\citep{Nishida:2016:ISU:2897824.2925951}.
 Both systems focus on inferring fixed-dimensional parameter vectors.
@@
 
-Prior work has also applied sketch-based program synthesis to authoring graphics programs.
-Sketch-n-Sketch is a bi-directional editing system in which direct manipulations to a program's output automatically propagate to the program source code~\cite{Hempel:2016:SSP:2984511.2984575}.
+\textbf{Hand-drawn sketches:} Prior work has also applied sketch-based program synthesis to authoring graphics programs.
+Sketch-n-Sketch is a bi-directional editing system in which direct manipulations to a program's output automatically propagate to the program source code~\citep{Hempel:2016:SSP:2984511.2984575}.
 We see this work as complementary to our own: programs produced by our method could be provided to a Sketch-n-Sketch-like system as a starting point for further editing.
-
-The CogSketch~\cite{forbus2011cogsketch} system also aims to have a
+The CogSketch system~\citep{forbus2011cogsketch} also aims to have a
 high-level understanding of hand-drawn figures. Their primary goal is
@@
 
-The idea that an execution trace could assist in program learning goes back to the 1970's~\cite{Summers:1977:MLP:321992.322002} and has  been applied in neural models of program induction, like Neural Program Interpreters~\cite{DBLP:journals/corr/ReedF15}.
+\textbf{The Trace Hypothesis:} The idea that an execution trace could assist in program learning goes back to the 1970's~\citep{Summers:1977:MLP:321992.322002} and has  been applied in neural models of program induction, like Neural Program Interpreters~\citep{DBLP:journals/corr/ReedF15}, or DeepCoder, which predicts what functions occur in the execution trace~\citep{BalGauBroetal16}.
 Our contribution to this idea is the trace hypothesis:
-that (unordered) traces can be inferred from perceptual data,
+that  trace sets can be inferred from perceptual data,
 and that the trace is the correct bridge between perception and symbolic representation.
@@
 
-\subsection{Future work}
-There are many directions for future work.
+%% \subsection{Future work}
+%% There are many directions for future work.
 The proposal network  currently handles only a very small subset of \LaTeX~drawing commands, though there is no reason that it could not be extended to handle more with a higher-capacity network.
-In the synthesis phase, a more expressive DSL---including subroutines, recursion, and symmetry groups beyond reflections---would allow the system to effectively model a wider variety of graphical phenomena.
-The synthesizer itself could also be the subject of future work: the system currently uses the general-purpose Sketch synthesizer, which can take minutes to hours to run, whereas custom-built domain-specific synthesizers can run much faster or even interactively~\cite{le2014flashextract}.
-
-In the parsing phase, the proposal network currently samples positional variables on a discrete $16\times 16$ grid.
+%% In the synthesis phase, a more expressive DSL---including subroutines, recursion, and symmetry groups beyond reflections---would allow the system to effectively model a wider variety of graphical phenomena.
+The synthesizer itself could also be the subject of future work: the system currently uses the general-purpose Sketch synthesizer, which can take minutes to hours to run, whereas custom-built domain-specific synthesizers can run much faster or even interactively~\citep{le2014flashextract}.
+
+%% In the parsing phase, the proposal network currently samples positional variables on a discrete grid.
 More general types of drawings could be supported by instead sampling from continuous distributions, e.g.
-using Mixture Density Networks (MDN)~\cite{MDN}.
-We prototyped a variant of our model that predicts continuous coordinates. See supplement.
-
-\subsection{Contributions}
+using Mixture Density Networks (MDN)~\citep{MDN}.
+%% We prototyped a variant of our model that predicts continuous coordinates. See supplement.
+
+\section{Contributions}
 
 We have presented a system for inferring graphics programs which generate \LaTeX-style figures from hand-drawn images.
-The system uses a combination of deep neural networks and stochastic search to parse drawings into symbolic traces; it then feeds these traces to a general-purpose program synthesis engine to infer a structured graphics program.
+The system uses a combination of deep neural networks and stochastic search to parse drawings into symbolic trace sets; it then feeds these traces to a general-purpose program synthesis engine to infer a structured graphics program.
 We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings and to organize them according to high-level geometric features.
@@
 In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the code.
-More generally, we believe that the two-phase system we have proposed---parsing into traces, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for other domains in which agents must programmatically reason about noisy perceptual input.
-
-\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on the design of the neural architecture.
-
-\subsubsection*{Supplemental information.} The supplement may be found at:~\url{http://web.mit.edu/ellisk/www/graphicsProgramSupplement.pdf}
+More generally, we believe the trace hypothesis, as realized in our two-phase system---parsing into trace sets, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for other domains in which agents must programmatically reason about noisy perceptual input.
+
+%% \subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on the design of the neural architecture.
+
+%% \subsubsection*{Supplemental information.} The supplement may be found at:~\url{http://web.mit.edu/ellisk/www/graphicsProgramSupplement.pdf}
 

### 2017-10-27 short.tex
additions to supplement

@@
 \newcommand{\exampleImageSize}{2cm}
+
+\usepackage{amsthm}
+
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
 
@@
   learn a convolutional neural network that proposes plausible drawing
-  primitives that explain an image. This set of drawing primitives is
-  like a trace of the primitive commands issued by a graphics
-  program. From this trace we use program synthesis techniques to
-  recover a graphics program with constructs such as variable
+  primitives that explain an image. These drawing primitives are
+  like a trace of the set of primitive commands issued by a graphics
+  program. We learn a model that uses program synthesis techniques to
+  recover a graphics program from that trace. These programs have constructs like variable
   bindings, iterative loops, or simple kinds of conditionals. With a
   graphics program in hand, we can correct errors made by the deep
-  network, cluster drawings by use of similar high-level geometric
+  network, measure similarity between drawings by use of similar high-level geometric
   structures, and extrapolate drawings.  Taken together these results
@@
 trace; see Tbl.~\ref{drawingCommandTable} for the drawing commands we currently model.  We predict the drawing
-command token-by-token,\footnote{A token is an atomic symbol  -- so the model is \emph{not} predicting lines of code character-by-character, but instead knows about the syntactic structure of primitive commands} conditioning each token both on the image
+command token-by-token,\footnote{Tokens are atomic symbols in the programming language  -- so the model is \emph{not} predicting lines of code character-by-character, but instead the model knows about the syntactic structure of primitive drawing commands} conditioning each token both on the image
 features and on the previously generated tokens. We also use a
@@
 by doing a beam search decoding to
-recover  trace sets traces maximizing $\probability_\theta
+recover  trace sets maximizing $\probability_\theta
 [T|I]$. But, if the network makes a mistake (predicts an incorrect
@@
   \end{minipage}%
-    \caption{(a): hand drawing. (b): Rendering of the trace our model infers for (a). (c): noisy rendering of (b).}\label{handDrawingExamples}
+    \caption{(a): hand drawing. (b): Rendering of the trace set our model infers for (a). (c): noisy rendering of (b).}\label{handDrawingExamples}
 \end{wrapfigure}
@@
 we made the drawings on graph paper.
-For each drawing we annotated a ground truth trace and have the neurally guided SMC sampler
+For each drawing we annotated a ground truth trace set and have the neurally guided SMC sampler
 produce many candidate traces for each drawing.
@@
       \begin{minipage}[c]{0.4\textwidth} 
-  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1,5,100)?
+  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1, 5, 100)?
     Distance to ground truth trace measured by the intersection over union of predicted vs.
 ground truth traces.
-(a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 5 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth trace.}\label{drawingIntersectionOverUnion}
+(a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 5 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth trace.
+Red: the full model.
+Other colors: lesioned versions of our model.}\label{drawingIntersectionOverUnion}
       \end{minipage}
@@
   \caption{Grammar over graphics programs.
-We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertical/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations ($\mathbb{Z}$\texttt{ * }Var\texttt{ + }$\mathbb{Z}$).}\label{DSL}
+We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertical/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations ($\mathbb{Z}\times$Var\texttt{+}$\mathbb{Z}$).}\label{DSL}
   \begin{tabular}{rl}\toprule
@@
   Statement$\to$&\texttt{reflect}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
-  Expression$\to$&$\mathbb{Z}$\texttt{ * }Var\texttt{ + }$\mathbb{Z}$\\
+  Expression$\to$&$\mathbb{Z}\times$Var\texttt{+}$\mathbb{Z}$\\
   Var$\to$&A free (unused) variable\\
@@
 satisfaction problem and then uses a SAT solver to find a minimum-cost
-program satisfying the specification.  Sketch requires that the
-program space be \emph{finite}, which here means that the depth of the
+program satisfying the specification.  Sketch requires a
+ \emph{finite program space}, which here means that the depth of the
 program syntax tree is bounded (we set the bound to 3),
@@
     \toprule
-    \textbf{Drawing}&\textbf{Trace}&\textbf{Program}&%\begin{tabular}{c}
+    \textbf{Drawing}&\textbf{Trace Set}&\textbf{Program}&%\begin{tabular}{c}
       \textbf{Compression factor}%\\\textbf{factor}
@@
 programs that concisely explain the data.
-In general these two desiderata are in tension:
+These two desiderata are in tension:
 tractable synthesis problems involve searching over smaller spaces,
@@
 
-\textbf{Definition: Bias optimality.} A search algorithm is $n$-\emph{bias optimal}
+\noindent\textbf{Definition: Bias-optimality.}
+   A search algorithm is $n$-\emph{bias optimal}
 with respect to a distribution $\probability_{\text{bias}}[\cdot ]$ if it is
@@
 Red dashed line is median time.
-Performance measured using cross validation.}\label{policyEvaluation}
+Learned policy evaluated using 20-fold cross validation.}\label{policyEvaluation}
 \end{figure}
@@
 distance metric over images.
-Tbl.~\ref{similarityMatrix} illustrates the kinds of drawings that these different metrics put closely together.
+Tbl.~\ref{similarityMatrix} illustrates the kinds of drawings that these different metrics put closely together,
+while the supplement shows low dimensional projections of
+program and image features.
 
@@
 and having our system automatically induce and extend the pattern.
-Fig.~\ref{extrapolationFigure} shows extrapolations produced by our system;
-see supplement for our full set of extrapolations.
+Fig.~\ref{extrapolationFigure} shows extrapolations produced by our system.
 \begin{figure}[H]

### 2017-10-27 supplement.tex
additions to supplement

@@
 % to compile a camera-ready version, add the [final] option, e.g.:
-\usepackage[final]{nips_2017}
+\usepackage{iclr2018_conference,times}%\usepackage[final]{nips_2017}
 
@@
 \usepackage{tikz}
+\usetikzlibrary{fit}
+\usetikzlibrary{arrows.meta}
+\usetikzlibrary{positioning}
+\usetikzlibrary{decorations.text,decorations.pathreplacing}
+\usetikzlibrary{decorations.pathmorphing}
+
 % As of 2011, we use the hyperref package to produce hyperlinks in the
@@
 \newcommand{\Expect}{\mathds{E}} %{{\rm I\kern-.3em E}}
+\newcommand{\indicator}{\mathds{1}} %{{\rm I\kern-.3em E}}
+\newcommand{\expect}{\mathds{E}} %{{\rm I\kern-.3em E}}
 \newcommand{\probability}{\mathds{P}} %{{\rm I\kern-.3em P}}
@@
 in accuracy we could possibly get is 70\% by looking at the top 10 traces. 
-\begin{wrapfigure}{R}{5.5cm}
+\begin{figure}[h]\centering
+  \begin{minipage}{6cm}
       \includegraphics[width = 5cm]{figures/programSuccess7.png}
   \includegraphics[width = 5cm]{figures/programSuccess16.png}
+    \end{minipage}
   \caption{Left: hand drawing.
@@
 Our learned prior favors shorter, simpler programs, thus (top example) continuing the pattern of not having an arrow is preferred, or (bottom example) continuing the binary search tree is preferred.}\label{exampleOfProgramCorrectingMistake}
-\end{wrapfigure}
+\end{figure}
+\pagebreak
 
+\section{Measuring similarity between drawings}
+
+We measure the similarity between two drawings by extracting features
+of the best programs that describe them. Our features are counts of the number of times that different components in the
+DSL were used.  We project these features down to a
+2-dimensional subspace using primary component analysis
+(PCA); see Fig.\ref{NMF}.  One could use many
+alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
+We used our learned distance metric between traces, $L_{\text{learned}}(\cdot|\cdot)$, and projected to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}).
+This reveals similarities between the objects in the drawings,
+while missing similarities at the level of the program.
+\begin{figure}[h]
+\centering  \begin{minipage}{\textwidth}\centering
+  %\includegraphics[width = 0.69\textwidth]{figures/PCA.png}
+  \includegraphics[width = 0.69\textwidth]{figures/PCA_improved.png}
+    \caption{PCA on features of the programs that were synthesized for each drawing.
+Symmetric figures cluster to the right; ``loopy'' figures cluster to the left; complicated programs are at the top and simple programs are at the bottom.}    \label{NMF}
+  \end{minipage} %\hfill
+  \begin{minipage}{\textwidth}\centering
+    \includegraphics[width = 0.69\textwidth]{figures/imageSimilarity.png} 
+    \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
+  \end{minipage}
+\end{figure}
+
+\section{Learning a bias optimal policy}
+Recall from the main paper that our goal is to estimate the policy minimizing the following loss:
+\begin{align}
+\textsc{Loss}(\theta ; \mathcal{D})& =  \expect_{T\sim\mathcal{D}}\left[ \min_{\sigma\in \text{\textsc{Best}}(T)}\frac{t(\sigma | T)}{\pi_\theta (\sigma | T)}\right] + \lambda \Vert\theta\Vert_2^2\label{policyLoss}\\
+\text{where }  \sigma \in\text{\textsc{Best}}(T) &\text{ if  a minimum cost program for }T \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t.
+}p\text{ evaluates to }T} \text{cost}(p) \nonumber
+\end{align}
+We make this optimization problem tractable by annealing our loss function during gradient descent:
+\begin{align}
+&  \textsc{Loss}_\beta(\theta ; \mathcal{D}) =  \expect_{T\sim\mathcal{D}}\left[ \textsc{SoftMinimum}_\beta \left\{
+    \frac{t(\sigma | T)}{\pi_\theta (\sigma | T)}    : \sigma\in \text{\textsc{Best}}(T)\right\}\right] + \lambda \Vert\theta\Vert_2^2\label{softenedObjective}\\
+  \text{where }&\textsc{SoftMinimum}_\beta (x_1,x_2,x_3,\cdots ) = \sum_n x_n  \frac{e^{-\beta x_n}}{\sum_{n'}e^{-\beta x_{n'}}}
+\end{align}
+Notice that $\textsc{SoftMinimum}_{\beta = \infty}(\cdot )$ is just $\min(\cdot )$.
+We set the regularization coefficient $\lambda = 0.1$ and minimize equation~\ref{softenedObjective}
+using Adam for 2000 steps, linearly increasing $\beta$ from $1$ to $2$.
+
+We parameterize the space of policies as a simple log bilinear model:
+\begin{equation}
+  \pi_{\theta}(\sigma |T)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{trace}}(T)\right)
+\end{equation}
+where:
+\begin{align*}
+  \phi_{\text{params}}(\sigma ) = [&\indicator [\sigma \text{ can loop}] ;\\
+    &\indicator [\sigma \text{ can reflect}];\\
+    &\indicator [\sigma \text{ is incremental}] ; \\
+    &\indicator [\sigma \text{ has depth bound }1];\indicator [\sigma \text{ has depth bound }2];\indicator [\sigma \text{ has depth bound }3];]\\
+  \phi_{\text{trace}}(T) = [&\text{\# circles in }T;\text{\# rectangles in }T;\text{\# lines in }T;1]
+  \end{align*}
+
+\pagebreak
 \section{Neural network architecture}
+
+\subsection{High-level overview}
+\tikzset{>=latex}
+\begin{figure}[t]
+  \begin{tikzpicture}
+  \node[draw,blue,ultra thick,anchor = west,inner sep=0pt,label=below:Target image: $I$](observation) at (0,-1) {\includegraphics[width = 2cm]{figures/expert-18.png}};
+  \node[draw,blue,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(T)$] (canvas) at (0,-4) {};
+  \draw[lightgray,ultra thin,step = 0.125] ([xshift = 0.5,yshift = 0.5]canvas.south west) grid ([xshift = -0.5,yshift = -0.5]canvas.north east);
+  % draw partial image on canvas
+  \draw (0.375cm,-3.25cm) circle (0.125cm);
+  \draw (0.625cm,-3.625) circle (0.125cm);
+  \draw (0.75cm,-3.375) circle (0.125cm);
+
+  \node[draw,ultra thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 3cm] (CNN) at (4.5,-2.5) {CNN};
+  \node[inner sep = 0pt](tensorProduct) at ([xshift = -1.5cm]CNN.west) {$\bigoplus$};
+
+  \node[rotate = -90,draw,ultra thick,inner sep=0pt,minimum width = 3cm,minimum height = 0.5cm] (features) at ([xshift = 1.5cm]CNN.east) {Image features};
+
+  \node[draw,ultra thick,minimum size = 1cm](c1) at ([xshift = 1.5cm]features.north) {MLP};
+  \node(l1) at ([yshift = -1.5cm]c1.south) {\verb|circle(|};
+  \node[draw,ultra thick,minimum size = 1cm](a2) at ([xshift = 1cm,yshift = 1.5cm]c1.east) {STN};
+  \node[draw,ultra thick,minimum size = 1cm](c2) at ([xshift = 1cm]c1.east) {MLP};
+  \draw[->,ultra thick] (a2.south) -- (c2.north);
+  \draw[->,ultra thick,red] (c1.south) -- (l1.north);
+  \node(l2) at ([yshift = -1.5cm]c2.south) {\verb|X=7,|};
+  \draw[->,ultra thick,red] (c2.south) -- (l2.north);
+  \node[draw,ultra thick,minimum size = 1cm](a3) at ([xshift = 1cm,yshift = 1.5cm]c2.east) {STN};
+  \node[draw,ultra thick,minimum size = 1cm](c3) at ([xshift = 1cm]c2.east) {MLP};
+
+  \draw[->,ultra thick] (a3.south) -- (c3.north);
+  \node(l3) at ([yshift = -1.5cm]c3.south) {\verb|Y=12)|};
+  \draw[->,ultra thick,red] (c3.south) -- (l3.north);
+
+  \draw[->,ultra thick] (features.north) -- (c1.west);
+  \draw[->,ultra thick] (features.north) to[out = 45,in = 160] (a2.north);
+  \draw[->,ultra thick] (features.north) to[out = 70,in = 140] (a3.north);
+  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c2.west);
+  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- ([yshift = -0.2cm]c3.west);
+  \draw[->,ultra thick] ([xshift = 0.25cm]l2.north) -- ([yshift = -0.25cm]c3.west);
+
+  \node(next)[draw,very thick,fit = (l1) (l2) (l3), dashed, label = below:{Next drawing command}] {};
+
+  \draw[-{>[scale = 1.5]},very thick,dashed] (next.west) -- ([yshift = -0.2cm]canvas.east) node [midway, below, sloped] (TextNode) {Renderer}; %: \LaTeX~Ti\emph{k}Z};
+
+  \draw[->,ultra thick] (canvas.east) -- (tensorProduct.south);%[yshift = -0.5cm]CNN.west);
+  \draw[->,ultra thick] (observation.east) -- (tensorProduct.north);%([yshift = 0.5cm]CNN.west);
+  \draw[->,ultra thick] (tensorProduct.east)  -- node[fill = white,rotate = 90] {{\tiny $256\times 256\times 2$}}  (CNN.west);
+  \draw[->,ultra thick] (CNN.east) -- node[fill = white,rotate = 90] {{\tiny $16\times 16\times 10$}} (features.south);
+%  \draw[]
+
+%  \node at (canvas.x,canvas.y) {Canvas};
+\end{tikzpicture}
+\caption{Our neural architecture for inferring the trace set of a graphics program from its output.
+\textcolor{blue}{Blue}: network inputs.
+Black: network operations.
+\textcolor{red}{Red}: samples from a multinomial.
+\texttt{Typewriter font}: network outputs.
+Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}.
+STN (spatial transformer network) is a differentiable attention mechanism~\citep{jaderberg2015spatial}.}  \label{architecture}
+\end{figure}
+For the model in Fig.~\ref{architecture}, the distribution over the next drawing command factorizes as:
+\begin{equation}
+  \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(T)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
+\end{equation}
+where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
+the target image, $T$ is a trace set, $\theta$ are the
+parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
+image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
+traces factorizes as:
+\begin{equation}
+  \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
+\end{equation}
+where $|T|$ is the length of trace $T$, the subscripts
+on $T$ index drawing commands within the trace (so $T_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
+token is emitted by the network to signal that the trace
+explains the image.
 
@@
 For readers wishing to generate their own synthetic training sets,
-we refer them to our source code at:~\url{https://github.com/ellisk42/TikZ}.
+we refer them to our source code at:~\url{redactedForAnonymity.com}.%https://github.com/ellisk42/TikZ}.
 
@@
 The rightmost column is the program we synthesized from a ground truth execution trace of the drawing.
+Note that because the inference procedure is stochastic,
+the top one most likely sample can vary from run to run.
+Below we report a representative sample from a run with 2000 particles.
 \input{synthesizerOutputs.tex}

### 2017-10-27 short.tex
example of a complicated program being learned

@@
 \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-Line(5,13, 2,10),
-  arrow = True)
+Line(5,13,2,10,arrow)
 Circle(5,9)
 Circle(8,5)
-Line(2,8, 2,6), 
-  arrow = True)
+Line(2,8, 2,6,arrow)
 Circle(2,5)
@@
  circle(-3*i+7,1)
- line(-3*i+7,4,-3*i+7,2,
-      arrow=True)
- line(4,9,-3*i+7,6,
-      arrow=True)
+ line(-3*i+7,4,-3*i+7,2,arrow)
+ line(4,9,-3*i+7,6,arrow)
 \end{lstlisting}
@@
 \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-Rectangle((1,10), (3,11))
-Rectangle((1,12), (3,13))
-Rectangle((4,8), (6,9))
-Rectangle((4,10), (6,11))
+Rectangle(1,10,3,11)
+Rectangle(1,12,3,13)
+Rectangle(4,8,6,9)
+Rectangle(4,10,6,11)
 \end{lstlisting}
@@
 \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-Line(11,14, 13,14), 
-  arrow = True)
+Line(11,14,13,14,arrow)
 Circle(10,10)
-Line(10,13, 10,11), 
-  arrow = True)
+Line(10,13,10,11,arrow)
 Circle(6,10)
@@
 for(i<4)
- line(-4*i+13,4,-4*i+13,2,
-      arrow=True)
+ line(-4*i+13,4,-4*i+13,2,arrow)
  for(j<3)
@@
   line(-4*j+10,5,-4*j+12,5,
-       arrow=True)
+       arrow)
 \end{lstlisting}
@@
 
-  \includegraphics[width = \exampleDrawingSize]{figures/expert-7-trim.png}&
+  \includegraphics[width = \exampleDrawingSize]{figures/expert-71-trim.png}&
 \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-Line(5,11,5,13)
-Circle(5,9)
-Circle(5,14)
-Line(8,12,8,13)
-\end{lstlisting}\small\emph{... etc. ...; 9 lines}%
+Line(3,10,3,14,arrow)
+Rectangle(11,8,15,10)
+Rectangle(11,14,15,15)
+Line(13,10,13,14,arrow)
+  \end{lstlisting}\small\emph{... etc. ...; 16 lines}%
   \end{minipage}&\begin{minipage}{\exampleProgramSize}
+%% \begin{lstlisting}
+%% for (i<3)
+%%  circle(-3*i+7,1)
+%%  circle(-3*i+7,6)
+%%  line(-3*i+7,-1*i+4,-3*i+7,5)
+%% \end{lstlisting}
 \begin{lstlisting}
-for (i<3)
- circle(-3*i+7,1)
- circle(-3*i+7,6)
- line(-3*i+7,-1*i+4,-3*i+7,5)
+for(i<3)
+ line(7,1,5*i+2,3,arrow)
+ for(j<i+1)
+  if(j>0)
+   line(5*j-1,9,5*i,5,arrow)
+  line(5*j+2,5,5*j+2,9,arrow)
+ rectangle(5*i,3,5*i+4,5)
+ rectangle(5*i,9,5*i+4,10)
+rectangle(2,0,12,1)
 \end{lstlisting}
-\end{minipage}&$\frac{9}{4} = 2.25\text{x}$\\\midrule
+\end{minipage}&$\frac{16}{9} = 1.8\text{x}$\\\midrule
 
@@
 Compared to the trace the programs are more compressive (right: programs have fewer lines than traces) and automatically group together related drawing commands.
-Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformations in the top figure and second figure to bottom.}\label{exampleSynthesisResults}
+Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformations in the top figure, and the complex program in the second figure to bottom.}\label{exampleSynthesisResults}
 %  \vspace{-0.7cm}

### 2017-10-27 short.tex
very fancy table

@@
 tool~\cite{solar2008program}.
-%Describing Sketch's program synthesis
-%algorithm is beyond the scope of this paper; see~\cite{solar2008program}.
-At a high level, Sketch takes as input a space of programs, along with
+%At a high level,
+Sketch takes as input a space of programs, along with
 a specification of the program's behavior and optionally a cost
@@
 program syntax tree is bounded (we set the bound to 3),
-but comes with the guarantee that it will
-always eventually find the globally optimal (depth-bounded) solution.
+but has the guarantee that it 
+always eventually finds the globally optimal solution.
 In exchange for this optimality guarantee
@@
 with 27\% of the drawings timing out the synthesizer after 1 hour.
-See Fig.~\ref{exampleSynthesisResults} for examples of the kinds of programs our system recovers.
+Fig.~\ref{exampleSynthesisResults} shows programs recovered by our system.
 A main impediment to our use of these general techniques is
 the prohibitively high cost of searching for programs.
-We next describe how to learn to synthesize programs much faster (Section~\ref{learningASearchPolicy}),
+We next describe how to learn to synthesize programs much faster (Sec.~\ref{learningASearchPolicy}),
 timing out on 2\% of the drawings and solving 58\% of problems within a minute.
@@
 \end{lstlisting}
-\end{minipage}&$\frac{9}{5} = 1.8\text{x}$ %\\\bottomrule
+\end{minipage}&$\frac{9}{5} = 1.8\text{x}$ \\\bottomrule
   \end{tabular}
@@
 Compared to the trace the programs are more compressive (right: programs have fewer lines than traces) and automatically group together related drawing commands.
-Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure, and affine transformations in the top figure, and the complex program in the second figure to bottom.}\label{exampleSynthesisResults}
-%  \vspace{-0.7cm}
+Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
   \end{figure}
@@
   \end{table}
-
 Given a search policy, what is the best way of using it to quickly find minimum cost programs?
-We use a \emph{bias-optimal search algorithm} (see~\cite{schmidhuber2004optimal}):
+We use a \emph{bias-optimal search algorithm}~\citep{schmidhuber2004optimal}:
 
@@
 distance metric over images.
-Tbl.~\ref{similarityMatrix} illustrates the kinds of drawings that these different metrics put closely together,
+Fig.~\ref{similarityMatrix} illustrates the kinds of drawings that these different metrics put closely together,
 while the supplement shows low dimensional projections of
@@
 \newcommand{\similarityArrowSize}{0.35cm}
-\begin{table}[t]
-\centering  \caption{Pairs of images either close together or far apart in different features spaces.
-The symbol $\leftrightarrow$ points to the compared images.
-Program features base captures abstract notions like symmetry and repetition.
-Distance metric over images is $L_{\text{learned}}(\cdot|\cdot)$ (see Section~\ref{generalizingTheHandDrawings}).}\label{similarityMatrix}
-  \begin{tabular}{lll}
-    &\textbf{Close in program space}&\textbf{Far apart in program space}\\\\
-    \textbf{Close in image space}&\begin{tabular}{l}
+\begin{figure}[t]
+  \begin{tabular}{c|c|c|}
+    \multicolumn{1}{c}{}    &\multicolumn{1}{c}{\textbf{Close in program space}}&\multicolumn{1}{c}{\textbf{Far apart in program space}}\\\cline{2-3}
+    \multicolumn{1}{c|}{}&&\\
+    \multicolumn{1}{c|}{    \begin{tabular}{l}\textbf{Close in }\\ \textbf{image space} \end{tabular}}    &
+    \begin{tabular}{l}
       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-20-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-21-trim.png}\end{minipage}\\\\
@@
       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-64-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-97-trim.png}\end{minipage}
-      \end{tabular}&\\
-    \textbf{Far apart in image space}&
-    \begin{tabular}{l}
+    \end{tabular}\\
+    \multicolumn{1}{c|}{}&&\\\cline{2-3}
+    \multicolumn{1}{c|}{}&&\\
+    \multicolumn{1}{c|}{    \begin{tabular}{c}\textbf{Far apart in }\\ \textbf{image space} \end{tabular}}    &        \begin{tabular}{l}
       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
@@
     \end{tabular}
+\\    \multicolumn{1}{c|}{}&&\\\cline{2-3}\cline{2-3}    
   \end{tabular}
-  \end{table}
+
+  \centering
+\caption{Pairs of images either close together or far apart in different features spaces.
+The symbol $\leftrightarrow$ points to the compared images.
+Features of the program capture abstract notions like symmetry and repetition.
+Distance metric over images is $L_{\text{learned}}(\cdot|\cdot)$ (see Section~\ref{generalizingTheHandDrawings}).
+The off-diagonal entries highlight the difference between these metrics: similarity of programs captures high-level features like repetition and symmetry, whereas similarity of images correspondends to similar drawing commands being in similar places.
+See Section 2 of the supplement for more examples.}\label{similarityMatrix}  \end{figure}
 
@@
 we could change all of the circles to squares or make all of the lines be dashed.
-We \textbf{extrapolate} figures
+We extrapolate figures
 by increasing the number of times that loops are executed.

### 2017-10-27 short.tex
final version before I do some final proofreading

@@
 We achieve this by \emph{constraint-based program synthesis} \citep{solar2008program}.
-The program synthesizer searches the space of possible programs for one capable of producing the desired trace -- inducing structures like
+The program synthesizer searches the space of possible programs for one capable of producing the desired trace set -- inducing structures like
 symmetries, loops, or conditional branches.
@@
 already drawn.  It then decides either to stop drawing or proposes
-another drawing command to add to the trace; if it decides
+another drawing command to add to the trace set; if it decides
 to continue drawing, the predicted primitive is rendered to its
@@
 predicts a distribution over the next drawing command to add to the
-trace; see Tbl.~\ref{drawingCommandTable} for the drawing commands we currently model.  We predict the drawing
+trace set; see Tbl.~\ref{drawingCommandTable} for the drawing commands we currently model.  We predict the drawing
 command token-by-token,\footnote{Tokens are atomic symbols in the programming language  -- so the model is \emph{not} predicting lines of code character-by-character, but instead the model knows about the syntactic structure of primitive drawing commands} conditioning each token both on the image
@@
 We compare with a baseline that models the problem as image captioning (LSTM in Fig.~\ref{syntheticResults}).
-Given the target image, this baseline produces the trace in one shot by
+Given the target image, this baseline produces the trace set in one shot by
 using a CNN to extract features of the input which are passed to an LSTM which finally predicts
@@
 The density $L_{\text{learned}}(\cdot|\cdot)$ is predicted by a convolutional network that we train to predict
-the distance between two traces conditioned upon their renderings.
+the distance between two trace sets conditioned upon their renderings.
 We train our likelihood surrogate to approximate the symmetric difference,
-which is  the number of drawing commands by which two traces differ:
+which is  the number of drawing commands by which two trace sets  differ:
   \begin{equation}
@@
   \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1, 5, 100)?
-    Distance to ground truth trace measured by the intersection over union of predicted vs.
-ground truth traces.
+    Distance to ground truth trace set measured by the intersection over union of predicted vs.
+ground truth.
 (a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 5 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth trace.
@@
   program} better describes such structures.
-We seek to synthesize graphics programs from their traces.
+We seek to synthesize graphics programs from their trace sets.
 
@@
 
-Given the DSL and a trace $T$, we want to recover a program that both evaluates to $T$
+Given the DSL and a trace set $T$, we want to recover a program that both evaluates to $T$
 and, at the same time, is the ``best'' explanation of $T$.
@@
 with 27\% of the drawings timing out the synthesizer after 1 hour.
-Fig.~\ref{exampleSynthesisResults} shows programs recovered by our system.
+Tbl.~\ref{exampleSynthesisResults} shows programs recovered by our system.
 A main impediment to our use of these general techniques is
@@
 
-\begin{figure}[t]
+\begin{table}[t]
+  \caption{Example drawings (left), their ground truth trace sets (middle left), and programs synthesized from these traces (middle right).
+Compared to the trace the programs are more compressive (right: programs have fewer lines than traces) and automatically group together related drawing commands.
+Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
 %  \vspace{-0.6cm}
@@
   \end{tabular}
-\caption{Example drawings (left), their ground truth trace sets (middle left), and programs synthesized from these traces (middle right).
-Compared to the trace the programs are more compressive (right: programs have fewer lines than traces) and automatically group together related drawing commands.
-Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
-  \end{figure}
+  \end{table}
 
@@
 
-\begin{table}[h]\centering
-  \caption{Parameterization of different ways of posing the program synthesis problem.
-The policy learns to choose parameters likely to quickly yield a minimal cost program.
-We slightly abuse notation by writing $\sigma $ to mean an assignment to each of these parameters (so $\sigma $ assumes one of 24 different values) and to mean the set of programs selected by that parameterization (so $\sigma \subseteq \text{DSL}$)}\label{policyOutput}
-  \begin{tabular}{lll}\toprule
-  Parameter&Description&Range\\\midrule
-  Loops?&Is the program allowed to loop?&$\{\text{True},\text{False}\}$\\
-  Reflects?&Is the program allowed to have reflections?&$\{\text{True},\text{False}\}$\\
-  Incremental?&Solve the problem piece-by-piece or all at once?&$\{\text{True},\text{False}\}$\\
-  Maximum depth& Bound on the depth of the program syntax tree&$\{1,2,3\}$
-  \\\bottomrule
-  \end{tabular}
-  \end{table}
 Given a search policy, what is the best way of using it to quickly find minimum cost programs?
@@
 
-Intuitively, an $n$-bias optimal search algorithm
-spends at least $\probability_{\text{bias}}[\sigma ]/n$ of its time
-exploring solution space $\sigma $.
-An example of a $1$-bias optimal search algorithm is a time-sharing system
-that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
-We construct a $1$-bias optimal search algorithm for our domain by
-identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |T)$
-and $t(\sigma )  $ with how long the synthesizer takes to search  the programs in $\sigma $.
+Intuitively, an $n$-bias optimal search algorithm spends at least $\probability_{\text{bias}}[\sigma ]/n$ of its time exploring solution space $\sigma $.
+An example of a $1$-bias optimal search algorithm is a time-sharing system that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
+We construct a $1$-bias optimal search algorithm for our domain by identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |T)$ and $t(\sigma )  $ with how long the synthesizer takes to search  the programs in $\sigma $.
+This means that the search algorithm explores the entire program space, but spends most of its time searching through the regions of the space that  the policy judges to be most promising.
+
 Now in theory any $\pi_\theta(\cdot |\cdot ) $ is a bias-optimal searcher.
@@
 With this learned policy in hand we can synthesize 58\% of programs within a minute.
+\begin{table}[h]\centering
+  \caption{Parameterization of different ways of posing the program synthesis problem.
+The policy learns to choose parameters likely to quickly yield a minimal cost program.
+We slightly abuse notation by writing $\sigma $ to mean an assignment to each of these parameters (so $\sigma $ assumes one of 24 different values) and to mean the set of programs selected by that parameterization (so $\sigma \subseteq \text{DSL}$)}\label{policyOutput}
+  \begin{tabular}{lll}\toprule
+  Parameter&Description&Range\\\midrule
+  Loops?&Is the program allowed to loop?&$\{\text{True},\text{False}\}$\\
+  Reflects?&Is the program allowed to have reflections?&$\{\text{True},\text{False}\}$\\
+  Incremental?&Solve the problem piece-by-piece or all at once?&$\{\text{True},\text{False}\}$\\
+  Maximum depth& Bound on the depth of the program syntax tree&$\{1,2,3\}$
+  \\\bottomrule
+  \end{tabular}
+  \end{table}
 \begin{figure}[h]
@@
 
-\section{Applications of graphics program synthesis}\label{applicationsSection}
+\pagebreak\section{Applications of graphics program synthesis}\label{applicationsSection}
 Why synthesize a graphics program,

### 2017-12-05 revision.tex
shorter revision for iclr

--- 2017-10-27 short.tex
@@
 \usepackage{iclr2018_conference,times}
+%\iclrfinalcopy
 
@@
 
-% \title{Inferring Graphics Programs from Images}
 \title{Learning to Infer Graphics Programs from Hand-Drawn Images}
+
+%\lhead{nothing}
 
@@
 
-\author{
-Kevin Ellis\\
+\author{Kevin Ellis\\
   MIT\\
@@
 We present a hybrid architecture for inferring graphics programs that is structured around these two steps.
-For the first step, our approach uses a deep network to infer a set of primitive shape-drawing commands.
+For the first step,   a deep network to infers a set of primitive shape-drawing commands.
 We refer to this set as a \emph{trace set} since it corresponds to the set of commands in a program's execution trace but lacks the high-level structure that determines how the program decided to issue them.
@@
 and Attend-Infer-Repeat~\citep{eslami1603attend}.
-Our model constructs the
-trace one drawing command at a time.  When predicting the next drawing
-command, the network takes as input the target image $I$ as well as
-the rendered output of previous drawing commands.  Intuitively, the
-network looks at the image it wants to explain, as well as what it has
-already drawn.  It then decides either to stop drawing or proposes
-another drawing command to add to the trace set; if it decides
-to continue drawing, the predicted primitive is rendered to its
-``canvas'' and the process repeats.
-
+The network constructs the
+trace set one drawing command at a time, conditioned on what it has drawn so far.
+%When predicting the next drawing
+%command, the network takes as input the target image $I$ as well as
+%the rendered output of previous drawing commands.
+%Intuitively, the network looks at the image it wants to explain, as well as what it has already drawn.
+It then decides either to stop drawing or proposes another drawing command to add to the trace set; if it decides to continue drawing, the predicted primitive is rendered to its ``canvas'' and the process repeats.
 Fig.~\ref{architecture} illustrates this architecture.  We first
-pass a $256\times 256$ target image and a rendering of the trace so
+pass a $256\times 256$ target image and a rendering of the trace set so
 far (encoded as a two-channel image) to a convolutional network. Given
@@
 trace set; see Tbl.~\ref{drawingCommandTable} for the drawing commands we currently model.  We predict the drawing
-command token-by-token,\footnote{Tokens are atomic symbols in the programming language  -- so the model is \emph{not} predicting lines of code character-by-character, but instead the model knows about the syntactic structure of primitive drawing commands} conditioning each token both on the image
+command token-by-token,%\footnote{Tokens are atomic symbols in the programming language  -- so the model is \emph{not} predicting lines of code character-by-character, but instead the model knows about the syntactic structure of primitive drawing commands}
+ conditioning each token both on the image
 features and on the previously generated tokens. We also use a
@@
   \node[draw,ultra thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 3cm] (CNN) at (4.5,-2.5) {CNN};
-  \node[inner sep = 0pt](tensorProduct) at ([xshift = -1.5cm]CNN.west) {$\bigoplus$};
+  \node[inner sep = 0pt](tensorProduct) at ([xshift = -1.5cm]CNN.west) {$\bigotimes$};
 
@@
   \end{tabular}&\begin{tabular}{l}
-    Finishes drawing command inference
+    Finishes trace set inference
     \end{tabular}
@@
 %% \end{equation}
-%% where $|T|$ is the length of trace $T$, the subscripts
+%% where $|T|$ is the length of trace set $T$, the subscripts
 %% on $T$ index drawing commands within the trace (so $T_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
-%% token is emitted by the network to signal that the trace
+%% token is emitted by the network to signal that the trace set
 %% explains the image.
-
 We train the network by sampling trace sets $T$ and target
@@
   by gradient ascent.
-We trained the network on $10^5$ scenes, which takes a little less than a day on an Nvidia TitanX GPU.
-
-Training does not require backpropagation across the sequence
-of drawing commands: drawing to the canvas `blocks' the gradients,
-effectively offloading memory to an external visual store.  
-This approach is like an autoregressive version of
-Attend-Infer-Repeat~\citep{eslami1603attend}, but critically, without a learned
-  recurrent memory state, e.g. an RNN.  We can do without an RNN
-because we learn from ground truth (image, trace) pairs.  This
-allows us to handle scenes with many objects without
-worrying about the conditioning of gradients as they propagate
-over long sequences, and makes training more straightforward: it
-is just maximum likelihood estimation of the model parameters.
+We trained the network on $10^5$ scenes, which takes a day on an Nvidia TitanX GPU.
+
+%% Training does not require backpropagation across the sequence
+%% of drawing commands: drawing to the canvas `blocks' the gradients,
+%% effectively offloading memory to an external visual store.  
+%% This approach is like an autoregressive version of
+%% Attend-Infer-Repeat~\citep{eslami1603attend}, but critically, without a learned
+%%   recurrent memory state, e.g. an RNN.  We can do without an RNN
+%% because we learn from ground truth (image, trace) pairs.  This
+%% allows us to handle scenes with many objects without
+%% worrying about the conditioning of gradients as they propagate
+%% over long sequences, and makes training more straightforward: it
+%% is just maximum likelihood estimation of the model parameters.
 
@@
 the SMC sampler, we use pixel-wise distance as a surrogate
-\clearpage\begin{wrapfigure}{R}{8cm}
-  \centering
-      \includegraphics[width = 7cm]{figures/editDistance36.png}
-%    \includegraphics[width = 4cm]{figures/accuracy.png}
-      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
-It generalizes to scenes with many more objects.
-Neither the stochastic search nor the neural network are sufficient on their own.
-\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}
-\end{wrapfigure}
-\noindent
 for a
@@
 
+\begin{wrapfigure}{R}{8cm}
+  \centering
+      \includegraphics[width = 7cm]{figures/editDistance36.png}
+%    \includegraphics[width = 4cm]{figures/accuracy.png}
+      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
+It generalizes to scenes with many more objects.
+Neither the stochastic search nor the neural network are sufficient on their own.
+\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}%\vspace{-1cm}
+\end{wrapfigure}
+
 Fig.~\ref{syntheticResults}
@@
 using a CNN to extract features of the input which are passed to an LSTM which finally predicts
-the trace token-by-token.
+the trace set token-by-token.
 This architecture is used in several successful neural models of image captioning (e.g.,~\cite{vinyals2015show}),
@@
 So, for hand drawings,
-we \emph{learn} a surrogate likelihood function,
+we learn a surrogate likelihood function,
 $L_{\text{learned}}(\cdot|\cdot)$.
@@
 
-Pixel-wise
-distance
-metrics are sensitive to the details of how
-arrows, dashes, and corners are drawn -- but we wish to be invariant
-to these details.
-So, we learn a distance metric over images that
-approximates the distance metric in the search space over traces.
+%% Pixel-wise distance metrics are sensitive to the details of how
+%% arrows, dashes, and corners are drawn -- but we wish to be invariant
+%% to these details.
+%% So, we learn a distance metric over images that
+%% approximates the distance metric in the search space over traces.
 
@@
 For each drawing we annotated a ground truth trace set and have the neurally guided SMC sampler
-produce many candidate traces for each drawing.
+produce many candidate interpretations for each drawing.
 For 63\% of the drawings, the Top-1 most likely sample exactly matches the
-ground truth; with more samples, the model finds traces
+ground truth; with more samples, the model finds trace sets
 that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
@@
   \begin{minipage}[c]{0.57\textwidth} 
-    \centering  \includegraphics[width = 8cm]{figures/drawingAccuracy.png}
+    \centering  \includegraphics[width = 8cm]{figures/drawingAccuracy.png}            \vspace{-0.5cm}
   \end{minipage}\hfill%
@@
 ground truth.
-(a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 5 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth trace.
+(a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 5 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth.
 Red: the full model.
-Other colors: lesioned versions of our model.}\label{drawingIntersectionOverUnion}
+Other colors: lesioned versions of our model.}\label{drawingIntersectionOverUnion}            \vspace{-0.5cm}
       \end{minipage}
@@
 Python, a more tractable approach is to specify what in the program
-languages community is called a Domain Specific Language (DSL)~\cite{polozov2015flashmeta}. Our DSL (Tbl.~\ref{DSL})
+languages community is called a Domain Specific Language (DSL)~\citep{polozov2015flashmeta}. Our DSL (Tbl.~\ref{DSL})
 encodes prior knowledge of what graphics programs tend to look like.
@@
 program synthesis problems. We use the state-of-the-art Sketch
-tool~\cite{solar2008program}.
+tool~\citep{solar2008program}.
 %At a high level,
@@
 \begin{table}[t]
-  \caption{Example drawings (left), their ground truth trace sets (middle left), and programs synthesized from these traces (middle right).
-Compared to the trace the programs are more compressive (right: programs have fewer lines than traces) and automatically group together related drawing commands.
-Note the nested loops in the Ising model, special case conditionals for the HMM, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
+  \caption{Example drawings (left), their ground truth trace sets (middle left), and programs synthesized from these trace sets (middle right).
+Compared to the trace sets the programs are more compressive (right: programs have fewer lines than traces) and automatically group together related drawing commands.
+Note the nested loops  and special case conditionals in the Ising model, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
 %  \vspace{-0.6cm}
@@
      \end{minipage}&$\frac{6}{3} = 2\text{x}$\\\midrule
-     \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
-\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-Line(5,13,2,10,arrow)
-Circle(5,9)
-Circle(8,5)
-Line(2,8, 2,6,arrow)
-Circle(2,5)
-\end{lstlisting}
-\small\emph{... etc. ...; 13 lines}
-\end{minipage}&
-             \begin{minipage}{\exampleProgramSize}\begin{lstlisting}
-circle(4,10)
-for(i<3)
- circle(-3*i+7,5)
- circle(-3*i+7,1)
- line(-3*i+7,4,-3*i+7,2,arrow)
- line(4,9,-3*i+7,6,arrow)
-\end{lstlisting}
-\end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
+%%      \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
+%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
+%% Line(5,13,2,10,arrow)
+%% Circle(5,9)
+%% Circle(8,5)
+%% Line(2,8, 2,6,arrow)
+%% Circle(2,5)
+%% \end{lstlisting}
+%% \small\emph{... etc. ...; 13 lines}
+%% \end{minipage}&
+%%              \begin{minipage}{\exampleProgramSize}\begin{lstlisting}
+%% circle(4,10)
+%% for(i<3)
+%%  circle(-3*i+7,5)
+%%  circle(-3*i+7,1)
+%%  line(-3*i+7,4,-3*i+7,2,arrow)
+%%  line(4,9,-3*i+7,6,arrow)
+%% \end{lstlisting}
+%% \end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
     \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
@@
 \end{minipage}&$\frac{16}{3} = 5.3\text{x}$\\\midrule
-\includegraphics[width = \exampleDrawingSize]{figures/expert-75-extra-trim.png}&
-\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-Line(11,14,13,14,arrow)
-Circle(10,10)
-Line(10,13,10,11,arrow)
-Circle(6,10)
-\end{lstlisting}
-    \small\emph{... etc. ...; 15 lines}
-\end{minipage}&
-\begin{minipage}{\exampleProgramSize}
-    \begin{lstlisting}
-for(i<4)
- line(-4*i+13,4,-4*i+13,2,arrow)
- for(j<3)
-  if(j>0)
-   circle(-4*i+13,4*j+-3)
-  line(-4*j+10,5,-4*j+12,5,
-       arrow)
-\end{lstlisting}
-  \end{minipage}&$\frac{15}{6} = 2.5\text{x}$\\\midrule
+%% \includegraphics[width = \exampleDrawingSize]{figures/expert-75-extra-trim.png}&
+%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
+%% Line(11,14,13,14,arrow)
+%% Circle(10,10)
+%% Line(10,13,10,11,arrow)
+%% Circle(6,10)
+%% \end{lstlisting}
+%%     \small\emph{... etc. ...; 15 lines}
+%% \end{minipage}&
+%% \begin{minipage}{\exampleProgramSize}
+%%     \begin{lstlisting}
+%% for(i<4)
+%%  line(-4*i+13,4,-4*i+13,2,arrow)
+%%  for(j<3)
+%%   if(j>0)
+%%    circle(-4*i+13,4*j+-3)
+%%   line(-4*j+10,5,-4*j+12,5,
+%%        arrow)
+%% \end{lstlisting}
+%%   \end{minipage}&$\frac{15}{6} = 2.5\text{x}$\\\midrule
 
@@
 
-A search policy $\pi_\theta(\sigma  | T )$ takes as input a trace $T$ and predicts a distribution over synthesis problems, each of which is written $\sigma $ and corresponds to a set of possible programs to search over (so $\sigma \subset \text{DSL}$).
+A search policy $\pi_\theta(\sigma  | T )$ takes as input a trace set $T$ and predicts a distribution over synthesis problems, each of which is written $\sigma $ and corresponds to a set of possible programs to search over (so $\sigma \subset \text{DSL}$).
 Good policies will prefer tractable program spaces,
@@
 tractable synthesis problems involve searching over smaller spaces,
-but smaller spaces are less likely to contain a minimum cost program
-for explaining the trace.
+but smaller spaces are less likely to contain good programs.
+%a minimum cost program
+%for explaining $T$.
 Our goal now is to find the parameters of the policy, written $\theta$, which best navigate this trade-off.
@@
 This means that the search algorithm explores the entire program space, but spends most of its time searching through the regions of the space that  the policy judges to be most promising.
+
+%% \begin{figure}\centering
+%%   \begin{tikzpicture}
+%%     \node[anchor = west] at (0,5.25) {Entire program search space};
+%%     \draw[fill = yellow,fill opacity = 0.15,draw = black] (0,0) rectangle (5,5);
+%%     \draw [fill = yellow, opacity = 0.2] (0,0)--(0,2)--(4,0)--(0,0);
+%%     \draw [fill = yellow, opacity = 0.4,cycle] (0,5)--(0,1)--(3,5);
+%%     \draw [fill = yellow, opacity = 0.6,cycle] (2.5,5)--(3.2,0)--(5,0)--(5,5);
+%%     \draw (0,2) -- node[below,sloped]{short programs} (4,0);
+%%     \draw (0,2) -- node[above,sloped]{long programs} (4,0);
+%%     \draw (2.5,5) -- node[above,sloped]{programs w/ reflections} (3.2,0);
+%%     \draw (0,1) -- node[above,sloped]{ programs w/ loops} (3,5);
+%%     \node(p1)[anchor =west ] at (5.5,3.5) {$\pi_\theta(\text{short, no loop/reflect}) = $};
+%%     \draw [fill = yellow, fill opacity = 0.2,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p1.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p1.east);
+%%     \node(p2)[anchor =west ] at ([yshift = -0.5cm]p1.west) {$\pi_\theta(\text{long, loops}) = $};
+%%     \draw [fill = yellow, fill opacity = 0.4,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p2.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p2.east);
+%%     \node(p3)[anchor =west ] at ([yshift = -0.5cm]p2.west) {$\pi_\theta(\text{long, no loop/reflect}) = $};
+%%     \draw [fill = yellow, fill opacity = 0.15,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p3.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p3.east);
+%%     \node(p4)[anchor =west ] at ([yshift = -0.5cm]p3.west) {$\pi_\theta(\text{long, reflects}) = $};
+%%     \draw [fill = yellow, fill opacity = 0.6,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p4.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p4.east);
+%%     \node(p5)[anchor =west ] at ([yshift = -0.5cm]p4.west) {\emph{etc.}};
+%%   \end{tikzpicture}
+%%   \caption{The bias-optimal search algorithm divides the entire (intractable) program search space in to (tractable) program subspaces (written $\sigma $), each of which contains a restricted set of programs.
+For example, one subspace might be short programs which don't loop.
+The policy $\pi$ predicts a distribution over program subspaces.
+The weight that $\pi$ assigns to a subspace is indicated by it's yellow shading in the above figure.}
+%%   \end{figure}
 
@@
 To generate a training corpus for learning a policy which minimizes this loss,
-we synthesized minimum cost programs for each trace of our hand drawings
+we synthesized minimum cost programs for each trace set of our hand drawings
 and for each $\sigma $.
@@
 the parameter settings of $\sigma $ (see Tbl.~\ref{policyOutput})
-and $\phi_{\text{trace}}(T)$ extracts a few simple features of the trace $T$;
+and $\phi_{\text{trace}}(T)$ extracts a few simple features of the trace set $T$;
 see supplement for details.
@@
 
-\pagebreak\section{Applications of graphics program synthesis}\label{applicationsSection}
+\section{Applications of graphics program synthesis}\label{applicationsSection}
 Why synthesize a graphics program,
-if the trace already suffices to recover the objects in an image?
+if the trace set already suffices to recover the objects in an image?
 Within our domain of hand-drawn figures, graphics program synthesis has several uses:
-%\remark{I'm of two minds about how these subsections should be ordered.
-The current ordering leads with the coolest results, which is nice.
-But it's a bit...deflating?...to start with such cool results and then end on the somewhat technical point of how the synthesizer can help correct parse errors.
-An alternative would be to flip the ordering, starting with the technical point and building toward progressively cooler results.
-This requires a bit more patience on the part of the reader, but the overall narrative flow/payoff feels better.
-In any case, whatever ordering you pick should be the same order as these applications are mentioned in the abstract.}
 
@@
 we run the program synthesizer on the
-Top-$k$  most likely traces output by the neurally guided sampler.
+Top-$k$  most likely trace sets output by the neurally guided sampler.
 Then, the system
@@
 mistakes made by the neural network when
-a correct trace is in the Top-$k$.
+a correct trace set is in the Top-$k$.
 Our sampler could only do better on
-7/100 drawings by looking at the Top-5 or Top-100 sampled traces
+7/100 drawings by looking at the Top-5 or Top-100 samples
 (see Fig.~\ref{drawingIntersectionOverUnion}),
@@
 Fig.~\ref{similarityMatrix} illustrates the kinds of drawings that these different metrics put closely together,
-while the supplement shows low dimensional projections of
+while Sec.~2 of the supplement shows low dimensional projections of
 program and image features.
@@
 \begin{figure}[t]
-  \begin{tabular}{c|c|c|}
-    \multicolumn{1}{c}{}    &\multicolumn{1}{c}{\textbf{Close in program space}}&\multicolumn{1}{c}{\textbf{Far apart in program space}}\\\cline{2-3}
-    \multicolumn{1}{c|}{}&&\\
-    \multicolumn{1}{c|}{    \begin{tabular}{l}\textbf{Close in }\\ \textbf{image space} \end{tabular}}    &
+  \begin{tabular}{|c|c|}
+    \multicolumn{1}{c}{\textbf{Close in program space, far in image space}}&
+    \multicolumn{1}{c}{\textbf{Close in image space, far in program space}}\\\hline&\\
+
     \begin{tabular}{l}
-      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-20-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-21-trim.png}\end{minipage}\\\\
-      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-50-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-2-trim.png}\end{minipage}
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-16-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-17-trim.png}\end{minipage}
     \end{tabular} &
+
     \begin{tabular}{l}
@@
       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-64-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-97-trim.png}\end{minipage}
-    \end{tabular}\\
-    \multicolumn{1}{c|}{}&&\\\cline{2-3}
-    \multicolumn{1}{c|}{}&&\\
-    \multicolumn{1}{c|}{    \begin{tabular}{c}\textbf{Far apart in }\\ \textbf{image space} \end{tabular}}    &        \begin{tabular}{l}
-      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
-      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-16-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-17-trim.png}\end{minipage}
-    \end{tabular}&
-    \begin{tabular}{l}
-      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-75-extra-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-89-trim.png}\end{minipage}\\\\
-      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-3-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-39-trim.png}\end{minipage}
     \end{tabular}
-\\    \multicolumn{1}{c|}{}&&\\\cline{2-3}\cline{2-3}    
+\\&\\    \hline
+    %\\
+%    \multicolumn{1}{c|}{}&&\\\cline{2-3}
+%    \multicolumn{1}{c|}{}&&\\ \multicolumn{1}{c|}{}
+    %& %% \begin{tabular}{l}
+    %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
+    %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-16-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-17-trim.png}\end{minipage}
+    %% \end{tabular}
+    %&
+    %% \begin{tabular}{l}
+    %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-75-extra-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-89-trim.png}\end{minipage}\\\\
+    %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-3-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-39-trim.png}\end{minipage}
+    %% \end{tabular}
+%\\ \multicolumn{1}{c|}{}&&\\\cline{2-3}\cline{2-3}
   \end{tabular}
@@
 Features of the program capture abstract notions like symmetry and repetition.
-Distance metric over images is $L_{\text{learned}}(\cdot|\cdot)$ (see Section~\ref{generalizingTheHandDrawings}).
-The off-diagonal entries highlight the difference between these metrics: similarity of programs captures high-level features like repetition and symmetry, whereas similarity of images correspondends to similar drawing commands being in similar places.
-See Section 2 of the supplement for more examples.}\label{similarityMatrix}  \end{figure}
+Distance metric over images is $L_{\text{learned}}(\cdot|\cdot)$ (see Sec.~\ref{generalizingTheHandDrawings}).
+Similarity of programs captures high-level features like repetition and symmetry, whereas similarity of images corresponds to similar drawing commands being in similar places.
+See Sec.
+2 of the supplement for more examples.}\label{similarityMatrix}  \end{figure}
 
@@
   \includegraphics[width = \textwidth]{figures/extrapolationMatrix2.png}
-  \includegraphics[width = \textwidth]{figures/extrapolationMatrix3.png}  
+%  \includegraphics[width = \textwidth]{figures/extrapolationMatrix3.png}  
   \caption{Top, white: hand drawings. Bottom, black: extrapolations produced by
@@
 
-In the computer graphics literature, there have been other systems which convert sketches into procedural representations.
+%In the computer graphics literature, there have been other systems which convert sketches into procedural representations.
 One uses a convolutional network to match a sketch to the output of a parametric 3D modeling system~\citep{huang2017shape}.
@@
 
-\textbf{Hand-drawn sketches:} Prior work has also applied sketch-based program synthesis to authoring graphics programs.
+%\textbf{Hand-drawn sketches:} Prior work has also applied sketch-based program synthesis to authoring graphics programs.
 Sketch-n-Sketch is a bi-directional editing system in which direct manipulations to a program's output automatically propagate to the program source code~\citep{Hempel:2016:SSP:2984511.2984575}.
 We see this work as complementary to our own: programs produced by our method could be provided to a Sketch-n-Sketch-like system as a starting point for further editing.
-The CogSketch system~\citep{forbus2011cogsketch} also aims to have a
-high-level understanding of hand-drawn figures. Their primary goal is
-cognitive modeling (they apply their system to solving IQ-test
-style visual reasoning problems), whereas we are interested in
-building an automated AI application (e.g. in our system the user need
-not annotate which strokes correspond to which shapes; our neural
-network produces something equivalent to the annotations).
+
+%The CogSketch system~\citep{forbus2011cogsketch} also aims to have a high-level understanding of hand-drawn figures.
+Their primary goal is cognitive modeling (they apply their system to solving IQ-test style visual reasoning problems), whereas we are interested in building an automated AI application (e.g.
+in our system the user need not annotate which strokes correspond to which shapes; our neural network produces something equivalent to the annotations).
 %A key similarity however is that both CogSketch and our system have as a goal to make it easier to produce nice-looking figures.
@@
 that  trace sets can be inferred from perceptual data,
-and that the trace is the correct bridge between perception and symbolic representation.
+and that the trace set is a useful bridge between perception and symbolic representation.
 Our work is the first to articulate and explore this hypothesis

### 2017-12-05 makeArchive.sh

@@ -4,7 +4,8 @@ rm -r archive archive.tar
 mkdir archive
 mkdir archive/figures
 
-cp paper.tex main.bib paper.bbl nips_2017.sty /usr/share/texlive/texmf-dist/tex/latex/natbib/natbib.sty archive
+cp short.tex main.bib short.bbl iclr2018_conference.sty /usr/share/texlive/texmf-dist/tex/latex/natbib/natbib.sty archive
 
-cp `grep png paper.tex|sed 's/.*figures/figures/'|sed 's/}.*//'` archive/figures
+cp `grep png short.tex|sed 's/.*figures/figures/'|sed 's/}.*//'` archive/figures
+cp figures/expert-*-trim.png archive/figures
 tar cvf archive.tar archive/

### 2017-12-07 revision.tex
more shortening of the revision

@@
 \newtheorem{definition}{Definition}[section]
+\newtheorem{experiment}{Experiment} %[section]
 
@@
   graphics program in hand, we can correct errors made by the deep
-  network, measure similarity between drawings by use of similar high-level geometric
-  structures, and extrapolate drawings.  Taken together these results
+  network %, measure similarity between drawings by use of similar high-level geometric
+  %structures,
+  and extrapolate drawings.  Taken together these results
   are a step towards agents that induce useful, human-readable
@@
 
-The key observation behind our work is that generating a programmatic representation from an image of a diagram actually involves two distinct steps that require different technical approaches.
+The key observation behind our work is that generating a programmatic representation from an image of a diagram  involves two distinct steps that require different technical approaches.
 The first step involves identifying the components such as rectangles, lines and arrows that make up the image.
@@
 The program synthesizer searches the space of possible programs for one capable of producing the desired trace set -- inducing structures like
-symmetries, loops, or conditional branches.
+symmetries, loops, or conditionals.
 Although these program synthesizers do not need any training data,
@@
 
-Images are high-dimensional and unstructured while programs are high-level
-and symbolic. We resolve this mismatch by advancing a new model of
-collaboration between these two representations, which we call The Trace Hypothesis:
+One might be tempted to try to go directly from perceptual input (an image) to a program,
+much like recent neural models of program induction that regress from problem statements to programs (e.g.,~\cite{devlin2017robustfill}).
+We advocate an alternative model, which we call The Trace Hypothesis:
+
+%% Images are high-dimensional and unstructured while programs are high-level
+%% and symbolic. We resolve this mismatch by advancing a new model of
+%% collaboration between these two representations, which we call The Trace Hypothesis:
 
@@
 \begin{figure}[h]
-  \begin{tikzpicture}
+  \centering\begin{tikzpicture}
     \node[ thick,anchor = west,inner sep=0pt,label=below:{\small Perceptual input}](observation) at (0,0) {\includegraphics[width = 1.5cm]{figures/expert-39-trimmed.png}};
@@
     \end{lstlisting}};
-    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Extrapolation}](extrapolate) at (9.5,-0.4) {\includegraphics[width = 1.3cm]{figures/39-extrapolated.png}};
-    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Similarity}](similarity) at (11.3,0) {\includegraphics[width = 1cm]{figures/expert-38-trim.png}};
+    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Extrapolation}](extrapolate) at (9.9,-0.4) {\includegraphics[width = 1.3cm]{figures/39-extrapolated.png}};
+%    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Similarity}](similarity) at (11.3,0) {\includegraphics[width = 1cm]{figures/expert-38-trim.png}};
     \node[ultra thick,anchor = west,text width = 1.3cm,inner sep=0pt](errors) at (10,1) {\small Error correction};
@@
     \draw[->, thick] (program.east) to[out = 80,in = 180] (errors.west);
-    \draw[->, thick] (program.east) to[out = 40,in = -230] (similarity.west);
+%    \draw[->, thick] (program.east) to[out = 40,in = -230] (similarity.west);
         \draw[->, thick] (program.east) to[out = -90,in = 180] (extrapolate.west);
@@
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-([xshift = 150,yshift = -15]trace.south) -- node[below = 6pt] {{\small Section~\ref{applicationsSection}: Applications}} ([xshift = 250,yshift = -15]trace.south);
+([xshift = 150,yshift = -15]trace.south) -- node[below = 6pt] {{\small Section~\ref{applicationsSection}: Applications}} ([xshift = 230,yshift = -15]trace.south);
   \end{tikzpicture}
@@
 building on Levin search~\citep{levin1973universal}
-and generalizing recent work like DeepCoder~\citep{BalGauBroetal16}.
+and recent work like DeepCoder~\citep{BalGauBroetal16}.
 (3) The trace hypothesis: a framework for going from perception to programs,
@@
 trace set, $T$, from an image, $I$.
-Our model is a combination of  ideas from 
+Our model combines ideas from
 Neurally-Guided Procedural Models~\citep{ritchie2016neurally}
@@
 predicts a distribution over the next drawing command to add to the
-trace set; see Tbl.~\ref{drawingCommandTable} for the drawing commands we currently model.  We predict the drawing
-command token-by-token,%\footnote{Tokens are atomic symbols in the programming language  -- so the model is \emph{not} predicting lines of code character-by-character, but instead the model knows about the syntactic structure of primitive drawing commands}
- conditioning each token both on the image
-features and on the previously generated tokens. We also use a
+trace set; see Tbl.~\ref{drawingCommandTable} for the drawing commands we currently model.
+%We predict the drawing command token-by-token,
+%\footnote{Tokens are atomic symbols in the programming language  -- so the model is \emph{not} predicting lines of code character-by-character, but instead the model knows about the syntactic structure of primitive drawing commands}
+%%   conditioning each token both on the image
+%% features and on the previously generated tokens. 
+We also use a
 differentiable attention mechanism (Spatial Transformer
 Networks:~\cite{jaderberg2015spatial}) to let the model attend to
-different regions of the image while predicting each token. In Fig.~\ref{architecture} the network first decided to emit the \verb|circle| token
-conditioned on the image features, then it emitted the $x$ coordinate of
-the circle conditioned on the image features and the \verb|circle|
-token, and finally it predicted the $y$ coordinate of the circle
-conditioned on the image features, the \verb|circle| token, and the
-$x$ coordinate. We currently constrain
+different regions of the image while predicting drawing commands.
+%In Fig.~\ref{architecture} the network first decided to emit the \verb|circle| token
+%conditioned on the image features, then it emitted the $x$ coordinate of
+%the circle conditioned on the image features and the \verb|circle|
+%token, and finally it predicted the $y$ coordinate of the circle
+%conditioned on the image features, the \verb|circle| token, and the
+%$x$ coordinate.
+We currently constrain
 coordinates to lie on a discrete $16\times 16$ grid,
@@
 %those shown in Fig.~\ref{trainingData}.
-by doing a beam search decoding to
+by doing a beam search to
 recover  trace sets maximizing $\probability_\theta
-[T|I]$. But, if the network makes a mistake (predicts an incorrect
-drawing command), it has no way of recovering from the error.  
-To derender an image with $n$ objects, it must correctly predict $n$
-commands -- so its probability of success will decrease
-exponentially in $n$, assuming it has a nonzero chance of making a
-mistake.  For added robustness as $n$ becomes large, we treat the
-neural network outputs as proposals for a Sequential Monte Carlo (SMC) sampling scheme~\citep{SMCBook}.  For
-the SMC sampler, we use pixel-wise distance as a surrogate
-for a
-likelihood function. The SMC sampler is designed to produce samples
+[T|I]$. But, if the network predicts an incorrect
+drawing command, it has no way of recovering from that error.  
+%To derender an image with $n$ objects, it must correctly predict $n$ commands -- so its probability of success will decrease exponentially in $n$, assuming it has a nonzero chance of making a mistake.
+For added robustness % as $n$ becomes large,
+we treat the
+ network outputs as proposals for a Sequential Monte Carlo (SMC) sampling scheme~\citep{SMCBook}.
+%For the SMC sampler, we use pixel-wise distance as a surrogate for a likelihood function.
+The SMC sampler is designed to sample
 from the distribution $\propto L(I|\text{render}(T))
-\probability_\theta[T|I]$, where $L(\cdot | \cdot):\text{image}^2\to
-\mathbb{R}$ uses the distance between two images as a proxy for a
-likelihood. Unconventionally, the target distribution of the SMC sampler
-includes the likelihood under the proposal distribution.
-Intuitively, both the proposal
-distribution and the distance function offer complementary signals for
-whether a drawing command is correct.
-
+\probability_\theta[T|I]$, where $L(\cdot | \cdot)$
+%:\text{image}^2\to\mathbb{R}$
+uses the pixel-wise distance between two images as a proxy for a
+likelihood.
+Here, the network is learning a proposal distribution in an amortized way~\citep{paige2016inference}
+and using it to invert a generative model (the renderer).
+%% Unconventionally, the target distribution of the SMC sampler
+%% includes the likelihood under the proposal distribution.
+%% Intuitively, both the proposal
+%% distribution and the distance function offer complementary signals for
+%% whether a drawing command is correct.
 \begin{wrapfigure}{R}{8cm}
-  \centering
-      \includegraphics[width = 7cm]{figures/editDistance36.png}
+\vspace{-0.25cm}  \centering
+      \includegraphics[width = 7cm]{figures/averageNumberOfErrors.png}
 %    \includegraphics[width = 4cm]{figures/accuracy.png}
       \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
-It generalizes to scenes with many more objects.
-Neither the stochastic search nor the neural network are sufficient on their own.
-\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}%\vspace{-1cm}
+Model generalizes to scenes with many more objects.
+Neither SMC nor the neural network are sufficient on their own.
+\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}\vspace{-0.5cm}
 \end{wrapfigure}
 
-Fig.~\ref{syntheticResults}
-compares the neural network with SMC against the neural network by
-itself or SMC by itself.  Only the combination of the two passes a
+\textbf{Experiment 1.} 
+  To evaluate which components of the model are necessary to parse complicated scenes,
+  we compared  the neural network
+  with SMC against the neural network by
+itself or SMC by itself (Fig.~\ref{syntheticResults}).  Only the combination of the two passes a
 critical test of generalization: when trained on images with $\leq 12$
@@
 training data.
-We compare with a baseline that models the problem as image captioning (LSTM in Fig.~\ref{syntheticResults}).
-Given the target image, this baseline produces the trace set in one shot by
-using a CNN to extract features of the input which are passed to an LSTM which finally predicts
-the trace set token-by-token.
+We compare with a baseline that produces the trace set in one shot by
+using the CNN to extract features of the input which are passed to an LSTM which finally predicts
+the trace set token-by-token (LSTM in Fig.~\ref{syntheticResults}).
 This architecture is used in several successful neural models of image captioning (e.g.,~\cite{vinyals2015show}),
-but, for this domain, does not suffice to parse cluttered scenes with many objects.
+but, for this domain, cannot parse cluttered scenes with many objects.
 
@@
 
-\subsection{Generalizing to hand drawings}\label{generalizingTheHandDrawings}
+\subsection{Generalizing to real hand drawings}\label{generalizingTheHandDrawings}
 \begin{wrapfigure}{R}{6cm}
-\centering  \begin{minipage}[t]{2.5cm}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
+\centering\vspace{-0.7cm}  \begin{minipage}[t]{2.5cm}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
     \subcaption{}
@@
 
-A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
- We train the model
+%A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
+ We trained the model
 to generalize to hand drawings by introducing noise into the
@@
 
-We evaluate our system on 100 hand-drawn figures; see Fig.~\ref{drawingSuccesses}--\ref{drawingFailures}.
-These were drawn carefully but not perfectly.
-Because our model assumes that objects are snapped to a $16\times 16$ grid, 
-we made the drawings on graph paper.
-For each drawing we annotated a ground truth trace set and have the neurally guided SMC sampler
-produce many candidate interpretations for each drawing.
+  \textbf{Experiment 2.}
+    We evaluated, but did not train, our system on 100 real hand-drawn figures; see Fig.~\ref{drawingSuccesses}--\ref{drawingFailures}.
+These were drawn carefully but not perfectly with the aid of graph paper.
+%Because our model assumes that objects are snapped to a $16\times 16$ grid, 
+%we made the drawings on graph paper.
+For each drawing we annotated a ground truth trace set and had the neurally guided SMC sampler
+produce $10^3$ samples for each drawing.
 For 63\% of the drawings, the Top-1 most likely sample exactly matches the
@@
 corrects some of these small errors (Sec.~\ref{synthesizerHelpsParsing}).
-
 %% Because the model sometimes makes mistakes % on hand drawings,
@@
       \end{minipage}
-      \vspace{-1cm}
+
 \end{figure}
@@
 
-We constrain the space of allowed programs by writing down a context
-free grammar over a space of programs. Although it might be desirable
-to synthesize programs in a Turing-complete language such as Lisp or
-Python, a more tractable approach is to specify what in the program
+We constrain the space of programs by writing down a context
+free grammar over  programs -- 
+%Although it might be desirable to synthesize programs in a Turing-complete language such as Lisp or Python, a more tractable approach is to specify
+what in the program
 languages community is called a Domain Specific Language (DSL)~\citep{polozov2015flashmeta}. Our DSL (Tbl.~\ref{DSL})
@@
   Expression$\to$&$\mathbb{Z}\times$Var\texttt{+}$\mathbb{Z}$\\
-  Var$\to$&A free (unused) variable\\
-  $\mathbb{Z}\to$&an integer\\
-  Axis$\to$&\texttt{X = }$\mathbb{Z}$ | \texttt{Y = }$\mathbb{Z}$\\\bottomrule
+%  Var$\to$&A free (unused) variable\\
+  Axis$\to$&\texttt{X = }$\mathbb{Z}$ | \texttt{Y = }$\mathbb{Z}$\\
+    $\mathbb{Z}\to$&an integer\\\bottomrule
   \end{tabular}
@@
 
-Given the DSL and a trace set $T$, we want to recover a program that both evaluates to $T$
+Given the DSL and a trace set $T$, we want a program that both evaluates to $T$
 and, at the same time, is the ``best'' explanation of $T$.
@@
 but has the guarantee that it 
-always eventually finds the globally optimal solution.
+always eventually finds a globally optimal solution.
 In exchange for this optimality guarantee
@@
 learning a domain-specific \emph{search policy}.
-A search policy proposes search problems
+A search policy poses search problems
 like those in Eq.~\ref{programObjective},
@@
 
-A search policy $\pi_\theta(\sigma  | T )$ takes as input a trace set $T$ and predicts a distribution over synthesis problems, each of which is written $\sigma $ and corresponds to a set of possible programs to search over (so $\sigma \subset \text{DSL}$).
+A search policy $\pi_\theta(\sigma  | T )$ takes as input a trace set $T$ and predicts a distribution over synthesis problems, each of which is written $\sigma $ and corresponds to a set of possible programs to search over (so $\sigma \subseteq \text{DSL}$).
 Good policies will prefer tractable program spaces,
@@
 An example of a $1$-bias optimal search algorithm is a time-sharing system that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
-We construct a $1$-bias optimal search algorithm for our domain by identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |T)$ and $t(\sigma )  $ with how long the synthesizer takes to search  the programs in $\sigma $.
-This means that the search algorithm explores the entire program space, but spends most of its time searching through the regions of the space that  the policy judges to be most promising.
+We construct a $1$-bias optimal search algorithm by identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |T)$ and $t(\sigma )  = t(\sigma|T)$, where $t(\sigma|T)$ is how long the synthesizer takes to search $\sigma $ for a program for $T$.
+This means that the search algorithm explores the entire program space, but spends most of its time in the regions of the space that  the policy judges to be most promising.
 
@@
 %%   \end{figure}
-
 Now in theory any $\pi_\theta(\cdot |\cdot ) $ is a bias-optimal searcher.
@@
 \end{align}
+Practically, bias optimality has now bought us the following: (1) a guarantee that the policy will always find the minimum cost program; and (2) a differentiable loss function for the policy parameters that takes into account the cost of searching, in contrast to e.g.
+DeepCoder~\citep{BalGauBroetal16}.
+
 To generate a training corpus for learning a policy which minimizes this loss,
@@
 
-We contrast our learned search policy
-with two alternatives (see Fig.~\ref{policyEvaluation}):
-(1) \emph{Sketch}, which poses the
+\textbf{Experiment 3.}
+We compare synthesis times for our learned search policy
+with two alternatives (Fig.~\ref{policyEvaluation}):
+ \emph{Sketch}, which poses the
 entire problem wholesale to the Sketch program synthesizer;
-and (2) an \emph{Oracle},
+and an \emph{Oracle},
 a policy which always picks the quickest to search $\sigma $
@@
 $\sigma $ will take to search.
-The Oracle is an upper bound on the performance of any search policy.
+%The Oracle is an upper bound on the performance of any search policy.
 With this learned policy in hand we can synthesize 58\% of programs within a minute.
+\end{experiment}
 \begin{table}[h]\centering
@@
 Sketch: out-of-the-box performance of the Sketch~\citep{solar2008program} program synthesizer.
-Oracle: baseline that picks the easiest synthesis problem containing a minimum cost program.
+Oracle:  upper bounds  the performance of any search policy.
 Learned policy: a bias-optimal learned search policy running on an ideal timesharing machine.
-Oracle  upper bounds  the performance of any search policy.
 $\infty = $ timeout.
@@
 
-\subsection{Modeling similarity between drawings}
-Modeling drawings using programs opens up new ways to measure similarity between them.
-For example, we might say that two drawings are similar if they both contain loops of length 4,
-or if they share a reflectional symmetry,
-or if they are both organized according to a grid-like structure.
-
-We measure the similarity between two drawings by extracting features
-of the lowest-cost programs that describe them. Our features are counts of the number of times that different components in the
-DSL were used (Tbl.~\ref{DSL}).
-We  then find drawings which are either close together or far apart in program feature space.
-One could use many
-alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
-We used our learned distance metric between trace sets, $L_{\text{learned}}(\cdot|\cdot)$,
-to find drawings that are either close together or far apart according to the learned
-distance metric over images.
-Fig.~\ref{similarityMatrix} illustrates the kinds of drawings that these different metrics put closely together,
-while Sec.~2 of the supplement shows low dimensional projections of
-program and image features.
-
-\newcommand{\similaritySize}{1cm}
-\newcommand{\similarityArrowSize}{0.35cm}
-\begin{figure}[t]
-  \begin{tabular}{|c|c|}
-    \multicolumn{1}{c}{\textbf{Close in program space, far in image space}}&
-    \multicolumn{1}{c}{\textbf{Close in image space, far in program space}}\\\hline&\\
-
-    \begin{tabular}{l}
-      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
-      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-16-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-17-trim.png}\end{minipage}
-    \end{tabular} &
-
-    \begin{tabular}{l}
-      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-22-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-77-trim.png}\end{minipage}\\\\
-      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-64-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-97-trim.png}\end{minipage}
-    \end{tabular}
-\\&\\    \hline
-    %\\
-%    \multicolumn{1}{c|}{}&&\\\cline{2-3}
-%    \multicolumn{1}{c|}{}&&\\ \multicolumn{1}{c|}{}
-    %& %% \begin{tabular}{l}
+%% \subsection{Modeling similarity between drawings}
+%% Modeling drawings using programs opens up new ways to measure similarity between them.
+%% For example, we might say that two drawings are similar if they both contain loops of length 4,
+%% or if they share a reflectional symmetry,
+%% or if they are both organized according to a grid-like structure.
+
+%% We measure the similarity between two drawings by extracting features
+%% of the lowest-cost programs that describe them. Our features are counts of the number of times that different components in the
+%% DSL were used (Tbl.~\ref{DSL}).
+%% We  then find drawings which are either close together or far apart in program feature space.
+%% One could use many
+%% alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
+%% We used our learned distance metric between trace sets, $L_{\text{learned}}(\cdot|\cdot)$,
+%% to find drawings that are either close together or far apart according to the learned
+%% distance metric over images.
+%% Fig.~\ref{similarityMatrix} illustrates the kinds of drawings that these different metrics put closely together,
+%% while Sec.~2 of the supplement shows low dimensional projections of
+%% program and image features.
+
+%% \newcommand{\similaritySize}{1cm}
+%% \newcommand{\similarityArrowSize}{0.35cm}
+%% \begin{figure}[t]
+%%   \begin{tabular}{|c|c|}
+%%     \multicolumn{1}{c}{\textbf{Close in program space, far in image space}}&
+%%     \multicolumn{1}{c}{\textbf{Close in image space, far in program space}}\\\hline&\\
+
+%%     \begin{tabular}{l}
 %%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
 %%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-16-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-17-trim.png}\end{minipage}
+%%     \end{tabular} &
+
+%%     \begin{tabular}{l}
+%%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-22-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-77-trim.png}\end{minipage}\\\\
+%%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-64-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-97-trim.png}\end{minipage}
 %%     \end{tabular}
-    %&
-    %% \begin{tabular}{l}
-    %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-75-extra-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-89-trim.png}\end{minipage}\\\\
-    %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-3-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-39-trim.png}\end{minipage}
+%% \\&\\    \hline
+%%     %\\
+%% %    \multicolumn{1}{c|}{}&&\\\cline{2-3}
+%% %    \multicolumn{1}{c|}{}&&\\ \multicolumn{1}{c|}{}
+%%     %& %% \begin{tabular}{l}
+%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
+%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-16-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-17-trim.png}\end{minipage}
+%%     %% \end{tabular}
+%%     %&
+%%     %% \begin{tabular}{l}
+%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-75-extra-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-89-trim.png}\end{minipage}\\\\
+%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-3-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-39-trim.png}\end{minipage}
+%%     %% \end{tabular}
+%% %\\ \multicolumn{1}{c|}{}&&\\\cline{2-3}\cline{2-3}
 %%   \end{tabular}
-%\\ \multicolumn{1}{c|}{}&&\\\cline{2-3}\cline{2-3}
-  \end{tabular}
-
-  \centering
-\caption{Pairs of images either close together or far apart in different features spaces.
+
+%%   \centering
+%% \caption{Pairs of images either close together or far apart in different features spaces.
 The symbol $\leftrightarrow$ points to the compared images.
@@
 Fig.~\ref{extrapolationFigure} shows extrapolations produced by our system.
-\begin{figure}[H]
+\begin{figure}[H]\centering
   \includegraphics[width = \textwidth]{figures/extrapolationMatrix1.png}
@@
 
-%In the computer graphics literature, there have been other systems which convert sketches into procedural representations.
+In the computer graphics literature, there have been other systems which convert sketches into procedural representations.
 One uses a convolutional network to match a sketch to the output of a parametric 3D modeling system~\citep{huang2017shape}.
@@
 
-%\textbf{Hand-drawn sketches:} Prior work has also applied sketch-based program synthesis to authoring graphics programs.
+\textbf{Hand-drawn sketches:} Prior work has also applied sketch-based program synthesis to authoring graphics programs.
 Sketch-n-Sketch is a bi-directional editing system in which direct manipulations to a program's output automatically propagate to the program source code~\citep{Hempel:2016:SSP:2984511.2984575}.
@@
 
-%The CogSketch system~\citep{forbus2011cogsketch} also aims to have a high-level understanding of hand-drawn figures.
+The CogSketch system~\citep{forbus2011cogsketch} also aims to have a high-level understanding of hand-drawn figures.
 Their primary goal is cognitive modeling (they apply their system to solving IQ-test style visual reasoning problems), whereas we are interested in building an automated AI application (e.g.
 in our system the user need not annotate which strokes correspond to which shapes; our neural network produces something equivalent to the annotations).
-%A key similarity however is that both CogSketch and our system have as a goal to make it easier to produce nice-looking figures.
-%Unsupervised Program Synthesis~\cite{ellis2015unsupervised} is a related framework which was also applied to geometric reasoning problems.
+A key similarity however is that both CogSketch and our system have as a goal to make it easier to produce nice-looking figures.
+%% Unsupervised Program Synthesis~\cite{ellis2015unsupervised} is a related framework which was also applied to geometric reasoning problems.
 The goals of~\cite{ellis2015unsupervised} were cognitive modeling,
-%and they applied their technique to synthetic scenes used in human behavioral studies.
+%% and they applied their technique to synthetic scenes used in human behavioral studies.
 %% open domain sketch understanding.
@@
 The system uses a combination of deep neural networks and stochastic search to parse drawings into symbolic trace sets; it then feeds these traces to a general-purpose program synthesis engine to infer a structured graphics program.
-We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings and to organize them according to high-level geometric features.
+We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings.
 

### 2017-12-07 revision.tex
9.25 pages

@@
 much like recent neural models of program induction that regress from problem statements to programs (e.g.,~\cite{devlin2017robustfill}).
-We advocate an alternative model, which we call The Trace Hypothesis:
+We advocate an alternative framing, which we call The Trace Hypothesis:
 
@@
 
-Intuitively, an $n$-bias optimal search algorithm spends at least $\probability_{\text{bias}}[\sigma ]/n$ of its time exploring solution space $\sigma $.
+%Intuitively, an $n$-bias optimal search algorithm spends at least $\probability_{\text{bias}}[\sigma ]/n$ of its time exploring solution space $\sigma $.
 An example of a $1$-bias optimal search algorithm is a time-sharing system that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
@@
 We locally minimize this loss using gradient descent. % while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}.
-See supplement for details.
-Because we want to learn a policy from only $100$ hand-drawn sketches,
+%See supplement for details.
+Because we want to learn a policy from only $100$ hand-drawn diagrams,
 we chose a simple low-capacity, bilinear model for a policy:
@@
 \begin{figure}[h]
-  \centering  \includegraphics[width = 14cm]{figures/policyComparison.png}
+  \centering  \includegraphics[width = 11cm]{figures/policyComparison.png}
   \caption{How long does it typically take to synthesize a minimum cost program?
@@
 
-\subsection{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
-\begin{wrapfigure}{r}{5.5cm}\vspace{-0.5cm}
+\pagebreak\subsection{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
+\begin{wrapfigure}{r}{5cm}\vspace{-0.5cm}
   \includegraphics[width = 5cm]{figures/programSuccess7.png}
@@
 Right: interpretations favored after learning a prior over programs.
-Our learned prior favors shorter, simpler programs, thus (top example) continuing the pattern of not having an arrow is preferred, or (bottom example) continuing the ``binary search tree'' is preferred.}\label{exampleOfProgramCorrectingMistake}
-\vspace{0.5cm}  \end{wrapfigure}
+The prior favors  simpler programs, thus (top) continuing the pattern of not having an arrow is preferred, or (bottom) continuing the ``binary search tree'' is preferred.}\label{exampleOfProgramCorrectingMistake}
+\vspace{-0.75cm}  \end{wrapfigure}
 The program synthesizer corrects errors made by the neural network by favoring trace sets which lead to more
-concise or general programs.  For example, figures with perfectly aligned objects are preferable to figures whose parts are slightly misaligned, and precise alignment lends itself to short
+concise or general programs.  For example, figures with perfectly aligned objects are preferable, %% to figures whose parts are slightly misaligned,
+and precise alignment lends itself to short
 programs.
@@
 see supplement for details.
-
-This procedure can only fix
-mistakes made by the neural network when
+But, this procedure can only correct errors when
 a correct trace set is in the Top-$k$.
 Our sampler could only do better on
-7/100 drawings by looking at the Top-5 or Top-100 samples
+7/100 drawings by looking at the Top-100 samples
 (see Fig.~\ref{drawingIntersectionOverUnion}),
@@
 learning this prior does sometimes 
-help correct mistakes made by the neural network, and also
-occasionally introduces mistakes of its own; see
+help correct mistakes made by the neural network; %% , and also
+%% occasionally introduces mistakes of its own; 
+see
 Fig.~\ref{exampleOfProgramCorrectingMistake} for a representative
@@
 \subsection{Extrapolating figures}
-Having access to the source code of a graphics program facilitates coherent, high-level edits to the figure generated by that program. 
-For example,
-we could change all of the circles to squares or make all of the lines be dashed.
-We extrapolate figures
+Having access to the source code of a graphics program facilitates coherent, high-level image editing.
+%For example,
+%we could change all of the circles to squares or make all of the lines be dashed.
+For example we can extrapolate figures
 by increasing the number of times that loops are executed.
 Extrapolating repetitive visuals patterns comes naturally to humans,
-and building this ability into an application is practical:
+and is a practical application:
 imagine hand drawing a repetitive graphical model structure
@@
 \begin{figure}[H]\centering
-  \includegraphics[width = \textwidth]{figures/extrapolationMatrix1.png}
-  \includegraphics[width = \textwidth]{figures/extrapolationMatrix2.png}
+  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix1.png}
+  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix2.png}
 %  \includegraphics[width = \textwidth]{figures/extrapolationMatrix3.png}  
-  \caption{Top, white: hand drawings. Bottom, black: extrapolations produced by
-running loops for extra iterations.}\label{extrapolationFigure}
+   \caption{Top, white: hand drawings. Bottom, black: extrapolations produced by our system.}
+  \label{extrapolationFigure}
   \end{figure}
@@
 in our system the user need not annotate which strokes correspond to which shapes; our neural network produces something equivalent to the annotations).
-A key similarity however is that both CogSketch and our system have as a goal to make it easier to produce nice-looking figures.
+%A key similarity however is that both CogSketch and our system have as a goal to make it easier to produce nice-looking figures.
 %% Unsupervised Program Synthesis~\cite{ellis2015unsupervised} is a related framework which was also applied to geometric reasoning problems.

### 2017-12-11 revision.tex
removed noisy rendering figure and included a paragraph about the challenges in the introduction

@@
 (3) The trace hypothesis: a framework for going from perception to programs,
-which connects this work to other models of program induction that use traces,
+which connects this work to other trace--based models,
 like the  Neural Program Interpreter~\citep{DBLP:journals/corr/ReedF15}.
+
+Even with the high-level idea of a trace set, going from hand drawings to programs remains difficult. We address the following challenges:
+(1) Inferring trace sets from noisy hand drawings requires design choices from the deep learning and computer vision toolkits (Section~\ref{neuralNetworkSection}); (2) Discovering good programs requires solving a difficult combinatorial search problem, because the programs are often long and complicated (e.g., 9 lines of code, with nested loops and conditionals).
+We give a generic framework for learning a \emph{search policy} that quickly guides program synthesizers toward the target programs.
 
@@
 \subsection{Generalizing to real hand drawings}\label{generalizingTheHandDrawings}
-\begin{wrapfigure}{R}{6cm}
-\centering\vspace{-0.7cm}  \begin{minipage}[t]{2.5cm}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
-    \subcaption{}
-  \end{minipage}\\
-   \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
-    \subcaption{}
-  \end{minipage}%
-  \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
-    \subcaption{}
-  \end{minipage}%
-    \caption{(a): hand drawing. (b): Rendering of the trace set our model infers for (a). (c): noisy rendering of (b).}\label{handDrawingExamples}
-\end{wrapfigure}
+%% \begin{wrapfigure}{R}{6cm}
+%% \centering\vspace{-0.7cm}  \begin{minipage}[t]{2.5cm}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
+%%     \subcaption{}
+%%   \end{minipage}\\
+%%    \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
+%%     \subcaption{}
+%%   \end{minipage}%
+%%   \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
+%%     \subcaption{}
+%%   \end{minipage}%
+%%     \caption{(a): hand drawing. (b): Rendering of the trace set our model infers for (a). (c): noisy rendering of (b).}\label{handDrawingExamples}
+%% \end{wrapfigure}
 
@@
 renderings of the training target images.
-We designed this noise process to introduce the kinds of variations found in hand drawings (Fig.~\ref{handDrawingExamples}; see supplement for details).
+We designed this noise process to introduce the kinds of variations found in hand drawings (%% Fig.~\ref{handDrawingExamples}; 
+see supplement for details).
 

### 2017-12-13 revision.tex
added new section to the introduction

@@
 The new contributions of this work are:
-(1) A model that converts sketches to high-level programs:
+(1) The trace hypothesis: a framework for going from perception to programs,
+which connects this work to other trace--based models,
+like the  Neural Program Interpreter~\citep{DBLP:journals/corr/ReedF15};
+(2) A model based on the trace hypothesis that converts sketches to high-level programs:
 in contrast to converting images to vectors or low-level parses~\citep{huang2017shape,Nishida:2016:ISU:2897824.2925951,nsd,DBLP:journals/corr/Beltramelli17,im2latex}.
-(2) An algorithm for learning a policy for efficiently searching for programs,
+(3) A generic algorithm for learning a policy for efficiently searching for programs,
 building on Levin search~\citep{levin1973universal}
 and recent work like DeepCoder~\citep{BalGauBroetal16}.
-(3) The trace hypothesis: a framework for going from perception to programs,
-which connects this work to other trace--based models,
-like the  Neural Program Interpreter~\citep{DBLP:journals/corr/ReedF15}.
-
-Even with the high-level idea of a trace set, going from hand drawings to programs remains difficult. We address the following challenges:
-(1) Inferring trace sets from noisy hand drawings requires design choices from the deep learning and computer vision toolkits (Section~\ref{neuralNetworkSection}); (2) Discovering good programs requires solving a difficult combinatorial search problem, because the programs are often long and complicated (e.g., 9 lines of code, with nested loops and conditionals).
-We give a generic framework for learning a \emph{search policy} that quickly guides program synthesizers toward the target programs.
+
+Even with the high-level idea of a trace set, going from hand drawings to programs remains difficult. We address  these challenges:
+(1) Inferring trace sets from images requires \emph{domain-specific} design choices from the deep learning and computer vision toolkits (Sec.~\ref{neuralNetworkSection}).
+(2) Generalizing to noisy hand drawings requires learning a \emph{domain-specific} noise model that is invariant to the variations across hand drawings (Sec.~\ref{generalizingTheHandDrawings}).
+(3) Discovering good programs requires solving a difficult combinatorial search problem, because the programs are often long and complicated (e.g., 9 lines of code, with nested loops and conditionals).
+We give a \emph{domain-general} framework for learning a search policy that quickly guides program synthesizers toward the target programs (Sec.~\ref{learningASearchPolicy}).
 
@@
 predicts a distribution over the next drawing command to add to the
-trace set; see Tbl.~\ref{drawingCommandTable} for the drawing commands we currently model.
+trace set (see Tbl.~\ref{drawingCommandTable}).
 %We predict the drawing command token-by-token,
@@
 coordinates to lie on a discrete $16\times 16$ grid,
-but the grid could be made arbitrarily fine.  See supplement for the full details
-of the architecture, which we implemented in
-Tensorflow~\citep{tensorflow2015-whitepaper}.
+but the grid could be made arbitrarily fine.  %% See supplement for the full details
+%% of the architecture, which we implemented in
+%% Tensorflow~\citep{tensorflow2015-whitepaper}.
 %% \remark{There are some more details that are important to provide
@@
 
+\begin{wrapfigure}{r}{8cm}
+  \vspace{-0.25cm}
+  \centering
+      \includegraphics[width = 7cm]{figures/averageNumberOfErrors.png}
+      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
+Model generalizes to scenes with many more objects.
+Neither SMC nor the neural network are sufficient on their own.
+\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}\vspace{-0.7cm}
+\end{wrapfigure}
 Our network can ``derender'' random synthetic images
@@
 %% whether a drawing command is correct.
-\begin{wrapfigure}{R}{8cm}
-\vspace{-0.25cm}  \centering
-      \includegraphics[width = 7cm]{figures/averageNumberOfErrors.png}
-%    \includegraphics[width = 4cm]{figures/accuracy.png}
-      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
-Model generalizes to scenes with many more objects.
-Neither SMC nor the neural network are sufficient on their own.
-\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}\vspace{-0.5cm}
-\end{wrapfigure}
-
-\textbf{Experiment 1.} 
+
+\textbf{Experiment 1: Figure~\ref{syntheticResults}.}
   To evaluate which components of the model are necessary to parse complicated scenes,
@@
   with SMC against the neural network by
-itself or SMC by itself (Fig.~\ref{syntheticResults}).  Only the combination of the two passes a
+itself or SMC by itself.  Only the combination of the two passes a
 critical test of generalization: when trained on images with $\leq 12$
@@
 
-\textbf{Experiment 3.}
+\textbf{Experiment 3: Figure~\ref{policyEvaluation}.}
 We compare synthesis times for our learned search policy
-with two alternatives (Fig.~\ref{policyEvaluation}):
+with two alternatives:
  \emph{Sketch}, which poses the

### 2018-04-25 nips_2018.tex
nips 2018

--- 2017-12-13 revision.tex
@@
 % if you need to pass options to natbib, use, e.g.:
-\PassOptionsToPackage{numbers, compress}{natbib}
-% before loading nips_2017
-%
+% \PassOptionsToPackage{numbers, compress}{natbib}
+% before loading nips_2018
+
+% ready for submission
+\usepackage{nips_2018}
+
+% to compile a preprint version, e.g., for submission to arXiv, add
+% add the [preprint] option:
+% \usepackage[preprint]{nips_2018}
+
+% to compile a camera-ready version, add the [final] option, e.g.:
+% \usepackage[final]{nips_2018}
+
 % to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{nips_2017}
-
-%\usepackage{nips_2017}
-\usepackage{dsfont}
-% to compile a camera-ready version, add the [final] option, e.g.:
-%\usepackage[final]{nips_2017}
-%ICLR packages:
-\usepackage{iclr2018_conference,times}
-%\iclrfinalcopy
+% \usepackage[nonatbib]{nips_2018}
 
@@
 \usepackage{microtype}      % microtypography
+\usepackage{dsfont}
+\usepackage{verbatimbox}
 \usepackage{listings}
@@
 \title{Learning to Infer Graphics Programs from Hand-Drawn Images}
-
-%\lhead{nothing}
 
@@
   learn a convolutional neural network that proposes plausible drawing
-  primitives that explain an image. These drawing primitives are
-  like a trace of the set of primitive commands issued by a graphics
-  program. We learn a model that uses program synthesis techniques to
-  recover a graphics program from that trace. These programs have constructs like variable
-  bindings, iterative loops, or simple kinds of conditionals. With a
-  graphics program in hand, we can correct errors made by the deep
-  network %, measure similarity between drawings by use of similar high-level geometric
-  %structures,
-  and extrapolate drawings.  Taken together these results
-  are a step towards agents that induce useful, human-readable
-  programs from perceptual input.
+  primitives that explain an image. These drawing primitives are a
+  specification (spec) of what the graphics program needs to draw.
+  We learn a model that uses program synthesis techniques to
+  recover a graphics program from that spec. These programs have
+  constructs like variable bindings, iterative loops, or simple kinds
+  of conditionals. With a graphics program in hand, we can correct
+  errors made by the deep network and extrapolate drawings.  %% Taken
+  %% together these results are a step towards agents that induce useful,
+  %% human-readable programs from perceptual input.
 \end{abstract}
@@
 
- How can an agent convert noisy, high-dimensional perceptual input
- to a symbolic, abstract object, such as a computer program?  Here we
- consider this problem within a graphics program synthesis domain.  We
- develop an approach for converting  hand
- drawings into executable source code for drawing the original image.
- The graphics programs in our domain draw simple figures like those found in
- machine learning papers (see Fig.~\ref{firstPageExamples}a).
- \begin{figure}[H]\vspace{-0.7cm}
-  \begin{minipage}[t]{0.7\linewidth}  
-\begin{tabular}{llll}
-  \includegraphics[width = \exampleImageSize]{figures/expert-60.png}&
-  \includegraphics[width = \exampleImageSize]{figures/expert-5.png}&
-    \includegraphics[width = \exampleImageSize]{figures/expert-17.png}&
-    \includegraphics[width = \exampleImageSize]{figures/expert-58.png}\\
-  \includegraphics[width = \exampleImageSize]{figures/60.png}&
-  \includegraphics[width = \exampleImageSize]{figures/5.png}&
-    \includegraphics[width = \exampleImageSize]{figures/17.png}&
-    \includegraphics[width = \exampleImageSize]{figures/58.png}
-\end{tabular}
-\subcaption{}
-  \end{minipage}%
-  \begin{minipage}[t]{0.3\linewidth}
-    \begin{tikzpicture}
-      \node(picture) at (0,0) {\includegraphics[width = 2cm]{figures/expert-31.png}};
-      \draw[very thick,->] (picture.south)  -- (0,-2);
-    \end{tikzpicture}\\
-    \begin{minipage}[t]{0.3\linewidth}
-\begin{Verbatim}
+Human vision is rich -- we infer 3D shape, objects, parts of objects,
+and relations between objects -- but vision is also abstract:
+we can perceive the radial symmetry of a spiral staircase,
+the iterated repetition in the Ising model,
+see the forest for the trees, and also the recursion within the trees.
+How could we build an agent with similar visual inference abilities?
+Here we
+cast this problem as program learning,
+and take as our goal to learn high--level
+graphics programs from images.
+The graphics programs we consider draw simple figures like those found in machine learning papers
+(Fig.~\ref{firstPageExamples}),
+and capture high-level features of a drawing like
+symmetry, repetition, and reuse of structure.
+
+%% Vision as a kind of ``inverse graphics'' is an idea that is both intuitive and old,
+%% with many diverse recent takes on this framing -- neural network approaches like Attend--Infer--Repeat or Capsule Nets,
+%% or more structured approaches leveraging probabilistic programming~\cite{}.
+%% This vision--as--inverse--graphics metaphor addresses the important problem of
+%% inferring, from an image, the identities and poses of
+%% objects. But visual perception is richer than object identity and pose:
+
+ %% How can an agent convert noisy, high-dimensional perceptual input
+ %% to a symbolic, abstract object, such as a computer program?  Here we
+ %% consider this problem within a graphics program synthesis domain.  We
+ %% develop an approach for converting  hand
+ %% drawings into executable source code for drawing the original image.
+ %% The graphics programs in our domain draw simple figures like those found in
+ %% machine learning papers
+% (see Fig.~\ref{firstPageExamples}a)
+\begin{myverbbox}[\small]{\firstFirstPageCode}
 for (i < 3)
@@
   circle(3*i+1,-2*j+5)
-\end{Verbatim}      
-      \end{minipage}
+\end{myverbbox}
+\begin{myverbbox}[\small]{\secondFirstPageCode}
+reflect(y=8)
+ for(i<3)
+  if(i>0)
+   rectangle(3*i-1,2,3*i,3)
+  circle(3*i+1,3*i+1)
+\end{myverbbox}
+
+ \begin{figure}[H]%\vspace{-0.7cm}
+  \begin{minipage}[b]{0.35\linewidth}  \centering
+\begin{tabular}{ll}
+  \includegraphics[width = \exampleImageSize]{figures/expert-60.png}&
+%  \includegraphics[width = \exampleImageSize]{figures/expert-5.png}&
+%    \includegraphics[width = \exampleImageSize]{figures/expert-17.png}&
+    \includegraphics[width = \exampleImageSize]{figures/expert-58.png}\\
+  \includegraphics[width = \exampleImageSize]{figures/60.png}&
+%  \includegraphics[width = \exampleImageSize]{figures/5.png}&
+%    \includegraphics[width = \exampleImageSize]{figures/17.png}&
+    \includegraphics[width = \exampleImageSize]{figures/58.png}
+\end{tabular}
 \subcaption{}
   \end{minipage}
-  \caption{(a): Model learns to convert hand drawings (top) into \LaTeX~(rendered below). (b) Synthesizes high-level \emph{graphics program} from hand drawing.}\label{firstPageExamples}
+  %
+  \begin{minipage}[b]{0.6\linewidth}\centering
+    \begin{tikzpicture}
+      \node(picture1) at (0,-1) {\includegraphics[height = 1.5cm]{figures/expert-31.png}};
+      \node(picture2) [below = 0.3cm of picture1] {\includegraphics[height = 1.5cm]{figures/expert-72-trim.png}};
+      \node[right=1cm of picture1] (c1) {\fbox{\firstFirstPageCode}};
+      \node[right=1cm of picture2] (c2) {\fbox{\secondFirstPageCode}};
+      \draw[very thick,->] (picture1.east)  -- (c1.west);
+      \draw[very thick,->] (picture2.east)  -- (c2.west);
+    \end{tikzpicture}
+    \subcaption{}
+  \end{minipage}
+  \caption{(a): Model learns to convert hand drawings (top) into \LaTeX~(rendered below). (b) Learns to synthesize high-level graphics program from hand drawing.}\label{firstPageExamples}
 \end{figure}
 
-The key observation behind our work is that generating a programmatic representation from an image of a diagram  involves two distinct steps that require different technical approaches.
-The first step involves identifying the components such as rectangles, lines and arrows that make up the image.
-The second step involves identifying the high-level structure in how the components were drawn.
+ The key observation behind our work is that inferring the program from an image involves two distinct steps that require different technical approaches.
+The first step involves inferring what objects make up an image -- for diagrams, these are things like as rectangles, lines and arrows.
+The second step involves identifying the high-level structure in how the objects were drawn.
 In Fig.
@@
 
-We present a hybrid architecture for inferring graphics programs that is structured around these two steps.
-For the first step,   a deep network to infers a set of primitive shape-drawing commands.
-We refer to this set as a \emph{trace set} since it corresponds to the set of commands in a program's execution trace but lacks the high-level structure that determines how the program decided to issue them.
-%For added robustness, we train the network to produce a proposal distribution of the most likely traces and use stochastic search to find the trace that best matches the image.
-%The network is trained from an automatically-generated corpus of synthetic image-generating programs.
-The second step involves synthesizing a high-level program capable of producing the trace set identified by the first phase.
-%In principle, we could also train a neural network to learn this mapping.
-In practice, though, this would be challenging because it would no longer be sufficient to train the network with a synthetic corpus of randomly generated programs, since our goal is to generate programs that satisfy certain semantic constraints that ensure that we get the program that the user most likely intended.
-%This paper argues that this stage is best
-We achieve this by \emph{constraint-based program synthesis} \citep{solar2008program}.
-The program synthesizer searches the space of possible programs for one capable of producing the desired trace set -- inducing structures like
-symmetries, loops, or conditionals.
-Although these program synthesizers do not need any training data,
-we show how to learn a \emph{search policy} 
-in order to synthesize programs an order of magnitude faster than constraint-based synthesis techniques alone.
-
-One might be tempted to try to go directly from perceptual input (an image) to a program,
-much like recent neural models of program induction that regress from problem statements to programs (e.g.,~\cite{devlin2017robustfill}).
-We advocate an alternative framing, which we call The Trace Hypothesis:
-
-%% Images are high-dimensional and unstructured while programs are high-level
-%% and symbolic. We resolve this mismatch by advancing a new model of
-%% collaboration between these two representations, which we call The Trace Hypothesis:
-
-\noindent \textbf{The Trace Hypothesis.} The set of commands issued by a program,
-which we call a \emph{trace set},
-is the correct liaison between high-dimensional unstructured perceptual input and high-level structured symbolic representations.
-
-The roadmap of our paper is structured around the trace hypothesis, as outlined in Fig.~\ref{roadmap}.
+ Framed as probabilistic inference,
+ our two-step factoring cashes out as a generative model where a latent program
+ is executed to produce a set of drawing commands,
+ which are then rendered to form an image (Fig.~\ref{roadmap}).
+ We refer to this set of drawing commands as a \textbf{specification (spec)} because it specifies what the graphics program drew while lacking the high-level structure determining how the program decided to draw it.
+ We infer the spec from an image using stochastic search (Sequential Monte Carlo)
+ and infer a program from a spec using  \textbf{constraint-based program synthesis} \citep{solar2008program} --
+ synthesizing structures like symmetries, loops, or conditionals.
+ In practice, both stochastic search and program synthesis are
+ prohibitively slow,
+ and so we learn models that accelerate inference for both programs and specs,
+ in the spirit of ``amortized inference''~\cite{paige2016inference},
+ using a neural network to amortize the cost of inferring specs from images and using
+ a variant of Adaptive Levin Search~\cite{schmidhuber1997shifting}
+ to amortize the cost of synthesizing programs from specs.
  \begin{figure}[h]
   \centering\begin{tikzpicture}
-    \node[ thick,anchor = west,inner sep=0pt,label=below:{\small Perceptual input}](observation) at (0,0) {\includegraphics[width = 1.5cm]{figures/expert-39-trimmed.png}};
+    \node[ thick,anchor = west,inner sep=0pt,label={[yshift = 0.3cm]{\small Image}}](observation) at (0,0) {\includegraphics[width = 1.5cm]{figures/expert-39-trimmed.png}};
     \node[ultra thick,anchor = west,inner sep=0pt](traceSource) at (3,0.5){    \begin{lstlisting}[basicstyle = \scriptsize\ttfamily]
@@
       \includegraphics[width = 0.9cm]{figures/39-parse.png}}; 
-    \node(trace)[draw,thin,fit = (traceImage) (traceSource), label = below:{{\small Trace set}}] {};
-
-    \node[draw, thick,anchor = west,inner sep=2pt,label=below:{\small Program}](program) at (6.3,0) {
+    \node(trace)[draw,thin,fit = (traceImage) (traceSource), label = above:{{\small Spec}}] {};
+
+    \node[draw, thick,anchor = west,inner sep=2pt,label=above:{\small Program}](program) at (6.3,0) {
       \begin{lstlisting}
@@
     \end{lstlisting}};
-    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Extrapolation}](extrapolate) at (9.9,-0.4) {\includegraphics[width = 1.3cm]{figures/39-extrapolated.png}};
+    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Extrapolation}](extrapolate) at (9.9,0.5) {\includegraphics[width = 1.3cm]{figures/39-extrapolated.png}};
 %    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Similarity}](similarity) at (11.3,0) {\includegraphics[width = 1cm]{figures/expert-38-trim.png}};
-    \node[ultra thick,anchor = west,text width = 1.3cm,inner sep=0pt](errors) at (10,1) {\small Error correction};
-
-    \draw[->, thick] (observation.east) -- node[draw,fill = white,rotate = -90] {{\small Neural network}} (trace.west);
-    \draw[->, thick] (trace.east) -- node[draw,fill = white,rotate = -90] {{\small Program synthesis}} (program.west);
-    \draw[->, thick] (program.east) to[out = 80,in = 180] (errors.west);
+    \node[ultra thick,anchor = west,text width = 1.3cm,inner sep=0pt](errors) at (10,-1.2) {\small Error correction};
+
+    \draw[->, ultra thick] (trace.west) -- node[fill = white,rotate = -90] {{\small Rendering}} (observation.east);
+    \draw[->, thick, red] ([xshift = -5]observation.south) to[out = -30,in = -150] node[midway,yshift = -6]{{\small Learning + Stochastic search}} ([xshift = -15]trace.south);
+    \draw[->, ultra thick] (program.west) -- node[fill = white,rotate = -90] {{\small Execution}} (trace.east);
+    \draw[->, thick, red] ([xshift = 10]trace.south) to[out = -10,in = -170] node[midway,yshift = -6]{{\small Learning + Program synthesis}} ([xshift = 10]program.south);
+%    \draw[->, thick, red] (program.east) to[out = 80,in = 180] (errors.west);
 %    \draw[->, thick] (program.east) to[out = 40,in = -230] (similarity.west);
-        \draw[->, thick] (program.east) to[out = -90,in = 180] (extrapolate.west);
+    \draw[->, thick, red] (program.east) to[out = 60,in = 180] (extrapolate.west);
 
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-    ([yshift = -15,xshift = -115]trace.south) -- node[below = 6pt] {{\small Section~\ref{neuralNetworkSection}: Perception$\to$Trace set}} ([yshift = -15,xshift = -5]trace.south);
+    ([yshift = -15,xshift = -115]trace.south) -- node[below = 6pt] {{\small Section~\ref{neuralNetworkSection}: Image$\to$Spec}} ([yshift = -15,xshift = -5]trace.south);
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-    ([xshift = 5,yshift = -15]trace.south) -- node[below = 6pt] {{\small Section~\ref{programSynthesisSection}: Trace Set$\to$Program}} ([xshift = 140,yshift = -15]trace.south);
+    ([xshift = 5,yshift = -15]trace.south) -- node[below = 6pt] {{\small Section~\ref{programSynthesisSection}: Spec$\to$Program}} ([xshift = 140,yshift = -15]trace.south);
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
@@
   \end{tikzpicture}
-  \caption{Both the paper and the system pipeline are structured around the \emph{trace hypothesis}}\label{roadmap}
+  \caption{Black arrows: Top--down generative model; Program$\to$Spec$\to$Image. Red arrows: Bottom--up inference procedure.}\label{roadmap}
 \end{figure}
 
-The new contributions of this work are:
-(1) The trace hypothesis: a framework for going from perception to programs,
-which connects this work to other trace--based models,
-like the  Neural Program Interpreter~\citep{DBLP:journals/corr/ReedF15};
-(2) A model based on the trace hypothesis that converts sketches to high-level programs:
-in contrast to converting images to vectors or low-level parses~\citep{huang2017shape,Nishida:2016:ISU:2897824.2925951,nsd,DBLP:journals/corr/Beltramelli17,im2latex}.
-(3) A generic algorithm for learning a policy for efficiently searching for programs,
-building on Levin search~\citep{levin1973universal}
-and recent work like DeepCoder~\citep{BalGauBroetal16}.
-
-Even with the high-level idea of a trace set, going from hand drawings to programs remains difficult. We address  these challenges:
-(1) Inferring trace sets from images requires \emph{domain-specific} design choices from the deep learning and computer vision toolkits (Sec.~\ref{neuralNetworkSection}).
-(2) Generalizing to noisy hand drawings requires learning a \emph{domain-specific} noise model that is invariant to the variations across hand drawings (Sec.~\ref{generalizingTheHandDrawings}).
-(3) Discovering good programs requires solving a difficult combinatorial search problem, because the programs are often long and complicated (e.g., 9 lines of code, with nested loops and conditionals).
-We give a \emph{domain-general} framework for learning a search policy that quickly guides program synthesizers toward the target programs (Sec.~\ref{learningASearchPolicy}).
-
-%under a quantitative objective that maximizes the likelihood according to a prior distribution that aims to capture the user’s preference.
-
-%% The key observation behind our work is that generating a programmatic representation from an image of a diagram actually involves two distinct steps that require different technical approaches.
-The first step involves identifying the components such as boxes, lines and arrows that make up the image.
-The second step involves identifying the high-level structure in how the components were drawn; for example, in Fig.
-1(b), it means identifying that there is a pattern in how the circles and rectangles are being drawn that is best described with two nested loops, and which can easily be extrapolated to a bigger diagram.
-
-%% We present a hybrid architecture for inferring graphics programs that is structured around these two steps.
-For the first step, our approach uses a deep neural network to infer a sequence of primitive shape-drawing commands that can generate an image similar to the observed image.
-We refer to this sequence as an \emph{execution trace}, since it corresponds to the sequence of primitive commands that the desired program would have issued, but it lacks the high-level structure that determines how the program decided to issue those commands.
-For added robustness, we train the network to produce a proposal distribution of the most likely traces, and use stochastic search to find the trace that best matches the input.
-The network is trained from an automatically generated corpus of synthetic image generating programs.
-
-%% High dimensional perceptual input may seem ill matched to the abstract
-%% semantics of a programming language. But programs with constructs such as
-%% recursion or iteration produce a simpler \emph{execution trace} of
-%% primitive actions; for our domain, the primitive actions are drawing
-%% commands. Our hypothesis is that the execution trace of the program is
-%% better aligned with the perceptual input, and that the trace can act
-%% as a kind of bridge between perception and programs. We test this
-%% hypothesis by developing a model that learns to map from an image to
-%% the execution trace of the graphics program that drew it.  With the
-%% execution trace in hand, we can bring to bear techniques from the
-%% program synthesis community to recover the latent graphics program.
-%% This family of techniques, called \emph{constraint-based program synthesis}~\cite{solar2008program},
-%% work by modeling a set of possible programs inside of a constraint solver,
-%% such as a SAT or SMT solver~\cite{de2008z3}.
-%% These techniques excel at uncovering high-level symbolic structure,
-%% but are not well equipped to deal with real-valued perceptual inputs.
-
-%% We develop a hybrid architecture for inferring graphics programs.  Our
-%% approach uses a deep neural network infer an execution trace from an
-%% image; this network recovers primitive drawing operations such as
-%% lines, circles, or arrows, along with their parameters. For added
-%% robustness, we use the deep network as a proposal distribution for a
-%% stochastic search over execution traces.
-Section~\ref{neuralNetworkSection} describes this first stage of the architecture where we infer drawing commands from images, and explains how we handle noisy hand drawings.
-%% Finally, we use program synthesis techniques to recover the program from its
-%% trace.  The program synthesizer discovers constructs such as loops and
-%% geometric operations such as reflections and affine transformations.
-%% % \remark{This paragraph is all about making things a bit more
-%% Section~\ref{programSynthesisSection} describes how the architecture
-%% synthesizes programs from execution traces,
-%% and how those programs are used for  correcting errors made by the deep network, measuring similarity between hand drawings,
-%% and extrapolating figures.
-
-%   so you really need more specifics about program synth here.}
-
-%% Each of these three components -- the deep network, the stochastic
-%% search, the program synthesizer -- confers its own advantages. From
-%% the deep network, we get a fast system that can recover plausible
-%% execution traces in about a minute~\remark{A minute seems slow to me, for deep net inference...}. From the stochastic search, we get
-%% added robustness: essentially, the stochastic search can correct
-%% mistakes made by the deep network's proposals.  From the program
-%% synthesizer, we get abstraction: our system recovers coordinate
-%% transformations, for loops, and subroutines, which are useful for
-%% downstream tasks and can help correct some mistakes of the earlier stages.
-%% % \remark{I wonder if this would work even better as a bulleted list...}
-%% \remark{Tie these claims into the paper results: state what the `downstream' tasks are that you actually do, and refer to the sections where they occur}
-
-\section{Neural architecture for inferring trace sets}\label{neuralNetworkSection}
+\section{Neural architecture for inferring specs}\label{neuralNetworkSection}
 
 We developed a deep network architecture for efficiently inferring a
-trace set, $T$, from an image, $I$.
+spec, $S$, from a hand-drawn image, $I$.
 Our model combines ideas from
 Neurally-Guided Procedural Models~\citep{ritchie2016neurally}
-and Attend-Infer-Repeat~\citep{eslami1603attend}.
-The network constructs the
-trace set one drawing command at a time, conditioned on what it has drawn so far.
+and Attend-Infer-Repeat~\citep{eslami1603attend}, but
+we wish to emphasize
+that one could use
+many different approaches from the computer vision toolkit to
+parse an image into primitive drawing commands  (in our terminology, a ``spec'')~\cite{nsd}.
+Our network constructs the
+spec one drawing command at a time, conditioned on what it has drawn so far (Fig.~\ref{architecture}).
 %When predicting the next drawing
@@
 It then decides either to stop drawing or proposes another drawing command to add to the trace set; if it decides to continue drawing, the predicted primitive is rendered to its ``canvas'' and the process repeats.
-Fig.~\ref{architecture} illustrates this architecture.  We first
-pass a $256\times 256$ target image and a rendering of the trace set so
+We first
+pass a $256\times 256$ target image and a rendering of the drawing commands so
 far (encoded as a two-channel image) to a convolutional network. Given
 the features extracted by the convnet, a multilayer perceptron then
-predicts a distribution over the next drawing command to add to the
-trace set (see Tbl.~\ref{drawingCommandTable}).
+predicts a distribution over the next drawing command to execute
+(see Tbl.~\ref{drawingCommandTable}).
 %We predict the drawing command token-by-token,
@@
 \end{tikzpicture}
-\caption{Our neural architecture for inferring the trace set of a graphics program from its output.
+\caption{Our neural architecture for inferring the spec of a graphics program from its output.
 \textcolor{blue}{Blue}: network inputs.
@@
 %% explains the image.
-We train the network by sampling trace sets $T$ and target
+We trained our network by sampling specs $S$ and target
 images $I$ for randomly generated scenes
@@
 %Eq.~\ref{objective}
- the likelihood of $T$ given $I$ with respect to
- the model parameters, $\theta$,
-  by gradient ascent.
-We trained the network on $10^5$ scenes, which takes a day on an Nvidia TitanX GPU.
+ the likelihood of $S$ given $I$ with respect to
+ the model parameters, $\theta$, by gradient ascent.
+We trained on $10^5$ scenes, which takes a day on an Nvidia TitanX GPU.
 
@@
 by doing a beam search to
-recover  trace sets maximizing $\probability_\theta
-[T|I]$. But, if the network predicts an incorrect
+recover  specs maximizing $\probability_\theta[S|I]$. But, if the network predicts an incorrect
 drawing command, it has no way of recovering from that error.  
@@
 The SMC sampler is designed to sample
-from the distribution $\propto L(I|\text{render}(T))
-\probability_\theta[T|I]$, where $L(\cdot | \cdot)$
+from the distribution $\propto L(I|\text{render}(S))
+\probability_\theta[S|I]$, where $L(\cdot | \cdot)$
 %:\text{image}^2\to\mathbb{R}$
@@
 likelihood.
-Here, the network is learning a proposal distribution in an amortized way~\citep{paige2016inference}
-and using it to invert a generative model (the renderer).
+Here, the network is learning a proposal distribution to amortize the cost of inverting a generative model (the renderer)~\citep{paige2016inference}.
 %% Unconventionally, the target distribution of the SMC sampler
@@
 The density $L_{\text{learned}}(\cdot|\cdot)$ is predicted by a convolutional network that we train to predict
-the distance between two trace sets conditioned upon their renderings.
-We train our likelihood surrogate to approximate the symmetric difference,
-which is  the number of drawing commands by which two trace sets  differ:
+the distance between two specs conditioned upon their renderings.
+We $L_{\text{learned}}(\cdot |\cdot )$  to approximate the symmetric difference,
+which is  the number of drawing commands by which two specs  differ:
   \begin{equation}
-    -\log L_{\text{learned}}(\text{render}(T_1)|\text{render}(T_2))\approx |T_1 - T_2| + |T_2 - T_1|\label{symmetricDistance}
+    -\log L_{\text{learned}}(\text{render}(S_1)|\text{render}(S_2))\approx |S_1 - S_2| + |S_2 - S_1|\label{symmetricDistance}
     \end{equation}
@@
 
-  \textbf{Experiment 2.}
+  \textbf{Experiment 2: Figures~\ref{drawingSuccesses}--\ref{drawingIntersectionOverUnion}.}
     We evaluated, but did not train, our system on 100 real hand-drawn figures; see Fig.~\ref{drawingSuccesses}--\ref{drawingFailures}.
@@
 For each drawing we annotated a ground truth trace set and had the neurally guided SMC sampler
-produce $10^3$ samples for each drawing.
+produce $10^3$ samples. % for each drawing.
 For 63\% of the drawings, the Top-1 most likely sample exactly matches the
@@
   \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1, 5, 100)?
-    Distance to ground truth trace set measured by the intersection over union of predicted vs.
-ground truth.
+    Distance to ground truth measured by the intersection over union (IoU) of predicted vs.
+ground truth: IoU of sets $A$ and $B$ is $|A\cap B|/|A\cup B|$.
 (a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 5 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth.
@@
 
-\section{Synthesizing graphics programs from trace sets}\label{programSynthesisSection}
-Although the trace set of a graphics program describes the contents
-of a scene, it does not encode higher-level features of the image,
-such as repeated motifs or symmetries.  A \emph{graphics
-  program} better describes such structures.
-We seek to synthesize graphics programs from their trace sets.
+\section{Synthesizing graphics programs from specs}\label{programSynthesisSection}
+Although the spec describes the contents
+of a scene, it does not encode higher-level features of the image
+such as repeated motifs or symmetries, which are more naturally captured by a graphics program.
+We seek to synthesize graphics programs from their specs.
 
@@
 
-Given the DSL and a trace set $T$, we want a program that both evaluates to $T$
-and, at the same time, is the ``best'' explanation of $T$.
+Given the DSL and a spec $S$, we want a program that both satisfies $S$
+and, at the same time, is the ``best'' explanation of $S$.
 For example, we might prefer more general programs or, in the spirit of Occam's razor,
@@
 We wrap these intuitions up into a cost function over programs,
-and seek the minimum cost program consistent with $T$:
+and seek the minimum cost program consistent with $S$:
 \begin{equation}
-  \text{program}(T) = \argmin_{p\in \text{DSL, s.t. }p \text{ evaluates to } T} \text{cost}(p)\label{programObjective}
+  \text{program}(S) = \argmin_{p\in \text{DSL, s.t. }p \text{ consistent w/ } S} \text{cost}(p)\label{programObjective}
 \end{equation}
@@
 \begin{table}[t]
-  \caption{Example drawings (left), their ground truth trace sets (middle left), and programs synthesized from these trace sets (middle right).
-Compared to the trace sets the programs are more compressive (right: programs have fewer lines than traces) and automatically group together related drawing commands.
+  \caption{Example drawings (left), their ground truth specs (middle left), and programs synthesized from these specs (middle right).
+Compared to the specs the programs are more compressive (right: programs have fewer lines than specs) and automatically group together related drawing commands.
 Note the nested loops  and special case conditionals in the Ising model, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
@@
     \toprule
-    \textbf{Drawing}&\textbf{Trace Set}&\textbf{Program}&%\begin{tabular}{c}
+    \textbf{Drawing}&\textbf{Spec}&\textbf{Program}&%\begin{tabular}{c}
       \textbf{Compression factor}%\\\textbf{factor}
@@
 but make them much faster by
-learning a domain-specific \emph{search policy}.
+learning a domain-specific \textbf{search policy}.
 A search policy poses search problems
@@
 
-A search policy $\pi_\theta(\sigma  | T )$ takes as input a trace set $T$ and predicts a distribution over synthesis problems, each of which is written $\sigma $ and corresponds to a set of possible programs to search over (so $\sigma \subseteq \text{DSL}$).
+A search policy $\pi_\theta(\sigma  | T )$ takes as input a spec $S$ and predicts a distribution over synthesis problems, each of which is written $\sigma $ and corresponds to a set of possible programs to search over (so $\sigma \subseteq \text{DSL}$).
 Good policies will prefer tractable program spaces,
@@
 An example of a $1$-bias optimal search algorithm is a time-sharing system that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
-We construct a $1$-bias optimal search algorithm by identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |T)$ and $t(\sigma )  = t(\sigma|T)$, where $t(\sigma|T)$ is how long the synthesizer takes to search $\sigma $ for a program for $T$.
+We construct a $1$-bias optimal search algorithm by identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |S)$ and $t(\sigma )  = t(\sigma|S)$, where $t(\sigma|S)$ is how long the synthesizer takes to search $\sigma $ for a program for $S$.
 This means that the search algorithm explores the entire program space, but spends most of its time in the regions of the space that  the policy judges to be most promising.
@@
 \begin{align}
-\textsc{Loss}(\theta ; \mathcal{D})& =  \expect_{T\sim\mathcal{D}}\left[ \min_{\sigma\in \text{\textsc{Best}}(T)}\frac{t(\sigma | T)}{\pi_\theta (\sigma | T)}\right] + \lambda \Vert\theta\Vert_2^2\label{policyLoss}\\
-\text{where }  \sigma \in\text{\textsc{Best}}(T) &\text{ if  a minimum cost program for }T \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t.
-}p\text{ evaluates to }T} \text{cost}(p) \nonumber
+\textsc{Loss}(\theta ; \mathcal{D})& =  \expect_{S\sim\mathcal{D}}\left[ \min_{\sigma\in \text{\textsc{Best}}(S)}\frac{t(\sigma | S)}{\pi_\theta (\sigma | S)}\right] + \lambda \Vert\theta\Vert_2^2\label{policyLoss}\\
+\text{where }  \sigma \in\text{\textsc{Best}}(S) &\text{ if  a minimum cost program for }S \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t.
+}p\text{ evaluates to }S} \text{cost}(p) \nonumber
 \end{align}
@@
 To generate a training corpus for learning a policy which minimizes this loss,
-we synthesized minimum cost programs for each trace set of our hand drawings
+we synthesized minimum cost programs for each of our hand drawings
 and for each $\sigma $.
@@
 \begin{equation}
-  \pi_{\theta}(\sigma |T)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{trace}}(T)\right)
+  \pi_{\theta}(\sigma |S)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{spec}}(S)\right)
 \end{equation}
@@
 the parameter settings of $\sigma $ (see Tbl.~\ref{policyOutput})
-and $\phi_{\text{trace}}(T)$ extracts a few simple features of the trace set $T$;
+and $\phi_{\text{spec}}(S)$ extracts a few simple features of the trace set $S$;
 see supplement for details.
@@
 \begin{table}[h]\centering
-  \caption{Parameterization of different ways of posing the program synthesis problem.
-The policy learns to choose parameters likely to quickly yield a minimal cost program.
-We slightly abuse notation by writing $\sigma $ to mean an assignment to each of these parameters (so $\sigma $ assumes one of 24 different values) and to mean the set of programs selected by that parameterization (so $\sigma \subseteq \text{DSL}$)}\label{policyOutput}
+  \caption{Parameterization of different ways of posing the program synthesis problem. The policy learns to choose parameters likely to quickly yield a minimal cost program.
+    %We slightly abuse notation by writing $\sigma $ to mean an assignment to each of these parameters (so $\sigma $ assumes one of 24 different values) and to mean the set of programs selected by that parameterization (so $\sigma \subseteq \text{DSL}$)
+  }\label{policyOutput}
   \begin{tabular}{lll}\toprule
@@
 Why synthesize a graphics program,
-if the trace set already suffices to recover the objects in an image?
+if the spec already suffices to recover the objects in an image?
 Within our domain of hand-drawn figures, graphics program synthesis has several uses:
@@
 \vspace{-0.75cm}  \end{wrapfigure}
-The program synthesizer corrects errors made by the neural network by favoring trace sets which lead to more
+The program synthesizer corrects errors made by the neural network by favoring specs which lead to more
 concise or general programs.  For example, figures with perfectly aligned objects are preferable, %% to figures whose parts are slightly misaligned,
@@
 we run the program synthesizer on the
-Top-$k$  most likely trace sets output by the neurally guided sampler.
+Top-$k$  most likely specs output by the neurally guided sampler.
 Then, the system
@@
 The prior probability of a program is learned by picking the prior maximizing
-the likelihood of the ground truth trace sets;
+the likelihood of the ground truth specs;
 see supplement for details.
 But, this procedure can only correct errors when
-a correct trace set is in the Top-$k$.
+a correct spec is in the Top-$k$.
 Our sampler could only do better on
@@
 
-%% \subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on the design of the neural architecture.
-
-%% \subsubsection*{Supplemental information.} The supplement may be found at:~\url{http://web.mit.edu/ellisk/www/graphicsProgramSupplement.pdf}
-
-%\input{synthesizerOutputs.tex}
-
-\bibliographystyle{iclr2018_conference}
+\bibliographystyle{unsrt}
 {\small \bibliography{main}}

### 2018-04-25 revision.tex
nips 2018

@@
   learn a convolutional neural network that proposes plausible drawing
-  primitives that explain an image. These drawing primitives are
-  like a trace of the set of primitive commands issued by a graphics
+  primitives that explain an image. These drawing primitives are like
+  a trace of the set of primitive commands issued by a graphics
   program. We learn a model that uses program synthesis techniques to
-  recover a graphics program from that trace. These programs have constructs like variable
-  bindings, iterative loops, or simple kinds of conditionals. With a
-  graphics program in hand, we can correct errors made by the deep
-  network %, measure similarity between drawings by use of similar high-level geometric
-  %structures,
-  and extrapolate drawings.  Taken together these results
-  are a step towards agents that induce useful, human-readable
-  programs from perceptual input.
+  recover a graphics program from that trace. These programs have
+  constructs like variable bindings, iterative loops, or simple kinds
+  of conditionals. With a graphics program in hand, we can correct
+  errors made by the deep network and extrapolate drawings.  Taken
+  together these results are a step towards agents that induce useful,
+  human-readable programs from perceptual input.
 \end{abstract}
@@
 (1) Inferring trace sets from images requires \emph{domain-specific} design choices from the deep learning and computer vision toolkits (Sec.~\ref{neuralNetworkSection}).
-(2) Generalizing to noisy hand drawings requires learning a \emph{domain-specific} noise model that is invariant to the variations across hand drawings (Sec.~\ref{generalizingTheHandDrawings}).
+(2) Generalizing to noisy hand drawings, we will show, requires learning a \emph{domain-specific} noise model that is invariant to the variations across hand drawings (Sec.~\ref{generalizingTheHandDrawings}).
 (3) Discovering good programs requires solving a difficult combinatorial search problem, because the programs are often long and complicated (e.g., 9 lines of code, with nested loops and conditionals).
@@
   \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1, 5, 100)?
-    Distance to ground truth trace set measured by the intersection over union of predicted vs.
-ground truth.
+    Distance to ground truth trace set measured by the intersection over union (IoU) of predicted vs.
+ground truth: IoU of sets $A$ and $B$ is $|A\cap B|/|A\cup B|$.
 (a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 5 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth.

### 2018-04-25 supplement.tex
nips 2018

@@
 \maketitle
+
+\section{Further testing of the trace hypothesis}
+
+Recall that we factored the graphics program synthesis problem into two components: (1) a perception-facing component, whose job is to go from perceptual input to a set of commands that must occur in the execution trace of the program (\textbf{trace set}); and (2) a program synthesis component, whose job is to infer a program whose execution trace contains those commands.
+This is a different approach from other recent program induction models (e.g.,~\cite{devlin2017robustfill,nps}), which regress directly from a program induction problem to the source code of the program.
+We motivated the usefulness of our factoring of the problem via The Trace Hypothesis.
+
+\textbf{Experiment.} To test whether the trace hypothesis is necessary for our domain, we trained a model to regress directly from images to graphics programs.
+This baseline model, which we call the \emph{no-trace baseline}, was able to infer some simple programs, but failed completely on more sophisticated scenes.
+
+Baseline model architecture: The model architecture is a straightforward, image-captioning-style CNN$\to$LSTM.
+We keep the same CNN architecture from our main model (Section~\ref{CNNarchitecture}), with the sole difference that it takes only one image as input.
+The LSTM decoder produces the program token-by-token: so we flatten the program's hierarchical structure, and use special ``bracketing'' symbols to convey nesting structure, in the spirit of~\citep{vinyals2015grammar}.
+The LSTM decoder has 2 hidden layers with 1024 units.
+We used 64-dimensional embeddings for the program tokens.
+
+Training and evaluation: The model was trained on $10^7$ synthetically generated programs -- 2 orders of magnitude more data than the model we present in the main paper.
+We then evaluated the baseline on \emph{synthetic renders} of our 100 hand drawings (the testing set used throughout the paper).
+Recall that our model was evaluated on noisy real hand drawings.
+We sample programs from this baseline model conditioned on a synthetic render of a hand drawing, and report only the sampled program whose execution trace most closely matched the ground truth trace set, as measured by the symmetric difference of the two sets.
+We allow the baseline model to spend 1 hour drawing samples per drawing -- recall that our model finds 58\% of programs in under a minute.
+Together these training and evaluation choices are intended to make the problem as easy as possible for the no-trace baseline.
+
+Results: The no-trace  baseline succeeds for trivial programs (a few lines, no variables, loops, etc.); occasionally gets small amounts of simple looping structure; and fails utterly for most of our test cases.
+See Figure~\ref{noTrace}.
+
+\begin{figure}[h]\centering
+      \includegraphics[width = 2cm]{figures/noTraceOutputs/11.png}
+  \includegraphics[width = 2cm]{figures/noTraceOutputs/16.png}
+    \includegraphics[width = 2cm]{figures/noTraceOutputs/29.png}
+    \includegraphics[width = 2cm]{figures/noTraceOutputs/7.png}
+        \includegraphics[width = 2cm]{figures/noTraceOutputs/94.png}
+      \includegraphics[width = 2cm]{figures/noTraceOutputs/38.png}
+  \caption{Top, white: synthetic rendering of a hand drawing. Bottom, black: output of best program found by no-trace baseline.}\label{noTrace}
+  \end{figure}
 
@@
 
-\subsection{Convolutional network}
+\subsection{Convolutional network}\label{CNNarchitecture}
 The convolutional network takes as input 2 $256\times 256$ images
@@
 
+\begin{comment}
 \subsection{Predicting continuous coordinates using Mixture Density Networks}
@@
   \end{figure}
+\end{comment}
 \subsection{LSTM Baseline}

### 2018-04-28 nips_2018.tex
small tweaks
shortened - still need to kill almost a page

@@
 \newcommand{\probability}{\mathds{P}} %{{\rm I\kern-.3em P}}
+\newcommand{\indicator}{\mathds{I}} %{{\rm I\kern-.3em P}}
 
@@
 
-Human vision is rich -- we infer 3D shape, objects, parts of objects,
-and relations between objects -- but vision is also abstract:
+Human vision is rich -- we infer shape, objects, parts of objects,
+and relations between objects -- and vision is also abstract:
 we can perceive the radial symmetry of a spiral staircase,
@@
 and take as our goal to learn high--level
-graphics programs from images.
-The graphics programs we consider draw simple figures like those found in machine learning papers
+graphics programs from simple 2D drawings.
+The graphics programs we consider make figures like those found in machine learning papers
 (Fig.~\ref{firstPageExamples}),
@@
  Framed as probabilistic inference,
- our two-step factoring cashes out as a generative model where a latent program
+we interpret our two-step factoring  as a generative model where a latent program
  is executed to produce a set of drawing commands,
@@
       \includegraphics[width = 0.9cm]{figures/39-parse.png}}; 
-    \node(trace)[draw,thin,fit = (traceImage) (traceSource), label = above:{{\small Spec}}] {};
+    \node(trace)[draw,thin,fit = (traceImage) (traceSource), label = above:{{\small Drawing commands (Spec)}}] {};
 
@@
 many different approaches from the computer vision toolkit to
-parse an image into primitive drawing commands  (in our terminology, a ``spec'')~\cite{nsd}.
+parse an image in to primitive drawing commands  (in our terminology, a ``spec'')~\cite{nsd}.
 Our network constructs the
@@
 \end{figure}
-\begin{table}[t]
+\begin{table}[h]
   \caption{Primitive drawing commands currently supported by our model.}
@@
   \end{tabular}&\begin{tabular}{l}
-    Finishes trace set inference
+    Finishes spec inference
     \end{tabular}
@@
 images $I$ for randomly generated scenes
-and maximizing
+and maximizing $\probability_\theta[S|I]$,
 %Eq.~\ref{objective}
  the likelihood of $S$ given $I$ with respect to
- the model parameters, $\theta$, by gradient ascent.
+  model parameters $\theta$, by gradient ascent.
 We trained on $10^5$ scenes, which takes a day on an Nvidia TitanX GPU.
@@
 Neither SMC nor the neural network are sufficient on their own.
-\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}\vspace{-0.7cm}
+\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}%\vspace{-0.7cm}
 \end{wrapfigure}
@@
 by doing a beam search to
-recover  specs maximizing $\probability_\theta[S|I]$. But, if the network predicts an incorrect
+recover  specs maximizing $\probability_\theta[S|I]$. %% , where $\probability_\theta [\cdot |I]$ is
+%% the probability assigned by the network conditioned on image $I$
+ But, if the network predicts an incorrect
 drawing command, it has no way of recovering from that error.  
@@
 %For the SMC sampler, we use pixel-wise distance as a surrogate for a likelihood function.
-The SMC sampler is designed to sample
+Our SMC sampler draws samples
 from the distribution $\propto L(I|\text{render}(S))
@@
 to generalize to hand drawings by introducing noise into the
-renderings of the training target images.
-We designed this noise process to introduce the kinds of variations found in hand drawings (%% Fig.~\ref{handDrawingExamples}; 
+renderings of the training target images, where the noise process  mimics the kinds of variations found in hand drawings (%% Fig.~\ref{handDrawingExamples}; 
 see supplement for details).
-
-Our neurally-guided SMC procedure
-used pixel-wise distance as a surrogate for a likelihood function ($L(\cdot|\cdot)$ in section~\ref{neuralNetworkSection}).
-But pixel-wise distance fares poorly on hand drawings, which never exactly match
+While our neurally-guided SMC procedure
+used pixel-wise distance as a surrogate for a likelihood function ($L(\cdot|\cdot)$ in Sec.~\ref{neuralNetworkSection}),
+ pixel-wise distance fares poorly on hand drawings, which never exactly match
 the model's renders.
@@
 the distance between two specs conditioned upon their renderings.
-We $L_{\text{learned}}(\cdot |\cdot )$  to approximate the symmetric difference,
+We train $L_{\text{learned}}(\cdot |\cdot )$  to approximate the symmetric difference,
 which is  the number of drawing commands by which two specs  differ:
@@
 %we made the drawings on graph paper.
-For each drawing we annotated a ground truth trace set and had the neurally guided SMC sampler
+For each drawing we annotated a ground truth spec and had the neurally guided SMC sampler
 produce $10^3$ samples. % for each drawing.
@@
 We also penalize using many different numerical constants; see supplement.
+Returning to the generative model in Fig.~\ref{roadmap},
+this setup is the same as saying that the prior probability of a program $p$ is $\propto \exp\left(-\text{cost}(p) \right)$ and the likelihood of a spec $S$ given a program $p$ is $\indicator[p\text{ consistent w/ }S]$.
 %\remark{The flow here is a bit off/backwards.
@@
 \begin{table}[t]
-  \caption{Example drawings (left), their ground truth specs (middle left), and programs synthesized from these specs (middle right).
+  \caption{Drawings (left), their specs (middle left), and programs synthesized from these specs (middle right).
 Compared to the specs the programs are more compressive (right: programs have fewer lines than specs) and automatically group together related drawing commands.
-Note the nested loops  and special case conditionals in the Ising model, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
+Note nested loops  and conditionals in the Ising model, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
 %  \vspace{-0.6cm}
@@
 
-A search policy $\pi_\theta(\sigma  | T )$ takes as input a spec $S$ and predicts a distribution over synthesis problems, each of which is written $\sigma $ and corresponds to a set of possible programs to search over (so $\sigma \subseteq \text{DSL}$).
+A search policy $\pi_\theta(\sigma  | S )$ takes as input a spec $S$ and predicts a distribution over synthesis problems, each of which is written $\sigma $ and corresponds to a set of possible programs to search over (so $\sigma \subseteq \text{DSL}$).
 Good policies will prefer tractable program spaces,
@@
 With this learned policy in hand we can synthesize 58\% of programs within a minute.
-\end{experiment}
+%
 \begin{table}[h]\centering
@@
   \end{table}
-\begin{figure}[h]
-  \centering  \includegraphics[width = 11cm]{figures/policyComparison.png}
+\begin{table}[h]
+  \centering
+  \begin{minipage}[c]{0.4\textwidth}
+  \begin{tabular}{lll}
+    \toprule Model&\begin{tabular}{c}
+      Median \\search time
+      \end{tabular}&Timeouts\\\midrule
+    Sketch&274 sec&27\%\\
+    Oracle&6 sec&2\%\\
+    Learned policy&28 sec&2\%\\\bottomrule 
+    \end{tabular}.  
+  \end{minipage}\hfill%
+  \begin{minipage}[c]{0.5\textwidth}
     \caption{How long does it typically take to synthesize a minimum cost program?
@@
 Oracle:  upper bounds  the performance of any search policy.
-Learned policy: a bias-optimal learned search policy running on an ideal timesharing machine.
-$\infty = $ timeout.
+Learned policy: our bias-optimal learned search policy running.
+%% $\infty = $ timeout.
 Red dashed line is median time.
           Learned policy evaluated using 20-fold cross validation.}\label{policyEvaluation}
+    \end{minipage}
 \end{figure}
@@
 in our system the user need not annotate which strokes correspond to which shapes; our neural network produces something equivalent to the annotations).
-%A key similarity however is that both CogSketch and our system have as a goal to make it easier to produce nice-looking figures.
-%% Unsupervised Program Synthesis~\cite{ellis2015unsupervised} is a related framework which was also applied to geometric reasoning problems.
-The goals of~\cite{ellis2015unsupervised} were cognitive modeling,
-%% and they applied their technique to synthetic scenes used in human behavioral studies.
-%% open domain sketch understanding.
-structure mapping style model.
-also taps into cyc?
-the user segments the ink and labels them with concepts from knowledge base.
-like us they focus on compositional understanding.
-``cognitive simulation", solves things like Raven matrices in IQ tests.
-not really trying right now to be automated like our system.
-
-\textbf{The Trace Hypothesis:} The idea that an execution trace could assist in program learning goes back to the 1970's~\citep{Summers:1977:MLP:321992.322002} and has  been applied in neural models of program induction, like Neural Program Interpreters~\citep{DBLP:journals/corr/ReedF15}, or DeepCoder, which predicts what functions occur in the execution trace~\citep{BalGauBroetal16}.
-Our contribution to this idea is the trace hypothesis:
-that  trace sets can be inferred from perceptual data,
-and that the trace set is a useful bridge between perception and symbolic representation.
-Our work is the first to articulate and explore this hypothesis
-by demonstrating how a trace could be inferred and how it can be used to synthesize a high-level program.
-
-%% \subsection{Future work}
-%% There are many directions for future work.
-The proposal network  currently handles only a very small subset of \LaTeX~drawing commands, though there is no reason that it could not be extended to handle more with a higher-capacity network.
-%% In the synthesis phase, a more expressive DSL---including subroutines, recursion, and symmetry groups beyond reflections---would allow the system to effectively model a wider variety of graphical phenomena.
-The synthesizer itself could also be the subject of future work: the system currently uses the general-purpose Sketch synthesizer, which can take minutes to hours to run, whereas custom-built domain-specific synthesizers can run much faster or even interactively~\citep{le2014flashextract}.
-
-%% In the parsing phase, the proposal network currently samples positional variables on a discrete grid.
-More general types of drawings could be supported by instead sampling from continuous distributions, e.g.
-using Mixture Density Networks (MDN)~\citep{MDN}.
-%% We prototyped a variant of our model that predicts continuous coordinates. See supplement.
 
@@
 We have presented a system for inferring graphics programs which generate \LaTeX-style figures from hand-drawn images.
-The system uses a combination of deep neural networks and stochastic search to parse drawings into symbolic trace sets; it then feeds these traces to a general-purpose program synthesis engine to infer a structured graphics program.
+The system uses a combination of deep neural networks and stochastic search to parse drawings into symbolic specifications; it then feeds these specs to a general-purpose program synthesis engine to infer a structured graphics program.
 We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings.
-
 In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the code.
-More generally, we believe the trace hypothesis, as realized in our two-phase system---parsing into trace sets, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for other domains in which agents must programmatically reason about noisy perceptual input.
+More generally, we believe the problem of inferring visual programs is a promising direction for machine perception.
 

### 2018-04-28 nips_2018.tex
DC baseline data

@@
  using a neural network to amortize the cost of inferring specs from images and using
- a variant of Adaptive Levin Search~\cite{schmidhuber1997shifting}
+ a variant of Bias--Optimal Search~\cite{schmidhuber2004optimal}
  to amortize the cost of synthesizing programs from specs.
@@
   \centering\begin{tikzpicture}
-    \node[ thick,anchor = west,inner sep=0pt,label={[yshift = 0.3cm]{\small Image}}](observation) at (0,0) {\includegraphics[width = 1.5cm]{figures/expert-39-trimmed.png}};
-    \node[ultra thick,anchor = west,inner sep=0pt](traceSource) at (3,0.5){    \begin{lstlisting}[basicstyle = \scriptsize\ttfamily]
+  \node[ thick,anchor = west,inner sep=0pt,label={[yshift = 0.3cm]{\small \begin{tabular}{c}
+          Image\\
+          (Observed)
+  \end{tabular}}}](observation) at (0,0) {\includegraphics[width = 1.5cm]{figures/expert-39-trimmed.png}};
+    \node[ultra thick,anchor = west,inner sep=0pt](traceSource) at (3.7,0.5){    \begin{lstlisting}[basicstyle = \scriptsize\ttfamily]
 line, line,
@@
 \end{lstlisting}};
-    \node[ultra thick,anchor = west,inner sep=0pt](traceImage) at (3.3,-0.5) {
+    \node[ultra thick,anchor = west,inner sep=0pt](traceImage) at (4,-0.5) {
       \includegraphics[width = 0.9cm]{figures/39-parse.png}}; 
-    \node(trace)[draw,thin,fit = (traceImage) (traceSource), label = above:{{\small Drawing commands (Spec)}}] {};
-
-    \node[draw, thick,anchor = west,inner sep=2pt,label=above:{\small Program}](program) at (6.3,0) {
+    \node(trace)[draw,thin,fit = (traceImage) (traceSource), label = above:{{\small \begin{tabular}{c}
+            Spec/Drawing Commands\\
+            (Latent)
+    \end{tabular}}}] {};
+
+    \node[draw, thick,anchor = west,inner sep=2pt,label=above:{\small \begin{tabular}{c}
+          Program\\
+          (Latent)
+    \end{tabular}}](program) at (7.7,0) {
       \begin{lstlisting}
@@
     \end{lstlisting}};
-    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Extrapolation}](extrapolate) at (9.9,0.5) {\includegraphics[width = 1.3cm]{figures/39-extrapolated.png}};
+    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Extrapolation}](extrapolate) at (12,0.5) {\includegraphics[width = 1.3cm]{figures/39-extrapolated.png}};
 %    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Similarity}](similarity) at (11.3,0) {\includegraphics[width = 1cm]{figures/expert-38-trim.png}};
-    \node[ultra thick,anchor = west,text width = 1.3cm,inner sep=0pt](errors) at (10,-1.2) {\small Error correction};
+    \node[ultra thick,anchor = west,text width = 1.3cm,inner sep=0pt](errors) at (12.1,-1.2) {\small Error correction};
 
     \draw[->, ultra thick] (trace.west) -- node[fill = white,rotate = -90] {{\small Rendering}} (observation.east);
-    \draw[->, thick, red] ([xshift = -5]observation.south) to[out = -30,in = -150] node[midway,yshift = -6]{{\small Learning + Stochastic search}} ([xshift = -15]trace.south);
+    \draw[->, very thick, red] ([xshift = -5]observation.south) to[out = -30,in = -150] node[midway,yshift = -6]{{\small Learning + Stochastic search}} ([xshift = -15]trace.south);
     \draw[->, ultra thick] (program.west) -- node[fill = white,rotate = -90] {{\small Execution}} (trace.east);
-    \draw[->, thick, red] ([xshift = 10]trace.south) to[out = -10,in = -170] node[midway,yshift = -6]{{\small Learning + Program synthesis}} ([xshift = 10]program.south);
+    \draw[->, thick, red, very thick] ([xshift = 10]trace.south) to[out = -10,in = -170] node[midway,yshift = -6]{{\small Learning + Program synthesis}} ([xshift = 10]program.south);
 %    \draw[->, thick, red] (program.east) to[out = 80,in = 180] (errors.west);
 %    \draw[->, thick] (program.east) to[out = 40,in = -230] (similarity.west);
-    \draw[->, thick, red] (program.east) to[out = 60,in = 180] (extrapolate.west);
+    \draw[->, thick, red, very thick] (program.east) to[out = 60,in = 180] (extrapolate.west);
 
@@
 %Eq.~\ref{objective}
- the likelihood of $S$ given $I$ with respect to
+ the likelihood of $S$ given $I$, with respect to
   model parameters $\theta$, by gradient ascent.
@@
 \end{wrapfigure}
+
 Our network can ``derender'' random synthetic images
@@
 but, for this domain, cannot parse cluttered scenes with many objects.
-
-%% \begin{figure}[H]\centering
-%%   \begin{minipage}{6cm}
-%%     \begin{minipage}[t]{3cm}\fbox{\includegraphics[width=2.75cm]{figures/randomScene-58-7.png}}\end{minipage}%
-%%     \begin{minipage}[t]{3cm}\fbox{\includegraphics[width=2.75cm]{figures/randomScene-33-5.png}}\end{minipage}
-%%     \caption{Network is trained to infer traces for randomly generated scenes like the two shown above. See supplement for details of the training data generation.}\label{trainingData}
-%%   \end{minipage}\hfill%
-%%   \begin{minipage}{7.5cm}\centering
-%%     \includegraphics[width = 7cm]{figures/editDistance36.png}
-%% %    \includegraphics[width = 4cm]{figures/accuracy.png}
-%%       \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
-It generalizes to scenes with many more objects.
-Neither the stochastic search nor the neural network are sufficient on their own.
-\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}
-%%     \end{minipage}
-
-%%   \end{figure}
 
@@
 Given a search policy, what is the best way of using it to quickly find minimum cost programs?
-We use a \emph{bias-optimal search algorithm}~\citep{schmidhuber2004optimal}:
+We use a bias-optimal search algorithm~\citep{schmidhuber2004optimal}:
 
@@
 An example of a $1$-bias optimal search algorithm is a time-sharing system that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
+Bias-optimal search over program spaces is called \textbf{Levin Search}~\cite{levin1973universal}.
 We construct a $1$-bias optimal search algorithm by identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |S)$ and $t(\sigma )  = t(\sigma|S)$, where $t(\sigma|S)$ is how long the synthesizer takes to search $\sigma $ for a program for $S$.
@@
 \end{align}
-Practically, bias optimality has now bought us the following: (1) a guarantee that the policy will always find the minimum cost program; and (2) a differentiable loss function for the policy parameters that takes into account the cost of searching, in contrast to e.g.
+%Practically, bias optimality has now bought us the following: (1) a guarantee that the policy will always find the minimum cost program; and (2) a differentiable loss function for the policy parameters that takes into account the cost of searching, in contrast to e.g.
 DeepCoder~\citep{BalGauBroetal16}.
 
-To generate a training corpus for learning a policy which minimizes this loss,
+To generate a training corpus for learning a policy,
 we synthesized minimum cost programs for each of our hand drawings
-and for each $\sigma $.
+and for each $\sigma $,
 %Solving these
@@
 %With the training set in hand we  %This loss is differentiable but nonconvex even if $\pi_{\theta}(\cdot |\cdot )^{-1}$ is convex.
-We locally minimize this loss using gradient descent. % while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}.
+then minimized~\ref{policyLoss} using gradient descent. % while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}.
 %See supplement for details.
 Because we want to learn a policy from only $100$ hand-drawn diagrams,
-we chose a simple low-capacity, bilinear model for a policy:
+we chose a  low-capacity, bilinear model for $\pi$:
 \begin{equation}
@@
 We compare synthesis times for our learned search policy
-with two alternatives:
+with three alternatives:
  \emph{Sketch}, which poses the
  entire problem wholesale to the Sketch program synthesizer;
+ a DeepCoder--inspired model, \emph{DC}, that learns to predict which program components (loops, reflections)
+ are likely to be useful~\cite{BalGauBroetal16};
 and an \emph{Oracle},
@@
     Sketch&274 sec&27\%\\
+    DC&187 sec&2\%\\
     Oracle&6 sec&2\%\\
@@
   \begin{minipage}[c]{0.5\textwidth}
-    \caption{How long does it typically take to synthesize a minimum cost program?
+    \caption{Time to synthesize a minimum cost program.
 Sketch: out-of-the-box performance of the Sketch~\citep{solar2008program} program synthesizer.
+DC: Baseline that predicts program components, trained like~\cite{BalGauBroetal16}.
 Oracle:  upper bounds  the performance of any search policy.
-Learned policy: our bias-optimal learned search policy running.
-%% $\infty = $ timeout.
+Learned policy: ours  %% $\infty = $ timeout.
 Red dashed line is median time.
-          Learned policy evaluated using 20-fold cross validation.}\label{policyEvaluation}
+           evaluated using 20-fold cross validation.}\label{policyEvaluation}
     \end{minipage}
@@
 
-\textbf{Deep Learning:} Our neural network bears resemblance to the Attend-Infer-Repeat (AIR) system, which learns to decompose an image into its constituent objects~\citep{eslami1603attend}.
-AIR learns an iterative inference scheme which infers objects one by one and also decides when to stop inference.
+\textbf{Deep Learning:} Our neural network combines the architectural ideas of Attend-Infer-Repeat~\citep{eslami1603attend} -- which learns to decompose an image into its constituent objects -- with the training regime and SMC inference  of Neurally Guided Procedural Modeling~\cite{ritchie2016neurally} -- which learns to control procedural graphics programs.
+%AIR learns an iterative inference scheme which infers objects one by one and also decides when to stop inference.
 %; this is similar to our approach's first stage, which parses images into traces. Our approach further produces interpretable, symbolic programs which generate those traces.
-Our network  differs in its architecture and training regime: AIR learns a recurrent auto-encoding model via variational inference, whereas our parsing stage learns an autoregressive-style model from randomly-generated (trace, image) pairs.
+%Our network  differs in its architecture and training regime: AIR learns a recurrent auto-encoding model via variational inference, whereas our parsing stage learns an autoregressive-style model from randomly-generated (trace, image) pairs.
 %Finally, while AIR was evaluated on multi-MNIST images and synthetic 3D scenes, we focus on hand-drawn sketches.
-
 IM2LATEX~\citep{im2latex} is a recent work that also converts images to
@@
 programming constructs like loops and conditionals.
-Recovering a high-level program is more challenging than recovering markup
-because it is a highly under constrained symbolic reasoning problem.
-
-Our image-to-trace parsing architecture builds on prior work on controlling procedural graphics programs~\citep{ritchie2016neurally}.
+%Recovering a high-level program is more challenging than recovering markup
+%because it is a highly under constrained symbolic reasoning problem.
+
+%Our image-to-trace parsing architecture builds on prior work on controlling procedural graphics programs~\citep{ritchie2016neurally}.
 %Given a program which generates random 2D recursive structures such as vines, that system learns a structurally-identical ``guide program'' whose output can be directed, via neural networks, to resemble a given target image.
-We adapt this method to a different visual domain (figures composed of multiple objects), using a broad prior over possible scenes as the initial program and viewing the trace through the guide program as a symbolic parse of the target image.
-We then show how to efficiently synthesize higher-level programs from these traces.
+%% We adapt this method to a different visual domain (figures composed of multiple objects), using a broad prior over possible scenes as the initial program and viewing the trace through the guide program as a symbolic parse of the target image.
+%% We then show how to efficiently synthesize higher-level programs from these traces.
 

### 2018-04-28 nips_2018.tex
almost down to eight pages!
supplement updates

@@
 \newcommand{\probability}{\mathds{P}} %{{\rm I\kern-.3em P}}
-\newcommand{\indicator}{\mathds{I}} %{{\rm I\kern-.3em P}}
+\newcommand{\indicator}{\mathds{1}} %{{\rm I\kern-.3em P}}
 
@@
 \begin{equation}
-  \text{program}(S) = \argmin_{p\in \text{DSL, s.t. }p \text{ consistent w/ } S} \text{cost}(p)\label{programObjective}
+  %  \text{program}(S) = \argmin_{p\in \text{DSL, s.t. }p \text{ consistent w/ } S} \text{cost}(p)\label{programObjective}
+    \text{program}(S) = \argmax_{p\in \text{DSL}} \indicator\left[p \text{ consistent w/ } S \right]\exp \left( -\text{cost}(p) \right)\label{programObjective}
 \end{equation}
@@
 %Intuitively, an $n$-bias optimal search algorithm spends at least $\probability_{\text{bias}}[\sigma ]/n$ of its time exploring solution space $\sigma $.
-An example of a $1$-bias optimal search algorithm is a time-sharing system that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
-Bias-optimal search over program spaces is called \textbf{Levin Search}~\cite{levin1973universal}.
+Bias-optimal search over program spaces is known as \textbf{Levin Search}~\cite{levin1973universal}; an example of a $1$-bias optimal search algorithm is a time-sharing system that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
 We construct a $1$-bias optimal search algorithm by identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |S)$ and $t(\sigma )  = t(\sigma|S)$, where $t(\sigma|S)$ is how long the synthesizer takes to search $\sigma $ for a program for $S$.
@@
 
-\textbf{Experiment 3: Figure~\ref{policyEvaluation}.}
+\textbf{Experiment 3: Table~\ref{policyEvaluation}.}
 We compare synthesis times for our learned search policy
@@
  entire problem wholesale to the Sketch program synthesizer;
- a DeepCoder--inspired model, \emph{DC}, that learns to predict which program components (loops, reflections)
+ a DeepCoder--style model, \emph{DC}, which learns to predict which program components (loops, reflections)
  are likely to be useful~\cite{BalGauBroetal16};
@@
 Red dashed line is median time.
-           evaluated using 20-fold cross validation.}\label{policyEvaluation}
+           evaluated w/ 20-fold cross validation.}\label{policyEvaluation}
     \end{minipage}
@@
 
-\pagebreak\subsection{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
+\subsection{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
 \begin{wrapfigure}{r}{5cm}\vspace{-0.5cm}
@@
 DeepCoder~\citep{BalGauBroetal16} is a recent model which, like ours, learns to predict likely program components.
-Our work differs because we treat
-the problem as \emph{metareasoning}, identifying and modeling
+Our work differs by identifying and modeling
 the trade-off between tractability and probability of success.
@@
 %Finally, while AIR was evaluated on multi-MNIST images and synthetic 3D scenes, we focus on hand-drawn sketches.
-IM2LATEX~\citep{im2latex} is a recent work that also converts images to
-~\LaTeX.
-Their goal is to derender  \LaTeX~ equations,
-which recovers a markup language representation.
+IM2LATEX~\citep{im2latex} is a recent work that 
+ derenders  \LaTeX~ equations,
+recovering a markup language representation.
 Our goal is to go from

### 2018-04-28 supplement.tex
supplement updates

@@
 % to compile a camera-ready version, add the [final] option, e.g.:
-\usepackage{iclr2018_conference,times}%\usepackage[final]{nips_2017}
+%\usepackage{iclr2018_conference,times}
+\usepackage{nips_2017}
 
@@
 
-\section{Further testing of the trace hypothesis}
+\section{Why not use an end--to--end solution?}
 
-Recall that we factored the graphics program synthesis problem into two components: (1) a perception-facing component, whose job is to go from perceptual input to a set of commands that must occur in the execution trace of the program (\textbf{trace set}); and (2) a program synthesis component, whose job is to infer a program whose execution trace contains those commands.
+Recall that we factored the graphics program synthesis problem into two components: (1) a perception-facing component, whose job is to go from perceptual input to a set of commands that must occur in the execution of the program (\textbf{spec}); and (2) a program synthesis component, whose job is to infer a program whose execution contains those commands.
 This is a different approach from other recent program induction models (e.g.,~\cite{devlin2017robustfill,nps}), which regress directly from a program induction problem to the source code of the program.
-We motivated the usefulness of our factoring of the problem via The Trace Hypothesis.
 
-\textbf{Experiment.} To test whether the trace hypothesis is necessary for our domain, we trained a model to regress directly from images to graphics programs.
-This baseline model, which we call the \emph{no-trace baseline}, was able to infer some simple programs, but failed completely on more sophisticated scenes.
+\textbf{Experiment.} To test whether this factoring is necessary for our domain, we trained a model to regress directly from images to graphics programs.
+This baseline model, which we call the \emph{no-spec baseline}, was able to infer some simple programs, but failed completely on more sophisticated scenes.
 
@@
 Recall that our model was evaluated on noisy real hand drawings.
-We sample programs from this baseline model conditioned on a synthetic render of a hand drawing, and report only the sampled program whose execution trace most closely matched the ground truth trace set, as measured by the symmetric difference of the two sets.
+We sample programs from this baseline model conditioned on a synthetic render of a hand drawing, and report only the sampled program whose output most closely matched the ground truth spec spec, as measured by the symmetric difference of the two sets.
 We allow the baseline model to spend 1 hour drawing samples per drawing -- recall that our model finds 58\% of programs in under a minute.
-Together these training and evaluation choices are intended to make the problem as easy as possible for the no-trace baseline.
+Together these training and evaluation choices are intended to make the problem as easy as possible for the baseline.
 
-Results: The no-trace  baseline succeeds for trivial programs (a few lines, no variables, loops, etc.); occasionally gets small amounts of simple looping structure; and fails utterly for most of our test cases.
-See Figure~\ref{noTrace}.
+Results: The no-spec baseline succeeds for trivial programs (a few lines, no variables, loops, etc.); occasionally gets small amounts of simple looping structure; and fails utterly for most of our test cases.
+See Figure~\ref{noSpec}.
 
@@
       \includegraphics[width = 2cm]{figures/noTraceOutputs/38.png}
-  \caption{Top, white: synthetic rendering of a hand drawing. Bottom, black: output of best program found by no-trace baseline.}\label{noTrace}
+  \caption{Top, white: synthetic rendering of a hand drawing. Bottom, black: output of best program found by no-spec baseline.}\label{noSpec}
   \end{figure}
@@
 \section{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
-The program synthesizer can help correct errors from the execution trace proposal network by favoring execution traces which lead to more concise or general programs.
+The program synthesizer can help correct errors from the execution spec proposal network by favoring execution specs which lead to more concise or general programs.
 For example, one generally prefers figures with perfectly aligned objects over figures whose parts are slightly misaligned -- and precise alignment lends itself to short programs.
@@
 which the program synthesizer might be able to model as a loop or reflectional symmetry.
-So, in considering several candidate traces proposed by the neural network,
-we might prefer traces whose best programs have desirable features such being short or having iterated structures.
+So, in considering several candidate specs proposed by the neural network,
+we might prefer specs whose best programs have desirable features such being short or having iterated structures.
 
-Concretely, we implemented the following scheme: for an image $I$, the neurally guided sampling scheme of section 3 of the main paper samples a set of candidate traces, written $\mathcal{F}(I)$.
-Instead of predicting the most likely trace in $\mathcal{F}(I)$ according to the neural network,
-we can take into account the programs that best explain the traces. 
-Writing $\hat{T}(I)$ for the trace the model predicts for image $I$,
+Concretely, we implemented the following scheme: for an image $I$, the neurally guided sampling scheme of section 2 of the main paper samples a set of candidate specs, written $\mathcal{F}(I)$.
+Instead of predicting the most likely spec in $\mathcal{F}(I)$ according to the neural network,
+we can take into account the programs that best explain the specs. 
+Writing $\hat{S}(I)$ for the spec the model predicts for image $I$,
 \begin{equation}
-\hat{T}(I) = \argmax_{T\in \mathcal{F}(I)} L_{\text{learned}}(I | \text{render}(T))\times \probability_\theta[T|I] \times\probability_{\beta} [ \text{program}(T)] 
+\hat{S}(I) = \argmax_{S\in \mathcal{F}(I)} L_{\text{learned}}(I | \text{render}(S))\times \probability_\theta[S|I] \times\probability_{\beta} [ \text{program}(S)] 
 \end{equation}
@@
 
-Given a corpus of graphics program synthesis problems with annotated ground truth traces (i.e. $(I,T)$ pairs),
+Given a corpus of graphics program synthesis problems with annotated ground truth specs (i.e. $(I,S)$ pairs),
 we find a maximum likelihood estimate of $\beta$:
 \begin{equation}
-  \beta^* = \argmax_{\beta} \expect \left[ \log \frac{\probability_{\beta} [\text{program}(T)]\times L_{\text{learned}}(I|\text{render}(T))\times \probability_\theta[T|I]}{\sum_{T'\in \mathcal{F}(I)} \probability_{\beta} [\text{program}(T')]\times L_{\text{learned}}(I|\text{render}(T'))\times \probability_\theta[T'|I]} \right]
+  \beta^* = \argmax_{\beta} \expect \left[ \log \frac{\probability_{\beta} [\text{program}(S)]\times L_{\text{learned}}(I|\text{render}(S))\times \probability_\theta[S|I]}{\sum_{S'\in \mathcal{F}(I)} \probability_{\beta} [\text{program}(S')]\times L_{\text{learned}}(I|\text{render}(S'))\times \probability_\theta[S'|I]} \right]
 \end{equation}
 where the expectation is taken both over the model predictions and the
-$(I,T)$ pairs in the training corpus.  We define $\probability_{\beta}
+$(I,S)$ pairs in the training corpus.  We define $\probability_{\beta}
 [\cdot]$ to be a log linear distribution $\propto \exp
@@
 program, such as its size and how many loops it has, and use these
-features to help predict whether a trace is the correct explanation
+features to help predict whether a spec is the correct explanation
 for an image.
 
-We synthesized programs for the top 10 traces
+We synthesized programs for the top 10 specs
 output by the deep network.  Learning this prior over programs can
@@
 from Fig. 6 of the main paper that the best improvement
-in accuracy we could possibly get is 70\% by looking at the top 10 traces. 
+in accuracy we could possibly get is 70\% by looking at the top 10 specs. 
 \begin{figure}[h]\centering
@@
 alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
-We used our learned distance metric between traces, $L_{\text{learned}}(\cdot|\cdot)$, and projected to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}).
+We used our learned distance metric between specs, $L_{\text{learned}}(\cdot|\cdot)$, and projected to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}).
 This reveals similarities between the objects in the drawings,
@@
 \begin{align}
-&  \textsc{Loss}_\beta(\theta ; \mathcal{D}) =  \expect_{T\sim\mathcal{D}}\left[ \textsc{SoftMinimum}_\beta \left\{
-    \frac{t(\sigma | T)}{\pi_\theta (\sigma | T)}    : \sigma\in \text{\textsc{Best}}(T)\right\}\right] + \lambda \Vert\theta\Vert_2^2\label{softenedObjective}\\
+&  \textsc{Loss}_\beta(\theta ; \mathcal{D}) =  \expect_{S\sim\mathcal{D}}\left[ \textsc{SoftMinimum}_\beta \left\{
+    \frac{t(\sigma | S)}{\pi_\theta (\sigma | S)}    : \sigma\in \text{\textsc{Best}}(S)\right\}\right] + \lambda \Vert\theta\Vert_2^2\label{softenedObjective}\\
   \text{where }&\textsc{SoftMinimum}_\beta (x_1,x_2,x_3,\cdots ) = \sum_n x_n  \frac{e^{-\beta x_n}}{\sum_{n'}e^{-\beta x_{n'}}}
@@
     &\indicator [\sigma \text{ has depth bound }1];\indicator [\sigma \text{ has depth bound }2];\indicator [\sigma \text{ has depth bound }3];]\\
-  \phi_{\text{trace}}(T) = [&\text{\# circles in }T;\text{\# rectangles in }T;\text{\# lines in }T;1]
+  \phi_{\text{spec}}(S) = [&\text{\# circles in }S;\text{\# rectangles in }S;\text{\# lines in }S;1]
   \end{align*}
@@
   \begin{tikzpicture}
-  \node[draw,blue,ultra thick,anchor = west,inner sep=0pt,label=below:Target image: $I$](observation) at (0,-1) {\includegraphics[width = 2cm]{figures/expert-18.png}};
-  \node[draw,blue,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(T)$] (canvas) at (0,-4) {};
+  \node[draw,blue,ultra thick,anchor = west,inner sep=0pt,label=below:Sarget image: $I$](observation) at (0,-1) {\includegraphics[width = 2cm]{figures/expert-18.png}};
+  \node[draw,blue,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(S)$] (canvas) at (0,-4) {};
   \draw[lightgray,ultra thin,step = 0.125] ([xshift = 0.5,yshift = 0.5]canvas.south west) grid ([xshift = -0.5,yshift = -0.5]canvas.north east);
@@
 \begin{equation}
-  \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(T)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
+  \probability_\theta [t_1t_2\cdots t_K | I,S] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(S)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
 \end{equation}
 where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
-the target image, $T$ is a trace set, $\theta$ are the
+the target image, $S$ is a spec, $\theta$ are the
 parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
 image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
-traces factorizes as:
+specs factorizes as:
 \begin{equation}
-  \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
+  \probability_\theta [S|I] = \prod_{n = 1}^{|S|} \probability_\theta [S_n | I,S_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,S]\label{objective}
 \end{equation}
-where $|T|$ is the length of trace $T$, the subscripts
-on $T$ index drawing commands within the trace (so $T_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
-token is emitted by the network to signal that the trace
+where $|S|$ is the length of spec $S$, the subscripts
+on $S$ index drawing commands within the spec (so $S_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
+token is emitted by the network to signal that the spec
 explains the image.
@@
 We evaluated the MDN version of our model on hand drawings by (1)
-performing a beam search in order to find the trace maximizing
+performing a beam search in order to find the spec maximizing
 $\probability [T|I]$, and (2) constraining the predicted coordinates
@@
 \end{equation}
-Even after using Eq.~\ref{constrainingEquation} to constrain the predicted coordinates to lie on the $16\times 16$ grid, the MDN variant of the model only produces finished traces for 48/100 of the drawings.
-See Figure~\ref{continuousParses} to see the traces recovered by the beam search.
+Even after using Eq.~\ref{constrainingEquation} to constrain the predicted coordinates to lie on the $16\times 16$ grid, the MDN variant of the model only produces finished specs for 48/100 of the drawings.
+See Figure~\ref{continuousParses} to see the specs recovered by the beam search.
 
@@
 We  compared our deep network with a baseline that models the problem as a kind of image captioning.
-Given the target image, this baseline produces the program trace in one shot by
+Given the target image, this baseline produces the program spec in one shot by
 using a CNN to extract features of the input which are passed to an LSTM which finally predicts
-the trace token-by-token.
+the spec token-by-token.
 This general architecture is used in several successful neural models of image captioning (e.g.,~\cite{vinyals2015show}).
@@
 That is, it is preferable to leave some pixels unexplained;
-for once a particle in SMC adds a drawing primitive to its trace that is not actually in the latent scene,
+for once a particle in SMC adds a drawing primitive to its spec that is not actually in the latent scene,
 it can never recover from this error.
@@
 we put a Chinese restaurant process prior~\cite{gershman2012tutorial} over
-the values of the X and Y coordinates that occur in the execution trace.
+the values of the X and Y coordinates that occur in the execution spec.
 This encourages reuse of coordinate values,
@@
 
-We seek the minimum cost program which evaluates to (produces the drawing primitives in) an execution trace $T$:
+We seek the minimum cost program which evaluates to (produces the drawing primitives in) an execution spec $T$:
 \begin{equation}
@@
 %%   \STATE {\bfseries Input:} Neural network NN, beam size $N$, maximum length $L$, target image $x$
-%%   \STATE {\bfseries Output:} Samples of the program trace
+%%   \STATE {\bfseries Output:} Samples of the program spec
 %%   \STATE Set $B_0 = \{\text{empty program}\}$
@@
 The leftmost column is a hand drawing.
-The middle column is a rendering of the most likely trace discovered by the neurally guided SMC sampling scheme.
-The rightmost column is the program we synthesized from a ground truth execution trace of the drawing.
+The middle column is a rendering of the most likely spec discovered by the neurally guided SMC sampling scheme.
+The rightmost column is the program we synthesized from a ground truth execution spec of the drawing.
 Note that because the inference procedure is stochastic,

### 2018-05-08 nips_2018.tex
8 pages!

@@
 
- The key observation behind our work is that inferring the program from an image involves two distinct steps that require different technical approaches.
+ The key observation behind our work is that going from pixels to programs involves two distinct steps, each requiring different technical approaches.
 The first step involves inferring what objects make up an image -- for diagrams, these are things like as rectangles, lines and arrows.
-The second step involves identifying the high-level structure in how the objects were drawn.
+The second step involves identifying the higher-level visual concepts that describe how the objects were drawn.
 In Fig.
@@
 
- Framed as probabilistic inference,
-we interpret our two-step factoring  as a generative model where a latent program
+This two-step factoring can be framed as probabilistic inference in a generative model where a latent program
  is executed to produce a set of drawing commands,
@@
  We infer the spec from an image using stochastic search (Sequential Monte Carlo)
- and infer a program from a spec using  \textbf{constraint-based program synthesis} \citep{solar2008program} --
+ and infer a program from a spec using  constraint-based program synthesis~\citep{solar2008program} --
  synthesizing structures like symmetries, loops, or conditionals.
@@
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-    ([yshift = -15,xshift = -115]trace.south) -- node[below = 6pt] {{\small Section~\ref{neuralNetworkSection}: Image$\to$Spec}} ([yshift = -15,xshift = -5]trace.south);
+    ([yshift = -15,xshift = -130]trace.south) -- node[below = 6pt] {{\small Section~\ref{neuralNetworkSection}: Image$\to$Spec}} ([yshift = -15,xshift = -5]trace.south);
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-    ([xshift = 5,yshift = -15]trace.south) -- node[below = 6pt] {{\small Section~\ref{programSynthesisSection}: Spec$\to$Program}} ([xshift = 140,yshift = -15]trace.south);
+    ([xshift = 5,yshift = -15]trace.south) -- node[below = 6pt] {{\small Section~\ref{programSynthesisSection}: Spec$\to$Program}} ([xshift = 170,yshift = -15]trace.south);
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-([xshift = 150,yshift = -15]trace.south) -- node[below = 6pt] {{\small Section~\ref{applicationsSection}: Applications}} ([xshift = 230,yshift = -15]trace.south);
+([xshift = 180,yshift = -15]trace.south) -- node[below = 6pt] {{\small Section~\ref{applicationsSection}: Applications}} ([xshift = 250,yshift = -15]trace.south);
   \end{tikzpicture}
@@
  \end{figure}
+
+ The new contributions of this work are (1) a working model that can infer high-level symbolic programs from raw perceptual input, and (2) a technique for using learning to amortizing the cost of program synthesis, described in Section~\ref{learningASearchPolicy}.
 
@@
 \begin{figure}[t]
+  \begin{minipage}[c]{0.65\textwidth}
     \begin{tikzpicture}
   \node[draw,blue,ultra thick,anchor = west,inner sep=0pt,label=below:Target image: $I$](observation) at (0,-1) {\includegraphics[width = 2cm]{figures/expert-18.png}};
-  \node[draw,blue,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(T)$] (canvas) at (0,-4) {};
+  \node[draw,blue,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(S)$] (canvas) at (0,-4) {};
   \draw[lightgray,ultra thin,step = 0.125] ([xshift = 0.5,yshift = 0.5]canvas.south west) grid ([xshift = -0.5,yshift = -0.5]canvas.north east);
@@
 
-  \node[draw,ultra thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 3cm] (CNN) at (4.5,-2.5) {CNN};
-  \node[inner sep = 0pt](tensorProduct) at ([xshift = -1.5cm]CNN.west) {$\bigoplus$};
-
-  \node[rotate = -90,draw,ultra thick,inner sep=0pt,minimum width = 3cm,minimum height = 0.5cm] (features) at ([xshift = 1.5cm]CNN.east) {Image features};
-
-  \node[draw,ultra thick,minimum size = 1cm](c1) at ([xshift = 1.5cm]features.north) {MLP};
+  \node[draw,ultra thick,anchor = west,inner sep=0pt,minimum width = 1cm,minimum height = 2cm] (CNN) at (4,-2.5) {CNN};
+  \node[inner sep = 0pt](tensorProduct) at ([xshift = -1.3cm]CNN.west) {$\bigoplus$};
+
+  \node[draw,ultra thick,inner sep=0pt] (features) at ([xshift = 0.01cm]CNN.east) {};
+
+  \node[draw,ultra thick,minimum size = 1cm](c1) at ([xshift = 1cm]features) {MLP};
   \node(l1) at ([yshift = -1.5cm]c1.south) {\verb|circle(|};
@@
 
-  \draw[->,ultra thick] (features.north) -- (c1.west);
-  \draw[->,ultra thick] (features.north) to[out = 45,in = 160] (a2.north);
-  \draw[->,ultra thick] (features.north) to[out = 70,in = 140] (a3.north);
+  \draw[->,ultra thick] (features) -- (c1.west);
+  \draw[->,ultra thick] (features) to[out = 45,in = 160] (a2.north);
+  \draw[->,ultra thick] (features) to[out = 80,in = 140] (a3.north);
   \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c2.west);
@@
   \draw[->,ultra thick] (tensorProduct.east)  -- node[fill = white,rotate = 90] {{\tiny $256\times 256\times 2$}}  (CNN.west);
-  \draw[->,ultra thick] (CNN.east) -- node[fill = white,rotate = 90] {{\tiny $16\times 16\times 10$}} (features.south);
+  \draw[-,ultra thick] (CNN.east) -- %node[fill = white,rotate = 90] {{\tiny $16\times 16\times 10$}}
+  (features);
 %  \draw[]
@@
 \end{tikzpicture}
-\caption{Our neural architecture for inferring the spec of a graphics program from its output.
+  \end{minipage}  \hfill%
+  \begin{minipage}[c]{0.2\textwidth}
+    \caption{Neural architecture for inferring specs from images.
 \textcolor{blue}{Blue}: network inputs.
 Black: network operations.
-\textcolor{red}{Red}: samples from a multinomial.
+\textcolor{red}{Red}: draws from a multinomial.
 \texttt{Typewriter font}: network outputs.
-Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}.
-STN (spatial transformer network) is a differentiable attention mechanism~\citep{jaderberg2015spatial}.}  \label{architecture}
+Renders on a $16\times 16$ grid, shown in \textcolor{gray}{gray}.
+STN: differentiable attention mechanism~\citep{jaderberg2015spatial}.}  \label{architecture}
+    \end{minipage}
 \end{figure}
+
 \begin{table}[h]
@@
 
-\begin{wrapfigure}{r}{8cm}
-  \vspace{-0.25cm}
-  \centering
-      \includegraphics[width = 7cm]{figures/averageNumberOfErrors.png}
-      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
-Model generalizes to scenes with many more objects.
-Neither SMC nor the neural network are sufficient on their own.
-\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}%\vspace{-0.7cm}
-\end{wrapfigure}
-
 Our network can ``derender'' random synthetic images
@@
 training data.
-We compare with a baseline that produces the trace set in one shot by
+We compare with a baseline that produces the spec in one shot by
 using the CNN to extract features of the input which are passed to an LSTM which finally predicts
-the trace set token-by-token (LSTM in Fig.~\ref{syntheticResults}).
+the spec token-by-token (LSTM in Fig.~\ref{syntheticResults}).
 This architecture is used in several successful neural models of image captioning (e.g.,~\cite{vinyals2015show}),
 but, for this domain, cannot parse cluttered scenes with many objects.
+\begin{wrapfigure}{r}{8cm}
+  \vspace{-0.25cm}
+  \centering
+      \includegraphics[width = 7cm]{figures/averageNumberOfErrors.png}
+      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
+Model generalizes to scenes with many more objects.
+Neither SMC nor the neural network are sufficient on their own.
+\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}\vspace{-1cm}
+\end{wrapfigure}
 
@@
 For 63\% of the drawings, the Top-1 most likely sample exactly matches the
-ground truth; with more samples, the model finds trace sets
+ground truth; with more samples, the model finds specs
 that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
@@
 %for explaining $T$.
-Our goal now is to find the parameters of the policy, written $\theta$, which best navigate this trade-off.
+Our goal now is to find the parameters of the policy, written $\theta$, that best navigate this trade-off.
 
@@
 %Intuitively, an $n$-bias optimal search algorithm spends at least $\probability_{\text{bias}}[\sigma ]/n$ of its time exploring solution space $\sigma $.
-Bias-optimal search over program spaces is known as \textbf{Levin Search}~\cite{levin1973universal}; an example of a $1$-bias optimal search algorithm is a time-sharing system that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
+Bias-optimal search over program spaces is known as \textbf{Levin Search}~\cite{levin1973universal}; an example of a $1$-bias optimal search algorithm is an ideal time-sharing system that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
 We construct a $1$-bias optimal search algorithm by identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |S)$ and $t(\sigma )  = t(\sigma|S)$, where $t(\sigma|S)$ is how long the synthesizer takes to search $\sigma $ for a program for $S$.
@@
 To generate a training corpus for learning a policy,
-we synthesized minimum cost programs for each of our hand drawings
+we synthesized minimum cost programs for each  drawing
 and for each $\sigma $,
@@
 %See supplement for details.
-Because we want to learn a policy from only $100$ hand-drawn diagrams,
-we chose a  low-capacity, bilinear model for $\pi$:
-\begin{equation}
-  \pi_{\theta}(\sigma |S)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{spec}}(S)\right)
-\end{equation}
-where $\phi_{\text{params}}(\sigma  )$ is a one-hot encoding of
-the parameter settings of $\sigma $ (see Tbl.~\ref{policyOutput})
-and $\phi_{\text{spec}}(S)$ extracts a few simple features of the trace set $S$;
-see supplement for details.
+Because we want to learn a policy from only $100$ drawings,
+we parameterize $\pi$ with a  low-capacity bilinear model; see supplement.
+%for $\pi$:
+%% \begin{equation}
+%%   \pi_{\theta}(\sigma |S)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{spec}}(S)\right)
+%% \end{equation}
+%% where $\phi_{\text{params}}(\sigma  )$ is a one-hot encoding of
+%% the parameter settings of $\sigma $ (see Tbl.~\ref{policyOutput})
+%% and $\phi_{\text{spec}}(S)$ extracts a few simple features of the trace set $S$;
+%% see supplement for details.
 
@@
 We compare synthesis times for our learned search policy
-with three alternatives:
+with 4 alternatives:
  \emph{Sketch}, which poses the
  entire problem wholesale to the Sketch program synthesizer;
- a DeepCoder--style model, \emph{DC}, which learns to predict which program components (loops, reflections)
+ \emph{DC}, a DeepCoder--style model that learns to predict which program components (loops, reflections)
  are likely to be useful~\cite{BalGauBroetal16};
+ \emph{End--to-End},
+ which trains a recurrent neural network to regress directly from images to programs;
 and an \emph{Oracle},
@@
   \\\bottomrule
-  \end{tabular}
+  \end{tabular}\vspace{-0.5cm}
   \end{table}
@@
       Median \\search time
-      \end{tabular}&Timeouts\\\midrule
+    \end{tabular}&\begin{tabular}{c}
+      Timeouts\\(1 hr)
+      \end{tabular}\\\midrule
     Sketch&274 sec&27\%\\
     DC&187 sec&2\%\\
+    End--to--End&63 sec&94\%\\
     Oracle&6 sec&2\%\\
-    Learned policy&28 sec&2\%\\\bottomrule 
-    \end{tabular}.  
+    Ours&28 sec&2\%\\\bottomrule 
+    \end{tabular}
   \end{minipage}\hfill%
@@
     \caption{Time to synthesize a minimum cost program.
-Sketch: out-of-the-box performance of the Sketch~\citep{solar2008program} program synthesizer.
-DC: Baseline that predicts program components, trained like~\cite{BalGauBroetal16}.
-Oracle:  upper bounds  the performance of any search policy.
-Learned policy: ours  %% $\infty = $ timeout.
+Sketch: out-of-the-box performance of Sketch~\citep{solar2008program}.
+DC: Deep--Coder style baseline that predicts program components, trained like~\cite{BalGauBroetal16}.
+End--to--End: neural network trained to regress directly from images to programs.
+Oracle:  upper bounds  the performance of any bias--optimal search policy.
+Ours:  %% $\infty = $ timeout.
 Red dashed line is median time.
@@
   \end{minipage}
+  \vspace{-0.5cm}
 \end{figure}
@@
 \section{Applications of graphics program synthesis}\label{applicationsSection}
-Why synthesize a graphics program,
-if the spec already suffices to recover the objects in an image?
-Within our domain of hand-drawn figures, graphics program synthesis has several uses:
+%% Why synthesize a graphics program,
+%% if the spec already suffices to recover the objects in an image?
+%% Within our domain of hand-drawn figures, graphics program synthesis has several uses:
 
@@
 
-In the computer graphics literature, there have been other systems which convert sketches into procedural representations.
-One uses a convolutional network to match a sketch to the output of a parametric 3D modeling system~\citep{huang2017shape}.
-Another uses convolutional networks to support sketch-based instantiation of procedural primitives within an interactive architectural modeling system~\citep{Nishida:2016:ISU:2897824.2925951}.
-Both systems focus on inferring fixed-dimensional parameter vectors.
-In contrast, we seek to automatically infer a structured, programmatic representation of a sketch which captures higher-level visual patterns.
-
-\textbf{Hand-drawn sketches:} Prior work has also applied sketch-based program synthesis to authoring graphics programs.
-Sketch-n-Sketch is a bi-directional editing system in which direct manipulations to a program's output automatically propagate to the program source code~\citep{Hempel:2016:SSP:2984511.2984575}.
-We see this work as complementary to our own: programs produced by our method could be provided to a Sketch-n-Sketch-like system as a starting point for further editing.
-
+\textbf{Hand-drawn sketches:} Sketch-n-Sketch is a bi-directional editing system where direct manipulations to a program's output automatically propagate to the program source code~\citep{Hempel:2016:SSP:2984511.2984575}.
+This work  compliments our own: programs produced by our method could be provided to a Sketch-n-Sketch-like system as a starting point for further editing.
+Other systems in the computer graphics literature convert sketches to procedural representations, using a convolutional network to match a sketch to the output of a parametric 3D modeling system in~\citep{huang2017shape} or supporting interactive sketch-based instantiation of procedural primitives in~\citep{Nishida:2016:ISU:2897824.2925951}.
+In contrast, we seek to automatically infer a programmatic representation capturing higher-level visual patterns.
 The CogSketch system~\citep{forbus2011cogsketch} also aims to have a high-level understanding of hand-drawn figures.
-Their primary goal is cognitive modeling (they apply their system to solving IQ-test style visual reasoning problems), whereas we are interested in building an automated AI application (e.g.
+Their  goal is cognitive modeling, whereas we are interested in building an automated AI application.% (e.g.
 in our system the user need not annotate which strokes correspond to which shapes; our neural network produces something equivalent to the annotations).

### 2018-05-15 supplement.tex
supplement stuff

@@
 
-\section{Learning a bias optimal policy}
+\section{Learning a search policy}
+\subsection{Modeling}\label{searchPolicyModel}
 Recall from the main paper that our goal is to estimate the policy minimizing the following loss:
@@
   \end{align*}
+where the meaning of ``incremental'' is described in the next section.
+\subsection{Incremental Solving}
+Rather than give the sketch program synthesizer the entire spec all at once,
+we can instead give it subsets of the spec (subsets of the objects in the image)
+and ask it to synthesize a program for each subset.
+We then concatenate the resulting programs from each subset to get a program that explains the entire image,
+and we call this strategy ``incremental solving''.
+Incremental solving is not guaranteed to be faster,
+nor is it guaranteed to find a minimum cost program.
+Thus we allow the search policy to decide
+what fraction of our search time should be allocated to this incremental approach to program synthesis.
+Concretely, we partitioned a spec into its constituent lines, circles, and rectangles.
+\subsection{Baseline comparisons}
+In addition to the end-to-end baseline,
+we compared with a DeepCoder-style baseline (main paper, Section 3.1).
+DeepCoder (DC)~\cite{BalGauBroetal16}
+is an approach for learning to speed up program synthesizers.
+DC models are neural networks that
+predict, starting from a spec,
+the probability of a DSL component being in a minimal-cost program satisfying the spec.
+Writing $\text{DC}(S)$ for the distribution predicted by the neural network,
+DC is trained to maximize  the following objective:
+\begin{equation}
+  \expect_{S\sim\mathcal{D}}\left[\min_{p\in \text{\textsc{Best}}(S)} \sum_{x\in \text{DSL}} \log \left(\indicator\left[x\in p \right] \text{DC}(S)_x + \indicator\left[x\notin p \right] (1 - \text{DC}(S)_x)\right)
+    \right]
+\end{equation}
+where $x$ ranges over DSL components and $\text{DC}(S)_x\in \left[0,1 \right]$  is the probability predicted by the DC model for component $x$ for spec $S$.
 
+We provided our DC model with the same features given to our bias optimal search policy ($\phi_{spec}$ in section~\ref{searchPolicyModel}), and trained using the same 20-fold cross validation splits.
+To evaluate the DC baseline on held out data,
+we used the \emph{Sort-and-Add} policy described in the DeepCoder paper\cite{BalGauBroetal16}.
+
+Figure~\ref{policyEvaluation} shows histograms of the synthesis time for our model and baselines.
+
+\begin{figure}
+  \includegraphics[width = \textwidth]{figures/policyComparison_basic_DC+bias_20.png}
+    \caption{Time to synthesize a minimum cost program.
+Sketch: out-of-the-box performance of Sketch~\citep{solar2008program}.
+DC: Deep--Coder style baseline that predicts program components, trained like~\cite{BalGauBroetal16}.
+Oracle:  upper bounds  the performance of any bias--optimal search policy.
+$\infty = $ timeout.
+Red dashed line is median time.}
+  \end{figure}
 \pagebreak

### 2018-05-15 nips_2018.tex
supplement stuff
nicer figures and various edits

@@
 How could we build an agent with similar visual inference abilities?
-Here we
-cast this problem as program learning,
+As a small step in this direction, 
+we cast this problem as program learning,
 and take as our goal to learn high--level
@@
 (Fig.~\ref{firstPageExamples}),
-and capture high-level features of a drawing like
+and capture high-level features like %of a drawing like
 symmetry, repetition, and reuse of structure.
@@
  We refer to this set of drawing commands as a \textbf{specification (spec)} because it specifies what the graphics program drew while lacking the high-level structure determining how the program decided to draw it.
- We infer the spec from an image using stochastic search (Sequential Monte Carlo)
+ We infer a spec from an image using stochastic search (Sequential Monte Carlo)
  and infer a program from a spec using  constraint-based program synthesis~\citep{solar2008program} --
@@
  in the spirit of ``amortized inference''~\cite{paige2016inference},
- using a neural network to amortize the cost of inferring specs from images and using
+ training a neural network to amortize the cost of inferring specs from images and using
  a variant of Bias--Optimal Search~\cite{schmidhuber2004optimal}
@@
   \node[ thick,anchor = west,inner sep=0pt,label={[yshift = 0.3cm]{\small \begin{tabular}{c}
-          Image\\
-          (Observed)
+          \textbf{Image}\\
+          \textbf{(Observed)}
   \end{tabular}}}](observation) at (0,0) {\includegraphics[width = 1.5cm]{figures/expert-39-trimmed.png}};
@@
     \node(trace)[draw,thin,fit = (traceImage) (traceSource), label = above:{{\small \begin{tabular}{c}
-            Spec/Drawing Commands\\
-            (Latent)
+            \textbf{Spec/Drawing Commands}\\
+            \textbf{(Latent)}
     \end{tabular}}}] {};
@@
     \node[draw, thick,anchor = west,inner sep=2pt,label=above:{\small \begin{tabular}{c}
-          Program\\
-          (Latent)
+          \textbf{Program}\\
+          \textbf{(Latent)}
     \end{tabular}}](program) at (7.7,0) {
@@
 
-    \draw[->, ultra thick] (trace.west) -- node[fill = white,rotate = -90] {{\small Rendering}} (observation.east);
-    \draw[->, very thick, red] ([xshift = -5]observation.south) to[out = -30,in = -150] node[midway,yshift = -6]{{\small Learning + Stochastic search}} ([xshift = -15]trace.south);
-    \draw[->, ultra thick] (program.west) -- node[fill = white,rotate = -90] {{\small Execution}} (trace.east);
-    \draw[->, thick, red, very thick] ([xshift = 10]trace.south) to[out = -10,in = -170] node[midway,yshift = -6]{{\small Learning + Program synthesis}} ([xshift = 10]program.south);
+    \draw[->, ultra thick] ([yshift=10]trace.west) to[out = 150,in = 30] node[midway,yshift = 6]{{\small Rendering}} ([xshift=5,yshift=10]observation.east); % -- node[fill = white,rotate = -90] {{\small Rendering}}
+    \draw[->, very thick, red] ([yshift = -15,xshift=3]observation.east) to[out = -30,in = -150] node[midway,yshift = -12,xshift=5]{{\small \begin{tabular}{l}
+          Learning + \\Stochastic search
+    \end{tabular}}} ([yshift = -15]trace.west);
+    \draw[->, ultra thick] ([yshift=10]program.west) to[out = 150,in = 30] node[midway,yshift = 6] {{\small Execution}} ([yshift=10]trace.east);
+    \draw[->, very thick, red] ([yshift = -15,xshift=0]trace.east) to[out = -30,in = -150] node[midway,yshift = -12,xshift=9]{{\small \begin{tabular}{l}
+          Learning + \\Program synthesis
+    \end{tabular}}} ([yshift = -15]program.west);
+
+%    \draw[->, thick, red, very thick] ([xshift = 10]trace.south) to[out = -10,in = -170] node[midway,yshift = -6]{{\small Learning + Program synthesis}} ([xshift = 10]program.south);
 %    \draw[->, thick, red] (program.east) to[out = 80,in = 180] (errors.west);
@@
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-    ([yshift = -15,xshift = -130]trace.south) -- node[below = 6pt] {{\small Section~\ref{neuralNetworkSection}: Image$\to$Spec}} ([yshift = -15,xshift = -5]trace.south);
+    ([yshift = -11,xshift = -130]trace.south) -- node[below = 6pt] {{\small Section~\ref{neuralNetworkSection}: Image$\to$Spec}} ([yshift = -11,xshift = -5]trace.south);
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-    ([xshift = 5,yshift = -15]trace.south) -- node[below = 6pt] {{\small Section~\ref{programSynthesisSection}: Spec$\to$Program}} ([xshift = 170,yshift = -15]trace.south);
+    ([xshift = 5,yshift = -11]trace.south) -- node[below = 6pt] {{\small Section~\ref{programSynthesisSection}: Spec$\to$Program}} ([xshift = 170,yshift = -11]trace.south);
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-([xshift = 180,yshift = -15]trace.south) -- node[below = 6pt] {{\small Section~\ref{applicationsSection}: Applications}} ([xshift = 250,yshift = -15]trace.south);
+([xshift = 180,yshift = -11]trace.south) -- node[below = 6pt] {{\small Section~\ref{applicationsSection}: Applications}} ([xshift = 255,yshift = -11]trace.south);
   \end{tikzpicture}
-  \caption{Black arrows: Top--down generative model; Program$\to$Spec$\to$Image. Red arrows: Bottom--up inference procedure.}\label{roadmap}
+  \caption{Black arrows: Top--down generative model; Program$\to$Spec$\to$Image.
+{\color{red}Red} arrows: Bottom--up inference procedure.
+\textbf{Bold:} Random variables (image/spec/program)}\label{roadmap}
  \end{figure}
 
- The new contributions of this work are (1) a working model that can infer high-level symbolic programs from raw perceptual input, and (2) a technique for using learning to amortizing the cost of program synthesis, described in Section~\ref{learningASearchPolicy}.
+ The new contributions of this work are (1) a working model that can infer high-level symbolic programs from perceptual input, and (2) a technique for using learning to amortize the cost of program synthesis, described in Section~\ref{learningASearchPolicy}.
 
@@
 
-    \caption{Near misses. Rightmost: illusory contours (note: no SMC)}\label{drawingFailures}
+    \caption{Near misses. Rightmost: illusory contours (note: no SMC in rightmost)}\label{drawingFailures}
   \end{minipage}
@@
 Although the spec describes the contents
-of a scene, it does not encode higher-level features of the image
+of a scene, it does not encode higher-level features of an image
 such as repeated motifs or symmetries, which are more naturally captured by a graphics program.
@@
 \begin{table}[t]
-  \caption{Drawings (left), their specs (middle left), and programs synthesized from these specs (middle right).
+  \caption{Drawings (left), their specs (middle left), and programs synthesized from those specs (middle right).
 Compared to the specs the programs are more compressive (right: programs have fewer lines than specs) and automatically group together related drawing commands.
-Note nested loops  and conditionals in the Ising model, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
+Note the nested loops  and conditionals in the Ising model, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
 %  \vspace{-0.6cm}
@@
 Given a search policy, what is the best way of using it to quickly find minimum cost programs?
-We use a bias-optimal search algorithm~\citep{schmidhuber2004optimal}:
+We use a bias-optimal search algorithm (c.f. Schmidhuber 2004~\citep{schmidhuber2004optimal}):
 
@@
 reranks the Top-$k$  by  the prior probability of their programs.
-The prior probability of a program is learned by picking the prior maximizing
+The prior probability of a program is learned by optimizing the parameters of the prior so as to maximize
 the likelihood of the ground truth specs;
@@
 systematically compares constraint-based program synthesis techniques
-against gradient-based search techniques, like those used to train
+against gradient-based search methods, like those used to train
 Differentiable Neural Computers~\citep{graves2016hybrid}.  The TerpreT
@@
 In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the code.
-More generally, we believe the problem of inferring visual programs is a promising direction for machine perception.
+More generally, we believe the problem of inferring visual programs is a promising direction for research in machine perception.
 

### 2018-09-07 nips_2018.tex
poster

@@
   primitives that explain an image. These drawing primitives are a
-  specification (spec) of what the graphics program needs to draw.
-  We learn a model that uses program synthesis techniques to
-  recover a graphics program from that spec. These programs have
-  constructs like variable bindings, iterative loops, or simple kinds
-  of conditionals. With a graphics program in hand, we can correct
-  errors made by the deep network and extrapolate drawings.  %% Taken
-  %% together these results are a step towards agents that induce useful,
-  %% human-readable programs from perceptual input.
+  specification (spec) of what the graphics program needs to draw.  We
+  learn a model that uses program synthesis techniques to recover a
+  graphics program from that spec. These programs have constructs like
+  variable bindings, iterative loops, or simple kinds of
+  conditionals. With a graphics program in hand, we can correct errors
+  made by the deep network and extrapolate drawings.
 \end{abstract}
@@
 \begin{wrapfigure}{r}{8cm}
-  \vspace{-0.25cm}
+  \vspace{0.4cm}
   \centering
@@
 Neither SMC nor the neural network are sufficient on their own.
-\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}\vspace{-1cm}
+\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}\vspace{-1.5cm}
 \end{wrapfigure}
@@
 DC: Deep--Coder style baseline that predicts program components, trained like~\cite{BalGauBroetal16}.
-End--to--End: neural network trained to regress directly from images to programs.
+End--to--End: neural net trained to regress directly from images to programs, which fails to find valid programs 94\% of the time.
 Oracle:  upper bounds  the performance of any bias--optimal search policy.

### 2018-09-07 pipeline.tex
poster

--- 2018-09-07 nips_2018.tex
@@
-\documentclass{article}
+\documentclass[crop,tikz]{standalone}
 
-% if you need to pass options to natbib, use, e.g.:
-% \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading nips_2018
-
-% ready for submission
-\usepackage{nips_2018}
-
-% to compile a preprint version, e.g., for submission to arXiv, add
-% add the [preprint] option:
-% \usepackage[preprint]{nips_2018}
-
-% to compile a camera-ready version, add the [final] option, e.g.:
-% \usepackage[final]{nips_2018}
-
-% to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{nips_2018}
-
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{hyperref}       % hyperlinks
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
-\usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
-\usepackage{dsfont}
 \usepackage{verbatimbox}
@@
 \usepackage{graphicx} % more modern
-%\usepackage{epsfig} % less modern
-%\usepackage{subfig} 
-\usepackage{fancyvrb}
-
-\usepackage{caption}
-\usepackage{subcaption}
-
-\fvset{fontsize=\footnotesize}
-
-\usepackage{multirow}
-\usepackage{array}
-
-\usepackage{amssymb}
-\usepackage{listings}
-\usepackage{wrapfig}
-\usepackage{tabularx}
-
-\usepackage{verbatim}
- \usepackage{booktabs}
- % For algorithms
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{tikz}
 \usetikzlibrary{fit}
@@
 
-% As of 2011, we use the hyperref package to produce hyperlinks in the
-% resulting PDF.  If this breaks your system, please commend out the
-% following usepackage line and replace \usepackage{icml2016} with
-% \usepackage[nohyperref]{icml2016} above.
-\usepackage{amsmath}
-\usepackage{hyperref}
-\DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays
-% \DeclareMathOperator{\argmin}{argmin} % no space, limits underneath in displays
-\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays
-% \DeclareMathOperator{\argmax}{argmax} % no space, limits underneath in displays
+\begin{document}
 
-\newcommand{\expect}{\mathds{E}} %{{\rm I\kern-.3em E}}
-\newcommand{\probability}{\mathds{P}} %{{\rm I\kern-.3em P}}
-\newcommand{\indicator}{\mathds{1}} %{{\rm I\kern-.3em P}}
-
-\newcommand{\remark}[1]{\textcolor{red}{[#1]}}
-\newcommand{\exampleImageSize}{2cm}
-
-\usepackage{amsthm}
-
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{experiment}{Experiment} %[section]
-
-\title{Learning to Infer Graphics Programs from Hand-Drawn Images}
-
-% The \author macro works with any number of authors. There are two
-% commands used to separate the names and addresses of multiple
-% authors: \And and \AND.
-%
-% Using \And between authors leaves it to LaTeX to determine where to
-% break the lines. Using \AND forces a line break at that point. So,
-% if LaTeX puts 3 of 4 authors names on the first line, and the last
-% on the second line, try using \AND instead of \And before the third
-% author name.
-
-\author{Kevin Ellis\\
-  MIT\\
-  \texttt{ellisk@mit.edu} \\
-  \And
-  Daniel Ritchie\\
-Brown University\\
- \texttt{daniel\_ritchie@brown.edu} \\
- \And
- Armando Solar-Lezama\\
- MIT\\
-\texttt{asolar@csail.mit.edu} \\
-\And
-Joshua B. Tenenbaum \\
-MIT\\
-\texttt{jbt@mit.edu}
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
-  %% \And
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
-  %% \And
-  %% Coauthor \\
-  %% Affiliation \\
-  %% Address \\
-  %% \texttt{email} \\
-}
-
-\begin{document}
-% \nipsfinalcopy is no longer used
-
-\maketitle
-
-\begin{abstract}
-  We introduce a model that learns to convert simple hand drawings
-  into graphics programs written in a subset of \LaTeX.~The model
-  combines techniques from deep learning and program synthesis.  We
-  learn a convolutional neural network that proposes plausible drawing
-  primitives that explain an image. These drawing primitives are a
-  specification (spec) of what the graphics program needs to draw.  We
-  learn a model that uses program synthesis techniques to recover a
-  graphics program from that spec. These programs have constructs like
-  variable bindings, iterative loops, or simple kinds of
-  conditionals. With a graphics program in hand, we can correct errors
-  made by the deep network and extrapolate drawings.
-\end{abstract}
-
-\section{Introduction}
-
-Human vision is rich -- we infer shape, objects, parts of objects,
-and relations between objects -- and vision is also abstract:
-we can perceive the radial symmetry of a spiral staircase,
-the iterated repetition in the Ising model,
-see the forest for the trees, and also the recursion within the trees.
-How could we build an agent with similar visual inference abilities?
-As a small step in this direction, 
-we cast this problem as program learning,
-and take as our goal to learn high--level
-graphics programs from simple 2D drawings.
-The graphics programs we consider make figures like those found in machine learning papers
-(Fig.~\ref{firstPageExamples}),
-and capture high-level features like %of a drawing like
-symmetry, repetition, and reuse of structure.
-
-%% Vision as a kind of ``inverse graphics'' is an idea that is both intuitive and old,
-%% with many diverse recent takes on this framing -- neural network approaches like Attend--Infer--Repeat or Capsule Nets,
-%% or more structured approaches leveraging probabilistic programming~\cite{}.
-%% This vision--as--inverse--graphics metaphor addresses the important problem of
-%% inferring, from an image, the identities and poses of
-%% objects. But visual perception is richer than object identity and pose:
-
- %% How can an agent convert noisy, high-dimensional perceptual input
- %% to a symbolic, abstract object, such as a computer program?  Here we
- %% consider this problem within a graphics program synthesis domain.  We
- %% develop an approach for converting  hand
- %% drawings into executable source code for drawing the original image.
- %% The graphics programs in our domain draw simple figures like those found in
- %% machine learning papers
-% (see Fig.~\ref{firstPageExamples}a)
-\begin{myverbbox}[\small]{\firstFirstPageCode}
-for (i < 3)
- rectangle(3*i,-2*i+4,
-           3*i+2,6)
- for (j < i + 1)
-  circle(3*i+1,-2*j+5)
-\end{myverbbox}
-\begin{myverbbox}[\small]{\secondFirstPageCode}
-reflect(y=8)
- for(i<3)
-  if(i>0)
-   rectangle(3*i-1,2,3*i,3)
-  circle(3*i+1,3*i+1)
-\end{myverbbox}
-
- \begin{figure}[H]%\vspace{-0.7cm}
-  \begin{minipage}[b]{0.35\linewidth}  \centering
-\begin{tabular}{ll}
-  \includegraphics[width = \exampleImageSize]{figures/expert-60.png}&
-%  \includegraphics[width = \exampleImageSize]{figures/expert-5.png}&
-%    \includegraphics[width = \exampleImageSize]{figures/expert-17.png}&
-    \includegraphics[width = \exampleImageSize]{figures/expert-58.png}\\
-  \includegraphics[width = \exampleImageSize]{figures/60.png}&
-%  \includegraphics[width = \exampleImageSize]{figures/5.png}&
-%    \includegraphics[width = \exampleImageSize]{figures/17.png}&
-    \includegraphics[width = \exampleImageSize]{figures/58.png}
-\end{tabular}
-\subcaption{}
-  \end{minipage}
-  %
-  \begin{minipage}[b]{0.6\linewidth}\centering
   \begin{tikzpicture}
-      \node(picture1) at (0,-1) {\includegraphics[height = 1.5cm]{figures/expert-31.png}};
-      \node(picture2) [below = 0.3cm of picture1] {\includegraphics[height = 1.5cm]{figures/expert-72-trim.png}};
-      \node[right=1cm of picture1] (c1) {\fbox{\firstFirstPageCode}};
-      \node[right=1cm of picture2] (c2) {\fbox{\secondFirstPageCode}};
-      \draw[very thick,->] (picture1.east)  -- (c1.west);
-      \draw[very thick,->] (picture2.east)  -- (c2.west);
-    \end{tikzpicture}
-    \subcaption{}
-  \end{minipage}
-  \caption{(a): Model learns to convert hand drawings (top) into \LaTeX~(rendered below). (b) Learns to synthesize high-level graphics program from hand drawing.}\label{firstPageExamples}
-\end{figure}
-
- The key observation behind our work is that going from pixels to programs involves two distinct steps, each requiring different technical approaches.
-The first step involves inferring what objects make up an image -- for diagrams, these are things like as rectangles, lines and arrows.
-The second step involves identifying the higher-level visual concepts that describe how the objects were drawn.
-In Fig.
-1(b), it means identifying a pattern in how the circles and rectangles are being drawn that is best described with two nested loops, and which can easily be extrapolated to a bigger diagram.
-
-This two-step factoring can be framed as probabilistic inference in a generative model where a latent program
- is executed to produce a set of drawing commands,
- which are then rendered to form an image (Fig.~\ref{roadmap}).
- We refer to this set of drawing commands as a \textbf{specification (spec)} because it specifies what the graphics program drew while lacking the high-level structure determining how the program decided to draw it.
- We infer a spec from an image using stochastic search (Sequential Monte Carlo)
- and infer a program from a spec using  constraint-based program synthesis~\citep{solar2008program} --
- synthesizing structures like symmetries, loops, or conditionals.
- In practice, both stochastic search and program synthesis are
- prohibitively slow,
- and so we learn models that accelerate inference for both programs and specs,
- in the spirit of ``amortized inference''~\cite{paige2016inference},
- training a neural network to amortize the cost of inferring specs from images and using
- a variant of Bias--Optimal Search~\cite{schmidhuber2004optimal}
- to amortize the cost of synthesizing programs from specs.
- \begin{figure}[h]
-  \centering\begin{tikzpicture}
   \node[ thick,anchor = west,inner sep=0pt,label={[yshift = 0.3cm]{\small \begin{tabular}{c}
@@
     \end{lstlisting}};
-    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Extrapolation}](extrapolate) at (12,0.5) {\includegraphics[width = 1.3cm]{figures/39-extrapolated.png}};
+    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Extrapolation}](extrapolate) at (12,1) {\includegraphics[width = 1.3cm]{figures/39-extrapolated.png}};
 %    \node[ultra thick,anchor = west,inner sep=0pt,label=below:{\small Similarity}](similarity) at (11.3,0) {\includegraphics[width = 1cm]{figures/expert-38-trim.png}};
-    \node[ultra thick,anchor = west,text width = 1.3cm,inner sep=0pt](errors) at (12.1,-1.2) {\small Error correction};
+    \node[ultra thick,anchor = west,inner sep=0pt](errors) at (12.1,-1) {\begin{tabular}{l}
+        \small Error \\\small correction
+    \end{tabular}};
 
@@
 %    \draw[->, thick, red, very thick] ([xshift = 10]trace.south) to[out = -10,in = -170] node[midway,yshift = -6]{{\small Learning + Program synthesis}} ([xshift = 10]program.south);
-%    \draw[->, thick, red] (program.east) to[out = 80,in = 180] (errors.west);
+    \draw[->, very thick, red] (program.east) to[out = -60,in = 180] (errors.west);
 %    \draw[->, thick] (program.east) to[out = 40,in = -230] (similarity.west);
@@
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-    ([yshift = -11,xshift = -130]trace.south) -- node[below = 6pt] {{\small Section~\ref{neuralNetworkSection}: Image$\to$Spec}} ([yshift = -11,xshift = -5]trace.south);
+    ([yshift = -11,xshift = -130]trace.south) -- node[below = 6pt] {{\small  Image$\to$Spec}} ([yshift = -11,xshift = -5]trace.south);
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-    ([xshift = 5,yshift = -11]trace.south) -- node[below = 6pt] {{\small Section~\ref{programSynthesisSection}: Spec$\to$Program}} ([xshift = 170,yshift = -11]trace.south);
+    ([xshift = 5,yshift = -11]trace.south) -- node[below = 6pt] {{\small  Spec$\to$Program}} ([xshift = 170,yshift = -11]trace.south);
     \draw[decoration = {brace,mirror,raise = 5pt},decorate,thick]
-([xshift = 180,yshift = -11]trace.south) -- node[below = 6pt] {{\small Section~\ref{applicationsSection}: Applications}} ([xshift = 255,yshift = -11]trace.south);
+([xshift = 180,yshift = -11]trace.south) -- node[below = 6pt] {{\small  Applications}} ([xshift = 255,yshift = -11]trace.south);
   \end{tikzpicture}
-  \caption{Black arrows: Top--down generative model; Program$\to$Spec$\to$Image.
-{\color{red}Red} arrows: Bottom--up inference procedure.
-\textbf{Bold:} Random variables (image/spec/program)}\label{roadmap}
- \end{figure}
-
- The new contributions of this work are (1) a working model that can infer high-level symbolic programs from perceptual input, and (2) a technique for using learning to amortize the cost of program synthesis, described in Section~\ref{learningASearchPolicy}.
-
-\section{Neural architecture for inferring specs}\label{neuralNetworkSection}
-
-We developed a deep network architecture for efficiently inferring a
-spec, $S$, from a hand-drawn image, $I$.
-Our model combines ideas from
-Neurally-Guided Procedural Models~\citep{ritchie2016neurally}
-and Attend-Infer-Repeat~\citep{eslami1603attend}, but
-we wish to emphasize
-that one could use
-many different approaches from the computer vision toolkit to
-parse an image in to primitive drawing commands  (in our terminology, a ``spec'')~\cite{nsd}.
-Our network constructs the
-spec one drawing command at a time, conditioned on what it has drawn so far (Fig.~\ref{architecture}).
-%When predicting the next drawing
-%command, the network takes as input the target image $I$ as well as
-%the rendered output of previous drawing commands.
-%Intuitively, the network looks at the image it wants to explain, as well as what it has already drawn.
-It then decides either to stop drawing or proposes another drawing command to add to the trace set; if it decides to continue drawing, the predicted primitive is rendered to its ``canvas'' and the process repeats.
-We first
-pass a $256\times 256$ target image and a rendering of the drawing commands so
-far (encoded as a two-channel image) to a convolutional network. Given
-the features extracted by the convnet, a multilayer perceptron then
-predicts a distribution over the next drawing command to execute
-(see Tbl.~\ref{drawingCommandTable}).
-%We predict the drawing command token-by-token,
-%\footnote{Tokens are atomic symbols in the programming language  -- so the model is \emph{not} predicting lines of code character-by-character, but instead the model knows about the syntactic structure of primitive drawing commands}
-%%   conditioning each token both on the image
-%% features and on the previously generated tokens. 
-We also use a
-differentiable attention mechanism (Spatial Transformer
-Networks:~\cite{jaderberg2015spatial}) to let the model attend to
-different regions of the image while predicting drawing commands.
-%In Fig.~\ref{architecture} the network first decided to emit the \verb|circle| token
-%conditioned on the image features, then it emitted the $x$ coordinate of
-%the circle conditioned on the image features and the \verb|circle|
-%token, and finally it predicted the $y$ coordinate of the circle
-%conditioned on the image features, the \verb|circle| token, and the
-%$x$ coordinate.
-We currently constrain
-coordinates to lie on a discrete $16\times 16$ grid,
-but the grid could be made arbitrarily fine.  %% See supplement for the full details
-%% of the architecture, which we implemented in
-%% Tensorflow~\citep{tensorflow2015-whitepaper}.
-%% \remark{There are some more details that are important to provide
-%%   about this architecture in the supplement: the
-%%   functional form(s) of the probability distributions over tokens, the
-%%   network layer sizes, which MLPs share parameters, etc.}
-
-\tikzset{>=latex}
-\begin{figure}[t]
-  \begin{minipage}[c]{0.65\textwidth}
-    \begin{tikzpicture}
-  \node[draw,blue,ultra thick,anchor = west,inner sep=0pt,label=below:Target image: $I$](observation) at (0,-1) {\includegraphics[width = 2cm]{figures/expert-18.png}};
-  \node[draw,blue,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(S)$] (canvas) at (0,-4) {};
-  \draw[lightgray,ultra thin,step = 0.125] ([xshift = 0.5,yshift = 0.5]canvas.south west) grid ([xshift = -0.5,yshift = -0.5]canvas.north east);
-  % draw partial image on canvas
-  \draw (0.375cm,-3.25cm) circle (0.125cm);
-  \draw (0.625cm,-3.625) circle (0.125cm);
-  \draw (0.75cm,-3.375) circle (0.125cm);
-
-  \node[draw,ultra thick,anchor = west,inner sep=0pt,minimum width = 1cm,minimum height = 2cm] (CNN) at (4,-2.5) {CNN};
-  \node[inner sep = 0pt](tensorProduct) at ([xshift = -1.3cm]CNN.west) {$\bigoplus$};
-
-  \node[draw,ultra thick,inner sep=0pt] (features) at ([xshift = 0.01cm]CNN.east) {};
-
-  \node[draw,ultra thick,minimum size = 1cm](c1) at ([xshift = 1cm]features) {MLP};
-  \node(l1) at ([yshift = -1.5cm]c1.south) {\verb|circle(|};
-  \node[draw,ultra thick,minimum size = 1cm](a2) at ([xshift = 1cm,yshift = 1.5cm]c1.east) {STN};
-  \node[draw,ultra thick,minimum size = 1cm](c2) at ([xshift = 1cm]c1.east) {MLP};
-  \draw[->,ultra thick] (a2.south) -- (c2.north);
-  \draw[->,ultra thick,red] (c1.south) -- (l1.north);
-  \node(l2) at ([yshift = -1.5cm]c2.south) {\verb|X=7,|};
-  \draw[->,ultra thick,red] (c2.south) -- (l2.north);
-  \node[draw,ultra thick,minimum size = 1cm](a3) at ([xshift = 1cm,yshift = 1.5cm]c2.east) {STN};
-  \node[draw,ultra thick,minimum size = 1cm](c3) at ([xshift = 1cm]c2.east) {MLP};
-
-  \draw[->,ultra thick] (a3.south) -- (c3.north);
-  \node(l3) at ([yshift = -1.5cm]c3.south) {\verb|Y=12)|};
-  \draw[->,ultra thick,red] (c3.south) -- (l3.north);
-
-  \draw[->,ultra thick] (features) -- (c1.west);
-  \draw[->,ultra thick] (features) to[out = 45,in = 160] (a2.north);
-  \draw[->,ultra thick] (features) to[out = 80,in = 140] (a3.north);
-  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c2.west);
-  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- ([yshift = -0.2cm]c3.west);
-  \draw[->,ultra thick] ([xshift = 0.25cm]l2.north) -- ([yshift = -0.25cm]c3.west);
-
-  \node(next)[draw,very thick,fit = (l1) (l2) (l3), dashed, label = below:{Next drawing command}] {};
-
-  \draw[-{>[scale = 1.5]},very thick,dashed] (next.west) -- ([yshift = -0.2cm]canvas.east) node [midway, below, sloped] (TextNode) {Renderer}; %: \LaTeX~Ti\emph{k}Z};
-
-  \draw[->,ultra thick] (canvas.east) -- (tensorProduct.south);%[yshift = -0.5cm]CNN.west);
-  \draw[->,ultra thick] (observation.east) -- (tensorProduct.north);%([yshift = 0.5cm]CNN.west);
-  \draw[->,ultra thick] (tensorProduct.east)  -- node[fill = white,rotate = 90] {{\tiny $256\times 256\times 2$}}  (CNN.west);
-  \draw[-,ultra thick] (CNN.east) -- %node[fill = white,rotate = 90] {{\tiny $16\times 16\times 10$}}
-  (features);
-%  \draw[]
-
-%  \node at (canvas.x,canvas.y) {Canvas};
-\end{tikzpicture}
-  \end{minipage}  \hfill%
-  \begin{minipage}[c]{0.2\textwidth}
-    \caption{Neural architecture for inferring specs from images.
-\textcolor{blue}{Blue}: network inputs.
-Black: network operations.
-\textcolor{red}{Red}: draws from a multinomial.
-\texttt{Typewriter font}: network outputs.
-Renders on a $16\times 16$ grid, shown in \textcolor{gray}{gray}.
-STN: differentiable attention mechanism~\citep{jaderberg2015spatial}.}  \label{architecture}
-    \end{minipage}
-\end{figure}
-
-\begin{table}[h]
-  \caption{Primitive drawing commands currently supported by our model.}
-\label{drawingCommandTable}
-\begin{tabular}{ll}\toprule
-  \begin{tabular}{l}
-    \verb|circle|$(x,y)$
-  \end{tabular}& \begin{tabular}{l}
-    Circle at $(x,y)$
-    \end{tabular}\\
-  \begin{tabular}{l}
-    \verb|rectangle|$(x_1,y_1,x_2,y_2)$
-  \end{tabular}&\begin{tabular}{l}
-    Rectangle with corners at $(x_1,y_1)$ \& $(x_2,y_2)$
-    \end{tabular}\\
-  \begin{tabular}{l}
-    \verb|line|$(x_1,y_1,x_2,y_2,$\\
-    \hspace{1cm}$\text{arrow}\in\{0,1\},\text{dashed}\in\{0,1\})$
-  \end{tabular}&\begin{tabular}{l}
-    Line from $(x_1,y_1)$ to  $(x_2,y_2)$,\\\hspace{1cm}optionally with an arrow and/or dashed
-    \end{tabular}\\
-  \begin{tabular}{l}
-    \verb|STOP|
-  \end{tabular}&\begin{tabular}{l}
-    Finishes spec inference
-    \end{tabular}
-\\  \bottomrule
-\end{tabular}
-\end{table}
-
-%% For the model in Fig.~\ref{architecture}, the distribution over the next drawing command factorizes as:
-%% \begin{equation}
-%%   \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(T)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
-%% \end{equation}
-%% where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
-%% the target image, $T$ is a trace set, $\theta$ are the
-%% parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
-%% image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
-%% traces factorizes as:
-%% \begin{equation}
-%%   \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
-%% \end{equation}
-%% where $|T|$ is the length of trace set $T$, the subscripts
-%% on $T$ index drawing commands within the trace (so $T_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
-%% token is emitted by the network to signal that the trace set
-%% explains the image.
-We trained our network by sampling specs $S$ and target
-images $I$ for randomly generated scenes
-and maximizing $\probability_\theta[S|I]$,
-%Eq.~\ref{objective}
- the likelihood of $S$ given $I$, with respect to
-  model parameters $\theta$, by gradient ascent.
-We trained on $10^5$ scenes, which takes a day on an Nvidia TitanX GPU.
-
-%% Training does not require backpropagation across the sequence
-%% of drawing commands: drawing to the canvas `blocks' the gradients,
-%% effectively offloading memory to an external visual store.  
-%% This approach is like an autoregressive version of
-%% Attend-Infer-Repeat~\citep{eslami1603attend}, but critically, without a learned
-%%   recurrent memory state, e.g. an RNN.  We can do without an RNN
-%% because we learn from ground truth (image, trace) pairs.  This
-%% allows us to handle scenes with many objects without
-%% worrying about the conditioning of gradients as they propagate
-%% over long sequences, and makes training more straightforward: it
-%% is just maximum likelihood estimation of the model parameters.
-
-Our network can ``derender'' random synthetic images
-%those shown in Fig.~\ref{trainingData}.
-by doing a beam search to
-recover  specs maximizing $\probability_\theta[S|I]$. %% , where $\probability_\theta [\cdot |I]$ is
-%% the probability assigned by the network conditioned on image $I$
- But, if the network predicts an incorrect
-drawing command, it has no way of recovering from that error.  
-%To derender an image with $n$ objects, it must correctly predict $n$ commands -- so its probability of success will decrease exponentially in $n$, assuming it has a nonzero chance of making a mistake.
-For added robustness % as $n$ becomes large,
-we treat the
- network outputs as proposals for a Sequential Monte Carlo (SMC) sampling scheme~\citep{SMCBook}.
-%For the SMC sampler, we use pixel-wise distance as a surrogate for a likelihood function.
-Our SMC sampler draws samples
-from the distribution $\propto L(I|\text{render}(S))
-\probability_\theta[S|I]$, where $L(\cdot | \cdot)$
-%:\text{image}^2\to\mathbb{R}$
-uses the pixel-wise distance between two images as a proxy for a
-likelihood.
-Here, the network is learning a proposal distribution to amortize the cost of inverting a generative model (the renderer)~\citep{paige2016inference}.
-%% Unconventionally, the target distribution of the SMC sampler
-%% includes the likelihood under the proposal distribution.
-%% Intuitively, both the proposal
-%% distribution and the distance function offer complementary signals for
-%% whether a drawing command is correct.
-
-\textbf{Experiment 1: Figure~\ref{syntheticResults}.}
-  To evaluate which components of the model are necessary to parse complicated scenes,
-  we compared  the neural network
-  with SMC against the neural network by
-itself or SMC by itself.  Only the combination of the two passes a
-critical test of generalization: when trained on images with $\leq 12$
-objects, it successfully parses scenes with many more objects than the
-training data.
-We compare with a baseline that produces the spec in one shot by
-using the CNN to extract features of the input which are passed to an LSTM which finally predicts
-the spec token-by-token (LSTM in Fig.~\ref{syntheticResults}).
-This architecture is used in several successful neural models of image captioning (e.g.,~\cite{vinyals2015show}),
-but, for this domain, cannot parse cluttered scenes with many objects.
-\begin{wrapfigure}{r}{8cm}
-  \vspace{0.4cm}
-  \centering
-      \includegraphics[width = 7cm]{figures/averageNumberOfErrors.png}
-      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
-Model generalizes to scenes with many more objects.
-Neither SMC nor the neural network are sufficient on their own.
-\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}\vspace{-1.5cm}
-\end{wrapfigure}
-
-\subsection{Generalizing to real hand drawings}\label{generalizingTheHandDrawings}
-%% \begin{wrapfigure}{R}{6cm}
-%% \centering\vspace{-0.7cm}  \begin{minipage}[t]{2.5cm}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
-%%     \subcaption{}
-%%   \end{minipage}\\
-%%    \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
-%%     \subcaption{}
-%%   \end{minipage}%
-%%   \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
-%%     \subcaption{}
-%%   \end{minipage}%
-%%     \caption{(a): hand drawing. (b): Rendering of the trace set our model infers for (a). (c): noisy rendering of (b).}\label{handDrawingExamples}
-%% \end{wrapfigure}
-
-%A practical application of our neural network is the automatic conversion of hand drawings into a subset of \LaTeX.
- We trained the model
-to generalize to hand drawings by introducing noise into the
-renderings of the training target images, where the noise process  mimics the kinds of variations found in hand drawings (%% Fig.~\ref{handDrawingExamples}; 
-see supplement for details).
-While our neurally-guided SMC procedure
-used pixel-wise distance as a surrogate for a likelihood function ($L(\cdot|\cdot)$ in Sec.~\ref{neuralNetworkSection}),
- pixel-wise distance fares poorly on hand drawings, which never exactly match
-the model's renders.
-So, for hand drawings,
-we learn a surrogate likelihood function,
-$L_{\text{learned}}(\cdot|\cdot)$.
-The density $L_{\text{learned}}(\cdot|\cdot)$ is predicted by a convolutional network that we train to predict
-the distance between two specs conditioned upon their renderings.
-We train $L_{\text{learned}}(\cdot |\cdot )$  to approximate the symmetric difference,
-which is  the number of drawing commands by which two specs  differ:
-  \begin{equation}
-    -\log L_{\text{learned}}(\text{render}(S_1)|\text{render}(S_2))\approx |S_1 - S_2| + |S_2 - S_1|\label{symmetricDistance}
-    \end{equation}
-
-%% Pixel-wise distance metrics are sensitive to the details of how
-%% arrows, dashes, and corners are drawn -- but we wish to be invariant
-%% to these details.
-%% So, we learn a distance metric over images that
-%% approximates the distance metric in the search space over traces.
-
-  \textbf{Experiment 2: Figures~\ref{drawingSuccesses}--\ref{drawingIntersectionOverUnion}.}
-    We evaluated, but did not train, our system on 100 real hand-drawn figures; see Fig.~\ref{drawingSuccesses}--\ref{drawingFailures}.
-These were drawn carefully but not perfectly with the aid of graph paper.
-%Because our model assumes that objects are snapped to a $16\times 16$ grid, 
-%we made the drawings on graph paper.
-For each drawing we annotated a ground truth spec and had the neurally guided SMC sampler
-produce $10^3$ samples. % for each drawing.
-For 63\% of the drawings, the Top-1 most likely sample exactly matches the
-ground truth; with more samples, the model finds specs
-that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
-We will show that the program synthesizer
-corrects some of these small errors (Sec.~\ref{synthesizerHelpsParsing}).
-%% Because the model sometimes makes mistakes % on hand drawings,
-%% we envision it working as follows:
-%% a user sketches a diagram,
-%% and the system responds by proposing a few candidate interpretations.
-%% The user could then select the one closest to their intention and edit it if necessary.
-
-\setlength\tabcolsep{3.5pt}
-\begin{figure}[H]
-  \begin{minipage}[t]{8.25cm}
-    \begin{tabular}{llll}
-      \includegraphics[width = 2cm]{figures/expert-38.png}&
-      \includegraphics[width = 2cm]{figures/expert-73.png}&
-      \includegraphics[width = 2cm]{figures/expert-77.png}&
-      \includegraphics[width = 2cm]{figures/expert-21.png}
-      \\
-      \includegraphics[width = 2cm]{figures/38-parse.png}     &
-      \includegraphics[width = 2cm]{figures/73-parse.png}     &
-      \includegraphics[width = 2cm]{figures/77-parse.png}    &
-      \includegraphics[width = 2cm]{figures/21-parse.png}    
-      \end{tabular}
-    \caption{Left to right: Ising model, recurrent network architecture, figure from a deep learning textbook \cite{Goodfellow-et-al-2016}, graphical model}\label{drawingSuccesses}
-  \end{minipage}
-\hfill  \begin{minipage}[t]{4.25cm}
-    \begin{tabular}{ll}
-          \includegraphics[width = 2cm]{figures/expert-1.png}&
-          \includegraphics[width = 2cm]{figures/expert-34.png}\\
-      \includegraphics[width = 2cm]{figures/expert-1-parse.png}     &
-              \includegraphics[width = 2cm]{figures/34-parse.png}    
-    \end{tabular}
-
-    \caption{Near misses. Rightmost: illusory contours (note: no SMC in rightmost)}\label{drawingFailures}
-  \end{minipage}
-
-%  \caption{Example drawings above model outputs.
-See also Fig.~\ref{firstPageExamples}.
-Stochastic search (SMC) can help correct for these errors, as can the program synthesizer (Section~\ref{synthesizerHelpsParsing})}\label{lotsOfHandDrawings}
-\end{figure}
-\setlength\tabcolsep{6pt}
-
-\begin{figure}[h]\centering
-  \begin{minipage}[c]{0.57\textwidth} 
-    \centering  \includegraphics[width = 8cm]{figures/drawingAccuracy.png}            \vspace{-0.5cm} 
-  \end{minipage}\hfill%
-      \begin{minipage}[c]{0.4\textwidth} 
-  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1, 5, 100)?
-    Distance to ground truth measured by the intersection over union (IoU) of predicted vs.
-ground truth: IoU of sets $A$ and $B$ is $|A\cap B|/|A\cup B|$.
-(a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 5 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth.
-Red: the full model.
-Other colors: lesioned versions of our model.}\label{drawingIntersectionOverUnion}            \vspace{-0.5cm}
-      \end{minipage}
-
-\end{figure}
-
-%\pagebreak
-
-\section{Synthesizing graphics programs from specs}\label{programSynthesisSection}
-Although the spec describes the contents
-of a scene, it does not encode higher-level features of an image
-such as repeated motifs or symmetries, which are more naturally captured by a graphics program.
-We seek to synthesize graphics programs from their specs.
-
-We constrain the space of programs by writing down a context
-free grammar over  programs -- 
-%Although it might be desirable to synthesize programs in a Turing-complete language such as Lisp or Python, a more tractable approach is to specify
-what in the program
-languages community is called a Domain Specific Language (DSL)~\citep{polozov2015flashmeta}. Our DSL (Tbl.~\ref{DSL})
-encodes prior knowledge of what graphics programs tend to look like.
-
-\begin{table}[H]
-  \caption{Grammar over graphics programs.
-We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertical/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations ($\mathbb{Z}\times$Var\texttt{+}$\mathbb{Z}$).}\label{DSL}
-  \begin{tabular}{rl}\toprule
-  Program$\to$&Statement; $\cdots$; Statement\\
-  Statement$\to$&\texttt{circle}(Expression,Expression)\\
-  Statement$\to$&\texttt{rectangle}(Expression,Expression,Expression,Expression)\\
-  Statement$\to$&\texttt{line}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
-  Statement$\to$&\texttt{for}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ if }$(\text{Var} > 0)$\texttt{ \{ }Program\texttt{ \}; }Program\texttt{ \}}\\
-  Statement$\to$&\texttt{reflect}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
-  Expression$\to$&$\mathbb{Z}\times$Var\texttt{+}$\mathbb{Z}$\\
-%  Var$\to$&A free (unused) variable\\
-  Axis$\to$&\texttt{X = }$\mathbb{Z}$ | \texttt{Y = }$\mathbb{Z}$\\
-    $\mathbb{Z}\to$&an integer\\\bottomrule
-  \end{tabular}
-\end{table}
-
-Given the DSL and a spec $S$, we want a program that both satisfies $S$
-and, at the same time, is the ``best'' explanation of $S$.
-For example, we might prefer more general programs or, in the spirit of Occam's razor,
-prefer shorter programs.
-We wrap these intuitions up into a cost function over programs,
-and seek the minimum cost program consistent with $S$:
-\begin{equation}
-  %  \text{program}(S) = \argmin_{p\in \text{DSL, s.t. }p \text{ consistent w/ } S} \text{cost}(p)\label{programObjective}
-    \text{program}(S) = \argmax_{p\in \text{DSL}} \indicator\left[p \text{ consistent w/ } S \right]\exp \left( -\text{cost}(p) \right)\label{programObjective}
-\end{equation}
-We define the
-cost of a program to be the number of Statement's it contains (Tbl.~\ref{DSL}).
-We also penalize using many different numerical constants; see supplement.
-Returning to the generative model in Fig.~\ref{roadmap},
-this setup is the same as saying that the prior probability of a program $p$ is $\propto \exp\left(-\text{cost}(p) \right)$ and the likelihood of a spec $S$ given a program $p$ is $\indicator[p\text{ consistent w/ }S]$.
-%\remark{The flow here is a bit off/backwards.
-``We want a program that evaluates to $T$ and also minimizes some measure of program cost''---why do we care about cost?
-It'd be better to start by making a ``Bayesian Occam's razor'' appeal (e.g.
-the most compact/general program is the more likely explanation) and then saying that one way to do this is to minimize a cost function which is proportional to program length.}
-
-The constrained optimization problem in
-Eq.~\ref{programObjective} is intractable in general, but there
-exist efficient-in-practice tools for finding exact solutions to such
-program synthesis problems. We use the state-of-the-art Sketch
-tool~\citep{solar2008program}.
-%At a high level,
-Sketch takes as input a space of programs, along with
-a specification of the program's behavior and optionally a cost
-function.  It translates the synthesis problem into a constraint
-satisfaction problem and then uses a SAT solver to find a minimum-cost
-program satisfying the specification.  Sketch requires a
- \emph{finite program space}, which here means that the depth of the
-program syntax tree is bounded (we set the bound to 3),
-but has the guarantee that it 
-always eventually finds a globally optimal solution.
-In exchange for this optimality guarantee
-it comes with no guarantees
-on runtime.
-For our domain synthesis times vary from minutes to hours,
-with 27\% of the drawings timing out the synthesizer after 1 hour.
-Tbl.~\ref{exampleSynthesisResults} shows programs recovered by our system.
-A main impediment to our use of these general techniques is
-the prohibitively high cost of searching for programs.
-We next describe how to learn to synthesize programs much faster (Sec.~\ref{learningASearchPolicy}),
-timing out on 2\% of the drawings and solving 58\% of problems within a minute.
-
-\newcommand{\exampleProgramSize}{4cm}
-\newcommand{\exampleTraceSize}{3.5cm}
-\newcommand{\exampleDrawingSize}{1.25cm}
-\lstset{basicstyle = \scriptsize\ttfamily}
-
-\begin{table}[t]
-  \caption{Drawings (left), their specs (middle left), and programs synthesized from those specs (middle right).
-Compared to the specs the programs are more compressive (right: programs have fewer lines than specs) and automatically group together related drawing commands.
-Note the nested loops  and conditionals in the Ising model, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
-%  \vspace{-0.6cm}
-\centering  \begin{tabular}{m{1.5cm}llc}
-    \toprule
-    \textbf{Drawing}&\textbf{Spec}&\textbf{Program}&%\begin{tabular}{c}
-      \textbf{Compression factor}%\\\textbf{factor}
-      %      \end{tabular}\\
-      \\
-    \midrule
-    \includegraphics[width = \exampleDrawingSize]{figures/expert-29-trim.png}&
-\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-Line(2,15, 4,15)
-Line(4,9, 4,13)
-Line(3,11, 3,14)
-Line(2,13, 2,15)
-Line(3,14, 6,14)
-Line(4,13, 8,13)
-\end{lstlisting}
-\end{minipage}&     \begin{minipage}{\exampleProgramSize} \begin{lstlisting}
-for(i<3)
- line(i,-1*i+6,
-      2*i+2,-1*i+6)
- line(i,-2*i+4,i,-1*i+6)
-       \end{lstlisting}
-     \end{minipage}&$\frac{6}{3} = 2\text{x}$\\\midrule
-%%      \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
-%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-%% Line(5,13,2,10,arrow)
-%% Circle(5,9)
-%% Circle(8,5)
-%% Line(2,8, 2,6,arrow)
-%% Circle(2,5)
-%% \end{lstlisting}
-%% \small\emph{... etc. ...; 13 lines}
-%% \end{minipage}&
-%%              \begin{minipage}{\exampleProgramSize}\begin{lstlisting}
-%% circle(4,10)
-%% for(i<3)
-%%  circle(-3*i+7,5)
-%%  circle(-3*i+7,1)
-%%  line(-3*i+7,4,-3*i+7,2,arrow)
-%%  line(4,9,-3*i+7,6,arrow)
-%% \end{lstlisting}
-%% \end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
-    \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
-\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-Circle(5,8)
-Circle(2,8)
-Circle(8,11)
-Line(2,9, 2,10)
-Circle(8,8)
-Line(3,8, 4,8)
-Line(3,11, 4,11)
-\end{lstlisting}
-  \small\emph{... etc. ...; 21 lines}
-\end{minipage}&\begin{minipage}{\exampleProgramSize}
-\begin{lstlisting}
-for(i<3)
- for(j<3)
-  if(j>0)
-   line(-3*j+8,-3*i+7,
-        -3*j+9,-3*i+7)
-   line(-3*i+7,-3*j+8,
-        -3*i+7,-3*j+9)
-  circle(-3*j+7,-3*i+7)
-\end{lstlisting}
-\end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
-\includegraphics[width = \exampleDrawingSize]{figures/expert-101-trim.png}&
-\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-Rectangle(1,10,3,11)
-Rectangle(1,12,3,13)
-Rectangle(4,8,6,9)
-Rectangle(4,10,6,11)
-\end{lstlisting}
-  \small\emph{... etc. ...; 16 lines}
-\end{minipage}&\begin{minipage}{\exampleProgramSize}
-\begin{lstlisting}
-for(i<4)
- for(j<4)
-  rectangle(-3*i+9,-2*j+6,
-            -3*i+11,-2*j+7)
-\end{lstlisting}
-\end{minipage}&$\frac{16}{3} = 5.3\text{x}$\\\midrule
-%% \includegraphics[width = \exampleDrawingSize]{figures/expert-75-extra-trim.png}&
-%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-%% Line(11,14,13,14,arrow)
-%% Circle(10,10)
-%% Line(10,13,10,11,arrow)
-%% Circle(6,10)
-%% \end{lstlisting}
-%%     \small\emph{... etc. ...; 15 lines}
-%% \end{minipage}&
-%% \begin{minipage}{\exampleProgramSize}
-%%     \begin{lstlisting}
-%% for(i<4)
-%%  line(-4*i+13,4,-4*i+13,2,arrow)
-%%  for(j<3)
-%%   if(j>0)
-%%    circle(-4*i+13,4*j+-3)
-%%   line(-4*j+10,5,-4*j+12,5,
-%%        arrow)
-%% \end{lstlisting}
-%%   \end{minipage}&$\frac{15}{6} = 2.5\text{x}$\\\midrule
-
-  \includegraphics[width = \exampleDrawingSize]{figures/expert-71-trim.png}&
-\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-Line(3,10,3,14,arrow)
-Rectangle(11,8,15,10)
-Rectangle(11,14,15,15)
-Line(13,10,13,14,arrow)
-  \end{lstlisting}\small\emph{... etc. ...; 16 lines}%
-  \end{minipage}&\begin{minipage}{\exampleProgramSize}
-%% \begin{lstlisting}
-%% for (i<3)
-%%  circle(-3*i+7,1)
-%%  circle(-3*i+7,6)
-%%  line(-3*i+7,-1*i+4,-3*i+7,5)
-%% \end{lstlisting}
-\begin{lstlisting}
-for(i<3)
- line(7,1,5*i+2,3,arrow)
- for(j<i+1)
-  if(j>0)
-   line(5*j-1,9,5*i,5,arrow)
-  line(5*j+2,5,5*j+2,9,arrow)
- rectangle(5*i,3,5*i+4,5)
- rectangle(5*i,9,5*i+4,10)
-rectangle(2,0,12,1)
-\end{lstlisting}
-\end{minipage}&$\frac{16}{9} = 1.8\text{x}$\\\midrule
-
-  \includegraphics[width = \exampleDrawingSize]{figures/expert-72-trim.png}&
-
-\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-Circle(2,8)
-Rectangle(6,9, 7,10)
-Circle(8,8)
-Rectangle(6,12, 7,13)
-Rectangle(3,9, 4,10)
-\end{lstlisting}\small\emph{... etc. ...; 9 lines}
-  \end{minipage}&\begin{minipage}{\exampleProgramSize}
-\begin{lstlisting}
-reflect(y=8)
- for(i<3)
-  if(i>0)
-   rectangle(3*i-1,2,3*i,3)
-  circle(3*i+1,3*i+1)
-\end{lstlisting}
-\end{minipage}&$\frac{9}{5} = 1.8\text{x}$ \\\bottomrule
-  \end{tabular}
-  \end{table}
-
-\subsection{Learning a search policy for synthesizing programs}\label{learningASearchPolicy}
-
-We want to leverage powerful, domain-general techniques from the program synthesis community,
-but make them much faster by
-learning a domain-specific \textbf{search policy}.
-A search policy poses search problems
-like those in Eq.~\ref{programObjective},
-but also offers additional constraints on the structure of the program (Tbl.~\ref{policyOutput}).
-For example, a policy might decide to first try searching over small programs before searching over large programs,
-or decide to prioritize searching over programs that have loops.
-
-A search policy $\pi_\theta(\sigma  | S )$ takes as input a spec $S$ and predicts a distribution over synthesis problems, each of which is written $\sigma $ and corresponds to a set of possible programs to search over (so $\sigma \subseteq \text{DSL}$).
-Good policies will prefer tractable program spaces,
-so that the search procedure will terminate early, 
-but should also prefer program spaces likely to contain
-programs that concisely explain the data.
-These two desiderata are in tension:
-tractable synthesis problems involve searching over smaller spaces,
-but smaller spaces are less likely to contain good programs.
-%a minimum cost program
-%for explaining $T$.
-Our goal now is to find the parameters of the policy, written $\theta$, that best navigate this trade-off.
-
-Given a search policy, what is the best way of using it to quickly find minimum cost programs?
-We use a bias-optimal search algorithm (c.f. Schmidhuber 2004~\citep{schmidhuber2004optimal}):
-
-\noindent\textbf{Definition: Bias-optimality.} 
-   A search algorithm is $n$-\emph{bias optimal}
-with respect to a distribution $\probability_{\text{bias}}[\cdot ]$ if it is
-guaranteed to find a solution in $\sigma $ after searching for at least time
-$n\times\frac{t(\sigma )}{\probability_{\text{bias}}[\sigma ]}$, where $t(\sigma )$ is the time it
-takes to verify that $\sigma $ contains a solution to the
-search problem.
-
-%Intuitively, an $n$-bias optimal search algorithm spends at least $\probability_{\text{bias}}[\sigma ]/n$ of its time exploring solution space $\sigma $.
-Bias-optimal search over program spaces is known as \textbf{Levin Search}~\cite{levin1973universal}; an example of a $1$-bias optimal search algorithm is an ideal time-sharing system that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
-We construct a $1$-bias optimal search algorithm by identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |S)$ and $t(\sigma )  = t(\sigma|S)$, where $t(\sigma|S)$ is how long the synthesizer takes to search $\sigma $ for a program for $S$.
-This means that the search algorithm explores the entire program space, but spends most of its time in the regions of the space that  the policy judges to be most promising.
-
-%% \begin{figure}\centering
-%%   \begin{tikzpicture}
-%%     \node[anchor = west] at (0,5.25) {Entire program search space};
-%%     \draw[fill = yellow,fill opacity = 0.15,draw = black] (0,0) rectangle (5,5);
-%%     \draw [fill = yellow, opacity = 0.2] (0,0)--(0,2)--(4,0)--(0,0);
-%%     \draw [fill = yellow, opacity = 0.4,cycle] (0,5)--(0,1)--(3,5);
-%%     \draw [fill = yellow, opacity = 0.6,cycle] (2.5,5)--(3.2,0)--(5,0)--(5,5);
-%%     \draw (0,2) -- node[below,sloped]{short programs} (4,0);
-%%     \draw (0,2) -- node[above,sloped]{long programs} (4,0);
-%%     \draw (2.5,5) -- node[above,sloped]{programs w/ reflections} (3.2,0);
-%%     \draw (0,1) -- node[above,sloped]{ programs w/ loops} (3,5);
-%%     \node(p1)[anchor =west ] at (5.5,3.5) {$\pi_\theta(\text{short, no loop/reflect}) = $};
-%%     \draw [fill = yellow, fill opacity = 0.2,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p1.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p1.east);
-%%     \node(p2)[anchor =west ] at ([yshift = -0.5cm]p1.west) {$\pi_\theta(\text{long, loops}) = $};
-%%     \draw [fill = yellow, fill opacity = 0.4,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p2.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p2.east);
-%%     \node(p3)[anchor =west ] at ([yshift = -0.5cm]p2.west) {$\pi_\theta(\text{long, no loop/reflect}) = $};
-%%     \draw [fill = yellow, fill opacity = 0.15,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p3.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p3.east);
-%%     \node(p4)[anchor =west ] at ([yshift = -0.5cm]p3.west) {$\pi_\theta(\text{long, reflects}) = $};
-%%     \draw [fill = yellow, fill opacity = 0.6,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p4.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p4.east);
-%%     \node(p5)[anchor =west ] at ([yshift = -0.5cm]p4.west) {\emph{etc.}};
-%%   \end{tikzpicture}
-%%   \caption{The bias-optimal search algorithm divides the entire (intractable) program search space in to (tractable) program subspaces (written $\sigma $), each of which contains a restricted set of programs.
-For example, one subspace might be short programs which don't loop.
-The policy $\pi$ predicts a distribution over program subspaces.
-The weight that $\pi$ assigns to a subspace is indicated by it's yellow shading in the above figure.}
-%%   \end{figure}
-Now in theory any $\pi_\theta(\cdot |\cdot ) $ is a bias-optimal searcher.
-But the actual runtime of the algorithm depends strongly upon
-the bias $\probability_{\text{bias}}[\cdot ]$.
-Our new approach is to learn $\probability_{\text{bias}}[\cdot ]$
-by picking the policy minimizing the
-expected bias-optimal time to solve a training corpus, $\mathcal{D}$, of graphics program synthesis problems:
-\begin{align}
-\textsc{Loss}(\theta ; \mathcal{D})& =  \expect_{S\sim\mathcal{D}}\left[ \min_{\sigma\in \text{\textsc{Best}}(S)}\frac{t(\sigma | S)}{\pi_\theta (\sigma | S)}\right] + \lambda \Vert\theta\Vert_2^2\label{policyLoss}\\
-\text{where }  \sigma \in\text{\textsc{Best}}(S) &\text{ if  a minimum cost program for }S \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t.
-}p\text{ evaluates to }S} \text{cost}(p) \nonumber
-\end{align}
-%Practically, bias optimality has now bought us the following: (1) a guarantee that the policy will always find the minimum cost program; and (2) a differentiable loss function for the policy parameters that takes into account the cost of searching, in contrast to e.g.
-DeepCoder~\citep{BalGauBroetal16}.
-
-To generate a training corpus for learning a policy,
-we synthesized minimum cost programs for each  drawing
-and for each $\sigma $,
-%Solving these
-%\footnote{There are 100 the drawings and $2\times 2\times 2\times 3 = 24$ different values of $\sigma $}
-%synthesis problems takes a little over a day on 40 CPUs.
-%With the training set in hand we  %This loss is differentiable but nonconvex even if $\pi_{\theta}(\cdot |\cdot )^{-1}$ is convex.
-then minimized~\ref{policyLoss} using gradient descent. % while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}.
-%See supplement for details.
-Because we want to learn a policy from only $100$ drawings,
-we parameterize $\pi$ with a  low-capacity bilinear model; see supplement.
-%for $\pi$:
-%% \begin{equation}
-%%   \pi_{\theta}(\sigma |S)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{spec}}(S)\right)
-%% \end{equation}
-%% where $\phi_{\text{params}}(\sigma  )$ is a one-hot encoding of
-%% the parameter settings of $\sigma $ (see Tbl.~\ref{policyOutput})
-%% and $\phi_{\text{spec}}(S)$ extracts a few simple features of the trace set $S$;
-%% see supplement for details.
-
-\textbf{Experiment 3: Table~\ref{policyEvaluation}.}
-We compare synthesis times for our learned search policy
-with 4 alternatives:
- \emph{Sketch}, which poses the
- entire problem wholesale to the Sketch program synthesizer;
- \emph{DC}, a DeepCoder--style model that learns to predict which program components (loops, reflections)
- are likely to be useful~\cite{BalGauBroetal16};
- \emph{End--to-End},
- which trains a recurrent neural network to regress directly from images to programs;
-and an \emph{Oracle},
-a policy which always picks the quickest to search $\sigma $
- also containing a minimum cost program.
-Our approach improves upon Sketch by itself,
-and comes close to the Oracle's performance.
-One could never construct this Oracle,
-because the agent does not know ahead of time which
-$\sigma $'s contain minimum cost programs nor does it know how long each
-$\sigma $ will take to search.
-%The Oracle is an upper bound on the performance of any search policy.
-With this learned policy in hand we can synthesize 58\% of programs within a minute.
-%
-\begin{table}[h]\centering
-  \caption{Parameterization of different ways of posing the program synthesis problem. The policy learns to choose parameters likely to quickly yield a minimal cost program.
-    %We slightly abuse notation by writing $\sigma $ to mean an assignment to each of these parameters (so $\sigma $ assumes one of 24 different values) and to mean the set of programs selected by that parameterization (so $\sigma \subseteq \text{DSL}$)
-  }\label{policyOutput}
-  \begin{tabular}{lll}\toprule
-  Parameter&Description&Range\\\midrule
-  Loops?&Is the program allowed to loop?&$\{\text{True},\text{False}\}$\\
-  Reflects?&Is the program allowed to have reflections?&$\{\text{True},\text{False}\}$\\
-  Incremental?&Solve the problem piece-by-piece or all at once?&$\{\text{True},\text{False}\}$\\
-  Maximum depth& Bound on the depth of the program syntax tree&$\{1,2,3\}$
-  \\\bottomrule
-  \end{tabular}\vspace{-0.5cm}
-  \end{table}
-\begin{table}[h]
-  \centering
-  \begin{minipage}[c]{0.4\textwidth}
-  \begin{tabular}{lll}
-    \toprule Model&\begin{tabular}{c}
-      Median \\search time
-    \end{tabular}&\begin{tabular}{c}
-      Timeouts\\(1 hr)
-      \end{tabular}\\\midrule
-    Sketch&274 sec&27\%\\
-    DC&187 sec&2\%\\
-    End--to--End&63 sec&94\%\\
-    Oracle&6 sec&2\%\\
-    Ours&28 sec&2\%\\\bottomrule 
-    \end{tabular}
-  \end{minipage}\hfill%
-  \begin{minipage}[c]{0.5\textwidth}
-    \caption{Time to synthesize a minimum cost program.
-Sketch: out-of-the-box performance of Sketch~\citep{solar2008program}.
-DC: Deep--Coder style baseline that predicts program components, trained like~\cite{BalGauBroetal16}.
-End--to--End: neural net trained to regress directly from images to programs, which fails to find valid programs 94\% of the time.
-Oracle:  upper bounds  the performance of any bias--optimal search policy.
-Ours:  %% $\infty = $ timeout.
-Red dashed line is median time.
-           evaluated w/ 20-fold cross validation.}\label{policyEvaluation}
-  \end{minipage}
-  \vspace{-0.5cm}
-\end{figure}
-
-\section{Applications of graphics program synthesis}\label{applicationsSection}
-%% Why synthesize a graphics program,
-%% if the spec already suffices to recover the objects in an image?
-%% Within our domain of hand-drawn figures, graphics program synthesis has several uses:
-
-\subsection{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
-\begin{wrapfigure}{r}{5cm}\vspace{-0.5cm}
-  \includegraphics[width = 5cm]{figures/programSuccess7.png}
-  \includegraphics[width = 5cm]{figures/programSuccess16.png}
-  \caption{Left: hand drawings.
-Center: interpretations favored by the deep network.
-Right: interpretations favored after learning a prior over programs.
-The prior favors  simpler programs, thus (top) continuing the pattern of not having an arrow is preferred, or (bottom) continuing the ``binary search tree'' is preferred.}\label{exampleOfProgramCorrectingMistake}
-\vspace{-0.75cm}  \end{wrapfigure}
-The program synthesizer corrects errors made by the neural network by favoring specs which lead to more
-concise or general programs.  For example, figures with perfectly aligned objects are preferable, %% to figures whose parts are slightly misaligned,
-and precise alignment lends itself to short
-programs.
-Concretely,
-we run the program synthesizer on the
-Top-$k$  most likely specs output by the neurally guided sampler.
-Then, the system
-reranks the Top-$k$  by  the prior probability of their programs.
-The prior probability of a program is learned by optimizing the parameters of the prior so as to maximize
-the likelihood of the ground truth specs;
-see supplement for details.
-But, this procedure can only correct errors when
-a correct spec is in the Top-$k$.
-Our sampler could only do better on
-7/100 drawings by looking at the Top-100 samples
-(see Fig.~\ref{drawingIntersectionOverUnion}),
-precluding a statistically significant analysis of how much
-learning a prior over programs could help correct errors.
-But,
-learning this prior does sometimes 
-help correct mistakes made by the neural network; %% , and also
-%% occasionally introduces mistakes of its own; 
-see
-Fig.~\ref{exampleOfProgramCorrectingMistake} for a representative
-example of the kinds of corrections that it makes.
-See supplement for details.
-
-%% This is equivalent to doing
-%% MAP inference in a generative model where the program is first drawn
-%% from $\probability_{\beta} [\cdot]$, then the program is executed deterministically,
-%% and then we observe a noisy version of the program's output, where $L_\text{learned}(I|\text{render}(\cdot))\times\probability_\theta[\cdot|I]$
-%% is our observation model.
-
-%% Learning this prior over programs can
-%%  On the whole
-%% it modestly improves our Top-1 accuracy from 58\% to 61\%.  Recall that
-%% from Fig.~\ref{drawingIntersectionOverUnion} that the best improvement
-%% in accuracy we could possibly get is 65\% by looking at the top 10 traces.
-
-%% \subsection{Modeling similarity between drawings}
-%% Modeling drawings using programs opens up new ways to measure similarity between them.
-%% For example, we might say that two drawings are similar if they both contain loops of length 4,
-%% or if they share a reflectional symmetry,
-%% or if they are both organized according to a grid-like structure.
-
-%% We measure the similarity between two drawings by extracting features
-%% of the lowest-cost programs that describe them. Our features are counts of the number of times that different components in the
-%% DSL were used (Tbl.~\ref{DSL}).
-%% We  then find drawings which are either close together or far apart in program feature space.
-%% One could use many
-%% alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
-%% We used our learned distance metric between trace sets, $L_{\text{learned}}(\cdot|\cdot)$,
-%% to find drawings that are either close together or far apart according to the learned
-%% distance metric over images.
-%% Fig.~\ref{similarityMatrix} illustrates the kinds of drawings that these different metrics put closely together,
-%% while Sec.~2 of the supplement shows low dimensional projections of
-%% program and image features.
-
-%% \newcommand{\similaritySize}{1cm}
-%% \newcommand{\similarityArrowSize}{0.35cm}
-%% \begin{figure}[t]
-%%   \begin{tabular}{|c|c|}
-%%     \multicolumn{1}{c}{\textbf{Close in program space, far in image space}}&
-%%     \multicolumn{1}{c}{\textbf{Close in image space, far in program space}}\\\hline&\\
-
-%%     \begin{tabular}{l}
-%%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
-%%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-16-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-17-trim.png}\end{minipage}
-%%     \end{tabular} &
-
-%%     \begin{tabular}{l}
-%%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-22-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-77-trim.png}\end{minipage}\\\\
-%%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-64-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-97-trim.png}\end{minipage}
-%%     \end{tabular}
-%% \\&\\    \hline
-%%     %\\
-%% %    \multicolumn{1}{c|}{}&&\\\cline{2-3}
-%% %    \multicolumn{1}{c|}{}&&\\ \multicolumn{1}{c|}{}
-%%     %& %% \begin{tabular}{l}
-%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
-%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-16-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-17-trim.png}\end{minipage}
-%%     %% \end{tabular}
-%%     %&
-%%     %% \begin{tabular}{l}
-%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-75-extra-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-89-trim.png}\end{minipage}\\\\
-%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-3-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-39-trim.png}\end{minipage}
-%%     %% \end{tabular}
-%% %\\ \multicolumn{1}{c|}{}&&\\\cline{2-3}\cline{2-3}
-%%   \end{tabular}
-
-%%   \centering
-%% \caption{Pairs of images either close together or far apart in different features spaces.
-The symbol $\leftrightarrow$ points to the compared images.
-Features of the program capture abstract notions like symmetry and repetition.
-Distance metric over images is $L_{\text{learned}}(\cdot|\cdot)$ (see Sec.~\ref{generalizingTheHandDrawings}).
-Similarity of programs captures high-level features like repetition and symmetry, whereas similarity of images corresponds to similar drawing commands being in similar places.
-See Sec.
-2 of the supplement for more examples.}\label{similarityMatrix}  \end{figure}
-
-%% We project these features down to a
-%% 2-dimensional subspace using primary component analysis
-%% (PCA); see Fig.\ref{NMF}.  One could use many
-%% alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
-%% We used our learned distance metric between traces, $L_{\text{learned}}(\cdot|\cdot)$, and projected to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}).
-This reveals similarities between the objects in the drawings,
-%% while missing similarities at the level of the program.
-%% \begin{figure}[h]
-%% \centering  \begin{minipage}{\textwidth}\centering
-%%   %\includegraphics[width = 0.69\textwidth]{figures/PCA.png}
-%%   \includegraphics[width = 0.69\textwidth]{figures/PCA_improved.png}
-%%     \caption{PCA on features of the programs that were synthesized for each drawing.
-Symmetric figures cluster to the right; ``loopy'' figures cluster to the left; complicated programs are at the top and simple programs are at the bottom.}    \label{NMF}
-%%   \end{minipage} %\hfill
-%%   \begin{minipage}{\textwidth}\centering
-%%     \includegraphics[width = 0.69\textwidth]{figures/imageSimilarity.png} 
-%%     \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
-%%   \end{minipage}
-%% \end{figure}
-
-\subsection{Extrapolating figures}
-Having access to the source code of a graphics program facilitates coherent, high-level image editing.
-%For example,
-%we could change all of the circles to squares or make all of the lines be dashed.
-For example we can extrapolate figures
-by increasing the number of times that loops are executed.
-Extrapolating repetitive visuals patterns comes naturally to humans,
-and is a practical application:
-imagine hand drawing a repetitive graphical model structure
-and having our system automatically induce and extend the pattern.
-Fig.~\ref{extrapolationFigure} shows extrapolations produced by our system.
-\begin{figure}[H]\centering
-  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix1.png}
-  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix2.png}
-%  \includegraphics[width = \textwidth]{figures/extrapolationMatrix3.png}  
-   \caption{Top, white: hand drawings. Bottom, black: extrapolations produced by our system.}
-  \label{extrapolationFigure}
-  \end{figure}
-%\input{extrapolations.tex}
-
-% \remark{Seems like you're still fleshing this part out, but I'll give my feedback anyway: (1) This subsection could really use a motivational introduction, e.g.
-``The program synthesizer can help correct errors/bad proposals from the neural network by favoring execution traces which lead to more concise/general programs.'' (2) The image likelihood function should probably be introduced sooner, when you talk about SMC/beam search.
-(3) Where does $\theta$ come from?
-Is it set by hand?
-Learned?
-(4) How does Eq.
-4 get used?
-Is this a modification to the beam search objective / SMC posterior?
-If so, it'd be great to have set up the version without it in an earlier section, and then be able to refer to this as a small modification of the previous equation.}
-
-%\pagebreak
-%\section{Discussion}
-
-\section{Related work}
-
-\textbf{Program Induction:}
-Our approach to learning to search for programs draws theoretical
-underpinnings from Levin
-search~\citep{levin1973universal,solomonoff1984optimum} and
-Schmidhuber's OOPS model~\citep{schmidhuber2004optimal}.
-DeepCoder~\citep{BalGauBroetal16} is a recent model which, like ours, learns to predict likely program components.
-Our work differs by identifying and modeling
-the trade-off between tractability and probability of success.
-TerpreT~\citep{gaunt2016terpret} 
-systematically compares constraint-based program synthesis techniques
-against gradient-based search methods, like those used to train
-Differentiable Neural Computers~\citep{graves2016hybrid}.  The TerpreT
-experiments motivate our use of constraint-based techniques.
-
-\textbf{Deep Learning:} Our neural network combines the architectural ideas of Attend-Infer-Repeat~\citep{eslami1603attend} -- which learns to decompose an image into its constituent objects -- with the training regime and SMC inference  of Neurally Guided Procedural Modeling~\cite{ritchie2016neurally} -- which learns to control procedural graphics programs.
-%AIR learns an iterative inference scheme which infers objects one by one and also decides when to stop inference.
-%; this is similar to our approach's first stage, which parses images into traces. Our approach further produces interpretable, symbolic programs which generate those traces.
-%Our network  differs in its architecture and training regime: AIR learns a recurrent auto-encoding model via variational inference, whereas our parsing stage learns an autoregressive-style model from randomly-generated (trace, image) pairs.
-%Finally, while AIR was evaluated on multi-MNIST images and synthetic 3D scenes, we focus on hand-drawn sketches.
-IM2LATEX~\citep{im2latex} is a recent work that 
- derenders  \LaTeX~ equations,
-recovering a markup language representation.
-Our goal is to go from
-noisy input to a high-level program,
-which goes beyond markup languages by supporting
-programming constructs like loops and conditionals.
-%Recovering a high-level program is more challenging than recovering markup
-%because it is a highly under constrained symbolic reasoning problem.
-
-%Our image-to-trace parsing architecture builds on prior work on controlling procedural graphics programs~\citep{ritchie2016neurally}.
-%Given a program which generates random 2D recursive structures such as vines, that system learns a structurally-identical ``guide program'' whose output can be directed, via neural networks, to resemble a given target image.
-%% We adapt this method to a different visual domain (figures composed of multiple objects), using a broad prior over possible scenes as the initial program and viewing the trace through the guide program as a symbolic parse of the target image.
-%% We then show how to efficiently synthesize higher-level programs from these traces.
-
-\textbf{Hand-drawn sketches:} Sketch-n-Sketch is a bi-directional editing system where direct manipulations to a program's output automatically propagate to the program source code~\citep{Hempel:2016:SSP:2984511.2984575}.
-This work  compliments our own: programs produced by our method could be provided to a Sketch-n-Sketch-like system as a starting point for further editing.
-Other systems in the computer graphics literature convert sketches to procedural representations, using a convolutional network to match a sketch to the output of a parametric 3D modeling system in~\citep{huang2017shape} or supporting interactive sketch-based instantiation of procedural primitives in~\citep{Nishida:2016:ISU:2897824.2925951}.
-In contrast, we seek to automatically infer a programmatic representation capturing higher-level visual patterns.
-The CogSketch system~\citep{forbus2011cogsketch} also aims to have a high-level understanding of hand-drawn figures.
-Their  goal is cognitive modeling, whereas we are interested in building an automated AI application.% (e.g.
-in our system the user need not annotate which strokes correspond to which shapes; our neural network produces something equivalent to the annotations).
-
-\section{Contributions}
-
-We have presented a system for inferring graphics programs which generate \LaTeX-style figures from hand-drawn images.
-The system uses a combination of deep neural networks and stochastic search to parse drawings into symbolic specifications; it then feeds these specs to a general-purpose program synthesis engine to infer a structured graphics program.
-We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings.
-In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the code.
-More generally, we believe the problem of inferring visual programs is a promising direction for research in machine perception.
-
-\bibliographystyle{unsrt}
-{\small \bibliography{main}}
-
 \end{document}

### 2018-09-07 poster.tex
poster

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jacobs Landscape Poster
% LaTeX Template
% Version 1.1 (14/06/14)
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
% 
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[final]{beamer}

\usepackage{listings}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{etoolbox}
\usepackage{booktabs}
\AtBeginEnvironment{algorithm}{%
  \setlength{\columnwidth}{\linewidth}%
}

\usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster
\usepackage{tipa}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usetheme{confposter} % Use the confposter theme supplied with this template
\usepackage{sidecap}
\setbeamercolor{block title}{fg=ngreen,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
% Many more colors are available for use in beamerthemeconfposter.sty

%-----------------------------------------------------------
% Define the column widths and overall poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708

\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usepackage{dsfont}

\newtheorem{proposition}{Proposition}
\newcommand{\expect}{\mathds{E}} %{{\rm I\kern-.3em E}}
\newcommand{\probability}{\mathds{P}} %{{\rm I\kern-.3em P}}
\newcommand{\indicator}{\mathds{1}} %{{\rm I\kern-.3em P}}

%\newtheorem{definition}{Definition}

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{76in} % A0 width: 46.8in
\setlength{\paperheight}{41in} % NIPS16 : 36
\setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.22\paperwidth} % Width of one column
\setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

\usepackage{etoolbox}
\makeatletter
\patchcmd{\beamer@@tmpl@headline}{wd=47in}{wd=75in}{}{}
\makeatother

\usepackage{graphicx}  % Required for including images
\usepackage{verbatim}
\usepackage{booktabs} % Top and bottom rules for tables
\usepackage{fancyvrb}
\DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays
% \DeclareMathOperator{\argmin}{argmin} % no space, limits underneath in displays
\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays
% \DeclareMathOperator{\argmax}{argmax} % no space, limits underneath in displays

\newcommand{\expect}{\mathds{E}} %{{\rm I\kern-.3em E}}
\newcommand{\probability}{\mathds{P}} %{{\rm I\kern-.3em P}}
\newcommand{\indicator}{\mathds{1}} %{{\rm I\kern-.3em P}}

\begin{SaveVerbatim}[]{ListSketch}
Program ::=
  (if Bool List
    (append RecursiveList
            RecursiveList
            RecursiveList))
Bool ::= (<= Int) | (>= Int)
Int  ::= 0 | (1+ Int) | (1- Int)
       | (length List) | (head List)
List ::= nil | (filter Bool List)
      | X | (tail List) | (list Int)
RecursiveList ::= List
                | (recurse List)
\end{SaveVerbatim}

\begin{SaveVerbatim}[]{TextSketch}
Program ::= Term | Program + Term
Term    ::= String | substr(Pos,Pos)
Pos     ::= Number
         |  pos(String,String,Number)
Number  ::= 0 | 1 | 2 | ... 
         | -1 | -2 | ...
String  ::= Character 
         |  Character + String
Character ::= a | b | c | ...
\end{SaveVerbatim}

\usepackage{wrapfig}

%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------
\usepackage{stmaryrd}
\newcommand{\tuple}[1]{\ensuremath{\left \langle #1\right \rangle}}
\newcommand{\sem}[1]{[\mkern-6mu[#1]\mkern-6mu]} %\newcommand{\sem}[1]{\llbracket #1\rrbracket}

\usetikzlibrary{trees}
\usetikzlibrary{fit}
\usetikzlibrary{calc}
\usetikzlibrary{bayesnet}

\usepackage{arydshln}

\usepackage[normalem]{ulem}
\newcommand{\theSystem}{\textsc{DreamCoder}}
\title{Learning to Infer Graphics Programs from Hand-Drawn Images} % Poster title

\author{Kevin Ellis, Daniel Ritchie, Lucas Morales, Mathias Sabl\'e Meyer,  Joshua B. Tenenbaum, Armando Solar-Lezama} % Author(s)

\institute{Massachusetts Institute of Technology \& Brown University} % Institution(s)

%----------------------------------------------------------------------------------------

\begin{document}
\addtobeamertemplate{headline}{} 
{\begin{tikzpicture}[remember picture, overlay]
     \node [anchor=north east, inner sep=3cm]  at (current page.north east)
           {\includegraphics[height=7cm]{figures/csail.png}};
                \node [anchor=north west, inner sep=3cm]  at (current page.north west)
     {\includegraphics[height=5cm]{figures/bcs.png}};
\end{tikzpicture}}

\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks

\setlength{\belowcaptionskip}{2ex} % White space under figures
\setlength\belowdisplayshortskip{2ex} % White space under equations

\begin{frame}[t] % The whole poster is enclosed in one beamer frame

\begin{columns}[t] % The whole poster consists of three major columns, the second of which is split into two columns twice - the [t] option aligns each column's content to the top

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The first column

%----------------------------------------------------------------------------------------
%	OBJECTIVES
%----------------------------------------------------------------------------------------

  \begin{alertblock}{Hand drawings to high-level graphics procedures}
    Convert image of hand drawing into $\LaTeX$ (left pair: top white is drawing, bottom black is $\LaTeX$ render). Infer high-level graphics program from drawing: captures higher-order structure like repetition, motifs, symmetries.
    \includegraphics[width = \textwidth]{firstPageExample.pdf}
\end{alertblock}

\begin{block}{Two-Stage Pipeline}
\hspace{-5cm}  \includegraphics[width = 50cm]{pipeline.pdf}

  Black arrows: Top--down generative model; Program$\to$Spec$\to$Image. {\color{red}Red} arrows: Bottom--up inference procedure. \textbf{Bold:} Random variables (image/spec/program)
\end{block}

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\begin{block}{Parsing Images into Drawing Commands (specs)}
\vspace{-3cm}  \includegraphics[width = 40cm]{architecture.pdf}

{\small   \textcolor{blue}{Blue}: network inputs. Black: network operations. \textcolor{red}{Red}: draws from a multinomial. \texttt{Typewriter font}: network outputs. Renders on a $16\times 16$ grid, shown in \textcolor{gray}{gray}. STN: differentiable attention mechanism. \textbf{Combined with stochastic search (Sequential Monte Carlo)}}

%\begin{figure}[h]\centering
  \begin{minipage}[c]{0.49\textwidth} 
    \centering  \includegraphics[width = \textwidth]{figures/drawingAccuracy.png}            \vspace{-0.5cm} 
  \end{minipage}\hfill%
      \begin{minipage}[c]{0.5\textwidth} 
  {\small (Left) NN outputs vs ground truth on hand drawings (measured by IoU), as we consider larger sets of samples (1, 5, 100).
     (a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 5 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth. Red: the full model. Other colors: ablations. Model is at ceiling for synthetic $\LaTeX$ output.}
      \end{minipage}

%\end{figure}
\end{block}

%% \begin{block}{Problem Framing}
%%   \begin{itemize}
%%   \item Sketch specifies a large but finite set of programs, $S$
%%   \item Program description length: $\lvert x \rvert$ for $x\in S$
%%   \item Prior over programs: $\propto 2^{- \lvert x \rvert }$
%%   \item Posterior over programs: call this $p(x)$, defined as $\propto 2^{- \lvert x \rvert } \mathds{1}[x \text{ consistent with input/output examples}]$
%%   \end{itemize}
%%   Our goal then  is to sample from $p(\cdot)$.
%% \end{block}

%------------------------------------------------

%----------------------------------------------------------------------------------------

\end{column} % End of the first column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\twocolwid} % Begin a column which is two columns wide (column 2)

\begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column

\begin{column}{\onecolwid}\vspace{-.6in} % The first column within column 2 (column 2.1)

%----------------------------------------------------------------------------------------
%	MATERIALS
%----------------------------------------------------------------------------------------
%

%%  \begin{alertblock}{Bayesian Program Learning \& other approaches} %
    %% Why might a learner represent knowledge as a program,
    %% rather than the representations popular in much of machine learning,
    %% such as a large matrix of weights or a graphical model?
    %% Programs (probabilistic or deterministic)
    %% excel at representing knowledge that is (1) symbolic; (2) compositional; or (3) higher-order.
    %% We are motivated by the success of program induction
    %% in both AI domains,
    %% like semantic parsing and programming by demonstration,
    %% and in cognitive modeling,
    %% like intuitive theory learning~\cite{logical}.
%%\end{alertblock}

  \begin{block}{Domain-Specific Language for Graphics Programs}
 We allow loops (\texttt{for}) with conditionals (\texttt{if}), vertical/horizontal reflections (\texttt{reflect}), variables (Var) and affine transformations ($\mathbb{Z}\times$Var\texttt{+}$\mathbb{Z}$).
  \begin{tabular}{rl}\toprule
  Program$\to$&Statement; $\cdots$; Statement\\
  Statement$\to$&\texttt{circle}(Expression,Expression)\\
  Statement$\to$&\texttt{rectangle}(Expression,Expression,Expression,Expression)\\
  Statement$\to$&\texttt{line}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
  Statement$\to$&\texttt{for}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ if }$(\text{Var} > 0)$\texttt{ \{ }Program\texttt{ \}; }Program\texttt{ \}}\\
  Statement$\to$&\texttt{reflect}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
  Expression$\to$&$\mathbb{Z}\times$Var\texttt{+}$\mathbb{Z}$\\
%  Var$\to$&A free (unused) variable\\
  Axis$\to$&\texttt{X = }$\mathbb{Z}$ | \texttt{Y = }$\mathbb{Z}$\\
    $\mathbb{Z}\to$&an integer\\\bottomrule
  \end{tabular}
  \end{block}

  \begin{block}{Learning \& Constraint-Based Program Synthesis}
    \textbf{Sketch}: state-of-the-art program synthesizer. Solar-Lezama 2008.\\Solves, for spec $S$ \& program $p$:
$$
  \text{program}(S) = \argmin_{p\in \text{DSL, s.t. }p \text{ consistent w/ } S} \text{cost}(p)\label{programObjective}
$$
  \textbf{Learn policy $\pi_\theta$ to accelerate program synthesizer's search.}\\ $\pi_\theta(\cdot |S) \in  \Delta^\Sigma$,
  where $\Sigma\ni\sigma $ a set of synthesis problem (i.e., $\sigma \in \Sigma $ is a sketch)

%%   \noindent\textbf{Definition: Bias-optimality.}  (c.f. Schmidhuber 2004)
%%    A search algorithm is $n$-\emph{bias optimal}
%% with respect to a distribution $\probability_{\text{bias}}[\cdot ]$ if it is
%% guaranteed to find a solution in $\sigma $ after searching for at least time
%% $n\times\frac{t(\sigma )}{\probability_{\text{bias}}[\sigma ]}$, where $t(\sigma )$ is the time it
%% takes to verify that $\sigma $ contains a solution to the
%% search problem.

%% Here, $\probability_{\text{bias}}[\cdot ] = \pi_\theta(\cdot |S)$.
\textbf{Inference strategy}: Timeshare according to $\pi_\theta(\cdot |S)$, like in Levin Search
  \begin{figure}\centering
  \begin{tikzpicture}[scale=3]
    \node[anchor = west] at (0,5.25) {Entire program search space};
    \draw[fill = yellow,fill opacity = 0.15,draw = black] (0,0) rectangle (5,5);
    \draw [fill = yellow, opacity = 0.2] (0,0)--(0,2)--(4,0)--(0,0);
    \draw [fill = yellow, opacity = 0.4,cycle] (0,5)--(0,1)--(3,5);
    \draw [fill = yellow, opacity = 0.6,cycle] (2.5,5)--(3.2,0)--(5,0)--(5,5);
    \draw (0,2) -- node[below,sloped]{short programs} (4,0);
    \draw (0,2) -- node[above,sloped]{long programs} (4,0);
    \draw (2.5,5) -- node[above,sloped]{programs w/ reflections} (3.2,0);
    \draw (0,1) -- node[above,sloped]{ programs w/ loops} (3,5);
    \node(p1)[anchor =west ] at (5.5,3.5) {$\pi_\theta(\text{short, no loop/reflect}) = $};
    \draw [fill = yellow, fill opacity = 0.2,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p1.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p1.east);
    \node(p2)[anchor =west ] at ([yshift = -0.5cm]p1.west) {$\pi_\theta(\text{long, loops}) = $};
    \draw [fill = yellow, fill opacity = 0.4,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p2.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p2.east);
    \node(p3)[anchor =west ] at ([yshift = -0.5cm]p2.west) {$\pi_\theta(\text{long, no loop/reflect}) = $};
    \draw [fill = yellow, fill opacity = 0.15,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p3.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p3.east);
    \node(p4)[anchor =west ] at ([yshift = -0.5cm]p3.west) {$\pi_\theta(\text{long, reflects}) = $};
    \draw [fill = yellow, fill opacity = 0.6,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p4.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p4.east);
    \node(p5)[anchor =west ] at ([yshift = -0.5cm]p4.west) {\emph{etc.}};
  \end{tikzpicture}
  \caption{The bias-optimal search algorithm divides the entire (intractable) program search space in to (tractable) program subspaces (written $\sigma $), each of which contains a restricted set of programs. For example, one subspace might be short programs which don't loop. The policy $\pi$ predicts a distribution over program subspaces:  weight assigned by $\pi$ indicated by  shading}
\end{figure}

Differentiable loss ($\mathcal{D}$ a corpus of synthesis problems):
\begin{align}
\textsc{Loss}(\theta ; \mathcal{D})& =  \expect_{S\sim\mathcal{D}}\left[ \min_{\sigma\in \text{\textsc{Best}}(S)}\frac{t(\sigma | S)}{\pi_\theta (\sigma | S)}\right] + \lambda \Vert\theta\Vert_2^2\label{policyLoss}\\
\text{where }  \sigma \in\text{\textsc{Best}}(S) &\text{ if  a minimum cost program for }S \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t. }p\text{ evaluates to }S} \text{cost}(p) \nonumber
\end{align}

\includegraphics[width = \textwidth]{figures/policyComparison_basic_DC+bias_20.png}

Time to synthesize a minimum cost program. Sketch: out-of-the-box performance of Sketch. DC: Deep--Coder style baseline that predicts program components, trained like Balog 2016. Oracle:  upper bounds  the performance of any bias--optimal search policy. $\infty = $ timeout. Red dashed line is median time
  \end{block}

%----------------------------------------------------------------------------------------

\end{column} % End of column 2.1

\begin{column}{\onecolwid}\vspace{-.6in} % The second column within column 2 (column 2.2)

%----------------------------------------------------------------------------------------
%	METHODS
%----------------------------------------------------------------------------------------

  \begin{block}{Extrapolating Drawings}
    Automatically extrapolate by increasing loop bounds. Top white: Hand drawing. Bottom black: extrapolation.

      \includegraphics[width = \textwidth]{figures/extrapolationMatrix1.png}\\
  \includegraphics[width = \textwidth]{figures/extrapolationMatrix2.png}\\
  \includegraphics[width = \textwidth]{figures/extrapolationMatrix3.png}  \\
\end{block}

  \begin{block}{Example System Outputs}
\includegraphics[width = \textwidth]{examplePrograms.pdf} 
\end{block}

\begin{block}{Learning from very few examples}
\begin{figure}[h]\centering
  \begin{minipage}{0.45\textwidth}\centering
    \includegraphics[width=\textwidth]{smallFractionSolving.png}
  \caption{Results averaged across 19 problems. Solid: \theSystem{} . Dashed: enumerating 100 programs. Dotted: MDL.}\label{flashPerformance}        \end{minipage}%
\hspace{0.025\textwidth}\begin{minipage}{0.45\textwidth}\centering
    \includegraphics[width=0.7\textwidth]{small_mdl.png}
    \caption{MDL learner vs \theSystem{} on one-shot learning. Predictions marginalize out the program.}\label{mdl}
  \end{minipage}
\end{figure}

%\textbf{Multiple explanations aids one-shot learning.} After a single example, the shortest program is probably not correct -- but one of the top sampled \emph{behaviors} (marginalizing over the program) might be.

\textbf{Good performance needs tilt correction.} w/o low-tilt approximation, get no samples for any of these problems after an hour, vs $\approx 1$ minute w/ \theSystem

\end{block}

%% \begin{block}{The Cost of Sampling}
%%   Amortized cost of 100 samples from \theSystem :

%%   \vspace{1cm}

%%   \hspace{9cm}\vspace{1cm}    \begin{tabular}{lll}\toprule
%%      1 example\hspace{0.9cm}      &  2 examples\hspace{0.9cm}          &     3 examples\\\midrule
%% $84 \pm 3$ sec &$21 \pm 1$ sec & $49\pm 3$ sec
%% \end{tabular}

%% \textbf{Good performance needs tilt correction.} w/o low-tilt approximation, get no samples for any of these problems after an hour!

%% \textbf{Can closely approximate posterior with little overhead.}

%% %\vspace{-2.5cm}
%% \begin{tabular}{cl}
%%   \begin{tabular}{c}
%%     \includegraphics[width=25cm]{trim-trade-off.png}
%%     \end{tabular}&
%%   \begin{tabular}{l}
%%     \parbox{15cm}{Accuracy (colored contours) vs Performance (monochrome cells) trade-off; upper bounds plotted. Performance measured in expected solver invocations; accuracy measured in log KL divergence.}
%%     \end{tabular}
%% \end{tabular}
%% %\end{figure}

%%   \end{block}
%----------------------------------------------------------------------------------------

\end{column} % End of column 2.2

\end{columns} % End of the split of column 2 - any content after this will now take up 2 columns width

%----------------------------------------------------------------------------------------

\begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column again

 % End of column 2.1

\begin{column}{\onecolwid} % The second column within column 2 (column 2.2)

%----------------------------------------------------------------------------------------
%	RESULTS
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------

\end{column} % End of column 2.2

\end{columns} % End of the split of column 2

\end{column} % End of the second column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The third column

%----------------------------------------------------------------------------------------
%	CONCLUSION
%----------------------------------------------------------------------------------------

  \begin{alertblock}{NEW: Wake-Sleep DSL learning with \theSystem}

    \begin{minipage}[c]{0.45\textwidth}
    \begin{itemize}
    \item \textbf{Wake:} Synthesize programs from DSL + neural net (`recognition model') to guide search
    \item \textbf{Sleep-G:} Grow DSL, using grammar induction algorithms
    \item \textbf{Sleep-R:} Train neural net on programs found during waking (`experience replay') and samples from DSL (`dreaming')
    \end{itemize}
    \end{minipage}%
    \begin{minipage}[c]{0.48\textwidth}      
    \begin{tikzpicture}[scale=3,line width=1.5mm]
    \begin{scope}[shift = {(1,-1)}]
    \node[align = center](synthesis) at (6,4) {Search for \\programs: $p$};
    \node[align = center](DSL) at (3,1) {DSL: $\mathcal{D}$};
    \node[align = center](recognitionModel) at (9,1) {Recognition \\model: $Q$};

    \draw [->] (synthesis.-120) to[out = -150,in = 60] node[below,rotate = 45,align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-G)}} (DSL.30);
    \draw [->] (synthesis.-60) to[out = -30,in = 120] node[below,rotate=-45,align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-R)}} (recognitionModel.150);
    \draw [->] (DSL.east) to[out = -30,in = 210] node[above, align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-R)}} (recognitionModel.west);

    \draw [->,dashed] (DSL.north) to[out = 90,in = 180] node[fill=dblue!10,align = center]{  \footnotesize{Inductive bias}\\\footnotesize{(Wake)}} (synthesis.west);
    \draw [->,dashed] (recognitionModel.north) to[out = 90,in = 0] node[fill=dblue!10,align = center]{{\footnotesize Makes tractable}\\{\footnotesize (Wake)}} (synthesis.east);
  \end{scope}
    \end{tikzpicture}
      \end{minipage}
  \end{alertblock}

\begin{block}{\theSystem~outputs for three different task domains}

\hspace{-2cm}\includegraphics[width = 1.15\textwidth]{figures/3DSL.png}
{\small Top: Tasks from three domains we apply our algorithm to, each followed by the programs \theSystem~ discovers for them. Bottom: Several examples from learned DSL. Notice that learned DSL primitives can call each other, and that \theSystem~rediscovers higher-order functions like \code{filter} ($f_1$ under List Functions)}
\end{block}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{block}{Bayesian framing}

  \begin{minipage}[c]{0.45\textwidth}
      \begin{tikzpicture}[scale=4,line width=1.5mm]

  \node[latent,scale=3] at (3.5,3) (dx){$\mathcal{D}$};
  \node[latent,scale=3] at ([xshift=2cm]dx) (zp){$p_n$};
  \node[obs,scale=3] at ([xshift=2cm]zp) (xp) {$x_n$};
  \plate {}{(zp)(xp)}{};
%  \node[align = center] at ([yshift = -1.2cm,xshift = 1cm]xp.east) {(b) \\recognition model};
  \draw [->,red] (xp.south) to[out = -90,in = -90] node(nn){} (zp.south);
%  \draw [->,red] (tx.west) -- (zp.east);
  \draw [->] (dx.east) -- (zp.west);
  \draw [->] (zp.east) -- (xp.west);

  \node at (nn) {
    \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=0.5,shift={+(-1,2.5)}}]
      \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
      \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
      \node[rectangle] at (1,1) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (I-\name) at (0,-\y) {};
      \foreach \name / \y in {1,...,3}
          \node[neuron] (H-\name) at (1,-\y-0.5) {};
      \foreach \name / \y in {1,...,4}
          \node[neuron] (O-\name) at (2,-\y) {};
      \foreach \source in {1,...,4}
          \foreach \dest in {1,...,3}
              \draw [-latex] (I-\source) -- (H-\dest);
      \foreach \source in {1,...,3}
          \foreach \dest in {1,...,4}
              \draw [-latex] (H-\source) -- (O-\dest);
    \end{tikzpicture}
  };
  \node[shift={+(0,-1.7)}] at (nn) { $Q$  };

      \end{tikzpicture}
      $x_n$: program synthesis problem. $p_n$: (latent) program solving $x_n$. $Q(p|x)$: (learned) neural recognition model. $\mathcal{D}$: (latent) DSL.
  \end{minipage}\qquad%
  \begin{minipage}[c]{0.4\textwidth}

  $$
\underbrace{p_n^* =   \argmax_{p_n}\probability[x_n|p_n]\probability[p_n|\mathcal{D}^*]}_{\text{\textbf{Wake}}}
$$
\vspace{0.5cm}
$$
\underbrace{\mathcal{D}^* = \argmax_{\mathcal{D}}    \probability[\mathcal{D}]\prod_n\sum_{p_n}\probability[x_n|p_n]\probability[p_n|\mathcal{D}]}_{\textbf{\text{Sleep-G}}}
$$
\vspace{0.5cm}
$$\underbrace{Q^* = \argmin_Q \text{KL}\left(\probability[p|x,\mathcal{D}] || Q(p|x)\right) }_{\text{\textbf{Sleep-R}}}$$
    \end{minipage}

\end{block}

%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

\setbeamercolor{block title}{fg=red,bg=white} % Change the block title color
%% \begin{block}{References}

%%   %\nocite{*} % Insert publications even if they are not cited in the poster
%%   \renewcommand{\refname}{\vspace{-0.8em}}
%%           \bibliographystyle{plain}
%%           \bibliography{main}
%% %\small{\bibliographystyle{plain}
%% %\bibliography{main}}

%% \end{block}

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\setbeamercolor{block title}{fg=red,bg=white} % Change the block title color

%% \begin{block}{Acknowledgements}

%% \small{\rmfamily{We are grateful for feedback from Adam Smith, Kuldeep Meel, and our anonymous reviewers.
%% Work supported by AFOSR award FA9550-16-1-0012.}} \\

%% \end{block}

%----------------------------------------------------------------------------------------
%	CONTACT INFORMATION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------

\end{column} % End of the third column

\end{columns} % End of all the columns in the poster

\end{frame} % End of the enclosing frame

\end{document}

### 2018-09-21 nips_2018.tex
progress on camera ready

@@
 % ready for submission
-\usepackage{nips_2018}
+\usepackage[final]{nips_2018}
 
@@
 
-\author{Kevin Ellis\\
-  MIT\\
-  \texttt{ellisk@mit.edu} \\
-  \And
-  Daniel Ritchie\\
-Brown University\\
- \texttt{daniel\_ritchie@brown.edu} \\
- \And
- Armando Solar-Lezama\\
- MIT\\
-\texttt{asolar@csail.mit.edu} \\
-\And
-Joshua B. Tenenbaum \\
-MIT\\
-\texttt{jbt@mit.edu}
+\author{Kevin Ellis$^{1,*}$\qquad Daniel Ritchie$^2$\qquad  Armando Solar-Lezama$^1$\qquad Joshua B. Tenenbaum$^1$\\
+  $^1$Massachusetts Institute of Technology\qquad $^2$Brown University\\
+  $^*$Primary contact: \texttt{ellisk@mit.edu}%% \\
+%%   \texttt{ellisk@mit.edu} \\
+%%   \And
+%%   Daniel Ritchie\\
+%% Brown University\\
+%%  \texttt{daniel\_ritchie@brown.edu} \\
+%%  \And
+%%  Armando Solar-Lezama\\
+%%  MIT\\
+%% \texttt{asolar@csail.mit.edu} \\
+%% \And
+%% Joshua B. Tenenbaum \\
+%% MIT\\
+%% \texttt{jbt@mit.edu}
   %% Affiliation \\
@@
 
-\begin{figure}[h]\centering
+\begin{figure}[h]\vspace{-1cm}\centering
   \begin{minipage}[c]{0.57\textwidth} 
@@
   \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1, 5, 100)?
-    Distance to ground truth measured by the intersection over union (IoU) of predicted vs.
-ground truth: IoU of sets $A$ and $B$ is $|A\cap B|/|A\cup B|$.
+    Distance to ground truth measured by the intersection over union (IoU) of predicted spec vs.
+ground truth spec: IoU of sets (specs) $A$ and $B$ is $|A\cap B|/|A\cup B|$.
 (a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 5 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth.
@@
 Compared to the specs the programs are more compressive (right: programs have fewer lines than specs) and automatically group together related drawing commands.
-Note the nested loops  and conditionals in the Ising model, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
+Note the nested loops in second figure, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
 %  \vspace{-0.6cm}
@@
 %% \end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
-    \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
-\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-Circle(5,8)
-Circle(2,8)
-Circle(8,11)
-Line(2,9, 2,10)
-Circle(8,8)
-Line(3,8, 4,8)
-Line(3,11, 4,11)
-\end{lstlisting}
-  \small\emph{... etc. ...; 21 lines}
-\end{minipage}&\begin{minipage}{\exampleProgramSize}
-\begin{lstlisting}
-for(i<3)
- for(j<3)
-  if(j>0)
-   line(-3*j+8,-3*i+7,
-        -3*j+9,-3*i+7)
-   line(-3*i+7,-3*j+8,
-        -3*i+7,-3*j+9)
-  circle(-3*j+7,-3*i+7)
-\end{lstlisting}
-\end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
+%%     \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
+%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
+%% Circle(5,8)
+%% Circle(2,8)
+%% Circle(8,11)
+%% Line(2,9, 2,10)
+%% Circle(8,8)
+%% Line(3,8, 4,8)
+%% Line(3,11, 4,11)
+%% \end{lstlisting}
+%%   \small\emph{... etc. ...; 21 lines}
+%% \end{minipage}&\begin{minipage}{\exampleProgramSize}
+%% \begin{lstlisting}
+%% for(i<3)
+%%  for(j<3)
+%%   if(j>0)
+%%    line(-3*j+8,-3*i+7,
+%%         -3*j+9,-3*i+7)
+%%    line(-3*i+7,-3*j+8,
+%%         -3*i+7,-3*j+9)
+%%   circle(-3*j+7,-3*i+7)
+%% \end{lstlisting}
+%% \end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
 \includegraphics[width = \exampleDrawingSize]{figures/expert-101-trim.png}&
@@
 Line(13,10,13,14,arrow)
-  \end{lstlisting}\small\emph{... etc. ...; 16 lines}%
+  \end{lstlisting}\small\emph{... etc. ...; 16 lines}
   \end{minipage}&\begin{minipage}{\exampleProgramSize}
@@
 %  \includegraphics[width = \textwidth]{figures/extrapolationMatrix3.png}  
-   \caption{Top, white: hand drawings. Bottom, black: extrapolations produced by our system.}
-  \label{extrapolationFigure}
+   \caption{Top, white: drawings. Bottom, black: extrapolations automatically produced by our system.}
+  \label{extrapolationFigure}\vspace{-0.25cm}
   \end{figure}
 %\input{extrapolations.tex}
-
-% \remark{Seems like you're still fleshing this part out, but I'll give my feedback anyway: (1) This subsection could really use a motivational introduction, e.g.
-``The program synthesizer can help correct errors/bad proposals from the neural network by favoring execution traces which lead to more concise/general programs.'' (2) The image likelihood function should probably be introduced sooner, when you talk about SMC/beam search.
-(3) Where does $\theta$ come from?
-Is it set by hand?
-Learned?
-(4) How does Eq.
-4 get used?
-Is this a modification to the beam search objective / SMC posterior?
-If so, it'd be great to have set up the version without it in an earlier section, and then be able to refer to this as a small modification of the previous equation.}
 
@@
 experiments motivate our use of constraint-based techniques.
+Neurally Guided Deductive Search (NGDS:~\cite{ngds})
+is a recent neurosymbolic approach;
+combining our work with ideas from NGDS could be promising.
 
 \textbf{Deep Learning:} Our neural network combines the architectural ideas of Attend-Infer-Repeat~\citep{eslami1603attend} -- which learns to decompose an image into its constituent objects -- with the training regime and SMC inference  of Neurally Guided Procedural Modeling~\cite{ritchie2016neurally} -- which learns to control procedural graphics programs.
+The very recent SPIRAL~\cite{ganin2018synthesizing}  system
+learns to infer
+procedures for controlling a `pen' to derender highly diverse natural images,
+complementing our focus here on more abstract
+procedures but less natural images.
 %AIR learns an iterative inference scheme which infers objects one by one and also decides when to stop inference.
@@
 %Finally, while AIR was evaluated on multi-MNIST images and synthetic 3D scenes, we focus on hand-drawn sketches.
-IM2LATEX~\citep{im2latex} is a recent work that 
- derenders  \LaTeX~ equations,
-recovering a markup language representation.
+IM2LATEX~\citep{im2latex} and pix2code~\cite{DBLP:journals/corr/Beltramelli17} are recent works that 
+ derender  \LaTeX~ equations and GUIs, respectively,
+both recovering a markup-like representation.
 Our goal is to go from
@@
 This work  compliments our own: programs produced by our method could be provided to a Sketch-n-Sketch-like system as a starting point for further editing.
-Other systems in the computer graphics literature convert sketches to procedural representations, using a convolutional network to match a sketch to the output of a parametric 3D modeling system in~\citep{huang2017shape} or supporting interactive sketch-based instantiation of procedural primitives in~\citep{Nishida:2016:ISU:2897824.2925951}.
+Other systems in the computer graphics literature convert sketches to procedural representations, e.g.
+using a convolutional network to match a sketch to the output of a parametric 3D modeling system in~\citep{huang2017shape}.
+%% or supporting interactive sketch-based instantiation of procedural primitives in~\citep{Nishida:2016:ISU:2897824.2925951}
 In contrast, we seek to automatically infer a programmatic representation capturing higher-level visual patterns.
@@
 in our system the user need not annotate which strokes correspond to which shapes; our neural network produces something equivalent to the annotations).
-
+%\vspace{-0.51cm}
 \section{Contributions}
 
-We have presented a system for inferring graphics programs which generate \LaTeX-style figures from hand-drawn images.
-The system uses a combination of deep neural networks and stochastic search to parse drawings into symbolic specifications; it then feeds these specs to a general-purpose program synthesis engine to infer a structured graphics program.
-We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings.
-In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the code.
+We have presented a system for inferring graphics programs which generate \LaTeX-style figures from hand-drawn images using a combination of learning, stochastic search, and program synthesis.
+%We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings.
+In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an AI write the code.
 More generally, we believe the problem of inferring visual programs is a promising direction for research in machine perception.
+\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on the design of the neural architecture. Work funded by NSF GRFP (K.E.) and NSF Award 
+\#1753684 (D.R.)
 

### 2018-09-22 long.tex
long version of the paper

--- 2018-09-07 nips_2018.tex
@@
 coordinates to lie on a discrete $16\times 16$ grid,
-but the grid could be made arbitrarily fine.  %% See supplement for the full details
+but the grid could be made arbitrarily fine. Appendix~\ref{architectureDetails} gives full architectural detail.  %% See supplement for the full details
 %% of the architecture, which we implemented in
@@
 
-%% For the model in Fig.~\ref{architecture}, the distribution over the next drawing command factorizes as:
-%% \begin{equation}
-%%   \probability_\theta [t_1t_2\cdots t_K | I,T] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(T)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
-%% \end{equation}
-%% where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
-%% the target image, $T$ is a trace set, $\theta$ are the
-%% parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
-%% image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
-%% traces factorizes as:
-%% \begin{equation}
-%%   \probability_\theta [T|I] = \prod_{n = 1}^{|T|} \probability_\theta [T_n | I,T_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,T]\label{objective}
-%% \end{equation}
-%% where $|T|$ is the length of trace set $T$, the subscripts
-%% on $T$ index drawing commands within the trace (so $T_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
-%% token is emitted by the network to signal that the trace set
-%% explains the image.
+For the model in Fig.~\ref{architecture}, the distribution over the next drawing command factorizes as:
+\begin{equation}
+  \probability_\theta [t_1t_2\cdots t_K | I,S] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(S)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
+\end{equation}
+where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
+the target image, $S$ is a spec, $\theta$ are the
+parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
+image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
+specs factorizes as:
+\begin{equation}
+  \probability_\theta [S|I] = \prod_{n = 1}^{|S|} \probability_\theta [S_n | I,S_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,S]\label{objective}
+\end{equation}
+where $|S|$ is the length of spec $S$, the subscripts
+on $S$ index drawing commands within the spec (so $S_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
+token is emitted by the network to signal that the spec
+explains the image.
 We trained our network by sampling specs $S$ and target
-images $I$ for randomly generated scenes
+images $I$ for randomly generated scenes\footnote{Because the rendering process ignores the ordering of drawing commands in the spec, the mapping from spec to image is many-to-one.
+When generating random training data for the neural network, we put the drawing commands into a canonical order (left-to-right, top-to-bottom, first drawing circles, then rectangles, and finally lines/arrows.)}
 and maximizing $\probability_\theta[S|I]$,
@@
 Here, the network is learning a proposal distribution to amortize the cost of inverting a generative model (the renderer)~\citep{paige2016inference}.
-%% Unconventionally, the target distribution of the SMC sampler
-%% includes the likelihood under the proposal distribution.
-%% Intuitively, both the proposal
-%% distribution and the distance function offer complementary signals for
-%% whether a drawing command is correct.
+Unconventionally, the target distribution of the SMC sampler
+includes the likelihood under the proposal distribution.
+Intuitively, both the proposal
+distribution and the distance function offer complementary signals for
+whether a drawing command is correct,
+and we found that combining these signals gave higher accuracy.
 
@@
   with SMC against the neural network by
-itself or SMC by itself.  Only the combination of the two passes a
+itself (using beam search) or SMC by itself.  Only the combination of the two passes a
 critical test of generalization: when trained on images with $\leq 12$
@@
 training data.
-We compare with a baseline that produces the spec in one shot by
+We also compare with a baseline that produces the spec in one shot by
 using the CNN to extract features of the input which are passed to an LSTM which finally predicts
-the spec token-by-token (LSTM in Fig.~\ref{syntheticResults}).
+the spec token-by-token (LSTM in Fig.~\ref{syntheticResults}; Appendix~\ref{captioningBaseline}).
 This architecture is used in several successful neural models of image captioning (e.g.,~\cite{vinyals2015show}),
@@
 Neither SMC nor the neural network are sufficient on their own.
-\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}\vspace{-1.5cm}
+\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}%\vspace{-1.5cm}
 \end{wrapfigure}
@@
 \subsection{Generalizing to real hand drawings}\label{generalizingTheHandDrawings}
-%% \begin{wrapfigure}{R}{6cm}
-%% \centering\vspace{-0.7cm}  \begin{minipage}[t]{2.5cm}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
-%%     \subcaption{}
-%%   \end{minipage}\\
-%%    \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
-%%     \subcaption{}
-%%   \end{minipage}%
-%%   \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
-%%     \subcaption{}
-%%   \end{minipage}%
-%%     \caption{(a): hand drawing. (b): Rendering of the trace set our model infers for (a). (c): noisy rendering of (b).}\label{handDrawingExamples}
-%% \end{wrapfigure}
+\begin{wrapfigure}{R}{6cm}
+\centering\vspace{-0.7cm}  \begin{minipage}[t]{2.5cm}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
+    \subcaption{hand drawing}
+  \end{minipage}\\
+   \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
+    \subcaption{rendering of (a)'s inferred spec}
+  \end{minipage}\qquad% 
+  \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
+    \subcaption{noisy rendering of (b)}
+  \end{minipage}%
+  \caption{Noisy renderings produced in \LaTeX~Ti\emph{k}Z w/ \texttt{pencildraw} package (Appendix~\ref{noisyAppendix})}
+    \label{handDrawingExamples} 
+\end{wrapfigure}
 
@@
 to generalize to hand drawings by introducing noise into the
-renderings of the training target images, where the noise process  mimics the kinds of variations found in hand drawings (%% Fig.~\ref{handDrawingExamples}; 
-see supplement for details).
+renderings of the training target images, where the noise process  mimics the kinds of variations found in hand drawings (Fig.~\ref{handDrawingExamples}).
 While our neurally-guided SMC procedure
@@
   \end{equation}
+  Appendix~\ref{distanceAppendix} details the architecture and training of $L_{\text{learned}}$.
 
@@
     These were drawn carefully but not perfectly with the aid of graph paper.
-%Because our model assumes that objects are snapped to a $16\times 16$ grid, 
-%we made the drawings on graph paper.
     For each drawing we annotated a ground truth spec and had the neurally guided SMC sampler
@@
 corrects some of these small errors (Sec.~\ref{synthesizerHelpsParsing}).
-%% Because the model sometimes makes mistakes % on hand drawings,
-%% we envision it working as follows:
-%% a user sketches a diagram,
-%% and the system responds by proposing a few candidate interpretations.
-%% The user could then select the one closest to their intention and edit it if necessary.
-
+Because the model sometimes makes mistakes on hand drawings,
+we envision it working as follows:
+a user sketches a diagram,
+and the system responds by proposing a few candidate interpretations.
+The user could then select the one closest to their intention and edit it if necessary.
+
+%\pagebreak
 \setlength\tabcolsep{3.5pt}
@@
 
-We constrain the space of programs by writing down a context
-free grammar over  programs -- 
-%Although it might be desirable to synthesize programs in a Turing-complete language such as Lisp or Python, a more tractable approach is to specify
+Although it might seem desirable to synthesize programs in a Turing-complete language such as Lisp or Python, a more tractable approach is to specify
 what in the program
@@
 cost of a program to be the number of Statement's it contains (Tbl.~\ref{DSL}).
-We also penalize using many different numerical constants; see supplement.
+We also penalize using many different numerical constants; see Appendix~\ref{costAppendix}.
 Returning to the generative model in Fig.~\ref{roadmap},
@@
      \end{minipage}&$\frac{6}{3} = 2\text{x}$\\\midrule
-%%      \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
-%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-%% Line(5,13,2,10,arrow)
-%% Circle(5,9)
-%% Circle(8,5)
-%% Line(2,8, 2,6,arrow)
-%% Circle(2,5)
-%% \end{lstlisting}
-%% \small\emph{... etc. ...; 13 lines}
-%% \end{minipage}&
-%%              \begin{minipage}{\exampleProgramSize}\begin{lstlisting}
-%% circle(4,10)
-%% for(i<3)
-%%  circle(-3*i+7,5)
-%%  circle(-3*i+7,1)
-%%  line(-3*i+7,4,-3*i+7,2,arrow)
-%%  line(4,9,-3*i+7,6,arrow)
-%% \end{lstlisting}
-%% \end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
+     \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
+\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
+Line(5,13,2,10,arrow)
+Circle(5,9)
+Circle(8,5)
+Line(2,8, 2,6,arrow)
+Circle(2,5)
+\end{lstlisting}
+\small\emph{... etc. ...; 13 lines}
+\end{minipage}&
+             \begin{minipage}{\exampleProgramSize}\begin{lstlisting}
+circle(4,10)
+for(i<3)
+ circle(-3*i+7,5)
+ circle(-3*i+7,1)
+ line(-3*i+7,4,-3*i+7,2,arrow)
+ line(4,9,-3*i+7,6,arrow)
+\end{lstlisting}
+\end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
     \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
@@
 
-A search policy $\pi_\theta(\sigma  | S )$ takes as input a spec $S$ and predicts a distribution over synthesis problems, each of which is written $\sigma $ and corresponds to a set of possible programs to search over (so $\sigma \subseteq \text{DSL}$).
+Formally, our search policy, $\pi_\theta(\sigma  | S )$, takes as input a spec $S$ and predicts a distribution over search problems, each of which is written $\sigma $ and corresponds to a set of possible programs to search over (so $\sigma \subseteq \text{DSL}$).
+We assume a finite\footnote{It is not strictly necessary that $\Sigma$ be a finite set, only that it be recursively enumerable.
+For example, Levin Search considers the setting where the infinite set of all Turing machines serves as $\Sigma$.} family of
+search problems, which we write $\Sigma$,
+and require that every program in the DSL
+is contained in at least one $\sigma \in \Sigma$.
+
 Good policies will prefer tractable program spaces,
@@
 We construct a $1$-bias optimal search algorithm by identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |S)$ and $t(\sigma )  = t(\sigma|S)$, where $t(\sigma|S)$ is how long the synthesizer takes to search $\sigma $ for a program for $S$.
-This means that the search algorithm explores the entire program space, but spends most of its time in the regions of the space that  the policy judges to be most promising.
-
-%% \begin{figure}\centering
-%%   \begin{tikzpicture}
-%%     \node[anchor = west] at (0,5.25) {Entire program search space};
-%%     \draw[fill = yellow,fill opacity = 0.15,draw = black] (0,0) rectangle (5,5);
-%%     \draw [fill = yellow, opacity = 0.2] (0,0)--(0,2)--(4,0)--(0,0);
-%%     \draw [fill = yellow, opacity = 0.4,cycle] (0,5)--(0,1)--(3,5);
-%%     \draw [fill = yellow, opacity = 0.6,cycle] (2.5,5)--(3.2,0)--(5,0)--(5,5);
-%%     \draw (0,2) -- node[below,sloped]{short programs} (4,0);
-%%     \draw (0,2) -- node[above,sloped]{long programs} (4,0);
-%%     \draw (2.5,5) -- node[above,sloped]{programs w/ reflections} (3.2,0);
-%%     \draw (0,1) -- node[above,sloped]{ programs w/ loops} (3,5);
-%%     \node(p1)[anchor =west ] at (5.5,3.5) {$\pi_\theta(\text{short, no loop/reflect}) = $};
-%%     \draw [fill = yellow, fill opacity = 0.2,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p1.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p1.east);
-%%     \node(p2)[anchor =west ] at ([yshift = -0.5cm]p1.west) {$\pi_\theta(\text{long, loops}) = $};
-%%     \draw [fill = yellow, fill opacity = 0.4,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p2.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p2.east);
-%%     \node(p3)[anchor =west ] at ([yshift = -0.5cm]p2.west) {$\pi_\theta(\text{long, no loop/reflect}) = $};
-%%     \draw [fill = yellow, fill opacity = 0.15,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p3.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p3.east);
-%%     \node(p4)[anchor =west ] at ([yshift = -0.5cm]p3.west) {$\pi_\theta(\text{long, reflects}) = $};
-%%     \draw [fill = yellow, fill opacity = 0.6,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p4.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p4.east);
-%%     \node(p5)[anchor =west ] at ([yshift = -0.5cm]p4.west) {\emph{etc.}};
-%%   \end{tikzpicture}
-%%   \caption{The bias-optimal search algorithm divides the entire (intractable) program search space in to (tractable) program subspaces (written $\sigma $), each of which contains a restricted set of programs.
+Intuitively, this means that the search algorithm explores the entire program space, but spends most of its time in the regions of the space that  the policy judges to be most promising.
+Concretely,
+this means that our
+synthesis strategy is to
+run many different
+program searches \emph{in parallel} (i.e., run in parallel different instances of the synthesizer, one for each  $\sigma\in \Sigma$),
+but to allocate
+compute time to a $\sigma $ in proportion to $\pi_\theta(\sigma |S)$.
+
+\begin{figure}\centering
+  \begin{tikzpicture}
+    \node[anchor = west] at (0,5.25) {Entire program search space};
+    \draw[fill = yellow,fill opacity = 0.15,draw = black] (0,0) rectangle (5,5);
+    \draw [fill = yellow, opacity = 0.2] (0,0)--(0,2)--(4,0)--(0,0);
+    \draw [fill = yellow, opacity = 0.4,cycle] (0,5)--(0,1)--(3,5);
+    \draw [fill = yellow, opacity = 0.6,cycle] (2.5,5)--(3.2,0)--(5,0)--(5,5);
+    \draw (0,2) -- node[below,sloped]{short programs} (4,0);
+    \draw (0,2) -- node[above,sloped]{long programs} (4,0);
+    \draw (2.5,5) -- node[above,sloped]{programs w/ reflections} (3.2,0);
+    \draw (0,1) -- node[above,sloped]{ programs w/ loops} (3,5);
+    \node(p1)[anchor =west ] at (5.5,3.5) {$\pi_\theta(\text{short, no loop/reflect}|S) = $};
+    \draw [fill = yellow, fill opacity = 0.2,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p1.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p1.east);
+    \node(p2)[anchor =west ] at ([yshift = -0.5cm]p1.west) {$\pi_\theta(\text{long, loops}|S) = $};
+    \draw [fill = yellow, fill opacity = 0.4,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p2.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p2.east);
+    \node(p3)[anchor =west ] at ([yshift = -0.5cm]p2.west) {$\pi_\theta(\text{long, no loop/reflect}|S) = $};
+    \draw [fill = yellow, fill opacity = 0.15,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p3.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p3.east);
+    \node(p4)[anchor =west ] at ([yshift = -0.5cm]p3.west) {$\pi_\theta(\text{long, reflects}|S) = $};
+    \draw [fill = yellow, fill opacity = 0.6,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p4.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p4.east);
+    \node(p5)[anchor =west ] at ([yshift = -0.5cm]p4.west) {\emph{etc.}};
+  \end{tikzpicture}
+  \caption{The bias-optimal search algorithm divides the entire (intractable) program search space in to (tractable) program subspaces (written $\sigma $), each of which contains a restricted set of programs.
 For example, one subspace might be short programs which don't loop.
 The policy $\pi$ predicts a distribution over program subspaces.
-The weight that $\pi$ assigns to a subspace is indicated by it's yellow shading in the above figure.}
-%%   \end{figure}
+The weight that $\pi$ assigns to a subspace is indicated by its yellow shading in the above figure, and is conditioned on the spec $S$.}
+  \end{figure}
+
 Now in theory any $\pi_\theta(\cdot |\cdot ) $ is a bias-optimal searcher.
@@
 by picking the policy minimizing the
-expected bias-optimal time to solve a training corpus, $\mathcal{D}$, of graphics program synthesis problems:
+expected bias-optimal time to solve a training corpus, $\mathcal{D}$, of graphics program synthesis problems:\footnote{This loss is differentiable but nonconvex even if $\pi_{\theta}(\cdot |\cdot )^{-1}$ is convex.}
 \begin{align}
@@
 To generate a training corpus for learning a policy,
-we synthesized minimum cost programs for each  drawing
+we synthesized minimum cost programs for each of our hand drawings
 and for each $\sigma $,
@@
 %synthesis problems takes a little over a day on 40 CPUs.
-%With the training set in hand we  %This loss is differentiable but nonconvex even if $\pi_{\theta}(\cdot |\cdot )^{-1}$ is convex.
-then minimized~\ref{policyLoss} using gradient descent. % while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}.
+%With the training set in hand we  %
+then minimized Eq.~\ref{policyLoss} using gradient descent while annealing a softened minimum to the hard minimization in Eq.~\ref{policyLoss} (see Appendix~\ref{policyAppendix}).
 %See supplement for details.
 Because we want to learn a policy from only $100$ drawings,
-we parameterize $\pi$ with a  low-capacity bilinear model; see supplement.
+we parameterize $\pi$ with a  low-capacity bilinear model:
 %for $\pi$:
-%% \begin{equation}
-%%   \pi_{\theta}(\sigma |S)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{spec}}(S)\right)
-%% \end{equation}
-%% where $\phi_{\text{params}}(\sigma  )$ is a one-hot encoding of
-%% the parameter settings of $\sigma $ (see Tbl.~\ref{policyOutput})
-%% and $\phi_{\text{spec}}(S)$ extracts a few simple features of the trace set $S$;
-%% see supplement for details.
+\begin{equation}
+  \pi_{\theta}(\sigma |S)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{spec}}(S)\right)
+\end{equation}
+where $\phi_{\text{params}}(\sigma  )$ is a one-hot encoding of
+the parameter settings of $\sigma $ (see Tbl.~\ref{policyOutput})
+and $\phi_{\text{spec}}(S)$ extracts a vector of counts of the drawing primitives in $S$;
+thus $\theta$ has only 96 real-valued parameters.\footnote{$\theta$ has only 96 parameters because it
+  is a matrix mapping a 4-dimensional feature vector into a 24-dimensional output space.
+  The output space is 24-dimensional because $\sigma $ assumes one of 24 different values,
+  and the input space is 4-dimensional because we have three different drawing primitives,
+along with an extra dimension for a `bias' term.}
 
@@
  \emph{DC}, a DeepCoder--style model that learns to predict which program components (loops, reflections)
- are likely to be useful~\cite{BalGauBroetal16};
+ are likely to be useful~\cite{BalGauBroetal16} (Appendix~\ref{dcAppendix});
  \emph{End--to-End},
- which trains a recurrent neural network to regress directly from images to programs;
+ which trains a recurrent neural network to regress directly from images to programs (Appendix~\ref{eeAppendix});
 and an \emph{Oracle},
@@
     Oracle&6 sec&2\%\\
-    Ours&28 sec&2\%\\\bottomrule 
+    Ours&29 sec&2\%\\\bottomrule 
     \end{tabular}
@@
 \end{figure} 
+\begin{figure}
+  \includegraphics[width = \textwidth]{figures/policyComparison_basic_DC+bias_20.png}
+    \caption{Time to synthesize a minimum cost program (compare w/ Table~\ref{policyEvaluation}).
+Sketch: out-of-the-box performance of Sketch~\citep{solar2008program}.
+DC: Deep--Coder style baseline that predicts program components, trained like~\cite{BalGauBroetal16}.
+Oracle:  upper bounds  the performance of any bias--optimal search policy.
+End--to--End: not shown because it times out on 96\% of drawings, and has its median time (63s) calculated only on non-timeouts, where is the other comparisons include timeouts in their median calculation.
+$\infty = $ timeout.
+Red dashed line is median time.}
+  \end{figure}
 
@@
 \subsection{Correcting errors made by the neural network}\label{synthesizerHelpsParsing}
+The program synthesizer can help correct errors from the execution spec proposal network by favoring  specs which lead to more concise or general programs.
+For example, one generally prefers figures with perfectly aligned objects over figures whose parts are slightly misaligned -- and precise alignment lends itself to short programs.
+Similarly, figures often have repeated parts,
+which the program synthesizer might be able to model as a loop or reflectional symmetry.
+So, in considering several candidate specs proposed by the neural network,
+we might prefer specs whose best programs have desirable features such being short or having iterated structures.
+Intuitively,
+this is like the `top down' influence of cognition upon perception:
+a reasoning engine (the program synthesizer)
+can influence the agent's percept
+through higher-level considerations  like symmetry and alignment.
+
+Concretely, we implemented the following scheme: for an image $I$, the neurally guided sampling scheme (Section~\ref{neuralNetworkSection}) samples a set of candidate specs, written $\mathcal{F}(I)$.
+Instead of predicting the most likely spec in $\mathcal{F}(I)$ according to the neural network,
+we can take into account the programs that best explain the specs. 
+Writing $\hat{S}(I)$ for the spec the model predicts for image $I$,
+\begin{equation}
+\hat{S}(I) = \argmax_{S\in \mathcal{F}(I)} L_{\text{learned}}(I | \text{render}(S))\times \probability_\theta[S|I] \times\probability_{\beta} [ \text{program}(S)] 
+\end{equation}
+where $\probability_{\beta} [\cdot]$ is a prior probability
+distribution over programs parameterized by $\beta$.
+This is equivalent to doing
+MAP inference in a generative model where the program is first drawn
+from $\probability_{\beta} [\cdot]$, then the program is executed deterministically,
+and then we observe a noisy version of the program's output, where $L_\text{learned}(I|\text{render}(\cdot))\times\probability_\theta[\cdot|I]$
+is our observation model.
+
+Given a corpus of graphics program synthesis problems with annotated ground truth specs (i.e. $(I,S)$ pairs),
+we find a maximum likelihood estimate of $\beta$:
+\begin{equation}
+  \beta^* = \argmax_{\beta} \expect \left[ \log \frac{\probability_{\beta} [\text{program}(S)]\times L_{\text{learned}}(I|\text{render}(S))\times \probability_\theta[S|I]}{\sum_{S'\in \mathcal{F}(I)} \probability_{\beta} [\text{program}(S')]\times L_{\text{learned}}(I|\text{render}(S'))\times \probability_\theta[S'|I]} \right]
+\end{equation}
 \begin{wrapfigure}{r}{5cm}\vspace{-0.5cm}
@@
 Right: interpretations favored after learning a prior over programs.
-The prior favors  simpler programs, thus (top) continuing the pattern of not having an arrow is preferred, or (bottom) continuing the ``binary search tree'' is preferred.}\label{exampleOfProgramCorrectingMistake}
-\vspace{-0.75cm}  \end{wrapfigure}
-The program synthesizer corrects errors made by the neural network by favoring specs which lead to more
-concise or general programs.  For example, figures with perfectly aligned objects are preferable, %% to figures whose parts are slightly misaligned,
-and precise alignment lends itself to short
-programs.
-Concretely,
-we run the program synthesizer on the
-Top-$k$  most likely specs output by the neurally guided sampler.
-Then, the system
-reranks the Top-$k$  by  the prior probability of their programs.
-The prior probability of a program is learned by optimizing the parameters of the prior so as to maximize
-the likelihood of the ground truth specs;
-see supplement for details.
-But, this procedure can only correct errors when
-a correct spec is in the Top-$k$.
-Our sampler could only do better on
-7/100 drawings by looking at the Top-100 samples
-(see Fig.~\ref{drawingIntersectionOverUnion}),
-precluding a statistically significant analysis of how much
-learning a prior over programs could help correct errors.
-But,
-learning this prior does sometimes 
-help correct mistakes made by the neural network; %% , and also
-%% occasionally introduces mistakes of its own; 
-see
+The prior favors  simpler programs, thus (top) continuing the pattern of not having an arrow is preferred, or (bottom) continuing the ``binary search tree'' is preferred.}\vspace{-1cm}\label{exampleOfProgramCorrectingMistake}
+  \end{wrapfigure}
+where the expectation is taken both over the model predictions and the
+$(I,S)$ pairs in the training corpus.  We define $\probability_{\beta}
+[\cdot]$ to be a log linear distribution $\propto \exp
+(\beta\cdot \phi(\text{program}))$, where $\phi(\cdot)$ is a feature
+extractor for programs.  We extract a few basic features of a
+program, such as its size and how many loops it has, and use these
+features to help predict whether a spec is the correct explanation
+for an image.
+
+We synthesized programs for the top 10 specs
+output by the deep network.  Learning this prior over programs can
+help correct mistakes made by the neural network, and also
+occasionally introduces mistakes of its own; see
 Fig.~\ref{exampleOfProgramCorrectingMistake} for a representative
-example of the kinds of corrections that it makes.
-See supplement for details.
+example of the kinds of corrections that it makes. On the whole
+it modestly improves our Top-1 accuracy from 63\% to 67\%.  Recall that
+from Fig.~\ref{drawingIntersectionOverUnion} that the best improvement
+in accuracy we could possibly get is 70\% by looking at the top 10 specs.
 
@@
 
+\appendix
+
+\section{Appendix}
+
+\subsection{Neural architecture details}\label{architectureDetails}
+
+\subsubsection{Convolutional network}
+The convolutional network takes as input 2 $256\times 256$ images
+represented as a $2\times 256\times 256$ volume. These are
+passed through two layers of convolutions separated by ReLU
+nonlinearities and max pooling:
+\begin{itemize}
+\item Layer 1: 20 $8\times 8$ convolutions, 2 $16\times 4$ convolutions, 2 $4\times 16$ convolutions. Followed by $8\times 8$ pooling with a stride size of 4.
+\item Layer 2: 10 $8\times 8$ convolutions. Followed by $4\times 4$ pooling with a stride size of 4.
+\end{itemize}
+
+\subsubsection{Autoregressive decoding of drawing commands}
+
+Given the image features $f$, we predict the first token (i.e., the name of the drawing command: \verb|circle|, \verb|rectangle|, \verb|line|, or \verb|STOP|) using logistic regression:
+\begin{equation}
+  \probability [t_1]\propto \exp\left( W_{t_1}f + b_{t_1}\right)
+\end{equation}
+where $W_{t_1}$ is a learned weight matrix and  $b_{t_1}$ is a learned bias vector.
+
+Given an attention mechanism $a(\cdot | \cdot)$, subsequent tokens are predicted as:
+\begin{equation}
+  \probability [t_n|t_{1:(n - 1)}]\propto \text{MLP}_{t_1,n}(a(f|t_{1:(n - 1)}) \oplus \bigoplus_{j < n} \text{oneHot}(t_j))\label{discreteTokenPrediction}
+\end{equation}
+Thus each token of each drawing primitive has its own learned MLP.
+For predicting the coordinates of lines we found that using 32 hidden nodes with sigmoid activations worked well;
+for other tokens the MLP's are just logistic regression (no hidden nodes).
+
+We use Spatial Transformer Networks~\cite{jaderberg2015spatial}
+as our attention mechanism.
+The parameters of the spatial transform are predicted on the basis of previously predicted tokens.
+For example, in order to decide where to focus our attention when predicting the $y$ coordinate of a circle,
+we condition upon both the identity of the drawing command (\verb|circle|) and upon the value of the previously predicted $x$ coordinate:
+\begin{equation}
+  a(f|t_{1:(n - 1)}) = \text{AffineTransform}(f, \text{MLP}_{t_1,n}(\bigoplus_{j < n}\text{oneHot}(t_j)))
+  \label{spatialTransformEquation}
+\end{equation}
+So, we learn a different network for predicting special transforms
+\emph{for each drawing command} (value of $t_1$) and also \emph{for each token of the drawing command}.
+These networks ($\text{MLP}_{t_1,n}$ in equation~\ref{spatialTransformEquation}) have no hidden layers and
+output the 6 entries of an affine transformation matrix; see~\cite{jaderberg2015spatial}
+for more details.
+
+Training takes a little bit less than a day on a Nvidia TitanX GPU.
+The network was trained on $10^5$ synthetic examples.
+
+\subsection{LSTM Baseline for Parsing into Specs}\label{captioningBaseline}
+We  compared our deep network with a baseline that models the problem as a kind of image captioning.
+Given the target image, this baseline produces the program spec in one shot by
+using a CNN to extract features of the input which are passed to an LSTM which finally predicts
+the spec token-by-token.
+This general architecture is used in several successful neural models of image captioning (e.g.,~\cite{vinyals2015show}).
+
+Concretely, we kept the image feature extractor architecture (a CNN) as in our model,
+but only passed it one image as input (the target image to explain).
+Then, instead of using an autoregressive decoder to predict a single drawing command,
+we used an LSTM to predict a sequence of drawing commands token-by-token.
+This LSTM had 128 memory cells,
+and at each time step produced as output the next token in the sequence of drawing commands.
+It took as input both the image representation and its previously predicted token.
+
+\subsection{Architecture and training of $L_{\text{learned}}$}\label{distanceAppendix}
+Our architecture for
+$L_{\text{learned}}(\text{render}(S_1)|\text{render}(S_2))$ has the
+same series of convolutions as the network that predicts the next
+drawing command. We train it to predict two scalars: $|S_1 - S_2|$ and
+$|S_2 - S_1|$.  These predictions are made using linear regression
+from the image features followed by a ReLU nonlinearity; this
+nonlinearity makes sense because the predictions can never be negative
+but could be arbitrarily large positive numbers.
+
+We train this network by sampling random synthetic scenes for $S_1$,
+and then perturbing them in small ways to produce $S_2$.
+We minimize the squared loss between the network's prediction and the ground truth symmetric differences.
+$S_1$ is rendered in the ``simulated hand drawing'' style (Section~\ref{generalizingTheHandDrawings}).
+
+\subsection{Simulating hand drawings}\label{noisyAppendix}
+We introduce noise into the \LaTeX~rendering process by:
+\begin{itemize}
+\item Rescaling the image intensity by a factor chosen uniformly at random from $[0.5,1.5]$
+\item Translating the image by $\pm 3$ pixels chosen uniformly random
+\item Rendering the \LaTeX~using the \verb|pencildraw| style,
+  which adds random perturbations to the paths drawn by \LaTeX in a way designed to resemble a pencil.
+\item Randomly perturbing the positions and sizes of primitive  \LaTeX drawing commands
+\end{itemize}
+Empirically this noise process is close enough to the kinds of variations introduced by
+an actual hand drawing that
+the learned model generalizes to
+our test set of hand drawings,
+\emph{despite} having never been trained on any real hand drawings.
+
+\subsection{A cost function over programs}\label{costAppendix}
+Programs incur a cost of 1 for each command (primitive drawing action,
+loop, or reflection).  They incur a cost of $\frac{1}{3}$ for each
+unique coefficient they use in a linear transformation beyond the
+first coefficient. This encourages reuse of coefficients, which leads
+to code that has translational symmetry; rather than provide a
+translational symmetry operator as we did with reflection, we modify
+what is effectively a prior over the space of program so that it tends
+to produce programs that have this symmetry.
+
+Programs also incur a cost of 1 for having loops of constant length 2;
+otherwise there is often no pressure from the cost function to explain
+a repetition of length 2 as being a reflection rather a loop.
+
+\subsection{Training a search policy}\label{policyAppendix}
+Recall from the main paper that our goal is to estimate the policy minimizing the following loss:
+\begin{align}
+\textsc{Loss}(\theta ; \mathcal{D})& =  \expect_{S\sim\mathcal{D}}\left[ \min_{\sigma\in \text{\textsc{Best}}(S)}\frac{t(\sigma | S)}{\pi_\theta (\sigma | S)}\right] + \lambda \Vert\theta\Vert_2^2\label{policyLoss}\\
+\text{where }  \sigma \in\text{\textsc{Best}}(S) &\text{ if  a minimum cost program for }S \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t.
+}p\text{ evaluates to }S} \text{cost}(p) \nonumber
+\end{align}
+We make this optimization problem tractable by annealing our loss function during gradient descent:
+\begin{align}
+&  \textsc{Loss}_\beta(\theta ; \mathcal{D}) =  \expect_{S\sim\mathcal{D}}\left[ \textsc{SoftMinimum}_\beta \left\{
+    \frac{t(\sigma | S)}{\pi_\theta (\sigma | S)}    : \sigma\in \text{\textsc{Best}}(S)\right\}\right] + \lambda \Vert\theta\Vert_2^2\label{softenedObjective}\\
+  \text{where }&\textsc{SoftMinimum}_\beta (x_1,x_2,x_3,\cdots ) = \sum_n x_n  \frac{e^{-\beta x_n}}{\sum_{n'}e^{-\beta x_{n'}}}
+\end{align}
+Notice that $\textsc{SoftMinimum}_{\beta = \infty}(\cdot )$ is just $\min(\cdot )$.
+We set the regularization coefficient $\lambda = 0.1$ and minimize equation~\ref{softenedObjective}
+using Adam for 2000 steps, linearly increasing $\beta$ from $1$ to $2$.
+
+\subsection{Program synthesis baselines}
+\subsubsection{DeepCoder}\label{dcAppendix}
+We compared our synthesis policy with a DeepCoder-style baseline.
+DeepCoder (DC)~\cite{BalGauBroetal16}
+is an approach for learning to speed up program synthesizers.
+DC models are neural networks that
+predict, starting from a spec,
+the probability of a DSL component being in a minimal-cost program satisfying the spec.
+Writing $\text{DC}(S)$ for the distribution predicted by the neural network,
+DC is trained to maximize  the following objective:
+\begin{equation}
+  \expect_{S\sim\mathcal{D}}\left[\min_{p\in \text{\textsc{Best}}(S)} \sum_{x\in \text{DSL}} \log \left(\indicator\left[x\in p \right] \text{DC}(S)_x + \indicator\left[x\notin p \right] (1 - \text{DC}(S)_x)\right)
+    \right]
+\end{equation}
+where $x$ ranges over DSL components and $\text{DC}(S)_x\in \left[0,1 \right]$  is the probability predicted by the DC model for component $x$ for spec $S$.
+
+We provided our DC model with the same features given to our bias optimal search policy ($\phi_{spec}$ in Section~\ref{learningASearchPolicy}), used the same log-linear model, and trained using the same 20-fold cross validation splits.
+To evaluate the DC baseline on held out data,
+we used the \emph{Sort-and-Add} policy described in the DeepCoder paper~\cite{BalGauBroetal16}.
+
+\subsubsection{End--to--End}\label{eeAppendix}
+
+Recall that we factored the graphics program synthesis problem into two components: (1) a perception-facing component, whose job is to go from perceptual input to a set of commands that must occur in the execution of the program (\textbf{spec}); and (2) a program synthesis component, whose job is to infer a program whose execution contains those commands.
+This is a different approach from other recent program induction models (e.g.,~\cite{devlin2017robustfill,nps}), which regress directly from a program induction problem to the source code of the program.
+
+\textbf{Experiment.} To test whether this factoring is necessary for our domain, we trained a model to regress directly from images to graphics programs.
+This baseline model, which we call the \emph{no-spec baseline}, was able to infer some simple programs, but failed completely on more sophisticated scenes.
+
+Baseline model architecture: The model architecture is a straightforward, image-captioning-style CNN$\to$LSTM.
+We keep the same CNN architecture from our main model, with the sole difference that it takes only one image as input.
+The LSTM decoder produces the program token-by-token: so we flatten the program's hierarchical structure, and use special ``bracketing'' symbols to convey nesting structure, in the spirit of~\citep{vinyals2015grammar}.
+The LSTM decoder has 2 hidden layers with 1024 units.
+We used 64-dimensional embeddings for the program tokens.
+
+Training and evaluation: The model was trained on $10^7$ synthetically generated programs -- 2 orders of magnitude more data than the model we present in the main paper.
+We then evaluated the baseline on \emph{synthetic renders} of our 100 hand drawings (the testing set used throughout the paper).
+Recall that our model was evaluated on noisy real hand drawings.
+We sample programs from this baseline model conditioned on a synthetic render of a hand drawing, and report only the sampled program whose output most closely matched the ground truth spec spec, as measured by the symmetric difference of the two sets.
+We allow the baseline model to spend 1 hour drawing samples per drawing -- recall that our model finds 58\% of programs in under a minute.
+Together these training and evaluation choices are intended to make the problem as easy as possible for the baseline.
+
+Results: The no-spec baseline succeeds for trivial programs (a few lines, no variables, loops, etc.); occasionally gets small amounts of simple looping structure; and fails utterly for most of our test cases.
+See Figure~\ref{noSpec}.
+
+\begin{figure}[h]\centering
+      \includegraphics[width = 2cm]{figures/noTraceOutputs/11.png}
+  \includegraphics[width = 2cm]{figures/noTraceOutputs/16.png}
+    \includegraphics[width = 2cm]{figures/noTraceOutputs/29.png}
+    \includegraphics[width = 2cm]{figures/noTraceOutputs/7.png}
+        \includegraphics[width = 2cm]{figures/noTraceOutputs/94.png}
+      \includegraphics[width = 2cm]{figures/noTraceOutputs/38.png}
+  \caption{Top, white: synthetic rendering of a hand drawing. Bottom, black: output of best program found by no-spec baseline.}\label{noSpec}
+  \end{figure}
+
 \end{document}

### 2018-09-22 nips_2018.tex
long version of the paper

@@
   with SMC against the neural network by
-itself or SMC by itself.  Only the combination of the two passes a
+itself (i.e., w/ beam search) or SMC by itself.  Only the combination of the two passes a
 critical test of generalization: when trained on images with $\leq 12$

### 2018-09-23 long.tex
image similarity added to long draft

@@
 
-%% \subsection{Modeling similarity between drawings}
-%% Modeling drawings using programs opens up new ways to measure similarity between them.
-%% For example, we might say that two drawings are similar if they both contain loops of length 4,
-%% or if they share a reflectional symmetry,
-%% or if they are both organized according to a grid-like structure.
-
-%% We measure the similarity between two drawings by extracting features
-%% of the lowest-cost programs that describe them. Our features are counts of the number of times that different components in the
-%% DSL were used (Tbl.~\ref{DSL}).
-%% We  then find drawings which are either close together or far apart in program feature space.
-%% One could use many
-%% alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
-%% We used our learned distance metric between trace sets, $L_{\text{learned}}(\cdot|\cdot)$,
-%% to find drawings that are either close together or far apart according to the learned
-%% distance metric over images.
-%% Fig.~\ref{similarityMatrix} illustrates the kinds of drawings that these different metrics put closely together,
-%% while Sec.~2 of the supplement shows low dimensional projections of
-%% program and image features.
-
-%% \newcommand{\similaritySize}{1cm}
-%% \newcommand{\similarityArrowSize}{0.35cm}
-%% \begin{figure}[t]
-%%   \begin{tabular}{|c|c|}
-%%     \multicolumn{1}{c}{\textbf{Close in program space, far in image space}}&
-%%     \multicolumn{1}{c}{\textbf{Close in image space, far in program space}}\\\hline&\\
-
-%%     \begin{tabular}{l}
-%%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
-%%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-16-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-17-trim.png}\end{minipage}
-%%     \end{tabular} &
-
-%%     \begin{tabular}{l}
-%%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-22-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-77-trim.png}\end{minipage}\\\\
-%%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-64-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-97-trim.png}\end{minipage}
-%%     \end{tabular}
-%% \\&\\    \hline
-%%     %\\
-%% %    \multicolumn{1}{c|}{}&&\\\cline{2-3}
-%% %    \multicolumn{1}{c|}{}&&\\ \multicolumn{1}{c|}{}
-%%     %& %% \begin{tabular}{l}
-%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
-%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-16-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-17-trim.png}\end{minipage}
-%%     %% \end{tabular}
-%%     %&
-%%     %% \begin{tabular}{l}
-%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-75-extra-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-89-trim.png}\end{minipage}\\\\
-%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-3-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-39-trim.png}\end{minipage}
-%%     %% \end{tabular}
-%% %\\ \multicolumn{1}{c|}{}&&\\\cline{2-3}\cline{2-3}
-%%   \end{tabular}
-
-%%   \centering
-%% \caption{Pairs of images either close together or far apart in different features spaces.
+\subsection{Modeling similarity between drawings}
+Modeling drawings using programs opens up new ways to measure similarity between them.
+For example, we might say that two drawings are similar if they both contain loops of length 4,
+or if they share a reflectional symmetry,
+or if they are both organized according to a grid-like structure.
+
+We measure the similarity between two drawings by extracting features
+of the lowest-cost programs that describe them. Our features are counts of the number of times that different components in the
+DSL were used (Tbl.~\ref{DSL}).
+We  then find drawings which are either close together or far apart in program feature space.
+One could use many
+alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
+We used our learned distance metric between specs, $L_{\text{learned}}(\cdot|\cdot)$,
+to find drawings that are either close together or far apart according to the learned
+distance metric over images.
+Fig.~\ref{similarityMatrix} illustrates the kinds of drawings that these different metrics put closely together.
+
+\newcommand{\similaritySize}{1cm}
+\newcommand{\similarityArrowSize}{0.35cm}
+\begin{figure}[t]
+  \begin{tabular}{c|c|c|}
+    \multicolumn{1}{c}{}    &\multicolumn{1}{c}{\textbf{Close in program space}}&\multicolumn{1}{c}{\textbf{Far apart in program space}}\\\cline{2-3}
+    \multicolumn{1}{c|}{}&&\\
+    \multicolumn{1}{c|}{    \begin{tabular}{l}\textbf{Close in }\\ \textbf{image space} \end{tabular}}    &
+    \begin{tabular}{l}
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-20-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-21-trim.png}\end{minipage}\\\\
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-50-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-2-trim.png}\end{minipage}
+    \end{tabular} &
+    \begin{tabular}{l}
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-22-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-77-trim.png}\end{minipage}\\\\
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-64-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-97-trim.png}\end{minipage}
+    \end{tabular}\\
+    \multicolumn{1}{c|}{}&&\\\cline{2-3}
+    \multicolumn{1}{c|}{}&&\\
+    \multicolumn{1}{c|}{    \begin{tabular}{c}\textbf{Far apart in }\\ \textbf{image space} \end{tabular}}    &        \begin{tabular}{l}
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-16-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-17-trim.png}\end{minipage}
+    \end{tabular}&
+    \begin{tabular}{l}
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-75-extra-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-89-trim.png}\end{minipage}\\\\
+      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-3-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-39-trim.png}\end{minipage}
+    \end{tabular}
+\\    \multicolumn{1}{c|}{}&&\\\cline{2-3}\cline{2-3}    
+  \end{tabular}
+
+  \centering
+\caption{Pairs of images either close together or far apart in different features spaces.
 The symbol $\leftrightarrow$ points to the compared images.
 Features of the program capture abstract notions like symmetry and repetition.
-Distance metric over images is $L_{\text{learned}}(\cdot|\cdot)$ (see Sec.~\ref{generalizingTheHandDrawings}).
-Similarity of programs captures high-level features like repetition and symmetry, whereas similarity of images corresponds to similar drawing commands being in similar places.
-See Sec.
-2 of the supplement for more examples.}\label{similarityMatrix}  \end{figure}
-
-%% We project these features down to a
-%% 2-dimensional subspace using primary component analysis
-%% (PCA); see Fig.\ref{NMF}.  One could use many
-%% alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
-%% We used our learned distance metric between traces, $L_{\text{learned}}(\cdot|\cdot)$, and projected to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}).
-This reveals similarities between the objects in the drawings,
-%% while missing similarities at the level of the program.
-%% \begin{figure}[h]
-%% \centering  \begin{minipage}{\textwidth}\centering
-%%   %\includegraphics[width = 0.69\textwidth]{figures/PCA.png}
-%%   \includegraphics[width = 0.69\textwidth]{figures/PCA_improved.png}
-%%     \caption{PCA on features of the programs that were synthesized for each drawing.
-Symmetric figures cluster to the right; ``loopy'' figures cluster to the left; complicated programs are at the top and simple programs are at the bottom.}    \label{NMF}
-%%   \end{minipage} %\hfill
-%%   \begin{minipage}{\textwidth}\centering
-%%     \includegraphics[width = 0.69\textwidth]{figures/imageSimilarity.png} 
-%%     \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
-%%   \end{minipage}
-%% \end{figure}
+Distance metric over images is $L_{\text{learned}}(\cdot|\cdot)$ (see Section~\ref{generalizingTheHandDrawings}).
+The off-diagonal entries highlight the difference between these metrics: similarity of programs captures high-level features like repetition and symmetry, whereas similarity of images correspondends to similar drawing commands being in similar places.}\label{similarityMatrix}  \end{figure}
 
@@
   \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix2.png}
-%  \includegraphics[width = \textwidth]{figures/extrapolationMatrix3.png}  
+  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix3.png}  
    \caption{Top, white: hand drawings. Bottom, black: extrapolations produced by our system.}

### 2018-09-26 nips_2018.tex
funding acknowledgments

@@
 More generally, we believe the problem of inferring visual programs is a promising direction for research in machine perception.
-\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on the design of the neural architecture. Work funded by NSF GRFP (K.E.) and NSF Award 
-\#1753684 (D.R.)
+\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on  the neural architecture. Funding from NSF GRFP, NSF Award 
+\#1753684, and the MUSE program (Darpa grant FA8750-14-2-0242).
 

### 2018-10-18 nips_2018.tex
progress toward camera ready

@@
 \usepackage{caption}
+\usepackage{capt-of}
 \usepackage{subcaption}
@@
 % author name.
-
-\author{Kevin Ellis$^{1,*}$\qquad Daniel Ritchie$^2$\qquad  Armando Solar-Lezama$^1$\qquad Joshua B. Tenenbaum$^1$\\
-  $^1$Massachusetts Institute of Technology\qquad $^2$Brown University\\
-  $^*$Primary contact: \texttt{ellisk@mit.edu}%% \\
-%%   \texttt{ellisk@mit.edu} \\
-%%   \And
-%%   Daniel Ritchie\\
-%% Brown University\\
-%%  \texttt{daniel\_ritchie@brown.edu} \\
-%%  \And
-%%  Armando Solar-Lezama\\
-%%  MIT\\
-%% \texttt{asolar@csail.mit.edu} \\
-%% \And
-%% Joshua B. Tenenbaum \\
-%% MIT\\
-%% \texttt{jbt@mit.edu}
+%% Kevin Ellis$^{1,*}$\qquad Daniel Ritchie$^2$\qquad  Armando Solar-Lezama$^1$\qquad Joshua B. Tenenbaum$^1$\\
+  %% $^1$Massachusetts Institute of Technology\qquad $^2$Brown University\\
+  %% $^*$Primary contact: \texttt{ellisk@mit.edu}%% \\
+\author{Kevin Ellis\\MIT\\\texttt{ellisk@mit.edu}\\
+ \And
+ Daniel Ritchie\\Brown University\\\texttt{daniel\_ritchie@brown.edu}\\
+ \AND
+ Armando Solar-Lezama\\MIT\\\texttt{asolar@csail.mit.edu}\\
+ \And
+ Joshua B. Tenenbaum \\MIT\\\texttt{jbt@mit.edu}\\
   %% Affiliation \\
@@
 We trained our network by sampling specs $S$ and target
-images $I$ for randomly generated scenes
+images $I$ for randomly generated scenes\footnote{Because rendering ignores ordering  we put the drawing commands into a canonical order}
 and maximizing $\probability_\theta[S|I]$,
@@
 but, for this domain, cannot parse cluttered scenes with many objects.
+\begin{figure}[h]\centering
+  \begin{minipage}[c]{7cm}
+      \includegraphics[width = 7cm]{figures/averageNumberOfErrors.png}    
+  \end{minipage}\hspace{0.5cm}%
+  \begin{minipage}[c]{6cm}
+      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
+Out-of-sample generalization: Model generalizes to scenes with many more objects ($\approx$ at ceiling when tested on twice as many objects as were in the training data).
+Neither SMC nor the neural network are sufficient on their own.
+\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object).
+Average number of errors is (\# incorrect drawing commands predicted by model)$+$(\# correct commands that were not predicted by model).}\label{syntheticResults}
+    \end{minipage}
+  \end{figure}
 \begin{wrapfigure}{r}{8cm}
-  \vspace{0.4cm}
+  \vspace{-0.2cm}
   \centering
-      \includegraphics[width = 7cm]{figures/averageNumberOfErrors.png}
-      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
-Model generalizes to scenes with many more objects.
-Neither SMC nor the neural network are sufficient on their own.
-\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}\vspace{-1.5cm}
+
 \end{wrapfigure}
@@
 %Intuitively, an $n$-bias optimal search algorithm spends at least $\probability_{\text{bias}}[\sigma ]/n$ of its time exploring solution space $\sigma $.
-Bias-optimal search over program spaces is known as \textbf{Levin Search}~\cite{levin1973universal}; an example of a $1$-bias optimal search algorithm is an ideal time-sharing system that allocates $\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
-We construct a $1$-bias optimal search algorithm by identifying $\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |S)$ and $t(\sigma )  = t(\sigma|S)$, where $t(\sigma|S)$ is how long the synthesizer takes to search $\sigma $ for a program for $S$.
-This means that the search algorithm explores the entire program space, but spends most of its time in the regions of the space that  the policy judges to be most promising.
+Bias-optimal search over program spaces is known as \textbf{Levin
+  Search}~\cite{levin1973universal}; an example of a $1$-bias optimal
+search algorithm is an ideal time-sharing system that allocates
+$\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
+We construct a $1$-bias optimal search algorithm by identifying
+$\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |S)$ and
+$t(\sigma ) = t(\sigma|S)$, where $t(\sigma|S)$ is how long the
+synthesizer takes to search $\sigma $ for a program for
+$S$. Intuitively, this means that the search algorithm explores the
+entire program space, but spends most of its time in the regions of
+the space that the policy judges to be most promising.  Concretely,
+this means that our synthesis strategy is to run many different
+program searches \emph{in parallel} (i.e., run in parallel different
+instances of the synthesizer, one for each $\sigma$), but to
+allocate compute time to a $\sigma $ in proportion to
+$\pi_\theta(\sigma |S)$.
 
@@
 %With the training set in hand we  %This loss is differentiable but nonconvex even if $\pi_{\theta}(\cdot |\cdot )^{-1}$ is convex.
-then minimized~\ref{policyLoss} using gradient descent. % while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}.
+then minimized~\ref{policyLoss} using gradient descent while annealing a softened minimum to the hard minimization equation~\ref{policyLoss}.
 %See supplement for details.
 Because we want to learn a policy from only $100$ drawings,
-we parameterize $\pi$ with a  low-capacity bilinear model; see supplement.
+we parameterize $\pi$ with a  low-capacity bilinear model with only 96 real-valued parameters; see supplement.
 %for $\pi$:
@@
 
-\textbf{Experiment 3: Table~\ref{policyEvaluation}.}
+\textbf{Experiment 3: Table~\ref{policyEvaluation}; Figure~\ref{policyHistogram}.}
 We compare synthesis times for our learned search policy
@@
   \end{minipage}
-  \vspace{-0.5cm}
-\end{figure}
+
+\vspace{1cm}
+
+  \includegraphics[width = \textwidth]{figures/policyComparison_basic_DC+bias_20.png}%
+  \captionof{figure}{Time to synthesize a minimum cost program (compare w/ Table~\ref{policyEvaluation}).
+End--to--End: not shown because it times out on 96\% of drawings, and has its median time (63s) calculated only on non-timeouts, wheras the other comparisons include timeouts in their median calculation.
+$\infty = $ timeout.
+Red dashed line is median time.}\label{policyHistogram}
+\end{table}
+
+\pagebreak
 
@@
 Having access to the source code of a graphics program facilitates coherent, high-level image editing.
-%For example,
-%we could change all of the circles to squares or make all of the lines be dashed.
-For example we can extrapolate figures
+For example,
+we could change all of the circles to squares or make all of the lines be dashed,
+or we can (automatically) extrapolate figures
 by increasing the number of times that loops are executed.
@@
 Other systems in the computer graphics literature convert sketches to procedural representations, e.g.
-using a convolutional network to match a sketch to the output of a parametric 3D modeling system in~\citep{huang2017shape}.
-%% or supporting interactive sketch-based instantiation of procedural primitives in~\citep{Nishida:2016:ISU:2897824.2925951}
+using a convolutional network to match a sketch to the output of a parametric 3D modeling system in~\citep{huang2017shape} or supporting interactive sketch-based instantiation of procedural primitives in~\citep{Nishida:2016:ISU:2897824.2925951}
 In contrast, we seek to automatically infer a programmatic representation capturing higher-level visual patterns.
@@
 \subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on  the neural architecture. Funding from NSF GRFP, NSF Award 
-\#1753684, and the MUSE program (Darpa grant FA8750-14-2-0242).
+\#1753684, and the MUSE program (DARPA grant FA8750-14-2-0242).
 

### 2018-10-18 nips_2018.tex
almost, ready!

@@
 coordinates to lie on a discrete $16\times 16$ grid,
-but the grid could be made arbitrarily fine.  %% See supplement for the full details
-%% of the architecture, which we implemented in
-%% Tensorflow~\citep{tensorflow2015-whitepaper}.
-%% \remark{There are some more details that are important to provide
-%%   about this architecture in the supplement: the
-%%   functional form(s) of the probability distributions over tokens, the
-%%   network layer sizes, which MLPs share parameters, etc.}
+but the grid could be made arbitrarily fine.
 
@@
 We trained on $10^5$ scenes, which takes a day on an Nvidia TitanX GPU.
-
+Supplement Section 1 gives the full details of the architecture and training of this network.
 %% Training does not require backpropagation across the sequence
@@
 to generalize to hand drawings by introducing noise into the
-renderings of the training target images, where the noise process  mimics the kinds of variations found in hand drawings (%% Fig.~\ref{handDrawingExamples}; 
-see supplement for details).
+renderings of the training target images, where the noise process  mimics the kinds of variations found in hand drawings.
 While our neurally-guided SMC procedure
@@
   \end{equation}
+Supplement Section 2 explains the architecture and training of $L_{\text{learned}}$.
 
@@
 cost of a program to be the number of Statement's it contains (Tbl.~\ref{DSL}).
-We also penalize using many different numerical constants; see supplement.
+We also penalize using many different numerical constants; see Supplement Section 3.
 Returning to the generative model in Fig.~\ref{roadmap},
@@
 Because we want to learn a policy from only $100$ drawings,
-we parameterize $\pi$ with a  low-capacity bilinear model with only 96 real-valued parameters; see supplement.
+we parameterize $\pi$ with a  low-capacity bilinear model with only 96 real-valued parameters. Supplement Section 4 further details the parameterization and training of the policy.
 %for $\pi$:
@@
 
-\textbf{Experiment 3: Table~\ref{policyEvaluation}; Figure~\ref{policyHistogram}.}
+\textbf{Experiment 3: Table~\ref{policyEvaluation}; Figure~\ref{policyHistogram}; Supplement Section 4.}
 We compare synthesis times for our learned search policy
@@
 example of the kinds of corrections that it makes.
-See supplement for details.
+See Supplement Section 5 for details.
 

### 2018-10-18 supplement.tex
almost, ready!

@@
 %\usepackage{iclr2018_conference,times}
-\usepackage{nips_2017}
+\usepackage[final]{nips_2017}
 
@@
 
-\section{Why not use an end--to--end solution?}
+\section{Neural network architecture and training}
+
+\subsection{High-level overview}
+
+For the model in Fig.~\ref{architecture}, the distribution over the next drawing command factorizes as:
+\begin{equation}
+  \probability_\theta [t_1t_2\cdots t_K | I,S] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(S)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
+\end{equation}
+where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
+the target image, $S$ is a spec, $\theta$ are the
+parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
+image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
+specs factorizes as:
+\begin{equation}
+  \probability_\theta [S|I] = \prod_{n = 1}^{|S|} \probability_\theta [S_n | I,S_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,S]\label{objective}
+\end{equation}
+where $|S|$ is the length of spec $S$, the subscripts
+on $S$ index drawing commands within the spec (so $S_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
+token is emitted by the network to signal that the spec
+explains the image.
+\tikzset{>=latex}
+\begin{figure}
+  \begin{tikzpicture}
+  \node[draw,blue,ultra thick,anchor = west,inner sep=0pt,label=below:Sarget image: $I$](observation) at (0,-1) {\includegraphics[width = 2cm]{figures/expert-18.png}};
+  \node[draw,blue,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(S)$] (canvas) at (0,-4) {};
+  \draw[lightgray,ultra thin,step = 0.125] ([xshift = 0.5,yshift = 0.5]canvas.south west) grid ([xshift = -0.5,yshift = -0.5]canvas.north east);
+  % draw partial image on canvas
+  \draw (0.375cm,-3.25cm) circle (0.125cm);
+  \draw (0.625cm,-3.625) circle (0.125cm);
+  \draw (0.75cm,-3.375) circle (0.125cm);
+
+  \node[draw,ultra thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 3cm] (CNN) at (4.5,-2.5) {CNN};
+  \node[inner sep = 0pt](tensorProduct) at ([xshift = -1.5cm]CNN.west) {$\bigoplus$};
+
+  \node[rotate = -90,draw,ultra thick,inner sep=0pt,minimum width = 3cm,minimum height = 0.5cm] (features) at ([xshift = 1.5cm]CNN.east) {Image features};
+
+  \node[draw,ultra thick,minimum size = 1cm](c1) at ([xshift = 1.5cm]features.north) {MLP};
+  \node(l1) at ([yshift = -1.5cm]c1.south) {\verb|circle(|};
+  \node[draw,ultra thick,minimum size = 1cm](a2) at ([xshift = 1cm,yshift = 1.5cm]c1.east) {STN};
+  \node[draw,ultra thick,minimum size = 1cm](c2) at ([xshift = 1cm]c1.east) {MLP};
+  \draw[->,ultra thick] (a2.south) -- (c2.north);
+  \draw[->,ultra thick,red] (c1.south) -- (l1.north);
+  \node(l2) at ([yshift = -1.5cm]c2.south) {\verb|X=7,|};
+  \draw[->,ultra thick,red] (c2.south) -- (l2.north);
+  \node[draw,ultra thick,minimum size = 1cm](a3) at ([xshift = 1cm,yshift = 1.5cm]c2.east) {STN};
+  \node[draw,ultra thick,minimum size = 1cm](c3) at ([xshift = 1cm]c2.east) {MLP};
+
+  \draw[->,ultra thick] (a3.south) -- (c3.north);
+  \node(l3) at ([yshift = -1.5cm]c3.south) {\verb|Y=12)|};
+  \draw[->,ultra thick,red] (c3.south) -- (l3.north);
+
+  \draw[->,ultra thick] (features.north) -- (c1.west);
+  \draw[->,ultra thick] (features.north) to[out = 45,in = 160] (a2.north);
+  \draw[->,ultra thick] (features.north) to[out = 70,in = 140] (a3.north);
+  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c2.west);
+  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- ([yshift = -0.2cm]c3.west);
+  \draw[->,ultra thick] ([xshift = 0.25cm]l2.north) -- ([yshift = -0.25cm]c3.west);
+
+  \node(next)[draw,very thick,fit = (l1) (l2) (l3), dashed, label = below:{Next drawing command}] {};
+
+  \draw[-{>[scale = 1.5]},very thick,dashed] (next.west) -- ([yshift = -0.2cm]canvas.east) node [midway, below, sloped] (TextNode) {Renderer}; %: \LaTeX~Ti\emph{k}Z};
+
+  \draw[->,ultra thick] (canvas.east) -- (tensorProduct.south);%[yshift = -0.5cm]CNN.west);
+  \draw[->,ultra thick] (observation.east) -- (tensorProduct.north);%([yshift = 0.5cm]CNN.west);
+  \draw[->,ultra thick] (tensorProduct.east)  -- node[fill = white,rotate = 90] {{\tiny $256\times 256\times 2$}}  (CNN.west);
+  \draw[->,ultra thick] (CNN.east) -- node[fill = white,rotate = 90] {{\tiny $16\times 16\times 10$}} (features.south);
+%  \draw[]
+
+%  \node at (canvas.x,canvas.y) {Canvas};
+\end{tikzpicture}
+\caption{Our neural architecture for inferring the spec of a graphics program from its output.
+\textcolor{blue}{Blue}: network inputs.
+Black: network operations.
+\textcolor{red}{Red}: samples from a multinomial.
+\texttt{Typewriter font}: network outputs.
+Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}.
+STN (spatial transformer network) is a differentiable attention mechanism~\citep{jaderberg2015spatial}.}  \label{architecture}
+\end{figure}
+\subsection{Convolutional network}\label{CNNarchitecture}
+The convolutional network takes as input 2 $256\times 256$ images
+represented as a $2\times 256\times 256$ volume. These are
+passed through two layers of convolutions separated by ReLU
+nonlinearities and max pooling:
+\begin{itemize}
+\item Layer 1: 20 $8\times 8$ convolutions, 2 $16\times 4$ convolutions, 2 $4\times 16$ convolutions. Followed by $8\times 8$ pooling with a stride size of 4.
+\item Layer 2: 10 $8\times 8$ convolutions. Followed by $4\times 4$ pooling with a stride size of 4.
+\end{itemize}
+
+\subsection{Autoregressive decoding of drawing commands}
+
+Given the image features $f$, we predict the first token (i.e., the name of the drawing command: \verb|circle|, \verb|rectangle|, \verb|line|, or \verb|STOP|) using logistic regression:
+\begin{equation}
+  \probability [t_1]\propto \exp\left( W_{t_1}f + b_{t_1}\right)
+\end{equation}
+where $W_{t_1}$ is a learned weight matrix and  $b_{t_1}$ is a learned bias vector.
+
+Given an attention mechanism $a(\cdot | \cdot)$, subsequent tokens are predicted as:
+\begin{equation}
+  \probability [t_n|t_{1:(n - 1)}]\propto \text{MLP}_{t_1,n}(a(f|t_{1:(n - 1)}) \oplus \bigoplus_{j < n} \text{oneHot}(t_j))\label{discreteTokenPrediction}
+\end{equation}
+Thus each token of each drawing primitive has its own learned MLP.
+For predicting the coordinates of lines we found that using 32 hidden nodes with sigmoid activations worked well;
+for other tokens the MLP's are just logistic regression (no hidden nodes).
+
+We use Spatial Transformer Networks~\cite{jaderberg2015spatial}
+as our attention mechanism.
+The parameters of the spatial transform are predicted on the basis of previously predicted tokens.
+For example, in order to decide where to focus our attention when predicting the $y$ coordinate of a circle,
+we condition upon both the identity of the drawing command (\verb|circle|) and upon the value of the previously predicted $x$ coordinate:
+\begin{equation}
+  a(f|t_{1:(n - 1)}) = \text{AffineTransform}(f, \text{MLP}_{t_1,n}(\bigoplus_{j < n}\text{oneHot}(t_j)))
+  \label{spatialTransformEquation}
+\end{equation}
+So, we learn a different network for predicting special transforms
+\emph{for each drawing command} (value of $t_1$) and also \emph{for each token of the drawing command}.
+These networks ($\text{MLP}_{t_1,n}$ in equation~\ref{spatialTransformEquation}) have no hidden layers and
+output the 6 entries of an affine transformation matrix; see~\cite{jaderberg2015spatial}
+for more details.
+
+Training takes a little bit less than a day on a Nvidia TitanX GPU.
+The network was trained on $10^5$ synthetic examples.
+\subsection{LSTM Baseline}
+
+We  compared our deep network with a baseline that models the problem as a kind of image captioning.
+Given the target image, this baseline produces the program spec in one shot by
+using a CNN to extract features of the input which are passed to an LSTM which finally predicts
+the spec token-by-token.
+This general architecture is used in several successful neural models of image captioning (e.g.,~\cite{vinyals2015show}).
+
+Concretely, we kept the image feature extractor architecture (a CNN) as in our model,
+but only passed it one image as input (the target image to explain).
+Then, instead of using an autoregressive decoder to predict a single drawing command,
+we used an LSTM to predict a sequence of drawing commands token-by-token.
+This LSTM had 128 memory cells,
+and at each time step produced as output the next token in the sequence of drawing commands.
+It took as input both the image representation and its previously predicted token.
+
+\subsection{Generating synthetic training data}
+
+We generated synthetic training data for the neural network by
+sampling \LaTeX~code according to the following generative process:
+First,
+the number of objects in the scene are sampled uniformly from 1 to 12.
+For each object we uniformly sample its identity (circle, rectangle, or line).
+Then we sample the parameters of the circles,
+than the parameters of the rectangles,
+and finally the parameters of the lines;
+this has the effect of teaching the network to first draw the circles in the scene,
+then the rectangles,
+and finally the lines.
+We furthermore put the circle (respectively, rectangle and line) drawing commands in order by
+left-to-right, bottom-to-top;
+thus the training data enforces a canonical order in which to draw any scene.
+
+To make the training data look more like naturally occurring figures,
+we put a Chinese restaurant process prior~\cite{gershman2012tutorial} over
+the values of the X and Y coordinates that occur in the execution spec.
+This encourages reuse of coordinate values,
+and so produces training data that tends to have parts that are nicely aligned.
+
+In the synthetic training data we excluded any sampled scenes that had
+overlapping drawing commands.  As shown in the main paper, the network
+is then able to generalize to scenes with, for example, intersecting
+lines or lines that penetrate a rectangle.
+
+When sampling the endpoints of a line,
+we biased the sampling process so that it would
+be more likely to start an endpoint
+along one of the sides of a rectangle or at the boundary of a circle.
+If $n$ is the number of points either along the side of a rectangle or at the boundary of a circle,
+we would sample an arbitrary endpoint with probability $\frac{2}{2 + n}$
+and sample one of the ``attaching'' endpoints with probability $\frac{1}{2 + n}$.
+
+See figure~\ref{exampleTrainingData} for examples of the kinds of scenes that the network is trained on.
+\begin{figure}
+  \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-58-7.png}}\end{minipage}
+  \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-33-5.png}}\end{minipage}
+  \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-4-4.png}}\end{minipage}
+  \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-26-7.png}}\end{minipage}
+      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-25-4.png}}\end{minipage}\\
+      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-22-3.png}}\end{minipage}
+      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-20-7.png}}\end{minipage}
+      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-19-3.png}}\end{minipage}
+      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-17-7.png}}\end{minipage}
+      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-1-4.png}}\end{minipage}
+      \caption{Example synthetic training data}\label{exampleTrainingData}
+\end{figure}
+
+For readers wishing to generate their own synthetic training sets,
+we refer them to our source code at:~\url{https://github.com/ellisk42/TikZ}.
+
+%\pagebreak
+\section{Generalizing to real hand drawings}
+\subsection{Simulating hand drawings}\label{simulatingHandDrawings}
+
+We introduce noise into the \LaTeX~rendering process by:
+
+\begin{itemize}
+\item Rescaling the image intensity by a factor chosen uniformly at random from $[0.5,1.5]$
+\item Translating the image by $\pm 3$ pixels chosen uniformly random
+\item Rendering the \LaTeX~using the \verb|pencildraw| style,
+  which adds random perturbations to the paths drawn by \LaTeX in a way designed to resemble a pencil.
+\item Randomly perturbing the positions and sizes of primitive  \LaTeX drawing commands
+\end{itemize}
+
+\begin{figure}
+
+\centering\vspace{-0.7cm}  \begin{minipage}[t]{2.5cm}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
+    \subcaption{hand drawing}
+  \end{minipage}\\
+   \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
+    \subcaption{rendering of (a)'s inferred spec}
+  \end{minipage}\qquad% 
+  \begin{minipage}[t]{2.5cm}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
+    \subcaption{noisy rendering of (b)}
+  \end{minipage}%
+  \caption{Noisy renderings produced in \LaTeX~Ti\emph{k}Z w/ \texttt{pencildraw} package }
+    \label{handDrawingExamples} 
+\end{figure}
+
+\subsection{A learned likelihood surrogate}
+
+Our architecture for
+$L_{\text{learned}}(\text{render}(T_1)|\text{render}(T_2))$ has the
+same series of convolutions as the network that predicts the next
+drawing command. We train it to predict two scalars: $|T_1 - T_2|$ and
+$|T_2 - T_1|$.  These predictions are made using linear regression
+from the image features followed by a ReLU nonlinearity; this
+nonlinearity makes sense because the predictions can never be negative
+but could be arbitrarily large positive numbers.
+
+We train this network by sampling random synthetic scenes for $T_1$,
+and then perturbing them in small ways to produce $T_2$.
+We minimize the squared loss between the network's prediction and the ground truth symmetric differences.
+$T_1$ is rendered in a ``simulated hand drawing'' style which Section~\ref{simulatingHandDrawings} describes.
+%\pagebreak
+
+\section{The cost function for programs}
+
+We seek the minimum cost program which evaluates to (produces the drawing primitives in) an execution spec $T$:
+\begin{equation}
+  \text{program}(T) = \argmin_{\substack{p\in \text{DSL}\\p \text{ evaluates to } T}} \text{cost}(p)\label{programObjective}
+\end{equation}
+
+Programs incur a cost of 1 for each command (primitive drawing action,
+loop, or reflection).  They incur a cost of $\frac{1}{3}$ for each
+unique coefficient they use in a linear transformation beyond the
+first coefficient. This encourages reuse of coefficients, which leads
+to code that has translational symmetry; rather than provide a
+translational symmetry operator as we did with reflection, we modify
+what is effectively a prior over the space of program so that it tends
+to produce programs that have this symmetry.
+
+Programs also incur a cost of 1 for having loops of constant length 2;
+otherwise there is often no pressure from the cost function to explain
+a repetition of length 2 as being a reflection rather a loop.
+
+\section{Learning a search policy}
+\subsection{Modeling}\label{searchPolicyModel}
+Recall from the main paper that our goal is to estimate the policy minimizing the following loss:
+\begin{align}
+\textsc{Loss}(\theta ; \mathcal{D})& =  \expect_{S\sim\mathcal{D}}\left[ \min_{\sigma\in \text{\textsc{Best}}(S)}\frac{t(\sigma | S)}{\pi_\theta (\sigma | S)}\right] + \lambda \Vert\theta\Vert_2^2\label{policyLoss}\\
+\text{where }  \sigma \in\text{\textsc{Best}}(S) &\text{ if  a minimum cost program for }S \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t.
+}p\text{ evaluates to }S} \text{cost}(p) \nonumber
+\end{align}
+We make this optimization problem tractable by annealing our loss function during gradient descent:
+\begin{align}
+&  \textsc{Loss}_\beta(\theta ; \mathcal{D}) =  \expect_{S\sim\mathcal{D}}\left[ \textsc{SoftMinimum}_\beta \left\{
+    \frac{t(\sigma | S)}{\pi_\theta (\sigma | S)}    : \sigma\in \text{\textsc{Best}}(S)\right\}\right] + \lambda \Vert\theta\Vert_2^2\label{softenedObjective}\\
+  \text{where }&\textsc{SoftMinimum}_\beta (x_1,x_2,x_3,\cdots ) = \sum_n x_n  \frac{e^{-\beta x_n}}{\sum_{n'}e^{-\beta x_{n'}}}
+\end{align}
+Notice that $\textsc{SoftMinimum}_{\beta = \infty}(\cdot )$ is just $\min(\cdot )$.
+We set the regularization coefficient $\lambda = 0.1$ and minimize equation~\ref{softenedObjective}
+using Adam for 2000 steps, linearly increasing $\beta$ from $1$ to $2$.
+
+We parameterize the space of policies as a simple log bilinear model:
+\begin{equation}
+  \pi_{\theta}(\sigma |S)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{spec}}(S)\right)
+\end{equation}
+where:
+\begin{align*}
+  \phi_{\text{params}}(\sigma ) = [&\indicator [\sigma \text{ can loop}] ;\\
+    &\indicator [\sigma \text{ can reflect}];\\
+    &\indicator [\sigma \text{ is incremental}] ; \\
+    &\indicator [\sigma \text{ has depth bound }1];\indicator [\sigma \text{ has depth bound }2];\indicator [\sigma \text{ has depth bound }3];]\\
+  \phi_{\text{spec}}(S) = [&\text{\# circles in }S;\text{\# rectangles in }S;\text{\# lines in }S;1]
+  \end{align*}
+where the meaning of ``incremental'' is described in the next section.
+\subsection{Incremental Solving}
+Rather than give the sketch program synthesizer the entire spec all at once,
+we can instead give it subsets of the spec (subsets of the objects in the image)
+and ask it to synthesize a program for each subset.
+We then concatenate the resulting programs from each subset to get a program that explains the entire image,
+and we call this strategy ``incremental solving''.
+Incremental solving is not guaranteed to be faster,
+nor is it guaranteed to find a minimum cost program.
+Thus we allow the search policy to decide
+what fraction of our search time should be allocated to this incremental approach to program synthesis.
+Concretely, we partitioned a spec into its constituent lines, circles, and rectangles.
+\subsection{Baseline comparisons}
+
+\subsubsection{DeepCoder-style baseline}
+
+In addition to the end-to-end baseline,
+we compared with a DeepCoder-style baseline (main paper, Section 3.1).
+DeepCoder (DC)~\cite{BalGauBroetal16}
+is an approach for learning to speed up program synthesizers.
+DC models are neural networks that
+predict, starting from a spec,
+the probability of a DSL component being in a minimal-cost program satisfying the spec.
+Writing $\text{DC}(S)$ for the distribution predicted by the neural network,
+DC is trained to maximize  the following objective:
+\begin{equation}
+  \expect_{S\sim\mathcal{D}}\left[\min_{p\in \text{\textsc{Best}}(S)} \sum_{x\in \text{DSL}} \log \left(\indicator\left[x\in p \right] \text{DC}(S)_x + \indicator\left[x\notin p \right] (1 - \text{DC}(S)_x)\right)
+    \right]
+\end{equation}
+where $x$ ranges over DSL components and $\text{DC}(S)_x\in \left[0,1 \right]$  is the probability predicted by the DC model for component $x$ for spec $S$.
+
+We provided our DC model with the same features given to our bias optimal search policy ($\phi_{spec}$ in section~\ref{searchPolicyModel}), and trained using the same 20-fold cross validation splits.
+To evaluate the DC baseline on held out data,
+we used the \emph{Sort-and-Add} policy described in the DeepCoder paper\cite{BalGauBroetal16}.
+
+\subsubsection{End-to-End baseline}
 
@@
 \end{figure}
-\pagebreak
+%\pagebreak
 
@@
 
-\section{Learning a search policy}
-\subsection{Modeling}\label{searchPolicyModel}
-Recall from the main paper that our goal is to estimate the policy minimizing the following loss:
-\begin{align}
-\textsc{Loss}(\theta ; \mathcal{D})& =  \expect_{S\sim\mathcal{D}}\left[ \min_{\sigma\in \text{\textsc{Best}}(S)}\frac{t(\sigma | S)}{\pi_\theta (\sigma | S)}\right] + \lambda \Vert\theta\Vert_2^2\label{policyLoss}\\
-\text{where }  \sigma \in\text{\textsc{Best}}(S) &\text{ if  a minimum cost program for }S \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t.
-}p\text{ evaluates to }S} \text{cost}(p) \nonumber
-\end{align}
-We make this optimization problem tractable by annealing our loss function during gradient descent:
-\begin{align}
-&  \textsc{Loss}_\beta(\theta ; \mathcal{D}) =  \expect_{S\sim\mathcal{D}}\left[ \textsc{SoftMinimum}_\beta \left\{
-    \frac{t(\sigma | S)}{\pi_\theta (\sigma | S)}    : \sigma\in \text{\textsc{Best}}(S)\right\}\right] + \lambda \Vert\theta\Vert_2^2\label{softenedObjective}\\
-  \text{where }&\textsc{SoftMinimum}_\beta (x_1,x_2,x_3,\cdots ) = \sum_n x_n  \frac{e^{-\beta x_n}}{\sum_{n'}e^{-\beta x_{n'}}}
-\end{align}
-Notice that $\textsc{SoftMinimum}_{\beta = \infty}(\cdot )$ is just $\min(\cdot )$.
-We set the regularization coefficient $\lambda = 0.1$ and minimize equation~\ref{softenedObjective}
-using Adam for 2000 steps, linearly increasing $\beta$ from $1$ to $2$.
+%\pagebreak
 
-We parameterize the space of policies as a simple log bilinear model:
-\begin{equation}
-  \pi_{\theta}(\sigma |S)\propto \exp \left( \phi_{\text{params}}(\sigma )^\top\theta \phi_{\text{spec}}(S)\right)
-\end{equation}
-where:
-\begin{align*}
-  \phi_{\text{params}}(\sigma ) = [&\indicator [\sigma \text{ can loop}] ;\\
-    &\indicator [\sigma \text{ can reflect}];\\
-    &\indicator [\sigma \text{ is incremental}] ; \\
-    &\indicator [\sigma \text{ has depth bound }1];\indicator [\sigma \text{ has depth bound }2];\indicator [\sigma \text{ has depth bound }3];]\\
-  \phi_{\text{spec}}(S) = [&\text{\# circles in }S;\text{\# rectangles in }S;\text{\# lines in }S;1]
-  \end{align*}
-where the meaning of ``incremental'' is described in the next section.
-\subsection{Incremental Solving}
-Rather than give the sketch program synthesizer the entire spec all at once,
-we can instead give it subsets of the spec (subsets of the objects in the image)
-and ask it to synthesize a program for each subset.
-We then concatenate the resulting programs from each subset to get a program that explains the entire image,
-and we call this strategy ``incremental solving''.
-Incremental solving is not guaranteed to be faster,
-nor is it guaranteed to find a minimum cost program.
-Thus we allow the search policy to decide
-what fraction of our search time should be allocated to this incremental approach to program synthesis.
-Concretely, we partitioned a spec into its constituent lines, circles, and rectangles.
-\subsection{Baseline comparisons}
-In addition to the end-to-end baseline,
-we compared with a DeepCoder-style baseline (main paper, Section 3.1).
-DeepCoder (DC)~\cite{BalGauBroetal16}
-is an approach for learning to speed up program synthesizers.
-DC models are neural networks that
-predict, starting from a spec,
-the probability of a DSL component being in a minimal-cost program satisfying the spec.
-Writing $\text{DC}(S)$ for the distribution predicted by the neural network,
-DC is trained to maximize  the following objective:
-\begin{equation}
-  \expect_{S\sim\mathcal{D}}\left[\min_{p\in \text{\textsc{Best}}(S)} \sum_{x\in \text{DSL}} \log \left(\indicator\left[x\in p \right] \text{DC}(S)_x + \indicator\left[x\notin p \right] (1 - \text{DC}(S)_x)\right)
-    \right]
-\end{equation}
-where $x$ ranges over DSL components and $\text{DC}(S)_x\in \left[0,1 \right]$  is the probability predicted by the DC model for component $x$ for spec $S$.
+%% \begin{comment}
+%% \subsection{Predicting continuous coordinates using Mixture Density Networks}
 
-We provided our DC model with the same features given to our bias optimal search policy ($\phi_{spec}$ in section~\ref{searchPolicyModel}), and trained using the same 20-fold cross validation splits.
-To evaluate the DC baseline on held out data,
-we used the \emph{Sort-and-Add} policy described in the DeepCoder paper\cite{BalGauBroetal16}.
+%% Our main paper describes a neural model for parsing hand drawings
+%% into~\LaTeX, but comes with the restriction that all of the
+%% coordinates of all the drawing commands are snapped to a $16\times 16$
+%% grid. Now we describe a variant of our model that
+%% can predict continuous real valued coordinates.
 
-Figure~\ref{policyEvaluation} shows histograms of the synthesis time for our model and baselines.
+%% The key obstacle to overcome is \emph{multimodality}: if the network
+%% is unsure whether it should predict a coordinate value of $a$ or $b$,
+%% we wish to predict a distribution that splits its mass between $a$ and
+%% $b$, rather than predicting the single value $\frac{a + b}{2}$.  In
+%% the model where everything is snapped to a discrete grid, supporting
+%% this multimodality falls out naturally from our parameterization of
+%% the network predictions (i.e., the network predicts the parameters of
+%% a multinomial distribution). To predict continuous real valued
+%% coordinates we turn to Mixture Density Networks (MDN:~\cite{MDN}).  In
+%% an MDN, a distribution over a real-valued random variable is
+%% parameterized using a mixture of Gaussians, and the deep network
+%% predicts the parameters of the Gaussian mixture.
 
-\begin{figure}
-  \includegraphics[width = \textwidth]{figures/policyComparison_basic_DC+bias_20.png}
-    \caption{Time to synthesize a minimum cost program.
-Sketch: out-of-the-box performance of Sketch~\citep{solar2008program}.
-DC: Deep--Coder style baseline that predicts program components, trained like~\cite{BalGauBroetal16}.
-Oracle:  upper bounds  the performance of any bias--optimal search policy.
-$\infty = $ timeout.
-Red dashed line is median time.}
-  \end{figure}
-\pagebreak
-\section{Neural network architecture}
+%% Concretely,
+%% we modify our autoregressive drawing command decoder to
+%% predict distributions over real-valued coordinates
+%% as:
+%% \begin{equation}
+%%   p(t_n|t_{1:(n - 1)}) = \text{MDN}_{t_1,n} (a(f|t_{1:(n - 1)}) \oplus \bigoplus_{j < n} t_j)\text{, if }n^{\text{th}}\text{ token is continuous}\label{continuousDensityEquation}
+%% \end{equation}
+%% Compare this equation with Equation~\ref{discreteTokenPrediction} to see that we have only
+%% replaced a draw from a multinomial (whose parameters are predicted by an MLP)
+%% with a draw from a mixture of Gaussians (whose parameters are predicted by an MDN).
+%% Otherwise the two models are identical.
 
-\subsection{High-level overview}
-\tikzset{>=latex}
-\begin{figure}[t]
-  \begin{tikzpicture}
-  \node[draw,blue,ultra thick,anchor = west,inner sep=0pt,label=below:Sarget image: $I$](observation) at (0,-1) {\includegraphics[width = 2cm]{figures/expert-18.png}};
-  \node[draw,blue,thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 2cm,label=below:Canvas: render$(S)$] (canvas) at (0,-4) {};
-  \draw[lightgray,ultra thin,step = 0.125] ([xshift = 0.5,yshift = 0.5]canvas.south west) grid ([xshift = -0.5,yshift = -0.5]canvas.north east);
-  % draw partial image on canvas
-  \draw (0.375cm,-3.25cm) circle (0.125cm);
-  \draw (0.625cm,-3.625) circle (0.125cm);
-  \draw (0.75cm,-3.375) circle (0.125cm);
+%% For an MDN $i$ with $K$ mixture components that takes as input $x$, we parameterize it's output distribution as:
+%% \begin{eqnarray}
+%%   \text{MDN}_i(x) &=& \sum_{1\leq k\leq K} \pi_{i,k}(x)\times \mathcal{N}(\mu_{i,k}(x),\sigma^2_{i,k}(x))\\
+%%   \mu_{i,k}(x)& = &\text{sigmoid} (W^{\mu_{i,k}}x + b^{\mu_{i,k}}x)\label{mixtureMean}
+%%   \\\sigma^2_{i,k}(x)& = &\log \left(1 + \exp\left(W^{\sigma^2_{i,k}}x + b^{\sigma^2_{i,k}}x\right) \right)
+%%   \\\pi_{i,k}(x)& = &\frac{\exp\left(W^{\pi_{i,k}}x + b^{\pi_{i,k}}x \right)}{\sum_{k'} \exp\left(W^{\pi_{i,k'}}x + b^{\pi_{i,k'}}x \right)}
+%%   \end{eqnarray}
+%% where $W$ with a superscript is a learned weight matrix and $b$ is a
+%% learned bias vector. Notice that Equation~\ref{mixtureMean} normalizes
+%% the predicted means to be within $[0,1]$: this is because we wish to
+%% constrain the predicted coordinates to lie within the plane
+%% $[0,1]^2$. We used $K = 16$ mixture components.
 
-  \node[draw,ultra thick,anchor = west,inner sep=0pt,minimum width = 2cm,minimum height = 3cm] (CNN) at (4.5,-2.5) {CNN};
-  \node[inner sep = 0pt](tensorProduct) at ([xshift = -1.5cm]CNN.west) {$\bigoplus$};
+%% Figure~\ref{syntheticContinuous}  shows the behavior of the MDN variant of our model on noisy synthetic drawings.
+%% Contrast these mediocre results with Figure~4 of the main paper to see that although
+%% our main model is essentially at ceiling for parsing scenes like these,
+%% the MDN variant fares poorly in comparison.
+%% \begin{figure}
+%%   \includegraphics[width = \textwidth]{figures/syntheticContinuous.png}
+%%   \caption{Left column: \LaTeX~output corrupted by noise process designed to resemble the variability is introduced by hand drawings.
+Right columns: samples from the MDN variant of the model.}\label{syntheticContinuous}
+%% \end{figure}
 
-  \node[rotate = -90,draw,ultra thick,inner sep=0pt,minimum width = 3cm,minimum height = 0.5cm] (features) at ([xshift = 1.5cm]CNN.east) {Image features};
+%% We evaluated the MDN version of our model on hand drawings by (1)
+%% performing a beam search in order to find the spec maximizing
+%% $\probability [T|I]$, and (2) constraining the predicted coordinates
+%% to lie on the $16\times 16$ grid. We constrain the predicted coordinates
+%% to lie on the grid by integrating the predicted densities about each grid location.
+%% So, using the probability density $p(t_n|t_{1:(n - 1)})$ in Eq.~\ref{continuousDensityEquation},
+%% we compute a probability mass function $\probability [t_n|t_{1:(n - 1)}]$ as:
+%% \begin{equation}
+%%   \probability [t_n = t|t_{1:(n - 1)}] = \int_{t - \frac{1}{2}}^{t + \frac{1}{2}} \mathrm{d}t_n \; p(t_n|t_{1:(n - 1)})\label{constrainingEquation}
+%% \end{equation}
+%% Even after using Eq.~\ref{constrainingEquation} to constrain the predicted coordinates to lie on the $16\times 16$ grid, the MDN variant of the model only produces finished specs for 48/100 of the drawings.
+%% See Figure~\ref{continuousParses} to see the specs recovered by the beam search.
 
-  \node[draw,ultra thick,minimum size = 1cm](c1) at ([xshift = 1.5cm]features.north) {MLP};
-  \node(l1) at ([yshift = -1.5cm]c1.south) {\verb|circle(|};
-  \node[draw,ultra thick,minimum size = 1cm](a2) at ([xshift = 1cm,yshift = 1.5cm]c1.east) {STN};
-  \node[draw,ultra thick,minimum size = 1cm](c2) at ([xshift = 1cm]c1.east) {MLP};
-  \draw[->,ultra thick] (a2.south) -- (c2.north);
-  \draw[->,ultra thick,red] (c1.south) -- (l1.north);
-  \node(l2) at ([yshift = -1.5cm]c2.south) {\verb|X=7,|};
-  \draw[->,ultra thick,red] (c2.south) -- (l2.north);
-  \node[draw,ultra thick,minimum size = 1cm](a3) at ([xshift = 1cm,yshift = 1.5cm]c2.east) {STN};
-  \node[draw,ultra thick,minimum size = 1cm](c3) at ([xshift = 1cm]c2.east) {MLP};
-
-  \draw[->,ultra thick] (a3.south) -- (c3.north);
-  \node(l3) at ([yshift = -1.5cm]c3.south) {\verb|Y=12)|};
-  \draw[->,ultra thick,red] (c3.south) -- (l3.north);
-
-  \draw[->,ultra thick] (features.north) -- (c1.west);
-  \draw[->,ultra thick] (features.north) to[out = 45,in = 160] (a2.north);
-  \draw[->,ultra thick] (features.north) to[out = 70,in = 140] (a3.north);
-  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- (c2.west);
-  \draw[->,ultra thick] ([xshift = 0.25cm]l1.north) -- ([yshift = -0.2cm]c3.west);
-  \draw[->,ultra thick] ([xshift = 0.25cm]l2.north) -- ([yshift = -0.25cm]c3.west);
-
-  \node(next)[draw,very thick,fit = (l1) (l2) (l3), dashed, label = below:{Next drawing command}] {};
-
-  \draw[-{>[scale = 1.5]},very thick,dashed] (next.west) -- ([yshift = -0.2cm]canvas.east) node [midway, below, sloped] (TextNode) {Renderer}; %: \LaTeX~Ti\emph{k}Z};
-
-  \draw[->,ultra thick] (canvas.east) -- (tensorProduct.south);%[yshift = -0.5cm]CNN.west);
-  \draw[->,ultra thick] (observation.east) -- (tensorProduct.north);%([yshift = 0.5cm]CNN.west);
-  \draw[->,ultra thick] (tensorProduct.east)  -- node[fill = white,rotate = 90] {{\tiny $256\times 256\times 2$}}  (CNN.west);
-  \draw[->,ultra thick] (CNN.east) -- node[fill = white,rotate = 90] {{\tiny $16\times 16\times 10$}} (features.south);
-%  \draw[]
-
-%  \node at (canvas.x,canvas.y) {Canvas};
-\end{tikzpicture}
-\caption{Our neural architecture for inferring the spec of a graphics program from its output.
-\textcolor{blue}{Blue}: network inputs.
-Black: network operations.
-\textcolor{red}{Red}: samples from a multinomial.
-\texttt{Typewriter font}: network outputs.
-Renders snapped to a $16\times 16$ grid, illustrated in \textcolor{gray}{gray}.
-STN (spatial transformer network) is a differentiable attention mechanism~\citep{jaderberg2015spatial}.}  \label{architecture}
-\end{figure}
-For the model in Fig.~\ref{architecture}, the distribution over the next drawing command factorizes as:
-\begin{equation}
-  \probability_\theta [t_1t_2\cdots t_K | I,S] = \prod_{k = 1}^K \probability_\theta \left[t_k | a_\theta \left(f_\theta(I,\text{render}(S)) | \{t_j\}_{j = 1}^{k - 1}\right), \{t_j\}_{j = 1}^{k - 1}\right]
-\end{equation}
-where $t_1t_2\cdots t_K$ are the tokens in the drawing command, $I$ is
-the target image, $S$ is a spec, $\theta$ are the
-parameters of the neural network, $f_\theta(\cdot,\cdot)$ is the
-image feature extractor (convolutional network), and $a_\theta(\cdot|\cdot)$ is an attention mechanism. The distribution over
-specs factorizes as:
-\begin{equation}
-  \probability_\theta [S|I] = \prod_{n = 1}^{|S|} \probability_\theta [S_n | I,S_{1:(n-1)}]\times\probability_\theta [\verb|STOP| | I,S]\label{objective}
-\end{equation}
-where $|S|$ is the length of spec $S$, the subscripts
-on $S$ index drawing commands within the spec (so $S_n$ is a sequence of tokens: $t_1t_2\cdots t_K$), and the \verb|STOP|
-token is emitted by the network to signal that the spec
-explains the image.
-
-\subsection{Convolutional network}\label{CNNarchitecture}
-The convolutional network takes as input 2 $256\times 256$ images
-represented as a $2\times 256\times 256$ volume. These are
-passed through two layers of convolutions separated by ReLU
-nonlinearities and max pooling:
-\begin{itemize}
-\item Layer 1: 20 $8\times 8$ convolutions, 2 $16\times 4$ convolutions, 2 $4\times 16$ convolutions. Followed by $8\times 8$ pooling with a stride size of 4.
-\item Layer 2: 10 $8\times 8$ convolutions. Followed by $4\times 4$ pooling with a stride size of 4.
-\end{itemize}
-
-\subsection{Autoregressive decoding of drawing commands}
-
-Given the image features $f$, we predict the first token (i.e., the name of the drawing command: \verb|circle|, \verb|rectangle|, \verb|line|, or \verb|STOP|) using logistic regression:
-\begin{equation}
-  \probability [t_1]\propto \exp\left( W_{t_1}f + b_{t_1}\right)
-\end{equation}
-where $W_{t_1}$ is a learned weight matrix and  $b_{t_1}$ is a learned bias vector.
-
-Given an attention mechanism $a(\cdot | \cdot)$, subsequent tokens are predicted as:
-\begin{equation}
-  \probability [t_n|t_{1:(n - 1)}]\propto \text{MLP}_{t_1,n}(a(f|t_{1:(n - 1)}) \oplus \bigoplus_{j < n} \text{oneHot}(t_j))\label{discreteTokenPrediction}
-\end{equation}
-Thus each token of each drawing primitive has its own learned MLP.
-For predicting the coordinates of lines we found that using 32 hidden nodes with sigmoid activations worked well;
-for other tokens the MLP's are just logistic regression (no hidden nodes).
-
-We use Spatial Transformer Networks~\cite{jaderberg2015spatial}
-as our attention mechanism.
-The parameters of the spatial transform are predicted on the basis of previously predicted tokens.
-For example, in order to decide where to focus our attention when predicting the $y$ coordinate of a circle,
-we condition upon both the identity of the drawing command (\verb|circle|) and upon the value of the previously predicted $x$ coordinate:
-\begin{equation}
-  a(f|t_{1:(n - 1)}) = \text{AffineTransform}(f, \text{MLP}_{t_1,n}(\bigoplus_{j < n}\text{oneHot}(t_j)))
-  \label{spatialTransformEquation}
-\end{equation}
-So, we learn a different network for predicting special transforms
-\emph{for each drawing command} (value of $t_1$) and also \emph{for each token of the drawing command}.
-These networks ($\text{MLP}_{t_1,n}$ in equation~\ref{spatialTransformEquation}) have no hidden layers and
-output the 6 entries of an affine transformation matrix; see~\cite{jaderberg2015spatial}
-for more details.
-
-Training takes a little bit less than a day on a Nvidia TitanX GPU.
-The network was trained on $10^5$ synthetic examples.
-
-\begin{comment}
-\subsection{Predicting continuous coordinates using Mixture Density Networks}
-
-Our main paper describes a neural model for parsing hand drawings
-into~\LaTeX, but comes with the restriction that all of the
-coordinates of all the drawing commands are snapped to a $16\times 16$
-grid. Now we describe a variant of our model that
-can predict continuous real valued coordinates.
-
-The key obstacle to overcome is \emph{multimodality}: if the network
-is unsure whether it should predict a coordinate value of $a$ or $b$,
-we wish to predict a distribution that splits its mass between $a$ and
-$b$, rather than predicting the single value $\frac{a + b}{2}$.  In
-the model where everything is snapped to a discrete grid, supporting
-this multimodality falls out naturally from our parameterization of
-the network predictions (i.e., the network predicts the parameters of
-a multinomial distribution). To predict continuous real valued
-coordinates we turn to Mixture Density Networks (MDN:~\cite{MDN}).  In
-an MDN, a distribution over a real-valued random variable is
-parameterized using a mixture of Gaussians, and the deep network
-predicts the parameters of the Gaussian mixture.
-
-Concretely,
-we modify our autoregressive drawing command decoder to
-predict distributions over real-valued coordinates
-as:
-\begin{equation}
-  p(t_n|t_{1:(n - 1)}) = \text{MDN}_{t_1,n} (a(f|t_{1:(n - 1)}) \oplus \bigoplus_{j < n} t_j)\text{, if }n^{\text{th}}\text{ token is continuous}\label{continuousDensityEquation}
-\end{equation}
-Compare this equation with Equation~\ref{discreteTokenPrediction} to see that we have only
-replaced a draw from a multinomial (whose parameters are predicted by an MLP)
-with a draw from a mixture of Gaussians (whose parameters are predicted by an MDN).
-Otherwise the two models are identical.
-
-For an MDN $i$ with $K$ mixture components that takes as input $x$, we parameterize it's output distribution as:
-\begin{eqnarray}
-  \text{MDN}_i(x) &=& \sum_{1\leq k\leq K} \pi_{i,k}(x)\times \mathcal{N}(\mu_{i,k}(x),\sigma^2_{i,k}(x))\\
-  \mu_{i,k}(x)& = &\text{sigmoid} (W^{\mu_{i,k}}x + b^{\mu_{i,k}}x)\label{mixtureMean}
-  \\\sigma^2_{i,k}(x)& = &\log \left(1 + \exp\left(W^{\sigma^2_{i,k}}x + b^{\sigma^2_{i,k}}x\right) \right)
-  \\\pi_{i,k}(x)& = &\frac{\exp\left(W^{\pi_{i,k}}x + b^{\pi_{i,k}}x \right)}{\sum_{k'} \exp\left(W^{\pi_{i,k'}}x + b^{\pi_{i,k'}}x \right)}
-  \end{eqnarray}
-where $W$ with a superscript is a learned weight matrix and $b$ is a
-learned bias vector. Notice that Equation~\ref{mixtureMean} normalizes
-the predicted means to be within $[0,1]$: this is because we wish to
-constrain the predicted coordinates to lie within the plane
-$[0,1]^2$. We used $K = 16$ mixture components.
-
-Figure~\ref{syntheticContinuous}  shows the behavior of the MDN variant of our model on noisy synthetic drawings.
-Contrast these mediocre results with Figure~4 of the main paper to see that although
-our main model is essentially at ceiling for parsing scenes like these,
-the MDN variant fares poorly in comparison.
-\begin{figure}
-  \includegraphics[width = \textwidth]{figures/syntheticContinuous.png}
-  \caption{Left column: \LaTeX~output corrupted by noise process designed to resemble the variability is introduced by hand drawings.
-Right columns: samples from the MDN variant of the model.}\label{syntheticContinuous}
-\end{figure}
-
-We evaluated the MDN version of our model on hand drawings by (1)
-performing a beam search in order to find the spec maximizing
-$\probability [T|I]$, and (2) constraining the predicted coordinates
-to lie on the $16\times 16$ grid. We constrain the predicted coordinates
-to lie on the grid by integrating the predicted densities about each grid location.
-So, using the probability density $p(t_n|t_{1:(n - 1)})$ in Eq.~\ref{continuousDensityEquation},
-we compute a probability mass function $\probability [t_n|t_{1:(n - 1)}]$ as:
-\begin{equation}
-  \probability [t_n = t|t_{1:(n - 1)}] = \int_{t - \frac{1}{2}}^{t + \frac{1}{2}} \mathrm{d}t_n \; p(t_n|t_{1:(n - 1)})\label{constrainingEquation}
-\end{equation}
-Even after using Eq.~\ref{constrainingEquation} to constrain the predicted coordinates to lie on the $16\times 16$ grid, the MDN variant of the model only produces finished specs for 48/100 of the drawings.
-See Figure~\ref{continuousParses} to see the specs recovered by the beam search.
-
-\begin{figure}
-  \includegraphics[width = \textwidth]{figures/continuousParses.png}
-  \caption{Parsing hand drawings using the MDN variant of our
-    model. Black-on-white: hand drawings. White-on-black, below each
-    hand drawing: the parse inferred by the model.}\label{continuousParses} 
-  \end{figure}
-\end{comment}
-\subsection{LSTM Baseline}
-
-We  compared our deep network with a baseline that models the problem as a kind of image captioning.
-Given the target image, this baseline produces the program spec in one shot by
-using a CNN to extract features of the input which are passed to an LSTM which finally predicts
-the spec token-by-token.
-This general architecture is used in several successful neural models of image captioning (e.g.,~\cite{vinyals2015show}).
-
-Concretely, we kept the image feature extractor architecture (a CNN) as in our model,
-but only passed it one image as input (the target image to explain).
-Then, instead of using an autoregressive decoder to predict a single drawing command,
-we used an LSTM to predict a sequence of drawing commands token-by-token.
-This LSTM had 128 memory cells,
-and at each time step produced as output the next token in the sequence of drawing commands.
-It took as input both the image representation and its previously predicted token.
-
-\subsection{A learned likelihood surrogate}
-
-Our architecture for
-$L_{\text{learned}}(\text{render}(T_1)|\text{render}(T_2))$ has the
-same series of convolutions as the network that predicts the next
-drawing command. We train it to predict two scalars: $|T_1 - T_2|$ and
-$|T_2 - T_1|$.  These predictions are made using linear regression
-from the image features followed by a ReLU nonlinearity; this
-nonlinearity makes sense because the predictions can never be negative
-but could be arbitrarily large positive numbers.
-
-We train this network by sampling random synthetic scenes for $T_1$,
-and then perturbing them in small ways to produce $T_2$.
-We minimize the squared loss between the network's prediction and the ground truth symmetric differences.
-$T_1$ is rendered in a ``simulated hand drawing'' style which we describe next.
-
-\section{Simulating hand drawings}
-
-We introduce noise into the \LaTeX~rendering process by:
-
-\begin{itemize}
-\item Rescaling the image intensity by a factor chosen uniformly at random from $[0.5,1.5]$
-\item Translating the image by $\pm 3$ pixels chosen uniformly random
-\item Rendering the \LaTeX~using the \verb|pencildraw| style,
-  which adds random perturbations to the paths drawn by \LaTeX in a way designed to resemble a pencil.
-\item Randomly perturbing the positions and sizes of primitive  \LaTeX drawing commands
-\end{itemize}
-
-\section{Likelihood surrogate for synthetic data}
-For synthetic data (e.g., \LaTeX~output)
-it is relatively straightforward to engineer an adequate distance measure between images,
-because it is possible for the system to discover
-drawing commands that exactly match the pixels in the target image.
-We use:
-\begin{equation}
-  -\log L(I_1|I_2) = \sum_{1\leq x\leq 256} \sum_{1\leq y\leq 256} |I_1[x,y] - I_2[x,y]|\begin{cases}
-    \alpha\text{, if }$I_1[x,y] > I_2[x,y]$\\
-    \beta\text{, if }$I_1[x,y] <  I_2[x,y]$\\
-        0\text{, if }$I_1[x,y] = I_2[x,y]$\\
-    \end{cases}
-  \end{equation}
-where $\alpha$, $\beta$ are constants that control the trade-off
-between preferring to explain the pixels in the image (at the expense
-of having extraneous pixels) and not predicting pixels where they
-don't exist (at the expense of leaving some pixels unexplained). Because our sampling procedure incrementally constructs the scene part-by-part,
-we want $\alpha > \beta$.
-That is, it is preferable to leave some pixels unexplained;
-for once a particle in SMC adds a drawing primitive to its spec that is not actually in the latent scene,
-it can never recover from this error.
-In our experiments on synthetic data we used $\alpha = 0.8$ and $\beta = 0.04$. 
-\section{Generating synthetic training data}
-
-We generated synthetic training data for the neural network by
-sampling \LaTeX~code according to the following generative process:
-First,
-the number of objects in the scene are sampled uniformly from 1 to 12.
-For each object we uniformly sample its identity (circle, rectangle, or line).
-Then we sample the parameters of the circles,
-than the parameters of the rectangles,
-and finally the parameters of the lines;
-this has the effect of teaching the network to first draw the circles in the scene,
-then the rectangles,
-and finally the lines.
-We furthermore put the circle (respectively, rectangle and line) drawing commands in order by
-left-to-right, bottom-to-top;
-thus the training data enforces a canonical order in which to draw any scene.
-
-To make the training data look more like naturally occurring figures,
-we put a Chinese restaurant process prior~\cite{gershman2012tutorial} over
-the values of the X and Y coordinates that occur in the execution spec.
-This encourages reuse of coordinate values,
-and so produces training data that tends to have parts that are nicely aligned.
-
-In the synthetic training data we excluded any sampled scenes that had
-overlapping drawing commands.  As shown in the main paper, the network
-is then able to generalize to scenes with, for example, intersecting
-lines or lines that penetrate a rectangle.
-
-When sampling the endpoints of a line,
-we biased the sampling process so that it would
-be more likely to start an endpoint
-along one of the sides of a rectangle or at the boundary of a circle.
-If $n$ is the number of points either along the side of a rectangle or at the boundary of a circle,
-we would sample an arbitrary endpoint with probability $\frac{2}{2 + n}$
-and sample one of the ``attaching'' endpoints with probability $\frac{1}{2 + n}$.
-
-See figure~\ref{exampleTrainingData} for examples of the kinds of scenes that the network is trained on.
-\begin{figure}
-  \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-58-7.png}}\end{minipage}
-  \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-33-5.png}}\end{minipage}
-  \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-4-4.png}}\end{minipage}
-  \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-26-7.png}}\end{minipage}
-      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-25-4.png}}\end{minipage}\\
-      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-22-3.png}}\end{minipage}
-      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-20-7.png}}\end{minipage}
-      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-19-3.png}}\end{minipage}
-      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-17-7.png}}\end{minipage}
-      \begin{minipage}[t]{2.2cm}\fbox{\includegraphics[width=2cm]{figures/randomScene-1-4.png}}\end{minipage}
-      \caption{Example synthetic training data}\label{exampleTrainingData}
-\end{figure}
-
-For readers wishing to generate their own synthetic training sets,
-we refer them to our source code at:~\url{redactedForAnonymity.com}.%https://github.com/ellisk42/TikZ}.
-
-\section{The cost function for programs}
-
-We seek the minimum cost program which evaluates to (produces the drawing primitives in) an execution spec $T$:
-\begin{equation}
-  \text{program}(T) = \argmin_{\substack{p\in \text{DSL}\\p \text{ evaluates to } T}} \text{cost}(p)\label{programObjective}
-\end{equation}
-
-Programs incur a cost of 1 for each command (primitive drawing action,
-loop, or reflection).  They incur a cost of $\frac{1}{3}$ for each
-unique coefficient they use in a linear transformation beyond the
-first coefficient. This encourages reuse of coefficients, which leads
-to code that has translational symmetry; rather than provide a
-translational symmetry operator as we did with reflection, we modify
-what is effectively a prior over the space of program so that it tends
-to produce programs that have this symmetry.
-
-Programs also incur a cost of 1 for having loops of constant length 2;
-otherwise there is often no pressure from the cost function to explain
-a repetition of length 2 as being a reflection rather a loop.
+%% \begin{figure}
+%%   \includegraphics[width = \textwidth]{figures/continuousParses.png}
+%%   \caption{Parsing hand drawings using the MDN variant of our
+%%     model. Black-on-white: hand drawings. White-on-black, below each
+%%     hand drawing: the parse inferred by the model.}\label{continuousParses} 
+%%   \end{figure}
+%% \end{comment}
 

### 2018-10-18 long.tex
long version of the paper

@@
 % ready for submission
-\usepackage[final]{nips_2018}
+\usepackage[preprint]{nips_2018}
 
@@
 \usepackage{listings}
+\usepackage{capt-of}
 \lstset{basicstyle = \small\ttfamily}
@@
 
-\author{Kevin Ellis$^{1,*}$\qquad Daniel Ritchie$^2$\qquad  Armando Solar-Lezama$^1$\qquad Joshua B. Tenenbaum$^1$\\
-  $^1$Massachusetts Institute of Technology\qquad $^2$Brown University\\
-  $^*$Primary contact: \texttt{ellisk@mit.edu}%% \\
-%%   \texttt{ellisk@mit.edu} \\
-%%   \And
-%%   Daniel Ritchie\\
-%% Brown University\\
-%%  \texttt{daniel\_ritchie@brown.edu} \\
-%%  \And
-%%  Armando Solar-Lezama\\
-%%  MIT\\
-%% \texttt{asolar@csail.mit.edu} \\
-%% \And
-%% Joshua B. Tenenbaum \\
-%% MIT\\
-%% \texttt{jbt@mit.edu}
+\author{Kevin Ellis\\MIT\\\texttt{ellisk@mit.edu}\\
+ \And
+ Daniel Ritchie\\Brown University\\\texttt{daniel\_ritchie@brown.edu}\\
+ \AND
+ Armando Solar-Lezama\\MIT\\\texttt{asolar@csail.mit.edu}\\
+ \And
+ Joshua B. Tenenbaum \\MIT\\\texttt{jbt@mit.edu}\\
   %% Affiliation \\
@@
 but, for this domain, cannot parse cluttered scenes with many objects.
-\begin{wrapfigure}{r}{8cm}
-  \vspace{0.4cm}
-  \centering
+\begin{figure}[h]\centering
+  \begin{minipage}[c]{7cm}
       \includegraphics[width = 7cm]{figures/averageNumberOfErrors.png}    
+  \end{minipage}\hspace{0.5cm}%
+  \begin{minipage}[c]{6cm}
       \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects.
-Model generalizes to scenes with many more objects.
+Out-of-sample generalization: Model generalizes to scenes with many more objects ($\approx$ at ceiling when tested on twice as many objects as were in the training data).
 Neither SMC nor the neural network are sufficient on their own.
-\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object)}\label{syntheticResults}%\vspace{-1.5cm}
-\end{wrapfigure}
+\# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object).
+Average number of errors is (\# incorrect drawing commands predicted by model)$+$(\# correct commands that were not predicted by model).}\label{syntheticResults}
+    \end{minipage}
+  \end{figure}
 
@@
 \begin{wrapfigure}{R}{6cm}
-\centering\vspace{-0.7cm}  \begin{minipage}[t]{2.5cm}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
+\vspace{-0.7cm}\centering\vspace{-0.7cm}  \begin{minipage}[t]{2.5cm}\centering\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
     \subcaption{hand drawing}
@@
   \caption{Noisy renderings produced in \LaTeX~Ti\emph{k}Z w/ \texttt{pencildraw} package (Appendix~\ref{noisyAppendix})}
-    \label{handDrawingExamples} 
+    \label{handDrawingExamples} \vspace{-1cm}
 \end{wrapfigure}
@@
   \\\bottomrule
-  \end{tabular}\vspace{-0.5cm}
+  \end{tabular}\vspace{0.5cm}
   \end{table}
@@
     Oracle&6 sec&2\%\\
-    Ours&29 sec&2\%\\\bottomrule 
+    Ours&28 sec&2\%\\\bottomrule 
     \end{tabular}
@@
   \end{minipage}
-  \vspace{-0.5cm}
-\end{figure} 
-\begin{figure}
-  \includegraphics[width = \textwidth]{figures/policyComparison_basic_DC+bias_20.png}
-    \caption{Time to synthesize a minimum cost program (compare w/ Table~\ref{policyEvaluation}).
-Sketch: out-of-the-box performance of Sketch~\citep{solar2008program}.
-DC: Deep--Coder style baseline that predicts program components, trained like~\cite{BalGauBroetal16}.
-Oracle:  upper bounds  the performance of any bias--optimal search policy.
-End--to--End: not shown because it times out on 96\% of drawings, and has its median time (63s) calculated only on non-timeouts, where is the other comparisons include timeouts in their median calculation.
+
+\vspace{1cm}
+
+  \includegraphics[width = \textwidth]{figures/policyComparison_basic_DC+bias_20.png}%
+  \captionof{figure}{Time to synthesize a minimum cost program (compare w/ Table~\ref{policyEvaluation}).
+End--to--End: not shown because it times out on 96\% of drawings, and has its median time (63s) calculated only on non-timeouts, wheras the other comparisons include timeouts in their median calculation.
 $\infty = $ timeout.
-Red dashed line is median time.}
-  \end{figure}
+Red dashed line is median time.}\label{policyHistogram}
+\end{table}
 
@@
 \end{equation}
+where the expectation is taken both over the model predictions and the
+$(I,S)$ pairs in the training corpus.  We define $\probability_{\beta}
+[\cdot]$ to be a log linear distribution $\propto \exp
+(\beta\cdot \phi(\text{program}))$, where $\phi(\cdot)$ is a feature
+extractor for programs.  We extract a few basic features of a
+program, such as its size and how many loops it has, and use these
+features to help predict whether a spec is the correct explanation
+for an image.
 \begin{wrapfigure}{r}{5cm}\vspace{-0.5cm}
@@
   \end{wrapfigure}
-where the expectation is taken both over the model predictions and the
-$(I,S)$ pairs in the training corpus.  We define $\probability_{\beta}
-[\cdot]$ to be a log linear distribution $\propto \exp
-(\beta\cdot \phi(\text{program}))$, where $\phi(\cdot)$ is a feature
-extractor for programs.  We extract a few basic features of a
-program, such as its size and how many loops it has, and use these
-features to help predict whether a spec is the correct explanation
-for an image.
-
 We synthesized programs for the top 10 specs
@@
 
+\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on  the neural architecture. Funding from NSF GRFP, NSF Award 
+\#1753684, and the MUSE program (DARPA grant FA8750-14-2-0242).
+
 \bibliographystyle{unsrt}

### 2018-10-18 makeArchive.sh
archive nonsense

@@ -2,10 +2,10 @@
 
 rm -r archive archive.tar
 mkdir archive
-mkdir archive/figures
+mkdir archive/
 
-cp short.tex main.bib short.bbl iclr2018_conference.sty /usr/share/texlive/texmf-dist/tex/latex/natbib/natbib.sty archive
+cp long.tex main.bib long.bbl nips_2018.sty /usr/share/texlive/texmf-dist/tex/latex/natbib/natbib.sty archive
 
-cp `grep png short.tex|sed 's/.*figures/figures/'|sed 's/}.*//'` archive/figures
+cp --parents `grep png long.tex|sed 's/.*figures/figures/'|sed 's/}.*//'` archive/
 cp figures/expert-*-trim.png archive/figures
 tar cvf archive.tar archive/

### 2018-10-26 nips_2018.tex
long version of the paper
fixed figures

@@
   \end{figure}
-\begin{wrapfigure}{r}{8cm}
-  \vspace{-0.2cm}
-  \centering
-
-\end{wrapfigure}
 
@@
 \begin{figure}[H]
-  \begin{minipage}[t]{8.25cm}
+  \begin{minipage}[t]{9cm}
     \begin{tabular}{llll}
@@
 Compared to the specs the programs are more compressive (right: programs have fewer lines than specs) and automatically group together related drawing commands.
-Note the nested loops in second figure, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
+Note the nested loops  and conditionals in the Ising model, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
 %  \vspace{-0.6cm}
@@
      \end{minipage}&$\frac{6}{3} = 2\text{x}$\\\midrule
-%%      \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
-%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-%% Line(5,13,2,10,arrow)
-%% Circle(5,9)
-%% Circle(8,5)
-%% Line(2,8, 2,6,arrow)
-%% Circle(2,5)
-%% \end{lstlisting}
-%% \small\emph{... etc. ...; 13 lines}
-%% \end{minipage}&
-%%              \begin{minipage}{\exampleProgramSize}\begin{lstlisting}
-%% circle(4,10)
-%% for(i<3)
-%%  circle(-3*i+7,5)
-%%  circle(-3*i+7,1)
-%%  line(-3*i+7,4,-3*i+7,2,arrow)
-%%  line(4,9,-3*i+7,6,arrow)
-%% \end{lstlisting}
-%% \end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
-%%     \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
-%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-%% Circle(5,8)
-%% Circle(2,8)
-%% Circle(8,11)
-%% Line(2,9, 2,10)
-%% Circle(8,8)
-%% Line(3,8, 4,8)
-%% Line(3,11, 4,11)
-%% \end{lstlisting}
-%%   \small\emph{... etc. ...; 21 lines}
-%% \end{minipage}&\begin{minipage}{\exampleProgramSize}
-%% \begin{lstlisting}
-%% for(i<3)
-%%  for(j<3)
-%%   if(j>0)
-%%    line(-3*j+8,-3*i+7,
-%%         -3*j+9,-3*i+7)
-%%    line(-3*i+7,-3*j+8,
-%%         -3*i+7,-3*j+9)
-%%   circle(-3*j+7,-3*i+7)
-%% \end{lstlisting}
-%% \end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
+     \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
+\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
+Line(5,13,2,10,arrow)
+Circle(5,9)
+Circle(8,5)
+Line(2,8, 2,6,arrow)
+Circle(2,5)
+\end{lstlisting}
+\small\emph{... etc. ...; 13 lines}
+\end{minipage}&
+             \begin{minipage}{\exampleProgramSize}\begin{lstlisting}
+circle(4,10)
+for(i<3)
+ circle(-3*i+7,5)
+ circle(-3*i+7,1)
+ line(-3*i+7,4,-3*i+7,2,arrow)
+ line(4,9,-3*i+7,6,arrow)
+\end{lstlisting}
+\end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
+    \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
+\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
+Circle(5,8)
+Circle(2,8)
+Circle(8,11)
+Line(2,9, 2,10)
+Circle(8,8)
+Line(3,8, 4,8)
+Line(3,11, 4,11)
+\end{lstlisting}
+  \small\emph{... etc. ...; 21 lines}
+\end{minipage}&\begin{minipage}{\exampleProgramSize}
+\begin{lstlisting}
+for(i<3)
+ for(j<3)
+  if(j>0)
+   line(-3*j+8,-3*i+7,
+        -3*j+9,-3*i+7)
+   line(-3*i+7,-3*j+8,
+        -3*i+7,-3*j+9)
+  circle(-3*j+7,-3*i+7)
+\end{lstlisting}
+\end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
 \includegraphics[width = \exampleDrawingSize]{figures/expert-101-trim.png}&
@@
 %% \begin{figure}\centering
-%%   \begin{tikzpicture}
+%%   \begin{minipage}[c]{0.4\textwidth}
+%%     \begin{tikzpicture}[scale=0.8]
 %%         \node[anchor = west] at (0,5.25) {Entire program search space};
+%%         \footnotesize
 %%     \draw[fill = yellow,fill opacity = 0.15,draw = black] (0,0) rectangle (5,5);
 %%     \draw [fill = yellow, opacity = 0.2] (0,0)--(0,2)--(4,0)--(0,0);
-%%     \draw [fill = yellow, opacity = 0.4,cycle] (0,5)--(0,1)--(3,5);
-%%     \draw [fill = yellow, opacity = 0.6,cycle] (2.5,5)--(3.2,0)--(5,0)--(5,5);
+%%     \draw [fill = yellow, opacity = 0.4] (0,5)--(0,1)--(3,5);
+%%     \draw [fill = yellow, opacity = 0.6] (2.5,5)--(3.2,0)--(5,0)--(5,5);
 %%     \draw (0,2) -- node[below,sloped]{short programs} (4,0);
@@
 %%     \draw (0,1) -- node[above,sloped]{ programs w/ loops} (3,5);
-%%     \node(p1)[anchor =west ] at (5.5,3.5) {$\pi_\theta(\text{short, no loop/reflect}) = $};
-%%     \draw [fill = yellow, fill opacity = 0.2,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p1.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p1.east);
-%%     \node(p2)[anchor =west ] at ([yshift = -0.5cm]p1.west) {$\pi_\theta(\text{long, loops}) = $};
-%%     \draw [fill = yellow, fill opacity = 0.4,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p2.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p2.east);
-%%     \node(p3)[anchor =west ] at ([yshift = -0.5cm]p2.west) {$\pi_\theta(\text{long, no loop/reflect}) = $};
-%%     \draw [fill = yellow, fill opacity = 0.15,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p3.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p3.east);
-%%     \node(p4)[anchor =west ] at ([yshift = -0.5cm]p3.west) {$\pi_\theta(\text{long, reflects}) = $};
-%%     \draw [fill = yellow, fill opacity = 0.6,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p4.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p4.east);
-%%     \node(p5)[anchor =west ] at ([yshift = -0.5cm]p4.west) {\emph{etc.}};
+%%     %% \node(p1)[anchor =west ] at (5.5,3.5) {$\pi_\theta(\text{short, no loop/reflect}|S) = $};
+%%     %% \draw [fill = yellow, fill opacity = 0.2,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p1.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p1.east);
+%%     %    \node(p2)[anchor =west ] at ([yshift = -0.5cm]p1.west) {$\pi_\theta(\text{long, loops}|S) = $};
+
+%%     %% \node(p2)[anchor =west ] at (0,-0.5) {$\pi_\theta(\text{long, loops}|S) = $};
+%%     %% \draw [fill = yellow, fill opacity = 0.4,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p2.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p2.east);
+%%     %% \node(p3)[anchor =west ] at ([yshift = -0.5cm]p2.west) {$\pi_\theta(\text{long, no loop/reflect}|S) = $};
+%%     %% \draw [fill = yellow, fill opacity = 0.15,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p3.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p3.east);
+
+%%     %% \node(p4)[anchor =west ] at ([yshift = -0.5cm]p3.west) {$\pi_\theta(\text{long, reflects}|S) = $};
+%%     %% \draw [fill = yellow, fill opacity = 0.6,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p4.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p4.east);
+
+%%     %\node(p5)[anchor =west ] at ([yshift = -0.5cm]p3.west) {\emph{etc.}};
 %%   \end{tikzpicture}
+%%     \end{minipage}
+%%   \begin{minipage}[c]{0.5\textwidth}
 %%           \caption{The bias-optimal search algorithm divides the entire (intractable) program search space in to (tractable) program subspaces (written $\sigma $), each of which contains a restricted set of programs.
@@
 The policy $\pi$ predicts a distribution over program subspaces.
-The weight that $\pi$ assigns to a subspace is indicated by it's yellow shading in the above figure.}
+The weight that $\pi$ assigns to a subspace is indicated by its yellow shading in the above figure, and is conditioned on the spec $S$.}
+%%     \end{minipage}
 %%   \end{figure}
+
 Now in theory any $\pi_\theta(\cdot |\cdot ) $ is a bias-optimal searcher.
@@
 
-\vspace{1cm}
+\vspace{0.2cm}
 
@@
 
-\pagebreak
+%\pagebreak
 
@@
   \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix2.png}
-%  \includegraphics[width = \textwidth]{figures/extrapolationMatrix3.png}  
+  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix3.png}  
    \caption{Top, white: drawings. Bottom, black: extrapolations automatically produced by our system.}
-  \label{extrapolationFigure}\vspace{-0.25cm}
+  \label{extrapolationFigure}\vspace{-0.5cm}
   \end{figure}
@@
 \subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on  the neural architecture. Funding from NSF GRFP, NSF Award 
-\#1753684, and the MUSE program (DARPA grant FA8750-14-2-0242).
+\#1753684, the MUSE program (DARPA grant FA8750-14-2-0242),
+and AFOSR award FA9550-16-1-0012.
 

### 2018-10-26 makeArchive.sh

@@ -4,7 +4,9 @@ rm -r archive archive.tar
 mkdir archive
 mkdir archive/
 
-cp long.tex main.bib long.bbl nips_2018.sty /usr/share/texlive/texmf-dist/tex/latex/natbib/natbib.sty archive
+cp long.tex main.bib long.bbl nips_2018.sty archive
+#cp /usr/share/texlive/texmf-dist/tex/latex/natbib/natbib.sty archive
+cp natbib.sty archive
 
 cp --parents `grep png long.tex|sed 's/.*figures/figures/'|sed 's/}.*//'` archive/
 cp figures/expert-*-trim.png archive/figures

### 2018-11-17 long.tex
archive nonsense
fixed figures
progress on poster

@@
 % if you need to pass options to natbib, use, e.g.:
-% \PassOptionsToPackage{numbers, compress}{natbib}
+\PassOptionsToPackage{numbers}{natbib}
 % before loading nips_2018
@@
   conditionals. With a graphics program in hand, we can correct errors
-  made by the deep network and extrapolate drawings.
+  made by the deep network, measure similarity between drawings by use of similar high-level geometric structures, and extrapolate drawings.
 \end{abstract}
-
+\vspace{-0.3cm}
 \section{Introduction}
@@
     \draw [fill = yellow, opacity = 0.2] (0,0)--(0,2)--(4,0)--(0,0);
-    \draw [fill = yellow, opacity = 0.4,cycle] (0,5)--(0,1)--(3,5);
-    \draw [fill = yellow, opacity = 0.6,cycle] (2.5,5)--(3.2,0)--(5,0)--(5,5);
+    \draw [fill = yellow, opacity = 0.4] (0,5)--(0,1)--(3,5);
+    \draw [fill = yellow, opacity = 0.6] (2.5,5)--(3.2,0)--(5,0)--(5,5);
     \draw (0,2) -- node[below,sloped]{short programs} (4,0);

### 2018-11-17 nips_2018.tex
progress on poster

--- 2018-10-18 nips_2018.tex
@@
 %% \end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
-%%     \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
-%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-%% Circle(5,8)
-%% Circle(2,8)
-%% Circle(8,11)
-%% Line(2,9, 2,10)
-%% Circle(8,8)
-%% Line(3,8, 4,8)
-%% Line(3,11, 4,11)
-%% \end{lstlisting}
-%%   \small\emph{... etc. ...; 21 lines}
-%% \end{minipage}&\begin{minipage}{\exampleProgramSize}
-%% \begin{lstlisting}
-%% for(i<3)
-%%  for(j<3)
-%%   if(j>0)
-%%    line(-3*j+8,-3*i+7,
-%%         -3*j+9,-3*i+7)
-%%    line(-3*i+7,-3*j+8,
-%%         -3*i+7,-3*j+9)
-%%   circle(-3*j+7,-3*i+7)
-%% \end{lstlisting}
-%% \end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
+    \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
+\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
+Circle(5,8)
+Circle(2,8)
+Circle(8,11)
+Line(2,9, 2,10)
+Circle(8,8)
+Line(3,8, 4,8)
+Line(3,11, 4,11)
+\end{lstlisting}
+  \small\emph{... etc. ...; 21 lines}
+\end{minipage}&\begin{minipage}{\exampleProgramSize}
+\begin{lstlisting}
+for(i<3)
+ for(j<3)
+  if(j>0)
+   line(-3*j+8,-3*i+7,
+        -3*j+9,-3*i+7)
+   line(-3*i+7,-3*j+8,
+        -3*i+7,-3*j+9)
+  circle(-3*j+7,-3*i+7)
+\end{lstlisting}
+\end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
 \includegraphics[width = \exampleDrawingSize]{figures/expert-101-trim.png}&
@@
 \end{minipage}&$\frac{16}{3} = 5.3\text{x}$\\\midrule
-%% \includegraphics[width = \exampleDrawingSize]{figures/expert-75-extra-trim.png}&
-%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
-%% Line(11,14,13,14,arrow)
-%% Circle(10,10)
-%% Line(10,13,10,11,arrow)
-%% Circle(6,10)
-%% \end{lstlisting}
-%%     \small\emph{... etc. ...; 15 lines}
-%% \end{minipage}&
-%% \begin{minipage}{\exampleProgramSize}
-%%     \begin{lstlisting}
-%% for(i<4)
-%%  line(-4*i+13,4,-4*i+13,2,arrow)
-%%  for(j<3)
-%%   if(j>0)
-%%    circle(-4*i+13,4*j+-3)
-%%   line(-4*j+10,5,-4*j+12,5,
-%%        arrow)
-%% \end{lstlisting}
-%%   \end{minipage}&$\frac{15}{6} = 2.5\text{x}$\\\midrule
-
+\includegraphics[width = \exampleDrawingSize]{figures/expert-75-extra-trim.png}&
+\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
+Line(11,14,13,14,arrow)
+Circle(10,10)
+Line(10,13,10,11,arrow)
+Circle(6,10)
+\end{lstlisting}
+    \small\emph{... etc. ...; 15 lines}
+\end{minipage}&
+\begin{minipage}{\exampleProgramSize}
+    \begin{lstlisting}
+for(i<4)
+ line(-4*i+13,4,-4*i+13,2,arrow)
+ for(j<3)
+  if(j>0)
+   circle(-4*i+13,4*j+-3)
+  line(-4*j+10,5,-4*j+12,5,
+       arrow)
+\end{lstlisting}
+  \end{minipage}&$\frac{15}{6} = 2.5\text{x}$\\\midrule    
   \includegraphics[width = \exampleDrawingSize]{figures/expert-71-trim.png}&
@@
 \end{minipage}&$\frac{9}{5} = 1.8\text{x}$ \\\bottomrule
-  \end{tabular}
+  \end{tabular}\vspace{-0.5cm}
   \end{table}
@@
 We use a bias-optimal search algorithm (c.f. Schmidhuber 2004~\citep{schmidhuber2004optimal}):
-
-\noindent\textbf{Definition: Bias-optimality.} 
+\\\noindent\textbf{Definition: Bias-optimality.} 
    A search algorithm is $n$-\emph{bias optimal}
@@
 the space that the policy judges to be most promising.  Concretely,
-this means that our synthesis strategy is to run many different
+this means that we run many different
 program searches \emph{in parallel} (i.e., run in parallel different
@@
 
-%% \begin{figure}\centering
-%%   \begin{tikzpicture}
-%%     \node[anchor = west] at (0,5.25) {Entire program search space};
-%%     \draw[fill = yellow,fill opacity = 0.15,draw = black] (0,0) rectangle (5,5);
-%%     \draw [fill = yellow, opacity = 0.2] (0,0)--(0,2)--(4,0)--(0,0);
-%%     \draw [fill = yellow, opacity = 0.4,cycle] (0,5)--(0,1)--(3,5);
-%%     \draw [fill = yellow, opacity = 0.6,cycle] (2.5,5)--(3.2,0)--(5,0)--(5,5);
-%%     \draw (0,2) -- node[below,sloped]{short programs} (4,0);
-%%     \draw (0,2) -- node[above,sloped]{long programs} (4,0);
-%%     \draw (2.5,5) -- node[above,sloped]{programs w/ reflections} (3.2,0);
-%%     \draw (0,1) -- node[above,sloped]{ programs w/ loops} (3,5);
-%%     \node(p1)[anchor =west ] at (5.5,3.5) {$\pi_\theta(\text{short, no loop/reflect}) = $};
+\begin{comment}
+\begin{figure}\centering
+  \begin{minipage}[c]{0.45\textwidth}
+    \begin{tikzpicture}[scale=0.8]
+        \node[anchor = west] at (1,4.25) {Entire program search space};
+        \footnotesize
+    \draw[fill = yellow,fill opacity = 0.15,draw = black] (0,0) rectangle (7,4);
+    \draw [fill = yellow, opacity = 0.2] (0,0)--(0,2)--(7,0)--(0,0);
+    \draw [fill = yellow, opacity = 0.4] (0,4)--(0,1)--(6,4);
+    \draw [fill = yellow, opacity = 0.6] (4.5,4)--(5.2,0)--(7,0)--(7,4);
+    \draw (0,2) -- node[below,sloped]{short programs} (7,0);
+    \draw (0,2) -- node[above,sloped]{long programs} (7,0);
+    \draw[align=center] (4.5,4) -- node[above,sloped]{programs w/ \\reflections} (5.2,0);
+    \draw[align=center] (0,1) -- node[above,sloped]{ programs w/ \\loops} (6,4);
+    %% \node(p1)[anchor =west ] at (5.5,3.5) {$\pi_\theta(\text{short, no loop/reflect}|S) = $};
     %% \draw [fill = yellow, fill opacity = 0.2,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p1.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p1.east);
-%%     \node(p2)[anchor =west ] at ([yshift = -0.5cm]p1.west) {$\pi_\theta(\text{long, loops}) = $};
-%%     \draw [fill = yellow, fill opacity = 0.4,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p2.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p2.east);
-%%     \node(p3)[anchor =west ] at ([yshift = -0.5cm]p2.west) {$\pi_\theta(\text{long, no loop/reflect}) = $};
-%%     \draw [fill = yellow, fill opacity = 0.15,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p3.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p3.east);
-%%     \node(p4)[anchor =west ] at ([yshift = -0.5cm]p3.west) {$\pi_\theta(\text{long, reflects}) = $};
+    %%    \node(p2)[anchor =west ] at ([yshift = -0.5cm]p1.west) {$\pi_\theta(\text{long, loops}|S) = $};
+
+    \node(p2)[anchor =west ] at (0,-0.5) {$\pi_\theta(\text{long, loops}|S) = $};
+    \draw [fill = yellow, fill opacity = 0.4,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p2.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p2.east);
+    \node(p3)[anchor =west ] at ([yshift = -0.5cm]p2.west) {$\pi_\theta(\text{long, no loop/reflect}|S) = $};
+    \draw [fill = yellow, fill opacity = 0.15,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p3.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p3.east);
+
+    %% \node(p4)[anchor =west ] at ([yshift = -0.5cm]p3.west) {$\pi_\theta(\text{long, reflects}|S) = $};
     %% \draw [fill = yellow, fill opacity = 0.6,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p4.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p4.east);
-%%     \node(p5)[anchor =west ] at ([yshift = -0.5cm]p4.west) {\emph{etc.}};
-%%   \end{tikzpicture}
-%%   \caption{The bias-optimal search algorithm divides the entire (intractable) program search space in to (tractable) program subspaces (written $\sigma $), each of which contains a restricted set of programs.
+
+    \node(p5)[anchor =west ] at ([yshift = 8pt,xshift=20pt]p3.east) {\emph{etc.}};
+  \end{tikzpicture}
+    \end{minipage}
+  \begin{minipage}[c]{0.5\textwidth}
+          \caption{The bias-optimal search algorithm divides the entire (intractable) program search space in to (tractable) program subspaces (written $\sigma $), each of which contains a restricted set of programs.
 For example, one subspace might be short programs which don't loop.
 The policy $\pi$ predicts a distribution over program subspaces.
-The weight that $\pi$ assigns to a subspace is indicated by it's yellow shading in the above figure.}
-%%   \end{figure}
+The weight that $\pi$ assigns to a subspace is indicated by its yellow shading in the figure to the left, and is conditioned on the spec $S$.}
+    \end{minipage}\vspace{-0.5cm}
+\end{figure}
+  \end{comment}
+
 Now in theory any $\pi_\theta(\cdot |\cdot ) $ is a bias-optimal searcher.
@@
   \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix2.png}
-%  \includegraphics[width = \textwidth]{figures/extrapolationMatrix3.png}  
+  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix3.png}  
    \caption{Top, white: drawings. Bottom, black: extrapolations automatically produced by our system.}
-  \label{extrapolationFigure}\vspace{-0.25cm}
+  \label{extrapolationFigure}%\vspace{-0.8cm}
   \end{figure}
@@
 More generally, we believe the problem of inferring visual programs is a promising direction for research in machine perception.
-\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on  the neural architecture. Funding from NSF GRFP, NSF Award 
-\#1753684, and the MUSE program (DARPA grant FA8750-14-2-0242).
+\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on  the neural architecture, and for funding from NSF GRFP, NSF Award 
+\#1753684, the MUSE program (DARPA grant FA8750-14-2-0242),
+and AFOSR award FA9550-16-1-0012.
+This material is based upon work supported by the Center for Brains, Minds and Machines (CBMM), funded by NSF STC award CCF-1231216.
+
+\subsubsection*{Code, data, and drafts}
+A longer version of this paper is available at~\url{https://arxiv.org/abs/1707.09627}.
+The code and data are available at~\url{https://github.com/ellisk42/TikZ}.
 

### 2018-11-17 poster.tex
progress on poster

@@
 \newlength{\threecolwid}
-\setlength{\paperwidth}{76in} % A0 width: 46.8in
-\setlength{\paperheight}{41in} % NIPS16 : 36
+\setlength{\paperwidth}{96in} % A0 width: 46.8in
+\setlength{\paperheight}{48in} % NIPS16 : 36
 \setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
@@
 
-\author{Kevin Ellis, Daniel Ritchie, Lucas Morales, Mathias Sabl\'e Meyer,  Joshua B. Tenenbaum, Armando Solar-Lezama} % Author(s)
+\author{Kevin Ellis, Daniel Ritchie, Armando Solar-Lezama,  Joshua B. Tenenbaum} % Author(s)
 
@@
 
-  \begin{block}{Example System Outputs}
-\includegraphics[width = \textwidth]{examplePrograms.pdf} 
+  \begin{block}{Error correction}
+    `Top down' influences upon perception: reasoning engine (program synthesizer) can influence
+    agent's percept through higher-level considerations like symmetry and alignment.
+    \begin{align*}
+      \hat{S}(I) &= \argmax_{S\in \mathcal{F}(I)} L_{\text{learned}}(I | \text{render}(S))\times \probability_\theta[S|I] \times\probability_{\beta} [ \text{program}(S)] \\
+        \beta^* &= \argmax_{\beta} \expect \left[ \log \frac{\probability_{\beta} [\text{program}(S)]\times L_{\text{learned}}(I|\text{render}(S))\times \probability_\theta[S|I]}{\sum_{S'\in \mathcal{F}(I)} \probability_{\beta} [\text{program}(S')]\times L_{\text{learned}}(I|\text{render}(S'))\times \probability_\theta[S'|I]} \right]
+    \end{align*}
+    where $\mathcal{F}(I)$ is set of parses output by neural net on image $I$;
+    $\probability_\beta[\cdot ]$ is prior over programs parameterized by $\beta$;
+    and expectation is taken over a corpus of
+    program synthesis problems.
+
+    \vspace{2cm}
+    \begin{figure}
+        \includegraphics[width = 0.6\textwidth]{figures/programSuccess7.png}\hfill
+  \includegraphics[width = 0.6\textwidth]{figures/programSuccess16.png}
+  \caption{Left: hand drawings.
+Center: interpretations favored by the deep network.
+Right: interpretations favored after learning a prior over programs.
+The prior favors  simpler programs, thus (top) continuing the pattern of not having an arrow is preferred, or (bottom) continuing the ``binary search tree'' is preferred.}
+      \end{figure}
     \end{block}
 
-\begin{block}{Learning from very few examples}
-\begin{figure}[h]\centering
-  \begin{minipage}{0.45\textwidth}\centering
-    \includegraphics[width=\textwidth]{smallFractionSolving.png}
-  \caption{Results averaged across 19 problems. Solid: \theSystem{} . Dashed: enumerating 100 programs. Dotted: MDL.}\label{flashPerformance}        \end{minipage}%
-\hspace{0.025\textwidth}\begin{minipage}{0.45\textwidth}\centering
-    \includegraphics[width=0.7\textwidth]{small_mdl.png}
-    \caption{MDL learner vs \theSystem{} on one-shot learning. Predictions marginalize out the program.}\label{mdl}
-  \end{minipage}
-\end{figure}
-
-%\textbf{Multiple explanations aids one-shot learning.} After a single example, the shortest program is probably not correct -- but one of the top sampled \emph{behaviors} (marginalizing over the program) might be.
-
-\textbf{Good performance needs tilt correction.} w/o low-tilt approximation, get no samples for any of these problems after an hour, vs $\approx 1$ minute w/ \theSystem
-
-\end{block}
-
-%% \begin{block}{The Cost of Sampling}
-%%   Amortized cost of 100 samples from \theSystem :
-
-%%   \vspace{1cm}
-
-%%   \hspace{9cm}\vspace{1cm}    \begin{tabular}{lll}\toprule
-%%      1 example\hspace{0.9cm}      &  2 examples\hspace{0.9cm}          &     3 examples\\\midrule
-%% $84 \pm 3$ sec &$21 \pm 1$ sec & $49\pm 3$ sec
-%% \end{tabular}
-
-%% \textbf{Good performance needs tilt correction.} w/o low-tilt approximation, get no samples for any of these problems after an hour!
-
-%% \textbf{Can closely approximate posterior with little overhead.}
-
-%% %\vspace{-2.5cm}
-%% \begin{tabular}{cl}
-%%   \begin{tabular}{c}
-%%     \includegraphics[width=25cm]{trim-trade-off.png}
-%%     \end{tabular}&
-%%   \begin{tabular}{l}
-%%     \parbox{15cm}{Accuracy (colored contours) vs Performance (monochrome cells) trade-off; upper bounds plotted.
-Performance measured in expected solver invocations; accuracy measured in log KL divergence.}
-%%     \end{tabular}
-%% \end{tabular}
-%% %\end{figure}
-
-%%   \end{block}
 %----------------------------------------------------------------------------------------
@@
 
-  \begin{alertblock}{NEW: Wake-Sleep DSL learning with \theSystem}
-
-    \begin{minipage}[c]{0.45\textwidth}
-    \begin{itemize}
-    \item \textbf{Wake:} Synthesize programs from DSL + neural net (`recognition model') to guide search
-    \item \textbf{Sleep-G:} Grow DSL, using grammar induction algorithms
-    \item \textbf{Sleep-R:} Train neural net on programs found during waking (`experience replay') and samples from DSL (`dreaming')
-    \end{itemize}
-    \end{minipage}%
-    \begin{minipage}[c]{0.48\textwidth}      
-    \begin{tikzpicture}[scale=3,line width=1.5mm]
-    \begin{scope}[shift = {(1,-1)}]
-    \node[align = center](synthesis) at (6,4) {Search for \\programs: $p$};
-    \node[align = center](DSL) at (3,1) {DSL: $\mathcal{D}$};
-    \node[align = center](recognitionModel) at (9,1) {Recognition \\model: $Q$};
-
-    \draw [->] (synthesis.-120) to[out = -150,in = 60] node[below,rotate = 45,align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-G)}} (DSL.30);
-    \draw [->] (synthesis.-60) to[out = -30,in = 120] node[below,rotate=-45,align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-R)}} (recognitionModel.150);
-    \draw [->] (DSL.east) to[out = -30,in = 210] node[above, align = center]{{\footnotesize Trains}\\{\footnotesize (Sleep-R)}} (recognitionModel.west);
-
-    \draw [->,dashed] (DSL.north) to[out = 90,in = 180] node[fill=dblue!10,align = center]{  \footnotesize{Inductive bias}\\\footnotesize{(Wake)}} (synthesis.west);
-    \draw [->,dashed] (recognitionModel.north) to[out = 90,in = 0] node[fill=dblue!10,align = center]{{\footnotesize Makes tractable}\\{\footnotesize (Wake)}} (synthesis.east);
-  \end{scope}
-    \end{tikzpicture}
-      \end{minipage}
-  \end{alertblock}
-
-\begin{block}{\theSystem~outputs for three different task domains}
-
-\hspace{-2cm}\includegraphics[width = 1.15\textwidth]{figures/3DSL.png}
-{\small Top: Tasks from three domains we apply our algorithm to, each followed by the programs \theSystem~ discovers for them.
-Bottom: Several examples from learned DSL.
-Notice that learned DSL primitives can call each other, and that \theSystem~rediscovers higher-order functions like \code{filter} ($f_1$ under List Functions)}
-\end{block}
-
-%----------------------------------------------------------------------------------------
-%	ADDITIONAL INFORMATION
-%----------------------------------------------------------------------------------------
-
-\begin{block}{Bayesian framing}
-
-  \begin{minipage}[c]{0.45\textwidth}
-      \begin{tikzpicture}[scale=4,line width=1.5mm]
-
-  \node[latent,scale=3] at (3.5,3) (dx){$\mathcal{D}$};
-  \node[latent,scale=3] at ([xshift=2cm]dx) (zp){$p_n$};
-  \node[obs,scale=3] at ([xshift=2cm]zp) (xp) {$x_n$};
-  \plate {}{(zp)(xp)}{};
-%  \node[align = center] at ([yshift = -1.2cm,xshift = 1cm]xp.east) {(b) \\recognition model};
-  \draw [->,red] (xp.south) to[out = -90,in = -90] node(nn){} (zp.south);
-%  \draw [->,red] (tx.west) -- (zp.east);
-  \draw [->] (dx.east) -- (zp.west);
-  \draw [->] (zp.east) -- (xp.west);
-
-  \node at (nn) {
-    \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=0.5,shift={+(-1,2.5)}}]
-      \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
-      \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
-      \node[rectangle] at (1,1) {};
-      \foreach \name / \y in {1,...,4}
-          \node[neuron] (I-\name) at (0,-\y) {};
-      \foreach \name / \y in {1,...,3}
-          \node[neuron] (H-\name) at (1,-\y-0.5) {};
-      \foreach \name / \y in {1,...,4}
-          \node[neuron] (O-\name) at (2,-\y) {};
-      \foreach \source in {1,...,4}
-          \foreach \dest in {1,...,3}
-              \draw [-latex] (I-\source) -- (H-\dest);
-      \foreach \source in {1,...,3}
-          \foreach \dest in {1,...,4}
-              \draw [-latex] (H-\source) -- (O-\dest);
-    \end{tikzpicture}
-  };
-  \node[shift={+(0,-1.7)}] at (nn) { $Q$  };
-
-      \end{tikzpicture}
-      $x_n$: program synthesis problem. $p_n$: (latent) program solving $x_n$. $Q(p|x)$: (learned) neural recognition model. $\mathcal{D}$: (latent) DSL.
-  \end{minipage}\qquad%
-  \begin{minipage}[c]{0.4\textwidth}
-
-  $$
-\underbrace{p_n^* =   \argmax_{p_n}\probability[x_n|p_n]\probability[p_n|\mathcal{D}^*]}_{\text{\textbf{Wake}}}
-$$
-\vspace{0.5cm}
-$$
-\underbrace{\mathcal{D}^* = \argmax_{\mathcal{D}}    \probability[\mathcal{D}]\prod_n\sum_{p_n}\probability[x_n|p_n]\probability[p_n|\mathcal{D}]}_{\textbf{\text{Sleep-G}}}
-$$
-\vspace{0.5cm}
-$$\underbrace{Q^* = \argmin_Q \text{KL}\left(\probability[p|x,\mathcal{D}] || Q(p|x)\right) }_{\text{\textbf{Sleep-R}}}$$
-    \end{minipage}
-
+      \begin{block}{Example System Outputs}
+\includegraphics[width = \textwidth]{examplePrograms.pdf} 
 \end{block}

### 2018-11-17 supplement.tex
progress on poster

@@
  \texttt{daniel\_ritchie@brown.edu} \\
- \And
+ \AND
  Armando Solar-Lezama\\
@@
 \section{Learning a search policy}
+
+Figure~\ref{yellow} provides additional intuition for
+how the policy biases and informs the program synthesizer:
+the entire program search space is carved up into smaller subsets,
+and we search within each of these subsets \emph{simultaneously and in parallel},
+but where the fraction of
+compute time allocated to each subset
+is proportional to the weight assigned to it by the policy.
+
+\begin{figure}\centering
+  \begin{tikzpicture}
+    \node[anchor = west] at (0,5.25) {Entire program search space};
+    \draw[fill = yellow,fill opacity = 0.15,draw = black] (0,0) rectangle (5,5);
+    \draw [fill = yellow, opacity = 0.2] (0,0)--(0,2)--(4,0)--(0,0);
+    \draw [fill = yellow, opacity = 0.4] (0,5)--(0,1)--(3,5);
+    \draw [fill = yellow, opacity = 0.6] (2.5,5)--(3.2,0)--(5,0)--(5,5);
+    \draw (0,2) -- node[below,sloped]{short programs} (4,0);
+    \draw (0,2) -- node[above,sloped]{long programs} (4,0);
+    \draw (2.5,5) -- node[above,sloped]{programs w/ reflections} (3.2,0);
+    \draw (0,1) -- node[above,sloped]{ programs w/ loops} (3,5);
+    \node(p1)[anchor =west ] at (5.5,3.5) {$\pi_\theta(\text{short, no loop/reflect}|S) = $};
+    \draw [fill = yellow, fill opacity = 0.2,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p1.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p1.east);
+    \node(p2)[anchor =west ] at ([yshift = -0.5cm]p1.west) {$\pi_\theta(\text{long, loops}|S) = $};
+    \draw [fill = yellow, fill opacity = 0.4,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p2.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p2.east);
+    \node(p3)[anchor =west ] at ([yshift = -0.5cm]p2.west) {$\pi_\theta(\text{long, no loop/reflect}|S) = $};
+    \draw [fill = yellow, fill opacity = 0.15,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p3.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p3.east);
+    \node(p4)[anchor =west ] at ([yshift = -0.5cm]p3.west) {$\pi_\theta(\text{long, reflects}|S) = $};
+    \draw [fill = yellow, fill opacity = 0.6,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p4.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p4.east);
+    \node(p5)[anchor =west ] at ([yshift = -0.5cm]p4.west) {\emph{etc.}};
+  \end{tikzpicture}
+  \caption{The bias-optimal search algorithm divides the entire (intractable) program search space in to (tractable) program subspaces (written $\sigma $), each of which contains a restricted set of programs.
+For example, one subspace might be short programs which don't loop.
+The policy $\pi$ predicts a distribution over program subspaces.
+The weight that $\pi$ assigns to a subspace is indicated by its yellow shading in the above figure, and is conditioned on the spec $S$.}\label{yellow}
+  \end{figure}
+
 \subsection{Modeling}\label{searchPolicyModel}

### 2018-11-17 poster.tex
TikZ poster finished!

@@
 \makeatletter
-\patchcmd{\beamer@@tmpl@headline}{wd=47in}{wd=75in}{}{}
+\patchcmd{\beamer@@tmpl@headline}{wd=47in}{wd=95in}{}{}
 \makeatother
@@
 {\begin{tikzpicture}[remember picture, overlay]
-     \node [anchor=north east, inner sep=3cm]  at (current page.north east)
+     \node [anchor=north east, inner sep=3cm]  at ([yshift=2cm]current page.north east)
+           {\includegraphics[height=10cm]{figures/Brown.png}};
+                \node [anchor=north west, inner sep=3cm]  at (current page.north west)
      {\includegraphics[height=7cm]{figures/csail.png}};
-                \node [anchor=north west, inner sep=3cm]  at (current page.north west)
-     {\includegraphics[height=5cm]{figures/bcs.png}};
 \end{tikzpicture}}
@@
 
-\begin{block}{Two-Stage Pipeline}
-\hspace{-5cm}  \includegraphics[width = 50cm]{pipeline.pdf}
+      \begin{block}{Example System Outputs}
+\includegraphics[width = \textwidth]{examplePrograms.pdf} 
+      \end{block}
 
-  Black arrows: Top--down generative model; Program$\to$Spec$\to$Image. {\color{red}Red} arrows: Bottom--up inference procedure. \textbf{Bold:} Random variables (image/spec/program)
-\end{block}
+      \begin{alertblock}{\red Acknowledgments}
+         We are grateful for advice from Will Grathwohl and Jiajun Wu on  the neural architecture. Funding from NSF GRFP, NSF Award 
+\#1753684, the MUSE program (DARPA grant FA8750-14-2-0242),
+and AFOSR award FA9550-16-1-0012.
+        \end{alertblock}
 
@@
 %----------------------------------------------------------------------------------------
-
-\begin{block}{Parsing Images into Drawing Commands (specs)}
-\vspace{-3cm}  \includegraphics[width = 40cm]{architecture.pdf}
-
-{\small   \textcolor{blue}{Blue}: network inputs.
-Black: network operations.
-\textcolor{red}{Red}: draws from a multinomial.
-\texttt{Typewriter font}: network outputs.
-Renders on a $16\times 16$ grid, shown in \textcolor{gray}{gray}.
-STN: differentiable attention mechanism.
-\textbf{Combined with stochastic search (Sequential Monte Carlo)}}
-
-%\begin{figure}[h]\centering
-  \begin{minipage}[c]{0.49\textwidth} 
-    \centering  \includegraphics[width = \textwidth]{figures/drawingAccuracy.png}            \vspace{-0.5cm} 
-  \end{minipage}\hfill%
-      \begin{minipage}[c]{0.5\textwidth} 
-  {\small (Left) NN outputs vs ground truth on hand drawings (measured by IoU), as we consider larger sets of samples (1, 5, 100).
-     (a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 5 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth.
-Red: the full model.
-Other colors: ablations.
-Model is at ceiling for synthetic $\LaTeX$ output.}
-      \end{minipage}
-
-%\end{figure}
-\end{block}
 
@@
 \begin{column}{\twocolwid} % Begin a column which is two columns wide (column 2)
+
+  \begin{block}{Two-Stage Pipeline}
+\centering  \includegraphics[width = 80cm]{pipeline.pdf}
+
+  Black arrows: Top--down generative model; Program$\to$Spec$\to$Image. {\color{red}Red} arrows: Bottom--up inference procedure. \textbf{Bold:} Random variables (image/spec/program)
+\end{block}
 
@@
 %%\end{alertblock}
+
+\begin{block}{Parsing Images into Drawing Commands (specs)}
+\hspace{10cm}  \includegraphics[width = 40cm]{architecture.pdf}
+
+{\small   \textcolor{blue}{Blue}: network inputs.
+Black: network operations.
+\textcolor{red}{Red}: draws from a multinomial.
+\texttt{Typewriter font}: network outputs.
+Renders on a $16\times 16$ grid, shown in \textcolor{gray}{gray}.
+STN: differentiable attention mechanism.
+\textbf{Combined with stochastic search (Sequential Monte Carlo)}}
+
+\end{block}
+
+\begin{block}{Generalizing to real hand drawings}
+  \textbf{  Train on simulated noisy data (left) \& learn distance metric between images (right)}\\
+  \newcommand{\noisySize}{0.2\textwidth}
+  \begin{minipage}[t]{\noisySize}
+    \centering\includegraphics[width = \textwidth]{figures/expert-60-reduced.png}\\
+{\small     (a): hand drawing}
+  \end{minipage}%
+  \begin{minipage}[t]{\noisySize}
+    \centering\includegraphics[width = \textwidth]{figures/60-1-reduced.png}\\
+{\small     (b): noisy render of (a)}
+  \end{minipage}\hfill%
+  \begin{minipage}[t]{0.5\textwidth}\vspace{-9cm}
+    \textbf{Learned distance metric}\\
+    Serves as likelihood surrogate for SMC
+      \begin{align*}
+    -\log L_{\text{learned}}(\text{render}&(S_1)|\text{render}(S_2))\approx\\& |S_1 - S_2| + |S_2 - S_1|\label{symmetricDistance}
+      \end{align*}
+      $S_1$: noisy render of random scene\\
+      $S_2$: nonnoisy render of random scene
+  \end{minipage}%
+
+  \vspace{3cm}
+
+    \begin{minipage}[c]{0.49\textwidth} 
+    \centering  \includegraphics[width = \textwidth]{figures/drawingAccuracy.png}            \vspace{-0.5cm} 
+  \end{minipage}\hfill%
+      \begin{minipage}[c]{0.5\textwidth} 
+  {\small (Left) NN outputs vs ground truth on hand drawings (measured by IoU), as we consider larger sets of samples (1, 5, 100).
+     (a) for 63\% of drawings the model's top prediction is exactly correct; (b) for 70\% of drawings the ground truth is in the top 5 model predictions; (c) for 4\% of drawings all of the model outputs have no overlap with the ground truth.
+Red: the full model.
+Other colors: ablations.
+Model is at ceiling for synthetic $\LaTeX$ output.}
+      \end{minipage}
+
+  \end{block}
+
+%----------------------------------------------------------------------------------------
+
+\end{column} % End of column 2.1
+
+\begin{column}{\onecolwid}\vspace{-.6in} % The second column within column 2 (column 2.2)
+
+%----------------------------------------------------------------------------------------
+%	METHODS
+%----------------------------------------------------------------------------------------
 
@@
 
-\includegraphics[width = \textwidth]{figures/policyComparison_basic_DC+bias_20.png}
+\begin{flushright}
+  Experimental results on synthesis policy: See lower right of poster
+  \end{flushright}
 
-Time to synthesize a minimum cost program.
-Sketch: out-of-the-box performance of Sketch.
-DC: Deep--Coder style baseline that predicts program components, trained like Balog 2016.
-Oracle:  upper bounds  the performance of any bias--optimal search policy.
-$\infty = $ timeout.
-Red dashed line is median time
-  \end{block}
-
-%----------------------------------------------------------------------------------------
-
-\end{column} % End of column 2.1
-
-\begin{column}{\onecolwid}\vspace{-.6in} % The second column within column 2 (column 2.2)
-
-%----------------------------------------------------------------------------------------
-%	METHODS
-%----------------------------------------------------------------------------------------
-
-  \begin{block}{Extrapolating Drawings}
-    Automatically extrapolate by increasing loop bounds. Top white: Hand drawing. Bottom black: extrapolation.
-
-      \includegraphics[width = \textwidth]{figures/extrapolationMatrix1.png}\\
-  \includegraphics[width = \textwidth]{figures/extrapolationMatrix2.png}\\
-  \includegraphics[width = \textwidth]{figures/extrapolationMatrix3.png}  \\
-  \end{block}
-
-  \begin{block}{Error correction}
-    `Top down' influences upon perception: reasoning engine (program synthesizer) can influence
-    agent's percept through higher-level considerations like symmetry and alignment.
-    \begin{align*}
-      \hat{S}(I) &= \argmax_{S\in \mathcal{F}(I)} L_{\text{learned}}(I | \text{render}(S))\times \probability_\theta[S|I] \times\probability_{\beta} [ \text{program}(S)] \\
-        \beta^* &= \argmax_{\beta} \expect \left[ \log \frac{\probability_{\beta} [\text{program}(S)]\times L_{\text{learned}}(I|\text{render}(S))\times \probability_\theta[S|I]}{\sum_{S'\in \mathcal{F}(I)} \probability_{\beta} [\text{program}(S')]\times L_{\text{learned}}(I|\text{render}(S'))\times \probability_\theta[S'|I]} \right]
-    \end{align*}
-    where $\mathcal{F}(I)$ is set of parses output by neural net on image $I$;
-    $\probability_\beta[\cdot ]$ is prior over programs parameterized by $\beta$;
-    and expectation is taken over a corpus of
-    program synthesis problems.
-
-    \vspace{2cm}
-    \begin{figure}
-        \includegraphics[width = 0.6\textwidth]{figures/programSuccess7.png}\hfill
-  \includegraphics[width = 0.6\textwidth]{figures/programSuccess16.png}
-  \caption{Left: hand drawings.
-Center: interpretations favored by the deep network.
-Right: interpretations favored after learning a prior over programs.
-The prior favors  simpler programs, thus (top) continuing the pattern of not having an arrow is preferred, or (bottom) continuing the ``binary search tree'' is preferred.}
-      \end{figure}
   \end{block}
@@
 
-      \begin{block}{Example System Outputs}
-\includegraphics[width = \textwidth]{examplePrograms.pdf} 
+  \begin{block}{Extrapolating Drawings}
+    Automatically extrapolate by increasing loop bounds. Top white: Hand drawing. Bottom black: extrapolation.
+
+      \includegraphics[width = \textwidth]{figures/extrapolationMatrix1.png}\\
+  \includegraphics[width = \textwidth]{figures/extrapolationMatrix2.png}\\
+  \includegraphics[width = \textwidth]{figures/extrapolationMatrix3.png}  \\
+  \end{block}
+
+  \begin{block}{Error correction}
+    `Top down' influences upon perception: reasoning engine (program synthesizer) can influence
+    agent's percept through higher-level considerations like symmetry and alignment.
+    \begin{align*}
+      \hat{S}(I) &= \argmax_{S\in \mathcal{F}(I)} L_{\text{learned}}(I | \text{render}(S))\times \probability_\theta[S|I] \times\probability_{\beta} [ \text{program}(S)] \\
+        \beta^* &= \argmax_{\beta} \expect \left[ \log \frac{\probability_{\beta} [\text{program}(S)]\times L_{\text{learned}}(I|\text{render}(S))\times \probability_\theta[S|I]}{\sum_{S'\in \mathcal{F}(I)} \probability_{\beta} [\text{program}(S')]\times L_{\text{learned}}(I|\text{render}(S'))\times \probability_\theta[S'|I]} \right]
+    \end{align*}
+    where $\mathcal{F}(I)$ is set of parses output by neural net on image $I$;
+    $\probability_\beta[\cdot ]$ is prior over programs parameterized by $\beta$;
+    and expectation is taken over a corpus of
+    program synthesis problems.
+
+    \vspace{2cm}
+    \begin{figure}
+        \includegraphics[width = 0.5\textwidth]{figures/programSuccess7.png}\\
+  \includegraphics[width = 0.5\textwidth]{figures/programSuccess16.png}
+  \caption{Left: hand drawings.
+Center: interpretations favored by the deep network.
+Right: interpretations favored after learning a prior over programs.
+The prior favors  simpler programs, thus (top) continuing the pattern of not having an arrow is preferred, or (bottom) continuing the ``binary search tree'' is preferred.}
+    \end{figure}
+\vspace{-1cm}
+  \end{block}
+
+  \begin{block}{Synthesis times}    
+    \includegraphics[width = \textwidth]{figures/policyComparison_basic_DC+bias_20.png}
+
+{\small Time to synthesize a minimum cost program.
+Sketch: out-of-the-box performance of Sketch.
+DC: Deep--Coder style baseline that predicts program components, trained like Balog 2016.
+Oracle:  upper bounds  the performance of any bias--optimal search policy.
+$\infty = $ timeout.
+Red dashed line is median time}
     \end{block}

### 2018-12-05 spotlight.tex
spotlight before Armando revision

\documentclass[aspectratio=169,final]{beamer}
\setbeamersize{text margin left=5pt,text margin right=5pt}
\setbeamertemplate{navigation symbols}{}

\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tikz}

\usepackage{amsmath}
\newcommand{\expect}{\mathds{E}} %{{\rm I\kern-.3em E}}
\newcommand{\probability}{\mathds{P}} %{{\rm I\kern-.3em P}}
\newcommand{\indicator}{\mathds{1}} %{{\rm I\kern-.3em P}}
\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays
\DeclareMathOperator*{\argmin}{arg\,min} % thin space, limits underneath in displays

\begin{document}

\begin{frame}{\centering  Learning to Infer Graphics Programs from Hand-Drawn Images\\
    \centering\small  Kevin Ellis$^1$, Daniel Ritchie$^2$, Armando Solar-Lezama$^1$, Joshua B. Tenenbaum$^1$\\
  \small   $^1$: MIT. $^2$: Brown University.}
\centering
  \begin{tabular}{lllll}
\visible<2->{    \includegraphics[height = 0.1\textwidth]{figures/staircase}}&
\visible<3->{    \includegraphics[height = 0.1\textwidth]{figures/tree}}&
\visible<4->{    \includegraphics[height = 0.1\textwidth]{figures/gears}}&
\visible<5->{    \includegraphics[height = 0.1\textwidth]{figures/Simmons}&
        \includegraphics[height = 0.1\textwidth]{figures/randomFields}}
  \end{tabular}

  \vspace{.1cm}

\visible<6->{    \includegraphics[width = 0.9\textwidth]{firstSpotlightExample.pdf}}

  \end{frame}

\begin{frame}{Image$\to$Program Pipeline}
\centering  \includegraphics[width = 0.76\textwidth]{pipeline.pdf}

\vspace{1cm}

  \includegraphics[width = 0.7\textwidth]{exampleProgramsSpotlight.pdf}
\end{frame}

\begin{frame}{Parsing images into \LaTeX~TikZ Commands}

  %% \vspace{-0.5cm}
{\footnotesize  Neurally Guided Procedural Modeling (Ritchie et al 2016) + Attend, Infer, Repeat (Eslami et al 2016)}
  \vspace{-0.5cm}
  \begin{center}
    \begin{tabular}{c}
\raisebox{-.5\height}{    \includegraphics[width = 0.6\textwidth]{architecture.pdf}            }
%%       &
%% \raisebox{-.5\height}{\includegraphics[width = 0.3\textwidth]{figures/averageNumberOfErrors.png}}
      \end{tabular}

  \end{center}
    \newcommand{\noisySize}{0.12\textwidth}
    \visible<2->{
\hspace{0.1\textwidth}      \begin{minipage}[t]{\noisySize}
        \centering\includegraphics[width = \textwidth]{figures/expert-60-reduced.png}\\
                                  {\small     (a): hand drawing}
      \end{minipage}%
      \begin{minipage}[t]{\noisySize}
        \centering\includegraphics[width = \textwidth]{figures/60-1-reduced.png}\\
                                  {\small     (b): noisy render of (a)'s spec}
      \end{minipage}}%
    %% \visible<3->{\begin{minipage}{0.35\textwidth}
    %%     \begin{flushright}
    %%       \textbf{Learned distance metric}\\
    %%       \small    Serves as likelihood surrogate
    %%       \begin{align*}
    %%         \displaystyle\qquad    -\log L_{\text{learned}}(\text{render}&(S_1)|\text{render}(S_2))\approx\\& |S_1 - S_2| + |S_2 - S_1|
    %%       \end{align*}
    %%       $S_1$: noisy render\\
    %%       $S_2$: nonnoisy render
    %%     \end{flushright}
    %% \end{minipage}}%
    \hspace{0.2\textwidth}%
    \visible<3->{\begin{minipage}[c]{0.3\textwidth}
\vspace{-0.4cm}      \includegraphics[width = 0.8\textwidth]{figures/evaluationPhase1}
    \end{minipage}}
\end{frame}

\begin{frame}{Parsing images into \LaTeX~TikZ Commands}

  %% \vspace{-0.5cm}
{\footnotesize  Neurally Guided Procedural Modeling (Ritchie et al 2016) + Attend, Infer, Repeat (Eslami et al 2016)}
  \vspace{-0.5cm}
  \begin{center}
    \begin{tabular}{c}
\raisebox{-.5\height}{    \includegraphics[width = 0.6\textwidth]{architecture.pdf}            }
%%       &
%% \raisebox{-.5\height}{\includegraphics[width = 0.3\textwidth]{figures/averageNumberOfErrors.png}}
      \end{tabular}

  \end{center}
    \newcommand{\noisySize}{0.12\textwidth}
    \visible<1->{
\hspace{0.1\textwidth}      \begin{minipage}[t]{\noisySize}
        \centering\includegraphics[width = \textwidth]{figures/expert-60-reduced.png}\\
                                  {\small     (a): hand drawing}
      \end{minipage}%
      \begin{minipage}[t]{\noisySize}
        \centering\includegraphics[width = \textwidth]{figures/60-1-reduced.png}\\
                                  {\small     (b): noisy render of (a)'s spec}
      \end{minipage}}%
    %% \visible<3->{\begin{minipage}{0.35\textwidth}
    %%     \begin{flushright}
    %%       \textbf{Learned distance metric}\\
    %%       \small    Serves as likelihood surrogate
    %%       \begin{align*}
    %%         \displaystyle\qquad    -\log L_{\text{learned}}(\text{render}&(S_1)|\text{render}(S_2))\approx\\& |S_1 - S_2| + |S_2 - S_1|
    %%       \end{align*}
    %%       $S_1$: noisy render\\
    %%       $S_2$: nonnoisy render
    %%     \end{flushright}
    %% \end{minipage}}%
    \hspace{0.2\textwidth}%
    \visible<1->{\begin{minipage}[c]{0.3\textwidth}
\vspace{-0.4cm}      \includegraphics[width = 0.8\textwidth]{figures/evaluationPhase2}
    \end{minipage}}
\end{frame}

\begin{frame}{Synthesizing high-level programs from specs (spec$ = $drawing commands)}
  Constraint-based program synthesis; SAT solver (Solar-Lezama 2008)
  \begin{equation*}
  %  \text{program}(S) = \argmin_{p\in \text{DSL, s.t. }p \text{ consistent w/ } S} \text{cost}(p)\label{programObjective}
    \text{program}(S) = \argmin_{\substack{p\in \text{DSL}\\p\text{ consistent w/ }S}} \text{cost}(p)
  \end{equation*}
  min cost$\approx$simple+short\\
  DSL: \textbf{D}omain \textbf{S}pecific \textbf{L}anguage: variables, arithmetic, loops, conditionals

  \vspace{0.8cm}

\footnotesize\centering    \begin{tabular}{rl}\toprule
  Program$\to$&Statement; $\cdots$; Statement\\
  Statement$\to$&\texttt{circle}(Expression,Expression)\\
  Statement$\to$&\texttt{rectangle}(Expression,Expression,Expression,Expression)\\
  Statement$\to$&\texttt{line}(Expression,Expression,Expression,Expression,Boolean,Boolean)\\
  Statement$\to$&\texttt{for}$(0\leq \text{Var}  < \text{Expression})$\texttt{ \{ if }$(\text{Var} > 0)$\texttt{ \{ }Program\texttt{ \}; }Program\texttt{ \}}\\
  Statement$\to$&\texttt{reflect}$(\text{Axis})$\texttt{ \{ }Program\texttt{ \}}\\
  Expression$\to$&$\mathbb{Z}\times$Var\texttt{+}$\mathbb{Z}$\\
%  Var$\to$&A free (unused) variable\\
  Axis$\to$&\texttt{X = }$\mathbb{Z}$ \vert \texttt{Y = }$\mathbb{Z}$\\
    $\mathbb{Z}\to$&an integer\\\bottomrule
  \end{tabular}

\end{frame}

\begin{frame}{Learning to quickly synthesize programs}
    Learn search policy $\pi (\text{program subspace} | \text{spec})$
  \\Think of the subspace as an ``ansatz''

OBJECTIVE (cf Bias-Optimal Search, Schmidhuber 2004):  $$\pi^* = \argmin_\pi\sum_{\text{spec}}\min_{\substack{\text{all subspaces}\\\text{subspace solves spec}}} \frac{\mathbb{E}[\text{time to exhaustively search the subspace}]}{\pi (\text{subspace}|\text{spec})}$$

  \vspace{-0.15cm}
    \begin{tikzpicture}[scale=0.8]
    \node[anchor = west] at (0,5.25) {Entire program search space};
\footnotesize    \draw[fill = yellow,fill opacity = 0.15,draw = black] (0,0) rectangle (5,5);
    \draw [fill = yellow, opacity = 0.2] (0,0)--(0,2)--(4,0)--(0,0);
    \draw [fill = yellow, opacity = 0.4] (0,5)--(0,1)--(3,5);
    \draw [fill = yellow, opacity = 0.6] (2.5,5)--(3.2,0)--(5,0)--(5,5);
    \draw (0,2) -- node[below,sloped]{short programs} (4,0);
    \draw (0,2) -- node[above,sloped]{long programs} (4,0);
    \draw (2.5,5) -- node[above,sloped]{programs w/ reflections} (3.2,0);
    \draw (0,1) -- node[above,sloped]{ programs w/ loops} (3,5);
    \node(p1)[anchor =west ] at (5.0,3.5) {$\pi(\text{short, no loop/reflect}|S) = $};
    \draw [fill = yellow, fill opacity = 0.2,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p1.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p1.east);
    \node(p2)[anchor =west ] at ([yshift = -0.5cm]p1.west) {$\pi(\text{long, loops}|S) = $};
    \draw [fill = yellow, fill opacity = 0.4,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p2.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p2.east);
    \node(p3)[anchor =west ] at ([yshift = -0.5cm]p2.west) {$\pi(\text{long, no loop/reflect}|S) = $};
    \draw [fill = yellow, fill opacity = 0.15,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p3.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p3.east);
    \node(p4)[anchor =west ] at ([yshift = -0.5cm]p3.west) {$\pi(\text{long, reflects}|S) = $};
    \draw [fill = yellow, fill opacity = 0.6,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p4.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p4.east);
    \node(p5)[anchor =west ] at ([yshift = -0.5cm]p4.west) {\emph{etc.}};
\visible<2->{        \node at (15.2,3) {\includegraphics[width = 3.6cm]{figures/2policyComparison}};}
  \end{tikzpicture}

\end{frame}

\begin{frame}{Application: Error correction}
  \textbf{learn prior over programs (simple$\approx$better), jointly infer likely parse+program}\\
  \textbf{Top-down influence upon perception}

  \vspace{0.4cm}

\def\arraystretch{0.0}
  \centering\begin{tabular}{p{3cm}p{3cm}p{3cm}}
\toprule     \centering Drawing&Neural net output&Corrected output\\\midrule 
\multicolumn{3}{c}{        \includegraphics[width = 9cm]{figures/programSuccess7.png} }\\
\multicolumn{3}{c}{        \includegraphics[width = 9cm]{figures/programSuccess16.png} }

    \end{tabular}

\end{frame}

\begin{frame}{Application: Extrapolating drawings}
  \centering  \includegraphics[height = 0.3\textheight]{figures/extrapolationMatrix1.png}
\\  \includegraphics[height = 0.3\textheight]{figures/extrapolationMatrix2.png}
\\  \includegraphics[height = 0.3\textheight]{figures/extrapolationMatrix3.png}

\end{frame}

\begin{frame}{\Huge Visual input$\to$Program: Poster AB \#25}

  \centering  \includegraphics[width = 0.8\textwidth]{firstSpotlightExample.pdf}
  \vspace{1cm}
\\\centering  \includegraphics[height = 0.3\textheight]{figures/extrapolationMatrix3.png}

  \end{frame}

\end{document}
